### 2018-09-07 outputs/docs/paper/notes.Rmd
Hope this works

---
title: "Does parliament matter for Australian government policy?"
author: Rohan Alexander
date: "`r format(Sys.time(), '%d %B %Y')`"
# output: 
#   pdf_document: 
#     latex_engine: xelatex
output:  
  bookdown::pdf_document2:
    fig_caption: yes
    latex_engine: xelatex

bibliography: bibliography.bib
fontsize: 12pt
number_sections: yes
#geometry: margin=2in
  # :
  #   toc: true
  #   toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h')
```

# Introduction
<!--
Australian federal government spending is expected to account for about 26 per cent of GDP in 2016-17, and over the past 40 years it has averaged 24.9 per cent (2016-17 Budget Paper No.1, Table 10). Government spending is an important part of GDP but we do not have a good understanding of how governments decide on their eventual spending decision, or even how much of an impact a government has on government spending. Anecdotally, the answer seems to be considered obvious, but no one seems to be able to agree on what that obvious answer is. That is what this paper is about.

From a political institutions perspective, a strict separation of powers suggests that Australia's parliament would be the preeminent institution determining government spending. Hansard is the written record of what was said in parliament. So, it should be possible to analyse Hansard to see if parliament does in fact determine government spending. In Australia, the members of the executive -- cabinet -- must also be members of the legislative -- parliament. So even if spending were determined by the executive then Hansard should have explanatory power.

A literature in political economy examines government spending as an outcome of politicians trying to, for instance: get re-elected, fulfil campaign pledges, or express partisan preferences (for a summary see, for instance, @Benassy-Quere2010 [p. 9]). And it is undeniable that politicians in a liberal democracy have considerable scope to allocate spending at the level of hundreds-of-thousands, or millions, of dollars. But it is not so clear that they have an impact on spending on a macroeconomic level. In order for that political economy literature on why politicians affect government spending to be important, it must be established whether they even affect it to a significant degree.

This paper is at the intersection of positive economics, in that it looks at the impact of policy on the economy, and political economy, in that it examines how those policy decisions are made. In this paper, I analyse 'who said what' in Australia's parliament and how politicians voted. I then use this to explain disaggregated government spending. I use Hansard as the record of what was said in parliament and who said it. -->

Hansard provides a record of all debates in the Commonwealth parliament. The stability of Australia's government over this period, and the division of power between the federal and state governments make Australia especially well-disposed for analysis. Also, @ButlinBarnardPincus1982 [p. 4] argue, Australian governments have played a larger role 'throughout virtually the whole of Australian history in all decision-making processes' and have been a 'much more significant' influence on the economy than in comparable countries.

Using natural language processing I attribute a topic to each statement in Hansard. I then classify whether the statement is objective or subjective, and whether subjective statements are positive or negative. This creates a dataset of the opinions that parliamentarians held on various topics over time. From other sources, I add information about the role of the parliamentarian at the time they made that statement. **[Expand/amend as completed.]**

Government spending data is available from various sources and at various levels of disaggregation. Initially, I just examine total government spending, but I also disaggregate the spending into various areas. **[Expand/amend as completed.]**

<!--
The contribution of this paper is to bring separate threads in existing economics literatures to analyse whether what is said in parliament affects government spending. If parliament in a liberal democracy is essentially just a 'talk shop' with little actual impact on government spending, then analysis of government spending would need to focus on other institutions. Alternatively, if parliament plays an important role, then further analysis of how these government spending decisions occur is needed. Either way, there are implications for our understanding of the institutions that determine about a quarter of GDP.
-->

# Literature
<!--
This paper fits into the traditions of both positive economics and political economy and builds on existing economics literatures. The Hansard records of other countries have been analysed using natural language processing, albeit not for this purpose. And the Australian Hansard record has been examined by hand. Similarly, while there has been much analysis of the impact of different political institutions and the efficiency of government spending, there has not been much examination of what happens within parliament.
-->

## Hansard analysis
@Whyte2014 uses Canadian and UK Hansard records to analyse whether parliamentary disruptions have increased in those countries since 1994. Python is used to process Hansard XML files and then the frequency of interruptions by the members of parliament or calls for order from the speaker is determined. (Using similar methods @Willis2017 examines the UK Climate Change Bill to understand how politicians understand and articulate climate change.) @Whyte2014 is limited to frequency comparisons because the digitised Canadian Hansard was, at that time, only available to 1993. Subsequently the Canadian Hansard was digitised, as described by @BeelenEtc2017.

That digitisation of the Canadian Hansard allowed @Whyte2017 to examine the same question over a longer time-frame -- 1926 to 2015 -- and with more sophisticated methods. @Whyte2017 codes Hansard so that a speech fragment is one of five states: a government backbencher speaking; a minister speaking; an opposition member speaking; an interruption; or a statement by the Speaker of the House. The state of a speech fragment is then considered as an explanatory variable for the state of the next speech fragment in a multinomial logit model. The dataset has 3.1 million speeches of which about five per cent are interruptions. Future work is planned to extend the analysis to consider tone and context.

@Duthie2016 analyse UK Hansard records using natural language processing to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990. For each statement four tags were applied: source-person, target-person, support, attack. @Duthie2016 use the Stanford Named Entity Recognizer to extract statements that contain names, organisations and locations, and then the Stanford Part-of-Speech Tagger to extract statements that contain pronouns. @Duthie2016 add domain specific rules to account for the language nuances of the parliament, and then use the Stanford Classifier Library, which uses supervised learning techniques, and the Sentiment Word Lexicon which contains 2,006 words tagged as positive and 4,738 words tagged as negative to analyse sentiment. They find that changes in language are associated with periods of political change, for instance when there was infighting in the Labour Party and when Margaret Thatcher became prime minister.

@GrijzenhoutMarxJijkoun2014 examine various natural language processing options in the context of the Dutch House of Representatives. After hand coding a corpus, they compare the results of various automated processes. They find that machine-learning algorithms perform the best and provide a helpful summary of many different processes. Dutch parliamentary records are particularly rich because DutchParl provides a digital corpus of all parliamentary documents, as detailed in @MarxSchuth2010

More generally, Hansard records have been analysed for various purposes. For instance, @Rasiah2010 examines Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003. @GansLeigh2012 examined Australian Hansard records by hand to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment. @Willis2017 looks at a corpus of 97,000 words from UK Hansard records to try to understand how politicians understand climate change. @SealeyBates2016 examine the responses of British Prime Ministers to find that their focus on cognitive and communicative processes. @Graham2016 examines Hansard records for New Zealand between 1890 and 1950 to analyse unparliamentary language. And @WilkersonSmithStramp2015 looks for similarities in how legislation is written in the US.

More recently, @Curran2017 consider New Zealand parliament's Hansard to model the topics discussed between 2003 and 2016. They use LDA to detect themes that have been talked about.

<!--
## Government spending
### International
@Frey1978 [p. 5] lamented that '(e)conomics and politics depend closely and intimately on one another in a modern society. Is this fact duly accounted for in current economic thought?'. Since then there has been a push to integrate politics into economic research, and this paper fits into that broad research agenda.

Generally, from a positive economics approach, there has been much work explaining aggregate or disaggregated government spending on the basis of various explanatory variables. For instance, @DiMatteoDiMatteo1998 explain Canadian government expenditure on health care over the period 1965 to 1991 as a function of variables such as provincial income, proportion of the population over 65 and federal transfers. Similarly, @Mauro1998 examines whether corruption can explain government expenditure across a cross-section of countries.

In a similar style, although from a political economy approach, @PerssonRolandTabellini2007, @Tabellini2000 and @PerssonTabellini2010 link the level of government spending with political economy considerations such as electoral rules and political institutions. They are interested in how fiscal policy, in terms of the features of government spending and taxation, is determined. Electoral rules and political institutions should impact the number of parties, which should influence government formation and fiscal policy. The focus of political economy on institutions is a feature of @North1985. More recently, @AcemogluJohnsonRobinson2005 [p. 392] conduct their analysis within a framework where political institutions and the distribution of resources imply economic and political institutions, which in turn imply economic performance and the distribution of resources.

### Australia
@Coulson2016 has a similar interest to the broad question in this paper: to what extent is parliament a genuine actor in the policy process. To help answer this @Coulson2016 examines budget estimates committees using Hansard records for three Australian states: Queensland; Victoria; and South Australia, over five budget years: 2011-12 to 2015-16. The analysis is done by hand which limits the extent of the records that could be examined in a reasonable time. If parliament, or in this case, budget estimates committees (which are made up of parliamentarians), are important then the topics that the parliamentarians discuss should be related to the budget documents that were ostensibly the focus of the committee at that time. @Coulson2016 finds that approximately half of the topics raised by the parliamentarians were related to the budget documents being examined and that the parliamentarians focussed more on the budget measures than government policy or operational matters.

This paper also fits into an existing literature on examining the role of government in Australia's economic history. For instance, @Boot1998, @Frost2000 and @Boot2000 focus on the role of government in the 1800s. While @Boot1998 and @Frost2000 disagree about the specific contribution, they agree that political concerns did influence government decision-making, and it was not just economic efficiency.

-->

# Data

## Hansard

### Overview
In 1901 six former British colonies federated to form Australia. The first parliament sat on 9 May 1901, and a written record of what has been said in parliament is available since that time. Based on the UK parliament, this record is called Hansard.

The mission statement of Hansard is: 'To provide an accurate, substantially verbatim account of the proceedings of the parliament and its committees which, while usually correcting obvious mistakes, neither adds to nor detracts from the meaning of the speech or the illustration of the argument.' (http://www.aph.gov.au/Parliamentary_Business/Hansard, accessed 12 September 2017).

While Hansard is not necessarily verbatim, it should be close enough for the purposes of this paper. For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis. @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians. Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.

### Initial Hansard dataset
The Australian Parliament House makes Hansard available online (http://www.aph.gov.au/Parliamentary_Business/Hansard). Tim Sherratt at the University of Canberra has scraped the website and makes the entire Hansard for 1901 to 1980 available in XML files (http://historichansard.net/). After downloading Sherratt's XML files, some initial exploration can be done to illustrate the structure and content of the files.

Sherratt has each day's Hansard in a separate XML file and those are grouped in folders by year. For instance, "19480311_reps_18_196.xml" is the Hansard record for 11 March 1948 and is within the 1948 folder.

The content of each XML file can be searched for its \<session.header> tag to get information such as the date, parliament and session numbers, etc for that file. Speeches occur within \<debate> tags, with information about the broad content and type of that particular debate contained within child \<debateinfo> and \<subdebateinfo> tags. Within each particular set of \<debate> tags there can be many \<speech> tags. Typically, toward the start of a <speech> tag there will be a \<talk.start> tag, followed by information about the talker contained within <talker> tags. Examples of the data contained within \<talker> tags include: page.no, name.id, electorate, party, role, in.gov, first.speech, and actual name.

While it is possible to analyse the XML files themselves, converting the XML files into rectangular tables makes it easier to use a wider variety of R packages. The other advantage is that it makes some of the errors more obvious. The rectangular dataframe has almost three million obversations and 21 variables. Further information on each of the variables:

- debate_title: **[ADD DESCRIPTION]**
- debate_page.no: **[ADD DESCRIPTION]**
- debate_type: **[ADD DESCRIPTION]**
- subdebate_title: **[ADD DESCRIPTION]**
- subdebate_page.no: **[ADD DESCRIPTION]**
- speakerID: **[ADD DESCRIPTION]**
- speaker_name_meta: **[ADD DESCRIPTION]**
- speaker_name_display: **[ADD DESCRIPTION]**
- page_number: **[ADD DESCRIPTION]**
- electorate: **[ADD DESCRIPTION]**
- party: **[ADD DESCRIPTION]**
- role: **[ADD DESCRIPTION]**
- in_gov: A 
- first_speech: **[ADD DESCRIPTION]**
- statement: **[ADD DESCRIPTION]**
- statement_type: **[ADD DESCRIPTION]**
- dates: **[ADD DESCRIPTION]**
- parliament.no: **[ADD DESCRIPTION]**
- session.no: **[ADD DESCRIPTION]**
- period.no: **[ADD DESCRIPTION]**
- chamber: **[ADD DESCRIPTION]**

The Hansard records that Sherratt scraped were messy and this carried through to the Sherratt XML files and then the rectangular table. While there are implications both ways, overall it is expected that three million is an overstatement of the number of records.

I examined the first 10,000 rows row-by-row and identified two types of errors that increased the number of observations:

1. In certain cases rows neeed to be pushed into the one above as they contain no additional information other than speech text that is just a continuation of the speech text in the earlier row. For instance, **[INSERT EXAMPLE.]** Out of the first 10,000 rows this occurs on X rows: 1139, 1289, 1290, 1291, 1292, 1293, 1294, 1309, 1350, 1351, 1426, 1433, 1505.
2. There are some rows where Hansard text has been identified as being spoken, but it is a stage direction. For instance, **[INSERT EXAMPLE.]** Examining the original Hansard documents suggests this occured during the digitisation process because it would have been difficult to automatically distinguish spoken text from direction. Out of the first 10,000 rows this occurs on X rows: 10, 50, 65, 68, 69, 76, 79, 80, 83, 84, 85, 99, 100, 104, 105, 329, 336, 925, 926, 1407, 1408, 1412, 1415, 1422.

I identified one type of error that reduces the number of statements made by a particular politican, but not the overall number of observations:

1. Sometimes, particuarly in earlier years the identity of the speaker needs to be pulled out of first part of the text. This means that it has not been attributed to a particular politician although it is still a row in the table. For instance, **[INSERT EXAMPLE]**. Out of the first 10,000 rows this occurs on X rows: 1158, 1243, 1249, 1274, 1307, 1314, 1322, 1367, 1372, 1419, 1454, 1466, 1470, 1476, 1497

Finally, I identified one type of error where text has not been included in the table, and will slightly increase the number of observations:

1. **[INSERT DETAILS OF THAT EXAMPLE]**.

The impact of the first three errors should be able to be mitigated using statistical learning classification. While this will not find all the examples, it should find many. The final error will need to be addressed by improved parsing of the XML.

### Addressing the known issues
**[TBD]**

### Fixing the spelling
https://stackoverflow.com/questions/24443388/stemming-with-r-text-analysis/24454727#24454727

### Preliminary summary
Notwithstanding the known issues identified above, some initial summary statistics can be created for the Hansard dataset.

#### Number of parliamentarians
There are 757 unique speaker IDs. While some members have

speaker_name_meta - 773
speaker_name_display - 3313

#### Turnover of politicians
Athanassios Gouglas examines the turnover of Australian politicians using information from parliamentary yearbooks. Gouglas has many measures of turnover and detailed analysis of their implications. It is possible to estimate the number of new MPs each year using Hansard records. While there are too many caveats for this to be an appropriate alternative to Gouglas' yearbook appropriate, comparing the results here with Gouglas is a useful check on the Hansard data. (An example of a caveat is that it is possible for a politician to be in parliament but not speak. That politican would not show up in the Hansard record, but would show up in the yearbook.)

I started with all Hansard statements for 1901-1980. Then I grouped the statements by the politician that was speaking. Then I took the year of the first speech for each politician. Finally I summarised that by year.

The graph of this, along with a best fit curve, is in Gouglas_turnover.pdf (attached). The y-axis is the proportion of the seats that were taken up by new politicians that year.

After this, I realised that my estimate of the average was being held down by non-election years. So I looked up the years of elections in Australia and then tried to work out when the politicians elected in that election would have been speaking for the first time in parliament. (For instance, if the election was in December of a year then most probably wouldn’t have spoken for the first time until the following year so the year of interest is the following year - there’s a bit of error introduced here.) Combining that with the earlier data meant that I could set all other years to NA.

The graph of that, along with the best fit curve, is in Douglas_turnover_select.pdf (attached).

I’ve attached the summary data by year as a CSV in case you’re interested. ‘Seats’ is the total number of seats available in parliament, ‘important’ is a dummy for whether that year is likely to have lots of new politicians from an election, ‘new_hansard_speakers’ is the number of new politicians recorded as making statements in that year, ‘gouglas_new’ is the new speakers as a proportion of the seats; ‘gouglas_new_important’ adds NA to a year if it’s not important (there’s going to be a little bit of error introduced here, but ballpark figures should be right). BTW I dropped 1901 because that was the first year so it was skewing the best fit!

Words: Total number of words?

In the ten years from Federation, did they talk about and resolve whatever it was that were the reasons for Federation?

'Customs and excise duties were to become almost the federal government's sole revenue source for the first 10 years of Federation, and a major source in the years leading to World War 2. They were the subject of intense debate in teh parliament.' @Wilson2015 [p. 333]. Is this true? Etc etc, there's other claims about debate on this page.

### Sentiment analysis
**[TBD.]**

## Government spending
**[Expand/amend - need longer and disaggregated series - ABS Year Book.]**

# Analysis
**[TBD.]**

# Outstanding issues and future steps
- Add Senate Hansard
- Add Committees Hansard
- Consider statements in newspapers (Trove)

# Conclusion
**[TBD.]**

\newpage

# (APPENDIX) Appendix {-}

# Topic analysis
## Overview
Each statement in Hansard needs to be classified by its topic. Sometimes Hansard includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way. One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, as implemented by the R package 'topicmodels' by @Grun2011.

The key assumption behind the LDA method is that each statement, 'a document', in Hansard is made by a speaker who decides the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics. The topics are not specified *ex ante*; they are an outcome of the method. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. This provides more flexibility than other approaches such as a strict word count method. The goal is to have the words found in Hansard group themselves to define topics.

## Document generation process
As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about. After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.

More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics. For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).

```{r topicsoverdocuments, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
document_1 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
  )

document_2 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
  )

par(mfrow=c(2,1))
ggplot(document_1, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 1") +
  coord_cartesian(ylim = c(0, 0.4))

ggplot(document_2, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

Similarly, each topic could be considered a probability distribution over terms. To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion. For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).

```{r topicsoverterms, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
topic_1 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
  )

topic_2 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
  )

# par(mar = c(4, 4, 0.1, 0.1))
ggplot(topic_1, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 1") +
  coord_cartesian(ylim = c(0, 0.4))
ggplot(topic_2, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

Following @BleiLafferty2009, @blei2012 and @GriffithsSteyvers2004, the process by which a document is generated is more formally considered to be:

1. There are $1, 2, \dots, k, \dots, K$ topics and the vocabulary consists of $1, 2, \dots, V$ terms. For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms. The distribution over the terms for the $k$th topic is $\beta_k$. Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.
2. Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $1, 2, \dots, d, \dots, D$ documents. The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$. Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\alpha)$. Again, strictly $\alpha$ is vector of length $K$ of hyperparameters, but in practice each is usually the same value.
3. If there are $1, 2, \dots, n, \dots, N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$. 
    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.

[^Dirichletfootnote]: The Dirichlet distribution is a variation of the beta distribution that is commonly used as a prior for categorical and multinomial variables. If there are just two categories, then the Dirichlet and the beta distributions are the same. In the special case of a symmetric Dirichlet distribution, $\eta=1$, it is equivalent to a uniform distribution. If $\eta<1$, then the distribution is sparse and concentrated on a smaller number of the values, and this number decreases as $\eta$ decreases. A hyperparameter is a parameter of a prior distribution.

Given this set-up, the joint distribution for the variables is (@blei2012, p.6):
$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}) = \prod^{K}_{i=1}p(\beta_i) \prod^{D}_{d=1}p(\theta_d) \left(\prod^N_{n=1}p(z_{d,n}|\theta_d)p\left(w_{d,n}|\beta_{1:K},z_{d,n}\right) \right).$$

Based on this document generation process the analysis problem, discussed in the next section, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$. This is intractable directly, but can be approximated (@GriffithsSteyvers2004 and @blei2012).

## Analysis process
After the documents are created, they are all that we have to analyse. The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'. We do not know the topics of each document, nor how terms defined the topics. That is, we do not know the probability distributions of Figures \@ref(fig:topicsoverdocuments) or \@ref(fig:topicsoverterms). In a sense we are trying to reverse the document generation process -- we have the terms and we would like to discover the topics.

If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics (@SteyversGriffiths2006). The outcomes of the LDA process are probability distributions and these define the topics. Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic. That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document (@blei2012, p.7): 
$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N} | w_{1:D, 1:N}) = \frac{p\left(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}\right)}{p(w_{1:D, 1:N})}.$$

The initial practical step when implementing LDA given a corpus of documents is to remove 'stop words'. These are words that are common, but that don't typically help to define topics. There is a general list of stop words such as: "a"; "a's"; "able"; "about"; "above"... An additional list of words that are commonly found in Hansard, but likely don't help define topics is added to the general list. These additions include words such as: "act"; "amendment"; "amount"; "australia"; "australian"; "bill"... A full list can be found in Appendix \@ref(hansard-stop-word). We also remove punctuation and capitalisation. The documents need to then be transformed into a document-term-matrix. This is essentially a table with a column of the number of times each term appears in each document.

After the dataset is ready, the R package 'topicmodels' by @Grun2011 can be used to implement LDA and approximate the posterior. It does this using Gibbs sampling or the variational expectation-maximization algorithm. Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents. Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.7). It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.6):
$$p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} $$
where $z'_{d, n}$ refers to all other topic assignments; $\lambda'_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$; $\lambda'_{.\rightarrow k}$ is a count of how many other times that any term has been assigned to topic $k$; $\lambda'^{(d)}_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$ in that particular document; and $\lambda'^{(d)}_{-i}$ is a count of how many other times that term has been assigned in that document. Once $z_{d,n}$ has been estimated, then estimates for the distribution of words into topics and topics into documents can be backed out.

This conditional distribution assigns topics depending on how often a term has been assigned to that topic previously, and how common the topic is in that document (@SteyversGriffiths2006). The initial random allocation of topics means that the results of early passes through the corpus of document are poor, but given enough time the algorithm converges to an appropriate estimate.

## Warnings and extensions
The choice of the number of topics, *k*, affects the results, and must be specified *a priori*. If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use a test and training set process. Essentially, this means running the process on a variety of possible values for *k* and then picking an appropriate value that performs well.

One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter (@blei2012). It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order. Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation. For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.

\newpage

# Hansard stop word
The following words were added to the usual list of stop words: "1", "2", "act", "amendment", "amount", "australia", "australian", "bill", "board", "cent", "clause", "commission", "committee", "commonwealth", "countries", "country", "day", "deal", "debate", "department", "desire", "duty", "gentleman", "government", "honorable", "honourable", "house", "increase", "labor", "labour", "leader", "legislation", "matter", "minister", "money", "national", "opposition", "parliament", "party", "people", "policy", "position", "power", "prime", "proposed", "public", "question", "regard", "report", "service", "situation", "south", "speaker", "statement", "support", "system", "time", "united", "vote", and "wales".

\newpage

# References

### 2018-09-07 scripts/to_make_graphs/make_graph_of_topics.R

@@ -27,6 +27,26 @@ migration_data <- migration_data %>%
   select(document, topic, gamma, type)
 
 
+
+misc_data$event[1] <- 
+  "WWI
+starts"
+
+misc_data$event[2] <- 
+  "WWII
+starts"
+
+misc_data$event[3] <- 
+  "Vietnam
+War"
+
+misc_data$event[4] <- 
+  "White
+Aust.
+ends"
+
+
+
 # each_days_topics <- each_days_topics %>% 
 #   arrange(document, topic) 
 
@@ -57,14 +77,14 @@ ggplot() +
   geom_smooth(data = td_gamma, mapping = aes(x = document, y = gamma, group = factor(topic), label = factor(topic)), colour = "grey90", se = FALSE) +
   # geom_vline(data = misc_elections_data, aes(xintercept = electionDate), linetype = "dashed") +
   geom_vline(data = misc_data, aes(xintercept = year), linetype = "dashed", color = "grey50") +
-  geom_text_repel(data = misc_data, aes(x = year, y = 0.40, label = event), nudge_x = 5, size = 5) +
-  geom_smooth(data = td_gamma[td_gamma$topic %in% c(6, 14, 16, 17, 20),], mapping = aes(x = document, y = gamma, colour = factor(topic), group = factor(topic), label = factor(topic)), se = FALSE, size = 2) +
+  geom_text_repel(data = misc_data, aes(x = year, y = 0.40, label = event), nudge_x = 5, size = 10) +
+  geom_smooth(data = td_gamma[td_gamma$topic %in% c(6, 14, 16, 17, 20),], mapping = aes(x = document, y = gamma, colour = factor(topic), group = factor(topic), label = factor(topic)), se = FALSE, size = 6) +
   # geom_text() +
   # geom_line() +
   theme_classic() +
   guides(color = guide_legend(title = "Topic")) +
-  theme(    text = element_text(size=20),
-    axis.title.y = element_blank(),
+  theme(    text = element_text(size=40),
+            axis.title.y = element_blank(),
             axis.title.x = element_blank()
   ) +
   scale_colour_viridis_d() +

### 2018-09-07 scripts/to_model_topics/topic_modelling_stm.R

@@ -2,7 +2,7 @@
 # Purpose: Associate a group, based on similar topics, for every statement in Hansard.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 5 September 2018
+# Last updated: 6 September 2018
 # Prerequisites: 
 # Issues:
 
@@ -11,37 +11,27 @@
 # Load libraries
 # devtools::install_github("dgrtwo/drlib")
 library(drlib)
-# library(dplyr)
 library(lubridate)
 # library(modelr) # Used in the kfolds section
-# install.packages("stm")
 library(stm)
-# citation('stm')
 library(tictoc)
 library(tidytext)
 library(tidyverse)
-# library(tm)
-# library(topicmodels)
 library(viridis)
 # update.packages()
 
-# Load Hansard statements
-load("outputs/hansard/all_hansard_words_by_date.Rda") # Takes a while
+# Load Hansard words by day
+load("outputs/for_topic_models/all_hansard_words_by_date.Rda") # Takes a while
 
 
-#### Get a sample of the days ####
+#### Take a sample from the days ####
 set.seed(123)
 some_random_rows <- sample(1:nrow(all_hansard_words), 1000) # Change the integer to a larger number through if you want
 some_days_hansard_words <- all_hansard_words[some_random_rows, ]
 rm(all_hansard_words, some_random_rows)
-# Here - what you want to do for the graph is to aggregate the days by years then run it
-
-# housethat -> house that
-# tbe -> the
-# there seems to be lots of 'tile' and 'tlie' - are these percentile errors?
 
 
-#### Temp fix for dodgy words
+#### Temp fix for dodgy words ####
 # Temp fix for getting rid of politicians names
 politicians <- read_csv("data/politicians/politicians_by_individuals.csv") %>% 
   select(surname) %>% 
@@ -60,7 +50,6 @@ custom_stop_words <- bind_rows(
     lexicon = rep("custom", length(word))
   )
 )
-
 
 
 ## Sweet graph from https://juliasilge.com/blog/sherlock-holmes-stm/
@@ -101,7 +90,7 @@ hansard_tf_idf <- tidy_hansard %>%
   ungroup
 
 
[…]

### 2018-09-07 scripts/to_scrape_websites/get_URLs_of_hansard_PDFs-senate.R

@@ -1,0 +1,494 @@
+#### Preamble ####
+# Purpose: I threw a wish (initial scraper) in the well (Hansard website), Don't ask me I'll never tell (because my code is embarrasing), I looked to you as it fell (threw errors), And now you're (Hansard website) in my way (why don't you just have a bulk downloader?), I'd trade my soul for a wish (bulk downloader), Pennies and dimes for a kiss (bulk downloader), I wasn't looking for this (scraping expedition), But now you're in my way (and a conference deadline is imminent).
+# The Hansard website has some tres changeable urls for the PDFs so it seems less uncertain to just to get the explicit address of the PDFs instead of using a rule. This scraper gets those URLs. This isn't pretty, but it works.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 6 September 2018
+# Prerequisites: You need the pages of the search results.
+# To do: 
+
+
+#### Set up workspace ####
+library(tidyverse)
+library(rvest)
+
+
+#### Pages of search results that list the PDFs ####
+
+
+#### Load a batch of them ####
+pages <- c("http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=2;query=Dataset%3Ahansards,hansards80;resCount=Default",
+           "http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=3;query=Dataset%3Ahansards,hansards80;resCount=Default",
+           "http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=4;query=Dataset%3Ahansards,hansards80;resCount=Default",
+           "http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=5;query=Dataset%3Ahansards,hansards80;resCount=Default",
[…]

### 2018-09-11 outputs/docs/events/paper.Rmd
Start papers and get missing PDFs in HoR and start QLD

---
title: 'Nobody expects the Spanish Inquisition: How events drive topics in Australian parliaments'
author: "Rohan Alexander"
date: "10/09/2018"
abstract: "I examine Australian hansard records "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

What events changed the course of topics in Parliament, and what was the pattern before? Eg What did we miss out on because of 9/11 or the assassination? Combine them with the average length that it takes to get legislation through to be specific about what stopped. Similarly, how does the topics change after a change of government? Eg What could have happened if Kevin 07 didn’t kick Howard out.

# Data
Hansards are available for all six Australian states and the Commonwealth although the period varies (Table 1). Do we just focus on the lower houses?

| Parliament | House | Years used | Notes |
|:------|-----:|---------:|------:|
| Commonwealth | House of Representatives | 1901 - 2017 | - |

# Political events
>*When you change the government, you change the country.* Paul Keating

# External events
>*Events, dear boy, events.* Attributed to Harold Macmillan

# Summary
What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.

### 2018-09-11 outputs/docs/mentions/paper.Rmd
Start papers and get missing PDFs in HoR and start QLD

---
title: 'Slide into my mentions: Who gets incumbancy advantage in Australia?'
author: "Rohan Alexander"
date: "10/09/2018"
abstract: "I examine Australian hansards to create measures of a politician's importance within parliament. I then show these measures are positively correlated with incumbancy advantage."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
Measuring the advantage of incumbency has been of interest to scholars since the second election. Bias makes it difficult to

Who gets kicked out at an election? Do people at the centre get kicked out? Measure those at the centre by those that have high mentions.

### 2018-09-11 scripts/to_scrape_websites/get_1981_1960_PDFs.R

@@ -1,0 +1,49 @@
+#### Preamble ####
+# Purpose: This file gets Australian Hansard PDF files for the senate from the parliament website.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 10 September 2018
+# Prerequisites: Need a list of csvs to walk through - URLs_for_1901-2017_PDFs_senate.csv
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/URLs_for_1981_and_1960.csv")
+
+data_to_scrape <- data_to_scrape %>% 
+  filter(file_name %in% c("1960-12-06.pdf", "1960-12-01.pdf", "1960-11-30.pdf", "1960-11-29.pdf", "1960-11-24.pdf", "1960-11-23.pdf", "1960-11-22.pdf", "1960-11-17.pdf", "1960-11-16.pdf", "1960-11-15.pdf", "1960-11-10.pdf", "1960-11-09.pdf", "1960-11-08.pdf", "1960-04-28.pdf", "1960-04-27.pdf", "1960-04-07.pdf", "1960-09-22.pdf", "1960-09-21.pdf", "1960-09-20.pdf"))
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("pdfs/", save_name)
+
+dir.create("pdfs") # Creates the directory - throws warning but does not overwrite if there's already a directory
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(15:30, 1)) # Space out requests by somewhere between 15 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
[…]

### 2018-09-11 scripts/to_scrape_websites/get_URLs_of_hansard_PDFs.R

@@ -460,6 +460,18 @@ pages <- c("http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=y
            "http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=46;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221970s%22;resCount=Default",
            "http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=47;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221970s%22;resCount=Default")
 
+
+
+pages <- c("http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=0;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221980s%22%20Year%3A%221980%22;resCount=Default",
+"http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=1;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221980s%22%20Year%3A%221980%22;resCount=Default",
+"http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=2;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221980s%22%20Year%3A%221980%22;resCount=Default",
+"http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=3;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221980s%22%20Year%3A%221980%22;resCount=Default",
+"http://parlinfo.aph.gov.au/parlInfo/search/summary/summary.w3p;adv=yes;orderBy=_fragment_number,doc_date-rev;page=4;query=Dataset%3Ahansardr,hansardr80%20Decade%3A%221960s%22%20Year%3A%221960%22;resCount=Default",
[…]

### 2018-09-11 outputs/docs/events/paper.Rmd
Update events paper

@@
 ---
-title: 'Nobody expects the Spanish Inquisition: How events drive topics in Australian parliaments'
-author: "Rohan Alexander"
-date: "10/09/2018"
-abstract: "I examine Australian hansard records "
+title: 'Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?'
+author:
+- name: Rohan Alexander
+  affiliation: Australian National University
+date: "`r format(Sys.time(), '%d %B %Y')`"
+abstract: "We use a structural text model to explore the impact of various events on what was said in Australian parliaments. We find that 1) [TBD]; 2) [TBD]; and 3) [TBD]."
 output: html_document
+number_sections: yes
+bibliography: ../bibliography.bib
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
 ```
@@
 # Introduction
+New governments often try to be different to the governments they replace.
+For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
+Similarly, significant events can alter the course of a government.
+For instance, consider the change in the Howard government after the 9/11 attacks.
+However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party?
+And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?
 
-What events changed the course of topics in Parliament, and what was the pattern before?
-Eg What did we miss out on because of 9/11 or the assassination?
+In this paper we use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to model the topics of discussion in Australian parliaments.
+The advantage of this model is that it allows for topics to be correlated between sitting days, which then allows us to test for changes in topics at various events.
+
+We find [INSERT RESULTS].
+
+Our work fits into [WHATEVER IT FITS INTO].
+While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and hence can identify patterns that may otherwise be overlooked.
+
+<!-- What events changed the course of topics in Parliament, and what was the pattern before?
+Eg What did we miss out on because of 9/11, or an assassination?
 Combine them with the average length that it takes to get legislation through to be specific about what stopped.
@@
 Eg What could have happened if Kevin 07 didn’t kick Howard out.
+-->
 
 # Data
-Hansards are available for all six Australian states and the Commonwealth although the period varies (Table 1). Do we just focus on the lower houses?
+Following the example of the UK, a text-based record of what was said in Australian parliaments called Hansard has been regularly made available since their establishment.
+While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
+@Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.
+Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.
+
+The parliaments generally make their hansard records available online in PDF formats that can be processed by text readers such as @Ooms2018pdftools.
+Some records such as the early days of the New South Wales parliament have yet to be put through a professional OCR process, although the Google Tesseract engine as implemented by @Ooms2018tesseract can be used to provide a useful first-pass if necessary.
+Hansard records that are still images are not used in this analysis (see the Appendix for more details).
+
+Hansard records are available for all six Australian states and the Commonwealth although the period varies (Table 1).
+Here we focus on the lower houses although a similar analysis is possible in a bicameral setting.
 
@@
 | Commonwealth | House of Representatives | 1901 - 2017 | - |
+| Queensland | ? | 1861 - 2017 | - |
+| New South Wales | ? | ? - 2017 | - |
+| Victoria | ? | ? - 2017 | - |
+| Tasmania | ? | ? - 2017 | - |
+| South Australia | ? | ? - 2017 | - |
+| Western Australia | ? | ? - 2017 | - |
 
-# Political events
->*When you change the government, you change the country.* Paul Keating
+We start with the PDFs that have been through an OCR process (or compiled more recently using software that makes them readable by default) as supplied by various parliaments (see the Appendix for specific sources).
+We then use the PDFtools R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the Tidyverse R package of @WickhamHadleyTidyverse, the Tidytext R package of @SilgeRobinson2016 and the [INSERT OTHERS].
+The result is a
 
-# External events
->*Events, dear boy, events.* Attributed to Harold Macmillan
+# Model
+The model that we use in this paper is the Structural Topic Model (STM) as implemented by the STM R package of @RobertsStewartAiroldiRPackage.
+The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
+In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.
 
-# Summary
+## Latent Dirichlet Allocation
+### Overview
+Each statement in Hansard needs to be classified by its topic.
+Sometimes Hansard includes titles that make the topic clear.
+But not every statement has a title and the titles do not always define topics in a well-defined and consistent way.
+One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, as implemented by the R package 'topicmodels' by @Grun2011.
+
+The key assumption behind the LDA method is that each statement, 'a document', in Hansard is made by a speaker who decides the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics.
+A topic could be thought of as a collection of terms, and a document as a collection of topics.
+The topics are not specified *ex ante*; they are an outcome of the method.
+Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
+This provides more flexibility than other approaches such as a strict word count method.
+The goal is to have the words found in Hansard group themselves to define topics.
+
+### Document generation process
+As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.
+After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.
+
+More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics.
+For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
+
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
+document_1 <- tibble(
+  Topics = c(
+  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
+  ),
+  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
+  )
+
+document_2 <- tibble(
+  Topics = c(
+  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
+  ),
+  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
+  )
+
+par(mfrow=c(2,1))
+ggplot(document_1, aes(Topics, Probability)) +
+  geom_point() +
+  theme_classic() +
+  labs(title = "Distribution over topics for Document 1") +
+  coord_cartesian(ylim = c(0, 0.4))
+
+ggplot(document_2, aes(Topics, Probability)) +
+  geom_point() +
+  theme_classic() +
+  labs(title = "Distribution over topics for Document 2") +
+  coord_cartesian(ylim = c(0, 0.4))
+```
+
+Similarly, each topic could be considered a probability distribution over terms.
+To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion.
+For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
+
+```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
+topic_1 <- tibble(
+  Terms = c(
+  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
+  ),
+  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
+  )
+
+topic_2 <- tibble(
+  Terms = c(
+  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
+  ),
+  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
+  )
+
+# par(mar = c(4, 4, 0.1, 0.1))
+ggplot(topic_1, aes(Terms, Probability)) +
+  geom_point() +
+  theme_classic() +
+  labs(title = "Distribution over terms for Topic 1") +
+  coord_cartesian(ylim = c(0, 0.4))
+ggplot(topic_2, aes(Terms, Probability)) +
+  geom_point() +
+  theme_classic() +
+  labs(title = "Distribution over terms for Topic 2") +
+  coord_cartesian(ylim = c(0, 0.4))
+```
+
+Following @BleiLafferty2009, @blei2012 and @GriffithsSteyvers2004, the process by which a document is generated is more formally considered to be:
+
+1.
+There are $1, 2, \dots, k, \dots, K$ topics and the vocabulary consists of $1, 2, \dots, V$ terms.
+For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms.
+The distribution over the terms for the $k$th topic is $\beta_k$.
+Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.
+2.
+Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $1, 2, \dots, d, \dots, D$ documents.
+The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
+Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\alpha)$.
+Again, strictly $\alpha$ is vector of length $K$ of hyperparameters, but in practice each is usually the same value.
+3. If there are $1, 2, \dots, n, \dots, N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
+    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$. 
+    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.
+
+[^Dirichletfootnote]: The Dirichlet distribution is a variation of the beta distribution that is commonly used as a prior for categorical and multinomial variables.
+If there are just two categories, then the Dirichlet and the beta distributions are the same.
+In the special case of a symmetric Dirichlet distribution, $\eta=1$, it is equivalent to a uniform distribution.
+If $\eta<1$, then the distribution is sparse and concentrated on a smaller number of the values, and this number decreases as $\eta$ decreases.
+A hyperparameter is a parameter of a prior distribution.
+
+Given this set-up, the joint distribution for the variables is (@blei2012, p.6):
+$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}) = \prod^{K}_{i=1}p(\beta_i) \prod^{D}_{d=1}p(\theta_d) \left(\prod^N_{n=1}p(z_{d,n}|\theta_d)p\left(w_{d,n}|\beta_{1:K},z_{d,n}\right) \right).$$
+
+Based on this document generation process the analysis problem, discussed in the next section, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
+This is intractable directly, but can be approximated (@GriffithsSteyvers2004 and @blei2012).
+
+### Analysis process
+After the documents are created, they are all that we have to analyse.
+The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'.
+We do not know the topics of each document, nor how terms defined the topics.
+That is, we do not know the probability distributions of Figures \@ref(fig:topicsoverdocuments) or \@ref(fig:topicsoverterms).
+In a sense we are trying to reverse the document generation process -- we have the terms and we would like to discover the topics.
+
+If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics (@SteyversGriffiths2006).
+The outcomes of the LDA process are probability distributions and these define the topics.
+Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
+That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document (@blei2012, p.7):
+$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N} | w_{1:D, 1:N}) = \frac{p\left(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}\right)}{p(w_{1:D, 1:N})}.$$
+
+The initial practical step when implementing LDA given a corpus of documents is to remove 'stop words'.
+These are words that are common, but that don't typically help to define topics.
+There is a general list of stop words such as: "a"; "a's"; "able"; "about"; "above"...
+An additional list of words that are commonly found in Hansard, but likely don't help define topics is added to the general list.
+These additions include words such as: "act"; "amendment"; "amount"; "australia"; "australian"; "bill"...
+A full list can be found in Appendix \@ref(hansard-stop-word).
+We also remove punctuation and capitalisation.
+The documents need to then be transformed into a document-term-matrix.
+This is essentially a table with a column of the number of times each term appears in each document.
+
+After the dataset is ready, the R package 'topicmodels' by @Grun2011 can be used to implement LDA and approximate the posterior.
+It does this using Gibbs sampling or the variational expectation-maximization algorithm.
+Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
+Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.7).
+It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.6):
+$$p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} $$
+where $z'_{d, n}$ refers to all other topic assignments; $\lambda'_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$; $\lambda'_{.\rightarrow k}$ is a count of how many other times that any term has been assigned to topic $k$; $\lambda'^{(d)}_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$ in that particular document; and $\lambda'^{(d)}_{-i}$ is a count of how many other times that term has been assigned in that document.
+Once $z_{d,n}$ has been estimated, then estimates for the distribution of words into topics and topics into documents can be backed out.
+
+This conditional distribution assigns topics depending on how often a term has been assigned to that topic previously, and how common the topic is in that document (@SteyversGriffiths2006).
+The initial random allocation of topics means that the results of early passes through the corpus of document are poor, but given enough time the algorithm converges to an appropriate estimate.
+
+### Warnings and extensions
+The choice of the number of topics, *k*, affects the results, and must be specified *a priori*.
+If there is a strong reason for a particular number, then this can be used.
+Otherwise, one way to choose an appropriate number is to use a test and training set process.
+Essentially, this means running the process on a variety of possible values for *k* and then picking an appropriate value that performs well.
+
+One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter (@blei2012).
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+This motivates the use of the Structural Topic Model, described in the next section.
+
+## Structural Topic Model
+### Overview and example
+[TBD]
+
+Note that each of the states and the Commonwealth are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.
+
+### Considering events
+[TBD]
+
+# Results
+## Political events
+>*When you change the government, you change the country.* Paul Keating, Australian Prime Minister.
+
+Change of government.
+
+## Polling events
+Major change in polls.
+
+## External events
+>*Events, dear boy, events.* Attributed to Harold Macmillan, British Prime Minister.
+
+Major event such as 9/11 attacks, or economic change.
+
+# Summary and conclusions
 What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.
+
+Text analysis has well-known biases and weaknesses and is a complement to more detailed analysis such as qualitative methods and case studies.
+We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
+
+# Appendix
+## Robustness of results
+Here we change the number of sitting days considered either side of an event.
+The results in the main section of the paper are for the nearest ten days either side of an event.
+Here are show that the results are essentially the same if the nearest one, two, five, and twenty days either side of an event.
+
+## Document sources
+Where from?
+###OCR vs not
+
+# References

### 2018-09-11 outputs/docs/mentions/paper.Rmd
Update events paper

@@
 ---
-title: 'Slide into my mentions: Who gets incumbancy advantage in Australia?'
+title: 'Slide into my mentions, please: Who gets incumbancy advantage in Australia?'
 author: "Rohan Alexander"
-date: "10/09/2018"
+date: "11/09/2018"
 abstract: "I examine Australian hansards to create measures of a politician's importance within parliament. I then show these measures are positively correlated with incumbancy advantage."
@@
 # Introduction
-Measuring the advantage of incumbency has been of interest to scholars since the second election. Bias makes it difficult to
+Understanding the incumbency advantage has been of interest since at least the second election.
+But biases makes it difficult to estimate.
+Various approaches have been used to account for this, but they tend to treat incumbents as interchangeable [BE MORE SPECIFIC HERE].
 
-Who gets kicked out at an election? Do people at the centre get kicked out? Measure those at the centre by those that have high mentions.
+In this paper I use Australian hansard records to produce a measure of centrality for each incumbent that I interact with incumbency status in a simple Gelman and King (1990) style model.
+
+In contrast to Eggers, et al., (2015) who focuses on 1987-2007 and only at a Commonwealth House of Representatives level, I find that [INSERT RESULTS HERE].
+
+<!-- Who gets kicked out at an election? Do people at the centre get kicked out? Measure those at the centre by those that have high mentions.  -->
+
+# Data
+## Centrality
+To construct measures of centrality, or importance, I use the Hansard records for the Australian Commonwealth, and the six states over the period that they are available.
+The availability of this data is summarised in Table 1.
+
+[INSERT TABLE 1]
+
+For more information on this dataset please see the Appendix.
+
+## Elections
+
+# Model
+Following Gelamn and
+
+# Results
+
+# Summary and conclusions

### 2018-09-12 outputs/docs/events/paper.Rmd
Update events paper and basis of QLD scraper

@@
 ---
-title: 'Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?'
+title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
 author:
-- name: Rohan Alexander
-  affiliation: Australian National University
+  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
+  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "We use a structural text model to explore the impact of various events on what was said in Australian parliaments. We find that 1) [TBD]; 2) [TBD]; and 3) [TBD]."
-output: html_document
-number_sections: yes
+fontsize: 12pt
+output: 
+  pdf_document:
+    number_sections: true
 bibliography: ../bibliography.bib
+abstract: |
+  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017.
+We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].
+
 ---
@@
 # Introduction
-New governments often try to be different to the governments they replace.
+New governments often go out of their way to be different to the governments they replace.
 For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
@@
 The advantage of this model is that it allows for topics to be correlated between sitting days, which then allows us to test for changes in topics at various events.
+The events that we focus on are changes in: 1) government; 2) the political environment (as defined by polling or other results); 3) economic conditions; and 4) the significant events (such as the 9/11 attacks or the Bali Bombings).
 
-We find [INSERT RESULTS].
+We find [INSERT RESULTS]. We also explored the other direction (the impact of what was said in parliaments on events) but it was difficult to find significant effects.
 
@@
 We start with the PDFs that have been through an OCR process (or compiled more recently using software that makes them readable by default) as supplied by various parliaments (see the Appendix for specific sources).
-We then use the PDFtools R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the Tidyverse R package of @WickhamHadleyTidyverse, the Tidytext R package of @SilgeRobinson2016 and the [INSERT OTHERS].
+We then use the \texttt{PDFtools} R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS].
 The result is a
@@
 # Model
-The model that we use in this paper is the Structural Topic Model (STM) as implemented by the STM R package of @RobertsStewartAiroldiRPackage.
+The primary model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{STM} R package of @RobertsStewartAiroldiRPackage.
 The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
@@
 ## Latent Dirichlet Allocation
-### Overview
-Each statement in Hansard needs to be classified by its topic.
+Each day's Hansard record needs to be classified by its topic.
 Sometimes Hansard includes titles that make the topic clear.
-But not every statement has a title and the titles do not always define topics in a well-defined and consistent way.
-One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, as implemented by the R package 'topicmodels' by @Grun2011.
+But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
+One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.
 
-The key assumption behind the LDA method is that each statement, 'a document', in Hansard is made by a speaker who decides the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics.
+The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics.
 A topic could be thought of as a collection of terms, and a document as a collection of topics.
@@
 This provides more flexibility than other approaches such as a strict word count method.
-The goal is to have the words found in Hansard group themselves to define topics.
+The goal is to have the words found in each day's Hansard group themselves to define topics.
 
-### Document generation process
 As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.
@@
 
-Based on this document generation process the analysis problem, discussed in the next section, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
+Based on this document generation process the analysis problem, discussed next, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
 This is intractable directly, but can be approximated (@GriffithsSteyvers2004 and @blei2012).
 
-### Analysis process
 After the documents are created, they are all that we have to analyse.
@@
 Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
-That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document (@blei2012, p.7):
+That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document (@blei2012, p.
+7):
 $$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N} | w_{1:D, 1:N}) = \frac{p\left(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}\right)}{p(w_{1:D, 1:N})}.$$
 
-The initial practical step when implementing LDA given a corpus of documents is to remove 'stop words'.
+The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'.
 These are words that are common, but that don't typically help to define topics.
@@
 Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
-Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.7).
-It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.6):
+Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.
+7).
+It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.
+6):
 $$p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} $$
@@
 
-### Warnings and extensions
 The choice of the number of topics, *k*, affects the results, and must be specified *a priori*.
@@
 ## Political events
->*When you change the government, you change the country.* Paul Keating, Australian Prime Minister.
+>*When you change the government, you change the country.* Paul Keating.
 
@@
 ## Polling events
-Major change in polls.
+>*The only poll that matters is the one on election day.* John Howard.
+
+[TBD]
+
+## Economic events
+
+Major economic changes.
+
+[TBD]
 
 ## External events
->*Events, dear boy, events.* Attributed to Harold Macmillan, British Prime Minister.
+>*Events, dear boy, events.* Attributed to Harold Macmillan.
 
@@
 
+\newpage
+
 # Appendix
+## Selection of number of topics
+
 ## Robustness of results
@@
 Where from?
-###OCR vs not
+
+Which years are being used (not non-OCRd)
+
+\newpage
 

### 2018-09-12 scripts/to_scrape_websites/get_URLs_of_hansard_dates-qld.R

@@ -1,0 +1,46 @@
+#### Preamble ####
+# Purpose: This file gets Queensland index PDF files for the senate from the parliament website.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 11 September 2018
+# Prerequisites: Need a list of csvs to walk through - URLs_for_1901-2017_PDFs_senate.csv
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/addressesforqldindices.csv")
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("pdfs/", save_name)
+
+dir.create("pdfs")
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(15:30, 1)) # Space out requests by somewhere between 15 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
+save_name <- save_name[3:length(save_name)] # main run
+address_to_visit <- address_to_visit[3:length(address_to_visit)] # main run
+
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
+

### 2018-09-12 outputs/docs/events/paper.Rmd
Get example STM model working

@@
 abstract: |
-  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017.
-We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].
+  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the mid-1800s through to 2017.
+We find that 1) changes of government where the party in power also changes, result in significant changes in topics discussed in parliament, but when the party does not change the topics are unchanged; 2) polling results do not have a significant effect; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change.
 
@@
 New governments often go out of their way to be different to the governments they replace.
-For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
-Similarly, significant events can alter the course of a government.
+For instance, Kevin Rudd's apology to Indigenous Australians was supported by all living former Prime Ministers apart from his immediate predecessor.
+Similarly,  Similarly, significant events can alter the course of a government.
 For instance, consider the change in the Howard government after the 9/11 attacks.

### 2018-09-12 scripts/to_model_topics/topic_modelling_stm.R

@@ -278,216 +278,3 @@ write_csv(td_gamma, path = "outputs/td_gamma.csv")
 
 
 
-
-
-
-
-
-
-
-
-hansardSelect <-
-  selectModel(
-    out$documents,
-    out$vocab,
-    K = 20,
-    max.em.its = 75,
-    data = out$meta,
-    runs = 20,
-    seed = 8458159 # Thank you to the authors of STM
-  )
-
-plotModels(hansardSelect, pch=c(1,2,3,4), legend.position="bottomright") # Want a model with points in top right
-
-selectedModel <- hansardSelect$runout[[2]]
-
-storage <-
-  searchK(
-    out$documents,
-    out$vocab,
-    K = c(5, 10, 15, 20, 25, 30),
-    data = meta
-  )
-
-labelTopics(selectedModel, c(3, 7, 20))
-
-thoughts3 <- findThoughts(selectedModel, texts = some_days_hansard_words$words, n = 2, topics = 3)$docs[[1]]
-thoughts20 <- findThoughts(selectedModel, texts = some_days_hansard_words$words, n = 2, topics = 20)$docs[[1]]
-
-# par(mfrow = c(1, 2),mar = c(.5, .5, 1, .5))
-# plotQuote(thoughts3, width = 30, main = "Topic 3")
-# plotQuote(thoughts20, width = 30, main = "Topic 20")
-
-plot.STM(selectedModel,type = "summary")
-
-
-
-
-prep <- estimateEffect(1:3 ~ treatment, selectedModel, some_days_hansard_words)
-plot(prep, "treatment", model=gadarianFit,
-     method="pointestimate")
-
-?plot.estimateEffect
-
-plot(mod.out.corr)
-
-draws <- thetaPosterior(selectedModel)
-
-
-
-# Bind custom list of stopwords to the default list
-custom_stop_words <- bind_rows(
-  stop_words, # The default list
-  data_frame(
-    word = c(
[…]

### 2018-09-12 scripts/to_parse_pdfs/parse_each_pdf_and_save_csv_pdftools.R

@@ -3,7 +3,7 @@
 # Purpose: This file takes Australian Hansard PDF files and it converts them to CSVs of text data that can be analysed.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 9 September 2018
+# Last updated: 12 September 2018
 # Prerequisites: You need to have downloaded the PDFs from the parliament's website. There are many GBs of PDFs and they are saved on an external drive - have fun finding that future-Rohan - and also the Berkeley Demography server. For testing purposes there should be some in the /inputs/for_testing_hansard_pdf folder.
 # To do:
 # - Check which footers need to be replaced

### 2018-09-13 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update the paper format and minor improvements to the column splitter

--- 2018-09-12 outputs/docs/events/paper.Rmd
@@
 ---
-title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
-author:
-  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
-  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
-date: "`r format(Sys.time(), '%d %B %Y')`"
-fontsize: 12pt
 output: 
   pdf_document:
-    number_sections: true
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: svm-latex-ms.tex
+title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
+thanks: "Thank you to X, Y and Z for their helpful comments, guidance and suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcomed**: rohan.alexander@anu.edu.au"
+author:
+- name: Monica Alexander
+  affiliation: University of Toronto
+- name: Rohan Alexander
+  affiliation: Australian National University
+abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
+keywords: "text analysis, politics, Australia"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+fontfamily: mathpazo
+fontsize: 12pt
+# spacing: double
 bibliography: ../bibliography.bib
-abstract: |
-  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017.
-We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].
-
+biblio-style: apsr
+endnote: no
 ---
@@
 # Introduction
-New governments often go out of their way to be different to the governments they replace.
-For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
+New governments often go to some trouble to be different from the governments they replace.
+For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his immediate predecessor.
 Similarly, significant events can alter the course of a government.
-For instance, consider the change in the Howard government after the 9/11 attacks.
+For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings.
 However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party?
@@
 
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
-document_1 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
-  )
+<!-- ```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'} -->
+<!-- document_1 <- tibble( -->
+<!--   Topics = c( -->
+<!--   "topic 1", "topic 2", "topic 3", "topic 4", "topic 5" -->
+<!--   ), -->
+<!--   Probability = c(0.40, 0.40, 0.1, 0.05, 0.05) -->
+<!--   ) -->
 
-document_2 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
-  )
+<!-- document_2 <- tibble( -->
+<!--   Topics = c( -->
+<!--   "topic 1", "topic 2", "topic 3", "topic 4", "topic 5" -->
+<!--   ), -->
+<!--   Probability = c(0.01, 0.04, 0.35, 0.20, 0.4) -->
+<!--   )   -->
 
-par(mfrow=c(2,1))
-ggplot(document_1, aes(Topics, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over topics for Document 1") +
-  coord_cartesian(ylim = c(0, 0.4))
+<!-- par(mfrow=c(2,1)) -->
+<!-- ggplot(document_1, aes(Topics, Probability)) + -->
+<!--   geom_point() + -->
+<!--   theme_classic() + -->
+<!--   labs(title = "Distribution over topics for Document 1") + -->
+<!--   coord_cartesian(ylim = c(0, 0.4)) -->
 
-ggplot(document_2, aes(Topics, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over topics for Document 2") +
-  coord_cartesian(ylim = c(0, 0.4))
-```
+<!-- ggplot(document_2, aes(Topics, Probability)) + -->
+<!--   geom_point() + -->
+<!--   theme_classic() + -->
+<!--   labs(title = "Distribution over topics for Document 2") + -->
+<!--   coord_cartesian(ylim = c(0, 0.4)) -->
+<!-- ``` -->
 
@@
 
-```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
-topic_1 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
-  )
+<!-- ```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'} -->
+<!-- topic_1 <- tibble( -->
+<!--   Terms = c( -->
+<!--   "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english" -->
+<!--   ), -->
+<!--   Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2) -->
+<!--   ) -->
 
-topic_2 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
-  )
+<!-- topic_2 <- tibble( -->
+<!--   Terms = c( -->
+<!--   "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english" -->
+<!--   ), -->
+<!--   Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142) -->
+<!--   )   -->
 
-# par(mar = c(4, 4, 0.1, 0.1))
-ggplot(topic_1, aes(Terms, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over terms for Topic 1") +
-  coord_cartesian(ylim = c(0, 0.4))
-ggplot(topic_2, aes(Terms, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over terms for Topic 2") +
-  coord_cartesian(ylim = c(0, 0.4))
-```
+<!-- # par(mar = c(4, 4, 0.1, 0.1)) -->
+<!-- ggplot(topic_1, aes(Terms, Probability)) + -->
+<!--   geom_point() + -->
+<!--   theme_classic() + -->
+<!--   labs(title = "Distribution over terms for Topic 1") + -->
+<!--   coord_cartesian(ylim = c(0, 0.4)) -->
+<!-- ggplot(topic_2, aes(Terms, Probability)) + -->
+<!--   geom_point() + -->
+<!--   theme_classic() + -->
+<!--   labs(title = "Distribution over terms for Topic 2") + -->
+<!--   coord_cartesian(ylim = c(0, 0.4)) -->
+<!-- ``` -->
 

### 2018-09-13 outputs/docs/events/svm-rmarkdown-article-example.tex
Update the paper format and minor improvements to the column splitter

\documentclass[12pt,]{article}
\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{mathpazo}

  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}

\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center

\renewenvironment{abstract}
 {{%
    \setlength{\leftmargin}{0mm}
    \setlength{\rightmargin}{\leftmargin}%
  }%
  \relax}
 {\endlist}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother

\setcounter{secnumdepth}{0}

\usepackage{longtable,booktabs}

\title{Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments? \thanks{Thank you to X, Y, Z and Y for their helpful comments, guidance and
suggestions. \textbf{Version as of}: September 13, 2018;
\textbf{Comments welcomed}:
\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }

\author{\Large Monica Alexander\vspace{0.05in} \newline\normalsize\emph{University of Toronto}   \and \Large Rohan Alexander\vspace{0.05in} \newline\normalsize\emph{Australian National University}  }

\date{}

\usepackage{titlesec}

\titleformat*{\section}{\normalsize\bfseries}
\titleformat*{\subsection}{\normalsize\itshape}
\titleformat*{\subsubsection}{\normalsize\itshape}
\titleformat*{\paragraph}{\normalsize\itshape}
\titleformat*{\subparagraph}{\normalsize\itshape}

\usepackage{natbib}
\bibliographystyle{apsr}
\usepackage[strings]{underscore} % protect underscores in most circumstances

\newtheorem{hypothesis}{Hypothesis}
\usepackage{setspace}

\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \PassOptionsToPackage{hyphens}{url}\usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \PassOptionsToPackage{hyphens}{url}\usepackage[unicode=true]{hyperref}
\fi
}

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Monica Alexander (University of Toronto) and Rohan Alexander (Australian National University)},
             pdfkeywords = {text analysis, politics, Australia},  
            pdftitle={Nobody expects the Spanish Inquisition: Which events drive topic change
in Australian parliaments?},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% add tightlist ----------
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

% \pagenumbering{arabic}% resets `page` counter to 1 
%
% \maketitle

{% \usefont{T1}{pnc}{m}{n}
\setlength{\parindent}{0pt}
\thispagestyle{plain}
{\fontsize{18}{20}\selectfont\raggedright 
\maketitle  % title \par

}

{
   \vskip 13.5pt\relax \normalsize\fontsize{11}{12} 
\textbf{\authorfont Monica Alexander} \hskip 15pt \emph{\small University of Toronto}   \par \textbf{\authorfont Rohan Alexander} \hskip 15pt \emph{\small Australian National University}

}

}

\begin{abstract}

    \hbox{\vrule height .2pt width 39.14pc}

    \vskip 8.5pt % \small

\noindent We use a structural text model to explore the effect of various events
on what was said in Australian state and federal parliaments from the
mid-1800s through to 2017. We find that: 1) changes of government are
associated with topic changes only when there is also a change in the
party in power; 2) polling results appear dissociated from parliamentary
topics; 3) economic changes, such as financial crises have a significant
effect; and 4) other events, such as an unexpected attack tend not to
have a prolonged change.

\vskip 8.5pt \noindent \emph{Keywords}: text analysis, politics, Australia \par

    \hbox{\vrule height .2pt width 39.14pc}

\end{abstract}

\vskip 6.5pt

\noindent  \section{Introduction}\label{introduction}

New governments often go to some trouble to be different to the
governments they replace. For instance, Kevin Rudd's apology to
Indigenous Australians was supported by all living former Prime
Ministers apart from his immediate predecessor. Similarly, Similarly,
significant events can alter the course of a government. For instance,
consider the change in the Howard government after the 9/11 attacks.
However it is not so clear which events drive changes in topics, for
instance, do they change when the government is replaced by another of
its own party? And which events are temporary, for instance when an
economic crisis abates, do the topics return to pre-crisis levels?

In this paper we use the Structural Topic Model (STM) of
\citet{RobertsStewartAiroldi2016} to model the topics of discussion in
Australian parliaments. The advantage of this model is that it allows
for topics to be correlated between sitting days, which then allows us
to test for changes in topics at various events. The events that we
focus on are changes in: 1) government; 2) the political environment (as
defined by polling or other results); 3) economic conditions; and 4) the
significant events (such as the 9/11 attacks or the Bali Bombings).

We find {[}INSERT RESULTS{]}. We also explored the other direction (the
impact of what was said in parliaments on events) but it was difficult
to find significant effects.

Our work fits into {[}WHATEVER IT FITS INTO{]}. While using text as data
has well-known shortcomings, it allows larger-scale analysis that would
not be viable using less-automated approaches and hence can identify
patterns that may otherwise be overlooked.

\section{Data}\label{data}

Following the example of the UK, a text-based record of what was said in
Australian parliaments called Hansard has been regularly made available
since their establishment. While Hansard is not necessarily verbatim, it
is considered close enough for text-as-data purposes. For instance,
\citet{Mollin2008} found that in the case of the UK Hansard the
differences would only affect specialised linguistic analysis.
\citet{Edwards2016} examined Australia, New Zealand and the UK, and
found that changes were usually made by those responsible for creating
the Hansard record, instead of the parliamentarians. Both these findings
provide reassurance that differences between Hansard and a verbatim
record would not be meaningful for this paper.

The parliaments generally make their hansard records available online in
PDF formats that can be processed by text readers such as
\citet{Ooms2018pdftools}. Some records such as the early days of the New
South Wales parliament have yet to be put through a professional OCR
process, although the Google Tesseract engine as implemented by
\citet{Ooms2018tesseract} can be used to provide a useful first-pass if
necessary. Hansard records that are still images are not used in this
analysis (see the Appendix for more details).

Hansard records are available for all six Australian states and the
Commonwealth although the period varies (Table 1). Here we focus on the
lower houses although a similar analysis is possible in a bicameral
setting.

\begin{longtable}[]{@{}lrrr@{}}
\toprule
Parliament & House & Years used & Notes\tabularnewline
\midrule
\endhead
Commonwealth & House of Representatives & 1901 - 2017 & -\tabularnewline
Queensland & ? & 1861 - 2017 & -\tabularnewline
New South Wales & ? & ? - 2017 & -\tabularnewline
Victoria & ? & ? - 2017 & -\tabularnewline
Tasmania & ? & ? - 2017 & -\tabularnewline
South Australia & ? & ? - 2017 & -\tabularnewline
Western Australia & ? & ? - 2017 & -\tabularnewline
\bottomrule
\end{longtable}

We start with the PDFs that have been through an OCR process (or
compiled more recently using software that makes them readable by
default) as supplied by various parliaments (see the Appendix for
specific sources). We then use the \texttt{PDFtools} R package of
\citet{Ooms2018pdftools} to extract these as text-based CSV records, and
clean the records using functions from the \texttt{Tidyverse} R package
of \citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
\citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a

\section{Model}\label{model}

The primary model that we use in this paper is the Structural Topic
Model (STM) as implemented by the \texttt{STM} R package of
\citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
modelling is the Latent Dirichlet Allocation (LDA) model of
\citet{Blei2003latent}. In this section a brief overview of both the LDA
model and the STM approach is provided and then the specifics of how we
consider events in this setting are discussed.

\subsection{Latent Dirichlet
Allocation}\label{latent-dirichlet-allocation}

Each day's Hansard record needs to be classified by its topic. Sometimes
Hansard includes titles that make the topic clear. But not every
statement has a title and the titles do not always define topics in a
well-defined and consistent way, especially over longer time periods.
One way to get consistent estimates of the topics of each statement in
Hansard is to use the latent Dirichlet allocation (LDA) method of
\citet{Blei2003latent}, for instance as implemented by the R package
`topicmodels' by \citet{Grun2011}.

The key assumption behind the LDA method is that each day's text, `a
document', in Hansard is made by speakers who decide the topics they
would like to talk about in that document, and then chooses words,
`terms', that are appropriate to those topics. A topic could be thought
of as a collection of terms, and a document as a collection of topics.
The topics are not specified \emph{ex ante}; they are an outcome of the
method. Terms are not necessarily unique to a particular topic, and a
document could be about more than one topic. This provides more
flexibility than other approaches such as a strict word count method.
The goal is to have the words found in each day's Hansard group
themselves to define topics.

As applied to Hansard, the LDA method considers each statement to be a
result of a process where a politician first chooses the topics they
want to speak about. After choosing the topics, the speaker then chooses
appropriate words to use for each of those topics.

More generally, the LDA topic model works by considering each document
as having been generated by some probability distribution over topics.
For instance, if there were five topics and two documents, then the
first document may be comprised mostly of the first few topics; the
other document may be mostly about the final few topics (Figure
@ref(fig:topicsoverdocuments)).

Similarly, each topic could be considered a probability distribution
over terms. To choose the terms used in each document the speaker picks
terms from each topic in the appropriate proportion. For instance, if
there were ten terms, then one topic could be defined by giving more
weight to terms related to immigration; and some other topic may give
more weight to terms related to the economy (Figure
@ref(fig:topicsoverterms)).

Following \citet{BleiLafferty2009}, \citet{blei2012} and
\citet{GriffithsSteyvers2004}, the process by which a document is
generated is more formally considered to be:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  There are \(1, 2, \dots, k, \dots, K\) topics and the vocabulary
  consists of \(1, 2, \dots, V\) terms. For each topic, decide the terms
  that the topic uses by randomly drawing distributions over the terms.
  The distribution over the terms for the \(k\)th topic is \(\beta_k\).
  Typically a topic would be a small number of terms and so the
  Dirichlet distribution with hyperparameter \(0<\eta<1\) is used:
  \(\beta_k \sim \mbox{Dirichlet}(\eta)\).\footnote{The Dirichlet
    distribution is a variation of the beta distribution that is
    commonly used as a prior for categorical and multinomial variables.
    If there are just two categories, then the Dirichlet and the beta
    distributions are the same. In the special case of a symmetric
    Dirichlet distribution, \(\eta=1\), it is equivalent to a uniform
    distribution. If \(\eta<1\), then the distribution is sparse and
    concentrated on a smaller number of the values, and this number
    decreases as \(\eta\) decreases. A hyperparameter is a parameter of
    a prior distribution.} Strictly, \(\eta\) is actually a vector of
  hyperparameters, one for each \(K\), but in practice they all tend to
  be the same value.
\item
  Decide the topics that each document will cover by randomly drawing
  distributions over the \(K\) topics for each of the
  \(1, 2, \dots, d, \dots, D\) documents. The topic distributions for
  the \(d\)th document are \(\theta_d\), and \(\theta_{d,k}\) is the
  topic distribution for topic \(k\) in document \(d\). Again, the
  Dirichlet distribution with the hyperparameter \(0<\alpha<1\) is used
  here because usually a document would only cover a handful of topics:
  \(\theta_d \sim \mbox{Dirichlet}(\alpha)\). Again, strictly \(\alpha\)
  is vector of length \(K\) of hyperparameters, but in practice each is
  usually the same value.
\item
  If there are \(1, 2, \dots, n, \dots, N\) terms in the \(d\)th
  document, then to choose the \(n\)th term, \(w_{d, n}\):

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \tightlist
  \item
    Randomly choose a topic for that term \(n\), in that document \(d\),
    \(z_{d,n}\), from the multinomial distribution over topics in that
    document, \(z_{d,n} \sim \mbox{Multinomial}(\theta_d)\).
  \item
    Randomly choose a term from the relevant multinomial distribution
    over the terms for that topic,
    \(w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})\).
  \end{enumerate}
\end{enumerate}

Given this set-up, the joint distribution for the variables is
(\citet{blei2012}, p.6):
\[p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}) = \prod^{K}_{i=1}p(\beta_i) \prod^{D}_{d=1}p(\theta_d) \left(\prod^N_{n=1}p(z_{d,n}|\theta_d)p\left(w_{d,n}|\beta_{1:K},z_{d,n}\right) \right).\]

Based on this document generation process the analysis problem,
discussed next, is to compute a posterior over \(\beta_{1:K}\) and
\(\theta_{1:D}\), given \(w_{1:D, 1:N}\). This is intractable directly,
but can be approximated (\citet{GriffithsSteyvers2004} and
\citet{blei2012}).

After the documents are created, they are all that we have to analyse.
The term usage in each document, \(w_{1:D, 1:N}\), is observed, but the
topics are hidden, or `latent'. We do not know the topics of each
document, nor how terms defined the topics. That is, we do not know the
probability distributions of Figures @ref(fig:topicsoverdocuments) or
@ref(fig:topicsoverterms). In a sense we are trying to reverse the
document generation process -- we have the terms and we would like to
discover the topics.

If the earlier process around how the documents were generated is
assumed and we observe the terms in each document, then we can obtain
estimates of the topics (\citet{SteyversGriffiths2006}). The outcomes of
the LDA process are probability distributions and these define the
topics. Each term will be given a probability of being a member of a
particular topic, and each document will be given a probability of being
about a particular topic. That is, we are trying to calculate the
posterior distribution of the topics given the terms observed in each
document (\citet{blei2012}, p.~7):
\[p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N} | w_{1:D, 1:N}) = \frac{p\left(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}\right)}{p(w_{1:D, 1:N})}.\]

The initial practical step when implementing LDA given a collection of
documents is to remove `stop words'. These are words that are common,
but that don't typically help to define topics. There is a general list
of stop words such as: ``a''; ``a's''; ``able''; ``about'';
``above''\ldots{} An additional list of words that are commonly found in
Hansard, but likely don't help define topics is added to the general
list. These additions include words such as: ``act''; ``amendment'';
``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
can be found in Appendix @ref(hansard-stop-word). We also remove
punctuation and capitalisation. The documents need to then be
transformed into a document-term-matrix. This is essentially a table
with a column of the number of times each term appears in each document.

After the dataset is ready, the R package `topicmodels' by
\citet{Grun2011} can be used to implement LDA and approximate the
posterior. It does this using Gibbs sampling or the variational
expectation-maximization algorithm. Following
\citet{SteyversGriffiths2006} and \citet{Darling2011}, the Gibbs
sampling process attempts to find a topic for a particular term in a
particular document, given the topics of all other terms for all other
documents. Broadly, it does this by first assigning every term in every
document to a random topic, specified by Dirichlet priors with
\(\alpha = \frac{50}{K}\) and \(\eta = 0.1\)
(\citet{SteyversGriffiths2006} recommends \(\eta = 0.01\)), where
\(\alpha\) refers to the distribution over topics and \(\eta\) refers to
the distribution over terms (\citet{Grun2011}, p.~7). It then selects a
particular term in a particular document and assigns it to a new topic
based on the conditional distribution where the topics for all other
terms in all documents are taken as given (\citet{Grun2011}, p.~6):
\[p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} \]
where \(z'_{d, n}\) refers to all other topic assignments;
\(\lambda'_{n\rightarrow k}\) is a count of how many other times that
term has been assigned to topic \(k\); \(\lambda'_{.\rightarrow k}\) is
a count of how many other times that any term has been assigned to topic
\(k\); \(\lambda'^{(d)}_{n\rightarrow k}\) is a count of how many other
times that term has been assigned to topic \(k\) in that particular
document; and \(\lambda'^{(d)}_{-i}\) is a count of how many other times
that term has been assigned in that document. Once \(z_{d,n}\) has been
estimated, then estimates for the distribution of words into topics and
topics into documents can be backed out.

This conditional distribution assigns topics depending on how often a
term has been assigned to that topic previously, and how common the
topic is in that document (\citet{SteyversGriffiths2006}). The initial
random allocation of topics means that the results of early passes
through the corpus of document are poor, but given enough time the
algorithm converges to an appropriate estimate.

The choice of the number of topics, \emph{k}, affects the results, and
must be specified \emph{a priori}. If there is a strong reason for a
particular number, then this can be used. Otherwise, one way to choose
an appropriate number is to use a test and training set process.
Essentially, this means running the process on a variety of possible
values for \emph{k} and then picking an appropriate value that performs
well.

One weakness of the LDA method is that it considers a `bag of words'
where the order of those words does not matter (\citet{blei2012}). It is
possible to extend the model to reduce the impact of the bag-of-words
assumption and add conditionality to word order. Additionally,
alternatives to the Dirichlet distribution can be used to extend the
model to allow for correlation. For instance, in Hansard topics related
the army may be expected to be more commonly found with topics related
to the navy, but less commonly with topics related to banking. This
motivates the use of the Structural Topic Model, described in the next
section.

\subsection{Structural Topic Model}\label{structural-topic-model}

\subsubsection{Overview and example}\label{overview-and-example}

{[}TBD{]}

Note that each of the states and the Commonwealth are treated
independently here. Future work could expand the model to better
understand, and allow, for correlation between them.

\subsubsection{Considering events}\label{considering-events}

{[}TBD{]}

\section{Results}\label{results}

\subsection{Political events}\label{political-events}

\begin{quote}
\emph{When you change the government, you change the country.} Paul
Keating.
\end{quote}

Change of government.

\subsection{Polling events}\label{polling-events}

\begin{quote}
\emph{The only poll that matters is the one on election day.} John
Howard.
\end{quote}

{[}TBD{]}

\subsection{Economic events}\label{economic-events}

Major economic changes.

{[}TBD{]}

\subsection{External events}\label{external-events}

\begin{quote}
\emph{Events, dear boy, events.} Attributed to Harold Macmillan.
\end{quote}

Major event such as 9/11 attacks, or economic change.

\section{Summary and conclusions}\label{summary-and-conclusions}

What could happen if we had longer terms. Eg GST needed multiple
generations of politicians but carbon tax couldn't because it was one
generation.

Text analysis has well-known biases and weaknesses and is a complement
to more detailed analysis such as qualitative methods and case studies.
We consider the results presented in this paper, as well as many of
those results of the larger text-as-data research program, as fitting
within findings based on other methods.

\newpage

\section{Appendix}\label{appendix}

\subsection{Selection of number of
topics}\label{selection-of-number-of-topics}

\subsection{Robustness of results}\label{robustness-of-results}

Here we change the number of sitting days considered either side of an
event. The results in the main section of the paper are for the nearest
ten days either side of an event. Here are show that the results are
essentially the same if the nearest one, two, five, and twenty days
either side of an event.

\subsection{Document sources}\label{document-sources}

Where from?

Which years are being used (not non-OCRd)

\newpage

\newpage
\singlespacing 
\renewcommand\refname{References}
\bibliography{../bibliography.bib}

\end{document}

### 2018-09-13 scripts/to_parse_pdfs/parse_each_pdf_and_save_csv_pdftools.R

@@ -3,7 +3,7 @@
 # Purpose: This file takes Australian Hansard PDF files and it converts them to CSVs of text data that can be analysed.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 12 September 2018
+# Last updated: 13 September 2018
 # Prerequisites: You need to have downloaded the PDFs from the parliament's website. There are many GBs of PDFs and they are saved on an external drive - have fun finding that future-Rohan - and also the Berkeley Demography server. For testing purposes there should be some in the /inputs/for_testing_hansard_pdf folder.
 # To do:
 # - Check which footers need to be replaced
@@ -22,22 +22,16 @@ library(tidyverse)
 library(tictoc)
 library(tm)
 # update.packages()
-
 # Get the spell checker
 fix_wrong_spellings <- read_csv2("inputs/misc/misspelt_words_with_corrections.csv") %>% 
   mutate(numberOfCharacters = nchar(original)) %>% 
   arrange(desc(numberOfCharacters)) %>% 
   select(-numberOfCharacters)
-
-
-# load("outputs/misc/corrections.RData")
-
-# Set up furrr plan
+# Set up furrr
 plan(multiprocess)
 
 
 #### Create lists of PDFs to read and file names to save text as ####
-# Get list of Hansard PDF filenames
 # Change the path as required:
 # use_this_path_to_get_pdfs  <- "/Volumes/Backup/hansard_pdfs"
 use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
@@ -45,6 +39,7 @@ use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
 use_this_path_to_save_csv_files  <- "outputs/hansard/hansard_csv_files"
 # use_this_path_to_save_csv_files  <- "/Volumes/Backup/hansard_csv"
 
+# Get list of Hansard PDF filenames
 file_names <-
   list.files(
     path = use_this_path_to_get_pdfs,
@@ -52,31 +47,13 @@ file_names <-
     recursive = TRUE,
     full.names = TRUE
   )
-file_names <- file_names %>% sample()
-file_names
-
-# file_names <- sample(file_names, 500)  # Just get 500 of them
-# get_these <- paste0("/Volumes/Backup/hansard_pdfs/", relevant_dates$allDates, ".pdf")
-# file_names <- file_names[file_names %in% get_these] 
-
[…]

### 2018-09-15 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update the topic modelling and minor improvements to the paper

--- 2018-09-12 outputs/docs/events/paper.Rmd
@@
 ---
-title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
-author:
-  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
-  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
-date: "`r format(Sys.time(), '%d %B %Y')`"
-fontsize: 12pt
 output: 
   pdf_document:
-    number_sections: true
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    latex_engine: pdflatex
+    template: svm-latex-ms.tex
+title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for their helpful comments, guidance and suggestions.
+**Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
+author:
+- name: Monica Alexander
+  affiliation: University of Toronto
+- name: Rohan Alexander
+  affiliation: Australian National University
+abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
+keywords: "text analysis, politics, Australia"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+fontfamily: mathpazo
+fontsize: 12pt
+# spacing: double
 bibliography: ../bibliography.bib
-abstract: |
-  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017.
-We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].
-
+biblio-style: apsr
+endnote: no
 ---
@@
 # Introduction
-New governments often go out of their way to be different to the governments they replace.
-For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
+New governments often go to some trouble to be different from the governments they replace.
+For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard, and one of Tony Abbott's first acts was to repeal Rudd's carbon tax.
 Similarly, significant events can alter the course of a government.
-For instance, consider the change in the Howard government after the 9/11 attacks.
+For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings.
 However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party?
@@
 # Data
-Following the example of the UK, a text-based record of what was said in Australian parliaments called Hansard has been regularly made available since their establishment.
-While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+Following the example of the UK a text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^1] Hansard records are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
+For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015.
+In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990, and @Willis2017 examined how politicians understood climate change.
+In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
+
+Australian Hansard records have been analysed for various purposes, but usually not at scale.
+For instance, @Rasiah2010 examines Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
+@GansLeigh2012 examined Australian Hansard records by hand to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
+
+[^1]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
 For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
@@
 
-The parliaments generally make their hansard records available online in PDF formats that can be processed by text readers such as @Ooms2018pdftools.
-Some records such as the early days of the New South Wales parliament have yet to be put through a professional OCR process, although the Google Tesseract engine as implemented by @Ooms2018tesseract can be used to provide a useful first-pass if necessary.
-Hansard records that are still images are not used in this analysis (see the Appendix for more details).
-
-Hansard records are available for all six Australian states and the Commonwealth although the period varies (Table 1).
-Here we focus on the lower houses although a similar analysis is possible in a bicameral setting.
+The Australian parliaments generally make their Hansard records available online as PDFs that can be downloaded.
+The Federal parliament additionally makes XML records available for years between 1901 and 1980 as well as from 1997.
+There are roughly 65,000 **(UPDATE)** hansard records available across the chambers of the state and federal parliaments (Table 1) **(UPDATE NUMBERING)**.
+As with any larger-scale data process, there are many issues with this dataset of PDFs and the known ones are detailed in the Appendix.
 
@@
 
-We start with the PDFs that have been through an OCR process (or compiled more recently using software that makes them readable by default) as supplied by various parliaments (see the Appendix for specific sources).
-We then use the \texttt{PDFtools} R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS].
+The PDFs were processed using the \texttt{PDFtools} R package of @Ooms2018pdftools.
+A small proportion of the Hansard records had not been put through a professional OCR process and although the Google Tesseract engine as implemented by @Ooms2018tesseract provided some useful data, these were not used in this analysis.
+
+to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS].
 The result is a
@@
 
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics"}
 document_1 <- tibble(
@@
 
-par(mfrow=c(2,1))
+# par(mfrow=c(2,1))
 ggplot(document_1, aes(Topics, Probability)) +
@@
   coord_cartesian(ylim = c(0, 0.4))
-
 ggplot(document_2, aes(Topics, Probability)) +
@@
 # Appendix
+
+## Document sources
+Where from?
+
+Which years are being used (not non-OCRd)
+
+## Dataset issues
+Which PDFs are missing or have no content, etc.
+
+## PDF to CSV issues
+Insert graph of stop words over time.
+
 ## Selection of number of topics
@@
 
-## Document sources
-Where from?
-
-Which years are being used (not non-OCRd)
-
 \newpage

### 2018-09-15 outputs/docs/events/svm-rmarkdown-article-example.tex
Update the topic modelling and minor improvements to the paper

@@
 
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+
 \title{Nobody expects the Spanish Inquisition: Which events drive topic change
-in Australian parliaments? \thanks{Thank you to X, Y, Z and Y for their helpful comments, guidance and
-suggestions. \textbf{Version as of}: September 13, 2018;
-\textbf{Comments welcomed}:
+in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for
+their helpful comments, guidance and suggestions. \textbf{Version as
+of}: September 15, 2018; \textbf{Comments welcome}:
 \href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }
@@
 
-New governments often go to some trouble to be different to the
+New governments often go to some trouble to be different from the
 governments they replace. For instance, Kevin Rudd's apology to
-Indigenous Australians was supported by all living former Prime
-Ministers apart from his immediate predecessor. Similarly, Similarly,
+Indigenous Australians was not supported by John Howard, and one of Tony
+Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
 significant events can alter the course of a government. For instance,
-consider the change in the Howard government after the 9/11 attacks.
-However it is not so clear which events drive changes in topics, for
-instance, do they change when the government is replaced by another of
-its own party? And which events are temporary, for instance when an
-economic crisis abates, do the topics return to pre-crisis levels?
+consider the change in the Howard government after the 9/11 attacks or
+the 2002 Bali bombings. However it is not so clear which events drive
+changes in topics, for instance, do they change when the government is
+replaced by another of its own party? And which events are temporary,
+for instance when an economic crisis abates, do the topics return to
+pre-crisis levels?
 
@@
 
-Following the example of the UK, a text-based record of what was said in
-Australian parliaments called Hansard has been regularly made available
-since their establishment. While Hansard is not necessarily verbatim, it
-is considered close enough for text-as-data purposes. For instance,
+Following the example of the UK a text record called Hansard of what was
+said in Australian parliaments has been made available since their
+establishment.\footnote{While Hansard is not necessarily verbatim, it is
+  considered close enough for text-as-data purposes. For instance,
   \citet{Mollin2008} found that in the case of the UK Hansard the
@@
   found that changes were usually made by those responsible for creating
-the Hansard record, instead of the parliamentarians. Both these findings
-provide reassurance that differences between Hansard and a verbatim
-record would not be meaningful for this paper.
+  the Hansard record, instead of the parliamentarians. Both these
+  findings provide reassurance that differences between Hansard and a
+  verbatim record would not be meaningful for this paper.} Hansard
+records are an increasingly popular source of data as new methods and
+reduced computational costs make larger-scale analysis easier. For
+instance, the digitisation of the Canadian Hansard,
+\citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
+parliamentary disruptions in Canada increased between 1926 and 2015. In
+the UK, \citet{Duthie2016} analysed Hansard records to examine which
+politicians made supportive or aggressive statements toward other
+politicians between 1979 and 1990, and \citet{Willis2017} examined how
+politicians understood climate change. In New Zealand,
+\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
+and \citet{Graham2016} examined unparliamentary language between 1890
+and 1950.
 
-The parliaments generally make their hansard records available online in
-PDF formats that can be processed by text readers such as
-\citet{Ooms2018pdftools}. Some records such as the early days of the New
-South Wales parliament have yet to be put through a professional OCR
-process, although the Google Tesseract engine as implemented by
-\citet{Ooms2018tesseract} can be used to provide a useful first-pass if
-necessary. Hansard records that are still images are not used in this
-analysis (see the Appendix for more details).
+Australian Hansard records have been analysed for various purposes, but
+usually not at scale. For instance, \citet{Rasiah2010} examines Hansard
+records for the Australian House of Representatives to examine whether
+politicians attempted to evade questions about Iraq during February and
+March 2003. \citet{GansLeigh2012} examined Australian Hansard records by
+hand to associate mentions by politicians of certain public
+intellectuals with neutral or positive sentiment.
 
-Hansard records are available for all six Australian states and the
-Commonwealth although the period varies (Table 1). Here we focus on the
-lower houses although a similar analysis is possible in a bicameral
-setting.
+The Australian parliaments generally make their Hansard records
+available online as PDFs that can be downloaded. The Federal parliament
+additionally makes XML records available for years between 1901 and 1980
+as well as from 1997. There are roughly 65,000 \textbf{(UPDATE)} hansard
+records available across the chambers of the state and federal
+parliaments (Table 1) \textbf{(UPDATE NUMBERING)}. As with any
+larger-scale data process, there are many issues with this dataset of
+PDFs and the known ones are detailed in the Appendix.
 
@@
 
-We start with the PDFs that have been through an OCR process (or
-compiled more recently using software that makes them readable by
-default) as supplied by various parliaments (see the Appendix for
-specific sources). We then use the \texttt{PDFtools} R package of
-\citet{Ooms2018pdftools} to extract these as text-based CSV records, and
-clean the records using functions from the \texttt{Tidyverse} R package
-of \citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
+The PDFs were processed using the \texttt{PDFtools} R package of
+\citet{Ooms2018pdftools}. A small proportion of the Hansard records had
+not been put through a professional OCR process and although the Google
+Tesseract engine as implemented by \citet{Ooms2018tesseract} provided
+some useful data, these were not used in this analysis.
+
+to extract these as text-based CSV records, and clean the records using
+functions from the \texttt{Tidyverse} R package of
+\citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
 \citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a
@@
 
+\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
+\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-2.pdf}
+
 Similarly, each topic could be considered a probability distribution
@@
 @ref(fig:topicsoverterms)).
+
+\begin{figure}
+\includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1} \includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-2} \caption{Probability distributions over terms}\label{fig:topicsoverterms}
+\end{figure}
 
@@
 
+\subsection{Document sources}\label{document-sources}
+
+Where from?
+
+Which years are being used (not non-OCRd)
+
+\subsection{Dataset issues}\label{dataset-issues}
+
+Which PDFs are missing or have no content, etc.
+
+\subsection{PDF to CSV issues}\label{pdf-to-csv-issues}
+
+Insert graph of stop words over time.
+
 \subsection{Selection of number of
@@
 
-\subsection{Document sources}\label{document-sources}
-
-Where from?
-
-Which years are being used (not non-OCRd)
-
 \newpage

### 2018-09-15 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -25,62 +25,11 @@ library(viridis)
 plan(multiprocess)
 
 # Load Hansard words by day
-load("outputs/big_files_do_not_push/all_hansard_words_by_date.Rda") # Takes a while
+load("outputs/big_files_do_not_push/all_hansard_words_by_date.Rda") # Takes 30 sec or so
 # Load the election dates
 election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
 # Load the Hansard dates
 hansard_dates <- read_csv("inputs/misc/hansard_dates.csv")
-
-
-#### Identify the dates that are the 10 days of sitting immediately before and after an election ####
-all_dates <- tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) # First make a list of all the dates from Federation
-all_dates <- all_dates %>%
-  mutate(
-    electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
-    hansardDate = if_else(allDates %in% hansard_dates$hansardDates, 1, 0)
-  ) %>%
-  filter(electionDate == 1 | hansardDate == 1) %>% # Reduce that of all dates since Federation to only those that we have a Hansard for or that had an election
-  mutate(
-    tenAfterElectionDay = lag(electionDate, n = 10),
-    elevenBeforeElectionDay = lead(electionDate, n = 11)
-  ) %>% # Use eleven because we're going to get rid of 11 onward in order to get the ten
-  mutate(
-    elevenBeforeElectionDay = na_if(elevenBeforeElectionDay, 0),
-    tenAfterElectionDay = na_if(tenAfterElectionDay, 0)
-  )
-
-all_dates$elevenBeforeElectionDay[all_dates$elevenBeforeElectionDay == 1] <- 2
-
-relevant_dates <- all_dates %>%
-  mutate(tenAfterElectionDay = if_else(
-    !is.na(elevenBeforeElectionDay),
-    elevenBeforeElectionDay,
-    tenAfterElectionDay
-  )) %>%
-  fill(tenAfterElectionDay, .direction = "up") %>%
-  mutate(tenAfterElectionDay = na_if(tenAfterElectionDay, 2)) %>%
-  mutate(dateOfInterest = tenAfterElectionDay) %>%
-  select(-tenAfterElectionDay,-elevenBeforeElectionDay,-hansardDate) %>%
[…]

### 2018-09-16 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update data section of paper

@@
 title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for their helpful comments, guidance and suggestions.
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions.
 **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
@@
 New governments often go to some trouble to be different from the governments they replace.
-For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard, and one of Tony Abbott's first acts was to repeal Rudd's carbon tax.
-Similarly, significant events can alter the course of a government.
-For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings.
-However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party?
-And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?
+For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax.
+Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
+However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.
 
-In this paper we use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to model the topics of discussion in Australian parliaments.
-The advantage of this model is that it allows for topics to be correlated between sitting days, which then allows us to test for changes in topics at various events.
-The events that we focus on are changes in: 1) government; 2) the political environment (as defined by polling or other results); 3) economic conditions; and 4) the significant events (such as the 9/11 attacks or the Bali Bombings).
+In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days.
+We then construct a **[XYZ]** model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
 
-We find [INSERT RESULTS]. We also explored the other direction (the impact of what was said in parliaments on events) but it was difficult to find significant effects.
+We find **[INSERT RESULTS]**.
 
-Our work fits into [WHATEVER IT FITS INTO].
-While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and hence can identify patterns that may otherwise be overlooked.
+Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
+A forecasting model is then used to construct a counterfactual.
+Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis.
+While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
 
@@
 # Data
-Following the example of the UK a text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^1] Hansard records are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
-For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015.
-In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990, and @Willis2017 examined how politicians understood climate change.
+## Parliamentary text data
+Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Hansard records and their equivalents are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
+For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015 and @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
+In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
 In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
+And in the US @GentzkowShapiroTaddy2018 examine congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
 
-Australian Hansard records have been analysed for various purposes, but usually not at scale.
-For instance, @Rasiah2010 examines Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
-@GansLeigh2012 examined Australian Hansard records by hand to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
-
-[^1]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
 For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
 @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.
-Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.
 
-The Australian parliaments generally make their Hansard records available online as PDFs that can be downloaded.
-The Federal parliament additionally makes XML records available for years between 1901 and 1980 as well as from 1997.
-There are roughly 65,000 **(UPDATE)** hansard records available across the chambers of the state and federal parliaments (Table 1) **(UPDATE NUMBERING)**.
-As with any larger-scale data process, there are many issues with this dataset of PDFs and the known ones are detailed in the Appendix.
+Australian Hansard records have been analysed for various purposes, but usually not at larger-scale.
+For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
+And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
 
-| Parliament | House | Years used | Notes |
+Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
+There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**.
+As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.
+
+[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through today from Open Australia’s website.
+
+| Parliament       | House                    | Years used | Number of records |
 |:------|-----:|---------:|------:|
-| Commonwealth | House of Representatives | 1901 - 2017 | - |
-| Queensland | ? | 1861 - 2017 | - |
-| New South Wales | ? | ? - 2017 | - |
-| Victoria | ? | ? - 2017 | - |
-| Tasmania | ? | ? - 2017 | - |
-| South Australia | ? | ? - 2017 | - |
-| Western Australia | ? | ? - 2017 | - |
+| Commonwealth      | House of Representatives | 1901 - 2017 | 7,873 |
+|                   | Senate                   | 1901 - 2017 | **[TBD]** |
+| Queensland        | Legislative Assembly     | 1860 - 2017 | **[TBD]** |
+|                   | Legislative Council      | 1860 - 1922 | **[TBD]** |
+| New South Wales[^2]   | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
+|                   | Legislative Council     | 1856 - 2017 | **[TBD]** |
+| Victoria          | Legislative Assembly     | 1856 - 2017 | **[TBD]** |
+|                   | Legislative Council      | 1851 - 2017 | **[TBD]** |
+| Tasmania[^3]      | House of Assembly        | 1856 - 2017 | **[TBD]** |
+|                   | Legislative Council      | 1856 - 2017 | **[TBD]** |
+| South Australia[^4] | House of Assembly       | 1857 - 2017 | **[TBD]** |
+|                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
+| Western Australia[^5] | Legislative Assembly  | 1890 - 2017 | **[TBD]** |
+|                   | Legislative Council       | 1832 - 2017 | **[TBD]** |
 
-The PDFs were processed using the \texttt{PDFtools} R package of @Ooms2018pdftools.
-A small proportion of the Hansard records had not been put through a professional OCR process and although the Google Tesseract engine as implemented by @Ooms2018tesseract provided some useful data, these were not used in this analysis.
+[^2]: The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper.
+However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
 
-to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS].
-The result is a
+[^3]: **[Update this, depending on final Tassie records]**.
+
+[^4]: **[Update this, depending on final SA records]**.
+
+[^5]: **[Update this, depending on final WA records]**.
+
+The formatting of the Hansard records changes between the different parliaments and over time.
+We use R scripts to convert the PDFs into daily text records.[^seeMyScripts] These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
+An example of the latter issue is that 'the' is often parsed as 'thc'.
+These errors are fixed when they occur at scale and can be identified.
+
+[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in the Appendix. The full set of scripts are available on request.
+
+**[ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT RECORD?]**
+
+These daily records are the main data used in this paper, however the daily records are also further divided into individual-level records.
+Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
+Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed that day.
+
+Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
+For instance, when the Hansard record is trying to indicate that a person is speaking, as opposed to being mentioned (for more on the political effect of being mentioned see @Alexander2018), often the name is in upper case (e.g.
+'Mr WHITLAM' or 'Mr MENZIES'); followed by a dash or colon; or are next to some title within brackets.
+There is substantial variation in how the person making a statement is identified.
+Again some error is introduced at this stage because of inconsistencies over time and between the parliaments, as well as the errors introduced during the PDF parsing stage.
+There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.
+
+## Parliamentary meta data
+
+TALK ABOUT THE ADDITIONAL DATA
+
+In general,
+
+## Topic pre-processing
+There is much more on topic modelling in the next section because topics are the main data analysed in this paper, but here we briefly discuss the pre-processing steps  of creating the topics.
+
+records, and clean the records using functions from the \texttt{Tidyverse} R package of @Wickham2017, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a
 
@@
 
+## Example workflow
+Example of the workflow from PDF to text
+
 ## PDF to CSV issues

### 2018-09-16 outputs/docs/events/svm-rmarkdown-article-example.tex
Update data section of paper

@@
 \title{Nobody expects the Spanish Inquisition: Which events drive topic change
-in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton and Martine Mariotti for
-their helpful comments, guidance and suggestions. \textbf{Version as
-of}: September 15, 2018; \textbf{Comments welcome}:
+in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
+Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
+suggestions. \textbf{Version as of}: September 16, 2018;
+\textbf{Comments welcome}:
 \href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }
@@
 governments they replace. For instance, Kevin Rudd's apology to
-Indigenous Australians was not supported by John Howard, and one of Tony
-Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
-significant events can alter the course of a government. For instance,
-consider the change in the Howard government after the 9/11 attacks or
-the 2002 Bali bombings. However it is not so clear which events drive
-changes in topics, for instance, do they change when the government is
-replaced by another of its own party? And which events are temporary,
-for instance when an economic crisis abates, do the topics return to
-pre-crisis levels?
+Indigenous Australians was not supported by John Howard and then one of
+Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
+significant events such as the 9/11 attacks or the Great Recession have
+often altered the course of a government. However it is not so clear
+which events drive changes, for how long these changes persist, and what
+was given up due to the change.
 
-In this paper we use the Structural Topic Model (STM) of
-\citet{RobertsStewartAiroldi2016} to model the topics of discussion in
-Australian parliaments. The advantage of this model is that it allows
-for topics to be correlated between sitting days, which then allows us
-to test for changes in topics at various events. The events that we
-focus on are changes in: 1) government; 2) the political environment (as
-defined by polling or other results); 3) economic conditions; and 4) the
-significant events (such as the 9/11 attacks or the Bali Bombings).
+In this paper we examine text records of what was said in Australian
+state and federal parliaments from the mid-1800s through to 2017. We use
+the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
+impose structure such as correlation between days. We then construct a
+\textbf{{[}XYZ{]}} model to examine changes at various types of events,
+including: changes in government; changes in the political environment
+(as defined by polling or other results); changes in economic
+conditions; and other significant events (such as the 9/11 attacks or
+the Bali bombings).
 
-We find {[}INSERT RESULTS{]}. We also explored the other direction (the
-impact of what was said in parliaments on events) but it was difficult
-to find significant effects.
+We find \textbf{{[}INSERT RESULTS{]}}.
 
-Our work fits into {[}WHATEVER IT FITS INTO{]}. While using text as data
-has well-known shortcomings, it allows larger-scale analysis that would
-not be viable using less-automated approaches and hence can identify
-patterns that may otherwise be overlooked.
+Our paper applies a topic model to a dataset of larger-scale
+parliamentary text records from multiple Australian parliaments. A
+forecasting model is then used to construct a counterfactual. Our work
+fits into a growing literature that considers text as a input to more
+usual quantitative techniques, rather than requiring separate analysis.
+While using text as data has well-known shortcomings, it allows
+larger-scale analysis that would not be viable using less-automated
+approaches and so it can identify patterns that may otherwise be
+overlooked.
 
@@
 
-Following the example of the UK a text record called Hansard of what was
-said in Australian parliaments has been made available since their
-establishment.\footnote{While Hansard is not necessarily verbatim, it is
-  considered close enough for text-as-data purposes. For instance,
+\subsection{Parliamentary text data}\label{parliamentary-text-data}
+
+Following the example of the UK a daily text record called Hansard of
+what was said in Australian parliaments has been made available since
+their establishment.\footnote{While Hansard is not necessarily verbatim,
+  it is considered close enough for text-as-data purposes. For instance,
   \citet{Mollin2008} found that in the case of the UK Hansard the
@@
   found that changes were usually made by those responsible for creating
-  the Hansard record, instead of the parliamentarians. Both these
-  findings provide reassurance that differences between Hansard and a
-  verbatim record would not be meaningful for this paper.} Hansard
-records are an increasingly popular source of data as new methods and
-reduced computational costs make larger-scale analysis easier. For
-instance, the digitisation of the Canadian Hansard,
+  the Hansard record, instead of the parliamentarians.} Hansard records
+and their equivalents are an increasingly popular source of data as new
+methods and reduced computational costs make larger-scale analysis
+easier. For instance, the digitisation of the Canadian Hansard,
 \citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
-parliamentary disruptions in Canada increased between 1926 and 2015. In
-the UK, \citet{Duthie2016} analysed Hansard records to examine which
-politicians made supportive or aggressive statements toward other
-politicians between 1979 and 1990, and \citet{Willis2017} examined how
-politicians understood climate change. In New Zealand,
+parliamentary disruptions in Canada increased between 1926 and 2015 and
+\citet{RheaultCochran2018} to examine ideology and party polarisation in
+Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
+records to examine which politicians made supportive or aggressive
+statements toward other politicians between 1979 and 1990 and
+\citet{PetersonSpirling2018} examined polarisation. In New Zealand,
 \citet{Curran2017} modelled the topics discussed between 2003 and 2016,
 and \citet{Graham2016} examined unparliamentary language between 1890
-and 1950.
+and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
+congressional speech records from 1873 to 2016 to find that partisanship
+has risen in the past few decades.
 
 Australian Hansard records have been analysed for various purposes, but
-usually not at scale. For instance, \citet{Rasiah2010} examines Hansard
-records for the Australian House of Representatives to examine whether
-politicians attempted to evade questions about Iraq during February and
-March 2003. \citet{GansLeigh2012} examined Australian Hansard records by
-hand to associate mentions by politicians of certain public
+usually not at larger-scale. For instance, \citet{Rasiah2010} examined
+Hansard records for the Australian House of Representatives to examine
+whether politicians attempted to evade questions about Iraq during
+February and March 2003. And \citet{GansLeigh2012} examined Australian
+Hansard records to associate mentions by politicians of certain public
 intellectuals with neutral or positive sentiment.
 
-The Australian parliaments generally make their Hansard records
-available online as PDFs that can be downloaded. The Federal parliament
-additionally makes XML records available for years between 1901 and 1980
-as well as from 1997. There are roughly 65,000 \textbf{(UPDATE)} hansard
-records available across the chambers of the state and federal
-parliaments (Table 1) \textbf{(UPDATE NUMBERING)}. As with any
-larger-scale data process, there are many issues with this dataset of
-PDFs and the known ones are detailed in the Appendix.
+Australian parliaments generally make their daily Hansard records
+available online as PDFs and these are considered the official release.
+There is a more limited set of XML records available in some
+cases.\footnote{Tim Sherratt makes these XML records available as a
+  single download and also presents them in a website
+  (\url{http://historichansard.net/}) that can be used to explore
+  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
+  records from 1998 to 2014 are available from Andrew Turpin's website,
+  and from 2006 through today from Open Australia's website.} There are
+65,000 \textbf{{[}UPDATE{]}} Hansard records available across the state
+and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}. As
+with any larger-scale data process, there are various issues with some
+of the PDFs and the known ones are detailed in the Appendix.
 
@@
 \toprule
-Parliament & House & Years used & Notes\tabularnewline
+Parliament & House & Years used & Number of records\tabularnewline
 \midrule
 \endhead
-Commonwealth & House of Representatives & 1901 - 2017 & -\tabularnewline
-Queensland & ? & 1861 - 2017 & -\tabularnewline
-New South Wales & ? & ? - 2017 & -\tabularnewline
-Victoria & ? & ? - 2017 & -\tabularnewline
-Tasmania & ? & ? - 2017 & -\tabularnewline
-South Australia & ? & ? - 2017 & -\tabularnewline
-Western Australia & ? & ? - 2017 & -\tabularnewline
+Commonwealth & House of Representatives & 1901 - 2017 &
+7,873\tabularnewline
+& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+Queensland & Legislative Assembly & 1860 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1860 - 1922 & \textbf{{[}TBD{]}}\tabularnewline
+New South Wales\footnote{The NSW Legislative Council was established
+  earlier than 1856, however the earlier Hansard records have not been
+  through an independent OCR process and were not used in this paper.
+  However, the Google Tesseract OCR engine as implemented by
+  \citet{Ooms2018tesseract} provided useful data and these could be used
+  in the future.} & Legislative Assembly & 1856 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+Victoria & Legislative Assembly & 1856 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+Tasmania\footnote{\textbf{{[}Update this, depending on final Tassie
+  records{]}}.} & House of Assembly & 1856 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+South Australia\footnote{\textbf{{[}Update this, depending on final SA
+  records{]}}.} & House of Assembly & 1857 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+Western Australia\footnote{\textbf{{[}Update this, depending on final WA
+  records{]}}.} & Legislative Assembly & 1890 - 2017 &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
 \bottomrule
@@
 
-The PDFs were processed using the \texttt{PDFtools} R package of
-\citet{Ooms2018pdftools}. A small proportion of the Hansard records had
-not been put through a professional OCR process and although the Google
-Tesseract engine as implemented by \citet{Ooms2018tesseract} provided
-some useful data, these were not used in this analysis.
+The formatting of the Hansard records changes between the different
+parliaments and over time. We use R scripts to convert the PDFs into
+daily text records.\footnote{An example of the workflow and some
+  reduced-detail scripts are provided in the Appendix. The full set of
+  scripts are available on request.} These scripts are primarily based
+on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
+\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
+package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
+\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
+\citet{Gagolewski2018}. The functions of those packages are supported
+by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
+\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
+introduced at this stage because many of the records are in a two-column
+format that need to be separated, and the PDF parsing is not always
+accurate especially for older records. An example of the latter issue is
+that `the' is often parsed as `thc'. These errors are fixed when they
+occur at scale and can be identified.
 
-to extract these as text-based CSV records, and clean the records using
-functions from the \texttt{Tidyverse} R package of
-\citet{WickhamHadleyTidyverse}, the \texttt{Tidytext} R package of
-\citet{SilgeRobinson2016} and the {[}INSERT OTHERS{]}. The result is a
+\textbf{{[}ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT
+RECORD?{]}}
+
+These daily records are the main data used in this paper, however the
+daily records are also further divided into individual-level records.
+Sometimes these are just short interjections or notes that are not
+specific to any particular politician, such as `Honourable members
+interjecting'. Interjections are interesting in their own right, for
+instance \citet{Whyte2017} analysed them in a Canadian context for the
+period 1926 to 2015 to find that female MPs were more likely to be
+interrupted than male MPs, but do not usually contribute much to
+defining the topics being discussed that day.
+
+Usually the disaggregation into individual-level records is done by
+identifying politicians' names in particular patterns. For instance,
+when the Hansard record is trying to indicate that a person is speaking,
+as opposed to being mentioned (for more on the political effect of being
+mentioned see \citet{Alexander2018}), often the name is in upper case
+(e.g. `Mr WHITLAM' or `Mr MENZIES'); followed by a dash or colon; or are
+next to some title within brackets. There is substantial variation in
+how the person making a statement is identified. Again some error is
+introduced at this stage because of inconsistencies over time and
+between the parliaments, as well as the errors introduced during the PDF
+parsing stage. There is considerable variance but on average each daily
+record had 250 \textbf{{[}UPDATE{]}} individual-level records, resulting
+in roughly 15 million rows \textbf{{[}UPDATE{]}} across the state and
+federal parliaments.
+
+\subsection{Parliamentary meta data}\label{parliamentary-meta-data}
+
+TALK ABOUT THE ADDITIONAL DATA
+
+In general,
+
+\subsection{Topic pre-processing}\label{topic-pre-processing}
+
+There is much more on topic modelling in the next section because topics
+are the main data analysed in this paper, but here we briefly discuss
+the pre-processing steps of creating the topics.
+
+records, and clean the records using functions from the
+\texttt{Tidyverse} R package of \citet{Wickham2017}, the
+\texttt{Tidytext} R package of \citet{SilgeRobinson2016} and the
+{[}INSERT OTHERS{]}. The result is a
 
@@
 
+\subsection{Example workflow}\label{example-workflow}
+
+Example of the workflow from PDF to text
+
 \subsection{PDF to CSV issues}\label{pdf-to-csv-issues}

### 2018-09-17 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper

@@
 output: 
-  pdf_document:
+  bookdown::pdf_document2:
     citation_package: natbib
@@
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions.
-**Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au"
+**Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
 author:
@@
 fontsize: 12pt
+toc: FALSE
 # spacing: double
@@
 # Introduction
-New governments often go to some trouble to be different from the governments they replace.
+New governments often go to some trouble to be different to the governments they replace.
 For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax.
@@
 These errors are fixed when they occur at scale and can be identified.
+The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
 
@@
 
-## Parliamentary meta data
+Text usually needs to be pre-processed before topic models can be used.
+The specific steps that we take are to remove numbers and punctuation and to change all the words to lower case.
+Then the sentences are deconstructed and each word considered individually.
+In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
 
-TALK ABOUT THE ADDITIONAL DATA
+## Additional information
+Data from other sources are useful to complement the parliamentary text data.
+For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
+Also non-Hansard information about the politicians can inform the analysis.
+This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.
 
-In general,
+The main sources for this additional supplementary information are the handbooks supplied by the various parliaments (Table 2).
 
-## Topic pre-processing
-There is much more on topic modelling in the next section because topics are the main data analysed in this paper, but here we briefly discuss the pre-processing steps  of creating the topics.
+| Parliament  | House  | Source |
+|:------|-----:|---------:|
+| Commonwealth      | House of Representatives | Parliamentary Handbok |
+|                   | Senate                   | **[TBD]** |
+| Queensland        | Legislative Assembly     |  **[TBD]** |
+|                   | Legislative Council      | **[TBD]** |
+| New South Wales   | Legislative Assembly     | **[TBD]** |
+|                   | Legislative Council      | **[TBD]** |
+| Victoria          | Legislative Assembly     | **[TBD]** |
+|                   | Legislative Council      | **[TBD]** |
+| Tasmania          | House of Assembly        | **[TBD]** |
+|                   | Legislative Council      |  **[TBD]** |
+| South Australia   | House of Assembly        | **[TBD]** |
+|                   | Legislative Council      | **[TBD]** |
+| Western Australia | Legislative Assembly     | **[TBD]** |
+|                   | Legislative Council      | **[TBD]** |
 
-records, and clean the records using functions from the \texttt{Tidyverse} R package of @Wickham2017, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS]. The result is a
+The additional information from the handbooks had many errors and it was supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]
+
+[^seeMyAdditionalData]: An example of the additional information is provided in the Appendix. The datasets are available on request.
 
 # Model
-The primary model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{STM} R package of @RobertsStewartAiroldiRPackage.
+The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
 The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
@@
 ## Latent Dirichlet Allocation
-Each day's Hansard record needs to be classified by its topic.
-Sometimes Hansard includes titles that make the topic clear.
+When the text data is being modelled at the day level then each day's Hansard record needs to be classified by its topic.
+Although more- or less-fine levels of analysis are possible.
+Sometimes Hansard records includes titles that make the topic clear.
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.
+One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.
 
-The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics.
+The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
 A topic could be thought of as a collection of terms, and a document as a collection of topics.
 The topics are not specified *ex ante*; they are an outcome of the method.
+In this sense, this approach can be considered unsupervised machine learning.
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
@@
 After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.
-
 More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics.
@@
 
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics"}
-document_1 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
-  )
-
-document_2 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
-  )
-
-# par(mfrow=c(2,1))
-ggplot(document_1, aes(Topics, Probability)) +
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 3}
+tibble(
+  Topics = rep(c("1", "2", "3", "4", "5"), 2),
+  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
+  document = c(rep("Document 1", 5), rep("Document 2", 5))
+  ) %>%
+  ggplot(aes(Topics, Probability)) +
   geom_point() +
   theme_classic() +
-  labs(title = "Distribution over topics for Document 1") +
-  coord_cartesian(ylim = c(0, 0.4))
-ggplot(document_2, aes(Topics, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over topics for Document 2") +
-  coord_cartesian(ylim = c(0, 0.4))
+  facet_wrap(vars(document), ncol = 2, scales = "free") +
+  theme(strip.background = element_blank()) + 
+  coord_flip()
+
 ```
@@
 
-```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
-topic_1 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
-  )
-
-topic_2 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
-  )
-
-# par(mar = c(4, 4, 0.1, 0.1))
-ggplot(topic_1, aes(Terms, Probability)) +
+```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 3}
+tibble(
+  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
+  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
+  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
+  ) %>%
+  ggplot(aes(Terms, Probability)) +
   geom_point() +
   theme_classic() +
-  labs(title = "Distribution over terms for Topic 1") +
-  coord_cartesian(ylim = c(0, 0.4))
-ggplot(topic_2, aes(Terms, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over terms for Topic 2") +
-  coord_cartesian(ylim = c(0, 0.4))
+  facet_wrap(vars(Topics), ncol = 2, scales = "free") +
+  theme(strip.background = element_blank()) + 
+  coord_flip()
+
 ```

### 2018-09-17 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper

@@
 \textbf{Comments welcome}:
-\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}}  }
+\href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }
 
@@
 
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-New governments often go to some trouble to be different from the
+New governments often go to some trouble to be different to the
 governments they replace. For instance, Kevin Rudd's apology to
@@
 that `the' is often parsed as `thc'. These errors are fixed when they
-occur at scale and can be identified.
+occur at scale and can be identified. The \texttt{hunspell} package of
+\citet{Ooms2017} is also used to help find spelling issues.
 
@@
 
-\subsection{Parliamentary meta data}\label{parliamentary-meta-data}
+Text usually needs to be pre-processed before topic models can be used.
+The specific steps that we take are to remove numbers and punctuation
+and to change all the words to lower case. Then the sentences are
+deconstructed and each word considered individually. In addition to the
+packages already mentioned, in this step the R scripts to do this use
+the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
 
-TALK ABOUT THE ADDITIONAL DATA
+\subsection{Additional information}\label{additional-information}
 
-In general,
+Data from other sources are useful to complement the parliamentary text
+data. For instance, although the name, party, and division represented
+are contained in Hansard records they are inconsistent. Also non-Hansard
+information about the politicians can inform the analysis. This
+includes: date of birth and date of death; sex; date of entry to
+parliament and exit from parliament; some aspects of their pre- and
+post-parliamentary career; some aspects of their parliamentary career,
+such as ministry appointments; and electoral information such as primary
+and two-party-preferred results.
 
-\subsection{Topic pre-processing}\label{topic-pre-processing}
+The main sources for this additional supplementary information are the
+handbooks supplied by the various parliaments (Table 2).
 
-There is much more on topic modelling in the next section because topics
-are the main data analysed in this paper, but here we briefly discuss
-the pre-processing steps of creating the topics.
+\begin{longtable}[]{@{}lrr@{}}
+\toprule
+Parliament & House & Source\tabularnewline
+\midrule
+\endhead
+Commonwealth & House of Representatives & Parliamentary
+Handbok\tabularnewline
+& Senate & \textbf{{[}TBD{]}}\tabularnewline
+Queensland & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+New South Wales & Legislative Assembly &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+Victoria & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+Tasmania & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+South Australia & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+Western Australia & Legislative Assembly &
+\textbf{{[}TBD{]}}\tabularnewline
+& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
+\bottomrule
+\end{longtable}
 
-records, and clean the records using functions from the
-\texttt{Tidyverse} R package of \citet{Wickham2017}, the
-\texttt{Tidytext} R package of \citet{SilgeRobinson2016} and the
-{[}INSERT OTHERS{]}. The result is a
+The additional information from the handbooks had many errors and it was
+supplemented by data from the Australian Dictionary of Biography and
+Wikipedia.\footnote{An example of the additional information is provided
+  in the Appendix. The datasets are available on request.}
 
@@
 
-The primary model that we use in this paper is the Structural Topic
-Model (STM) as implemented by the \texttt{STM} R package of
+The main model that we use in this paper is the Structural Topic Model
+(STM) as implemented by the \texttt{stm} R package of
 \citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
@@
 
-Each day's Hansard record needs to be classified by its topic. Sometimes
-Hansard includes titles that make the topic clear. But not every
-statement has a title and the titles do not always define topics in a
-well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics of each statement in
-Hansard is to use the latent Dirichlet allocation (LDA) method of
-\citet{Blei2003latent}, for instance as implemented by the R package
-`topicmodels' by \citet{Grun2011}.
+When the text data is being modelled at the day level then each day's
+Hansard record needs to be classified by its topic. Although more- or
+less-fine levels of analysis are possible. Sometimes Hansard records
+includes titles that make the topic clear. But not every statement has a
+title and the titles do not always define topics in a well-defined and
+consistent way, especially over longer time periods. One way to get
+consistent estimates of the topics discussed in Hansard is to use the
+LDA method of \citet{Blei2003latent}, for instance as implemented by the
+R package `topicmodels' by \citet{Grun2011}.
 
@@
 document', in Hansard is made by speakers who decide the topics they
-would like to talk about in that document, and then chooses words,
+would like to talk about in that document, and then choose words,
 `terms', that are appropriate to those topics. A topic could be thought
@@
 The topics are not specified \emph{ex ante}; they are an outcome of the
-method. Terms are not necessarily unique to a particular topic, and a
-document could be about more than one topic. This provides more
-flexibility than other approaches such as a strict word count method.
-The goal is to have the words found in each day's Hansard group
+method. In this sense, this approach can be considered unsupervised
+machine learning. Terms are not necessarily unique to a particular
+topic, and a document could be about more than one topic. This provides
+more flexibility than other approaches such as a strict word count
+method. The goal is to have the words found in each day's Hansard group
 themselves to define topics.
@@
 want to speak about. After choosing the topics, the speaker then chooses
-appropriate words to use for each of those topics.
+appropriate words to use for each of those topics. More generally, the
+LDA topic model works by considering each document as having been
+generated by some probability distribution over topics. For instance, if
+there were five topics and two documents, then the first document may be
+comprised mostly of the first few topics; the other document may be
+mostly about the final few topics (Figure
+\ref{fig:topicsoverdocuments}).
 
-More generally, the LDA topic model works by considering each document
-as having been generated by some probability distribution over topics.
-For instance, if there were five topics and two documents, then the
-first document may be comprised mostly of the first few topics; the
-other document may be mostly about the final few topics (Figure
-@ref(fig:topicsoverdocuments)).
-
+\begin{figure}
+\centering
 \includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
-\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-2.pdf}
+\caption{\label{fig:topicsoverdocuments}Probability distributions over
+topics for two documents}
+\end{figure}
 
@@
 more weight to terms related to the economy (Figure
-@ref(fig:topicsoverterms)).
+\ref{fig:topicsoverterms}).
 
 \begin{figure}
-\includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1} \includegraphics[width=.49\linewidth]{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-2} \caption{Probability distributions over terms}\label{fig:topicsoverterms}
+\centering
+\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1.pdf}
+\caption{\label{fig:topicsoverterms}Probability distributions over terms}
 \end{figure}
@@
 document, nor how terms defined the topics. That is, we do not know the
-probability distributions of Figures @ref(fig:topicsoverdocuments) or
-@ref(fig:topicsoverterms). In a sense we are trying to reverse the
+probability distributions of Figures \ref{fig:topicsoverdocuments} or
+\ref{fig:topicsoverterms}. In a sense we are trying to reverse the
 document generation process -- we have the terms and we would like to
@@
 ``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
-can be found in Appendix @ref(hansard-stop-word). We also remove
+can be found in Appendix \ref{hansard-stop-word}. We also remove
 punctuation and capitalisation. The documents need to then be

### 2018-09-17 scripts/to_model_topics/first_make_topic_modelling_input_one_row_per_day.R

@@ -1,25 +1,20 @@
 #### Preamble ####
-# Purpose: This file takes Australian Hansard csv files and it converts them to a tidied tibble of text that can be analysed. The words are lowered and punctuation is removed, but stop words are not removed and they are not stemmed.
+# Purpose: This file takes Australian Hansard csv files and it converts them to a tidied tibble of text that can be analysed. The words are lowered and punctuation is removed, but stop words are not removed and they are not stemmed here.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 5 September 2018
-# Prerequisites: You need a folder of csv files e.g. the outputs of parse_each_pdf_and_save_csv_pdftools.R 
+# Last updated: 16 September 2018
+# Prerequisites: You need a folder of csv files e.g. the output of parse_each_pdf_and_save_csv_pdftools.R 
 # To do:
-# - Well, everything
+# - 
 
 
 #### Set up workspace ####
-# library(stringi)
-# library(stringr)
-# library(corpus)
 library(furrr)
 library(hunspell)
 library(lubridate)
-# library(SnowballC)
 library(tictoc)
 library(tidytext)
 library(tidyverse)
-# library(tm)
 # update.packages()
 
 

### 2018-09-17 scripts/to_model_topics/the_ficl.R

@@ -1,0 +1,28 @@
+install.packages("vars")
+library(vars)
+
+gammas <- read_csv("/Users/rohanalexander/Desktop/test_gammas.csv")
+
+data("Canada")
+head(Canada)
+
+gammas_test <- spread(gammas, topic, gamma)
+
+head(gammas_test)
+tail(gammas_test)
+
+head(Canada)
+
+VAR(gammas_test, p = 2, type = "none")
+
+
+
+install.packages("nnet")
+library(nnet)
+
+
+
+glm.fit = multinom(direccion~., data=datos)
+summary(glm.fit)
+#Prediction
+predict(glm.fit, newdata, "probs")

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add QLD scraper

@@
   affiliation: Australian National University
-abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+abstract: "We use a structural text model to explore what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+We then examine the effect of various events using a discrete choice model.
 We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
@@
 In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
-We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days.
-We then construct a **[XYZ]** model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
+We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days and changes over time, and for dimension reduction.
+We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
-A forecasting model is then used to construct a counterfactual.
+Our use of a discrete choice model allows us construct a counterfactual.
 Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis.
@@
 |                   | Senate                   | 1901 - 2017 | **[TBD]** |
-| Queensland        | Legislative Assembly     | 1860 - 2017 | **[TBD]** |
-|                   | Legislative Council      | 1860 - 1922 | **[TBD]** |
+| Queensland        | Legislative Assembly     | 1860 - 2017 | 9,699 |
+|                   | Legislative Council      | 1860 - 1922 | 4,156 |
 | New South Wales[^2]   | Legislative Assembly | 1856 - 2017 | **[TBD]** |

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.tex
Add QLD scraper

@@
 Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
-suggestions. \textbf{Version as of}: September 16, 2018;
+suggestions. \textbf{Version as of}: September 17, 2018;
 \textbf{Comments welcome}:
@@
 
-\noindent We use a structural text model to explore the effect of various events
-on what was said in Australian state and federal parliaments from the
-mid-1800s through to 2017. We find that: 1) changes of government are
-associated with topic changes only when there is also a change in the
-party in power; 2) polling results appear dissociated from parliamentary
-topics; 3) economic changes, such as financial crises have a significant
-effect; and 4) other events, such as an unexpected attack tend not to
-have a prolonged change.
+\noindent We use a structural text model to explore what was said in Australian
+state and federal parliaments from the mid-1800s through to 2017. We
+then examine the effect of various events using a discrete choice model.
+We find that: 1) changes of government are associated with topic changes
+only when there is also a change in the party in power; 2) polling
+results appear dissociated from parliamentary topics; 3) economic
+changes, such as financial crises have a significant effect; and 4)
+other events, such as an unexpected attack tend not to have a prolonged
+change.
 
@@
 the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
-impose structure such as correlation between days. We then construct a
-\textbf{{[}XYZ{]}} model to examine changes at various types of events,
-including: changes in government; changes in the political environment
-(as defined by polling or other results); changes in economic
-conditions; and other significant events (such as the 9/11 attacks or
-the Bali bombings).
+impose structure such as correlation between days and changes over time,
+and for dimension reduction. We then use a discrete choice model to
+examine changes at various types of events, including: changes in
+government; changes in the political environment (as defined by polling
+or other results); changes in economic conditions; and other significant
+events (such as the 9/11 attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale
-parliamentary text records from multiple Australian parliaments. A
-forecasting model is then used to construct a counterfactual. Our work
-fits into a growing literature that considers text as a input to more
-usual quantitative techniques, rather than requiring separate analysis.
-While using text as data has well-known shortcomings, it allows
-larger-scale analysis that would not be viable using less-automated
-approaches and so it can identify patterns that may otherwise be
-overlooked.
+parliamentary text records from multiple Australian parliaments. Our use
+of a discrete choice model allows us construct a counterfactual. Our
+work fits into a growing literature that considers text as a input to
+more usual quantitative techniques, rather than requiring separate
+analysis. While using text as data has well-known shortcomings, it
+allows larger-scale analysis that would not be viable using
+less-automated approaches and so it can identify patterns that may
+otherwise be overlooked.
 
@@
 & Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Queensland & Legislative Assembly & 1860 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1860 - 1922 & \textbf{{[}TBD{]}}\tabularnewline
+Queensland & Legislative Assembly & 1860 - 2017 & 9,699\tabularnewline
+& Legislative Council & 1860 - 1922 & 4,156\tabularnewline
 New South Wales\footnote{The NSW Legislative Council was established

### 2018-09-18 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -3,7 +3,7 @@
 # Purpose: Associate a group, based on similar topics, for every statement in Hansard that is either the last two weeks before an electin or the first two weeks.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 15 September 2018
+# Last updated: 17 September 2018
 # Prerequisites: 
 # Issues:
 
@@ -150,11 +150,51 @@ topic_model <- k_result %>%
   pull(topic_model) %>% 
   .[[1]]
 
-# Just run a quick one here for the results for the draft - DELETE START
+
+
+#### Just run a quick one here for the results for the draft - DELETE START
+# Identify which hansard date is the first after an election
+all_dates <- tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) # First make a list of all the dates from Federation
+all_dates <- all_dates %>%
+  mutate(
+    electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+    hansardDate = if_else(allDates %in% all_hansard_words$date, 1, 0)
+  ) %>%
+  filter(electionDate == 1 | hansardDate == 1) %>%  # Reduce that of all dates since Federation to only those that we have a Hansard for or that had an election
+  mutate(firstHansardAfterElection = lag(electionDate)) %>% 
+  select(allDates, firstHansardAfterElection) %>% 
+  filter(firstHansardAfterElection == 1)
+
+all_hansard_words <- all_hansard_words %>% 
+  left_join(all_dates, by = c("date" = "allDates"))
+
+all_hansard_words$firstHansardAfterElection[is.na(all_hansard_words$firstHansardAfterElection)] <- 0
+  
+processed_Hansard <- textProcessor(all_hansard_words$words, metadata = all_hansard_words)
+
+# HERE
+
+out <- prepDocuments(processed_Hansard$documents, processed_Hansard$vocab, processed_Hansard$meta, lower.thresh = 15)
+
+
+
+
+
+tidy_hansard <- tidy_hansard %>%
+  count(date, word, sort = TRUE) %>%
+  filter(n > 100)  # Here we remove any word that doesn't occur at least 100 times
+head(tidy_hansard)
+library(quanteda)
+?quanteda
+
+
+
 justOne <- stm(hansard_dfm, K = 100, verbose = TRUE)
 topic_model <- justOne
 rm(justOne)
-# DELETE END
+
[…]

### 2018-09-18 scripts/to_scrape_websites/get_1860-2017_PDFs_qld.R

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: This file gets Queensland Hansard PDF files from the parliament website.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 17 September 2018
+# Prerequisites: Need a list of csvs to walk through - URLs_for_QLD.csv
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/URLs_for_QLD.csv")
+
+# Randomise the order
+set.seed(1234)
+data_to_scrape <- data_to_scrape %>% 
+  mutate(orderByThisRandom = sample(1:nrow(data_to_scrape))) %>% 
+  arrange(orderByThisRandom) %>% 
+  select(-orderByThisRandom)
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("pdfs/", save_name)
+
+dir.create("pdfs")
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(15:30, 1)) # Space out requests by somewhere between 15 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
+# save_name <- save_name[3:length(save_name)] # main run
+# address_to_visit <- address_to_visit[3:length(address_to_visit)] # main run
+
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))

### 2018-09-18 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add Victoria to scraper

@@
   affiliation: Australian National University
-abstract: "We use a structural text model to explore what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+abstract: "We use a structural text model to categorise what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
 We then examine the effect of various events using a discrete choice model.
-We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
+We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results are dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant and persistent effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
 keywords: "text analysis, politics, Australia"
@@
 New governments often go to some trouble to be different to the governments they replace.
-For instance, Kevin Rudd's apology to Indigenous Australians was not supported by John Howard and then one of Tony Abbott's first acts was to repeal Rudd's carbon tax.
+For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal predecessor Kevin Rudd's carbon tax.
 Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
@@
 In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
-We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to impose structure such as correlation between days and changes over time, and for dimension reduction.
+We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
 We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
@@
 The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
-In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.
+In this section a brief overview of both the LDA model and the STM approach is provided.
+In a similar way to @MuellerRauh2018 we consider the outputs of the topic model as reduced dimension inputs.
+In our case they are inputs to a discrete choice model, and so we then discuss that model.
 

### 2018-09-18 scripts/to_scrape_websites/get_1860-2017_PDFs_QLD_and_NSW.R

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: This file gets Queensland and Victoria Hansard PDF files from the parliament website.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 18 September 2018
+# Prerequisites: Need a list of csvs to walk through - URLs_for_QLD_and_VIC.csv
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/URLs_for_QLD_and_VIC.csv")
+
+# Randomise the order
+set.seed(1234)
+data_to_scrape <- data_to_scrape %>% 
+  mutate(orderByThisRandom = sample(1:nrow(data_to_scrape))) %>% 
+  arrange(orderByThisRandom) %>% 
+  select(-orderByThisRandom)
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("pdfs/", save_name)
+
+dir.create("pdfs")
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(15:30, 1)) # Space out requests by somewhere between 15 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
+# save_name <- save_name[3:length(save_name)] # main run
+# address_to_visit <- address_to_visit[3:length(address_to_visit)] # main run
+
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))

### 2018-09-18 scripts/to_scrape_websites/get_URLs_of_hansard_dates-VIC.R

@@ -1,0 +1,176 @@
+#### Preamble ####
+# Purpose: I threw a wish (initial scraper) in the well (Hansard website), Don't ask me I'll never tell (because my code is embarrasing), I looked to you as it fell (threw errors), And now you're (Hansard website) in my way (why don't you just have a bulk downloader?), I'd trade my soul for a wish (bulk downloader), Pennies and dimes for a kiss (bulk downloader), I wasn't looking for this (scraping expedition), But now you're in my way (and a conference deadline is imminent).
+# The Hansard website has some tres changeable urls for the PDFs so it seems less uncertain to just to get the explicit address of the PDFs instead of using a rule. This scraper gets those URLs. This isn't pretty, but it works.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 18 September 2018
+# Prerequisites: You need the pages of the search results.
+# To do: 
+
+
+#### Set up workspace ####
+library(tidyverse)
+library(rvest)
+
+
+#### Pages of search results that list the PDFs ####
+
+
+#### Load a batch of them ####
+pages <- c(
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2938-hansard-1856-9",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2939-hansard-1860-1",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2940-hansard-1861-4",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2941-hansard-1864-5",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2864-hansard-1866-7",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2865-hansard-1868-70",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2866-hansard-1871-3",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2867-hansard-1874-6",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2868-hansard-1876-80",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2869-hansard-1880-1",
+  "https://www.parliament.vic.gov.au/hansard/26-hansard/articles/2870-hansard-1881-2",
[…]

### 2018-09-19 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update abstract

@@
     template: svm-latex-ms.tex
-title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
+title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions.
@@
   affiliation: Australian National University
-abstract: "We use a structural text model to categorise what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+abstract: "Government policy is partly driven by the topics that are discussed in parliament.
+Conversely, those same topics can indicate a government's priorities.
+But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary debate.
+In this paper, we systematically analyse how parliamentary debate has changed in response to different types of events in Australian history.
+We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
+We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
 We then examine the effect of various events using a discrete choice model.
-We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results are dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant and persistent effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
+We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects.
+Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
 keywords: "text analysis, politics, Australia"

### 2018-09-19 outputs/docs/events/svm-rmarkdown-article-example.tex
Update abstract

@@
 
-\title{Nobody expects the Spanish Inquisition: Which events drive topic change
-in Australian parliaments? \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
+\title{Nobody expects the Spanish Inquisition: The effect of events on
+Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
 Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
-suggestions. \textbf{Version as of}: September 17, 2018;
+suggestions. \textbf{Version as of}: September 18, 2018;
 \textbf{Comments welcome}:
@@
              pdfkeywords = {text analysis, politics, Australia},  
-            pdftitle={Nobody expects the Spanish Inquisition: Which events drive topic change
-in Australian parliaments?},
+            pdftitle={Nobody expects the Spanish Inquisition: The effect of events on
+Australian parliamentary discussion},
             colorlinks=true,
@@
 
-\noindent We use a structural text model to explore what was said in Australian
-state and federal parliaments from the mid-1800s through to 2017. We
-then examine the effect of various events using a discrete choice model.
-We find that: 1) changes of government are associated with topic changes
-only when there is also a change in the party in power; 2) polling
-results appear dissociated from parliamentary topics; 3) economic
-changes, such as financial crises have a significant effect; and 4)
-other events, such as an unexpected attack tend not to have a prolonged
-change.
+\noindent Government policy is partly driven by the topics that are discussed in
+parliament. Conversely, those same topics can indicate a government's
+priorities. But major events--both expected, such as an election, and
+unexpected, such as a recession or terrorist attack--can affect the
+course of parliamentary debate. In this paper, we systematically analyse
+how parliamentary debate has changed in response to different types of
+events in Australian history. We compile a dataset of what was said in
+Australian state and federal parliaments from the mid-1800s through to
+2017 based on available public records. We use a structural text model
+to reduce the dimensionality of the text and to impose prior knowledge
+such as correlation between days and changes over time. We then examine
+the effect of various events using a discrete choice model. We find
+that: 1) changes of government are associated with topic changes only
+when there is also a change of the party in power; and 2) economic
+events, such as financial crises, have significant and persistent
+effects. Our findings have implications for how we think about the
+longer-term trajectory of government policy as the media cycle becomes
+increasingly focused on short-term events.
 
@@
 governments they replace. For instance, Kevin Rudd's apology to
-Indigenous Australians was not supported by John Howard and then one of
-Tony Abbott's first acts was to repeal Rudd's carbon tax. Similarly,
-significant events such as the 9/11 attacks or the Great Recession have
-often altered the course of a government. However it is not so clear
-which events drive changes, for how long these changes persist, and what
-was given up due to the change.
+Indigenous Australians was not supported by his predecessor John Howard,
+and then one of Tony Abbott's first acts was to repeal predecessor Kevin
+Rudd's carbon tax. Similarly, significant events such as the 9/11
+attacks or the Great Recession have often altered the course of a
+government. However it is not so clear which events drive changes, for
+how long these changes persist, and what was given up due to the change.
 
@@
 state and federal parliaments from the mid-1800s through to 2017. We use
-the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016} to
-impose structure such as correlation between days and changes over time,
-and for dimension reduction. We then use a discrete choice model to
-examine changes at various types of events, including: changes in
+the Structural Topic Model (STM) of \citet{RobertsStewartAiroldi2016}
+for dimensionality reduction and to impose structure such as correlation
+between days and changes over time. We then use a discrete choice model
+to examine changes at various types of events, including: changes in
 government; changes in the political environment (as defined by polling
@@
 \citet{Blei2003latent}. In this section a brief overview of both the LDA
-model and the STM approach is provided and then the specifics of how we
-consider events in this setting are discussed.
+model and the STM approach is provided. In a similar way to
+\citet{MuellerRauh2018} we consider the outputs of the topic model as
+reduced dimension inputs. In our case they are inputs to a discrete
+choice model, and so we then discuss that model.
 

### 2018-09-21 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Minor fixes to the topic models

@@
 title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful suggestions.
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their helpful suggestions.
 **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
@@
 New governments often go to some trouble to be different to the governments they replace.
-For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal predecessor Kevin Rudd's carbon tax.
+For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax.
 Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
@@
 
-Australian Hansard records have been analysed for various purposes, but usually not at larger-scale.
+Australian Hansard records have been analysed for various purposes, but usually at a more-specific level than we do here.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
-There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**.
+There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**.
 As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.
@@
 
-The main sources for this additional supplementary information are the handbooks supplied by the various parliaments (Table 2).
-
-| Parliament  | House  | Source |
-|:------|-----:|---------:|
-| Commonwealth      | House of Representatives | Parliamentary Handbok |
-|                   | Senate                   | **[TBD]** |
-| Queensland        | Legislative Assembly     |  **[TBD]** |
-|                   | Legislative Council      | **[TBD]** |
-| New South Wales   | Legislative Assembly     | **[TBD]** |
-|                   | Legislative Council      | **[TBD]** |
-| Victoria          | Legislative Assembly     | **[TBD]** |
-|                   | Legislative Council      | **[TBD]** |
-| Tasmania          | House of Assembly        | **[TBD]** |
-|                   | Legislative Council      |  **[TBD]** |
-| South Australia   | House of Assembly        | **[TBD]** |
-|                   | Legislative Council      | **[TBD]** |
-| Western Australia | Legislative Assembly     | **[TBD]** |
-|                   | Legislative Council      | **[TBD]** |
-
-The additional information from the handbooks had many errors and it was supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]
+The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
+However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]
 
@@
 # Model
-The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
-The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
-In this section a brief overview of both the LDA model and the STM approach is provided.
-In a similar way to @MuellerRauh2018 we consider the outputs of the topic model as reduced dimension inputs.
+The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.
+Theoretically we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints.
+Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.
+
+The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
+In this section we provide a brief overview of both the LDA model and the STM.
+we consider the outputs of the topic model as reduced dimension inputs.
 In our case they are inputs to a discrete choice model, and so we then discuss that model.

### 2018-09-21 outputs/docs/events/svm-rmarkdown-article-example.tex
Minor fixes to the topic models

@@
 Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
-suggestions. \textbf{Version as of}: September 18, 2018;
+suggestions. \textbf{Version as of}: September 20, 2018;
 \textbf{Comments welcome}:
@@
 Indigenous Australians was not supported by his predecessor John Howard,
-and then one of Tony Abbott's first acts was to repeal predecessor Kevin
-Rudd's carbon tax. Similarly, significant events such as the 9/11
+and then one of Tony Abbott's first acts was to repeal his predecessor
+Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11
 attacks or the Great Recession have often altered the course of a
@@
 Australian Hansard records have been analysed for various purposes, but
-usually not at larger-scale. For instance, \citet{Rasiah2010} examined
-Hansard records for the Australian House of Representatives to examine
-whether politicians attempted to evade questions about Iraq during
-February and March 2003. And \citet{GansLeigh2012} examined Australian
-Hansard records to associate mentions by politicians of certain public
-intellectuals with neutral or positive sentiment.
+usually at a more-specific level than we do here. For instance,
+\citet{Rasiah2010} examined Hansard records for the Australian House of
+Representatives to examine whether politicians attempted to evade
+questions about Iraq during February and March 2003. And
+\citet{GansLeigh2012} examined Australian Hansard records to associate
+mentions by politicians of certain public intellectuals with neutral or
+positive sentiment.
 
@@
   and from 2006 through today from Open Australia's website.} There are
-65,000 \textbf{{[}UPDATE{]}} Hansard records available across the state
-and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}. As
-with any larger-scale data process, there are various issues with some
-of the PDFs and the known ones are detailed in the Appendix.
+65,000 \textbf{{[}UPDATE{]}} Hansard records publicly available across
+the state and federal parliaments (Table 1) \textbf{{[}UPDATE
+NUMBERING{]}}. As with any larger-scale data process, there are various
+issues with some of the PDFs and the known ones are detailed in the
+Appendix.
 
@@
 The main sources for this additional supplementary information are the
-handbooks supplied by the various parliaments (Table 2).
-
-\begin{longtable}[]{@{}lrr@{}}
-\toprule
-Parliament & House & Source\tabularnewline
-\midrule
-\endhead
-Commonwealth & House of Representatives & Parliamentary
-Handbok\tabularnewline
-& Senate & \textbf{{[}TBD{]}}\tabularnewline
-Queensland & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-New South Wales & Legislative Assembly &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-Victoria & Legislative Assembly & \textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-Tasmania & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-South Australia & House of Assembly & \textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-Western Australia & Legislative Assembly &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & \textbf{{[}TBD{]}}\tabularnewline
-\bottomrule
-\end{longtable}
-
-The additional information from the handbooks had many errors and it was
-supplemented by data from the Australian Dictionary of Biography and
-Wikipedia.\footnote{An example of the additional information is provided
-  in the Appendix. The datasets are available on request.}
+handbooks supplied by the various parliaments. However these had many
+errors and were supplemented by data from the Australian Dictionary of
+Biography and Wikipedia.\footnote{An example of the additional
+  information is provided in the Appendix. The datasets are available on
+  request.}
 
@@
 
-The main model that we use in this paper is the Structural Topic Model
+The main models that we use in this paper are the Structural Topic Model
 (STM) as implemented by the \texttt{stm} R package of
-\citet{RobertsStewartAiroldiRPackage}. The basis of this type of topic
-modelling is the Latent Dirichlet Allocation (LDA) model of
-\citet{Blei2003latent}. In this section a brief overview of both the LDA
-model and the STM approach is provided. In a similar way to
-\citet{MuellerRauh2018} we consider the outputs of the topic model as
-reduced dimension inputs. In our case they are inputs to a discrete
-choice model, and so we then discuss that model.
+\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
+implemented by the \texttt{XXXX} R package of \textbf{XYZ}.
+Theoretically we could have directly used the text as an input to the
+discrete choice model, but this is intractable due to computer memory
+and storage constraints. Instead, in a similar way to
+\citet{MuellerRauh2018}, we use the topics that the text is about as an
+input to another model, which in our case is a discrete choice model.
+
+The basis of the STM is the Latent Dirichlet Allocation (LDA) model of
+\citet{Blei2003latent}. In this section we provide a brief overview of
+both the LDA model and the STM. we consider the outputs of the topic
+model as reduced dimension inputs. In our case they are inputs to a
+discrete choice model, and so we then discuss that model.
 

### 2018-09-21 scripts/to_model_topics/the_ficl.R

@@ -13,16 +13,46 @@ tail(gammas_test)
 
 head(Canada)
 
-VAR(gammas_test, p = 2, type = "none")
+?VAR(gammas_test, p = 2, type = "none")
 
 
+
+#### 
+install.packages("betareg")
+library(betareg)
+
+test <- betareg()
+
+
+
+
+####
 
 install.packages("nnet")
 library(nnet)
-
-
-
-glm.fit = multinom(direccion~., data=datos)
+glm.fit = ?multinom(direccion~., data=datos)
 summary(glm.fit)
 #Prediction
 predict(glm.fit, newdata, "probs")
+
+
+
+
+
+
+####
+install.packages("mlogit")
+library(mlogit)
+gammas <- read_csv("/Users/rohanalexander/Desktop/test_gammas.csv")
+head(gammas)
+gamma_data <- mlogit.data(gammas, 
+                          choice = gamma,
+                          shape = long,
+                          varying = 
+                          id.var = 
+                            
+                            varying = c(2:9), 
+                          shape = "wide", choice =
+              "mode")
+
+f <- mFormula(choice ~ vcost | income + size | travel)

### 2018-09-21 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -3,7 +3,7 @@
 # Purpose: Associate a group, based on similar topics, for every statement in Hansard that is either the last two weeks before an electin or the first two weeks.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 17 September 2018
+# Last updated: 20 September 2018
 # Prerequisites: 
 # Issues:
 
@@ -74,7 +74,7 @@ rm(all_hansard_words, tidy_hansard_pieces)
 
 # Construct the TF-IDF measures on a day basis
 # By day
-# This takes about 10 minutes or so depending on the specifics - BYO book
+# This takes about 10 minutes or so depending on the specifics - BYO book and tea
 hansard_tf_idf <- tidy_hansard %>%
   count(date, word, sort = TRUE) %>% # Construct them by day
   bind_tf_idf(word, date, n) %>%
@@ -95,12 +95,57 @@ tidy_hansard <- tidy_hansard %>%
 
 hansard_dfm <- tidy_hansard %>%
   count(date, word, sort = TRUE) %>%
-  filter(n > 100) %>% # Here we remove any word that doesn't occur at least 100 times
+  filter(n > 100) %>% # Remove any word that doesn't occur at least 100 times
   cast_dfm(date, word, n)
+
+
+#### Side project to try to get meta data in START
+# https://stackoverflow.com/questions/47652890/stm-how-to-keep-metadata-when-converting-from-tm-to-stm-document-term-matrix
+library(quanteda)
+
+hansard_dfm <- tidy_hansard %>%
+  count(date, word, sort = TRUE) %>%
+  filter(n > 10) %>% 
+  group_by(date) %>% 
+  summarise(textid_field = paste(word, collapse = " ")) %>% 
+  rename(docid_field = date)
+
+# creates the corpus with document variables except for the "text"
+text_corpus3 <- corpus(hansard_dfm, text_field = "textid_field")
+
+# convert to document-feature matrix - cleaning options can be added
+# see ?tokens
+chat_DTM3 <- dfm(text_corpus3)
+
+# similar to tm::removeSparseTerms()
+DTM3 <- dfm_trim(chat_DTM3, sparsity = 0.990)
+
+# convert to STM format
+DTM_st <- convert(DTM3, to = "stm")
+
+# then it's all there
[…]

### 2018-09-22 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update text modelling

@@
 
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 3}
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
+
 tibble(
@@
   Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
-  document = c(rep("Document 1", 5), rep("Document 2", 5))
+  Document = c(rep("Document 1", 5), rep("Document 2", 5))
   ) %>%
-  ggplot(aes(Topics, Probability)) +
+  ggplot(aes(Topics, Probability, colour = Document)) +
   geom_point() +
   theme_classic() +
-  facet_wrap(vars(document), ncol = 2, scales = "free") +
-  theme(strip.background = element_blank()) + 
-  coord_flip()
+  coord_flip()  +
+  scale_colour_viridis_d()
 
@@
 
-```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 3}
+```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
 tibble(
@@
   ) %>%
-  ggplot(aes(Terms, Probability)) +
+  ggplot(aes(Terms, Probability, colour = Topics)) +
   geom_point() +
   theme_classic() +
-  facet_wrap(vars(Topics), ncol = 2, scales = "free") +
-  theme(strip.background = element_blank()) + 
-  coord_flip()
+  coord_flip() +
+  scale_colour_viridis_d()
 
@@
 These are words that are common, but that don't typically help to define topics.
-There is a general list of stop words such as: "a"; "a's"; "able"; "about"; "above"...
-An additional list of words that are commonly found in Hansard, but likely don't help define topics is added to the general list.
-These additions include words such as: "act"; "amendment"; "amount"; "australia"; "australian"; "bill"...
-A full list can be found in Appendix \@ref(hansard-stop-word).
-We also remove punctuation and capitalisation.
-The documents need to then be transformed into a document-term-matrix.
+There is a common list of stop words such as: "a"; "an"; and "and".
+However the exact list used depends on research of focus.
+In the case of Australian Hansard, these are words such as: "australia"; "australian"; and "bill".
+Punctuation and capitalisation is also typically removed.
+The documents then need to then be transformed into a document-term-matrix.
 This is essentially a table with a column of the number of times each term appears in each document.
@@
 ## Structural Topic Model
-### Overview and example
-[TBD]
+The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it includes additional information about documents.
+For instance, in general we usually have some information about the author and date of a document.
+In the case of Hansard, we know who was speaking and the date.
+STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
+That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+
+The STM is set-up to most easily include metadata to do with prevalence and content.
+Prevalence relates to the topic proportions in each document.
+For instance, we expect that topics related to the reasons for Federation such as tariffs and trade should be more prevalent in those earlier years than later.
+Similarly, we may expect topics to do with terrorism to be more prevalent in recent years than in earlier ones.
+Content relates to the words that make up each topic.
+For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
+
+The document generation process of @Blei2003latent discussed earlier is modified slightly by @RobertsStewartAiroldi2016:
+
+1. The proportion of a document dedicated to a topic is drawn "from a logistic-normal generalised linear model based on a vector of document covariates $X_d$":
+$$\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)$$
+"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." **THIS IS ALL QUOTES. NEED TO REWRITE.**
+2. Given a document-level content covariate
+
+HERE
+
+Following @BleiLafferty2009, @blei2012 and @GriffithsSteyvers2004, the process by which a document is generated is more formally considered to be:
+
+1.
+There are  For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms.
+The distribution over the terms for the $k$th topic is $\beta_k$.
+Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.
+
+STM can be implented using the stm R package of @RobertsStewartAiroldiRPackage.
 
@@
 # Summary and conclusions
+In this paper we examined
+
 What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.
@@
 We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
+
+Future work - examine how it chagned during Federation
 
@@
 Which PDFs are missing or have no content, etc.
+
+| year | I have this number in Reps | They say this number in Senate | They say this number in Reps | Difference in Reps | Comment                          | Source                                                                                           |
+|------|----------------------------|--------------------------------|------------------------------|--------------------|----------------------------------|--------------------------------------------------------------------------------------------------|
+| 1902 | 106                        | 93                             | 107                          | 1                  | Positive means I am missing some | https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear |
+| 1908 | 93                         | 84                             | 91                           | -2                 | Negative means I have too many   |                                                                                                  |
+| 1909 | 97                         | 71                             | 98                           | 1                  |                                  |                                                                                                  |
+| 1918 | 87                         | 68                             | 86                           | -1                 |                                  |                                                                                                  |
+| 1920 | 113                        | 76                             | 114                          | 1                  |                                  |                                                                                                  |
+| 1921 | 92                         | 79                             | 93                           | 1                  |                                  |                                                                                                  |
+| 1934 | 36                         | 22                             | 35                           | -1                 |                                  |                                                                                                  |
+| 1935 | 54                         | 37                             | 55                           | 1                  |                                  |                                                                                                  |
+| 1942 | 44                         | 36                             | 45                           | 1                  |                                  |                                                                                                  |
+| 1948 | 89                         | 39                             | 90                           | 1                  |                                  |                                                                                                  |
+| 1951 | 55                         | 40                             | 56                           | 1                  |                                  |                                                                                                  |
+| 1955 | 53                         | 36                             | 52                           | -1                 |                                  |                                                                                                  |
+| 1974 | 64                         | 64                             | 62                           | -2                 |                                  |                                                                                                  |
+| 1985 | 65                         | 74                             | 66                           | 1                  |                                  |                                                                                                  |
+| 1991 | 66                         | 83                             | 67                           | 1                  |                                  |                                                                                                  |
+| 1992 | 60                         | 76                             | 44                           | -16                |                                  |                                                                                                  |
+| 1993 | 47                         | 53                             | 46                           | -1                 |                                  |                                                                                                  |
+| 1994 | 69                         | 80                             | 68                           | -1                 |                                  |                                                                                                  |
+| 1995 | 71                         | 78                             | 70                           | -1                 |                                  |                                                                                                  |
+| 1997 | 79                         | 82                             | 76                           | -3                 |                                  |                                                                                                  |
+| 1998 | 56                         | 57                             | 54                           | -2                 |                                  |                                                                                                  |
+| 2000 | 71                         | 71                             | 73                           | 2                  |                                  |                                                                                                  |
+| 2002 | 68                         | 60                             | 69                           | 1                  |                                  |                                                                                                  |
+| 2003 | 74                         | 64                             | 75                           | 1                  |                                  |                                                                                                  |
+| 2004 | 58                         | 49                             | 59                           | 1                  |                                  |                                                                                                  |
+| 2012 | 63                         | 57                             | 67                           | 4                  |                                  |                                                                                                  |
 

### 2018-09-22 outputs/docs/events/svm-rmarkdown-article-example.tex
Update text modelling

@@
 Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
-Wang, Matt Jacob, Jill Sheppard and Matthew Kerby for their helpful
-suggestions. \textbf{Version as of}: September 20, 2018;
+Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their
+helpful suggestions. \textbf{Version as of}: September 22, 2018;
 \textbf{Comments welcome}:
@@
 documents is to remove `stop words'. These are words that are common,
-but that don't typically help to define topics. There is a general list
-of stop words such as: ``a''; ``a's''; ``able''; ``about'';
-``above''\ldots{} An additional list of words that are commonly found in
-Hansard, but likely don't help define topics is added to the general
-list. These additions include words such as: ``act''; ``amendment'';
-``amount''; ``australia''; ``australian''; ``bill''\ldots{} A full list
-can be found in Appendix \ref{hansard-stop-word}. We also remove
-punctuation and capitalisation. The documents need to then be
-transformed into a document-term-matrix. This is essentially a table
-with a column of the number of times each term appears in each document.
+but that don't typically help to define topics. There is a common list
+of stop words such as: ``a''; ``an''; and ``and''. However the exact
+list used depends on research of focus. In the case of Australian
+Hansard, these are words such as: ``australia''; ``australian''; and
+``bill''. Punctuation and capitalisation is also typically removed. The
+documents then need to then be transformed into a document-term-matrix.
+This is essentially a table with a column of the number of times each
+term appears in each document.
 
@@
 
-\subsubsection{Overview and example}\label{overview-and-example}
+The distinguishing aspect of the Structural Topic Model (STM) of
+\citet{RobertsStewartAiroldi2016} is that it includes additional
+information about documents. For instance, in general we usually have
+some information about the author and date of a document. In the case of
+Hansard, we know who was speaking and the date. STM allows this
+additional information to affect the construction of topics, though
+influencing either topical prevalence or topical content. That said, the
+assumption that there is some document generation process is the same as
+the LDA method, it is just that this process now includes metadata.
 
-{[}TBD{]}
+The STM is set-up to most easily include metadata to do with prevalence
+and content. Prevalence relates to the topic proportions in each
+document. For instance, we expect that topics related to the reasons for
+Federation such as tariffs and trade should be more prevalent in those
+earlier years than later. Similarly, we may expect topics to do with
+terrorism to be more prevalent in recent years than in earlier ones.
+Content relates to the words that make up each topic. For instance,
+there are changes in the use of language over the period for which we
+have data, and it would be better for these to not be responsible for
+defining different topics rather than being part of the same topic.
+
+The document generation process of \citet{Blei2003latent} discussed
+earlier is modified slightly by \citet{RobertsStewartAiroldi2016}:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  The proportion of a document dedicated to a topic is drawn ``from a
+  logistic-normal generalised linear model based on a vector of document
+  covariates \(X_d\)'':
+  \[\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)\]
+  ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
+  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.''
+  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.}
+\item
+  Given a document-level content covariate
+\end{enumerate}
+
+HERE
+
+Following \citet{BleiLafferty2009}, \citet{blei2012} and
+\citet{GriffithsSteyvers2004}, the process by which a document is
+generated is more formally considered to be:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  There are For each topic, decide the terms that the topic uses by
+  randomly drawing distributions over the terms. The distribution over
+  the terms for the \(k\)th topic is \(\beta_k\). Typically a topic
+  would be a small number of terms and so the Dirichlet distribution
+  with hyperparameter \(0<\eta<1\) is used:
+  \(\beta_k \sim \mbox{Dirichlet}(\eta)\).\footnote{The Dirichlet
+    distribution is a variation of the beta distribution that is
+    commonly used as a prior for categorical and multinomial variables.
+    If there are just two categories, then the Dirichlet and the beta
+    distributions are the same. In the special case of a symmetric
+    Dirichlet distribution, \(\eta=1\), it is equivalent to a uniform
+    distribution. If \(\eta<1\), then the distribution is sparse and
+    concentrated on a smaller number of the values, and this number
+    decreases as \(\eta\) decreases. A hyperparameter is a parameter of
+    a prior distribution.} Strictly, \(\eta\) is actually a vector of
+  hyperparameters, one for each \(K\), but in practice they all tend to
+  be the same value.
+\end{enumerate}
+
+STM can be implented using the stm R package of
+\citet{RobertsStewartAiroldiRPackage}.
 
@@
 
+In this paper we examined
+
 What could happen if we had longer terms. Eg GST needed multiple
@@
 within findings based on other methods.
+
+Future work - examine how it chagned during Federation
 
@@
 Which PDFs are missing or have no content, etc.
+
+\begin{longtable}[]{@{}lllllll@{}}
+\toprule
+\begin{minipage}[b]{0.02\columnwidth}\raggedright\strut
+year\strut
+\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
+I have this number in Reps\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
+They say this number in Senate\strut
+\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
+They say this number in Reps\strut
+\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright\strut
+Difference in Reps\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
+Comment\strut
+\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
+Source\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1902\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+106\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+93\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+107\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+Positive means I am missing some\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1908\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+93\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+84\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+91\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-2\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+Negative means I have too many\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1909\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+97\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+71\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+98\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1918\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+87\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+68\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+86\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1920\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+113\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+76\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+114\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1921\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+92\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+79\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+93\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1934\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+36\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+22\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+35\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1935\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+54\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+37\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+55\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1942\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+44\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+36\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+45\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1948\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+89\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+39\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+90\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1951\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+55\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+40\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+56\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1955\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+53\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+36\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+52\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1974\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+64\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+64\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+62\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-2\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1985\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+65\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+74\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+66\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1991\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+66\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+83\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+67\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1992\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+60\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+76\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+44\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-16\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1993\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+47\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+53\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+46\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1994\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+69\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+80\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+68\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1995\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+71\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+78\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+70\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1997\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+79\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+82\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+76\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-3\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+1998\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+56\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+57\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+54\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+-2\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+2000\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+71\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+71\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+73\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+2\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+2002\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+68\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+60\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+69\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+2003\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+74\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+64\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+75\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+2004\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+58\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+49\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+59\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+1\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
+2012\strut
+\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
+63\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+57\strut
+\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
+67\strut
+\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
+4\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
+\strut
+\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
+\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 

### 2018-09-22 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -1,25 +1,26 @@
 # !diagnostics off
 #### Preamble ####
-# Purpose: Associate a group, based on similar topics, for every statement in Hansard that is either the last two weeks before an electin or the first two weeks.
+# Purpose: Create topics, for the words used in each day of Hansard
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 20 September 2018
-# Prerequisites: 
+# Last updated: 22 September 2018
+# Prerequisites:
 # Issues:
 
 
 #### Workspace set-up ####
 # Load libraries
 # devtools::install_github("dgrtwo/drlib")
-library(drlib)
-library(furrr)
+# library(drlib)
+# library(furrr)
 library(lubridate)
-# library(modelr) # Used in the kfolds section
+# # library(modelr) # Used in the kfolds section
+library(quanteda)
 library(stm)
 library(tictoc)
 library(tidytext)
 library(tidyverse)
-library(viridis)
+# library(viridis)
 # update.packages()
 
 plan(multiprocess)
@@ -32,49 +33,62 @@ election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
 hansard_dates <- read_csv("inputs/misc/hansard_dates.csv")
 
 
+#### Create some date dummies ####
+# Create a dummy that increments when there's an election
+all_dates <-
+  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
+  mutate(electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+         electionDate = cumsum(electionDate)) %>% 
+  rename(electionCounter = electionDate)
+
+all_hansard_words <- all_hansard_words %>% 
+  left_join(all_dates, by = c("date" = "allDates"))
+
+rm(all_dates, election_dates, hansard_dates)
+
+
 #### Temp fix for dodgy words ####
 # Temp fix for getting rid of politicians names
-politicians <- read_csv("inputs/politicians/politicians_by_individuals.csv") %>% 
-  select(surname) %>% 
-  mutate(surname = str_to_lower(surname)) %>% 
-  unique() %>% 
+politicians <-
+  read_csv("inputs/politicians/politicians_by_individuals.csv") %>%
+  select(surname) %>%
+  mutate(surname = str_to_lower(surname)) %>%
+  unique() %>%
   pull()
 
[…]

### 2018-09-24 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Small improvements in paper

@@
 title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their helpful suggestions.
-**Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcome**: rohan.alexander@anu.edu.au."
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions.
+**Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
 author:
@@
 
-Australian Hansard records have been analysed for various purposes, but usually at a more-specific level than we do here.
+Australian Hansard records have been analysed for various purposes.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
-Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed that day.
+Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed.
 
@@
 The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.
-Theoretically we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints.
+In theory we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints.
 Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.
@@
 ## Latent Dirichlet Allocation
-When the text data is being modelled at the day level then each day's Hansard record needs to be classified by its topic.
-Although more- or less-fine levels of analysis are possible.
+Although more- or less-fine levels of analysis are possible, but here we are primarily interested in considering a day's topics.
+This means that each day's Hansard record needs to be classified by its topics.
 Sometimes Hansard records includes titles that make the topic clear.
@@
 The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
-A topic could be thought of as a collection of terms, and a document as a collection of topics.
+A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions.
 The topics are not specified *ex ante*; they are an outcome of the method.
-In this sense, this approach can be considered unsupervised machine learning.
+In this sense, this approach can be considered unsupervised statistical learning.
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
@@
 
-After the dataset is ready, the R package 'topicmodels' by @Grun2011 can be used to implement LDA and approximate the posterior.
-It does this using Gibbs sampling or the variational expectation-maximization algorithm.
+After the dataset is ready, the R \texttt{topicmodels} package of @Grun2011 can be used to implement LDA and approximate the posterior.
+It can do this using Gibbs sampling or the variational expectation-maximization algorithm.
 Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
@@
 ### Considering events
-[TBD]
+We consider the effect of political, economic, and other events on Australian parliamentary discussion.
+Political events are those related to a change of government or an election.
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession.
+Other events are those such as the 9/11 attacks, or the Bali Bombing.
+The list of events that we consider is detailed in Table 2 **[UPDATE TABLE NUMBERING]**.
 
@@
 Change of government.
-
-## Polling events
->*The only poll that matters is the one on election day.* John Howard.
-
-[TBD]
 

### 2018-09-24 outputs/docs/events/svm-rmarkdown-article-example.tex
Small improvements in paper

@@
 Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
-Wang, Matt Jacob, Leslie Root, Jill Sheppard and Matthew Kerby for their
-helpful suggestions. \textbf{Version as of}: September 22, 2018;
-\textbf{Comments welcome}:
+Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
+Cochrane for their helpful suggestions. \textbf{Version as of}: 23
+September 2018; \textbf{comments welcome}:
 \href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }
@@
 
-Australian Hansard records have been analysed for various purposes, but
-usually at a more-specific level than we do here. For instance,
-\citet{Rasiah2010} examined Hansard records for the Australian House of
-Representatives to examine whether politicians attempted to evade
-questions about Iraq during February and March 2003. And
+Australian Hansard records have been analysed for various purposes. For
+instance, \citet{Rasiah2010} examined Hansard records for the Australian
+House of Representatives to examine whether politicians attempted to
+evade questions about Iraq during February and March 2003. And
 \citet{GansLeigh2012} examined Australian Hansard records to associate
@@
 interrupted than male MPs, but do not usually contribute much to
-defining the topics being discussed that day.
+defining the topics being discussed.
 
@@
 \citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
-implemented by the \texttt{XXXX} R package of \textbf{XYZ}.
-Theoretically we could have directly used the text as an input to the
-discrete choice model, but this is intractable due to computer memory
-and storage constraints. Instead, in a similar way to
-\citet{MuellerRauh2018}, we use the topics that the text is about as an
-input to another model, which in our case is a discrete choice model.
+implemented by the \texttt{XXXX} R package of \textbf{XYZ}. In theory we
+could have directly used the text as an input to the discrete choice
+model, but this is intractable due to computer memory and storage
+constraints. Instead, in a similar way to \citet{MuellerRauh2018}, we
+use the topics that the text is about as an input to another model,
+which in our case is a discrete choice model.
 
@@
 
-When the text data is being modelled at the day level then each day's
-Hansard record needs to be classified by its topic. Although more- or
-less-fine levels of analysis are possible. Sometimes Hansard records
-includes titles that make the topic clear. But not every statement has a
-title and the titles do not always define topics in a well-defined and
-consistent way, especially over longer time periods. One way to get
-consistent estimates of the topics discussed in Hansard is to use the
-LDA method of \citet{Blei2003latent}, for instance as implemented by the
-R package `topicmodels' by \citet{Grun2011}.
+Although more- or less-fine levels of analysis are possible, but here we
+are primarily interested in considering a day's topics. This means that
+each day's Hansard record needs to be classified by its topics.
+Sometimes Hansard records includes titles that make the topic clear. But
+not every statement has a title and the titles do not always define
+topics in a well-defined and consistent way, especially over longer time
+periods. One way to get consistent estimates of the topics discussed in
+Hansard is to use the LDA method of \citet{Blei2003latent}, for instance
+as implemented by the R package `topicmodels' by \citet{Grun2011}.
 
@@
 `terms', that are appropriate to those topics. A topic could be thought
-of as a collection of terms, and a document as a collection of topics.
-The topics are not specified \emph{ex ante}; they are an outcome of the
+of as a collection of terms, and a document as a collection of topics,
+where these collections are defined by probability distributions. The
+topics are not specified \emph{ex ante}; they are an outcome of the
 method. In this sense, this approach can be considered unsupervised
-machine learning. Terms are not necessarily unique to a particular
+statistical learning. Terms are not necessarily unique to a particular
 topic, and a document could be about more than one topic. This provides
@@
 
-After the dataset is ready, the R package `topicmodels' by
+After the dataset is ready, the R \texttt{topicmodels} package of
 \citet{Grun2011} can be used to implement LDA and approximate the
-posterior. It does this using Gibbs sampling or the variational
+posterior. It can do this using Gibbs sampling or the variational
 expectation-maximization algorithm. Following

### 2018-09-24 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Minor updates to writeup

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(here)
+library(kableExtra)
+library(knitr)
 library(tidyverse)
+
+elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
+governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
+keyEconomicDates <- read_csv(here::here("inputs/misc/key_dates-economic.csv"), col_types = cols())
+keyOtherDates <- read_csv(here::here("inputs/misc/key_dates-other.csv"), col_types = cols())
+
 ```
@@
 
-Australian Hansard records have been analysed for various purposes.
+Australian Hansard records have been analysed for various purposes, usually at smaller-scale.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 
-The document generation process of @Blei2003latent discussed earlier is modified slightly by @RobertsStewartAiroldi2016:
+Again, the assumed process that generates the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is only slightly modified by @RobertsStewartAiroldi2016 for the STM:
 
 1. The proportion of a document dedicated to a topic is drawn "from a logistic-normal generalised linear model based on a vector of document covariates $X_d$":
-$$\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)$$
+$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)$$
 "where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." **THIS IS ALL QUOTES. NEED TO REWRITE.**
-2. Given a document-level content covariate
+2.
+**THIS IS ALL QUOTES.
+NEED TO REWRITE.** Given a document-level content covariate $y_d$, form the document-specific distribution over words representing each topic ($k$) using the baseline word distribution $m$, the topic specific deviation, $\kappa_k^{(t)}$, the covariate group deviation, $\kappa_{y_d}^{(c)}$, and the interaction between the two, $\kappa_{y_{d}k}^{(i)}$:
+$$\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$
 
@@
 
+```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/all_topics_usable.png"))
+```
+
+<!-- ![alt text](here::here(/outputs/figures/all_topics_usable.png)) -->
+
 Note that each of the states and the Commonwealth are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.
@@
 We consider the effect of political, economic, and other events on Australian parliamentary discussion.
-Political events are those related to a change of government or an election.
-Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession.
-Other events are those such as the 9/11 attacks, or the Bali Bombing.
-The list of events that we consider is detailed in Table 2 **[UPDATE TABLE NUMBERING]**.
+Political events are those related to a change of government or an election (Tables \@ref(tab:governments) and \@ref(tab:elections)).
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession (Table \@ref(tab:economicevents)).
+Other events are those such as the 9/11 attacks, or the Bali Bombing (Table \@ref(tab:otherevents)).
+The list of events that we consider is detailed in .
+
+```{r governments, echo = FALSE, results = 'asis'}
+
+governments %>% 
+  kable(booktabs = T, caption = "Change in governments") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r elections, echo = FALSE, results = 'asis'}
+
+elections %>% 
+  filter(election == 1) %>% 
+  select(year, electionDate, electionWinner) %>% 
+  kable("latex", booktabs = T, caption = "Elections") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r economicevents, echo = FALSE, results = 'asis'}
+
+keyEconomicDates %>% 
+  kable(booktabs = T, caption = "Key economic events") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r otherevents, echo = FALSE, results = 'asis'}
+
+keyOtherDates %>% 
+  kable(booktabs = T, caption = "Key other events") %>%
+  kable_styling(font_size = 8)
+
+```
 

### 2018-09-24 outputs/docs/events/svm-rmarkdown-article-example.tex
Minor updates to writeup

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 23
+Cochrane for their helpful suggestions. \textbf{Version as of}: 24
 September 2018; \textbf{comments welcome}:
@@
 
-Australian Hansard records have been analysed for various purposes. For
-instance, \citet{Rasiah2010} examined Hansard records for the Australian
-House of Representatives to examine whether politicians attempted to
-evade questions about Iraq during February and March 2003. And
-\citet{GansLeigh2012} examined Australian Hansard records to associate
-mentions by politicians of certain public intellectuals with neutral or
-positive sentiment.
+Australian Hansard records have been analysed for various purposes,
+usually at smaller-scale. For instance, \citet{Rasiah2010} examined
+Hansard records for the Australian House of Representatives to examine
+whether politicians attempted to evade questions about Iraq during
+February and March 2003. And \citet{GansLeigh2012} examined Australian
+Hansard records to associate mentions by politicians of certain public
+intellectuals with neutral or positive sentiment.
 
@@
   covariates \(X_d\)'':
-  \[\theta_d|X_d\gamma\sigma \sim logisticnormal(\mu = X_d\gamma, \sigma)\]
+  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)\]
   ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
@@
 \item
-  Given a document-level content covariate
+  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.} Given a document-level
+  content covariate \(y_d\), form the document-specific distribution
+  over words representing each topic (\(k\)) using the baseline word
+  distribution \(m\), the topic specific deviation, \(\kappa_k^{(t)}\),
+  the covariate group deviation, \(\kappa_{y_d}^{(c)}\), and the
+  interaction between the two, \(\kappa_{y_{d}k}^{(i)}\):
+  \[\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
 \end{enumerate}
@@
 
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/all_topics_usable} \caption{A caption}\label{fig:pressure}
+\end{figure}
+
 Note that each of the states and the Commonwealth are treated
@@
 
-{[}TBD{]}
+We consider the effect of political, economic, and other events on
+Australian parliamentary discussion. Political events are those related
+to a change of government or an election (Tables \ref{tab:governments}
+and \ref{tab:elections}). Economic events are defined by substantial
+changes in various economic measures, such as the onset of the Great
+Depression or the Great Recession (Table \ref{tab:economicevents}).
+Other events are those such as the 9/11 attacks, or the Bali Bombing
+(Table \ref{tab:otherevents}). The list of events that we consider is
+detailed in .
+
+\begin{table}
+
+\caption{\label{tab:governments}Change in governments}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllll}
+\toprule
+government & primeMinister & party & start & end & diedInOffice\\
+\midrule
+Barton & Edmund Barton & Protectionist & 1901-01-01 & 1903-09-24 & No\\
+Deakin 1 & Alfred Deakin & Protectionist & 1903-09-24 & 1904-04-27 & No\\
+Watson & Chris Watson & Labour & 1904-04-27 & 1904-08-18 & No\\
+Reid & George Reid & Free Trade & 1904-08-18 & 1905-07-05 & No\\
+Deakin 2 & Alfred Deakin & Protectionist & 1905-07-05 & 1908-11-13 & No\\
+\addlinespace
+Fisher 1 & Andrew Fisher & Labour & 1908-11-13 & 1909-06-02 & No\\
+Deakin 3 & Alfred Deakin & Commonwealth Liberal & 1909-06-02 & 1910-04-29 & No\\
+Fisher 2 & Andrew Fisher & Labor & 1910-04-29 & 1913-06-24 & No\\
+Cook & Joseph Cook & Commonwealth Liberal & 1913-06-24 & 1914-09-17 & No\\
+Fisher 3 & Andrew Fisher & Labor & 1914-09-17 & 1915-10-27 & No\\
+\addlinespace
+Hughes & Billy Hughes & Labor, National Labor and Nationalist & 1915-10-27 & 1923-02-09 & No\\
+Bruce & Stanley Bruce & Nationalist (Coalition) & 1923-02-09 & 1929-10-22 & No\\
+Scullin & James Scullin & Labor & 1929-10-22 & 1932-01-06 & No\\
+Lyons & Joseph Lyons & United Australia (Coalition) & 1932-01-06 & 1939-04-07 & Yes\\
+Page & Earle Page & Country (Coalition) & 1939-04-07 & 1939-04-26 & No\\
+\addlinespace
+Menzies 1 & Robert Menzies & United Australia (Coalition) & 1939-04-26 & 1941-08-28 & No\\
+Fadden & Arthur Fadden & Country (Coalition) & 1941-08-28 & 1941-10-07 & No\\
+Curtin & John Curtin & Labor & 1941-10-07 & 1945-07-05 & Yes\\
+Forde & Frank Forde & Labor & 1945-07-06 & 1945-07-13 & No\\
+Chifley & Ben Chifley & Labor & 1945-07-13 & 1949-12-19 & No\\
+\addlinespace
+Menzies 2 & Robert Menzies & Liberal (Coalition) & 1949-12-19 & 1966-01-26 & No\\
+Holt & Harold Holt & Liberal (Coalition) & 1966-01-26 & 1967-12-19 & Yes\\
+McEwen & John McEwen & Country (Coalition) & 1967-12-19 & 1968-01-10 & No\\
+Gorton & John Gorton & Liberal (Coalition) & 1968-01-10 & 1971-03-10 & No\\
+McMahon & William McMahon & Liberal (Coalition) & 1971-03-10 & 1972-12-05 & No\\
+\addlinespace
+Whitlam & Gough Whitlam & Labor & 1972-12-05 & 1975-11-11 & No\\
+Fraser & Malcolm Fraser & Liberal (Coalition) & 1975-11-11 & 1983-03-11 & No\\
+Hawke & Bob Hawke & Labor & 1983-03-11 & 1991-12-20 & No\\
+Keating & Paul Keating & Labor & 1991-12-20 & 1996-03-11 & No\\
+Howard & John Howard & Liberal (Coalition) & 1996-03-11 & 2007-12-03 & No\\
+\addlinespace
+Rudd 1 & Kevin Rudd & Labor & 2007-12-03 & 2010-06-24 & No\\
+Gillard & Julia Gillard & Labor & 2010-06-24 & 2013-06-27 & No\\
+Rudd 2 & Kevin Rudd & Labor & 2013-06-27 & 2013-09-18 & No\\
+Abbott & Tony Abbott & Liberal (Coalition) & 2013-09-18 & 2015-09-15 & No\\
+Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
+Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & - & -\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:elections}Elections}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{rll}
+\toprule
+year & electionDate & electionWinner\\
+\midrule
+1901 & 1901-03-29 & Non-labor\\
+1903 & 1903-12-16 & Non-labor\\
+1906 & 1906-12-12 & Non-labor\\
+1910 & 1910-04-13 & Labor\\
+1913 & 1913-05-31 & Non-labor\\
+\addlinespace
+1914 & 1914-09-05 & Labor\\
+1917 & 1917-05-05 & Non-labor\\
+1919 & 1919-12-13 & Non-labor\\
+1922 & 1922-12-16 & Non-labor\\
+1925 & 1925-11-14 & Non-labor\\
+\addlinespace
+1928 & 1928-11-17 & Non-labor\\
+1929 & 1929-10-12 & Labor\\
+1931 & 1931-12-19 & Non-labor\\
+1934 & 1934-09-15 & Non-labor\\
+1937 & 1937-10-23 & Non-labor\\
+\addlinespace
+1940 & 1940-09-21 & Non-labor\\
+1943 & 1943-08-21 & Labor\\
+1946 & 1946-09-28 & Labor\\
+1949 & 1949-12-10 & Non-labor\\
+1951 & 1951-08-28 & Non-labor\\
+\addlinespace
+1954 & 1954-05-29 & Non-labor\\
+1955 & 1955-12-10 & Non-labor\\
+1958 & 1958-11-22 & Non-labor\\
+1961 & 1961-12-09 & Non-labor\\
+1963 & 1963-11-30 & Non-labor\\
+\addlinespace
+1966 & 1966-11-26 & Non-labor\\
+1969 & 1969-10-25 & Non-labor\\
+1972 & 1972-12-02 & Labor\\
+1974 & 1974-05-18 & Labor\\
+1975 & 1975-12-13 & Non-labor\\
+\addlinespace
+1977 & 1977-12-10 & Non-labor\\
+1980 & 1980-10-18 & Non-labor\\
+1983 & 1983-03-05 & Labor\\
+1984 & 1984-12-01 & Labor\\
+1987 & 1987-07-11 & Labor\\
+\addlinespace
+1990 & 1990-03-24 & Labor\\
+1993 & 1993-03-13 & Labor\\
+1996 & 1996-03-02 & Non-labor\\
+1998 & 1998-10-03 & Non-labor\\
+2001 & 2001-11-10 & Non-labor\\
+\addlinespace
+2004 & 2004-10-09 & Non-labor\\
+2007 & 2007-11-24 & Labor\\
+2010 & 2010-08-21 & Labor\\
+2013 & 2013-09-07 & Non-labor\\
+2016 & 2016-07-02 & Non-labor\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:economicevents}Key economic events}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+theDate & event\\
+\midrule
+1907-11-08 & Harvester case\\
+1910-09-01 & Australian pound introduced (CHECK DATE)\\
+1929-10-29 & Black Tuesday Stock Market Crash\\
+1931-06-01 & Premiers' Plan (CHECK DATE)\\
+1966-02-14 & Decimalisation\\
+\addlinespace
+1973-01-01 & Fred Gruen 25\% tariff cut (DATE IS WRONG)\\
+1983-12-12 & Australian dollar is floated\\
+1984-02-01 & Medicare establised\\
+1987-10-19 & Black Monday Stock Market Crash\\
+1991-02-10 & State Bank of South Australia collapse\\
+\addlinespace
+1990-08-27 & State Bank of Victoria collapse (CHECK DATE)\\
+2000-07-01 & GST introduced\\
+2008-09-15 & Lehman Brothers bankruptcy\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:otherevents}Key other events}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+theDate & event\\
+\midrule
+1899-10-11 & Second Boer War starts\\
+1901-01-01 & Australia federated\\
+1902-05-31 & Second Boer War ends\\
+1914-07-28 & World War I starts\\
+1918-11-11 & World War I ends\\
+\addlinespace
+1932-05-13 & Jack Lang dismissed as NSW Premier\\
+1939-09-01 & World War II starts\\
+1945-09-02 & World War II ends\\
+1949-10-17 & Snowy Hydro construction begins\\
+1956-11-22 & Melbourne Olympics\\
+\addlinespace
+1962-08-03 & Australia enters Vietnam War\\
+1972-12-02 & Australia exits Vietnam War\\
+1973-10-20 & White Australian Policy ended\\
+1975-11-11 & The Dismissal\\
+1992-06-03 & Mabo\\
+\addlinespace
+1996-12-23 & Wik decision\\
+1996-03-28 & Port Arthur massacre\\
+1999-09-20 & INTERFET deployment begins\\
+2000-02-28 & INTERFET deployment ends\\
+2000-09-15 & Sydney Olympics\\
+\addlinespace
+2001-09-11 & 9/11 attack\\
+2002-10-12 & Bali bombings\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 Change of government.
-
-\subsection{Polling events}\label{polling-events}
-
-\begin{quote}
-\emph{The only poll that matters is the one on election day.} John
-Howard.
-\end{quote}
-
-{[}TBD{]}
 

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper and add voting data

@@
   affiliation: Australian National University
-abstract: "Government policy is partly driven by the topics that are discussed in parliament.
-Conversely, those same topics can indicate a government's priorities.
-But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary debate.
-In this paper, we systematically analyse how parliamentary debate has changed in response to different types of events in Australian history.
+abstract: "Government policy is partly driven by parliamentary discussion.
+Conversely, that same discussion can indicate a government's priorities.
+But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
+In this paper, we systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
 We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
@@
 
-Australian Hansard records have been analysed for various purposes, usually at smaller-scale.
+Australian Hansard records have been analysed for various purposes.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
+An example of what a page of Hansard looks like is included in Appendix **[ADD NUMBERING]**.
 There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**.
-As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in the Appendix.
+As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in Appendix **[ADD NUMBERING]**.
 
-[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
-Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through today from Open Australia’s website.
+[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
+The records can also be downloaded from the Australian Hansard website.
 
@@
 
-[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in the Appendix. The full set of scripts are available on request.
-
-**[ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT RECORD?]**
+[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in Appendix **[ADD NUMBERING]**. The full set of scripts are available on request.
 
@@
 In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
+**NEED TO bundle_ngrams i.e.
+olive oil should be olive_oil, not considered separately.**
 
@@
 
-[^seeMyAdditionalData]: An example of the additional information is provided in the Appendix. The datasets are available on request.
+[^seeMyAdditionalData]: An example of the additional information is provided in Appendix **[ADD NUMBERING]**. The datasets are available on request.
 
@@
 The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.
-In theory we could have directly used the text as an input to the discrete choice model, but this is intractable due to computer memory and storage constraints.
+In theory we could have directly used the text as an input to the discrete choice model, but this quickly becomes intractable due to computer memory and storage constraints.
 Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.
+In Appendix **[ADD NUMBERING]**, we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
 
@@
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.
+One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R \texttt{topicmodels} package of @Grun2011.
 
@@
 The topics are not specified *ex ante*; they are an outcome of the method.
-In this sense, this approach can be considered unsupervised statistical learning.
+In this sense, this approach can be considered unsupervised machine learning.
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
@@
 ## Structural Topic Model
-The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it includes additional information about documents.
-For instance, in general we usually have some information about the author and date of a document.
-In the case of Hansard, we know who was speaking and the date.
+The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
+For instance, we generally have some information about the author and the date that a document was created.
+In the case of Hansard, we know who was speaking and the date they spoke.
 STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
@@
 Prevalence relates to the topic proportions in each document.
-For instance, we expect that topics related to the reasons for Federation such as tariffs and trade should be more prevalent in those earlier years than later.
-Similarly, we may expect topics to do with terrorism to be more prevalent in recent years than in earlier ones.
+For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
+Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
 Content relates to the words that make up each topic.
@@
 Again, the assumed process that generates the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is only slightly modified by @RobertsStewartAiroldi2016 for the STM:
+The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM:
 
-1. The proportion of a document dedicated to a topic is drawn "from a logistic-normal generalised linear model based on a vector of document covariates $X_d$":
-$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)$$
-"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." **THIS IS ALL QUOTES. NEED TO REWRITE.**
+**THIS NEEDS WORK START**
+
+1.
+The proportion of a document dedicated to a topic, stored in the vector $\theta_d$, is drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a document covariates, $X_d$, following @RobertsStewartTingley2018:
+$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." This is in contrast to the Dirichlet distribution that characterises LDA.
 2.
@@
 NEED TO REWRITE.** Given a document-level content covariate $y_d$, form the document-specific distribution over words representing each topic ($k$) using the baseline word distribution $m$, the topic specific deviation, $\kappa_k^{(t)}$, the covariate group deviation, $\kappa_{y_d}^{(c)}$, and the interaction between the two, $\kappa_{y_{d}k}^{(i)}$:
-$$\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$
+$$\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$
 
-HERE
+**THIS NEEDS WORK END**
 
-Following @BleiLafferty2009, @blei2012 and @GriffithsSteyvers2004, the process by which a document is generated is more formally considered to be:
+We implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+We consider both topic prevalence and content to be functions of time.
+The choice of how many topics to use in the model is a situation-specific compromise.
+We use standard diagnostic techniques to decide on 80 topics, and more detail on this process is available in Appendix **[ADD NUMBERING]**.
 
-1.
-There are  For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms.
-The distribution over the terms for the $k$th topic is $\beta_k$.
-Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.
-
-STM can be implented using the stm R package of @RobertsStewartAiroldiRPackage.
+One way to summarise the results of the topic model is to **????**
 
@@
 
-<!-- ![alt text](here::here(/outputs/figures/all_topics_usable.png)) -->
-
 Note that each of the states and the Commonwealth are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.
@@
 We consider the effect of political, economic, and other events on Australian parliamentary discussion.
-Political events are those related to a change of government or an election (Tables \@ref(tab:governments) and \@ref(tab:elections)).
-Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession (Table \@ref(tab:economicevents)).
-Other events are those such as the 9/11 attacks, or the Bali Bombing (Table \@ref(tab:otherevents)).
-The list of events that we consider is detailed in .
+Political events are those related to a change of government or an election.
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession.
+Other events are those such as the 9/11 attacks, or the Bali Bombing.
+The full list of events that we consider is detailed in Appendix **[ADD NUMBERING]**.
+We consider events in two ways.
+The first is in the change in the word usage before and after events and the second is in changes in the topics.
 
-```{r governments, echo = FALSE, results = 'asis'}
+Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
+It will be higher for words that are rarely used across all documents, but commonly used in a document.
+For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
+However, 'aboriginal' is less common across, and so if it was especially prevelant in a particular document that may distinguish that document.
 
-governments %>% 
-  kable(booktabs = T, caption = "Change in governments") %>%
-  kable_styling(font_size = 8)
+When we consider events using tf-idf, we gather terms from more than one day.
+We define groups of days that are roughly analogous to sitting periods.
+If there is more than a week between a day then we define a new group, otherwise the day is in the existing group.
+We use various measures **(Text2vec R package has some?
+or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
 
-```
-
-```{r elections, echo = FALSE, results = 'asis'}
-
-elections %>% 
-  filter(election == 1) %>% 
-  select(year, electionDate, electionWinner) %>% 
-  kable("latex", booktabs = T, caption = "Elections") %>%
-  kable_styling(font_size = 8)
-
-```
-
-```{r economicevents, echo = FALSE, results = 'asis'}
-
-keyEconomicDates %>% 
-  kable(booktabs = T, caption = "Key economic events") %>%
-  kable_styling(font_size = 8)
-
-```
-
-```{r otherevents, echo = FALSE, results = 'asis'}
-
-keyOtherDates %>% 
-  kable(booktabs = T, caption = "Key other events") %>%
-  kable_styling(font_size = 8)
-
-```
+Changes in topics also help define how ...
 
@@
 
-## External events
+## Other events
 >*Events, dear boy, events.* Attributed to Harold Macmillan.
@@
 # Appendix
+
+## Example page
+
+```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
+```
 
@@
 
+## Events
+
+```{r governments, echo = FALSE, results = 'asis'}
+
+governments %>% 
+  kable(booktabs = T, caption = "Change in governments") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r elections, echo = FALSE, results = 'asis'}
+
+elections %>% 
+  filter(election == 1) %>% 
+  select(year, electionDate, electionWinner) %>% 
+  kable("latex", booktabs = T, caption = "Elections") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r economicevents, echo = FALSE, results = 'asis'}
+
+keyEconomicDates %>% 
+  kable(booktabs = T, caption = "Key economic events") %>%
+  kable_styling(font_size = 8)
+
+```
+
+```{r otherevents, echo = FALSE, results = 'asis'}
+
+keyOtherDates %>% 
+  kable(booktabs = T, caption = "Key other events") %>%
+  kable_styling(font_size = 8)
+
+```
+
+## Choosing number of topics
+
+Add the graphs and procedures.
+
+## word2vec alternative
+An alternative approach that follows @Taddy2015.
+
 \newpage

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper and add voting data

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 24
+Cochrane for their helpful suggestions. \textbf{Version as of}: 25
 September 2018; \textbf{comments welcome}:
@@
 
-\noindent Government policy is partly driven by the topics that are discussed in
-parliament. Conversely, those same topics can indicate a government's
-priorities. But major events--both expected, such as an election, and
-unexpected, such as a recession or terrorist attack--can affect the
-course of parliamentary debate. In this paper, we systematically analyse
-how parliamentary debate has changed in response to different types of
+\noindent Government policy is partly driven by parliamentary discussion.
+Conversely, that same discussion can indicate a government's priorities.
+But major events--both expected, such as an election, and unexpected,
+such as a recession or terrorist attack--can affect the course of
+parliamentary discussion. In this paper, we systematically analyse how
+parliamentary discussion changes in response to different types of
 events in Australian history. We compile a dataset of what was said in
@@
 
-Australian Hansard records have been analysed for various purposes,
-usually at smaller-scale. For instance, \citet{Rasiah2010} examined
-Hansard records for the Australian House of Representatives to examine
-whether politicians attempted to evade questions about Iraq during
-February and March 2003. And \citet{GansLeigh2012} examined Australian
-Hansard records to associate mentions by politicians of certain public
-intellectuals with neutral or positive sentiment.
+Australian Hansard records have been analysed for various purposes. For
+instance, \citet{Rasiah2010} examined Hansard records for the Australian
+House of Representatives to examine whether politicians attempted to
+evade questions about Iraq during February and March 2003. And
+\citet{GansLeigh2012} examined Australian Hansard records to associate
+mentions by politicians of certain public intellectuals with neutral or
+positive sentiment.
 
@@
 available online as PDFs and these are considered the official release.
-There is a more limited set of XML records available in some
-cases.\footnote{Tim Sherratt makes these XML records available as a
-  single download and also presents them in a website
-  (\url{http://historichansard.net/}) that can be used to explore
-  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
-  records from 1998 to 2014 are available from Andrew Turpin's website,
-  and from 2006 through today from Open Australia's website.} There are
-65,000 \textbf{{[}UPDATE{]}} Hansard records publicly available across
-the state and federal parliaments (Table 1) \textbf{{[}UPDATE
-NUMBERING{]}}. As with any larger-scale data process, there are various
-issues with some of the PDFs and the known ones are detailed in the
-Appendix.
+An example of what a page of Hansard looks like is included in Appendix
+\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
+available in some cases.\footnote{Tim Sherratt makes these XML records
+  available as a single download and also presents them in a website
+  (historichansard.net/) that can be used to explore Commonwealth
+  Hansard records from 1901 to 1980. Commonwealth XML records from 1998
+  to 2014 are available from Andrew Turpin's website, and from 2006
+  through to today from Open Australia's website. The records can also
+  be downloaded from the Australian Hansard website.} There are 65,000
+\textbf{{[}UPDATE{]}} Hansard records publicly available across the
+state and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}.
+As with any larger-scale data process, there are various issues with
+some of the PDFs and the known ones are detailed in Appendix
+\textbf{{[}ADD NUMBERING{]}}.
 
@@
 daily text records.\footnote{An example of the workflow and some
-  reduced-detail scripts are provided in the Appendix. The full set of
-  scripts are available on request.} These scripts are primarily based
-on: the \texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
-\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
-package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
+  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
+  NUMBERING{]}}. The full set of scripts are available on request.}
+These scripts are primarily based on: the \texttt{PDFtools} package of
+\citet{Ooms2018pdftools}; the \texttt{tidyverse} package of
+\citet{Wickham2017}; the \texttt{tm} package of
+\citet{FeinererHornik2018}; the \texttt{lubridate} package of
 \citet{GrolemundWickham2011}; and the \texttt{stringi} package of
@@
 \citet{Ooms2017} is also used to help find spelling issues.
-
-\textbf{{[}ADD PICTURE OF HANSARD RECORD AND THE SUBSEQUENT TEXT
-RECORD?{]}}
 
@@
 the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
+\textbf{NEED TO bundle\_ngrams i.e.~olive oil should be olive\_oil, not
+considered separately.}
 
@@
 Biography and Wikipedia.\footnote{An example of the additional
-  information is provided in the Appendix. The datasets are available on
-  request.}
+  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The
+  datasets are available on request.}
 
@@
 could have directly used the text as an input to the discrete choice
-model, but this is intractable due to computer memory and storage
-constraints. Instead, in a similar way to \citet{MuellerRauh2018}, we
-use the topics that the text is about as an input to another model,
-which in our case is a discrete choice model.
+model, but this quickly becomes intractable due to computer memory and
+storage constraints. Instead, in a similar way to
+\citet{MuellerRauh2018}, we use the topics that the text is about as an
+input to another model, which in our case is a discrete choice model. In
+Appendix \textbf{{[}ADD NUMBERING{]}}, we include an alternative
+approach that follows \citet{Taddy2015} by using word2vec, which more
+closely uses words, rather than topics, as an input.
 
@@
 Hansard is to use the LDA method of \citet{Blei2003latent}, for instance
-as implemented by the R package `topicmodels' by \citet{Grun2011}.
+as implemented by the R \texttt{topicmodels} package of
+\citet{Grun2011}.
 
@@
 method. In this sense, this approach can be considered unsupervised
-statistical learning. Terms are not necessarily unique to a particular
+machine learning. Terms are not necessarily unique to a particular
 topic, and a document could be about more than one topic. This provides
@@
 The distinguishing aspect of the Structural Topic Model (STM) of
-\citet{RobertsStewartAiroldi2016} is that it includes additional
-information about documents. For instance, in general we usually have
-some information about the author and date of a document. In the case of
-Hansard, we know who was speaking and the date. STM allows this
-additional information to affect the construction of topics, though
-influencing either topical prevalence or topical content. That said, the
-assumption that there is some document generation process is the same as
-the LDA method, it is just that this process now includes metadata.
+\citet{RobertsStewartAiroldi2016} is that it considers more than just a
+document's content when constructing topics. For instance, we generally
+have some information about the author and the date that a document was
+created. In the case of Hansard, we know who was speaking and the date
+they spoke. STM allows this additional information to affect the
+construction of topics, though influencing either topical prevalence or
+topical content. That said, the assumption that there is some document
+generation process is the same as the LDA method, it is just that this
+process now includes metadata.
 
@@
 document. For instance, we expect that topics related to the reasons for
-Federation such as tariffs and trade should be more prevalent in those
+Federation, such as tariffs and trade, should be more prevalent in those
 earlier years than later. Similarly, we may expect topics to do with
-terrorism to be more prevalent in recent years than in earlier ones.
-Content relates to the words that make up each topic. For instance,
-there are changes in the use of language over the period for which we
-have data, and it would be better for these to not be responsible for
-defining different topics rather than being part of the same topic.
-
-The document generation process of \citet{Blei2003latent} discussed
-earlier is modified slightly by \citet{RobertsStewartAiroldi2016}:
+terrorism to be more prevalent in recent years. Content relates to the
+words that make up each topic. For instance, there are changes in the
+use of language over the period for which we have data, and it would be
+better for these to not be responsible for defining different topics
+rather than being part of the same topic.
+
+Again, the assumed process that generates the documents is the key
+aspect as this will be reversed to estimate the topics. The document
+generation process of \citet{Blei2003latent} discussed earlier, is
+slightly modified by \citet{RobertsStewartAiroldi2016} for the STM:
+
+\textbf{THIS NEEDS WORK START}
 
@@
 \item
-  The proportion of a document dedicated to a topic is drawn ``from a
-  logistic-normal generalised linear model based on a vector of document
-  covariates \(X_d\)'':
-  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \sigma)\]
+  The proportion of a document dedicated to a topic, stored in the
+  vector \(\theta_d\), is drawn from a logistic-normal distribution,
+  parameterised such that the mean of that distribution, \(\mu\), is
+  affected by a document covariates, \(X_d\), following
+  \citet{RobertsStewartTingley2018}:
+  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)\]
   ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
-  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.''
-  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.}
+  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.'' This
+  is in contrast to the Dirichlet distribution that characterises LDA.
 \item
@@
   interaction between the two, \(\kappa_{y_{d}k}^{(i)}\):
-  \[\beta_{d,k}\sim exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
+  \[\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
 \end{enumerate}
 
-HERE
-
-Following \citet{BleiLafferty2009}, \citet{blei2012} and
-\citet{GriffithsSteyvers2004}, the process by which a document is
-generated is more formally considered to be:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  There are For each topic, decide the terms that the topic uses by
-  randomly drawing distributions over the terms. The distribution over
-  the terms for the \(k\)th topic is \(\beta_k\). Typically a topic
-  would be a small number of terms and so the Dirichlet distribution
-  with hyperparameter \(0<\eta<1\) is used:
-  \(\beta_k \sim \mbox{Dirichlet}(\eta)\).\footnote{The Dirichlet
-    distribution is a variation of the beta distribution that is
-    commonly used as a prior for categorical and multinomial variables.
-    If there are just two categories, then the Dirichlet and the beta
-    distributions are the same. In the special case of a symmetric
-    Dirichlet distribution, \(\eta=1\), it is equivalent to a uniform
-    distribution. If \(\eta<1\), then the distribution is sparse and
-    concentrated on a smaller number of the values, and this number
-    decreases as \(\eta\) decreases. A hyperparameter is a parameter of
-    a prior distribution.} Strictly, \(\eta\) is actually a vector of
-  hyperparameters, one for each \(K\), but in practice they all tend to
-  be the same value.
-\end{enumerate}
-
-STM can be implented using the stm R package of
-\citet{RobertsStewartAiroldiRPackage}.
+\textbf{THIS NEEDS WORK END}
+
+We implement the STM on the daily-level parliamentary text data
+described earlier using the \texttt{stm} R package of
+\citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
+and content to be functions of time. The choice of how many topics to
+use in the model is a situation-specific compromise. We use standard
+diagnostic techniques to decide on 80 topics, and more detail on this
+process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.
+
+One way to summarise the results of the topic model is to \textbf{????}
 
@@
 Australian parliamentary discussion. Political events are those related
-to a change of government or an election (Tables \ref{tab:governments}
-and \ref{tab:elections}). Economic events are defined by substantial
-changes in various economic measures, such as the onset of the Great
-Depression or the Great Recession (Table \ref{tab:economicevents}).
-Other events are those such as the 9/11 attacks, or the Bali Bombing
-(Table \ref{tab:otherevents}). The list of events that we consider is
-detailed in .
-
-\begin{table}
-
-\caption{\label{tab:governments}Change in governments}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{llllll}
-\toprule
-government & primeMinister & party & start & end & diedInOffice\\
-\midrule
-Barton & Edmund Barton & Protectionist & 1901-01-01 & 1903-09-24 & No\\
-Deakin 1 & Alfred Deakin & Protectionist & 1903-09-24 & 1904-04-27 & No\\
-Watson & Chris Watson & Labour & 1904-04-27 & 1904-08-18 & No\\
-Reid & George Reid & Free Trade & 1904-08-18 & 1905-07-05 & No\\
-Deakin 2 & Alfred Deakin & Protectionist & 1905-07-05 & 1908-11-13 & No\\
-\addlinespace
-Fisher 1 & Andrew Fisher & Labour & 1908-11-13 & 1909-06-02 & No\\
-Deakin 3 & Alfred Deakin & Commonwealth Liberal & 1909-06-02 & 1910-04-29 & No\\
-Fisher 2 & Andrew Fisher & Labor & 1910-04-29 & 1913-06-24 & No\\
-Cook & Joseph Cook & Commonwealth Liberal & 1913-06-24 & 1914-09-17 & No\\
-Fisher 3 & Andrew Fisher & Labor & 1914-09-17 & 1915-10-27 & No\\
-\addlinespace
-Hughes & Billy Hughes & Labor, National Labor and Nationalist & 1915-10-27 & 1923-02-09 & No\\
-Bruce & Stanley Bruce & Nationalist (Coalition) & 1923-02-09 & 1929-10-22 & No\\
-Scullin & James Scullin & Labor & 1929-10-22 & 1932-01-06 & No\\
-Lyons & Joseph Lyons & United Australia (Coalition) & 1932-01-06 & 1939-04-07 & Yes\\
-Page & Earle Page & Country (Coalition) & 1939-04-07 & 1939-04-26 & No\\
-\addlinespace
-Menzies 1 & Robert Menzies & United Australia (Coalition) & 1939-04-26 & 1941-08-28 & No\\
-Fadden & Arthur Fadden & Country (Coalition) & 1941-08-28 & 1941-10-07 & No\\
-Curtin & John Curtin & Labor & 1941-10-07 & 1945-07-05 & Yes\\
-Forde & Frank Forde & Labor & 1945-07-06 & 1945-07-13 & No\\
-Chifley & Ben Chifley & Labor & 1945-07-13 & 1949-12-19 & No\\
-\addlinespace
-Menzies 2 & Robert Menzies & Liberal (Coalition) & 1949-12-19 & 1966-01-26 & No\\
-Holt & Harold Holt & Liberal (Coalition) & 1966-01-26 & 1967-12-19 & Yes\\
-McEwen & John McEwen & Country (Coalition) & 1967-12-19 & 1968-01-10 & No\\
-Gorton & John Gorton & Liberal (Coalition) & 1968-01-10 & 1971-03-10 & No\\
-McMahon & William McMahon & Liberal (Coalition) & 1971-03-10 & 1972-12-05 & No\\
-\addlinespace
-Whitlam & Gough Whitlam & Labor & 1972-12-05 & 1975-11-11 & No\\
-Fraser & Malcolm Fraser & Liberal (Coalition) & 1975-11-11 & 1983-03-11 & No\\
-Hawke & Bob Hawke & Labor & 1983-03-11 & 1991-12-20 & No\\
-Keating & Paul Keating & Labor & 1991-12-20 & 1996-03-11 & No\\
-Howard & John Howard & Liberal (Coalition) & 1996-03-11 & 2007-12-03 & No\\
-\addlinespace
-Rudd 1 & Kevin Rudd & Labor & 2007-12-03 & 2010-06-24 & No\\
-Gillard & Julia Gillard & Labor & 2010-06-24 & 2013-06-27 & No\\
-Rudd 2 & Kevin Rudd & Labor & 2013-06-27 & 2013-09-18 & No\\
-Abbott & Tony Abbott & Liberal (Coalition) & 2013-09-18 & 2015-09-15 & No\\
-Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
-Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & - & -\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:elections}Elections}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{rll}
-\toprule
-year & electionDate & electionWinner\\
-\midrule
-1901 & 1901-03-29 & Non-labor\\
-1903 & 1903-12-16 & Non-labor\\
-1906 & 1906-12-12 & Non-labor\\
-1910 & 1910-04-13 & Labor\\
-1913 & 1913-05-31 & Non-labor\\
-\addlinespace
-1914 & 1914-09-05 & Labor\\
-1917 & 1917-05-05 & Non-labor\\
-1919 & 1919-12-13 & Non-labor\\
-1922 & 1922-12-16 & Non-labor\\
-1925 & 1925-11-14 & Non-labor\\
-\addlinespace
-1928 & 1928-11-17 & Non-labor\\
-1929 & 1929-10-12 & Labor\\
-1931 & 1931-12-19 & Non-labor\\
-1934 & 1934-09-15 & Non-labor\\
-1937 & 1937-10-23 & Non-labor\\
-\addlinespace
-1940 & 1940-09-21 & Non-labor\\
-1943 & 1943-08-21 & Labor\\
-1946 & 1946-09-28 & Labor\\
-1949 & 1949-12-10 & Non-labor\\
-1951 & 1951-08-28 & Non-labor\\
-\addlinespace
-1954 & 1954-05-29 & Non-labor\\
-1955 & 1955-12-10 & Non-labor\\
-1958 & 1958-11-22 & Non-labor\\
-1961 & 1961-12-09 & Non-labor\\
-1963 & 1963-11-30 & Non-labor\\
-\addlinespace
-1966 & 1966-11-26 & Non-labor\\
-1969 & 1969-10-25 & Non-labor\\
-1972 & 1972-12-02 & Labor\\
-1974 & 1974-05-18 & Labor\\
-1975 & 1975-12-13 & Non-labor\\
-\addlinespace
-1977 & 1977-12-10 & Non-labor\\
-1980 & 1980-10-18 & Non-labor\\
-1983 & 1983-03-05 & Labor\\
-1984 & 1984-12-01 & Labor\\
-1987 & 1987-07-11 & Labor\\
-\addlinespace
-1990 & 1990-03-24 & Labor\\
-1993 & 1993-03-13 & Labor\\
-1996 & 1996-03-02 & Non-labor\\
-1998 & 1998-10-03 & Non-labor\\
-2001 & 2001-11-10 & Non-labor\\
-\addlinespace
-2004 & 2004-10-09 & Non-labor\\
-2007 & 2007-11-24 & Labor\\
-2010 & 2010-08-21 & Labor\\
-2013 & 2013-09-07 & Non-labor\\
-2016 & 2016-07-02 & Non-labor\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:economicevents}Key economic events}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{ll}
-\toprule
-theDate & event\\
-\midrule
-1907-11-08 & Harvester case\\
-1910-09-01 & Australian pound introduced (CHECK DATE)\\
-1929-10-29 & Black Tuesday Stock Market Crash\\
-1931-06-01 & Premiers' Plan (CHECK DATE)\\
-1966-02-14 & Decimalisation\\
-\addlinespace
-1973-01-01 & Fred Gruen 25\% tariff cut (DATE IS WRONG)\\
-1983-12-12 & Australian dollar is floated\\
-1984-02-01 & Medicare establised\\
-1987-10-19 & Black Monday Stock Market Crash\\
-1991-02-10 & State Bank of South Australia collapse\\
-\addlinespace
-1990-08-27 & State Bank of Victoria collapse (CHECK DATE)\\
-2000-07-01 & GST introduced\\
-2008-09-15 & Lehman Brothers bankruptcy\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-\begin{table}
-
-\caption{\label{tab:otherevents}Key other events}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{ll}
-\toprule
-theDate & event\\
-\midrule
-1899-10-11 & Second Boer War starts\\
-1901-01-01 & Australia federated\\
-1902-05-31 & Second Boer War ends\\
-1914-07-28 & World War I starts\\
-1918-11-11 & World War I ends\\
-\addlinespace
-1932-05-13 & Jack Lang dismissed as NSW Premier\\
-1939-09-01 & World War II starts\\
-1945-09-02 & World War II ends\\
-1949-10-17 & Snowy Hydro construction begins\\
-1956-11-22 & Melbourne Olympics\\
-\addlinespace
-1962-08-03 & Australia enters Vietnam War\\
-1972-12-02 & Australia exits Vietnam War\\
-1973-10-20 & White Australian Policy ended\\
-1975-11-11 & The Dismissal\\
-1992-06-03 & Mabo\\
-\addlinespace
-1996-12-23 & Wik decision\\
-1996-03-28 & Port Arthur massacre\\
-1999-09-20 & INTERFET deployment begins\\
-2000-02-28 & INTERFET deployment ends\\
-2000-09-15 & Sydney Olympics\\
-\addlinespace
-2001-09-11 & 9/11 attack\\
-2002-10-12 & Bali bombings\\
-\bottomrule
-\end{tabular}
-\end{table}
+to a change of government or an election. Economic events are defined by
+substantial changes in various economic measures, such as the onset of
+the Great Depression or the Great Recession. Other events are those such
+as the 9/11 attacks, or the Bali Bombing. The full list of events that
+we consider is detailed in Appendix \textbf{{[}ADD NUMBERING{]}}. We
+consider events in two ways. The first is in the change in the word
+usage before and after events and the second is in changes in the
+topics.
+
+Differences in word usage can be evaluated using the term
+frequency-inverse document frequency (tf-idf) measure. It will be higher
+for words that are rarely used across all documents, but commonly used
+in a document. For instance, in Australian parliamentary text records
+`the' is commonly used in many documents and so the fact that it is used
+in any particular document is not usual. However, `aboriginal' is less
+common across, and so if it was especially prevelant in a particular
+document that may distinguish that document.
+
+When we consider events using tf-idf, we gather terms from more than one
+day. We define groups of days that are roughly analogous to sitting
+periods. If there is more than a week between a day then we define a new
+group, otherwise the day is in the existing group. We use various
+measures \textbf{(Text2vec R package has some? or some other package)}
+to define a baseline measure of how different each group is, and then
+test for whether groups separated by our events are significantly
+different to this baseline.
+
+Changes in topics also help define how \ldots{}
 
@@
 
-\subsection{External events}\label{external-events}
+\subsection{Other events}\label{other-events}
 
@@
 \section{Appendix}\label{appendix}
+
+\subsection{Example page}\label{example-page}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
+\end{figure}
 
@@
 
+\subsection{Events}\label{events}
+
+\begin{table}
+
+\caption{\label{tab:governments}Change in governments}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{llllll}
+\toprule
+government & primeMinister & party & start & end & diedInOffice\\
+\midrule
+Barton & Edmund Barton & Protectionist & 1901-01-01 & 1903-09-24 & No\\
+Deakin 1 & Alfred Deakin & Protectionist & 1903-09-24 & 1904-04-27 & No\\
+Watson & Chris Watson & Labour & 1904-04-27 & 1904-08-18 & No\\
+Reid & George Reid & Free Trade & 1904-08-18 & 1905-07-05 & No\\
+Deakin 2 & Alfred Deakin & Protectionist & 1905-07-05 & 1908-11-13 & No\\
+\addlinespace
+Fisher 1 & Andrew Fisher & Labour & 1908-11-13 & 1909-06-02 & No\\
+Deakin 3 & Alfred Deakin & Commonwealth Liberal & 1909-06-02 & 1910-04-29 & No\\
+Fisher 2 & Andrew Fisher & Labor & 1910-04-29 & 1913-06-24 & No\\
+Cook & Joseph Cook & Commonwealth Liberal & 1913-06-24 & 1914-09-17 & No\\
+Fisher 3 & Andrew Fisher & Labor & 1914-09-17 & 1915-10-27 & No\\
+\addlinespace
+Hughes & Billy Hughes & Labor, National Labor and Nationalist & 1915-10-27 & 1923-02-09 & No\\
+Bruce & Stanley Bruce & Nationalist (Coalition) & 1923-02-09 & 1929-10-22 & No\\
+Scullin & James Scullin & Labor & 1929-10-22 & 1932-01-06 & No\\
+Lyons & Joseph Lyons & United Australia (Coalition) & 1932-01-06 & 1939-04-07 & Yes\\
+Page & Earle Page & Country (Coalition) & 1939-04-07 & 1939-04-26 & No\\
+\addlinespace
+Menzies 1 & Robert Menzies & United Australia (Coalition) & 1939-04-26 & 1941-08-28 & No\\
+Fadden & Arthur Fadden & Country (Coalition) & 1941-08-28 & 1941-10-07 & No\\
+Curtin & John Curtin & Labor & 1941-10-07 & 1945-07-05 & Yes\\
+Forde & Frank Forde & Labor & 1945-07-06 & 1945-07-13 & No\\
+Chifley & Ben Chifley & Labor & 1945-07-13 & 1949-12-19 & No\\
+\addlinespace
+Menzies 2 & Robert Menzies & Liberal (Coalition) & 1949-12-19 & 1966-01-26 & No\\
+Holt & Harold Holt & Liberal (Coalition) & 1966-01-26 & 1967-12-19 & Yes\\
+McEwen & John McEwen & Country (Coalition) & 1967-12-19 & 1968-01-10 & No\\
+Gorton & John Gorton & Liberal (Coalition) & 1968-01-10 & 1971-03-10 & No\\
+McMahon & William McMahon & Liberal (Coalition) & 1971-03-10 & 1972-12-05 & No\\
+\addlinespace
+Whitlam & Gough Whitlam & Labor & 1972-12-05 & 1975-11-11 & No\\
+Fraser & Malcolm Fraser & Liberal (Coalition) & 1975-11-11 & 1983-03-11 & No\\
+Hawke & Bob Hawke & Labor & 1983-03-11 & 1991-12-20 & No\\
+Keating & Paul Keating & Labor & 1991-12-20 & 1996-03-11 & No\\
+Howard & John Howard & Liberal (Coalition) & 1996-03-11 & 2007-12-03 & No\\
+\addlinespace
+Rudd 1 & Kevin Rudd & Labor & 2007-12-03 & 2010-06-24 & No\\
+Gillard & Julia Gillard & Labor & 2010-06-24 & 2013-06-27 & No\\
+Rudd 2 & Kevin Rudd & Labor & 2013-06-27 & 2013-09-18 & No\\
+Abbott & Tony Abbott & Liberal (Coalition) & 2013-09-18 & 2015-09-15 & No\\
+Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
+Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & - & -\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:elections}Elections}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{rll}
+\toprule
+year & electionDate & electionWinner\\
+\midrule
+1901 & 1901-03-29 & Non-labor\\
+1903 & 1903-12-16 & Non-labor\\
+1906 & 1906-12-12 & Non-labor\\
+1910 & 1910-04-13 & Labor\\
+1913 & 1913-05-31 & Non-labor\\
+\addlinespace
+1914 & 1914-09-05 & Labor\\
+1917 & 1917-05-05 & Non-labor\\
+1919 & 1919-12-13 & Non-labor\\
+1922 & 1922-12-16 & Non-labor\\
+1925 & 1925-11-14 & Non-labor\\
+\addlinespace
+1928 & 1928-11-17 & Non-labor\\
+1929 & 1929-10-12 & Labor\\
+1931 & 1931-12-19 & Non-labor\\
+1934 & 1934-09-15 & Non-labor\\
+1937 & 1937-10-23 & Non-labor\\
+\addlinespace
+1940 & 1940-09-21 & Non-labor\\
+1943 & 1943-08-21 & Labor\\
+1946 & 1946-09-28 & Labor\\
+1949 & 1949-12-10 & Non-labor\\
+1951 & 1951-08-28 & Non-labor\\
+\addlinespace
+1954 & 1954-05-29 & Non-labor\\
+1955 & 1955-12-10 & Non-labor\\
+1958 & 1958-11-22 & Non-labor\\
+1961 & 1961-12-09 & Non-labor\\
+1963 & 1963-11-30 & Non-labor\\
+\addlinespace
+1966 & 1966-11-26 & Non-labor\\
+1969 & 1969-10-25 & Non-labor\\
+1972 & 1972-12-02 & Labor\\
+1974 & 1974-05-18 & Labor\\
+1975 & 1975-12-13 & Non-labor\\
+\addlinespace
+1977 & 1977-12-10 & Non-labor\\
+1980 & 1980-10-18 & Non-labor\\
+1983 & 1983-03-05 & Labor\\
+1984 & 1984-12-01 & Labor\\
+1987 & 1987-07-11 & Labor\\
+\addlinespace
+1990 & 1990-03-24 & Labor\\
+1993 & 1993-03-13 & Labor\\
+1996 & 1996-03-02 & Non-labor\\
+1998 & 1998-10-03 & Non-labor\\
+2001 & 2001-11-10 & Non-labor\\
+\addlinespace
+2004 & 2004-10-09 & Non-labor\\
+2007 & 2007-11-24 & Labor\\
+2010 & 2010-08-21 & Labor\\
+2013 & 2013-09-07 & Non-labor\\
+2016 & 2016-07-02 & Non-labor\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:economicevents}Key economic events}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+theDate & event\\
+\midrule
+1907-11-08 & Harvester case\\
+1910-09-01 & Australian pound introduced (CHECK DATE)\\
+1929-10-29 & Black Tuesday Stock Market Crash\\
+1931-06-01 & Premiers' Plan (CHECK DATE)\\
+1966-02-14 & Decimalisation\\
+\addlinespace
+1973-01-01 & Fred Gruen 25\% tariff cut (DATE IS WRONG)\\
+1983-12-12 & Australian dollar is floated\\
+1984-02-01 & Medicare establised\\
+1987-10-19 & Black Monday Stock Market Crash\\
+1991-02-10 & State Bank of South Australia collapse\\
+\addlinespace
+1990-08-27 & State Bank of Victoria collapse (CHECK DATE)\\
+2000-07-01 & GST introduced\\
+2008-09-15 & Lehman Brothers bankruptcy\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}
+
+\caption{\label{tab:otherevents}Key other events}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{ll}
+\toprule
+theDate & event\\
+\midrule
+1899-10-11 & Second Boer War starts\\
+1901-01-01 & Australia federated\\
+1902-05-31 & Second Boer War ends\\
+1914-07-28 & World War I starts\\
+1918-11-11 & World War I ends\\
+\addlinespace
+1932-05-13 & Jack Lang dismissed as NSW Premier\\
+1939-09-01 & World War II starts\\
+1945-09-02 & World War II ends\\
+1949-10-17 & Snowy Hydro construction begins\\
+1956-11-22 & Melbourne Olympics\\
+\addlinespace
+1962-08-03 & Australia enters Vietnam War\\
+1972-12-02 & Australia exits Vietnam War\\
+1973-10-20 & White Australian Policy ended\\
+1975-11-11 & The Dismissal\\
+1992-06-03 & Mabo\\
+\addlinespace
+1996-12-23 & Wik decision\\
+1996-03-28 & Port Arthur massacre\\
+1999-09-20 & INTERFET deployment begins\\
+2000-02-28 & INTERFET deployment ends\\
+2000-09-15 & Sydney Olympics\\
+\addlinespace
+2001-09-11 & 9/11 attack\\
+2002-10-12 & Bali bombings\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\subsection{Choosing number of topics}\label{choosing-number-of-topics}
+
+Add the graphs and procedures.
+
+\subsection{word2vec alternative}\label{word2vec-alternative}
+
+An alternative approach that follows \citet{Taddy2015}.
+
 \newpage

### 2018-09-26 scripts/to_analyse_topics/using-chi-square.R

@@ -10,16 +10,54 @@
 
 #### Workspace set-up ####
 # Load libraries
-# library(lubridate)
+library(lubridate)
 # library(quanteda)
 # library(stm)
 # library(tictoc)
-library(tidytext)
-# library(tidyverse)
+# library(tidytext)
+library(tidyverse)
 # library(viridis)
 # update.packages()
 
 # Load the election dates
 election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
 # Load topics
-election_dates <- read_csv(td_gamma, "test_gammas.csv")
+topics <- read_csv("outputs/big_files_do_not_push/test_gammas.csv")
+head(election_dates)
+head(topics)
+
+
+all_dates <-
+  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
+  mutate(electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+         electionDate = cumsum(electionDate)) %>% 
+  rename(electionCounter = electionDate)
+
+topics <- topics %>% 
+  left_join(all_dates, by = c("document" = "allDates"))
+
+rm(all_dates, election_dates)
+
+
+topics_test <- topics %>% 
+  filter(electionCounter %in% c(1, 2)) %>% 
+  group_by(electionCounter, topic) %>% 
+  summarise(ave_gamma = mean(gamma)) %>% 
+  mutate(ave_gamma = as.integer(ave_gamma*100000))
+
+topics_test <- topics_test %>% 
+  spread(electionCounter, ave_gamma) %>% 
+  rename(year1 = `1`, year2 = `2`) 
+
+topics_test$topic <- NULL
+topics_test[1:5,]
+
+library(MASS)       # load the MASS package 
+tbl = table(survey$Smoke, survey$Exer) 
+tbl %>% class()
+
+ggplot(topics_test, aes(x = topic, y = ave_gamma, colour = electionCounter))+
+  geom_point()
+
+
+chisq.test(topics_test[1:90,])

### 2018-09-26 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -3,7 +3,7 @@
 # Purpose: Create topics, for the words used in each day of Hansard
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 23 September 2018
+# Last updated: 25 September 2018
 # Prerequisites:
 # Issues:
 
@@ -155,23 +155,23 @@ rm(tidy_hansard_reduced, hansard_corpus, docsTM, vocabTM, metaTM)
 
 #HERE
 
-test <-
+model_prevalence_is_spline <-
   stm(
     documents = hansard_dfm$documents,
     vocab = hansard_dfm$vocab,
     K = 100,
-    prevalence =~ docid_field + electionCounter,
+    prevalence =~ s(as.numeric(docid_field)),
     data = hansard_dfm$meta,
     max.em.its = 75,
     init.type = "Spectral"
   )
 
-td_gamma <- tidy(test,
+td_gamma <- tidy(model_prevalence_is_spline,
                  matrix = "gamma",
                  document_names = hansard_dfm$meta$docid_field)
 td_gamma
 
-write_csv(td_gamma, "test_gammas.csv")
+write_csv(td_gamma, "gammas_model_prevalence_is_spline.csv")
 
 td_gamma %>% 
   mutate(document = ymd(document)) %>% 

### 2018-09-26 scripts/to_scrape_websites/get_HoR_voting.R

@@ -1,0 +1,46 @@
+#### Preamble ####
+# Purpose: This file gets Australian HoR voting from Adam Carr's Psephos
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 25 September 2018
+# Prerequisites: -
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/URLs_for_adam_carr.csv")
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("txt/", save_name)
+
+dir.create("txt")
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(15:30, 1)) # Space out requests by somewhere between 15 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
+save_name <- save_name[3:length(save_name)] # main run
+address_to_visit <- address_to_visit[3:length(address_to_visit)] # main run
+
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
+

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper

@@
 We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
-We then examine the effect of various events using a discrete choice model.
+We then examine the effect of various events using a simple discrete choice model.
 We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects.
@@
 Our use of a discrete choice model allows us construct a counterfactual.
-Our work fits into a growing literature that considers text as a input to more usual quantitative techniques, rather than requiring separate analysis.
+Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
 While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
@@
 
-[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
 Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
@@
 |                   | Legislative Council       | 1851 - 2017 | **[TBD]** |
-| Tasmania[^3]      | House of Assembly        | 1856 - 2017 | **[TBD]** |
+| Tasmania          | House of Assembly         | 1856 - 2017 | **[TBD]** |
 |                   | Legislative Council       | 1856 - 2017 | **[TBD]** |
-| South Australia[^4] | House of Assembly       | 1857 - 2017 | **[TBD]** |
+| South Australia   | House of Assembly         | 1857 - 2017 | **[TBD]** |
 |                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
-| Western Australia[^5] | Legislative Assembly  | 1890 - 2017 | **[TBD]** |
+| Western Australia | Legislative Assembly      | 1890 - 2017 | **[TBD]** |
 |                   | Legislative Council       | 1832 - 2017 | **[TBD]** |
@@
 However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
-
-[^3]: **[Update this, depending on final Tassie records]**.
-
-[^4]: **[Update this, depending on final SA records]**.
-
-[^5]: **[Update this, depending on final WA records]**.
 
@@
 In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
-**NEED TO bundle_ngrams i.e.
-olive oil should be olive_oil, not considered separately.**
+**[Need to bundle_ngrams i.e.
+olive oil is olive_oil]**
 
@@
 For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
+The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each aspect.
+For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
+Similarly, the content meta-data are
 
-Again, the assumed process that generates the documents is the key aspect as this will be reversed to estimate the topics.
+As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
 The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM:
 
-**THIS NEEDS WORK START**
+1.
+As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
+In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3):
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
 
-1.
-The proportion of a document dedicated to a topic, stored in the vector $\theta_d$, is drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a document covariates, $X_d$, following @RobertsStewartTingley2018:
-$$\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
-"where $X_d$ is a 1-by-p vector, $\gamma$ is a p-by-K - 1 matrix of coefficients and $\sigma$ is K-1 by K-1 covariance matrix." This is in contrast to the Dirichlet distribution that characterises LDA.
 2.
-**THIS IS ALL QUOTES.
-NEED TO REWRITE.** Given a document-level content covariate $y_d$, form the document-specific distribution over words representing each topic ($k$) using the baseline word distribution $m$, the topic specific deviation, $\kappa_k^{(t)}$, the covariate group deviation, $\kappa_{y_d}^{(c)}$, and the interaction between the two, $\kappa_{y_{d}k}^{(i)}$:
-$$\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) $$
+To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
+Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$:
+$$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$
 
-**THIS NEEDS WORK END**
+3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$:
+    a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics.
+    b. Randomly choose a term from the topic-specific multinomial distribution over terms.
 
-We implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
 We consider both topic prevalence and content to be functions of time.
-The choice of how many topics to use in the model is a situation-specific compromise.
-We use standard diagnostic techniques to decide on 80 topics, and more detail on this process is available in Appendix **[ADD NUMBERING]**.
+The choice of the number of topics to use in the model is a situation-specific compromise.
+We use standard diagnostic techniques to decide on 80 **[UPDATE]** topics.
+More detail on this process is available in Appendix **[ADD NUMBERING]**.
 
-One way to summarise the results of the topic model is to **????**
+The illustrate the output of an STM, Figure \@ref(fig:example_topics)) shows the estimated proportion of each day summarised by ten topics for the House of Representatives for 1901 through to 2017.
+**[RUN AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED.]**
 
-```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/all_topics_usable.png"))
+```{r example_topics, echo=FALSE, fig.cap="Estimated 10-topic-proportion", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
 ```
@@
 ### Considering events
-We consider the effect of political, economic, and other events on Australian parliamentary discussion.
+We are interested in the effect of political, economic, and other events on Australian parliamentary discussion.
 Political events are those related to a change of government or an election.
@@
 The full list of events that we consider is detailed in Appendix **[ADD NUMBERING]**.
-We consider events in two ways.
-The first is in the change in the word usage before and after events and the second is in changes in the topics.
+
+There are many ways to statistically consider the effect of events.
+Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which are commonly used in finance to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
+Alternatively, the time series aspect could be ignored, and then the topics could be
+
+We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.
 
@@
 For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
-However, 'aboriginal' is less common across, and so if it was especially prevelant in a particular document that may distinguish that document.
+However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
 
@@
 
-Future work - examine how it chagned during Federation
+Future work - examine how it changed during Federation
 

### 2018-09-26 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 25
+Cochrane for their helpful suggestions. \textbf{Version as of}: 26
 September 2018; \textbf{comments welcome}:
@@
 such as correlation between days and changes over time. We then examine
-the effect of various events using a discrete choice model. We find
-that: 1) changes of government are associated with topic changes only
-when there is also a change of the party in power; and 2) economic
+the effect of various events using a simple discrete choice model. We
+find that: 1) changes of government are associated with topic changes
+only when there is also a change of the party in power; and 2) economic
 events, such as financial crises, have significant and persistent
@@
 of a discrete choice model allows us construct a counterfactual. Our
-work fits into a growing literature that considers text as a input to
+work fits into a growing literature that considers text as an input to
 more usual quantitative techniques, rather than requiring separate
@@
   available as a single download and also presents them in a website
-  (historichansard.net/) that can be used to explore Commonwealth
-  Hansard records from 1901 to 1980. Commonwealth XML records from 1998
-  to 2014 are available from Andrew Turpin's website, and from 2006
-  through to today from Open Australia's website. The records can also
-  be downloaded from the Australian Hansard website.} There are 65,000
-\textbf{{[}UPDATE{]}} Hansard records publicly available across the
-state and federal parliaments (Table 1) \textbf{{[}UPDATE NUMBERING{]}}.
-As with any larger-scale data process, there are various issues with
-some of the PDFs and the known ones are detailed in Appendix
-\textbf{{[}ADD NUMBERING{]}}.
+  (\url{http://historichansard.net/}) that can be used to explore
+  Commonwealth Hansard records from 1901 to 1980. Commonwealth XML
+  records from 1998 to 2014 are available from Andrew Turpin's website,
+  and from 2006 through to today from Open Australia's website. The
+  records can also be downloaded from the Australian Hansard website.}
+There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
+available across the state and federal parliaments (Table 1)
+\textbf{{[}UPDATE NUMBERING{]}}. As with any larger-scale data process,
+there are various issues with some of the PDFs and the known ones are
+detailed in Appendix \textbf{{[}ADD NUMBERING{]}}.
 
@@
 & Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Tasmania\footnote{\textbf{{[}Update this, depending on final Tassie
-  records{]}}.} & House of Assembly & 1856 - 2017 &
+Tasmania & House of Assembly & 1856 - 2017 &
 \textbf{{[}TBD{]}}\tabularnewline
 & Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-South Australia\footnote{\textbf{{[}Update this, depending on final SA
-  records{]}}.} & House of Assembly & 1857 - 2017 &
+South Australia & House of Assembly & 1857 - 2017 &
 \textbf{{[}TBD{]}}\tabularnewline
 & Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Western Australia\footnote{\textbf{{[}Update this, depending on final WA
-  records{]}}.} & Legislative Assembly & 1890 - 2017 &
+Western Australia & Legislative Assembly & 1890 - 2017 &
 \textbf{{[}TBD{]}}\tabularnewline
@@
 the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
-\textbf{NEED TO bundle\_ngrams i.e.~olive oil should be olive\_oil, not
-considered separately.}
+\textbf{{[}Need to bundle\_ngrams i.e.~olive oil is olive\_oil{]}}
 
@@
 better for these to not be responsible for defining different topics
-rather than being part of the same topic.
-
-Again, the assumed process that generates the documents is the key
+rather than being part of the same topic. The prevalence meta-data for
+the \(d\)th document are in \(X_d\), which has one column for each
+aspect. For instance, if there were 10 documents and each had a date and
+an author, then \(X\) would be \(10\times 2\). Similarly, the content
+meta-data are
+
+As with LDA, the process assumed to generate the documents is the key
 aspect as this will be reversed to estimate the topics. The document
@@
 
-\textbf{THIS NEEDS WORK START}
-
 \begin{enumerate}
 \def\labelenumi{\arabic{enumi}.}
+\item
+  As with LDA, the topic distributions, that is, the proportion of a
+  document dedicated to a topic, for the \(d\)th document are
+  \(\theta_d\), and \(\theta\) is a vector with length \(D\). In
+  contrast to LDA, this is a drawn from a logistic-normal distribution,
+  parameterised such that the mean of that distribution, \(\mu\), is
+  affected by a vector of document covariates, \(X_d\) (following
+  \citet{RobertsStewartTingley2018}, p.3):
+  \[\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)\]
+\item
+  To decide the distribution over terms for each topic, \(\beta_{d,k}\),
+  start with some baseline distribution over the terms, \(m\).
+  Topic-\(k\)-specific deviations from this are controlled by
+  \(\kappa_k^{(t)}\), deviations due to the document meta-data are
+  controlled by \(\kappa_{y_d}^{(c)}\), and the interaction between
+  these two deviations is controlled by \(\kappa_{y_d,k}^{(i)}\):
+  \[\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) \]
+\item
+  Then if there are \(n\) terms in the \(d\)th document, then to choose
+  the \(n\)th term, \(w_{d,n}\):
+
+  \begin{enumerate}
+  \def\labelenumii{\alph{enumii}.}
   \tightlist
   \item
-  The proportion of a document dedicated to a topic, stored in the
-  vector \(\theta_d\), is drawn from a logistic-normal distribution,
-  parameterised such that the mean of that distribution, \(\mu\), is
-  affected by a document covariates, \(X_d\), following
-  \citet{RobertsStewartTingley2018}:
-  \[\theta_d|X_d\gamma\sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)\]
-  ``where \(X_d\) is a 1-by-p vector, \(\gamma\) is a p-by-K - 1 matrix
-  of coefficients and \(\sigma\) is K-1 by K-1 covariance matrix.'' This
-  is in contrast to the Dirichlet distribution that characterises LDA.
+    Randomly choose a topic for that term from the document-specific
+    multinomial distribution over topics.
   \item
-  \textbf{THIS IS ALL QUOTES. NEED TO REWRITE.} Given a document-level
-  content covariate \(y_d\), form the document-specific distribution
-  over words representing each topic (\(k\)) using the baseline word
-  distribution \(m\), the topic specific deviation, \(\kappa_k^{(t)}\),
-  the covariate group deviation, \(\kappa_{y_d}^{(c)}\), and the
-  interaction between the two, \(\kappa_{y_{d}k}^{(i)}\):
-  \[\beta_{d,k}\propto exp(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}) \]
+    Randomly choose a term from the topic-specific multinomial
+    distribution over terms.
   \end{enumerate}
-
-\textbf{THIS NEEDS WORK END}
-
-We implement the STM on the daily-level parliamentary text data
-described earlier using the \texttt{stm} R package of
+\end{enumerate}
+
+We primarily implement the STM on the daily-level parliamentary text
+data described earlier using the \texttt{stm} R package of
 \citet{RobertsStewartAiroldiRPackage}. We consider both topic prevalence
-and content to be functions of time. The choice of how many topics to
-use in the model is a situation-specific compromise. We use standard
-diagnostic techniques to decide on 80 topics, and more detail on this
-process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.
-
-One way to summarise the results of the topic model is to \textbf{????}
+and content to be functions of time. The choice of the number of topics
+to use in the model is a situation-specific compromise. We use standard
+diagnostic techniques to decide on 80 \textbf{{[}UPDATE{]}} topics. More
+detail on this process is available in Appendix \textbf{{[}ADD
+NUMBERING{]}}.
+
+The illustrate the output of an STM, Figure @ref(fig:example\_topics))
+shows the estimated proportion of each day summarised by ten topics for
+the House of Representatives for 1901 through to 2017. \textbf{{[}RUN
+AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED.{]}}
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/all_topics_usable} \caption{A caption}\label{fig:pressure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_example} \caption{Estimated 10-topic-proportion}(\#fig:example_topics)
 \end{figure}
@@
 
-We consider the effect of political, economic, and other events on
-Australian parliamentary discussion. Political events are those related
-to a change of government or an election. Economic events are defined by
-substantial changes in various economic measures, such as the onset of
-the Great Depression or the Great Recession. Other events are those such
-as the 9/11 attacks, or the Bali Bombing. The full list of events that
-we consider is detailed in Appendix \textbf{{[}ADD NUMBERING{]}}. We
-consider events in two ways. The first is in the change in the word
+We are interested in the effect of political, economic, and other events
+on Australian parliamentary discussion. Political events are those
+related to a change of government or an election. Economic events are
+defined by substantial changes in various economic measures, such as the
+onset of the Great Depression or the Great Recession. Other events are
+those such as the 9/11 attacks, or the Bali Bombing. The full list of
+events that we consider is detailed in Appendix \textbf{{[}ADD
+NUMBERING{]}}.
+
+There is a large number of ways to statistically consider the effect of
+events. Options that would take advantage of the time series nature of
+our data include: autoregressive moving average (ARMA) models which are
+commonly used in finance to test for structural breaks
+\textbf{{[}REFERENCE?{]}}; or splines could be fit with specific knot
+placements and then cross validation used to compare the RSS with a more
+general splines model.
+
+We consider events in two ways. The first is in the change in the word
 usage before and after events and the second is in changes in the
@@
 in any particular document is not usual. However, `aboriginal' is less
-common across, and so if it was especially prevelant in a particular
+common across, and so if it was especially prevalent in a particular
 document that may distinguish that document.

### 2018-09-26 scripts/to_make_graphs/make_graph_of_topics_example_paper.R

@@ -1,0 +1,61 @@
+# library(ggrepel)
+library(lubridate)
+library(tidyverse)
+
+td_gamma <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv")
+
+head(td_gamma)
+
+td_gamma_test <- td_gamma %>% 
+  mutate(decade = case_when(
+    document < 1909-12-31 ~ "1900s",
+    document < 1919-12-31 ~ "1910s",
+    document < 1929-12-31 ~ "1920s",
+    document < 1939-12-31 ~ "1930s",
+    document < 1949-12-31 ~ "1940s",
+    document < 1959-12-31 ~ "1950s",
+    document < 1969-12-31 ~ "1960s",
+    document < 1979-12-31 ~ "1970s",
+    document < 1989-12-31 ~ "1980s",
+    document < 1999-12-31 ~ "1990s",
+    document < 2009-12-31 ~ "2000s",
+    TRUE ~ "2010s"
+  )) %>% 
+  group_by(decade, topic) %>% 
+  summarise(ave_gamma = mean(gamma))
+
+td_gamma_test <- td_gamma %>% 
+  mutate(topic = case_when(
+    topic <= 10 ~ 1,
+    topic <= 20 ~ 2,
+    topic <= 30 ~ 3,
+    topic <= 40 ~ 4,
+    topic <= 50 ~ 5,
+    topic <= 60 ~ 6,
+    topic <= 70 ~ 7,
+    topic <= 80 ~ 8,
+    topic <= 90 ~ 9,
+    TRUE ~ 10
+  )) %>% 
+  group_by(document, topic) %>% 
+  summarise(ave_gamma = sum(gamma))
+
+td_gamma_test[1:20,]
+
+td_gamma_test_reduced <- td_gamma_test %>% 
+  filter(topic %in% c(3, 4, 10))
+
+ggplot(data = td_gamma_test, aes(x = document, y = ave_gamma, color = as.factor(topic))) +
+  geom_point(color = "grey", alpha = 0.5) +
+  geom_point(data = td_gamma_test_reduced) +
+  theme_classic() +
+  labs(x = "Date",
+       y = "Gamma") +
+  scale_colour_viridis_d()
+
+ggsave(
+    "outputs/figures/topics_example.pdf",
+     height = 6,
+     width = 8,
+     units = "in"
+  )

### 2018-09-27 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Try and fail to get model working and add wa url scraper

@@
 There are many ways to statistically consider the effect of events.
+One way would be to ignore the time series aspect and just group the topic proportions by each event and then run multinomial tests for whether the groups are different.
+Another would be to consider some type of multinomial logistic regression.
 Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which are commonly used in finance to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
-Alternatively, the time series aspect could be ignored, and then the topics could be
 
-We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.
+<!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.  -->
 
-Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
+<!-- Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
 It will be higher for words that are rarely used across all documents, but commonly used in a document.
@@
 However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
+-->
 
-When we consider events using tf-idf, we gather terms from more than one day.
+<!-- When we consider events using tf-idf, we gather terms from more than one day.
 We define groups of days that are roughly analogous to sitting periods.
@@
 or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
-
-Changes in topics also help define how ...
+-->
 

### 2018-09-27 scripts/to_analyse_topics/test.R

@@ -1,0 +1,94 @@
+# install.packages("rstan")
+# install.packages("rstanarm")
+# install.packages("arm")
+
+library("rstan")
+library("rstanarm")
+library("arm")
+library(tidyverse)
+library(lubridate)
+# options(mc.cores = parallel::detectCores())
+rstan_options(auto_write = TRUE)
+
+
+
+
+# Load the election dates
+election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
+# Load topics
+topics <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv")
+head(election_dates)
+head(topics)
+
+
+all_dates <-
+  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
+  mutate(electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+         electionDate = cumsum(electionDate)) %>% 
+  rename(electionCounter = electionDate)
+
+head(all_dates)
+
+topics <- topics %>% 
+  left_join(all_dates, by = c("document" = "allDates"))
+
+head(topics)
+
+topics_dates <- tibble(date = topics$document %>% unique())
+topics_dates <- topics_dates %>% 
+  arrange(date) %>% 
+  mutate(counter = 1:nrow(topics_dates))
+
+topics <- topics %>% 
+  left_join(topics_dates, by = c("document" = "date"))
+
+head(topics)
+
+topics_test <- topics %>% 
+  # filter(electionCounter %in% c(1, 2)) %>%
+  mutate(gamma = gamma * 1000000000,
+         gamma = as.integer(gamma)) %>% 
+  # filter(!topic %in% c(1, 2)) %>%
+  mutate(electionCounter = as.integer(electionCounter))
+
+head(topics_test)
+?scale
+
+
+# fit_1 <- stan_glmer(gamma ~ (1 + counter | topic) + counter + electionCounter, data=topics_test)
+# Allow varying slope and intercept for topics and, allow slope of counter to vary by topic
+
+fit_1 <-
+  lmer(
+    gamma ~ (1 | topic) + counter + electionCounter,
+    data = topics_test
+  )
+# Each topic gets a different intercept
+
+summary(fit_1)
+plot(fit_1)
+display(fit_1)
+ranef(fit_1)
+?fit
+
+
+# install.packages("merTools")
+# library(merTools)
[…]

### 2018-09-27 scripts/to_analyse_topics/using-chi-square.R

@@ -22,7 +22,7 @@ library(tidyverse)
 # Load the election dates
 election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
 # Load topics
-topics <- read_csv("outputs/big_files_do_not_push/test_gammas.csv")
+topics <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv")
 head(election_dates)
 head(topics)
 
@@ -35,6 +35,8 @@ all_dates <-
 
 topics <- topics %>% 
   left_join(all_dates, by = c("document" = "allDates"))
+
+head(topics)
 
 rm(all_dates, election_dates)
 
@@ -58,6 +60,6 @@ tbl %>% class()
 
 ggplot(topics_test, aes(x = topic, y = ave_gamma, colour = electionCounter))+
   geom_point()
+rmultinom(10, size = 12, prob = c(0.1,0.2,0.8))
 
-
-chisq.test(topics_test[1:90,])
+chisq.test(topics_test[1:5,])

### 2018-09-28 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update paper and add examples

@@
 ## Parliamentary text data
-Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Hansard records and their equivalents are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
-For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015 and @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
+Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012 or **[ANOTHER REFERENCE]**, often examined broader activity measures.
+This allowed for long time frames and wide comparisons.
+But Hansard records and their equivalents are an increasingly viable and popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
+
+The digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015 and @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
 In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
+As digitisation methods improve increasingly older UK records can be analysed, for instance @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
 In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
@@
 Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
-Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed.
+The high dimensional nature of text data means that the appropriate analysis dataset is research-question specific.
+For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
+But they are interesting in their own right and @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs.
 
@@
 The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.
-In theory we could have directly used the text as an input to the discrete choice model, but this quickly becomes intractable due to computer memory and storage constraints.
+In theory we could have directly used the text as an input to the discrete choice model, but this can become intractable.
 Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.
@@
 
-Change of government.
+Change of election
+
+```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_election.pdf"))
+```
+
+Change of government
+
+```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_government_change.pdf"))
+```
 
@@
 
-[TBD]
+Major change in economic conditions
+
+```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_economic_changes.pdf"))
+```
 
@@
 Major event such as 9/11 attacks, or economic change.
+
+Major other changes
+
+```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_other_changes.pdf"))
+```
 

### 2018-09-28 outputs/docs/events/svm-rmarkdown-article-example.tex
Update paper and add examples

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 26
+Cochrane for their helpful suggestions. \textbf{Version as of}: 28
 September 2018; \textbf{comments welcome}:
@@
   found that changes were usually made by those responsible for creating
-  the Hansard record, instead of the parliamentarians.} Hansard records
-and their equivalents are an increasingly popular source of data as new
-methods and reduced computational costs make larger-scale analysis
-easier. For instance, the digitisation of the Canadian Hansard,
-\citet{BeelenEtc2017}, allowed \citet{Whyte2017} to examine whether
-parliamentary disruptions in Canada increased between 1926 and 2015 and
-\citet{RheaultCochran2018} to examine ideology and party polarisation in
-Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
-records to examine which politicians made supportive or aggressive
-statements toward other politicians between 1979 and 1990 and
-\citet{PetersonSpirling2018} examined polarisation. In New Zealand,
-\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
-and \citet{Graham2016} examined unparliamentary language between 1890
-and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
-congressional speech records from 1873 to 2016 to find that partisanship
-has risen in the past few decades.
+  the Hansard record, instead of the parliamentarians.} Earlier work on
+the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
+\textbf{{[}ANOTHER REFERENCE{]}}, often examined broader activity
+measures. This allowed for long time frames and wide comparisons. But
+Hansard records and their equivalents are an increasingly viable and
+popular source of data as new methods and reduced computational costs
+make larger-scale analysis easier.
+
+The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
+\citet{Whyte2017} to examine whether parliamentary disruptions in Canada
+increased between 1926 and 2015 and \citet{RheaultCochran2018} to
+examine ideology and party polarisation in Britain and Canada. In the
+UK, \citet{Duthie2016} analysed Hansard records to examine which
+politicians made supportive or aggressive statements toward other
+politicians between 1979 and 1990 and \citet{PetersonSpirling2018}
+examined polarisation. As digitisation methods improve increasingly
+older UK records can be analysed, for instance \citet{Dimitruk2018}
+considers the effect of estate bills on prorogations in seventeenth
+century England. In New Zealand, \citet{Curran2017} modelled the topics
+discussed between 2003 and 2016, and \citet{Graham2016} examined
+unparliamentary language between 1890 and 1950. And in the US
+\citet{GentzkowShapiroTaddy2018} examine congressional speech records
+from 1873 to 2016 to find that partisanship has risen in the past few
+decades.
 
@@
 specific to any particular politician, such as `Honourable members
-interjecting'. Interjections are interesting in their own right, for
-instance \citet{Whyte2017} analysed them in a Canadian context for the
-period 1926 to 2015 to find that female MPs were more likely to be
-interrupted than male MPs, but do not usually contribute much to
-defining the topics being discussed.
+interjecting'. The high dimensional nature of text data means that the
+appropriate analysis dataset is research-question specific. For
+instance, in our paper interjections are not important because they do
+not usually contribute much to defining the topics being discussed. But
+they are interesting in their own right and \citet{Whyte2017} analysed
+them in a Canadian context for the period 1926 to 2015 to find that
+female MPs were more likely to be interrupted than male MPs.
 
@@
 could have directly used the text as an input to the discrete choice
-model, but this quickly becomes intractable due to computer memory and
-storage constraints. Instead, in a similar way to
+model, but this can become intractable. Instead, in a similar way to
 \citet{MuellerRauh2018}, we use the topics that the text is about as an
@@
 
-There is a large number of ways to statistically consider the effect of
-events. Options that would take advantage of the time series nature of
-our data include: autoregressive moving average (ARMA) models which are
-commonly used in finance to test for structural breaks
-\textbf{{[}REFERENCE?{]}}; or splines could be fit with specific knot
-placements and then cross validation used to compare the RSS with a more
-general splines model.
-
-We consider events in two ways. The first is in the change in the word
-usage before and after events and the second is in changes in the
-topics.
-
-Differences in word usage can be evaluated using the term
-frequency-inverse document frequency (tf-idf) measure. It will be higher
-for words that are rarely used across all documents, but commonly used
-in a document. For instance, in Australian parliamentary text records
-`the' is commonly used in many documents and so the fact that it is used
-in any particular document is not usual. However, `aboriginal' is less
-common across, and so if it was especially prevalent in a particular
-document that may distinguish that document.
-
-When we consider events using tf-idf, we gather terms from more than one
-day. We define groups of days that are roughly analogous to sitting
-periods. If there is more than a week between a day then we define a new
-group, otherwise the day is in the existing group. We use various
-measures \textbf{(Text2vec R package has some? or some other package)}
-to define a baseline measure of how different each group is, and then
-test for whether groups separated by our events are significantly
-different to this baseline.
-
-Changes in topics also help define how \ldots{}
+There are many ways to statistically consider the effect of events. One
+way would be to ignore the time series aspect and just group the topic
+proportions by each event and then run multinomial tests for whether the
+groups are different. Another would be to consider some type of
+multinomial logistic regression. Options that would take advantage of
+the time series nature of our data include: autoregressive moving
+average (ARMA) models which are commonly used in finance to test for
+structural breaks \textbf{{[}REFERENCE?{]}}; or splines could be fit
+with specific knot placements and then cross validation used to compare
+the RSS with a more general splines model.
 
@@
 
-Change of government.
+Change of election
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_election} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+Change of government
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_government_change} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-2}
+\end{figure}
 
@@
 
-{[}TBD{]}
+Major change in economic conditions
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_economic_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-3}
+\end{figure}
 
@@
 Major event such as 9/11 attacks, or economic change.
+
+Major other changes
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_other_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-4}
+\end{figure}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 Turnbull & Malcolm Turnbull & Liberal (Coalition) & 2015-09-15 & 2018-08-24 & No\\
-Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & - & -\\
+Morrison & Scott Morrison & Liberal (Coalition) & 2018-08-24 & NA & NA\\
 \bottomrule

### 2018-09-28 scripts/to_make_graphs/make_graph_of_topic_distributions_by_events.R

@@ -1,0 +1,115 @@
+
+# Load libraries
+library(lubridate)
+library(tidyverse)
+
+# Load the gammas from the topic model
+td_gamma <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv", col_types = cols())
+head(td_gamma)
+
+# Load the metadata that will define groups
+election_dates <- read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
+governmentChanges <- read_csv("inputs/misc/change_of_pm.csv", col_types = cols())
+keyEconomicDates <- read_csv("inputs/misc/key_dates-economic.csv", col_types = cols())
+keyOtherDates <- read_csv("inputs/misc/key_dates-other.csv", col_types = cols())
+
+
+# Join the metadata to the gammas data
+all_dates <-
+  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
+  mutate(electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+         electionDate = cumsum(electionDate),
+         governmentChangeDate = if_else(allDates %in% governmentChanges$end, 1, 0),
+         governmentChangeDate = cumsum(governmentChangeDate),
+         keyEconomicChange = if_else(allDates %in% keyEconomicDates$theDate, 1, 0),
+         keyEconomicChange = cumsum(keyEconomicChange),
+         keyOtherChange = if_else(allDates %in% keyOtherDates$theDate, 1, 0),
+         keyOtherChange = cumsum(keyOtherChange)) %>% 
+  rename(electionCounter = electionDate)
+head(all_dates)
+
+td_gamma <- td_gamma %>% 
+  left_join(all_dates, by = c("document" = "allDates"))
+head(td_gamma)
+
+
+td_gamma_reduced <- td_gamma %>% 
+  filter(topic %in% c(1:20)) %>% 
+  mutate(grouper = case_when(topic %in% c(1,5,9,13,17) ~ "Topics 1, 5, 9, 13, 17",
+                             topic %in% c(2,6,10,14,18) ~ "Topics 2, 6, 10, 14, 18",
+                             topic %in% c(3,7,11,15,19) ~ "Topics 3, 7, 11, 15, 19",
+                             TRUE ~ "Topics 4, 8, 12, 16, 20"
+                             ),
[…]

### 2018-09-28 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -3,7 +3,7 @@
 # Purpose: Create topics, for the words used in each day of Hansard
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 27 September 2018
+# Last updated: 28 September 2018
 # Prerequisites:
 # Issues:
 
@@ -171,31 +171,67 @@ head(metaTM)
 # head(hansard_stm)
 names(hansard_stm)
 
-
-#
-test <- convert(hansard_dfm, to = "data.frame")
-write_csv(test, "corpus.csv")
-
-library(tm)
-writeCorpus(hansard_corpus, "test")
-mytf7 <- ?corpus("corpus.csv", textfield = "inaugSpeech")
-
-summary(corpus(mytf7), 5)
-?dfm()
-
-#
+# Save a copy for the cloud - how do you actually save the corpus?
+# write_csv(tidy_hansard_reduced, "tidy_hansard_reduced.csv")
 
 # Clean up
-rm(tidy_hansard_reduced, hansard_corpus, docsTM, vocabTM, metaTM)
+rm(tidy_hansard_reduced, hansard_corpus, docsTM, vocabTM, metaTM, hansard_dfm)
 
 
-# 
-model_prevalence_is_spline <-
+
+
+
+model_prevalence_years_k_20 <-
   stm(
     documents = hansard_stm$documents,
     vocab = hansard_stm$vocab,
-    K = 100,
+    K = 20,
     prevalence =~ s(year),
+    data = hansard_stm$meta,
+    max.em.its = 75,
+    init.type = "Spectral"
+  )
+
+model_prevalence_years_k_20_elections <-
+  stm(
+    documents = hansard_stm$documents,
+    vocab = hansard_stm$vocab,
+    K = 20,
+    prevalence =~ s(year) + electionCounter,
+    data = hansard_stm$meta,
+    max.em.its = 75,
+    init.type = "Spectral"
+  )
+
+model_prevalence_years_k_20_governmentChangeDate <-
+  stm(
+    documents = hansard_stm$documents,
+    vocab = hansard_stm$vocab,
+    K = 20,
+    prevalence =~ s(year) + governmentChangeDate,
+    data = hansard_stm$meta,
+    max.em.its = 75,
+    init.type = "Spectral"
+  )
+
+
+model_prevalence_years_k_20_economicEvents <-
+  stm(
+    documents = hansard_stm$documents,
+    vocab = hansard_stm$vocab,
+    K = 20,
[…]

### 2018-09-29 outputs/docs/events/svm-rmarkdown-article-example.Rmd
GET TO DRAFT STAGE HOORAY

--- 2018-09-27 outputs/docs/events/svm-rmarkdown-article-example.Rmd
@@
 We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
-We then examine the effect of various events using a simple discrete choice model.
+We then examine the effect of various events.
 We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects.
@@
 
+yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
+  replace_na(list(Parliament = ""))
 elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
@@
 keyOtherDates <- read_csv(here::here("inputs/misc/key_dates-other.csv"), col_types = cols())
+significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
 
@@
 We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
-We then use a discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
+We then examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments. 
-Our use of a discrete choice model allows us construct a counterfactual.
+<!-- Our use of a discrete choice model allows us to construct a counterfactual.  -->
 Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
@@
 ## Parliamentary text data
-Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Hansard records and their equivalents are an increasingly popular source of data as new methods and reduced computational costs make larger-scale analysis easier.
-For instance, the digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @Whyte2017 to examine whether parliamentary disruptions in Canada increased between 1926 and 2015 and @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
+Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012 or **[ANOTHER REFERENCE - Maybe Frank Fisher 'Reframing Public Policy'?]**, often examined broader activity measures such as counts of sitting days.
+This allowed for long time frames and wide comparisons.
+But analysing Hansard records and their equivalents directly are an increasingly viable and popular source of data as new methods and reduced computational costs make larger-scale analysis easier, complementing other measures.
+
+The digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
 In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
+And as digitisation methods improve older UK records can be analysed, for instance @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
 In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
@@
 An example of what a page of Hansard looks like is included in Appendix **[ADD NUMBERING]**.
-There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table 1) **[UPDATE NUMBERING]**.
-As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in Appendix **[ADD NUMBERING]**.
+There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table \ref{tab:yearsusedtable}) **[UPDATE NUMBERING]**.
+As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in Appendix **[ADD NUMBERING]**.[^2]
 
@@
 
-| Parliament       | House                    | Years used | Number of records |
-|:------|-----:|---------:|------:|
-| Commonwealth      | House of Representatives  | 1901 - 2017 | 7,873 |
-|                   | Senate                    | 1901 - 2017 | **[TBD]** |
-| Queensland        | Legislative Assembly      | 1860 - 2017 | 9,699 |
-|                   | Legislative Council       | 1860 - 1922 | 4,156 |
-| New South Wales[^2]   | Legislative Assembly  | 1856 - 2017 | **[TBD]** |
-|                   | Legislative Council       | 1856 - 2017 | **[TBD]** |
-| Victoria          | Legislative Assembly      | 1856 - 2017 | **[TBD]** |
-|                   | Legislative Council       | 1851 - 2017 | **[TBD]** |
-| Tasmania          | House of Assembly         | 1856 - 2017 | **[TBD]** |
-|                   | Legislative Council       | 1856 - 2017 | **[TBD]** |
-| South Australia   | House of Assembly         | 1857 - 2017 | **[TBD]** |
-|                   | Legislative Council       | 1840 - 2017 | **[TBD]** |
-| Western Australia | Legislative Assembly      | 1890 - 2017 | **[TBD]** |
-|                   | Legislative Council       | 1832 - 2017 | **[TBD]** |
+```{r yearsusedtable, echo = FALSE, results = 'asis'}
+
+yearsUsed %>%
+  kable(
+    booktabs = T,
+    align = c('l', 'r', 'r', 'r'),
+    caption = "Hansard records used") %>%
+  kable_styling(font_size = 12)
+
+```
 
@@
 These errors are fixed when they occur at scale and can be identified.
+One way to provide assurance that mistakes in older records are not driving the results is to analyse the percentage of stop-words in each record over time.
+This details of this are provided in Appendix **[ADD NUMBERING]** and suggest that there is no significant difference in the quality of the parsing over time.
 The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
 
-[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in Appendix **[ADD NUMBERING]**. The full set of scripts are available on request.
+[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in Appendix **[ADD NUMBERING]**.
 
-These daily records are the main data used in this paper, however the daily records are also further divided into individual-level records.
+These daily records are the main level at which we consider the data in this paper, but the daily records are also further divided into individual-level records.
 Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
-Interjections are interesting in their own right, for instance @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs, but do not usually contribute much to defining the topics being discussed.
+The high dimensional nature of text data means that the appropriate analysis data are research-question specific and datasets need to be tidied toward that.
+For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
+But they are interesting in their own right and @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs.
 
 Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
-For instance, when the Hansard record is trying to indicate that a person is speaking, as opposed to being mentioned (for more on the political effect of being mentioned see @Alexander2018), often the name is in upper case (e.g.
-'Mr WHITLAM' or 'Mr MENZIES'); followed by a dash or colon; or are next to some title within brackets.
+For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned (for more on the political effect of being mentioned see @Alexander2018), often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
 There is substantial variation in how the person making a statement is identified.
-Again some error is introduced at this stage because of inconsistencies over time and between the parliaments, as well as the errors introduced during the PDF parsing stage.
+Again some error is introduced at this stage because of inconsistencies over time and between the parliaments.
 There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.
@@
 **[Need to bundle_ngrams i.e.
-olive oil is olive_oil]**
+New Zealand is new_zealand.]**
 
@@
 For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
-Also non-Hansard information about the politicians can inform the analysis.
+Also non-Hansard information about the politicians informs our analysis.
 This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.
@@
 The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
-However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData]
+However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData] The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
 
-[^seeMyAdditionalData]: An example of the additional information is provided in Appendix **[ADD NUMBERING]**. The datasets are available on request.
+[^seeMyAdditionalData]: An example of the additional information is provided in Appendix **[ADD NUMBERING]**.
 
 # Model
-The main models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.
-In theory we could have directly used the text as an input to the discrete choice model, but this quickly becomes intractable due to computer memory and storage constraints.
-Instead, in a similar way to @MuellerRauh2018, we use the topics that the text is about as an input to another model, which in our case is a discrete choice model.
+The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. 
+<!-- and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.  -->
+In a similar way to @MuellerRauh2018, we use these topics to analyse the effect of various events.
 In Appendix **[ADD NUMBERING]**, we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
@@
 In this section we provide a brief overview of both the LDA model and the STM.
-we consider the outputs of the topic model as reduced dimension inputs.
-In our case they are inputs to a discrete choice model, and so we then discuss that model.
+We consider the outputs of the topic model as reduced dimension inputs that can be analysed.
+<!-- within another model. In our case they are inputs to a discrete choice model, and so we then discuss that model. -->
 
@@
 More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics.
-For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
-
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
-
-tibble(
-  Topics = rep(c("1", "2", "3", "4", "5"), 2),
-  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
-  Document = c(rep("Document 1", 5), rep("Document 2", 5))
-  ) %>%
-  ggplot(aes(Topics, Probability, colour = Document)) +
-  geom_point() +
-  theme_classic() +
-  coord_flip()  +
-  scale_colour_viridis_d()
-
-```
-
 Similarly, each topic could be considered a probability distribution over terms.
 To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion.
-For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
-
-```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
-tibble(
-  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
-  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
-  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
-  ) %>%
-  ggplot(aes(Terms, Probability, colour = Topics)) +
-  geom_point() +
-  theme_classic() +
-  coord_flip() +
-  scale_colour_viridis_d()
-
-```
+Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix **[ADD NUMBERING]** illustrates an example with five topics, two documents, and ten terms.
 
@@
 
-The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'.
+<!-- The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'.
 These are words that are common, but that don't typically help to define topics.
@@
 This is essentially a table with a column of the number of times each term appears in each document.
+-->
 
-After the dataset is ready, the R \texttt{topicmodels} package of @Grun2011 can be used to implement LDA and approximate the posterior.
-It can do this using Gibbs sampling or the variational expectation-maximization algorithm.
-Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
-Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.
-7).
-It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.
-6):
-$$p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} $$
-where $z'_{d, n}$ refers to all other topic assignments; $\lambda'_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$; $\lambda'_{.\rightarrow k}$ is a count of how many other times that any term has been assigned to topic $k$; $\lambda'^{(d)}_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$ in that particular document; and $\lambda'^{(d)}_{-i}$ is a count of how many other times that term has been assigned in that document.
-Once $z_{d,n}$ has been estimated, then estimates for the distribution of words into topics and topics into documents can be backed out.
+<!-- After the dataset is ready, the R \texttt{topicmodels} package of @Grun2011 can be used to implement LDA and approximate the posterior.  -->
 
-This conditional distribution assigns topics depending on how often a term has been assigned to that topic previously, and how common the topic is in that document (@SteyversGriffiths2006).
-The initial random allocation of topics means that the results of early passes through the corpus of document are poor, but given enough time the algorithm converges to an appropriate estimate.
-
-The choice of the number of topics, *k*, affects the results, and must be specified *a priori*.
+Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior.
+A summary of these approaches is provided in Appendix **[ADD NUMBERING]**.
+The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
 If there is a strong reason for a particular number, then this can be used.
-Otherwise, one way to choose an appropriate number is to use a test and training set process.
-Essentially, this means running the process on a variety of possible values for *k* and then picking an appropriate value that performs well.
+Otherwise, one way to choose an appropriate number is to use cross validation.
 
@@
 In the case of Hansard, we know who was speaking and the date they spoke.
-STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
+The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
 That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
@@
 The choice of the number of topics to use in the model is a situation-specific compromise.
-We use standard diagnostic techniques to decide on 80 **[UPDATE]** topics.
-More detail on this process is available in Appendix **[ADD NUMBERING]**.
+We use standard diagnostic techniques with cross validation to decide on 80 **[UPDATE AS APPROPRIATE]** topics.
+More detail on this selection process is available in Appendix **[ADD NUMBERING]**.
 
-The illustrate the output of an STM, Figure \@ref(fig:example_topics)) shows the estimated proportion of each day summarised by ten topics for the House of Representatives for 1901 through to 2017.
-**[RUN AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED.]**
+Figure \@ref(fig:exampletopics) illustrates an output of the STM.
+This illustrative model only considers data from the House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be allocated to one of ten topics and highlights how the prominence of these topics changes over time.
+**[RUN AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED FROM THE GENERAL ONE!.]**
 
-```{r example_topics, echo=FALSE, fig.cap="Estimated 10-topic-proportion", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
+```{r exampletopics, echo=FALSE, fig.cap="Estimated 10-topic-proportion", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/topics_example.png"))
 ```
-
-Note that each of the states and the Commonwealth are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.
 
@@
 Another would be to consider some type of multinomial logistic regression.
-Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which are commonly used in finance to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
+Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which can be used to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
 
+**[MONICA  - LOOK AT THESE OR OTHER OPTIONS AND DECIDE ON A WAY.
+NEEDS TO ALLOW FOR SHORT AND LONG RUN AND ALSO ALLOW COINCIDENCE OF EVENTS.
+WE ONLY CONSIDER 20 TOPICS BELOW, BUT THAT'S UNDERDONE AND THE METHODS NEED TO ALLOW FOR MORE.]**
+
+We currently consider events in two ways.
+The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
+This illustrates the differences between the topics.
+The second is by including incrementing variables in the prevalence metdata.
+This groups each day by events and we can then conduct significance tests.
+Unfortunately both of these do not consider short-term effects.
+
+**[Use tf-idf between them as illustrative instead? Use that other measure of difference?]**
 <!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.  -->
@@
 # Results
-## Political events
->*When you change the government, you change the country.* Paul Keating.
+We are interested in considering the effect of various events on what is talked about in Australia's parliaments.
+Each of those parliaments are treated independently here.
+Future work could expand the model to better understand, and allow, for correlation between them.
 
-Change of government.
+We consider four types of events and group the day's topic proportions by these events.
+One unfortunate effect of this is that we only allow an event to have a long-run effect and ignore short-run effects.
+Another is that we ignore coincidence of events.
 
-## Economic events
+Figure \@ref(fig:electionsevents) shows the grouping by election.
+If elections had significant effects on the discussion in parliament then there would be considerable change between groups.
+However changes generally appear to be longer-term rather than election to election.
 
-Major economic changes.
+```{r electionsevents, echo=FALSE, fig.cap="Topic proportions grouped by elections", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_election.png"))
+```
 
-[TBD]
+Figure \@ref(fig:governmentevents) shows the grouping by government.
+This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election.
+Similarly, John Howard's three terms are all considered the one government for our purposes.
 
-## Other events
->*Events, dear boy, events.* Attributed to Harold Macmillan.
+Here we see much more difference between adjacent events. This suggests that new governments tend to talk about different topics than the government they replace.
 
-Major event such as 9/11 attacks, or economic change.
+```{r governmentevents, echo=FALSE, fig.cap="Topic proportions grouped by government", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_government_change.png"))
+```
+
+Figure \@ref(fig:economicevents) shows the grouping by major economic changes. There are considerable changes between adjacent events.
+
+```{r economicevents, echo=FALSE, fig.cap="Topic proportions grouped by economic events", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_economic_changes.png"))
+```
+
+Figure \@ref(fig:otherevents) shows the grouping by major other events, such as the 9/11 attacks.
+
+```{r otherevents, echo=FALSE, fig.cap="Topic proportions grouped by other events", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_other_changes.png"))
+```
+
+Another way to consider the effect of events is by including incrementing variables in the prevelance metadata.
+This then gets included in the topic modelling and the significance to each topic can be computed.
+Table \@ref(tab:dodgysignificances) summarises these by the type of dummy and the topic.
+At the five per cent level the events that we consider were significant for eight topics.
+This significance tended to be correlated, especially for economic and other events.
+
+```{r dodgysignificances, echo = FALSE, results = 'asis'}
+
+significances %>% 
+  kable(booktabs = T, caption = "Significance of dummy") %>%
+  kable_styling(font_size = 12)
+
+```
+
+For instance, all of the incrementing variables have a significant effect on the prevalence of Topic 1.
+Table \@ref(tab:topwordssig) shows that this has to do with tariffs and trade.
+On the other hand, Topic 2 has to do with aspects of daily life such as community and children, and Topic 3 has to do with legal issues and neither is significant.
+This is not surprising given the centrality of these concerns at all times.
+
+```{r topwordssig, echo = FALSE, results = 'asis'}
+
+top_words %>% 
+  kable(booktabs = T, caption = "Top words for each topic") %>%
+  kable_styling(font_size = 12)
+
+```
 
 # Summary and conclusions
-In this paper we examined
+In this paper we examined what was said in Australia's parliaments.
+We downloaded and parsed PDFs for Australian states and federal parliaments.
+We then used a text model to group the discussions into topics and analysed the effect of various events on the distribution of the discussion.
 
-What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.
+In general we found that changes in government changed the distribution of topics discussed in parliament, but that elections did not.
+We found that significant events such as 9/11 had substantial and lasting changes, but that with certain exceptions, economic events did not.
 
@@
 
-Future work - examine how it changed during Federation
+<!-- What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation. -->
 
 \newpage
+
+# (APPENDIX) Appendix {-}
 
@@
 
-```{r, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+Figure \@ref(fig:asdf)
+
+```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
 knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
@@
 
+## Topic modelling example and details
+### Examples
+For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
+
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
+
+tibble(
+  Topics = rep(c("1", "2", "3", "4", "5"), 2),
+  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
+  Document = c(rep("Document 1", 5), rep("Document 2", 5))
+  ) %>%
+  ggplot(aes(Topics, Probability, colour = Document)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip()  +
+  scale_colour_viridis_d()
+
+```
+
+For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
+
+```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
+tibble(
+  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
+  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
+  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
+  ) %>%
+  ggplot(aes(Terms, Probability, colour = Topics)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip() +
+  scale_colour_viridis_d()
+
+```
+
+### Solution details
+Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
+Broadly, it does this by first assigning every term in every document to a random topic, specified by Dirichlet priors with $\alpha = \frac{50}{K}$ and $\eta = 0.1$  (@SteyversGriffiths2006 recommends $\eta = 0.01$), where $\alpha$ refers to the distribution over topics and $\eta$ refers to the distribution over terms (@Grun2011, p.
+7).
+It then selects a particular term in a particular document and assigns it to a new topic based on the conditional distribution where the topics for all other terms in all documents are taken as given (@Grun2011, p.
+6):
+$$p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} $$
+where $z'_{d, n}$ refers to all other topic assignments; $\lambda'_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$; $\lambda'_{.\rightarrow k}$ is a count of how many other times that any term has been assigned to topic $k$; $\lambda'^{(d)}_{n\rightarrow k}$ is a count of how many other times that term has been assigned to topic $k$ in that particular document; and $\lambda'^{(d)}_{-i}$ is a count of how many other times that term has been assigned in that document.
+Once $z_{d,n}$ has been estimated, then estimates for the distribution of words into topics and topics into documents can be backed out.
+
+This conditional distribution assigns topics depending on how often a term has been assigned to that topic previously, and how common the topic is in that document (@SteyversGriffiths2006).
+The initial random allocation of topics means that the results of early passes through the corpus of document are poor, but given enough time the algorithm converges to an appropriate estimate.
+
 ## Selection of number of topics
@@
 
-```{r economicevents, echo = FALSE, results = 'asis'}
+```{r economics, echo = FALSE, results = 'asis'}
 
@@
 
-```{r otherevents, echo = FALSE, results = 'asis'}
+```{r others, echo = FALSE, results = 'asis'}
 

### 2018-09-29 outputs/docs/events/svm-rmarkdown-article-example.tex
GET TO DRAFT STAGE HOORAY

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 28
+Cochrane for their helpful suggestions. \textbf{Version as of}: 29
 September 2018; \textbf{comments welcome}:
@@
 such as correlation between days and changes over time. We then examine
-the effect of various events using a simple discrete choice model. We
-find that: 1) changes of government are associated with topic changes
-only when there is also a change of the party in power; and 2) economic
-events, such as financial crises, have significant and persistent
-effects. Our findings have implications for how we think about the
-longer-term trajectory of government policy as the media cycle becomes
-increasingly focused on short-term events.
+the effect of various events. We find that: 1) changes of government are
+associated with topic changes only when there is also a change of the
+party in power; and 2) economic events, such as financial crises, have
+significant and persistent effects. Our findings have implications for
+how we think about the longer-term trajectory of government policy as
+the media cycle becomes increasingly focused on short-term events.
 
@@
 for dimensionality reduction and to impose structure such as correlation
-between days and changes over time. We then use a discrete choice model
-to examine changes at various types of events, including: changes in
-government; changes in the political environment (as defined by polling
-or other results); changes in economic conditions; and other significant
-events (such as the 9/11 attacks or the Bali bombings).
+between days and changes over time. We then examine changes at various
+types of events, including: changes in government; changes in the
+political environment (as defined by polling or other results); changes
+in economic conditions; and other significant events (such as the 9/11
+attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale
-parliamentary text records from multiple Australian parliaments. Our use
-of a discrete choice model allows us construct a counterfactual. Our
+parliamentary text records from multiple Australian parliaments. Our
 work fits into a growing literature that considers text as an input to
@@
 the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
-\textbf{{[}ANOTHER REFERENCE{]}}, often examined broader activity
-measures. This allowed for long time frames and wide comparisons. But
-Hansard records and their equivalents are an increasingly viable and
-popular source of data as new methods and reduced computational costs
-make larger-scale analysis easier.
+\textbf{{[}ANOTHER REFERENCE - Maybe Frank Fisher `Reframing Public
+Policy'?{]}}, often examined broader activity measures such as counts of
+sitting days. This allowed for long time frames and wide comparisons.
+But analysing Hansard records and their equivalents directly are an
+increasingly viable and popular source of data as new methods and
+reduced computational costs make larger-scale analysis easier,
+complementing other measures.
 
 The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
-\citet{Whyte2017} to examine whether parliamentary disruptions in Canada
-increased between 1926 and 2015 and \citet{RheaultCochran2018} to
-examine ideology and party polarisation in Britain and Canada. In the
-UK, \citet{Duthie2016} analysed Hansard records to examine which
-politicians made supportive or aggressive statements toward other
-politicians between 1979 and 1990 and \citet{PetersonSpirling2018}
-examined polarisation. As digitisation methods improve increasingly
-older UK records can be analysed, for instance \citet{Dimitruk2018}
-considers the effect of estate bills on prorogations in seventeenth
-century England. In New Zealand, \citet{Curran2017} modelled the topics
-discussed between 2003 and 2016, and \citet{Graham2016} examined
-unparliamentary language between 1890 and 1950. And in the US
-\citet{GentzkowShapiroTaddy2018} examine congressional speech records
-from 1873 to 2016 to find that partisanship has risen in the past few
-decades.
+\citet{RheaultCochran2018} to examine ideology and party polarisation in
+Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
+records to examine which politicians made supportive or aggressive
+statements toward other politicians between 1979 and 1990 and
+\citet{PetersonSpirling2018} examined polarisation. And as digitisation
+methods improve older UK records can be analysed, for instance
+\citet{Dimitruk2018} considers the effect of estate bills on
+prorogations in seventeenth century England. In New Zealand,
+\citet{Curran2017} modelled the topics discussed between 2003 and 2016,
+and \citet{Graham2016} examined unparliamentary language between 1890
+and 1950. And in the US \citet{GentzkowShapiroTaddy2018} examine
+congressional speech records from 1873 to 2016 to find that partisanship
+has risen in the past few decades.
 
@@
 There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
-available across the state and federal parliaments (Table 1)
-\textbf{{[}UPDATE NUMBERING{]}}. As with any larger-scale data process,
-there are various issues with some of the PDFs and the known ones are
-detailed in Appendix \textbf{{[}ADD NUMBERING{]}}.
-
-\begin{longtable}[]{@{}lrrr@{}}
-\toprule
-Parliament & House & Years used & Number of records\tabularnewline
-\midrule
-\endhead
-Commonwealth & House of Representatives & 1901 - 2017 &
-7,873\tabularnewline
-& Senate & 1901 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Queensland & Legislative Assembly & 1860 - 2017 & 9,699\tabularnewline
-& Legislative Council & 1860 - 1922 & 4,156\tabularnewline
-New South Wales\footnote{The NSW Legislative Council was established
+available across the state and federal parliaments (Table
+\ref{tab:yearsusedtable}) \textbf{{[}UPDATE NUMBERING{]}}. As with any
+larger-scale data process, there are various issues with some of the
+PDFs and the known ones are detailed in Appendix \textbf{{[}ADD
+NUMBERING{]}}.\footnote{The NSW Legislative Council was established
   earlier than 1856, however the earlier Hansard records have not been
@@
   \citet{Ooms2018tesseract} provided useful data and these could be used
-  in the future.} & Legislative Assembly & 1856 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Victoria & Legislative Assembly & 1856 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1851 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Tasmania & House of Assembly & 1856 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1856 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-South Australia & House of Assembly & 1857 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1840 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
-Western Australia & Legislative Assembly & 1890 - 2017 &
-\textbf{{[}TBD{]}}\tabularnewline
-& Legislative Council & 1832 - 2017 & \textbf{{[}TBD{]}}\tabularnewline
+  in the future.}
+
+\begin{table}
+
+\caption{\label{tab:yearsusedtable}Hansard records used}
+\centering
+\fontsize{12}{14}\selectfont
+\begin{tabular}[t]{lrrr}
+\toprule
+Parliament & House & Years used & Number of records\\
+\midrule
+Commonwealth & House of Representatives & 1901 - 2017 & 7873\\
+ & Senate & 1901 - 2017 & TBD\\
+Queensland & Legislative Assembly & 1860 - 2017 & 9699\\
+ & Legislative Council & 1860 - 1922 & 4156\\
+New South Wales & Legislative Assembly & 1856 - 2017 & TBD\\
+\addlinespace
+ & Legislative Council & 1856 - 2017 & TBD\\
+Victoria & Legislative Assembly & 1856 - 2017 & TBD\\
+ & Legislative Council & 1851 - 2017 & TBD\\
+Tasmania & House of Assembly & 1856 - 2017 & TBD\\
+ & Legislative Council & 1856 - 2017 & TBD\\
+\addlinespace
+South Australia & House of Assembly & 1857 - 2017 & TBD\\
+ & Legislative Council & 1840 - 2017 & TBD\\
+Western Australia & Legislative Assembly & 1890 - 2017 & TBD\\
+ & Legislative Council & 1832 - 2017 & TBD\\
 \bottomrule
-\end{longtable}
+\end{tabular}
+\end{table}
 
@@
   reduced-detail scripts are provided in Appendix \textbf{{[}ADD
-  NUMBERING{]}}. The full set of scripts are available on request.}
-These scripts are primarily based on: the \texttt{PDFtools} package of
-\citet{Ooms2018pdftools}; the \texttt{tidyverse} package of
-\citet{Wickham2017}; the \texttt{tm} package of
-\citet{FeinererHornik2018}; the \texttt{lubridate} package of
+  NUMBERING{]}}.} These scripts are primarily based on: the
+\texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
+\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
+package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
 \citet{GrolemundWickham2011}; and the \texttt{stringi} package of
@@
 that `the' is often parsed as `thc'. These errors are fixed when they
-occur at scale and can be identified. The \texttt{hunspell} package of
-\citet{Ooms2017} is also used to help find spelling issues.
-
-These daily records are the main data used in this paper, however the
-daily records are also further divided into individual-level records.
-Sometimes these are just short interjections or notes that are not
-specific to any particular politician, such as `Honourable members
-interjecting'. The high dimensional nature of text data means that the
-appropriate analysis dataset is research-question specific. For
-instance, in our paper interjections are not important because they do
-not usually contribute much to defining the topics being discussed. But
-they are interesting in their own right and \citet{Whyte2017} analysed
-them in a Canadian context for the period 1926 to 2015 to find that
-female MPs were more likely to be interrupted than male MPs.
+occur at scale and can be identified. One way to provide assurance that
+mistakes in older records are not driving the results is to analyse the
+percentage of stop-words in each record over time. This details of this
+are provided in Appendix \textbf{{[}ADD NUMBERING{]}} and suggest that
+there is no significant difference in the quality of the parsing over
+time. The \texttt{hunspell} package of \citet{Ooms2017} is also used to
+help find spelling issues.
+
+These daily records are the main level at which we consider the data in
+this paper, but the daily records are also further divided into
+individual-level records. Sometimes these are just short interjections
+or notes that are not specific to any particular politician, such as
+`Honourable members interjecting'. The high dimensional nature of text
+data means that the appropriate analysis data are research-question
+specific and datasets need to be tidied toward that. For instance, in
+our paper interjections are not important because they do not usually
+contribute much to defining the topics being discussed. But they are
+interesting in their own right and \citet{Whyte2017} analysed them in a
+Canadian context for the period 1926 to 2015 to find that female MPs
+were more likely to be interrupted than male MPs.
 
@@
 identifying politicians' names in particular patterns. For instance,
-when the Hansard record is trying to indicate that a person is speaking,
-as opposed to being mentioned (for more on the political effect of being
-mentioned see \citet{Alexander2018}), often the name is in upper case
-(e.g. `Mr WHITLAM' or `Mr MENZIES'); followed by a dash or colon; or are
-next to some title within brackets. There is substantial variation in
-how the person making a statement is identified. Again some error is
-introduced at this stage because of inconsistencies over time and
-between the parliaments, as well as the errors introduced during the PDF
-parsing stage. There is considerable variance but on average each daily
-record had 250 \textbf{{[}UPDATE{]}} individual-level records, resulting
-in roughly 15 million rows \textbf{{[}UPDATE{]}} across the state and
-federal parliaments.
+when Hansard is indicating that a particular person is speaking, as
+opposed to being mentioned (for more on the political effect of being
+mentioned see \citet{Alexander2018}), often the name is in upper case,
+for instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon;
+or are next to some title within brackets. There is substantial
+variation in how the person making a statement is identified. Again some
+error is introduced at this stage because of inconsistencies over time
+and between the parliaments. There is considerable variance but on
+average each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
+records, resulting in roughly 15 million rows \textbf{{[}UPDATE{]}}
+across the state and federal parliaments.
 
@@
 the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
-\textbf{{[}Need to bundle\_ngrams i.e.~olive oil is olive\_oil{]}}
+\textbf{{[}Need to bundle\_ngrams i.e.~New Zealand is new\_zealand.{]}}
 
@@
 are contained in Hansard records they are inconsistent. Also non-Hansard
-information about the politicians can inform the analysis. This
-includes: date of birth and date of death; sex; date of entry to
-parliament and exit from parliament; some aspects of their pre- and
-post-parliamentary career; some aspects of their parliamentary career,
-such as ministry appointments; and electoral information such as primary
-and two-party-preferred results.
+information about the politicians informs our analysis. This includes:
+date of birth and date of death; sex; date of entry to parliament and
+exit from parliament; some aspects of their pre- and post-parliamentary
+career; some aspects of their parliamentary career, such as ministry
+appointments; and electoral information such as primary and
+two-party-preferred results.
 
@@
 Biography and Wikipedia.\footnote{An example of the additional
-  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The
-  datasets are available on request.}
+  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}.} The
+source for the electoral results is the Australian Electoral Commission
+and Adam Carr's Australian Election Archive.
 
@@
 
-The main models that we use in this paper are the Structural Topic Model
+The main model that we use in this paper is the Structural Topic Model
 (STM) as implemented by the \texttt{stm} R package of
-\citet{RobertsStewartAiroldiRPackage}, and a discrete choice model as
-implemented by the \texttt{XXXX} R package of \textbf{XYZ}. In theory we
-could have directly used the text as an input to the discrete choice
-model, but this can become intractable. Instead, in a similar way to
-\citet{MuellerRauh2018}, we use the topics that the text is about as an
-input to another model, which in our case is a discrete choice model. In
-Appendix \textbf{{[}ADD NUMBERING{]}}, we include an alternative
-approach that follows \citet{Taddy2015} by using word2vec, which more
-closely uses words, rather than topics, as an input.
+\citet{RobertsStewartAiroldiRPackage}. In a similar way to
+\citet{MuellerRauh2018}, we use these topics to analyse the effect of
+various events. In Appendix \textbf{{[}ADD NUMBERING{]}}, we include an
+alternative approach that follows \citet{Taddy2015} by using word2vec,
+which more closely uses words, rather than topics, as an input.
 
@@
 \citet{Blei2003latent}. In this section we provide a brief overview of
-both the LDA model and the STM. we consider the outputs of the topic
-model as reduced dimension inputs. In our case they are inputs to a
-discrete choice model, and so we then discuss that model.
+both the LDA model and the STM. We consider the outputs of the topic
+model as reduced dimension inputs that can be analysed.
 
@@
 LDA topic model works by considering each document as having been
-generated by some probability distribution over topics. For instance, if
-there were five topics and two documents, then the first document may be
-comprised mostly of the first few topics; the other document may be
-mostly about the final few topics (Figure
-\ref{fig:topicsoverdocuments}).
-
-\begin{figure}
-\centering
-\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
-\caption{\label{fig:topicsoverdocuments}Probability distributions over
-topics for two documents}
-\end{figure}
-
-Similarly, each topic could be considered a probability distribution
-over terms. To choose the terms used in each document the speaker picks
-terms from each topic in the appropriate proportion. For instance, if
-there were ten terms, then one topic could be defined by giving more
-weight to terms related to immigration; and some other topic may give
-more weight to terms related to the economy (Figure
-\ref{fig:topicsoverterms}).
-
-\begin{figure}
-\centering
-\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1.pdf}
-\caption{\label{fig:topicsoverterms}Probability distributions over terms}
-\end{figure}
+generated by some probability distribution over topics. Similarly, each
+topic could be considered a probability distribution over terms. To
+choose the terms used in each document the speaker picks terms from each
+topic in the appropriate proportion. Figures
+\ref{fig:topicsoverdocuments} and \ref{fig:topicsoverterms} in Appendix
+\textbf{{[}ADD NUMBERING{]}} illustrates an example with five topics,
+two documents, and ten terms.
 
@@
 
-The initial practical step when implementing LDA given a collection of
-documents is to remove `stop words'. These are words that are common,
-but that don't typically help to define topics. There is a common list
-of stop words such as: ``a''; ``an''; and ``and''. However the exact
-list used depends on research of focus. In the case of Australian
-Hansard, these are words such as: ``australia''; ``australian''; and
-``bill''. Punctuation and capitalisation is also typically removed. The
-documents then need to then be transformed into a document-term-matrix.
-This is essentially a table with a column of the number of times each
-term appears in each document.
-
-After the dataset is ready, the R \texttt{topicmodels} package of
-\citet{Grun2011} can be used to implement LDA and approximate the
-posterior. It can do this using Gibbs sampling or the variational
-expectation-maximization algorithm. Following
-\citet{SteyversGriffiths2006} and \citet{Darling2011}, the Gibbs
-sampling process attempts to find a topic for a particular term in a
-particular document, given the topics of all other terms for all other
-documents. Broadly, it does this by first assigning every term in every
-document to a random topic, specified by Dirichlet priors with
-\(\alpha = \frac{50}{K}\) and \(\eta = 0.1\)
-(\citet{SteyversGriffiths2006} recommends \(\eta = 0.01\)), where
-\(\alpha\) refers to the distribution over topics and \(\eta\) refers to
-the distribution over terms (\citet{Grun2011}, p.~7). It then selects a
-particular term in a particular document and assigns it to a new topic
-based on the conditional distribution where the topics for all other
-terms in all documents are taken as given (\citet{Grun2011}, p.~6):
-\[p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} \]
-where \(z'_{d, n}\) refers to all other topic assignments;
-\(\lambda'_{n\rightarrow k}\) is a count of how many other times that
-term has been assigned to topic \(k\); \(\lambda'_{.\rightarrow k}\) is
-a count of how many other times that any term has been assigned to topic
-\(k\); \(\lambda'^{(d)}_{n\rightarrow k}\) is a count of how many other
-times that term has been assigned to topic \(k\) in that particular
-document; and \(\lambda'^{(d)}_{-i}\) is a count of how many other times
-that term has been assigned in that document. Once \(z_{d,n}\) has been
-estimated, then estimates for the distribution of words into topics and
-topics into documents can be backed out.
-
-This conditional distribution assigns topics depending on how often a
-term has been assigned to that topic previously, and how common the
-topic is in that document (\citet{SteyversGriffiths2006}). The initial
-random allocation of topics means that the results of early passes
-through the corpus of document are poor, but given enough time the
-algorithm converges to an appropriate estimate.
-
-The choice of the number of topics, \emph{k}, affects the results, and
-must be specified \emph{a priori}. If there is a strong reason for a
-particular number, then this can be used. Otherwise, one way to choose
-an appropriate number is to use a test and training set process.
-Essentially, this means running the process on a variety of possible
-values for \emph{k} and then picking an appropriate value that performs
-well.
+Gibbs sampling or the variational expectation-maximization algorithm can
+be used to approximate the posterior. A summary of these approaches is
+provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The choice of the
+number of topics, \emph{k}, drives the results and must be specified
+\emph{a priori}. If there is a strong reason for a particular number,
+then this can be used. Otherwise, one way to choose an appropriate
+number is to use cross validation.
 
@@
 created. In the case of Hansard, we know who was speaking and the date
-they spoke. STM allows this additional information to affect the
+they spoke. The STM allows this additional information to affect the
 construction of topics, though influencing either topical prevalence or
@@
 to use in the model is a situation-specific compromise. We use standard
-diagnostic techniques to decide on 80 \textbf{{[}UPDATE{]}} topics. More
-detail on this process is available in Appendix \textbf{{[}ADD
-NUMBERING{]}}.
-
-The illustrate the output of an STM, Figure @ref(fig:example\_topics))
-shows the estimated proportion of each day summarised by ten topics for
-the House of Representatives for 1901 through to 2017. \textbf{{[}RUN
-AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED.{]}}
+diagnostic techniques with cross validation to decide on 80
+\textbf{{[}UPDATE AS APPROPRIATE{]}} topics. More detail on this
+selection process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.
+
+Figure \ref{fig:exampletopics} illustrates an output of the STM. This
+illustrative model only considers data from the House of Representatives
+between 1901 and 2017. It shows how each day's parliamentary discussion
+can be allocated to one of ten topics and highlights how the prominence
+of these topics changes over time. \textbf{{[}RUN AND GRAPH AN ACTUAL
+10-TOPIC MODEL - THESE DATA ARE JUST SUMMED FROM THE GENERAL ONE!.{]}}
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_example} \caption{Estimated 10-topic-proportion}(\#fig:example_topics)
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_example} \caption{Estimated 10-topic-proportion}\label{fig:exampletopics}
 \end{figure}
-
-Note that each of the states and the Commonwealth are treated
-independently here. Future work could expand the model to better
-understand, and allow, for correlation between them.
 
@@
 the time series nature of our data include: autoregressive moving
-average (ARMA) models which are commonly used in finance to test for
-structural breaks \textbf{{[}REFERENCE?{]}}; or splines could be fit
-with specific knot placements and then cross validation used to compare
-the RSS with a more general splines model.
+average (ARMA) models which can be used to test for structural breaks
+\textbf{{[}REFERENCE?{]}}; or splines could be fit with specific knot
+placements and then cross validation used to compare the RSS with a more
+general splines model.
+
+\textbf{{[}MONICA - LOOK AT THESE OR OTHER OPTIONS AND DECIDE ON A WAY.
+NEEDS TO ALLOW FOR SHORT AND LONG RUN AND ALSO ALLOW COINCIDENCE OF
+EVENTS. WE ONLY CONSIDER 20 TOPICS BELOW, BUT THAT'S UNDERDONE AND THE
+METHODS NEED TO ALLOW FOR MORE.{]}}
+
+We currently consider events in two ways. The first is graphically,
+grouping each of the daily topic proportions by the events and isolating
+the topics. This illustrates the differences between the topics. The
+second is by including incrementing variables in the prevalence metdata.
+This groups each day by events and we can then conduct significance
+tests. Unfortunately both of these do not consider short-term effects.
+
+\textbf{{[}Use tf-idf between them as illustrative instead? Use that
+other measure of difference?{]}}
 
@@
 
-\subsection{Political events}\label{political-events}
-
-\begin{quote}
-\emph{When you change the government, you change the country.} Paul
-Keating.
-\end{quote}
-
-Change of election
+We are interested in considering the effect of various events on what is
+talked about in Australia's parliaments. Each of those parliaments are
+treated independently here. Future work could expand the model to better
+understand, and allow, for correlation between them.
+
+We consider four types of events and group the day's topic proportions
+by these events. One unfortunate effect of this is that we only allow an
+event to have a long-run effect and ignore short-run effects. Another is
+that we ignore coincidence of events.
+
+Figure \ref{fig:electionsevents} shows the grouping by election. If
+elections had significant effects on the discussion in parliament then
+there would be considerable change between groups. However changes
+generally appear to be longer-term rather than election to election.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_election} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-1}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_election} \caption{Topic proportions grouped by elections}\label{fig:electionsevents}
 \end{figure}
 
-Change of government
+Figure \ref{fig:governmentevents} shows the grouping by government. This
+can be different to election groupings, for instance, the change from
+the Rudd to Gillard governments happened without an election. Similarly,
+John Howard's three terms are all considered the one government for our
+purposes.
+
+Here we see much more difference between adjacent events. This suggests
+that new governments tend to talk about different topics than the
+government they replace.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_government_change} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-2}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_government_change} \caption{Topic proportions grouped by government}\label{fig:governmentevents}
 \end{figure}
 
-\subsection{Economic events}\label{economic-events}
-
-Major economic changes.
-
-Major change in economic conditions
+Figure \ref{fig:economicevents} shows the grouping by major economic
+changes. There are considerable changes between adjacent events.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_economic_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-3}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_economic_changes} \caption{Topic proportions grouped by economic events}\label{fig:economicevents}
 \end{figure}
 
-\subsection{Other events}\label{other-events}
-
-\begin{quote}
-\emph{Events, dear boy, events.} Attributed to Harold Macmillan.
-\end{quote}
-
-Major event such as 9/11 attacks, or economic change.
-
-Major other changes
+Figure \ref{fig:otherevents} shows the grouping by major other events,
+such as the 9/11 attacks.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/topics_separated_by_other_changes} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-4}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/2018-09-28-topics_separated_by_other_changes} \caption{Topic proportions grouped by other events}\label{fig:otherevents}
 \end{figure}
 
+Another way to consider the effect of events is by including
+incrementing variables in the prevelance metadata. This then gets
+included in the topic modelling and the significance to each topic can
+be computed. Table \ref{tab:dodgysignificances} summarises these by the
+type of dummy and the topic. At the five per cent level the events that
+we consider were significant for eight topics. This significance tended
+to be correlated, especially for economic and other events.
+
+\begin{table}
+
+\caption{\label{tab:dodgysignificances}Significance of dummy}
+\centering
+\fontsize{12}{14}\selectfont
+\begin{tabular}[t]{rrrrr}
+\toprule
+Topic & Elections & Governments & Economic & Other\\
+\midrule
+1 & 0.00 & 0.00 & 0.00 & 0.04\\
+2 & 0.50 & 0.69 & 0.15 & 0.64\\
+3 & 0.18 & 0.36 & 0.28 & 0.58\\
+4 & 0.90 & 0.20 & 0.00 & 0.00\\
+5 & 0.88 & 0.15 & 0.15 & 0.70\\
+\addlinespace
+6 & 0.41 & 0.00 & 0.21 & 0.20\\
+7 & 0.03 & 0.00 & 0.00 & 0.00\\
+8 & 0.61 & 0.39 & 0.00 & 0.00\\
+9 & 0.18 & 0.24 & 0.83 & 0.62\\
+10 & 0.99 & 0.34 & 0.96 & 0.41\\
+\addlinespace
+11 & 0.00 & 0.13 & 0.18 & 0.22\\
+12 & 0.03 & 0.02 & 0.06 & 0.27\\
+13 & 0.00 & 0.00 & 0.00 & 0.00\\
+14 & 0.01 & 0.37 & 0.22 & 0.28\\
+15 & 0.62 & 0.50 & 0.12 & 0.64\\
+\addlinespace
+16 & 0.74 & 0.00 & 0.00 & 0.00\\
+17 & 0.01 & 0.40 & 0.80 & 0.16\\
+18 & 0.23 & 0.00 & 0.00 & 0.00\\
+19 & 0.31 & 0.00 & 0.00 & 0.00\\
+20 & 0.00 & 0.54 & 0.09 & 0.35\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+For instance, all of the incrementing variables have a significant
+effect on the prevalence of Topic 1. Table \ref{tab:topwordssig} shows
+that this has to do with tariffs and trade. On the other hand, Topic 2
+has to do with aspects of daily life such as community and children, and
+Topic 3 has to do with legal issues and neither is significant. This is
+not surprising given the centrality of these concerns at all times.
+
+\begin{table}
+
+\caption{\label{tab:topwordssig}Top words for each topic}
+\centering
+\fontsize{12}{14}\selectfont
+\begin{tabular}[t]{rl}
+\toprule
+Topic & Top words\\
+\midrule
+1 & tariff, duties, trade, customs, protection, item, industries\\
+2 & community, life, children, family, australians, women, rights\\
+3 & court, industrial, union, law, trade, arbitration, workers\\
+4 & services, community, care, education, funding, health, school\\
+5 & joseph, connection, money, federal, sydney, officers, service\\
+\addlinespace
+6 & pension, health, medical, scheme, service, week, social\\
+7 & total, roads, wul, expenditure, road, budget, assistance\\
+8 & health, billion, business, electorate, senator, community, budget\\
+9 & united, world, nations, international, war, defence, foreign\\
+10 & bank, royal, private, control, broadcasting, banking, money\\
+\addlinespace
+11 & taxation, income, treasurer, revenue, money, land, financial\\
+12 & speaker, vote, motion, senate, election, standing, electoral\\
+13 & war, defence, service, british, ill, britain, soldiers\\
+14 & territory, oil, northern, line, shipping, ships, company\\
+15 & wheat, wool, primary, production, farmers, export, zealand\\
+\addlinespace
+16 & tion, business, ing, governments, issue, speaker, health\\
+17 & amendments, section, information, service, person, provisions, law\\
+18 & education, service, development, housing, capital, territory, services\\
+19 & speaker, deputy, petitioners, petition, ing, pray, citizens\\
+20 & budget, economic, hear, employment, unemployment, governments, economy\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \section{Summary and conclusions}\label{summary-and-conclusions}
 
-In this paper we examined
-
-What could happen if we had longer terms. Eg GST needed multiple
-generations of politicians but carbon tax couldn't because it was one
-generation.
+In this paper we examined what was said in Australia's parliaments. We
+downloaded and parsed PDFs for Australian states and federal
+parliaments. We then used a text model to group the discussions into
+topics and analysed the effect of various events on the distribution of
+the discussion.
+
+In general we found that changes in government changed the distribution
+of topics discussed in parliament, but that elections did not. We found
+that significant events such as 9/11 had substantial and lasting
+changes, but that with certain exceptions, economic events did not.
 
@@
 
-Future work - examine how it changed during Federation
-
 \newpage
 
+\appendix
+
 \section{Appendix}\label{appendix}
@@
 
+Figure \ref{fig:asdf}
+
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:unnamed-chunk-5}
+\includegraphics[width=1\linewidth]{/Users/rohanalexander/Documents/phd/hansard/outputs/figures/example_hansard_page} \caption{Example Hansard page - 6 February 1902}\label{fig:asdf}
 \end{figure}
@@
 
+\subsection{Topic modelling example and
+details}\label{topic-modelling-example-and-details}
+
+\subsubsection{Examples}\label{examples}
+
+For instance, if there were five topics and two documents, then the
+first document may be comprised mostly of the first few topics; the
+other document may be mostly about the final few topics (Figure
+\ref{fig:topicsoverdocuments}).
+
+\begin{figure}
+\centering
+\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverdocuments-1.pdf}
+\caption{\label{fig:topicsoverdocuments}Probability distributions over
+topics for two documents}
+\end{figure}
+
+For instance, if there were ten terms, then one topic could be defined
+by giving more weight to terms related to immigration; and some other
+topic may give more weight to terms related to the economy (Figure
+\ref{fig:topicsoverterms}).
+
+\begin{figure}
+\centering
+\includegraphics{svm-rmarkdown-article-example_files/figure-latex/topicsoverterms-1.pdf}
+\caption{\label{fig:topicsoverterms}Probability distributions over terms}
+\end{figure}
+
+\subsubsection{Solution details}\label{solution-details}
+
+Following \citet{SteyversGriffiths2006} and \citet{Darling2011}, the
+Gibbs sampling process attempts to find a topic for a particular term in
+a particular document, given the topics of all other terms for all other
+documents. Broadly, it does this by first assigning every term in every
+document to a random topic, specified by Dirichlet priors with
+\(\alpha = \frac{50}{K}\) and \(\eta = 0.1\)
+(\citet{SteyversGriffiths2006} recommends \(\eta = 0.01\)), where
+\(\alpha\) refers to the distribution over topics and \(\eta\) refers to
+the distribution over terms (\citet{Grun2011}, p.~7). It then selects a
+particular term in a particular document and assigns it to a new topic
+based on the conditional distribution where the topics for all other
+terms in all documents are taken as given (\citet{Grun2011}, p.~6):
+\[p(z_{d, n}=k | w_{1:D, 1:N}, z'_{d, n}) \propto \frac{\lambda'_{n\rightarrow k}+\eta}{\lambda'_{.\rightarrow k}+V\eta} \frac{\lambda'^{(d)}_{n\rightarrow k}+\alpha}{\lambda'^{(d)}_{-i}+K\alpha} \]
+where \(z'_{d, n}\) refers to all other topic assignments;
+\(\lambda'_{n\rightarrow k}\) is a count of how many other times that
+term has been assigned to topic \(k\); \(\lambda'_{.\rightarrow k}\) is
+a count of how many other times that any term has been assigned to topic
+\(k\); \(\lambda'^{(d)}_{n\rightarrow k}\) is a count of how many other
+times that term has been assigned to topic \(k\) in that particular
+document; and \(\lambda'^{(d)}_{-i}\) is a count of how many other times
+that term has been assigned in that document. Once \(z_{d,n}\) has been
+estimated, then estimates for the distribution of words into topics and
+topics into documents can be backed out.
+
+This conditional distribution assigns topics depending on how often a
+term has been assigned to that topic previously, and how common the
+topic is in that document (\citet{SteyversGriffiths2006}). The initial
+random allocation of topics means that the results of early passes
+through the corpus of document are poor, but given enough time the
+algorithm converges to an appropriate estimate.
+
 \subsection{Selection of number of
@@
 
-\caption{\label{tab:economicevents}Key economic events}
+\caption{\label{tab:economics}Key economic events}
 \centering
@@
 
-\caption{\label{tab:otherevents}Key other events}
+\caption{\label{tab:others}Key other events}
 \centering

### 2018-09-29 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -181,6 +181,7 @@ rm(tidy_hansard_reduced, hansard_corpus, docsTM, vocabTM, metaTM, hansard_dfm)
 
 
 
+
 model_prevalence_years_k_20 <-
   stm(
     documents = hansard_stm$documents,
@@ -238,40 +239,57 @@ model_prevalence_years_k_20_otherEvents <-
   )
 
 
+significance <- tibble(Topic = c(1:20))
 
-estimateEffect(
+elections <- estimateEffect(
   1:20 ~ electionCounter + s(year),
   model_prevalence_years_k_20_elections,
   meta = hansard_stm$meta,
   uncertainty = "Global") %>%
   tidy() %>%
-  filter(term == "electionCounter")
+  filter(term == "electionCounter") %>% 
+  select(`p.value`)
 
-estimateEffect(
+governments <- estimateEffect(
   1:20 ~ governmentChangeDate + s(year),
   model_prevalence_years_k_20_governmentChangeDate,
   meta = hansard_stm$meta,
   uncertainty = "Global") %>%
   tidy() %>%
-  filter(term == "governmentChangeDate")
+  filter(term == "governmentChangeDate") %>% 
+  select(`p.value`)
 
-estimateEffect(
+economic <- estimateEffect(
   1:20 ~ keyEconomicChange + s(year),
   model_prevalence_years_k_20_economicEvents,
   meta = hansard_stm$meta,
   uncertainty = "Global") %>%
   tidy() %>%
-  filter(term == "keyEconomicChange")
+  filter(term == "keyEconomicChange") %>% 
+  select(`p.value`)
 
-estimateEffect(
+other <- estimateEffect(
   1:20 ~ keyOtherChange + s(year),
   model_prevalence_years_k_20_otherEvents,
   meta = hansard_stm$meta,
   uncertainty = "Global") %>%
   tidy() %>%
-  filter(term == "keyOtherChange")
+  filter(term == "keyOtherChange") %>% 
+  select(`p.value`)
 
+significance_all <- cbind(significance, elections, governments, economic, other)
+head(significance)
+colnames(significance_all) <- c("Topic", "Elections", "Governments", "Economic", "Other")
+head(significance_all)
 
+significance_all <- significance_all %>% 
+  mutate(Elections = round(Elections, digits = 2),
+         Governments = round(Governments, digits = 2),
+         Economic = round(Economic, digits = 2),
+         Other = round(Other, digits = 2))
[…]

### 2018-09-30 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Improve paper

@@
     fig_caption: true
+    number_sections: true
     latex_engine: pdflatex
     template: svm-latex-ms.tex
-title: "Nobody expects the Spanish Inquisition: The effect of events on Australian parliamentary discussion"
+title: "The Effect of Events on Australian Parliamentary Discussion (1870--2017)"
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions.
@@
   affiliation: Australian National University
-abstract: "Government policy is partly driven by parliamentary discussion.
-Conversely, that same discussion can indicate a government's priorities.
-But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
-In this paper, we systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
-We compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
-We use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
-We then examine the effect of various events.
-We find that: 1) changes of government are associated with topic changes only when there is also a change of the party in power; and 2) economic events, such as financial crises, have significant and persistent effects.
+abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
+We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
+We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
+Finally, we examine the effect of various events using a Bayesian choice model.
+We find that: 1) elections are associated with topic changes only when the party in power changes but a change in government sometimes does not require this to be associated with topic changes; and 2) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorism.
 Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
@@
 top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
+missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
 
@@
 # Introduction
-New governments often go to some trouble to be different to the governments they replace.
-For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax.
+Government policy is partly driven by parliamentary discussion.
+Conversely, that same discussion can indicate a government's priorities.
+But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
+For instance, new governments often go to some trouble to be different to the governments they replace, such as Kevin Rudd's apology to Indigenous Australians not being supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax.
 Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
-However it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.
+But it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.
 
@@
 We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
-We then examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
+We then use a simple discrete choice model to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
-<!-- Our use of a discrete choice model allows us to construct a counterfactual.  -->
+Our use of a discrete choice model - essentially a time series multinomial model of choices - allows us to construct a counterfactual.
 Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
@@
 ## Parliamentary text data
-Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012 or **[ANOTHER REFERENCE - Maybe Frank Fisher 'Reframing Public Policy'?]**, often examined broader activity measures such as counts of sitting days.
+Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
 This allowed for long time frames and wide comparisons.
@@
 
-The digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
+The recent digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
 In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
@@
 Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
-An example of what a page of Hansard looks like is included in Appendix **[ADD NUMBERING]**.
-There is a more limited set of XML records available in some cases.[^XMLfootnote] There are 65,000 **[UPDATE]** Hansard records publicly available across the state and federal parliaments (Table \ref{tab:yearsusedtable}) **[UPDATE NUMBERING]**.
-As with any larger-scale data process, there are various issues with some of the PDFs and the known ones are detailed in Appendix **[ADD NUMBERING]**.[^2]
+Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
+There are 65,000 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
+Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
 
@@
 
-[^2]: The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper.
-However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
-
 The formatting of the Hansard records changes between the different parliaments and over time.
-We use R scripts to convert the PDFs into daily text records.[^seeMyScripts] These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
-The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+We use scripts written in R (@R2018) to convert the PDFs into daily text records.
+An example of the workflow and some reduced-detail scripts are provided in Appendix \@ref(hansardworkflow).
 Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
 An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are fixed when they occur at scale and can be identified.
-One way to provide assurance that mistakes in older records are not driving the results is to analyse the percentage of stop-words in each record over time.
-This details of this are provided in Appendix **[ADD NUMBERING]** and suggest that there is no significant difference in the quality of the parsing over time.
-The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
+These errors are corrected when they occur at scale and can be identified.
+The percentage of stop-words in each record is reasonably consistent over time.
+This suggests that there is no significant difference in the quality of the parsing over time.
+Details of this process are provided in Appendix \@ref(stopwordsgraph).
 
-[^seeMyScripts]: An example of the workflow and some reduced-detail scripts are provided in Appendix **[ADD NUMBERING]**.
-
-These daily records are the main level at which we consider the data in this paper, but the daily records are also further divided into individual-level records.
+These daily records are the main level that we consider in this paper, but we also disaggregated them into individual-level records during the cleaning process.
 Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
-The high dimensional nature of text data means that the appropriate analysis data are research-question specific and datasets need to be tidied toward that.
+The high dimensional nature of text data means that the appropriate level and focus of the dataset being analysed tends to be specific to a research question.
 For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
@@
 Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
-For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned (for more on the political effect of being mentioned see @Alexander2018), often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
+For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned, often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
 There is substantial variation in how the person making a statement is identified.
@@
 
-Text usually needs to be pre-processed before topic models can be used.
-The specific steps that we take are to remove numbers and punctuation and to change all the words to lower case.
+Text is usually pre-processed before topic models are used.
+The specific steps that we take are to remove numbers and punctuation and to change the words to lower case.
 Then the sentences are deconstructed and each word considered individually.
-In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
 **[Need to bundle_ngrams i.e.
@@
 ## Additional information
-Data from other sources are useful to complement the parliamentary text data.
+Data from other sources are needed to complement the parliamentary text data.
 For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
@@
 The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
-However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.[^seeMyAdditionalData] The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
-
-[^seeMyAdditionalData]: An example of the additional information is provided in Appendix **[ADD NUMBERING]**.
+However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.
+The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
+An example of the additional information is provided in Appendix \@ref(additionalinformation).
 
 # Model
-The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage. 
-<!-- and a discrete choice model as implemented by the \texttt{XXXX} R package of **XYZ**.  -->
-In a similar way to @MuellerRauh2018, we use these topics to analyse the effect of various events.
-In Appendix **[ADD NUMBERING]**, we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
+The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage and a Bayesian discrete choice model.
+In a similar way to @MuellerRauh2018, we use topics to analyse the effect of various events.
+In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
 
@@
 In this section we provide a brief overview of both the LDA model and the STM.
-We consider the outputs of the topic model as reduced dimension inputs that can be analysed.
-<!-- within another model. In our case they are inputs to a discrete choice model, and so we then discuss that model. -->
+We consider the outputs of the topic model as reduced dimension inputs that can be analysed within another model.
+In our case they are inputs to a discrete choice model, and so we then discuss that model.
 
@@
 To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion.
-Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix **[ADD NUMBERING]** illustrates an example with five topics, two documents, and ten terms.
+Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrates an example with five topics, two documents, and ten terms.
 
@@
 Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior.
-A summary of these approaches is provided in Appendix **[ADD NUMBERING]**.
+A summary of these approaches is provided in Appendix \@ref(LDAposteriorestimation).
 The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
@@
 The choice of the number of topics to use in the model is a situation-specific compromise.
-We use standard diagnostic techniques with cross validation to decide on 80 **[UPDATE AS APPROPRIATE]** topics.
-More detail on this selection process is available in Appendix **[ADD NUMBERING]**.
+We use standard diagnostic techniques with cross validation to decide on 80 **[UPDATE]** topics.
+More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
 
@@
 Other events are those such as the 9/11 attacks, or the Bali Bombing.
-The full list of events that we consider is detailed in Appendix **[ADD NUMBERING]**.
+The full list of events that we consider is detailed in Appendix @ref(eventdetails).
 
@@
 This illustrates the differences between the topics.
-The second is by including incrementing variables in the prevalence metdata.
-This groups each day by events and we can then conduct significance tests.
+The second is by including incrementing variables in the prevalence metadata This groups each day by events and we can then conduct significance tests.
 Unfortunately both of these do not consider short-term effects.
@@
 
-# Appendix
+# Hansard details
 
-## Example page
+## Hansard sources {#hansardsources}
+Where from?
+
+Which years are being used (not non-OCRd)
+
+[IS THIS BEING REFERENCED IN THE TEXT????]
+
+## Example Hansard page {#examplehansardpage}
 
@@
 
-## Document sources
-Where from?
+## Known Hansard issues {#knownhansardissues}
 
-Which years are being used (not non-OCRd)
+The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper.
+However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
 
-## Dataset issues
 Which PDFs are missing or have no content, etc.
 
-| year | I have this number in Reps | They say this number in Senate | They say this number in Reps | Difference in Reps | Comment                          | Source                                                                                           |
-|------|----------------------------|--------------------------------|------------------------------|--------------------|----------------------------------|--------------------------------------------------------------------------------------------------|
-| 1902 | 106                        | 93                             | 107                          | 1                  | Positive means I am missing some | https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear |
-| 1908 | 93                         | 84                             | 91                           | -2                 | Negative means I have too many   |                                                                                                  |
-| 1909 | 97                         | 71                             | 98                           | 1                  |                                  |                                                                                                  |
-| 1918 | 87                         | 68                             | 86                           | -1                 |                                  |                                                                                                  |
-| 1920 | 113                        | 76                             | 114                          | 1                  |                                  |                                                                                                  |
-| 1921 | 92                         | 79                             | 93                           | 1                  |                                  |                                                                                                  |
-| 1934 | 36                         | 22                             | 35                           | -1                 |                                  |                                                                                                  |
-| 1935 | 54                         | 37                             | 55                           | 1                  |                                  |                                                                                                  |
-| 1942 | 44                         | 36                             | 45                           | 1                  |                                  |                                                                                                  |
-| 1948 | 89                         | 39                             | 90                           | 1                  |                                  |                                                                                                  |
-| 1951 | 55                         | 40                             | 56                           | 1                  |                                  |                                                                                                  |
-| 1955 | 53                         | 36                             | 52                           | -1                 |                                  |                                                                                                  |
-| 1974 | 64                         | 64                             | 62                           | -2                 |                                  |                                                                                                  |
-| 1985 | 65                         | 74                             | 66                           | 1                  |                                  |                                                                                                  |
-| 1991 | 66                         | 83                             | 67                           | 1                  |                                  |                                                                                                  |
-| 1992 | 60                         | 76                             | 44                           | -16                |                                  |                                                                                                  |
-| 1993 | 47                         | 53                             | 46                           | -1                 |                                  |                                                                                                  |
-| 1994 | 69                         | 80                             | 68                           | -1                 |                                  |                                                                                                  |
-| 1995 | 71                         | 78                             | 70                           | -1                 |                                  |                                                                                                  |
-| 1997 | 79                         | 82                             | 76                           | -3                 |                                  |                                                                                                  |
-| 1998 | 56                         | 57                             | 54                           | -2                 |                                  |                                                                                                  |
-| 2000 | 71                         | 71                             | 73                           | 2                  |                                  |                                                                                                  |
-| 2002 | 68                         | 60                             | 69                           | 1                  |                                  |                                                                                                  |
-| 2003 | 74                         | 64                             | 75                           | 1                  |                                  |                                                                                                  |
-| 2004 | 58                         | 49                             | 59                           | 1                  |                                  |                                                                                                  |
-| 2012 | 63                         | 57                             | 67                           | 4                  |                                  |                                                                                                  |
+```{r missingdays, echo = FALSE, results = 'asis'}
 
-## Example workflow
+missing_days %>% 
+  kable(booktabs = T, caption = "Missing days") %>%
+  kable_styling(font_size = 8)
+
+```
+
+Notes: Positive means I am missing some, Negative means I have too many.
+Source: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear
+
+## Example Hansard PDf to text record workflow {#hansardworkflow}
 Example of the workflow from PDF to text
 
-## PDF to CSV issues
+These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
+In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
+
+## Stopwords over time {#stopwordsgraph}
 Insert graph of stop words over time.
 
-## Topic modelling example and details
-### Examples
+\newpage
+
+# Additional information {#additionalinformation}
+**TBD**
+
+\newpage
+
+# word2vec alternative {#word2vec}
+An alternative approach that follows @Taddy2015.
+
+\newpage
+
+# Topic modelling example and details
+## Examples {#LDAexample}
 For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
@@
 
-### Solution details
+## Posterior estimation {#LDAposteriorestimation}
 Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
@@
 
-## Selection of number of topics
+## Selection of number of topics {#selecttopicnumber}
+**[TBD]**
 
 ## Robustness of results
+**[IS THIS BEING USED?]**
 Here we change the number of sitting days considered either side of an event.
@@
 
-## Events
+\newpage
+
+# Events {#eventdetails}
 
@@
 
-## Choosing number of topics
-
 Add the graphs and procedures.
-
-## word2vec alternative
-An alternative approach that follows @Taddy2015.
 

### 2018-09-30 outputs/docs/events/svm-rmarkdown-article-example.tex
Improve paper

@@
 
-\setcounter{secnumdepth}{0}
+% This controls whether you get numbers in the sections or not
+% \setcounter{secnumdepth}{0}
 
@@
 
-\title{Nobody expects the Spanish Inquisition: The effect of events on
-Australian parliamentary discussion \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
+\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 29
+Cochrane for their helpful suggestions. \textbf{Version as of}: 30
 September 2018; \textbf{comments welcome}:
@@
              pdfkeywords = {text analysis, politics, Australia},  
-            pdftitle={Nobody expects the Spanish Inquisition: The effect of events on
-Australian parliamentary discussion},
+            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1870--2017)},
             colorlinks=true,
@@
 
-\noindent Government policy is partly driven by parliamentary discussion.
+\noindent We systematically analyse how parliamentary discussion changes in
+response to different types of events in Australian history. We first
+compile a dataset of what was said in Australian state and federal
+parliaments from the mid-1800s through to 2017 based on available public
+records. We then use a structural text model to reduce the
+dimensionality of the text and to impose prior knowledge such as
+correlation between days and changes over time. Finally, we examine the
+effect of various events using a Bayesian choice model. We find that: 1)
+elections are associated with topic changes only when the party in power
+changes but a change in government sometimes does not require this to be
+associated with topic changes; and 2) economic events, such as financial
+crises, have less significant and persistent effects than other events
+such as terrorism. Our findings have implications for how we think about
+the longer-term trajectory of government policy as the media cycle
+becomes increasingly focused on short-term events.
+
+\vskip 8.5pt \noindent \emph{Keywords}: text analysis, politics, Australia \par
+
+    \hbox{\vrule height .2pt width 39.14pc}
+
+\end{abstract}
+
+\vskip 6.5pt
+
+\noindent  \section{Introduction}\label{introduction}
+
+Government policy is partly driven by parliamentary discussion.
 Conversely, that same discussion can indicate a government's priorities.
@@
 such as a recession or terrorist attack--can affect the course of
-parliamentary discussion. In this paper, we systematically analyse how
-parliamentary discussion changes in response to different types of
-events in Australian history. We compile a dataset of what was said in
-Australian state and federal parliaments from the mid-1800s through to
-2017 based on available public records. We use a structural text model
-to reduce the dimensionality of the text and to impose prior knowledge
-such as correlation between days and changes over time. We then examine
-the effect of various events. We find that: 1) changes of government are
-associated with topic changes only when there is also a change of the
-party in power; and 2) economic events, such as financial crises, have
-significant and persistent effects. Our findings have implications for
-how we think about the longer-term trajectory of government policy as
-the media cycle becomes increasingly focused on short-term events.
-
-\vskip 8.5pt \noindent \emph{Keywords}: text analysis, politics, Australia \par
-
-    \hbox{\vrule height .2pt width 39.14pc}
-
-\end{abstract}
-
-\vskip 6.5pt
-
-\noindent  \section{Introduction}\label{introduction}
-
-New governments often go to some trouble to be different to the
-governments they replace. For instance, Kevin Rudd's apology to
-Indigenous Australians was not supported by his predecessor John Howard,
-and then one of Tony Abbott's first acts was to repeal his predecessor
-Kevin Rudd's carbon tax. Similarly, significant events such as the 9/11
-attacks or the Great Recession have often altered the course of a
-government. However it is not so clear which events drive changes, for
-how long these changes persist, and what was given up due to the change.
+parliamentary discussion. For instance, new governments often go to some
+trouble to be different to the governments they replace, such as Kevin
+Rudd's apology to Indigenous Australians not being supported by his
+predecessor John Howard, and then one of Tony Abbott's first acts was to
+repeal his predecessor Kevin Rudd's carbon tax. Similarly, significant
+events such as the 9/11 attacks or the Great Recession have often
+altered the course of a government. But it is not so clear which events
+drive changes, for how long these changes persist, and what was given up
+due to the change.
 
@@
 for dimensionality reduction and to impose structure such as correlation
-between days and changes over time. We then examine changes at various
-types of events, including: changes in government; changes in the
-political environment (as defined by polling or other results); changes
-in economic conditions; and other significant events (such as the 9/11
-attacks or the Bali bombings).
+between days and changes over time. We then use a simple discrete choice
+model to examine changes at various types of events, including: changes
+in government; changes in the political environment (as defined by
+polling or other results); changes in economic conditions; and other
+significant events (such as the 9/11 attacks or the Bali bombings).
 
@@
 Our paper applies a topic model to a dataset of larger-scale
-parliamentary text records from multiple Australian parliaments. Our
-work fits into a growing literature that considers text as an input to
-more usual quantitative techniques, rather than requiring separate
-analysis. While using text as data has well-known shortcomings, it
-allows larger-scale analysis that would not be viable using
-less-automated approaches and so it can identify patterns that may
-otherwise be overlooked.
+parliamentary text records from multiple Australian parliaments. Our use
+of a discrete choice model - essentially a time series multinomial model
+of choices - allows us to construct a counterfactual. Our work fits into
+a growing literature that considers text as an input to more usual
+quantitative techniques, rather than requiring separate analysis. While
+using text as data has well-known shortcomings, it allows larger-scale
+analysis that would not be viable using less-automated approaches and so
+it can identify patterns that may otherwise be overlooked.
 
@@
   the Hansard record, instead of the parliamentarians.} Earlier work on
-the influence of parliaments, such as \citet{ZandenBuringhBosker2012} or
-\textbf{{[}ANOTHER REFERENCE - Maybe Frank Fisher `Reframing Public
-Policy'?{]}}, often examined broader activity measures such as counts of
-sitting days. This allowed for long time frames and wide comparisons.
-But analysing Hansard records and their equivalents directly are an
-increasingly viable and popular source of data as new methods and
-reduced computational costs make larger-scale analysis easier,
-complementing other measures.
-
-The digitisation of the Canadian Hansard, \citet{BeelenEtc2017}, allowed
-\citet{RheaultCochran2018} to examine ideology and party polarisation in
-Britain and Canada. In the UK, \citet{Duthie2016} analysed Hansard
-records to examine which politicians made supportive or aggressive
-statements toward other politicians between 1979 and 1990 and
+the influence of parliaments, such as \citet{ZandenBuringhBosker2012},
+often examined broader activity measures such as counts of sitting days.
+This allowed for long time frames and wide comparisons. But analysing
+Hansard records and their equivalents directly are an increasingly
+viable and popular source of data as new methods and reduced
+computational costs make larger-scale analysis easier, complementing
+other measures.
+
+The recent digitisation of the Canadian Hansard, \citet{BeelenEtc2017},
+allowed \citet{RheaultCochran2018} to examine ideology and party
+polarisation in Britain and Canada. In the UK, \citet{Duthie2016}
+analysed Hansard records to examine which politicians made supportive or
+aggressive statements toward other politicians between 1979 and 1990 and
 \citet{PetersonSpirling2018} examined polarisation. And as digitisation
@@
 available online as PDFs and these are considered the official release.
-An example of what a page of Hansard looks like is included in Appendix
-\textbf{{[}ADD NUMBERING{]}}. There is a more limited set of XML records
-available in some cases.\footnote{Tim Sherratt makes these XML records
-  available as a single download and also presents them in a website
+Additionally, there is a more limited set of XML records available in
+some cases.\footnote{Tim Sherratt makes these XML records available as a
+  single download and also presents them in a website
   (\url{http://historichansard.net/}) that can be used to explore
@@
   records can also be downloaded from the Australian Hansard website.}
-There are 65,000 \textbf{{[}UPDATE{]}} Hansard records publicly
-available across the state and federal parliaments (Table
-\ref{tab:yearsusedtable}) \textbf{{[}UPDATE NUMBERING{]}}. As with any
-larger-scale data process, there are various issues with some of the
-PDFs and the known ones are detailed in Appendix \textbf{{[}ADD
-NUMBERING{]}}.\footnote{The NSW Legislative Council was established
-  earlier than 1856, however the earlier Hansard records have not been
-  through an independent OCR process and were not used in this paper.
-  However, the Google Tesseract OCR engine as implemented by
-  \citet{Ooms2018tesseract} provided useful data and these could be used
-  in the future.}
+We detail the sources of our Hansard PDFs in \ref{hansardsources} and
+Appendix \ref{examplehansardpage} provides an example of what a Hansard
+PDF looks like. There are 65,000 \textbf{{[}UPDATE{]}} days worth of
+publicly available Hansard records across the state and federal
+parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process
+indicates concerns with a small number of PDFs and these are detailed in
+Appendix \ref{knownhansardissues}.
 
@@
 The formatting of the Hansard records changes between the different
-parliaments and over time. We use R scripts to convert the PDFs into
-daily text records.\footnote{An example of the workflow and some
-  reduced-detail scripts are provided in Appendix \textbf{{[}ADD
-  NUMBERING{]}}.} These scripts are primarily based on: the
-\texttt{PDFtools} package of \citet{Ooms2018pdftools}; the
-\texttt{tidyverse} package of \citet{Wickham2017}; the \texttt{tm}
-package of \citet{FeinererHornik2018}; the \texttt{lubridate} package of
-\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
-\citet{Gagolewski2018}. The functions of those packages are supported
-by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
-\texttt{tictoc} package of \citet{Izrailev2014}. Some error is
-introduced at this stage because many of the records are in a two-column
-format that need to be separated, and the PDF parsing is not always
-accurate especially for older records. An example of the latter issue is
-that `the' is often parsed as `thc'. These errors are fixed when they
-occur at scale and can be identified. One way to provide assurance that
-mistakes in older records are not driving the results is to analyse the
-percentage of stop-words in each record over time. This details of this
-are provided in Appendix \textbf{{[}ADD NUMBERING{]}} and suggest that
-there is no significant difference in the quality of the parsing over
-time. The \texttt{hunspell} package of \citet{Ooms2017} is also used to
-help find spelling issues.
-
-These daily records are the main level at which we consider the data in
-this paper, but the daily records are also further divided into
-individual-level records. Sometimes these are just short interjections
-or notes that are not specific to any particular politician, such as
-`Honourable members interjecting'. The high dimensional nature of text
-data means that the appropriate analysis data are research-question
-specific and datasets need to be tidied toward that. For instance, in
-our paper interjections are not important because they do not usually
-contribute much to defining the topics being discussed. But they are
-interesting in their own right and \citet{Whyte2017} analysed them in a
-Canadian context for the period 1926 to 2015 to find that female MPs
-were more likely to be interrupted than male MPs.
+parliaments and over time. We use scripts written in R (\citet{R2018})
+to convert the PDFs into daily text records. An example of the workflow
+and some reduced-detail scripts are provided in Appendix
+\ref{hansardworkflow}. Some error is introduced at this stage because
+many of the records are in a two-column format that need to be
+separated, and the PDF parsing is not always accurate especially for
+older records. An example of the latter issue is that `the' is often
+parsed as `thc'. These errors are corrected when they occur at scale and
+can be identified. The percentage of stop-words in each record is
+reasonably consistent over time. This suggests that there is no
+significant difference in the quality of the parsing over time. Details
+of this process are provided in Appendix \ref{stopwordsgraph}.
+
+These daily records are the main level that we consider in this paper,
+but we also disaggregated them into individual-level records during the
+cleaning process. Sometimes these are just short interjections or notes
+that are not specific to any particular politician, such as `Honourable
+members interjecting'. The high dimensional nature of text data means
+that the appropriate level and focus of the dataset being analysed tends
+to be specific to a research question. For instance, in our paper
+interjections are not important because they do not usually contribute
+much to defining the topics being discussed. But they are interesting in
+their own right and \citet{Whyte2017} analysed them in a Canadian
+context for the period 1926 to 2015 to find that female MPs were more
+likely to be interrupted than male MPs.
 
@@
 when Hansard is indicating that a particular person is speaking, as
-opposed to being mentioned (for more on the political effect of being
-mentioned see \citet{Alexander2018}), often the name is in upper case,
-for instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon;
-or are next to some title within brackets. There is substantial
-variation in how the person making a statement is identified. Again some
-error is introduced at this stage because of inconsistencies over time
-and between the parliaments. There is considerable variance but on
-average each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
+opposed to being mentioned, often the name is in upper case, for
+instance `Mr WHITLAM' or `Mr MENZIES'; followed by a dash or colon; or
+are next to some title within brackets. There is substantial variation
+in how the person making a statement is identified. Again some error is
+introduced at this stage because of inconsistencies over time and
+between the parliaments. There is considerable variance but on average
+each daily record had 250 \textbf{{[}UPDATE{]}} individual-level
 records, resulting in roughly 15 million rows \textbf{{[}UPDATE{]}}
@@
 
-Text usually needs to be pre-processed before topic models can be used.
-The specific steps that we take are to remove numbers and punctuation
-and to change all the words to lower case. Then the sentences are
-deconstructed and each word considered individually. In addition to the
-packages already mentioned, in this step the R scripts to do this use
-the \texttt{tidytext} R package of \citet{SilgeRobinson2016}.
-\textbf{{[}Need to bundle\_ngrams i.e.~New Zealand is new\_zealand.{]}}
+Text is usually pre-processed before topic models are used. The specific
+steps that we take are to remove numbers and punctuation and to change
+the words to lower case. Then the sentences are deconstructed and each
+word considered individually. \textbf{{[}Need to bundle\_ngrams i.e.~New
+Zealand is new\_zealand.{]}}
 
@@
 
-Data from other sources are useful to complement the parliamentary text
+Data from other sources are needed to complement the parliamentary text
 data. For instance, although the name, party, and division represented
@@
 errors and were supplemented by data from the Australian Dictionary of
-Biography and Wikipedia.\footnote{An example of the additional
-  information is provided in Appendix \textbf{{[}ADD NUMBERING{]}}.} The
-source for the electoral results is the Australian Electoral Commission
-and Adam Carr's Australian Election Archive.
+Biography and Wikipedia. The source for the electoral results is the
+Australian Electoral Commission and Adam Carr's Australian Election
+Archive. An example of the additional information is provided in
+Appendix \ref{additionalinformation}.
 
@@
 (STM) as implemented by the \texttt{stm} R package of
-\citet{RobertsStewartAiroldiRPackage}. In a similar way to
-\citet{MuellerRauh2018}, we use these topics to analyse the effect of
-various events. In Appendix \textbf{{[}ADD NUMBERING{]}}, we include an
-alternative approach that follows \citet{Taddy2015} by using word2vec,
-which more closely uses words, rather than topics, as an input.
+\citet{RobertsStewartAiroldiRPackage} and a Bayesian discrete choice
+model. In a similar way to \citet{MuellerRauh2018}, we use topics to
+analyse the effect of various events. In Appendix \ref{word2vec}, we
+include an alternative approach that follows \citet{Taddy2015} by using
+word2vec, which more closely uses words, rather than topics, as an
+input.
 
@@
 both the LDA model and the STM. We consider the outputs of the topic
-model as reduced dimension inputs that can be analysed.
+model as reduced dimension inputs that can be analysed within another
+model. In our case they are inputs to a discrete choice model, and so we
+then discuss that model.
 
@@
 \ref{fig:topicsoverdocuments} and \ref{fig:topicsoverterms} in Appendix
-\textbf{{[}ADD NUMBERING{]}} illustrates an example with five topics,
-two documents, and ten terms.
+\ref{LDAexample} illustrates an example with five topics, two documents,
+and ten terms.
 
@@
 be used to approximate the posterior. A summary of these approaches is
-provided in Appendix \textbf{{[}ADD NUMBERING{]}}. The choice of the
+provided in Appendix \ref{LDAposteriorestimation}. The choice of the
 number of topics, \emph{k}, drives the results and must be specified
@@
 diagnostic techniques with cross validation to decide on 80
-\textbf{{[}UPDATE AS APPROPRIATE{]}} topics. More detail on this
-selection process is available in Appendix \textbf{{[}ADD NUMBERING{]}}.
+\textbf{{[}UPDATE{]}} topics. More detail on this selection process is
+available in Appendix \ref{selecttopicnumber}.
 
@@
 those such as the 9/11 attacks, or the Bali Bombing. The full list of
-events that we consider is detailed in Appendix \textbf{{[}ADD
-NUMBERING{]}}.
+events that we consider is detailed in Appendix
+\citet{ref}(eventdetails).
 
@@
 the topics. This illustrates the differences between the topics. The
-second is by including incrementing variables in the prevalence metdata.
+second is by including incrementing variables in the prevalence metadata
 This groups each day by events and we can then conduct significance
@@
 
-\section{Appendix}\label{appendix}
-
-\subsection{Example page}\label{example-page}
+\section{Hansard details}\label{hansard-details}
+
+\subsection{Hansard sources}\label{hansardsources}
+
+Where from?
+
+Which years are being used (not non-OCRd)
+
+{[}IS THIS BEING REFERENCED IN THE TEXT????{]}
+
+\subsection{Example Hansard page}\label{examplehansardpage}
 
@@
 
-\subsection{Document sources}\label{document-sources}
-
-Where from?
-
-Which years are being used (not non-OCRd)
-
-\subsection{Dataset issues}\label{dataset-issues}
+\subsection{Known Hansard issues}\label{knownhansardissues}
+
+The NSW Legislative Council was established earlier than 1856, however
+the earlier Hansard records have not been through an independent OCR
+process and were not used in this paper. However, the Google Tesseract
+OCR engine as implemented by \citet{Ooms2018tesseract} provided useful
+data and these could be used in the future.
 
@@
 
-\begin{longtable}[]{@{}lllllll@{}}
+\begin{table}
+
+\caption{\label{tab:missingdays}Missing days}
+\centering
+\fontsize{8}{10}\selectfont
+\begin{tabular}[t]{rrrrr}
 \toprule
-\begin{minipage}[b]{0.02\columnwidth}\raggedright\strut
-year\strut
-\end{minipage} & \begin{minipage}[b]{0.09\columnwidth}\raggedright\strut
-I have this number in Reps\strut
-\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
-They say this number in Senate\strut
-\end{minipage} & \begin{minipage}[b]{0.10\columnwidth}\raggedright\strut
-They say this number in Reps\strut
-\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\raggedright\strut
-Difference in Reps\strut
-\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
-Comment\strut
-\end{minipage} & \begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
-Source\strut
-\end{minipage}\tabularnewline
+year & HoR PDFs                      & Senate sitting days           & HoR sitting days              & HoR difference\\
 \midrule
-\endhead
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1902\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-106\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-93\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-107\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-Positive means I am missing some\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1908\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-93\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-84\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-91\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--2\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-Negative means I have too many\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1909\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-97\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-71\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-98\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1918\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-87\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-68\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-86\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1920\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-113\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-76\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-114\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1921\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-92\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-79\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-93\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1934\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-36\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-22\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-35\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1935\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-54\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-37\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-55\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1942\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-44\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-36\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-45\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1948\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-89\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-39\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-90\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1951\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-55\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-40\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-56\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1955\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-53\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-36\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-52\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1974\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-64\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-64\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-62\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--2\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1985\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-65\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-74\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-66\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1991\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-66\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-83\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-67\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1992\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-60\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-76\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-44\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--16\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1993\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-47\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-53\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-46\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1994\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-69\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-80\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-68\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1995\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-71\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-78\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-70\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1997\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-79\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-82\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-76\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--3\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-1998\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-56\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-57\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-54\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
--2\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-2000\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-71\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-71\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-73\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-2\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-2002\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-68\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-60\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-69\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-2003\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-74\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-64\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-75\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-2004\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-58\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-49\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-59\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-1\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.02\columnwidth}\raggedright\strut
-2012\strut
-\end{minipage} & \begin{minipage}[t]{0.09\columnwidth}\raggedright\strut
-63\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-57\strut
-\end{minipage} & \begin{minipage}[t]{0.10\columnwidth}\raggedright\strut
-67\strut
-\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\raggedright\strut
-4\strut
-\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
-\strut
-\end{minipage} & \begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
-\strut
-\end{minipage}\tabularnewline
+1902 & 106 & 93 & 107 & 1\\
+1908 & 93 & 84 & 91 & -2\\
+1909 & 97 & 71 & 98 & 1\\
+1918 & 87 & 68 & 86 & -1\\
+1920 & 113 & 76 & 114 & 1\\
+\addlinespace
+1921 & 92 & 79 & 93 & 1\\
+1934 & 36 & 22 & 35 & -1\\
+1935 & 54 & 37 & 55 & 1\\
+1942 & 44 & 36 & 45 & 1\\
+1948 & 89 & 39 & 90 & 1\\
+\addlinespace
+1951 & 55 & 40 & 56 & 1\\
+1955 & 53 & 36 & 52 & -1\\
+1974 & 64 & 64 & 62 & -2\\
+1985 & 65 & 74 & 66 & 1\\
+1991 & 66 & 83 & 67 & 1\\
+\addlinespace
+1992 & 60 & 76 & 44 & -16\\
+1993 & 47 & 53 & 46 & -1\\
+1994 & 69 & 80 & 68 & -1\\
+1995 & 71 & 78 & 70 & -1\\
+1997 & 79 & 82 & 76 & -3\\
+\addlinespace
+1998 & 56 & 57 & 54 & -2\\
+2000 & 71 & 71 & 73 & 2\\
+2002 & 68 & 60 & 69 & 1\\
+2003 & 74 & 64 & 75 & 1\\
+2004 & 58 & 49 & 59 & 1\\
+2012 & 63 & 57 & 67 & 4\\
 \bottomrule
-\end{longtable}
-
-\subsection{Example workflow}\label{example-workflow}
+\end{tabular}
+\end{table}
+
+Notes: Positive means I am missing some, Negative means I have too many.
+Source:
+\url{https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear}
+
+\subsection{Example Hansard PDf to text record
+workflow}\label{hansardworkflow}
 
@@
 
-\subsection{PDF to CSV issues}\label{pdf-to-csv-issues}
+These scripts are primarily based on: the \texttt{PDFtools} package of
+\citet{Ooms2018pdftools}; the \texttt{tidyverse} package of
+\citet{Wickham2017}; the \texttt{tm} package of
+\citet{FeinererHornik2018}; the \texttt{lubridate} package of
+\citet{GrolemundWickham2011}; and the \texttt{stringi} package of
+\citet{Gagolewski2018}. The functions of those packages are supported
+by: the \texttt{furrr} package of \citet{VaughanDancho2018}; and the
+\texttt{tictoc} package of \citet{Izrailev2014}. The \texttt{hunspell}
+package of \citet{Ooms2017} is also used to help find spelling issues.
+In addition to the packages already mentioned, in this step the R
+scripts to do this use the \texttt{tidytext} R package of
+\citet{SilgeRobinson2016}.
+
+\subsection{Stopwords over time}\label{stopwordsgraph}
 
@@
 
-\subsection{Topic modelling example and
+\newpage
+
+\section{Additional information}\label{additionalinformation}
+
+\textbf{TBD}
+
+\newpage
+
+\section{word2vec alternative}\label{word2vec}
+
+An alternative approach that follows \citet{Taddy2015}.
+
+\newpage
+
+\section{Topic modelling example and
 details}\label{topic-modelling-example-and-details}
 
-\subsubsection{Examples}\label{examples}
+\subsection{Examples}\label{LDAexample}
 
@@
 
-\subsubsection{Solution details}\label{solution-details}
+\subsection{Posterior estimation}\label{LDAposteriorestimation}
 
@@
 
-\subsection{Selection of number of
-topics}\label{selection-of-number-of-topics}
+\subsection{Selection of number of topics}\label{selecttopicnumber}
+
+\textbf{{[}TBD{]}}
 
@@
 
-Here we change the number of sitting days considered either side of an
-event. The results in the main section of the paper are for the nearest
-ten days either side of an event. Here are show that the results are
-essentially the same if the nearest one, two, five, and twenty days
-either side of an event.
-
-\subsection{Events}\label{events}
+\textbf{{[}IS THIS BEING USED?{]}} Here we change the number of sitting
+days considered either side of an event. The results in the main section
+of the paper are for the nearest ten days either side of an event. Here
+are show that the results are essentially the same if the nearest one,
+two, five, and twenty days either side of an event.
+
+\newpage
+
+\section{Events}\label{eventdetails}
 
@@
 
-\subsection{Choosing number of topics}\label{choosing-number-of-topics}
-
 Add the graphs and procedures.
-
-\subsection{word2vec alternative}\label{word2vec-alternative}
-
-An alternative approach that follows \citet{Taddy2015}.
 

### 2018-10-02 scripts/to_monica/exploratory_2.Rmd
start of dirichlet modeling by MA

---
title: "Dirichlet?"
author: "Monica Alexander"
date: "10/1/2018"
output: html_document
---

Try and get this dirichlet thing going

```{r, message=F}
library(tidyverse)
library(lubridate)
library(boot)
library(rjags)
library(R2jags)
library(distortr)
```

Read in the data

```{r}
d <- read_csv("gammas_model_prevalence_years_k_20.csv")
dr <- d %>% 
  filter(document > ymd("2016-01-01"))
```

Plot these just to visualize. Note that the topics are really dominated by two particular ones.

```{r}
dr %>% 
  ggplot(aes(document, gamma, fill = factor(topic))) + geom_bar(stat = "identity")
```

Get info about sitting period, day number in sitting period etc. In this period we have 10 different sitting days. Sitting periods usually only have 8 days in them.

```{r}
dr_wide <- dr %>% 
  spread(topic, gamma)

dr_wide <- dr_wide %>% mutate(day_diff = document - lag(document))

k <- 1
dr_wide$group <- NA
for(i in 1:nrow(dr_wide)){
  if(is.na(dr_wide$day_diff[i])|dr_wide$day_diff[i]<7){
    k <- k
  }
  else{
    k <- k+1
  }
  dr_wide$group[i] <- k
}

dr_wide <- dr_wide %>% group_by(group) %>% 
  mutate(day_number = row_number())

```

Make back into long format. Now we have some covariates!

```{r}
dr_long <- dr_wide %>% 
  gather(topic, gamma, -document, -group, -day_number, -day_diff) %>% 
  arrange(document)
```

Think about a simple model here. The dependent variable is $\gamma_{stp}$, for sitting period $s$, day $t$ and topic $p$. This could be a function of: sitting period, the gamma of the same topic the day before, the year....

Start off with

$$
\gamma_{st,} \sim Dirichlet(\mu_{st,})\\
\log \mu_{stp} = \alpha_{sp} 
$$

So just linear in time for each topic and sitting period. Now need to get the data in the right form to fit:

```{r}
ntopics <- 20
y.stp <- array(NA, c(max(dr_long$group),max(dr_long$day_number), 20))

for (i in 1:ntopics){
  y.stp[,,i] <- dr_long %>% 
  ungroup() %>% 
  filter(topic==i) %>% 
  dplyr::select(-topic, -day_diff, -document) %>% 
  spread(day_number, gamma) %>% 
  dplyr::select(-group) %>% 
  as.matrix()
}

nsittings <- max(dr_long$group)
ndays.s <- dr_long %>% group_by(group) %>% summarise(days = max(day_number)) %>% dplyr::select(days) %>% pull()

```

Run the model:

```{r}
jags.data <- list(nsittings = nsittings,
                  ndays.s = ndays.s, 
                  ntopics = ntopics, 
                  y.stp = y.stp)
parnames <- c("alpha", "mu.stp")

mod <- jags(data = jags.data, 
            #n.iter = 5000,
            parameters.to.save=parnames,
            model.file = "model_dirichlet.txt")

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
```

```{r}
df_res <- c()
for(i in 1:nsittings){
  for(j in 1:ndays.s[i]){
    for(k in 1:ntopics)
    df_res <- rbind(df_res, tibble(group = i, day = j, topic = k, 
                                   document =  dr_long$document[dr_long$group==i&dr_long$day_number==j&dr_long$topic==k],
                                   median = (median(mcmc.array[,,paste0("mu.stp[",i,",",j, ",",k,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("mu.stp[",i,",",j, ",",k,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("mu.stp[",i,",",j, ",",k,"]")], 0.025))
    ))
  }
}
```

Plot:

```{r}
df_res %>% 
ggplot(aes(day, median, fill = factor(topic))) + geom_line(aes(color = factor(topic))) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  facet_wrap(~group)+
  geom_point(data = dr_long, aes((day_number), gamma, color = factor(topic)))
```

### 2018-10-02 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Add NSW scraping addresses and clean up literature and minor improvements to paper

@@
 We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
-We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and changes over time.
-Finally, we examine the effect of various events using a Bayesian choice model.
-We find that: 1) elections are associated with topic changes only when the party in power changes but a change in government sometimes does not require this to be associated with topic changes; and 2) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorism.
+We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time.
+Finally, we consider various events using Bayesian regression with a Dirichlet-distributed response variable.
+We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
 Our findings have implications for how we think about the longer-term trajectory of government policy as the media cycle becomes increasingly focused on short-term events."
@@
 Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
-There are 65,000 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
+There are roughly 54,331 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
   kable(booktabs = T, caption = "Missing days") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 12)
 
@@
   kable(booktabs = T, caption = "Change in governments") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 12)
 
@@
   kable("latex", booktabs = T, caption = "Elections") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 12)
 
@@
   kable(booktabs = T, caption = "Key economic events") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 12)
 
@@
   kable(booktabs = T, caption = "Key other events") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 12)
 

### 2018-10-02 outputs/docs/events/svm-rmarkdown-article-example.tex
Add NSW scraping addresses and clean up literature and minor improvements to paper

@@
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
-Cochrane for their helpful suggestions. \textbf{Version as of}: 30
-September 2018; \textbf{comments welcome}:
+Cochrane for their helpful suggestions. \textbf{Version as of}: 02
+October 2018; \textbf{comments welcome}:
 \href{mailto:rohan.alexander@anu.edu.au}{\nolinkurl{rohan.alexander@anu.edu.au}}.}  }
@@
 dimensionality of the text and to impose prior knowledge such as
-correlation between days and changes over time. Finally, we examine the
-effect of various events using a Bayesian choice model. We find that: 1)
-elections are associated with topic changes only when the party in power
-changes but a change in government sometimes does not require this to be
-associated with topic changes; and 2) economic events, such as financial
+correlation between days and steady changes over time. Finally, we
+consider various events using Bayesian regression with a
+Dirichlet-distributed response variable. We find that: 1) elections are
+associated with topic changes only when the party in power changes; 2) a
+change in government can be associated with topic changes even if the
+party in power does not change; 3) economic events, such as financial
 crises, have less significant and persistent effects than other events
-such as terrorism. Our findings have implications for how we think about
-the longer-term trajectory of government policy as the media cycle
-becomes increasingly focused on short-term events.
+such as terrorist attacks. Our findings have implications for how we
+think about the longer-term trajectory of government policy as the media
+cycle becomes increasingly focused on short-term events.
 
@@
  & Legislative Council & 1860 - 1922 & 4156\\
-New South Wales & Legislative Assembly & 1856 - 2017 & TBD\\
-\addlinespace
- & Legislative Council & 1856 - 2017 & TBD\\
-Victoria & Legislative Assembly & 1856 - 2017 & TBD\\
- & Legislative Council & 1851 - 2017 & TBD\\
-Tasmania & House of Assembly & 1856 - 2017 & TBD\\
- & Legislative Council & 1856 - 2017 & TBD\\
-\addlinespace
-South Australia & House of Assembly & 1857 - 2017 & TBD\\
- & Legislative Council & 1840 - 2017 & TBD\\
-Western Australia & Legislative Assembly & 1890 - 2017 & TBD\\
- & Legislative Council & 1832 - 2017 & TBD\\
+New South Wales & Legislative Assembly & 1879 - 2017 & 8903\\
+\addlinespace
+ & Legislative Council & 1879 - 2017 & 6463\\
+Victoria & Legislative Assembly & 1856 - 2017 & -\\
+ & Legislative Council & 1851 - 2017 & -\\
+Tasmania & House of Assembly & TBD - 2017 & TBD\\
+ & Legislative Council & TBD - 2017 & TBD\\
+\addlinespace
+South Australia & House of Assembly & TBD - 2017 & TBD\\
+ & Legislative Council & TBD - 2017 & TBD\\
+Western Australia & Legislative Assembly & 1890 - 2017 & 5977\\
+ & Legislative Council & 1870 - 2017 & 5725\\
 \bottomrule

### 2018-10-02 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -124,7 +124,15 @@ all_dates <-
          keyOtherChange = if_else(allDates %in% keyOtherDates$theDate, 1, 0),
          keyOtherChange = cumsum(keyOtherChange)) %>% 
   rename(electionCounter = electionDate)
+
 head(all_dates)
+# 
+# all_dates <- all_dates %>% 
+#   select(-keyEconomicChange, -keyOtherChange) %>% 
+#   mutate(governmentChangeDate = governmentChangeDate + 1) %>% 
+#   filter(allDates > "1901-03-29")
+# 
+# write_csv(all_dates, "dates_of_gov_and_election.csv")
 
 tidy_hansard_reduced <- tidy_hansard_reduced %>% 
   left_join(all_dates, by = c("docid_field" = "allDates"))

### 2018-10-02 scripts/to_scrape_websites/get_URLs_of_hansard_dates-NSW.R

@@ -1,0 +1,60 @@
+#### Preamble ####
+# Purpose: To get the URLs for the NSW PDFs
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 2 October 2018
+# Prerequisites: -
+# To do: 
+
+
+#### Set up workspace ####
+library(jsonlite)
+library(lubridate)
+library(tidyverse)
+library(rvest)
+# update.packages()
+
+
+#### Pages of search results that list the PDFs ####
+years <- c(1879:2017)
+pages_to_GET <- paste0("https://api.parliament.nsw.gov.au/api/hansard/search/year/", years)
+# pages_to_GET <- pages_to_GET[1]
+
+
+# Thanks to https://tclavelle.github.io/blog/r_and_apis/ and https://data.metinyazici.org/2017/10/working-with-web-data-in-r.html and https://stackoverflow.com/questions/43127114/sys-sleep-using-function-possibly-from-purrr-package and https://tclavelle.github.io/blog/r_and_apis/
+# pages_to_GET <- pages_to_GET[1:3]
+fromJSON_responses <- map(pages_to_GET, ~{
+  # pb$tick()$print()
+  Sys.sleep(20)
+  fromJSON(txt = .x)
+}) 
+
+fromJSON_responses
+
+nsw_hansard_tibble <- bind_rows(fromJSON_responses) %>% 
+  unnest(Events) %>% 
+  as_tibble()
+
+nsw_hansard_tibble <- nsw_hansard_tibble %>% 
+  mutate(date = ymd(date)) %>%
+  mutate(chamber_type = case_when(
+    Chamber == "Legislative Assembly" ~ "A",
+    Chamber == "Legislative Council" ~ "C",
+    TRUE ~ "Unsure"
+  )) %>% 
+  select(-style, -tooltip, -TocDocId, -Uncorrected)
+
+nsw_hansard_tibble <- nsw_hansard_tibble %>%
+  mutate(URL = case_when(
+    year(date) >= 1991 ~ paste0("https://api.parliament.nsw.gov.au/api/hansard/search/daily/pdf/", PdfDocId),
+    year(date) < 1991 ~ paste0("https://api.parliament.nsw.gov.au/api/hansard/search/daily/searchablepdf/", PdfDocId),
+    TRUE ~ "Unsure"
+  ))
+
+nsw_hansard_tibble <- nsw_hansard_tibble %>%
[…]

### 2018-10-02 scripts/to_scrape_websites/safelycompact.R

@@ -1,0 +1,19 @@
+#### Set up workspace ####
+library(tidyverse)
+library(rvest)
+
+
+pages_to_scrape <- c("https://en.wikipedia.org/wiki/Main_Page", "asdfasfasf")
+
+
+
+unstable_function <- function(the_page) {
+  read_html(the_page)
+}
+
+safe_function <- safely(unstable_function)
+
+map(pages_to_scrape, ~ safe_function(.x)) %>%
+  map("result") %>%
+  compact() 
+

### 2018-10-03 scripts/from_monica/exploratory_3.Rmd
dirichlet with random walk

--- 2018-10-02 scripts/to_monica/exploratory_2.Rmd
@@
 ---
-title: "Dirichlet?"
+title: "More complicated dirichlet"
 author: "Monica Alexander"
-date: "10/1/2018"
+date: "10/2/2018"
 output: html_document
@@
 
-Try and get this dirichlet thing going
+Now that a basic model seems to be working, let's try an build on this to get some more realistic estimates.
+
+Here's the model set-up and notation.
+Note we are indexing everything by sitting period $s$, time $t$ and topic $p$.
+Note that time $t$ refers to the day index within the sitting period (for now...
+maybe later we can add back in the date characteristics such as day of week?
+But probably not important for now).
+
+We are assuming the the probability of topic $p$ on day $t$ and sitting $s$, $\gamma_{stp}$ are Dirichlet distributed; this makes sense because it is the multivariate extension of the Beta distribution:
+
+$$
+\gamma_{stp} \sim Dirichlet(\mu_{stp})
+$$
+
+where the $\mu$'s could be interpreted as the 'true' topic probabilities distributions (less useful to thing about that here because the gammas are estimated to begin with.
+But anyway).
+The main goal of the modeling exercise is to find an appropriate and meaningful functional form for the $\mu$'s.
+In exploratory 2, we tried to model the $\mu$'s with just an intercept, one for each topic and sitting period, and that seem to work okay - but it doesn't allow for variation within a sitting period.
+Let's try a simple time series model:
+
+$$
+\log \mu_{stp} = \alpha_{sp} + \delta_{stp}\\
+\alpha_{s1} = 0 \\
+\alpha_{sp} \sim N(0, 100) \text { for } p>1 \\
+\delta_{s,t,p} \sim N(\delta_{s,t-1,p}, \sigma^2_{s}) \\
+\sigma^2_{s} \sim U(0, 40)
+$$
+
+In words: first line is overall model, second line is constraining first intercept to be zero (for identification purposes), third line is priors on all other intercepts, fourth line is random walk around each intercept, last line is prior on random walk variance.
+
+Let's try and fit this.
 
@@
 library(lubridate)
-library(boot)
 library(rjags)
 library(R2jags)
-library(distortr)
+source("plottrace.R")
 ```
 
-Read in the data
+Read in the data and reduce it down to only a couple of years.
 
@@
 dr <- d %>% 
-  filter(document > ymd("2016-01-01"))
+  filter(document > ymd("2017-08-01"))
 ```
 
-Plot these just to visualize. Note that the topics are really dominated by two particular ones.
+Plot to visualize.
 
@@
 
-Get info about sitting period, day number in sitting period etc. In this period we have 10 different sitting days. Sitting periods usually only have 8 days in them.
+Get info about sitting period, day number in sitting period.
 
@@
 
-Make back into long format. Now we have some covariates!
+Make back into long format.
 
@@
 
-Think about a simple model here.
-The dependent variable is $\gamma_{stp}$, for sitting period $s$, day $t$ and topic $p$.
-This could be a function of: sitting period, the gamma of the same topic the day before, the year....
-
-Start off with
-
-$$
-\gamma_{st,} \sim Dirichlet(\mu_{st,})\\
-\log \mu_{stp} = \alpha_{sp} 
-$$
-
-So just linear in time for each topic and sitting period. Now need to get the data in the right form to fit:
+Now need to get the data in the right form to fit:
 
@@
                   y.stp = y.stp)
-parnames <- c("alpha", "mu.stp")
+parnames <- c("alpha", "mu.stp", "delta")
+
+inits_list <- list()
+inits_list[["delta"]] <- y.stp*0
+
+all_inits <- list()
+for(i in 1:3){
+  all_inits[[i]] <- inits_list
+}
 
@@
             #n.iter = 5000,
+            #inits = all_inits,
             parameters.to.save=parnames,
-            model.file = "model_dirichlet.txt")
+            model.file = "model_dirichlet_2.txt")
 
@@
 mcmc.array <- mod$BUGSoutput$sims.array
+PlotTrace("alpha[1,16]", mcmc.array)
 ```
@@
 
-Plot:
-
 ```{r}

### 2018-10-03 outputs/docs/events/paper.Rmd
Clean up events paper

--- 2018-09-12 outputs/docs/events/paper.Rmd
@@
 ---
-title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
+output:
+  bookdown::pdf_document2:
+    citation_package: natbib
+    keep_tex: true
+    fig_caption: true
+    number_sections: true
+    latex_engine: pdflatex
+    template: svm-latex-ms.tex
+title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions.
+**Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
 author:
-  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
-  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
-date: "`r format(Sys.time(), '%d %B %Y')`"
+- name: Monica Alexander
+  affiliation: University of Toronto
+- name: Rohan Alexander
+  affiliation: Australian National University
+abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
+We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
+We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time.
+Finally, we consider the effect of various events using Bayesian hierarchical Dirichlet regression.
+We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on the short-term."
+keywords: "text analysis, politics, Australia"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+fontfamily: mathpazo
 fontsize: 12pt
-output: 
-  pdf_document:
-    number_sections: true
+toc: FALSE
+# spacing: double
 bibliography: ../bibliography.bib
-abstract: |
-  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017.
-We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].
-
+biblio-style: apsr
+endnote: no
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+library(here)
+library(kableExtra)
+library(knitr)
 library(tidyverse)
+
+yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
+  replace_na(list(Parliament = ""))
+elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
+governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
+keyEconomicDates <- read_csv(here::here("inputs/misc/key_dates-economic.csv"), col_types = cols())
+keyOtherDates <- read_csv(here::here("inputs/misc/key_dates-other.csv"), col_types = cols())
+significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
+missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
+
 ```
@@
 # Introduction
-New governments often go out of their way to be different to the governments they replace.
-For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor.
-Similarly, significant events can alter the course of a government.
-For instance, consider the change in the Howard government after the 9/11 attacks.
-However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party?
-And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?
+Government policy is partly driven by parliamentary discussion.
+Conversely, that same discussion can indicate a government's priorities.
+But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
+For instance, new governments often go to some trouble to be different to the governments they replace, such as Kevin Rudd's apology to Indigenous Australians not being supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax.
+Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
+But it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.
 
-In this paper we use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 to model the topics of discussion in Australian parliaments.
-The advantage of this model is that it allows for topics to be correlated between sitting days, which then allows us to test for changes in topics at various events.
-The events that we focus on are changes in: 1) government; 2) the political environment (as defined by polling or other results); 3) economic conditions; and 4) the significant events (such as the 9/11 attacks or the Bali Bombings).
+In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
+We then use Bayesian hierarchical Dirichlet regression to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
 
-We find [INSERT RESULTS]. We also explored the other direction (the impact of what was said in parliaments on events) but it was difficult to find significant effects.
+We find **[INSERT RESULTS]**.
 
-Our work fits into [WHATEVER IT FITS INTO].
-While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and hence can identify patterns that may otherwise be overlooked.
+Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
+Our use of Bayesian hierarchical Dirichlet regression allows us to construct a counterfactual.
+Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
+While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
 
@@
 # Data
-Following the example of the UK, a text-based record of what was said in Australian parliaments called Hansard has been regularly made available since their establishment.
-While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+## Parliamentary text data
+Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
+This allowed for long time frames and wide comparisons.
+But analysing Hansard records and their equivalents directly are an increasingly viable and popular source of data as new methods and reduced computational costs make larger-scale analysis easier, complementing other measures.
+
+The recent digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
+In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
+And as digitisation methods improve older UK records can be analysed, for instance @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
+In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
+And in the US @GentzkowShapiroTaddy2018 examine congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
+
+[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
 For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
 @Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.
-Both these findings provide reassurance that differences between Hansard and a verbatim record would not be meaningful for this paper.
 
-The parliaments generally make their hansard records available online in PDF formats that can be processed by text readers such as @Ooms2018pdftools.
-Some records such as the early days of the New South Wales parliament have yet to be put through a professional OCR process, although the Google Tesseract engine as implemented by @Ooms2018tesseract can be used to provide a useful first-pass if necessary.
-Hansard records that are still images are not used in this analysis (see the Appendix for more details).
+Australian Hansard records have been analysed for various purposes.
+For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
+And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
 
-Hansard records are available for all six Australian states and the Commonwealth although the period varies (Table 1).
-Here we focus on the lower houses although a similar analysis is possible in a bicameral setting.
+Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
+Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
+There are roughly 54,331 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
+Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
 
-| Parliament | House | Years used | Notes |
-|:------|-----:|---------:|------:|
-| Commonwealth | House of Representatives | 1901 - 2017 | - |
-| Queensland | ? | 1861 - 2017 | - |
-| New South Wales | ? | ? - 2017 | - |
-| Victoria | ? | ? - 2017 | - |
-| Tasmania | ? | ? - 2017 | - |
-| South Australia | ? | ? - 2017 | - |
-| Western Australia | ? | ? - 2017 | - |
+[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
+The records can also be downloaded from the Australian Hansard website.
 
-We start with the PDFs that have been through an OCR process (or compiled more recently using software that makes them readable by default) as supplied by various parliaments (see the Appendix for specific sources).
-We then use the \texttt{PDFtools} R package of @Ooms2018pdftools to extract these as text-based CSV records, and clean the records using functions from the \texttt{Tidyverse} R package of @WickhamHadleyTidyverse, the \texttt{Tidytext} R package of @SilgeRobinson2016 and the [INSERT OTHERS].
-The result is a
+```{r yearsusedtable, echo = FALSE, results = 'asis'}
+
+yearsUsed %>%
+  kable(
+    booktabs = T,
+    align = c('l', 'r', 'r', 'r'),
+    caption = "Hansard records used") %>%
+  kable_styling(font_size = 12)
+
+```
+
+The formatting of the Hansard records changes between the different parliaments and over time.
+We use scripts written in R (@R2018) to convert the PDFs into daily text records.
+An example of the workflow and some reduced-detail scripts are provided in Appendix \@ref(hansardworkflow).
+Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
+An example of the latter issue is that 'the' is often parsed as 'thc'.
+These errors are corrected when they occur at scale and can be identified.
+The percentage of stop-words in each record is reasonably consistent over time.
+This suggests that there is no significant difference in the quality of the parsing over time.
+Details of this process are provided in Appendix \@ref(stopwordsgraph).
+
+These daily records are the main level that we consider in this paper, but we also disaggregated them into individual-level records during the cleaning process.
+Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
+The high dimensional nature of text data means that the appropriate level and focus of the dataset being analysed tends to be specific to a research question.
+For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
+But they are interesting in their own right and @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs.
+
+Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
+For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned, often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
+There is substantial variation in how the person making a statement is identified.
+Again some error is introduced at this stage because of inconsistencies over time and between the parliaments.
+There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.
+
+Text is usually pre-processed before topic models are used.
+The specific steps that we take are to remove numbers and punctuation and to change the words to lower case.
+Then the sentences are deconstructed and each word considered individually.
+**[Need to bundle_ngrams i.e.
+New Zealand is new_zealand.]**
+
+## Additional information
+Data from other sources are needed to complement the parliamentary text data.
+For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
+Also non-Hansard information about the politicians informs our analysis.
+This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.
+
+The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
+However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.
+The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
+An example of the additional information is provided in Appendix \@ref(additionalinformation).
 
 # Model
-The primary model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{STM} R package of @RobertsStewartAiroldiRPackage.
-The basis of this type of topic modelling is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
-In this section a brief overview of both the LDA model and the STM approach is provided and then the specifics of how we consider events in this setting are discussed.
+The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage and a Bayesian discrete choice model.
+In a similar way to @MuellerRauh2018, we use topics to analyse the effect of various events.
+In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
+
+The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
+In this section we provide a brief overview of both the LDA model and the STM.
+We consider the outputs of the topic model as reduced dimension inputs that can be analysed within another model.
+In our case they are inputs to a discrete choice model, and so we then discuss that model.
 
 ## Latent Dirichlet Allocation
-Each day's Hansard record needs to be classified by its topic.
-Sometimes Hansard includes titles that make the topic clear.
+Although more- or less-fine levels of analysis are possible, but here we are primarily interested in considering a day's topics.
+This means that each day's Hansard record needs to be classified by its topics.
+Sometimes Hansard records includes titles that make the topic clear.
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics of each statement in Hansard is to use the latent Dirichlet allocation (LDA) method of @Blei2003latent, for instance as implemented by the R package 'topicmodels' by @Grun2011.
+One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R \texttt{topicmodels} package of @Grun2011.
 
-The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then chooses words, 'terms', that are appropriate to those topics.
-A topic could be thought of as a collection of terms, and a document as a collection of topics.
+The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
+A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions.
 The topics are not specified *ex ante*; they are an outcome of the method.
+In this sense, this approach can be considered unsupervised machine learning.
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
@@
 After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.
-
 More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics.
-For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
-
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
-document_1 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
-  )
-
-document_2 <- tibble(
-  Topics = c(
-  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
-  ),
-  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
-  )
-
-par(mfrow=c(2,1))
-ggplot(document_1, aes(Topics, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over topics for Document 1") +
-  coord_cartesian(ylim = c(0, 0.4))
-
-ggplot(document_2, aes(Topics, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over topics for Document 2") +
-  coord_cartesian(ylim = c(0, 0.4))
-```
-
 Similarly, each topic could be considered a probability distribution over terms.
 To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion.
-For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
-
-```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
-topic_1 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
-  )
-
-topic_2 <- tibble(
-  Terms = c(
-  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
-  ),
-  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
-  )
-
-# par(mar = c(4, 4, 0.1, 0.1))
-ggplot(topic_1, aes(Terms, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over terms for Topic 1") +
-  coord_cartesian(ylim = c(0, 0.4))
-ggplot(topic_2, aes(Terms, Probability)) +
-  geom_point() +
-  theme_classic() +
-  labs(title = "Distribution over terms for Topic 2") +
-  coord_cartesian(ylim = c(0, 0.4))
-```
+Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrates an example with five topics, two documents, and ten terms.
 
@@
 
-The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'.
+<!-- The initial practical step when implementing LDA given a collection of documents is to remove 'stop words'.
 These are words that are common, but that don't typically help to define topics.
-There is a general list of stop words such as: "a"; "a's"; "able"; "about"; "above"...
-An additional list of words that are commonly found in Hansard, but likely don't help define topics is added to the general list.
-These additions include words such as: "act"; "amendment"; "amount"; "australia"; "australian"; "bill"...
-A full list can be found in Appendix \@ref(hansard-stop-word).
-We also remove punctuation and capitalisation.
-The documents need to then be transformed into a document-term-matrix.
+There is a common list of stop words such as: "a"; "an"; and "and".
+However the exact list used depends on research of focus.
+In the case of Australian Hansard, these are words such as: "australia"; "australian"; and "bill".
+Punctuation and capitalisation is also typically removed.
+The documents then need to then be transformed into a document-term-matrix.
 This is essentially a table with a column of the number of times each term appears in each document.
+-->
 
-After the dataset is ready, the R package 'topicmodels' by @Grun2011 can be used to implement LDA and approximate the posterior.
-It does this using Gibbs sampling or the variational expectation-maximization algorithm.
+<!-- After the dataset is ready, the R \texttt{topicmodels} package of @Grun2011 can be used to implement LDA and approximate the posterior.  -->
+
+Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior.
+A summary of these approaches is provided in Appendix \@ref(LDAposteriorestimation).
+The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
+If there is a strong reason for a particular number, then this can be used.
+Otherwise, one way to choose an appropriate number is to use cross validation.
+
+One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter (@blei2012).
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+This motivates the use of the Structural Topic Model, described in the next section.
+
+## Structural Topic Model
+The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
+For instance, we generally have some information about the author and the date that a document was created.
+In the case of Hansard, we know who was speaking and the date they spoke.
+The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
+That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+
+The STM is set-up to most easily include metadata to do with prevalence and content.
+Prevalence relates to the topic proportions in each document.
+For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
+Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
+Content relates to the words that make up each topic.
+For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
+The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each aspect.
+For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
+Similarly, the content meta-data are
+
+As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM:
+
+1.
+As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
+In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3):
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+
+2.
+To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
+Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$:
+$$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$
+
+3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$:
+    a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics.
+    b. Randomly choose a term from the topic-specific multinomial distribution over terms.
+
+We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+We consider both topic prevalence and content to be functions of time.
+The choice of the number of topics to use in the model is a situation-specific compromise.
+We use standard diagnostic techniques with cross validation to decide on 80 **[UPDATE]** topics.
+More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
+
+Figure \@ref(fig:exampletopics) illustrates an output of the STM.
+This illustrative model only considers data from the House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be allocated to one of ten topics and highlights how the prominence of these topics changes over time.
+**[RUN AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED FROM THE GENERAL ONE!.]**
+
+```{r exampletopics, echo=FALSE, fig.cap="Estimated 10-topic-proportion", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/topics_example.png"))
+```
+
+### Considering events
+We are interested in the effect of political, economic, and other events on Australian parliamentary discussion.
+Political events are those related to a change of government or an election.
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession.
+Other events are those such as the 9/11 attacks, or the Bali Bombing.
+The full list of events that we consider is detailed in Appendix @ref(eventdetails).
+
+There are many ways to statistically consider the effect of events.
+One way would be to ignore the time series aspect and just group the topic proportions by each event and then run multinomial tests for whether the groups are different.
+Another would be to consider some type of multinomial logistic regression.
+Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which can be used to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
+
+**[MONICA  - LOOK AT THESE OR OTHER OPTIONS AND DECIDE ON A WAY.
+NEEDS TO ALLOW FOR SHORT AND LONG RUN AND ALSO ALLOW COINCIDENCE OF EVENTS.
+WE ONLY CONSIDER 20 TOPICS BELOW, BUT THAT'S UNDERDONE AND THE METHODS NEED TO ALLOW FOR MORE.]**
+
+We currently consider events in two ways.
+The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
+This illustrates the differences between the topics.
+The second is by including incrementing variables in the prevalence metadata This groups each day by events and we can then conduct significance tests.
+Unfortunately both of these do not consider short-term effects.
+
+**[Use tf-idf between them as illustrative instead? Use that other measure of difference?]**
+<!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.  -->
+
+<!-- Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
+It will be higher for words that are rarely used across all documents, but commonly used in a document.
+For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
+However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
+-->
+
+<!-- When we consider events using tf-idf, we gather terms from more than one day.
+We define groups of days that are roughly analogous to sitting periods.
+If there is more than a week between a day then we define a new group, otherwise the day is in the existing group.
+We use various measures **(Text2vec R package has some?
+or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
+-->
+
+# Results
+We are interested in considering the effect of various events on what is talked about in Australia's parliaments.
+Each of those parliaments are treated independently here.
+Future work could expand the model to better understand, and allow, for correlation between them.
+
+We consider four types of events and group the day's topic proportions by these events.
+One unfortunate effect of this is that we only allow an event to have a long-run effect and ignore short-run effects.
+Another is that we ignore coincidence of events.
+
+Figure \@ref(fig:electionsevents) shows the grouping by election.
+If elections had significant effects on the discussion in parliament then there would be considerable change between groups.
+However changes generally appear to be longer-term rather than election to election.
+
+```{r electionsevents, echo=FALSE, fig.cap="Topic proportions grouped by elections", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_election.png"))
+```
+
+Figure \@ref(fig:governmentevents) shows the grouping by government.
+This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election.
+Similarly, John Howard's three terms are all considered the one government for our purposes.
+
+Here we see much more difference between adjacent events. This suggests that new governments tend to talk about different topics than the government they replace.
+
+```{r governmentevents, echo=FALSE, fig.cap="Topic proportions grouped by government", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_government_change.png"))
+```
+
+Figure \@ref(fig:economicevents) shows the grouping by major economic changes. There are considerable changes between adjacent events.
+
+```{r economicevents, echo=FALSE, fig.cap="Topic proportions grouped by economic events", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_economic_changes.png"))
+```
+
+Figure \@ref(fig:otherevents) shows the grouping by major other events, such as the 9/11 attacks.
+
+```{r otherevents, echo=FALSE, fig.cap="Topic proportions grouped by other events", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_other_changes.png"))
+```
+
+Another way to consider the effect of events is by including incrementing variables in the prevelance metadata.
+This then gets included in the topic modelling and the significance to each topic can be computed.
+Table \@ref(tab:dodgysignificances) summarises these by the type of dummy and the topic.
+At the five per cent level the events that we consider were significant for eight topics.
+This significance tended to be correlated, especially for economic and other events.
+
+```{r dodgysignificances, echo = FALSE, results = 'asis'}
+
+significances %>% 
+  kable(booktabs = T, caption = "Significance of dummy") %>%
+  kable_styling(font_size = 12)
+
+```
+
+For instance, all of the incrementing variables have a significant effect on the prevalence of Topic 1.
+Table \@ref(tab:topwordssig) shows that this has to do with tariffs and trade.
+On the other hand, Topic 2 has to do with aspects of daily life such as community and children, and Topic 3 has to do with legal issues and neither is significant.
+This is not surprising given the centrality of these concerns at all times.
+
+```{r topwordssig, echo = FALSE, results = 'asis'}
+
+top_words %>% 
+  kable(booktabs = T, caption = "Top words for each topic") %>%
+  kable_styling(font_size = 12)
+
+```
+
+# Summary and conclusions
+In this paper we examined what was said in Australia's parliaments.
+We downloaded and parsed PDFs for Australian states and federal parliaments.
+We then used a text model to group the discussions into topics and analysed the effect of various events on the distribution of the discussion.
+
+In general we found that changes in government changed the distribution of topics discussed in parliament, but that elections did not.
+We found that significant events such as 9/11 had substantial and lasting changes, but that with certain exceptions, economic events did not.
+
+Text analysis has well-known biases and weaknesses and is a complement to more detailed analysis such as qualitative methods and case studies.
+We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
+
+<!-- What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation. -->
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+# Hansard details
+
+## Hansard sources {#hansardsources}
+Where from?
+
+Which years are being used (not non-OCRd)
+
+[IS THIS BEING REFERENCED IN THE TEXT????]
+
+## Example Hansard page {#examplehansardpage}
+
+Figure \@ref(fig:asdf)
+
+```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
+```
+
+## Known Hansard issues {#knownhansardissues}
+
+The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper.
+However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
+
+Which PDFs are missing or have no content, etc.
+
+```{r missingdays, echo = FALSE, results = 'asis'}
+
+missing_days %>% 
+  kable(booktabs = T, caption = "Missing days") %>%
+  kable_styling(font_size = 12)
+
+```
+
+Notes: Positive means I am missing some, Negative means I have too many.
+Source: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear
+
+## Example Hansard PDf to text record workflow {#hansardworkflow}
+Example of the workflow from PDF to text
+
+These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
+In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
+
+## Stopwords over time {#stopwordsgraph}
+Insert graph of stop words over time.
+
+\newpage
+
+# Additional information {#additionalinformation}
+**TBD**
+
+\newpage
+
+# word2vec alternative {#word2vec}
+An alternative approach that follows @Taddy2015.
+
+\newpage
+
+# Topic modelling example and details
+## Examples {#LDAexample}
+For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
+
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
+
+tibble(
+  Topics = rep(c("1", "2", "3", "4", "5"), 2),
+  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
+  Document = c(rep("Document 1", 5), rep("Document 2", 5))
+  ) %>%
+  ggplot(aes(Topics, Probability, colour = Document)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip()  +
+  scale_colour_viridis_d()
+
+```
+
+For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
+
+```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
+tibble(
+  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
+  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
+  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
+  ) %>%
+  ggplot(aes(Terms, Probability, colour = Topics)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip() +
+  scale_colour_viridis_d()
+
+```
+
+## Posterior estimation {#LDAposteriorestimation}
 Following @SteyversGriffiths2006 and @Darling2011, the Gibbs sampling process attempts to find a topic for a particular term in a particular document, given the topics of all other terms for all other documents.
@@
 
-The choice of the number of topics, *k*, affects the results, and must be specified *a priori*.
-If there is a strong reason for a particular number, then this can be used.
-Otherwise, one way to choose an appropriate number is to use a test and training set process.
-Essentially, this means running the process on a variety of possible values for *k* and then picking an appropriate value that performs well.
-
-One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter (@blei2012).
-It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
-Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-This motivates the use of the Structural Topic Model, described in the next section.
-
-## Structural Topic Model
-### Overview and example
-[TBD]
-
-Note that each of the states and the Commonwealth are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.
-
-### Considering events
-[TBD]
-
-# Results
-## Political events
->*When you change the government, you change the country.* Paul Keating.
-
-Change of government.
-
-## Polling events
->*The only poll that matters is the one on election day.* John Howard.
-
-[TBD]
-
-## Economic events
-
-Major economic changes.
-
-[TBD]
-
-## External events
->*Events, dear boy, events.* Attributed to Harold Macmillan.
-
-Major event such as 9/11 attacks, or economic change.
-
-# Summary and conclusions
-What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation.
-
-Text analysis has well-known biases and weaknesses and is a complement to more detailed analysis such as qualitative methods and case studies.
-We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
-
-\newpage
-
-# Appendix
-## Selection of number of topics
+## Selection of number of topics {#selecttopicnumber}
+**[TBD]**
 
 ## Robustness of results
+**[IS THIS BEING USED?]**
 Here we change the number of sitting days considered either side of an event.
@@
 
-## Document sources
-Where from?
+\newpage
 
-Which years are being used (not non-OCRd)
+# Events {#eventdetails}
+
+```{r governments, echo = FALSE, results = 'asis'}
+
+governments %>% 
+  kable(booktabs = T, caption = "Change in governments") %>%
+  kable_styling(font_size = 12)
+
+```
+
+```{r elections, echo = FALSE, results = 'asis'}
+
+elections %>% 
+  filter(election == 1) %>% 
+  select(year, electionDate, electionWinner) %>% 
+  kable("latex", booktabs = T, caption = "Elections") %>%
+  kable_styling(font_size = 12)
+
+```
+
+```{r economics, echo = FALSE, results = 'asis'}
+
+keyEconomicDates %>% 
+  kable(booktabs = T, caption = "Key economic events") %>%
+  kable_styling(font_size = 12)
+
+```
+
+```{r others, echo = FALSE, results = 'asis'}
+
+keyOtherDates %>% 
+  kable(booktabs = T, caption = "Key other events") %>%
+  kable_styling(font_size = 12)
+
+```
+
+Add the graphs and procedures.
 

### 2018-10-03 outputs/docs/events/svm-rmarkdown-article-example.tex
Clean up events paper

@@
 
-\title{The Effect of Events on Australian Parliamentary Discussion (1870--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
+\title{The Effect of Events on Australian Parliamentary Discussion (1851--2017) \thanks{Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi
 Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris
@@
              pdfkeywords = {text analysis, politics, Australia},  
-            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1870--2017)},
+            pdftitle={The Effect of Events on Australian Parliamentary Discussion (1851--2017)},
             colorlinks=true,
@@
 correlation between days and steady changes over time. Finally, we
-consider various events using Bayesian regression with a
-Dirichlet-distributed response variable. We find that: 1) elections are
-associated with topic changes only when the party in power changes; 2) a
-change in government can be associated with topic changes even if the
-party in power does not change; 3) economic events, such as financial
-crises, have less significant and persistent effects than other events
-such as terrorist attacks. Our findings have implications for how we
-think about the longer-term trajectory of government policy as the media
-cycle becomes increasingly focused on short-term events.
+consider the effect of various events using Bayesian hierarchical
+Dirichlet regression. We find that: 1) elections are associated with
+topic changes only when the party in power changes; 2) a change in
+government can be associated with topic changes even if the party in
+power does not change; 3) economic events, such as financial crises,
+have less significant and persistent effects than other events such as
+terrorist attacks. Our findings have implications for how we think about
+the longer-term trajectory of government policymaking as the media cycle
+becomes increasingly focused on the short-term.
 
@@
 for dimensionality reduction and to impose structure such as correlation
-between days and changes over time. We then use a simple discrete choice
-model to examine changes at various types of events, including: changes
-in government; changes in the political environment (as defined by
-polling or other results); changes in economic conditions; and other
-significant events (such as the 9/11 attacks or the Bali bombings).
+between days and changes over time. We then use Bayesian hierarchical
+Dirichlet regression to examine changes at various types of events,
+including: changes in government; changes in the political environment
+(as defined by polling or other results); changes in economic
+conditions; and other significant events (such as the 9/11 attacks or
+the Bali bombings).
 
@@
 parliamentary text records from multiple Australian parliaments. Our use
-of a discrete choice model - essentially a time series multinomial model
-of choices - allows us to construct a counterfactual. Our work fits into
-a growing literature that considers text as an input to more usual
-quantitative techniques, rather than requiring separate analysis. While
-using text as data has well-known shortcomings, it allows larger-scale
-analysis that would not be viable using less-automated approaches and so
-it can identify patterns that may otherwise be overlooked.
+of Bayesian hierarchical Dirichlet regression allows us to construct a
+counterfactual. Our work fits into a growing literature that considers
+text as an input to more usual quantitative techniques, rather than
+requiring separate analysis. While using text as data has well-known
+shortcomings, it allows larger-scale analysis that would not be viable
+using less-automated approaches and so it can identify patterns that may
+otherwise be overlooked.
 
@@
 Appendix \ref{examplehansardpage} provides an example of what a Hansard
-PDF looks like. There are 65,000 \textbf{{[}UPDATE{]}} days worth of
-publicly available Hansard records across the state and federal
+PDF looks like. There are roughly 54,331 \textbf{{[}UPDATE{]}} days
+worth of publicly available Hansard records across the state and federal
 parliaments (Table \ref{tab:yearsusedtable}). Our data cleaning process
@@
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{12}{14}\selectfont
 \begin{tabular}[t]{rrrrr}
@@
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{12}{14}\selectfont
 \begin{tabular}[t]{llllll}
@@
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{12}{14}\selectfont
 \begin{tabular}[t]{rll}
@@
 \centering
-\fontsize{8}{10}\selectfont
+\fontsize{12}{14}\selectfont
 \begin{tabular}[t]{ll}

### 2018-10-03 outputs/docs/events/paper.Rmd
Add NSW scraper

@@
     citation_package: natbib
-    keep_tex: true
+    keep_tex: false
     fig_caption: true
@@
 But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
-For instance, new governments often go to some trouble to be different to the governments they replace, such as Kevin Rudd's apology to Indigenous Australians not being supported by his predecessor John Howard, and then one of Tony Abbott's first acts was to repeal his predecessor Kevin Rudd's carbon tax.
-Similarly, significant events such as the 9/11 attacks or the Great Recession have often altered the course of a government.
-But it is not so clear which events drive changes, for how long these changes persist, and what was given up due to the change.
+For instance, think of how new governments often go to some trouble to be different to the one they replace.
+Or think of how events such as the 9/11 attacks altered government priorities.
 
-In this paper we examine text records of what was said in Australian state and federal parliaments from the mid-1800s through to 2017.
+In this paper we examine text records of what was said in Australian state and federal parliaments.
+Our earliest record is from 1851 and we consider the time period through to 2017.
 We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
@@
 
-We find **[INSERT RESULTS]**.
+We find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
 
 Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
-Our use of Bayesian hierarchical Dirichlet regression allows us to construct a counterfactual.
+The Bayesian hierarchical Dirichlet regression allows us to construct a counterfactual.
 Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
@@
 These errors are corrected when they occur at scale and can be identified.
+
 The percentage of stop-words in each record is reasonably consistent over time.
@@
 Details of this process are provided in Appendix \@ref(stopwordsgraph).
-
-These daily records are the main level that we consider in this paper, but we also disaggregated them into individual-level records during the cleaning process.
-Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
-The high dimensional nature of text data means that the appropriate level and focus of the dataset being analysed tends to be specific to a research question.
-For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
-But they are interesting in their own right and @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs.
-
-Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
-For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned, often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
-There is substantial variation in how the person making a statement is identified.
-Again some error is introduced at this stage because of inconsistencies over time and between the parliaments.
-There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.
-
+We mainly use Hansard records on a daily basis in this paper.
 Text is usually pre-processed before topic models are used.

### 2018-10-03 outputs/docs/mentions/paper.Rmd
Add NSW scraper

@@
 To construct measures of centrality, or importance, I use the Hansard records for the Australian Commonwealth, and the six states over the period that they are available.
-The availability of this data is summarised in Table 1.
+For details on the dataset please see Alexander and Alexander.
+Daily Hansard records were the main level that we considered in that paper, but here were disaggregated them into individual-level records.
+Sometimes these are just short interjections or notes that are not specific to any particular politician, such as 'Honourable members interjecting'.
+The high dimensional nature of text data means that the appropriate level and focus of the dataset being analysed tends to be specific to a research question.
+For instance, in our paper interjections are not important because they do not usually contribute much to defining the topics being discussed.
+But they are interesting in their own right and @Whyte2017 analysed them in a Canadian context for the period 1926 to 2015 to find that female MPs were more likely to be interrupted than male MPs.
 
-[INSERT TABLE 1]
+Usually the disaggregation into individual-level records is done by identifying politicians' names in particular patterns.
+For instance, when Hansard is indicating that a particular person is speaking, as opposed to being mentioned, often the name is in upper case, for instance 'Mr WHITLAM' or 'Mr MENZIES'; followed by a dash or colon; or are next to some title within brackets.
+There is substantial variation in how the person making a statement is identified.
+Again some error is introduced at this stage because of inconsistencies over time and between the parliaments.
+There is considerable variance but on average each daily record had 250 **[UPDATE]** individual-level records, resulting in roughly 15 million rows **[UPDATE]** across the state and federal parliaments.
 
-For more information on this dataset please see the Appendix.
+For more information on this dataset please see Alexander and Alexander and also Appendix X.
 

### 2018-10-03 scripts/to_scrape_websites/get_1870-1995_PDFs_NSW.R

@@ -1,0 +1,52 @@
+#### Preamble ####
+# Purpose: This file gets NSW Hansard PDF files from the parliament website.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 3 October 2018
+# Prerequisites: Need a list of csvs to walk through - NSW_addresses.csv
+# To do: -
+
+
+#### Set up workspace ####
+# Load libraries
+library(tidyverse)
+# update.packages()
+
+
+#### Create lists of URLs to scrape and file names to save the PDF as ####
+data_to_scrape <- read_csv("scripts/to_scrape_websites/addresses/NSW_addresses.csv")
+
+# Randomise the order
+set.seed(1234)
+data_to_scrape <- data_to_scrape %>% 
+  mutate(orderByThisRandom = sample(1:nrow(data_to_scrape))) %>% 
+  arrange(orderByThisRandom) %>% 
+  select(-orderByThisRandom)
+
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+
+save_name <- paste0("pdfs/", save_name)
+
+dir.create("pdfs")
+
+
+#### Create the function that will visit address_to_visit and save to save_name files ####
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  # Helpful so that you know progress when running it on all the records
+    Sys.sleep(sample(20:30, 1)) # Space out requests by somewhere between 20 and 30 seconds each
+  }
+
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+
+#### Walk through the lists and get the PDFs ####
+# save_name <- save_name[1:2] # testing it works
+# address_to_visit <- address_to_visit[1:2] # testing it works
+# save_name <- save_name[3:length(save_name)] # main run
+# address_to_visit <- address_to_visit[3:length(address_to_visit)] # main run
+
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))

### 2018-10-04 scripts/from_monica/exploratory_4.Rmd
progress on the means model

---
title: "Dirichlet with government groups"
author: "Monica Alexander"
date: "10/3/2018"
output: html_document
---

Now we have a model going, let's try and add in some groupings based on changes in government. Hopefully then we will be able to visualize the 'average' topic distributions across governments. Let's try

$$
\gamma_{stp} \sim Dirichlet(\mu_{stp}) \\ 
\log \mu_{stp} = \alpha_{sp} + \delta_{stp}\\
\alpha_{s1} = 0 \\
\alpha_{sp} \sim N(\eta_{g[s]}, \sigma^2_g) \text { for } p>1 \\
\delta_{s,t,p} \sim N(\delta_{s,t-1,p}, \sigma^2_{\delta}) \\
\sigma^2_{\delta} \sim U(0, 40)
$$

```{r}
library(tidyverse)
library(lubridate)
library(rjags)
library(R2jags)
source("plottrace.R")
```

```{r}
d1 <- read_csv("dates_of_gov_and_election.csv")
d2 <- read_csv("gammas_model_prevalence_years_k_20.csv")
d <- d2 %>% 
  left_join(d1 %>% rename(document = allDates))
```

```{r}
dr <- d %>% 
  filter(electionCounter %in%41:42)
```

```{r}
dr %>% 
  ggplot(aes(document, gamma, fill = factor(topic))) + geom_bar(stat = "identity")
```

```{r}
unique(dr$electionCounter)
```

Get info about sitting period, day number in sitting period.

```{r}
dr_wide <- dr %>% 
  spread(topic, gamma)

dr_wide <- dr_wide %>% mutate(day_diff = document - lag(document))

k <- 1
dr_wide$group <- NA
for(i in 1:nrow(dr_wide)){
  if(is.na(dr_wide$day_diff[i])|dr_wide$day_diff[i]<7){
    k <- k
  }
  else{
    k <- k+1
  }
  dr_wide$group[i] <- k
}

dr_wide <- dr_wide %>% group_by(group) %>% 
  mutate(day_number = row_number())

dr_long <- dr_wide %>% 
  gather(topic, gamma, -document, -group, -day_number, -day_diff, -electionCounter, -governmentChangeDate) %>% 
  arrange(document)

```

Now need to get the data in the right form to fit:

```{r}
ntopics <- 20
y.stp <- array(NA, c(max(dr_long$group), max(dr_long$day_number), 20))

for (i in 1:ntopics){
  y.stp[,,i] <- dr_long %>% 
  ungroup() %>% 
  filter(topic==i) %>% 
  dplyr::select(-topic, -day_diff, -document, -electionCounter, -governmentChangeDate) %>% 
  spread(day_number, gamma) %>% 
  dplyr::select(-group) %>% 
  as.matrix()
}

nsittings <- max(dr_long$group)
ndays.s <- dr_long %>% group_by(group) %>% summarise(days = max(day_number)) %>% dplyr::select(days) %>% pull()

election.s <- (dr_long %>% group_by(group) %>% summarise(election = electionCounter[row_number()==1]) %>% dplyr::select(election) %>% pull()) - min(dr_long$electionCounter) + 1

nelections <- length(unique(dr_long$electionCounter))

```

Run the model:

```{r}
jags.data <- list(nsittings = nsittings,
                  nelections = nelections,
                  ndays.s = ndays.s, 
                  election.s = election.s,
                  ntopics = ntopics, 
                  y.stp = y.stp)
parnames <- c("alpha", "mu.sp", "mu.alpha")

mod <- jags(data = jags.data, 
            #n.iter = 5000,
            parameters.to.save=parnames,
            model.file = "model_dirichlet_means.txt")

max(mod$BUGSoutput$summary[,"Rhat"])
mcmc.array <- mod$BUGSoutput$sims.array
PlotTrace("mu.alpha[1,1]", mcmc.array)
```

Extract and plot the results:

```{r}
df_res <- c()
for(i in 1:nsittings){
  for(j in 1:ndays.s[i]){
    for(k in 1:ntopics)
    df_res <- rbind(df_res, tibble(group = i, day = j, topic = k, 
                                   document =  dr_long$document[dr_long$group==i&dr_long$day_number==j&dr_long$topic==k],
                                   median = (median(mcmc.array[,,paste0("mu.sp[",i,",",k,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("mu.sp[",i,",",k,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("mu.sp[",i,",",k,"]")], 0.025))
    ))
  }
}
```

```{r}
df_res %>% 
ggplot(aes(day, median, fill = factor(topic))) + geom_line(aes(color = factor(topic))) + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  facet_wrap(~group)+
  geom_point(data = dr_long, aes((day_number), gamma, color = factor(topic)))
```

Pull out the means by election and have a look

```{r}
mu_res <- c()
for(i in 1:nelections){
  for(j in 1:ntopics)
    mu_res <- rbind(mu_res, tibble(election = i, topic = j, 
                                   median = (median(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.025))
    ))
}
```

```{r}
mu_res %>% 
  ggplot(aes(election, median, color = factor(election))) + 
  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
  facet_wrap(~topic)
```

Have a look at the alphas

```{r}
alpha_res <- c()
for(i in 1:nsittings){
  for(j in 1:ntopics)
    alpha_res <- rbind(alpha_res, tibble(sitting = i, topic = j, election = election.s[i],
                                   median = (median(mcmc.array[,,paste0("alpha[",i,",",j,"]")])),
                                   upper = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.975)),
                                   lower = (quantile(mcmc.array[,,paste0("alpha[",i,",",j,"]")], 0.025))
    ))
}
```

```{r}
ggplot(alpha_res, aes(median, group = factor(election), color = factor(election))) + 
  geom_density() + facet_wrap(~topic)
```

```{r}
alpha_res %>% 
  ggplot(aes(sitting, median, color = factor(election))) + geom_point() + facet_wrap(~topic)
```

### 2018-10-04 outputs/docs/events/paper.Rmd
Start states polarisation paper

@@
 title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions.
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions.
 **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."

### 2018-10-04 outputs/docs/events/paper.Rmd
Minor updates to paper

--- 2018-10-03 outputs/docs/events/paper.Rmd
@@
 title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions.
-**Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
+thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
 author:
@@
 abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
-We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
-We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time.
-Finally, we consider the effect of various events using Bayesian hierarchical Dirichlet regression.
+We first create a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
+To reduce the dimensionality of this dataset we then use a topic model that allows correlation and a steady change over time.
+Finally, we consider the effect of various events using a Bayesian hierarchical Dirichlet model.
 We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
-Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on the short-term."
+Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on short-term events."
 keywords: "text analysis, politics, Australia"
@@
 But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
-For instance, think of how new governments often go to some trouble to be different to the one they replace.
-Or think of how events such as the 9/11 attacks altered government priorities.
+For instance, think of how a new government often goes to some trouble to appear different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
 
@@
 Our earliest record is from 1851 and we consider the time period through to 2017.
-We use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 for dimensionality reduction and to impose structure such as correlation between days and changes over time.
-We then use Bayesian hierarchical Dirichlet regression to examine changes at various types of events, including: changes in government; changes in the political environment (as defined by polling or other results); changes in economic conditions; and other significant events (such as the 9/11 attacks or the Bali bombings).
+The dataset is detailed in Section \@ref(data).
+We use a topic model for dimensionality reduction and to allow for correlation between topics and steady changes over time.
+We then analyse the topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
+These events include: changes in government or elections; changes in economic conditions; and other significant events such as the 9/11 attacks.
+The models are detailed in Section \@ref(model).
 
-We find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+Section \@ref(results) details our results, but broadly we find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+**[More here on the nature of the differences.]**
 
-Our paper applies a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments.
-The Bayesian hierarchical Dirichlet regression allows us to construct a counterfactual.
-Our work fits into a growing literature that considers text as an input to more usual quantitative techniques, rather than requiring separate analysis.
-While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
+In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events.
+From a data perspective we contribute **[X]**.
+From a methods perspective, we contribute **[Y]**.
+Our model ican be used in many settings where the results of topic models need to be further analysed.
+
+Our work is cross-disciplinary and in the traditions of political economy, economic history, political science and statistics.
+It contributes a growing modern quantitative social sciences literature that considers text as an input to more usual techniques, rather than requiring separate analysis.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
 
@@
 Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
-Additionally, there is a more limited set of XML records available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
+Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
 There are roughly 54,331 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
@@
 ## Additional information
+**[Not sure this is being used - might be better in the other paper.]**
 Data from other sources are needed to complement the parliamentary text data.
@@
 # Model
-The main model that we use in this paper is the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage and a Bayesian discrete choice model.
-In a similar way to @MuellerRauh2018, we use topics to analyse the effect of various events.
+The models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and Bayesian hierarchical Dirichlet analysis model.
+In a similar way to @MuellerRauh2018, we use topics as an input to another model, in our case to analyse the effect of various events.
 In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
@@
 We consider the outputs of the topic model as reduced dimension inputs that can be analysed within another model.
-In our case they are inputs to a discrete choice model, and so we then discuss that model.
+We then discuss the Bayesian hierarchical Dirichlet analysis model that we use for this purpose.
 
@@
 
-### Considering events
+## Analysis model
 We are interested in the effect of political, economic, and other events on Australian parliamentary discussion.
 Political events are those related to a change of government or an election.
-Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or the Great Recession.
-Other events are those such as the 9/11 attacks, or the Bali Bombing.
-The full list of events that we consider is detailed in Appendix @ref(eventdetails).
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency.
+Other events are those such as the 9/11 attacks.
+The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
 
-There are many ways to statistically consider the effect of events.
-One way would be to ignore the time series aspect and just group the topic proportions by each event and then run multinomial tests for whether the groups are different.
-Another would be to consider some type of multinomial logistic regression.
-Options that would take advantage of the time series nature of our data include: autoregressive moving average (ARMA) models which can be used to test for structural breaks  **[REFERENCE?]**; or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model.
+<!-- **[Actually, maybe this whole paragraph not needed?]** There are many ways to consider the effect of events.
+One is to summarise the topic proportions by each event and then run multinomial tests for whether the groups are different, although this does not take full advantage of the frequency of our data.
+Another is to consider a variant of multinomial logistic regression, but then events would be constrained to have an effect in certain ways.
+An autoregressive moving average (ARMA) model could be used to test for structural breaks, but **[something]**.
+Or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model, but **[something]**.
+-->
 
-**[MONICA  - LOOK AT THESE OR OTHER OPTIONS AND DECIDE ON A WAY.
-NEEDS TO ALLOW FOR SHORT AND LONG RUN AND ALSO ALLOW COINCIDENCE OF EVENTS.
-WE ONLY CONSIDER 20 TOPICS BELOW, BUT THAT'S UNDERDONE AND THE METHODS NEED TO ALLOW FOR MORE.]**
+One output of topic modelling is a probability distribution over the topics for each document.
+In our case the documents are each day's text.
+We analyse events by focusing on those proportions, $\gamma$, which we index by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$.
+Note that time $t$ refers to the day index within a sitting period which is any collection of days separated from other days by at least a week.
+Our analysis model is:
 
-We currently consider events in two ways.
+\begin{align}
+\gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ 
+\log \mu_{stp} &= \alpha_{sp} + \delta_{stp}. (\#eq:meanforgammas) \\
+\alpha_{s1} &= 0 \\
+\alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 \\
+\delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) \\
+\sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40) 
+\end{align}
+
+Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
+The Dirichlet distribution is the multivariate extension of the Beta distribution, and the parameter controls where the 'weight' of the distribution lies.
+Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$ which is **X**, and $\delta_{stp}$, which is **Y**.
+These are themselves parameters.
+The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
+We consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **A** and a variance that depends on **B**.
+Similarly, $\delta_{stp}$ is modelled as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution.
+
+**[Does the variance parameter used in Equation 4 need to be specified too?]**
+
+An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
+
+<!-- We currently consider events in two ways.
 The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
@@
 Unfortunately both of these do not consider short-term effects.
+-->
 
-**[Use tf-idf between them as illustrative instead? Use that other measure of difference?]**
+<!-- **[Use tf-idf between them as illustrative instead? Use that other measure of difference?]** -->
+
 <!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics.  -->
@@
 We are interested in considering the effect of various events on what is talked about in Australia's parliaments.
-Each of those parliaments are treated independently here.
+Each of the parliaments and their houses are treated independently here.
 Future work could expand the model to better understand, and allow, for correlation between them.
@@
 We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
+
+While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
 
@@
 ## Selection of number of topics {#selecttopicnumber}
+
 **[TBD]**
@@
   kable(booktabs = T, caption = "Change in governments") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
   kable("latex", booktabs = T, caption = "Elections") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
   kable(booktabs = T, caption = "Key economic events") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
   kable(booktabs = T, caption = "Key other events") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
 
+# Analysis model {#modeldetailsandsimulation}
+
+Here we illustrate the validity of our analysis model using simulated data.
+
+\newpage
+
 # References

### 2018-10-04 outputs/docs/events/paper.Rmd
Update paper

@@
 
-In this paper we examine text records of what was said in Australian state and federal parliaments.
-Our earliest record is from 1851 and we consider the time period through to 2017.
-The dataset is detailed in Section \@ref(data).
+In this paper we examine text records of what was said in Australian state and federal parliaments. Our earliest record is from 1851 and we consider the time period through to 2017. 
+<!-- The dataset is detailed in Section \@ref(data).  -->
 We use a topic model for dimensionality reduction and to allow for correlation between topics and steady changes over time.
@@
 These events include: changes in government or elections; changes in economic conditions; and other significant events such as the 9/11 attacks.
-The models are detailed in Section \@ref(model).
+<!-- The models are detailed in Section \@ref(model). -->
 
-Section \@ref(results) details our results, but broadly we find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+<!-- Section \@ref(results) details our results, but broadly  -->
+We find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
 **[More here on the nature of the differences.]**
@@
 In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events.
-From a data perspective we contribute **[X]**.
-From a methods perspective, we contribute **[Y]**.
-Our model ican be used in many settings where the results of topic models need to be further analysed.
+From a data perspective we contribute **[?????]**.
+From a methods perspective, we contribute **[?????]**.
+Our model can be used in many settings where the results of topic models need to be further analysed.
 
 Our work is cross-disciplinary and in the traditions of political economy, economic history, political science and statistics.
-It contributes a growing modern quantitative social sciences literature that considers text as an input to more usual techniques, rather than requiring separate analysis.
+It contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
@@
 ## Analysis model
-We are interested in the effect of political, economic, and other events on Australian parliamentary discussion.
-Political events are those related to a change of government or an election.
-Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency.
-Other events are those such as the 9/11 attacks.
-The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
 
@@
 
-One output of topic modelling is a probability distribution over the topics for each document.
-In our case the documents are each day's text.
-We analyse events by focusing on those proportions, $\gamma$, which we index by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$.
+The main output of the STM that is of interest to us is the share of each topic in each document.
+We would like to know how those shares change given events.
+But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
+Instead, we put together a Bayesian hierarchical Dirichlet model that takes those shares as an input.
+
+We index each proportion, $\gamma$, by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$.
 Note that time $t$ refers to the day index within a sitting period which is any collection of days separated from other days by at least a week.
@@
 \gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ 
-\log \mu_{stp} &= \alpha_{sp} + \delta_{stp}. (\#eq:meanforgammas) \\
-\alpha_{s1} &= 0 \\
-\alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 \\
-\delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) \\
-\sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40) 
+\log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\
+\alpha_{s1} &= 0 (\#eq:zeroconstraint)\\
+\alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\
+\delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\
+\sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance)  
 \end{align}
+
+**[Does the variance parameter used in Equation 4 need to be specified too?]**
 
@@
 The Dirichlet distribution is the multivariate extension of the Beta distribution, and the parameter controls where the 'weight' of the distribution lies.
-Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$ which is **X**, and $\delta_{stp}$, which is **Y**.
+Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which means the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
 These are themselves parameters.
 The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
-We consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **A** and a variance that depends on **B**.
-Similarly, $\delta_{stp}$ is modelled as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution.
 
-**[Does the variance parameter used in Equation 4 need to be specified too?]**
+Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
+Equation \@ref(eq:alphasp) shows how we consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **[SOMETHING]** and a variance that depends on **[SOMETHING ELSE]**.
+Similarly, Equation \@ref(eq:deltasp) show how we model $\delta_{stp}$  as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution in Equation \@ref(eq:randomwalkvariance), that is, a random walk around each intercept.
 
-An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
+We run the model in Stan using the \texttt{RStan} package of @RStan. An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
 
@@
 Future work could expand the model to better understand, and allow, for correlation between them.
+
+Political events are those related to a change of government or an election.
+Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency.
+Other events are those such as the 9/11 attacks.
+The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
 

### 2018-10-05 scripts/to_model_topics/topic_modelling_stm-elections_focus.R
Get heldout working for topics selection

@@ -3,7 +3,7 @@
 # Purpose: Create topics, for the words used in each day of Hansard
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 28 September 2018
+# Last updated: 5 October 2018
 # Prerequisites:
 # Issues:
 
@@ -28,8 +28,8 @@ library(tidyverse)
 # Load Hansard words by day
 load("outputs/big_files_do_not_push/all_hansard_words_by_date.Rda") # Takes 30 sec or so
 # Load the metadata
-election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
-hansard_dates <- read_csv("inputs/misc/hansard_dates.csv")
+election_dates <- read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
+hansard_dates <- read_csv("inputs/misc/hansard_dates.csv", col_types = cols())
 governmentChanges <- read_csv("inputs/misc/change_of_pm.csv", col_types = cols())
 keyEconomicDates <- read_csv("inputs/misc/key_dates-economic.csv", col_types = cols())
 keyOtherDates <- read_csv("inputs/misc/key_dates-other.csv", col_types = cols())
@@ -332,31 +332,34 @@ summary(prep), topics = 1)
 
 
 many_models <-
-  data_frame(K = c(10, 20)) %>%
-  mutate(topic_model = future_map(
+  data_frame(K = c(20, 40, 60, 80, 100)) %>%
+  mutate(topic_model = map(
+    # mutate(topic_model = future_map(
     K,
     ~ stm(
       documents = hansard_stm$documents,
       vocab = hansard_stm$vocab,
       K = .,
-      prevalence =  ~ s(as.numeric(docid_field)),
+      # prevalence =  ~ s(as.numeric(docid_field)),
       data = hansard_stm$meta,
+      max.em.its = 75,
+      init.type = "Spectral",
       verbose = TRUE
-    ),
-    .progress = TRUE
+    )
+    # ),
+    # .progress = TRUE
   ))
 
+head(many_models)
 
-#### END
-
-heldout <- make.heldout(hansard_dfm)
+heldout <- make.heldout(documents = hansard_stm$documents, vocab = hansard_stm$vocab)
 
 k_result <- many_models %>%
   mutate(
     exclusivity = map(topic_model, exclusivity),
-    semantic_coherence = map(topic_model, semanticCoherence, hansard_dfm),
[…]

### 2018-10-06 outputs/docs/mentions/paper.Rmd
Update paper with better illustrative graph

@@
 
+## Additional information
+
+Data from other sources are needed to complement the parliamentary text data.
+For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
+Also non-Hansard information about the politicians informs our analysis.
+This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.
+
+The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
+However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.
+The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
+An example of the additional information is provided in Appendix \@ref(additionalinformation).
+
 ## Elections
@@
 # Summary and conclusions
+
+# Additional information {#additionalinformation}
+**TBD**
+
+\newpage

### 2018-10-06 scripts/to_make_graphs/make_graph_of_topics_example_paper.R

@@ -1,56 +1,31 @@
-# library(ggrepel)
+# Just a quick chart as an example for the paper
+
 library(lubridate)
 library(tidyverse)
 
-td_gamma <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv")
+td_gamma <- read_csv("outputs/topic_models_and_gammas/gammas_model_80.csv")
+dates <- read_csv("outputs/topic_models_and_gammas/dates.csv")
 
 head(td_gamma)
 
-td_gamma_test <- td_gamma %>% 
-  mutate(decade = case_when(
-    document < 1909-12-31 ~ "1900s",
-    document < 1919-12-31 ~ "1910s",
-    document < 1929-12-31 ~ "1920s",
-    document < 1939-12-31 ~ "1930s",
-    document < 1949-12-31 ~ "1940s",
-    document < 1959-12-31 ~ "1950s",
-    document < 1969-12-31 ~ "1960s",
-    document < 1979-12-31 ~ "1970s",
-    document < 1989-12-31 ~ "1980s",
-    document < 1999-12-31 ~ "1990s",
-    document < 2009-12-31 ~ "2000s",
-    TRUE ~ "2010s"
-  )) %>% 
-  group_by(decade, topic) %>% 
-  summarise(ave_gamma = mean(gamma))
+# td_gamma$document %>% unique() %>% length()
 
-td_gamma_test <- td_gamma %>% 
-  mutate(topic = case_when(
-    topic <= 10 ~ 1,
-    topic <= 20 ~ 2,
-    topic <= 30 ~ 3,
-    topic <= 40 ~ 4,
-    topic <= 50 ~ 5,
-    topic <= 60 ~ 6,
-    topic <= 70 ~ 7,
-    topic <= 80 ~ 8,
-    topic <= 90 ~ 9,
-    TRUE ~ 10
-  )) %>% 
-  group_by(document, topic) %>% 
-  summarise(ave_gamma = sum(gamma))
+td_gamma$date <- rep(dates$dates, 80)
 
-td_gamma_test[1:20,]
+set.seed(12345)
+td_gamma <- td_gamma %>% 
+  sample_frac(0.05) # reduce to 5 per cent of the dataset so that it doesn't take an age to load
 
-td_gamma_test_reduced <- td_gamma_test %>% 
-  filter(topic %in% c(3, 4, 10))
+td_gamma_reduced <- td_gamma %>% 
+  filter(topic %in% c(17))
 
[…]

### 2018-10-06 scripts/to_model_topics/topic_modelling_stm-elections_focus.R

@@ -104,7 +104,7 @@ head(tidy_hansard)
 tidy_hansard <- tidy_hansard %>%
   select(date, word)
 
-# The issue with using, the corpus construction function in the STM package is that it's really slow. But at the same time, the metadata is needed, so can't just use code from Julia Silge (maybe you can, but I don't know what to change). Anyway, this way works (cf STM alternative) and keeps metadata (cf Julia Silge code). If the dataset is smaller then use the STM function. If you don't need the metadata then use Julia Silge's code. Sure, this way is clumsy, but I need results for the paper draft and I can make this better later. Based on:
+# My issue with using the corpus construction function in the STM package is that it's really slow. But at the same time, the metadata is needed, so can't just use code from Julia Silge (maybe you can, but I don't know what to change). Anyway, this way works (cf STM alternative) and keeps metadata (cf Julia Silge code). If the dataset is smaller then use the STM function. If you don't need the metadata then use Julia Silge's code. Sure, this way is clumsy, but I need results for the paper draft and I can make this better later. Based on:
 # https://stackoverflow.com/questions/47652890/stm-how-to-keep-metadata-when-converting-from-tm-to-stm-document-term-matrix
 head(tidy_hansard)
 # Reduce the number of words that we have to deal with

### 2018-10-07 outputs/docs/events/paper.Rmd
Get heldout working for topics selection

@@
 The specific steps that we take are to remove numbers and punctuation and to change the words to lower case.
-Then the sentences are deconstructed and each word considered individually.
 **[Need to bundle_ngrams i.e.
-New Zealand is new_zealand.]**
-
-## Additional information
-**[Not sure this is being used - might be better in the other paper.]**
-Data from other sources are needed to complement the parliamentary text data.
-For instance, although the name, party, and division represented are contained in Hansard records they are inconsistent.
-Also non-Hansard information about the politicians informs our analysis.
-This includes: date of birth and date of death; sex; date of entry to parliament and exit from parliament; some aspects of their pre- and post-parliamentary career; some aspects of their parliamentary career, such as ministry appointments; and electoral information such as primary and two-party-preferred results.
-
-The main sources for this additional supplementary information are the handbooks supplied by the various parliaments.
-However these had many errors and were supplemented by data from the Australian Dictionary of Biography and Wikipedia.
-The source for the electoral results is the Australian Electoral Commission and Adam Carr's Australian Election Archive.
-An example of the additional information is provided in Appendix \@ref(additionalinformation).
+New Zealand is new_zealand.]** Then the sentences are deconstructed and each word considered individually.
 
@@
 The choice of the number of topics to use in the model is a situation-specific compromise.
-We use standard diagnostic techniques with cross validation to decide on 80 **[UPDATE]** topics.
+We use a standard diagnostic approach to decide on 80 **[UPDATE]** topics.
 More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
@@
 Figure \@ref(fig:exampletopics) illustrates an output of the STM.
-This illustrative model only considers data from the House of Representatives between 1901 and 2017.
-It shows how each day's parliamentary discussion can be allocated to one of ten topics and highlights how the prominence of these topics changes over time.
-**[RUN AND GRAPH AN ACTUAL 10-TOPIC MODEL - THESE DATA ARE JUST SUMMED FROM THE GENERAL ONE!.]**
+This illustrative example only shows five per cent of data from the House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be allocated to a topic and highlights how the prominence of these topics changes over time.
 
-```{r exampletopics, echo=FALSE, fig.cap="Estimated 10-topic-proportion", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/topics_example.png"))
+```{r exampletopics, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
 ```
@@
 But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
-Instead, we put together a Bayesian hierarchical Dirichlet model that takes those shares as an input.
+Instead, we use a Bayesian hierarchical Dirichlet model that takes those shares as an input.
 
@@
 Note that time $t$ refers to the day index within a sitting period which is any collection of days separated from other days by at least a week.
-Our analysis model is:
+Our model is:
 
@@
 
-Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
-The Dirichlet distribution is the multivariate extension of the Beta distribution, and the parameter controls where the 'weight' of the distribution lies.
-Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which means the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
+Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
+This is considered as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
+In a sense, $\mu_{stp}$ will be mean topic distributions over whatever time period is of interest.
+<!-- The Dirichlet distribution is the multivariate extension of the Beta distribution, and the parameter controls where the 'weight' of the distribution lies.  -->
+Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
 These are themselves parameters.
@@
 We run the model in Stan using the \texttt{RStan} package of @RStan. An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
+
+**[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]**
 
@@
 
-# Additional information {#additionalinformation}
-**TBD**
-
-\newpage
-
 # word2vec alternative {#word2vec}

### 2018-10-07 outputs/docs/events/paper.Rmd
Update paper and some of the meta data around events

@@
 We first create a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
-To reduce the dimensionality of this dataset we then use a topic model that allows correlation and a steady change over time.
-Finally, we consider the effect of various events using a Bayesian hierarchical Dirichlet model.
+To reduce the dimensionality of this dataset we use a topic model that allows for correlation and steady changes over time.
+We analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
 We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
@@
 governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
-keyEconomicDates <- read_csv(here::here("inputs/misc/key_dates-economic.csv"), col_types = cols())
-keyOtherDates <- read_csv(here::here("inputs/misc/key_dates-other.csv"), col_types = cols())
+keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
 significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
@@
 missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
+hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
 
@@
 In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events.
-From a data perspective we contribute **[?????]**.
-From a methods perspective, we contribute **[?????]**.
+From a data perspective we contribute **[TBD]**.
+From a methods perspective, we contribute **[TBD]**.
 Our model can be used in many settings where the results of topic models need to be further analysed.
@@
 **[Need to bundle_ngrams i.e.
-New Zealand is new_zealand.]** Then the sentences are deconstructed and each word considered individually.
+New Zealand is new_zealand and ad valorem is ad_valorem.]** Then the sentences are deconstructed and each word considered individually.
 
@@
 
-```{r exampletopics, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
 knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
@@
 
-The main output of the STM that is of interest to us is the share of each topic in each document.
-We would like to know how those shares change given events.
+The main output of the STM that is of interest to us is the proportion of each topic in each document.
+We would like to know how those proportions change given events.
 But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
-Instead, we use a Bayesian hierarchical Dirichlet model that takes those shares as an input.
+Instead, we use a Bayesian hierarchical Dirichlet model that takes those proportions as an input.
 
 We index each proportion, $\gamma$, by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$.
-Note that time $t$ refers to the day index within a sitting period which is any collection of days separated from other days by at least a week.
+For this purpose time, $t$, refers to the day index within a sitting period, and a sitting period is any collection of days separated from another collection of days by at least a week.
 Our model is:
@@
 We are interested in considering the effect of various events on what is talked about in Australia's parliaments. 
-Each of the parliaments and their houses are treated independently here.
-Future work could expand the model to better understand, and allow, for correlation between them.
-
+<!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
 Political events are those related to a change of government or an election.
-Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency.
-Other events are those such as the 9/11 attacks.
+Other events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
 The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
 
-We consider four types of events and group the day's topic proportions by these events.
-One unfortunate effect of this is that we only allow an event to have a long-run effect and ignore short-run effects.
-Another is that we ignore coincidence of events.
+First considering the mean topic distributions over governments, Figures \@ref(fig:mu1to20) - \@ref(fig:mu41to60).
+
+```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/mu_topic1-20.pdf"))
+```
+
+```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/mu_topic21-40.pdf"))
+```
+
+```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+knitr::include_graphics(here::here("outputs/figures/mu_topic41-60.pdf"))
+```
+
+Topics related to Federation such as the British Empire and the constitution decrease in importance over time. A substantial increase in the importance of issues dealing with
+
+Increasing from 20th gov: 2, 4, 8, 12,
+
+32 increases and then decreases
+
+Increases only recently: 33, 35
+
+Breakpoint: 23, 25, 49, 48, 46, 47, 41
 
@@
 
-```{r electionsevents, echo=FALSE, fig.cap="Topic proportions grouped by elections", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_election.png"))
-```
-
-Figure \@ref(fig:governmentevents) shows the grouping by government.
+Groupings by government.
 This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election.
@@
 Here we see much more difference between adjacent events. This suggests that new governments tend to talk about different topics than the government they replace.
-
-```{r governmentevents, echo=FALSE, fig.cap="Topic proportions grouped by government", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_government_change.png"))
-```
-
-Figure \@ref(fig:economicevents) shows the grouping by major economic changes. There are considerable changes between adjacent events.
-
-```{r economicevents, echo=FALSE, fig.cap="Topic proportions grouped by economic events", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_economic_changes.png"))
-```
-
-Figure \@ref(fig:otherevents) shows the grouping by major other events, such as the 9/11 attacks.
-
-```{r otherevents, echo=FALSE, fig.cap="Topic proportions grouped by other events", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_other_changes.png"))
-```
-
-Another way to consider the effect of events is by including incrementing variables in the prevelance metadata.
-This then gets included in the topic modelling and the significance to each topic can be computed.
-Table \@ref(tab:dodgysignificances) summarises these by the type of dummy and the topic.
-At the five per cent level the events that we consider were significant for eight topics.
-This significance tended to be correlated, especially for economic and other events.
-
-```{r dodgysignificances, echo = FALSE, results = 'asis'}
-
-significances %>% 
-  kable(booktabs = T, caption = "Significance of dummy") %>%
-  kable_styling(font_size = 12)
-
-```
 
@@
   kable(booktabs = T, caption = "Top words for each topic") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 8)
 
@@
 ## Hansard sources {#hansardsources}
-Where from?
+
+Hansard records are available from a variety of sources, as detailed in Table \ref{tab:hansardsourcestable}.
+
+```{r hansardsourcestable, cache = TRUE, echo = FALSE, results = 'asis'}
+
+hansard_sources %>%
+  kable(
+    booktabs = T,
+    align = c('l', 'r', 'r', 'r'),
+    caption = "Hansard sources and notes") %>%
+  kable_styling(font_size = 10)
+
+# Break cachee
+
+```
+
+Detail where from, and which years are being used and why.
 
 Which years are being used (not non-OCRd)
-
-[IS THIS BEING REFERENCED IN THE TEXT????]
 
@@
 
-```{r economics, echo = FALSE, results = 'asis'}
+```{r keyevents, echo = FALSE, results = 'asis'}
 
-keyEconomicDates %>% 
-  kable(booktabs = T, caption = "Key economic events") %>%
-  kable_styling(font_size = 10)
-
-```
-
-```{r others, echo = FALSE, results = 'asis'}
-
-keyOtherDates %>% 
-  kable(booktabs = T, caption = "Key other events") %>%
+keyEvents %>% 
+  kable(booktabs = T, caption = "Key events") %>%
   kable_styling(font_size = 10)

### 2018-10-07 ngrams.R

@@ -1,0 +1,15 @@
+# https://tutorials.quanteda.io/statistical-analysis/collocation/
+
+
+require(quanteda)
+install.packages("quanteda")
+library(quanteda)
+
+news_corp <- readRDS("/Users/rohanalexander/Downloads/data_corpus_guardian.rds")
+ndoc(news_corp)
+range(docvars(news_corp, 'date'))
+
+news_toks <- ?tokens(news_corp, remove_punct = TRUE)
+cap_col <- tokens_select(news_toks, '^[A-Z]', valuetype = 'regex', case_insensitive = FALSE, padding = TRUE) %>% 
+  textstat_collocations(min_count = 100)
+head(cap_col, 20)

### 2018-10-07 scripts/to_make_graphs/make_graphs_of_alpha_mu_sigma.R

@@ -1,0 +1,86 @@
+library(ggplot2)
+library(tidyverse)
+
+# Read data
+mu_res <- read_csv("scripts/from_monica/governments/mu_res.csv")
+sigma_res <- read_csv("scripts/from_monica/governments/sigma_res.csv")
+alpha_res <- read_csv("scripts/from_monica/governments/alpha_res.csv")
+
+
+# Make changes to data
+
+
+# Make graphs
+head(mu_res)
+mu_res$government %>% unique()
+mu_res %>%
+  filter(topic %in% 1:20) %>%
+  ggplot(aes(government, median, color = factor(government))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_wrap(vars(topic)) +
+  theme(legend.position="none")
+
+ggsave(
+  "outputs/figures/mu_topic1-20.pdf",
+  height = 6,
+  width = 8,
+  units = "in"
+)
+
+mu_res %>%
+  filter(topic %in% 21:40) %>%
+  ggplot(aes(government, median, color = factor(government))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_wrap(vars(topic)) +
+  theme(legend.position="none")
+
+ggsave(
+  "outputs/figures/mu_topic21-40.pdf",
+  height = 6,
+  width = 8,
+  units = "in"
+)
+
+mu_res %>%
+  filter(topic %in% 41:60) %>%
+  ggplot(aes(government, median, color = factor(government))) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_wrap(vars(topic)) +
+  theme(legend.position="none")
+
+ggsave(
+  "outputs/figures/mu_topic41-60.pdf",
+  height = 6,
+  width = 8,
+  units = "in"
+)
+
+
+
+
+head(sigma_res)
+sigma_res %>% 
+  filter(median<0.3) %>% 
+  ggplot(aes(government, median)) + 
+  geom_point() + 
+  geom_errorbar(aes(ymin = lower, ymax = upper))
+
+head(alpha_res)
+alpha_res %>% 
+  filter(median<0.3) %>% 
+  ggplot(aes(government, median)) + 
+  geom_point() + 
+  geom_errorbar(aes(ymin = lower, ymax = upper))
+
+
+
+
+ggsave(
[…]

### 2018-10-07 scripts/to_model_topics/the_ficl.R

@@ -1,58 +1,0 @@
-install.packages("vars")
-library(vars)
-
-gammas <- read_csv("/Users/rohanalexander/Desktop/test_gammas.csv")
-
-data("Canada")
-head(Canada)
-
-gammas_test <- spread(gammas, topic, gamma)
-
-head(gammas_test)
-tail(gammas_test)
-
-head(Canada)
-
-?VAR(gammas_test, p = 2, type = "none")
-
-
-
-#### 
-install.packages("betareg")
-library(betareg)
-
-test <- betareg()
-
-
-
-
-####
-
-install.packages("nnet")
-library(nnet)
-glm.fit = ?multinom(direccion~., data=datos)
-summary(glm.fit)
-#Prediction
-predict(glm.fit, newdata, "probs")
-
-
-
-
-
-
-####
-install.packages("mlogit")
-library(mlogit)
-gammas <- read_csv("/Users/rohanalexander/Desktop/test_gammas.csv")
-head(gammas)
-gamma_data <- mlogit.data(gammas, 
-                          choice = gamma,
-                          shape = long,
-                          varying = 
-                          id.var = 
-                            
-                            varying = c(2:9), 
-                          shape = "wide", choice =
-              "mode")
-
-f <- mFormula(choice ~ vcost | income + size | travel)

### 2018-10-08 ngrams.R
Update scripts folder and add multiword corrections list

@@ -1,15 +1,0 @@
-# https://tutorials.quanteda.io/statistical-analysis/collocation/
-
-
-require(quanteda)
-install.packages("quanteda")
-library(quanteda)
-
-news_corp <- readRDS("/Users/rohanalexander/Downloads/data_corpus_guardian.rds")
-ndoc(news_corp)
-range(docvars(news_corp, 'date'))
-
-news_toks <- ?tokens(news_corp, remove_punct = TRUE)
-cap_col <- tokens_select(news_toks, '^[A-Z]', valuetype = 'regex', case_insensitive = FALSE, padding = TRUE) %>% 
-  textstat_collocations(min_count = 100)
-head(cap_col, 20)

### 2018-10-08 scripts/run_2_parse_pdfs/parse_each_pdf_and_save_csv_pdftools.R

@@ -3,7 +3,7 @@
 # Purpose: This file takes Australian Hansard PDF files and it converts them to CSVs of text data that can be analysed.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 13 September 2018
+# Last updated: 8 October 2018
 # Prerequisites: You need to have downloaded the PDFs from the parliament's website. There are many GBs of PDFs and they are saved on an external drive - have fun finding that future-Rohan - and also the Berkeley Demography server. For testing purposes there should be some in the /inputs/for_testing_hansard_pdf folder.
 # To do:
 # - Check which footers need to be replaced

### 2018-10-08 scripts/to_analyse_topics/Untitled.R

@@ -1,4 +1,0 @@
-library(tidyverse)
-
-test <- read_lines("inputs/voting_data/1980repsqld.txt") %>% as_tibble()
-

### 2018-10-08 scripts/to_analyse_topics/gelman.R

@@ -1,92 +1,0 @@
-library("rstan")
-library("rstanarm")
-library("arm")
-# options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
-
-## 2.  Simulate a data structure with N_per_person measurements on each of J people
-
-J <- 50  # number of people in the experiment
-N_per_person <- 10 # number of measurements per person
-person_id <- rep(1:J, rep(N_per_person, J))
-index <- rep(1:N_per_person, J) 
-time <- index - 1  # time of measurements, from 0 to 9
-N <- length(person_id)
-a <- rnorm(J, 0, 1)
-b <- rnorm(J, 1, 1)
-theta <- 1
-sigma_y <- 1
-
-## 3.  Simulate data from a between-person experiment
-
-z <- sample(rep(c(0,1), J/2), J)
-y_pred <- a[person_id] + b[person_id]*time + theta*z[person_id]*time
-y <- rnorm(N, y_pred, sigma_y)
-z_full <- z[person_id]
-exposure <- z_full*time
-data_1 <- data.frame(time, person_id, exposure, y)
-
-## 4.  Simulate data from a within-person experiment:  for each person, do one treatment for the first half of the experiment and the other treatment for the second half.
-
-z_first_half <- z
-T_switch <- floor(0.5*max(time))
-z_full <- ifelse(time <= T_switch, z_first_half[person_id], 1 - z_first_half[person_id])
-for (j in 1:J){
-  exposure[person_id==j] <- cumsum(z_full[person_id==j])
-}
-y_pred <- a[person_id] + b[person_id]*time + theta*exposure
-y <- rnorm(N, y_pred, sigma_y)
-data_2 <- data.frame(time, person_id, exposure, y)
-
-## 5.  Graph the simulated data
-
-pdf("within_design.pdf", height=7, width=10)
-par(mfrow=c(2, 2))
-par(mar=c(3,3,3,1), mgp=c(1.5, .5, 0), tck=-.01)
-
-plot(range(time), range(data_1$y, data_2$y), xlab="time", ylab="y", type="n", bty="l", main="Between-person design:\nControl group")
-for (j in 1:J){
-  ok <- data_1$person_id==j
-  if (z[j] == 0){
-    points(time[ok], data_1$y[ok], pch=20, cex=.5)
[…]

### 2018-10-08 scripts/to_analyse_topics/test.R

@@ -1,94 +1,0 @@
-# install.packages("rstan")
-# install.packages("rstanarm")
-# install.packages("arm")
-
-library("rstan")
-library("rstanarm")
-library("arm")
-library(tidyverse)
-library(lubridate)
-# options(mc.cores = parallel::detectCores())
-rstan_options(auto_write = TRUE)
-
-
-
-
-# Load the election dates
-election_dates <- read_csv("inputs/misc/misc_elections_data.csv")
-# Load topics
-topics <- read_csv("outputs/big_files_do_not_push/gammas_model_prevalence_is_spline.csv")
-head(election_dates)
-head(topics)
-
-
-all_dates <-
-  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
-  mutate(electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
-         electionDate = cumsum(electionDate)) %>% 
-  rename(electionCounter = electionDate)
-
-head(all_dates)
-
-topics <- topics %>% 
-  left_join(all_dates, by = c("document" = "allDates"))
-
-head(topics)
-
-topics_dates <- tibble(date = topics$document %>% unique())
-topics_dates <- topics_dates %>% 
-  arrange(date) %>% 
-  mutate(counter = 1:nrow(topics_dates))
-
-topics <- topics %>% 
-  left_join(topics_dates, by = c("document" = "date"))
-
-head(topics)
-
-topics_test <- topics %>% 
-  # filter(electionCounter %in% c(1, 2)) %>%
-  mutate(gamma = gamma * 1000000000,
-         gamma = as.integer(gamma)) %>% 
-  # filter(!topic %in% c(1, 2)) %>%
-  mutate(electionCounter = as.integer(electionCounter))
-
-head(topics_test)
-?scale
-
-
-# fit_1 <- stan_glmer(gamma ~ (1 + counter | topic) + counter + electionCounter, data=topics_test)
-# Allow varying slope and intercept for topics and, allow slope of counter to vary by topic
-
-fit_1 <-
-  lmer(
-    gamma ~ (1 | topic) + counter + electionCounter,
-    data = topics_test
-  )
-# Each topic gets a different intercept
-
-summary(fit_1)
-plot(fit_1)
-display(fit_1)
-ranef(fit_1)
-?fit
-
-
-# install.packages("merTools")
-# library(merTools)
[…]

### 2018-10-09 outputs/docs/events/paper.Rmd
Update scripts folder and add multiword corrections list
Update the front matter splitter

@@
 Text is usually pre-processed before topic models are used.
-The specific steps that we take are to remove numbers and punctuation and to change the words to lower case.
-**[Need to bundle_ngrams i.e.
-New Zealand is new_zealand and ad valorem is ad_valorem.]** Then the sentences are deconstructed and each word considered individually.
+The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multiword names titles and phrases, such as new zealand to new_zealand.
+Then the sentences are deconstructed and each word considered individually.
 
@@
 These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+
 The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+
 The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
+
 In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
+
+And @Benoit2018 for compounding multiword expressions.
 

### 2018-10-09 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_save_csv_pdftools.R

@@ -1,0 +1,297 @@
+# !diagnostics off
+#### Preamble ####
+# Purpose: This file takes Australian Hansard PDF files and it converts them to CSVs of text data that can be analysed.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 8 October 2018
+# Prerequisites: You need to have downloaded the PDFs from the parliament's website. There are many GBs of PDFs and they are saved on an external drive - have fun finding that future-Rohan - and also the Berkeley Demography server. For testing purposes there should be some in the /inputs/for_testing_hansard_pdf folder.
+# To do:
+# - Check which footers need to be replaced
+# - Better identify which page talking starts at
+# - Deal with two columns better - e.g. line 162
+# - Better identify speakers and look within cells
+
+
+#### Set up workspace ####
+library(furrr)
+# devtools::install_github("DavisVaughan/furrr")
+library(lubridate)
+library(pdftools)
+library(stringi)
+library(tidyverse)
+library(tictoc)
+library(tm)
+# update.packages()
+# Set up furrr
+plan(multiprocess)
+
+
+#### Create lists of PDFs to read and file names to save text as ####
+# Change the path as required:
+use_this_path_to_get_pdfs  <- "/Volumes/Backup/hansard_pdfs"
+# use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
+
+use_this_path_to_save_csv_files  <- "outputs/hansard/temp"
+use_this_path_to_save_csv_files  <- "/Volumes/Backup/temp"
+# use_this_path_to_save_csv_files  <- "/Volumes/Backup/hansard_csv"
+
+# Get list of Hansard PDF filenames
+file_names <-
+  list.files(
+    path = use_this_path_to_get_pdfs,
+    pattern = "*.pdf",
+    recursive = TRUE,
+    full.names = TRUE
+  )
+file_names <- file_names %>% sample() # Randomise the order
+# file_names <- file_names %>% sample(500) # Get 500
+
+# Use this to get and remove the ones already done
+# file_names_already_done <-
+#   list.files(
+#     path = use_this_path_to_save_csv_files,
+#     pattern = "*.csv",
+#     recursive = TRUE,
+#     full.names = FALSE
+#   ) %>%
[…]

### 2018-10-09 scripts/run_2_parse_pdfs/run_3_split_based_on_topic_names_and_speakers.R
Update teh column splitter

@@ -1,0 +1,2 @@
+
+## The next task is to split out the topic names and the names of the speakers

### 2018-10-09 scripts/testing.R

@@ -1,267 +1,0 @@
-library(furrr)
-library(lubridate)
-library(pdftools)
-library(stringi)
-library(tidyverse)
-library(tictoc)
-library(tm)
-# update.packages()
-
-
-name_of_input_PDF_file <- "inputs/for_testing_hansard_pdf/1971-10-05.pdf" # uncomment for testing
-pdf_document <- pdf_text(name_of_input_PDF_file)
-
-# Get the date based on the filename
-date_of_doc <- basename(name_of_input_PDF_file) %>% # basename gets rid of the path to the file
-  str_replace(".pdf", "") %>% 
-  ymd()
-
-# Convert to tibble so that tidyverse can be used
-pdf_document_tibble <- tibble(text = pdf_document)
-rm(pdf_document)
-
-# Each row is now a page of the PDF so adding a column of the row numbers allows you to keep track of the page numbers later on
-pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
-
-# Separate each line (of each page) into it's own row
-pdf_document_tibble <-
-  separate_rows(pdf_document_tibble, text, sep = "\\n")
-
-# Fix some minor punctuation issues to make the analysis easier
-# str_count(pdf_document_tibble$text, "(?<=[:lower:])I(?=[:space:])") %>% sum() # Use this if you suspect an issue and it'll give you a count of how many rows are affected
-# which(str_detect(pdf_document_tibble$text, "(?<=[:lower:])I(?=[:space:])")==TRUE) # Use this to tell you what line it's on
-pdf_document_tibble$text <-
-  str_replace_all(pdf_document_tibble$text, "’", "'") 
-pdf_document_tibble$text <-
-  str_replace_all(pdf_document_tibble$text, "•", "-") # Some hyphens are being read in as big dots
-pdf_document_tibble$text <-
-  str_replace_all(pdf_document_tibble$text, "\\b- \\b", "") # Hyphens are being retained improperly e.g. Roh- an and that would affect the words analysis so needs to be fixed
-
-pdf_document_tibble$text <-
-  str_replace_all(pdf_document_tibble$text, "—", "-") # I'm as pedantic as the next person about dash, hyphen, em dash usage, but this is not the place.
-pdf_document_tibble$text <-
[…]

### 2018-10-12 outputs/docs/events/paper.Rmd
Update teh column splitter
stuff about analysis model

@@
 
-The main output of the STM that is of interest to us is the proportion of each topic in each document.
-We would like to know how those proportions change given events.
+The main output of the STM that is of interest to us is the proportion of each topic appearing in each document.
+Specifically, we are interested in how the distribution of topics changes in relation to different types of events.
 But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
-Instead, we use a Bayesian hierarchical Dirichlet model that takes those proportions as an input.
+Instead, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
+Specifically, we use a Bayesian hierarchical Dirichlet regression framework which relates proportions of each topic to underlying time trends, changes in goverments and elections.
 
-We index each proportion, $\gamma$, by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$.
-For this purpose time, $t$, refers to the day index within a sitting period, and a sitting period is any collection of days separated from another collection of days by at least a week.
-Our model is:
+Define $\gamma_{tp}$ to be the proportion of topic of topic $p$ on day $t$.
+We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Thus, the topic proportions on day $t$ are modeled in reference to their membership in a particular sitting period $s$.
+Firstly, we assume that each set of $\gamma_{t,}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[t],}$:
+
+$$
+\gamma_{t,} &\sim \mbox{Dirichlet}(\mu_{s[t],})
+$$
+This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
+
+The goal of the model is to relate these proportions to the government $g$ of time $t$, and also the days since the most recent election, $e$, while account for underlying time trends.
+Thus, the mean parameters $\mu_{sp}$ are modeled on the log scale as
+
+$$
+\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
+$$
+where:
+
+- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$
+- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election
+- $x_{s,k}$ is the $k$th basis spline in sitting period s
+- $\beta_{p,k}$ is a cofficient on the $k$th basis spline. 
+- $\delta_{s,p}$ is a structured random effect for each sittiing period and topic.
+
+The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
+$$
+\alpha_{g[s],p} \sim N(0, 100)
+$$
+
+The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
+In particular, we model this as an AR(1) in $d$:
+
+$$
+\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
+$$
+The value of the initial effect $\alpha_{e[s],0,p}$ and the AR(1) term $\rho$ both have non-informative priors:
+
+$$
+\alpha_{e[s],0,p} \sim N(0, 100)\\
+\rho_{e[s],p} \sim U(0,1)
+$$
+
+We model the underlying time trend in topics using splines regression.
+The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
+The $x_{s,k}$ for $k = 1,2,\dots K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
+We chose to place knot points every 5 sitting periods as this is the average length of time for a government to sit (**CHECK**).
+Non-informative priors are placed on the splines coefficients:
+$$
+\beta_{p,k} \sim N(0, 100)
+$$
+
+Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on the government/election effects.
+This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+The $\delta_{s,p}$'s are modeled as
+
+$$
+\delta_{s,p} \sim N(0, \sigma_{e[s],p}^2)
+$$
+
+The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
+If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
+Non-informative priors are placed on the variance parameters:
+
+$$
+\sigma_{e[s],p} \sim U(0,3)
+$$
+
+RA STUFF:
+
+The full model is:
 
@@
 
+For background on the Premiers' Plan see @Copland1934.
+
+For background on the Gruen tariff cut see @Gruen1975.
+
 Add the graphs and procedures.

### 2018-10-13 outputs/docs/events/paper.Rmd
Fix compilation issues

@@
 significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
-top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
 missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
@@
 $$
-\gamma_{t,} &\sim \mbox{Dirichlet}(\mu_{s[t],})
+\gamma_{t,} \sim \mbox{Dirichlet}(\mu_{s[t],})
 $$

### 2018-10-13 outputs/docs/events/paper.Rmd
removed the heres so monica could compile

@@
 ```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
+knitr::include_graphics("../../figures/topics_example.pdf")
 ```
@@
 ```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/mu_topic1-20.pdf"))
+knitr::include_graphics("../../figures/mu_topic1-20.pdf")
 ```
@@
 ```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/mu_topic21-40.pdf"))
+knitr::include_graphics("../../figures/mu_topic21-40.pdf")
 ```
@@
 ```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/mu_topic41-60.pdf"))
+knitr::include_graphics("../../figures/mu_topic41-60.pdf")
 ```
@@
 ```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
-knitr::include_graphics(here::here("outputs/figures/example_hansard_page.png"))
+knitr::include_graphics("../../figures/example_hansard_page.png")
 ```

### 2018-10-13 outputs/docs/events/paper.Rmd
added analysis model stuff

@@
 Specifically, we are interested in how the distribution of topics changes in relation to different types of events.
-But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
-Instead, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
+But with around 40 topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
+
+The STM framework allows for covariates to be included in the estimation of the topic distributions, $\theta_d$ (see equation **[XX]** above).
+This allows the certain types of relationships between topics and events to be assessed.
+However, there are several limitations to the STM covariate framework in this context:
+
+- There is no way of specifying more complicated autocorrelated functional forms of the effects of events over time.
+For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
+In the STM framework, it is possible to specify constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
+- There is no way of implementing partial pooling across groups of similar documents.
+The STM framework assumes that  documents are independently and identically distributed conditional on the covariates in the model.
+However, it could be expected that topic distributions within a particular government period, for example, may be more or less likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
+To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
+- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+For example, if we think that the 9/11 terrorist attacks had an effect on parliamentary discourse, a dummy for 9/11 would have to be included in the STM framework.
+Ideally, we would like to identify important events based on different-to-expected topic distributions, after account for time trends, government and election effects.
+
+To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
 Specifically, we use a Bayesian hierarchical Dirichlet regression framework which relates proportions of each topic to underlying time trends, changes in goverments and elections.
 
-Define $\gamma_{tp}$ to be the proportion of topic of topic $p$ on day $t$.
+Define $\gamma_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
+Note that $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ is equal to the estimated values of $\theta_d$ from the STM.
 We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Thus, the topic proportions on day $t$ are modeled in reference to their membership in a particular sitting period $s$.
-Firstly, we assume that each set of $\gamma_{t,}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[t],}$:
+Using this definition, there are a total of 745 sitting periods across all years of interest (1901--2017).
+
+The topic proportions on day $d$ are modeled in reference to their membership in a particular sitting period $s$.
+Firstly, we assume that each distribution of topics, $\gamma_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
 
 $$
-\gamma_{t,} \sim \mbox{Dirichlet}(\mu_{s[t],})
+\gamma_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
 $$
+where the notation $s[d]$ refers to the sitting period $s$ which day $d$ belongs to.
 This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
 
-The goal of the model is to relate these proportions to the government $g$ of time $t$, and also the days since the most recent election, $e$, while account for underlying time trends.
-Thus, the mean parameters $\mu_{sp}$ are modeled on the log scale as
+The goal of the model is to relate these proportions to the government $g$ of time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The mean parameters $\mu_{sp}$ are modeled on the log scale as
 
@@
 - $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election
-- $x_{s,k}$ is the $k$th basis spline in sitting period s
-- $\beta_{p,k}$ is a cofficient on the $k$th basis spline. 
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modeled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$, and $\beta_{p,k}$ is a cofficient on the $k$th basis spline.
 - $\delta_{s,p}$ is a structured random effect for each sittiing period and topic.
@@
 This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+In addition, this set up also partially pools effects across sitting periods.
 The $\delta_{s,p}$'s are modeled as
@@
 
-RA STUFF:
+We run the model in Stan using the \texttt{RStan} package of @RStan. An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
 
-The full model is:
+<!-- RA STUFF: -->
 
-\begin{align}
-\gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ 
-\log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\
-\alpha_{s1} &= 0 (\#eq:zeroconstraint)\\
-\alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\
-\delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\
-\sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance)  
-\end{align}
+<!-- The full model is: -->
 
-**[Does the variance parameter used in Equation 4 need to be specified too?]**
+<!-- \begin{align} -->
+<!-- \gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ -->
+<!-- \log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\ -->
+<!-- \alpha_{s1} &= 0 (\#eq:zeroconstraint)\\ -->
+<!-- \alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\ -->
+<!-- \delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\ -->
+<!-- \sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance) -->
+<!-- \end{align} -->
 
-Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
+<!-- **[Does the variance parameter used in Equation 4 need to be specified too?]** -->
+
+<!-- Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
 This is considered as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
 In a sense, $\mu_{stp}$ will be mean topic distributions over whatever time period is of interest.
-<!-- The Dirichlet distribution is the multivariate extension of the Beta distribution, and the parameter controls where the 'weight' of the distribution lies.  -->
-Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
+-->
+
+<!-- Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
 These are themselves parameters.
 The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
+-->
 
-Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
+<!-- Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
 Equation \@ref(eq:alphasp) shows how we consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **[SOMETHING]** and a variance that depends on **[SOMETHING ELSE]**.
 Similarly, Equation \@ref(eq:deltasp) show how we model $\delta_{stp}$  as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution in Equation \@ref(eq:randomwalkvariance), that is, a random walk around each intercept.
+-->
 
-We run the model in Stan using the \texttt{RStan} package of @RStan. An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
-
-**[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]**
+<!-- **[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]** -->
 

### 2018-10-13 outputs/docs/events/paper.Rmd
more paper changes

@@
 
-The STM is set-up to most easily include metadata to do with prevalence and content.
+The STM is set-up to include metadata to do with prevalence and content.
 Prevalence relates to the topic proportions in each document.
@@
 Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
+The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate.
+For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
 Content relates to the words that make up each topic.
 For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
-The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each aspect.
-For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
-Similarly, the content meta-data are
+STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
 
@@
 
-The STM framework allows for covariates to be included in the estimation of the topic distributions, $\theta_d$ (see equation **[XX]** above).
-This allows the certain types of relationships between topics and events to be assessed.
+As mentioned above, the STM framework allows for covariates to be included in the estimation of prevalence of topcs, $\theta_d$ (see equation **[XX]** above).
+This theoretically would allow certain types of relationships between topics and events to be assessed.
 However, there are several limitations to the STM covariate framework in this context:
@@
 To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use a Bayesian hierarchical Dirichlet regression framework which relates proportions of each topic to underlying time trends, changes in goverments and elections.
+Specifically, we use the estimated topic distributions from STM as an input into a Bayesian hierarchical Dirichlet regression framework, which relates proportions of each topic to underlying time trends, changes in goverments and elections.
+This set-up also allows us to identify 'outlying' topic distributions and relate these to other, non-scheduled political events.
 
 Define $\gamma_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
-Note that $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ is equal to the estimated values of $\theta_d$ from the STM.
+Note that the $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the STM.
 We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.

### 2018-10-13 scripts/run_4_model_topics/run_2_topic_modelling_stm-elections_focus.R
Update paper

@@ -150,7 +150,6 @@ head(tidy_hansard_reduced)
 rm(tidy_hansard)
 
 
-
 # Add metadata
 all_dates <-
   tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
@@ -160,15 +159,17 @@ all_dates <-
     governmentChangeDate = if_else(allDates %in% governmentChanges$end, 1, 0),
     governmentChangeDate = cumsum(governmentChangeDate),
     keyEvent = if_else(allDates %in% keyEvents$theDate, 1, 0),
-    keyEvent = cumsum(keyEvent)
-  ) %>%
-  rename(electionCounter = electionDate, governmentCounter = governmentChangeDate) %>% 
-  mutate(electionCounterCharacter = as.character(electionCounter),
-         governmentCounterCharacter = as.character(governmentCounter))
+    keyEvent = cumsum(keyEvent),
+    electionOrGovernmentDate = if_else(allDates %in% c(election_dates$electionDate, governmentChanges$end), 1, 0),
+    electionOrGovernmentDate = cumsum(electionOrGovernmentDate)) %>%
+  rename(
+    electionCounter = electionDate,
+    governmentCounter = governmentChangeDate,
+    electionOrGovernmentCounter = electionOrGovernmentDate
+  )
   
-
 head(all_dates)
-#
+
 # all_dates <- all_dates %>%
 #   select(-keyEconomicChange, -keyOtherChange) %>%
 #   mutate(governmentChangeDate = governmentChangeDate + 1) %>%
@@ -179,17 +180,27 @@ head(all_dates)
 tidy_hansard_reduced <- tidy_hansard_reduced %>%
   left_join(all_dates, by = c("docid_field" = "allDates"))
 
+head(tidy_hansard_reduced)
+tail(tidy_hansard_reduced)
+
 tidy_hansard_reduced <- tidy_hansard_reduced %>%
   mutate(
     electionCounter = as.integer(electionCounter),
     governmentCounter = as.integer(governmentCounter),
+    electionOrGovernmentCounter = as.integer(electionOrGovernmentCounter),
     keyEvent = as.integer(keyEvent),
     year = year(docid_field),
     year = as.integer(year)
   )
 head(tidy_hansard_reduced)
+tail(tidy_hansard_reduced)
+
+
+
+
 
 ##### FOR TESTING ######
[…]

### 2018-10-14 outputs/docs/events/paper.Rmd
changes to methods section

@@
 # Model
-The models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and Bayesian hierarchical Dirichlet analysis model.
+
+The goal of our modeling strategy is twofold.
+Firstly, we want to topic modeling __(REF)__ to summarise all text contained in Hansard into meaningful topics, which reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
+Secondly, we want to relate the resulting topic distributions to temporal trends, changes and events, such as governement changes, elections, and other external events.
+
+We use a Correlated Topic Model (CTM) __(REF)__ to obtain estimated topic distributions over time.
+We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
+We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
+__In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.__
+
+In the following sections, we describe both the topic modeling approach and the Bayesian hierarchical analysis model.
+Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving on the CTM, which is a natural extension of LDA.
+We then discuss the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
+
+<!-- The models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and Bayesian hierarchical Dirichlet analysis model.
 In a similar way to @MuellerRauh2018, we use topics as an input to another model, in our case to analyse the effect of various events.
-In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
+-->
 
-The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
+<!-- The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
 In this section we provide a brief overview of both the LDA model and the STM.
@@
 We then discuss the Bayesian hierarchical Dirichlet analysis model that we use for this purpose.
+-->
 
 ## Latent Dirichlet Allocation
-Although more- or less-fine levels of analysis are possible, but here we are primarily interested in considering a day's topics.
+Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics.
 This means that each day's Hansard record needs to be classified by its topics.
@@
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent, for instance as implemented by the R \texttt{topicmodels} package of @Grun2011.
+One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent.[^topicmodelsfootnote]
+
+[^topicmodelsfootnote]: For instance as implemented by the R \texttt{topicmodels} package of @Grun2011.
 
@@
 The distribution over the terms for the $k$th topic is $\beta_k$.
-Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $0<\eta<1$ is used: $\beta_k \sim \mbox{Dirichlet}(\eta)$.[^Dirichletfootnote] Strictly, $\eta$ is actually a vector of hyperparameters, one for each $K$, but in practice they all tend to be the same value.
+Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $\boldsymbol{\eta}$ is used: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.[^Dirichletfootnote] In practice, a symmetric Dirichlet distribution is usually used, where all elements of $\boldsymbol{\eta}$ are equal.
 2.
@@
 The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
-Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\alpha)$.
+Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
 Again, strictly $\alpha$ is vector of length $K$ of hyperparameters, but in practice each is usually the same value.
@@
 If there are just two categories, then the Dirichlet and the beta distributions are the same.
-In the special case of a symmetric Dirichlet distribution, $\eta=1$, it is equivalent to a uniform distribution.
+In the special case of a symmetric Dirichlet distribution, where all elements of $\eta=1$, it is equivalent to a uniform distribution.
 If $\eta<1$, then the distribution is sparse and concentrated on a smaller number of the values, and this number decreases as $\eta$ decreases.
@@
 
-One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter (@blei2012).
+One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
 It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
@@
 For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-This motivates the use of the Structural Topic Model, described in the next section.
+This motivates the use of the Correlated Topic Model, described in the next section.
 
-## Structural Topic Model
+## Correlated Topic Model
 The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.

### 2018-10-14 outputs/docs/events/paper.Rmd
added bit about CTM

@@
 Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-For instance, in Hansard topics related the army may be expected to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
 This motivates the use of the Correlated Topic Model, described in the next section.
@@
 ## Correlated Topic Model
-The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
+As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
+Indeed, the corrleation between topics is not modeled or accounted for.
+However, in relaity, we would expect Hansard topics related the army may be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+The goal of the CTM __(REF)__ is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
+
+As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is slightly modified.
+Rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
+
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
+This is the main addition of CTM over LDA, in that it replaces the assumption of the Dirichlet distribution with a more flexible logistic Normal distribution, which incorporates a covariance structure across the topics.
+The remainder of the steps of the document generating process are identical to LDA.
+
+However, the replacement of the Dirichlet distribution, which is conjugate to the multinomial, with the logistic Normal distribution adds a level of computational complexity to CTM.
+The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
+__(REF)__ develop a fast variational inference procedure for estimating the CTM.
+This estimation approach has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
+
+<!-- The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
 For instance, we generally have some information about the author and the date that a document was created.
@@
 That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+-->
 
-The STM is set-up to include metadata to do with prevalence and content.
+<!-- The STM is set-up to include metadata to do with prevalence and content.
 Prevalence relates to the topic proportions in each document.
@@
 STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
+-->
 
-As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM:
+<!-- As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM: -->
 
-1.
+<!-- 1.
 As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
-In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3):
-$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3): -->
+<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$ -->
 
-2.
+<!-- 2.
 To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
-Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$:
-$$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$
+Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$: -->
+<!-- $$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$ -->
 
-3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$:
-    a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics.
-    b. Randomly choose a term from the topic-specific multinomial distribution over terms.
+<!-- 3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$: -->
+<!--     a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics. -->
+<!--     b. Randomly choose a term from the topic-specific multinomial distribution over terms. -->
 
-We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+<!-- We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
 We consider both topic prevalence and content to be functions of time.
@@
 More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
+-->
 
-Figure \@ref(fig:exampletopics) illustrates an output of the STM.
-This illustrative example only shows five per cent of data from the House of Representatives between 1901 and 2017.
+Figure \@ref(fig:exampletopics) illustrates an output of the CTM This illustrative example only shows five per cent of data from the House of Representatives between 1901 and 2017.
 It shows how each day's parliamentary discussion can be allocated to a topic and highlights how the prominence of these topics changes over time.

### 2018-10-14 outputs/docs/events/paper.Rmd
changes to bayesian section

@@
 
-The main output of the STM that is of interest to us is the proportion of each topic appearing in each document.
-Specifically, we are interested in how the distribution of topics changes in relation to different types of events.
-But with around 40 topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
+The main output of the CTM of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
+For the next stage of the modeling process, we are interested in how the distribution of topics changes in relation to different types of events.
+But with around 40 topics **[UPDATE]** for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
 
-As mentioned above, the STM framework allows for covariates to be included in the estimation of prevalence of topcs, $\theta_d$ (see equation **[XX]** above).
-This theoretically would allow certain types of relationships between topics and events to be assessed.
-However, there are several limitations to the STM covariate framework in this context:
+One option for relating the topic distributions to events would be to use a Structural Topic Model (STM) [@RobertsStewartAiroldi2016].
+The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
+For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the government or election period, may affect the topics within that document.
+The STM allows this additional information, or meta-data, to affect the construction of topics, though influencing either topical prevalence or topical content.
+The assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+
+Consider a matrix of covariates $X_d$, where each column relates to a different covariate or aspect of the meta-data, and the row refers to document $d$ value of each covariate.
+Similar to the CTM, the STM assumes the topics within a document $\theta_d$ are a draw from a logistic Normal distribution with mean $\mu$.
+However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$:
+
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+
+The STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
+For example, one covariate within the model could be the government $g$ that was in power during the time corresponding to document $d$.
+However, there are several limitations to the STM covariate framework in relation to our goal of assess the relationship between topics and events:
 
@@
 For example, if we think that the 9/11 terrorist attacks had an effect on parliamentary discourse, a dummy for 9/11 would have to be included in the STM framework.
-Ideally, we would like to identify important events based on different-to-expected topic distributions, after account for time trends, government and election effects.
+Ideally, we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
 
 To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from STM as an input into a Bayesian hierarchical Dirichlet regression framework, which relates proportions of each topic to underlying time trends, changes in goverments and elections.
+Specifically, we use the estimated topic distributions from CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates proportions of each topic to underlying time trends, changes in goverments and elections.
 This set-up also allows us to identify 'outlying' topic distributions and relate these to other, non-scheduled political events.
 
-Define $\gamma_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
-Note that the $\gamma_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the STM.
+Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
+Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM.
 We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
@@
 The topic proportions on day $d$ are modeled in reference to their membership in a particular sitting period $s$.
-Firstly, we assume that each distribution of topics, $\gamma_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
+Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
 
 $$
-\gamma_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
+\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
 $$
@@
 $$
-\alpha_{e[s],0,p} \sim N(0, 100)\\
+\alpha_{e[s],0,p} \sim N(0, 100)
+$$
+$$
 \rho_{e[s],p} \sim U(0,1)
 $$
-
 We model the underlying time trend in topics using splines regression.
@@
 
-We run the model in Stan using the \texttt{RStan} package of @RStan. An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
+We run the model in Stan using the \texttt{RStan} package of @RStan. __An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation). __
 

### 2018-10-14 outputs/docs/events/paper.Rmd
UPdate paper

@@
     template: svm-latex-ms.tex
-title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
+title: "The Effect of Events on Australian Federal Parliamentary Discussion (1901--2017)"
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
@@
 abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
-We first create a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records.
-To reduce the dimensionality of this dataset we use a topic model that allows for correlation and steady changes over time.
+We first create a dataset of what was said in the Australian Federal parliament from 1901 through to 2017 based on available public records.
+To reduce the dimensionality of this dataset we use a correlated topic model.
 We analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
-Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on short-term events."
+We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 1) elections that do not result in a change in government are rarely associated with topic changes; 2)  3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycle becomes increasingly focused on short-term events."
 keywords: "text analysis, politics, Australia"
@@
 
-yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
-  replace_na(list(Parliament = ""))
 elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
@@
 But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
-For instance, think of how a new government often goes to some trouble to appear different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
+For instance, think of how a new government often goes to some trouble to seem different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
 
-In this paper we examine text records of what was said in Australian state and federal parliaments. Our earliest record is from 1851 and we consider the time period through to 2017. 
-<!-- The dataset is detailed in Section \@ref(data).  -->
-We use a topic model for dimensionality reduction and to allow for correlation between topics and steady changes over time.
+In this paper we examine text records of what was said in Australian's federal parliament.
+We create a dataset based on all sitting days from 1901 through to 2017.
+Over this period we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons.
+Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove punctuation and numbers and join commonly collocated words.
+
+We use a topic model that allows correlation between topics to reduce the dimensionality of our dataset.
 We then analyse the topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
-These events include: changes in government or elections; changes in economic conditions; and other significant events such as the 9/11 attacks.
-<!-- The models are detailed in Section \@ref(model). -->
+These events include: changes in government; elections; changes in economic conditions; and other significant events such as the 9/11 attacks.
 
-<!-- Section \@ref(results) details our results, but broadly  -->
-We find: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
-**[More here on the nature of the differences.]**
+The advantage of using an analysis model in this way is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
+The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
 
-In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events.
-From a data perspective we contribute **[TBD]**.
-From a methods perspective, we contribute **[TBD]**.
-Our model can be used in many settings where the results of topic models need to be further analysed.
+We find: 1) changes in government tend be associated with topic changes even when the party in power does not change.
+For instance, the change from Menzies to Holt in 1966; the change from Hawke to Keating in 1991; and the change from Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
+2) As expected, elections where the party in power also changes, such as Whitlam in 1972, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 2001 and 2004 Howard re-elections stand out as elections where the government was returned yet there was a significant change in topics.
+3) Economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+**[More here on that one.]** **[Do we have different slopes that we could talk about?]**
 
-Our work is cross-disciplinary and in the traditions of political economy, economic history, political science and statistics.
-It contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
+Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
@@
 Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
-This allowed for long time frames and wide comparisons.
-But analysing Hansard records and their equivalents directly are an increasingly viable and popular source of data as new methods and reduced computational costs make larger-scale analysis easier, complementing other measures.
+This allowed for long time-frames and wide comparisons.
+But analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.
+
+[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
+@Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.
+As those who create Hansard are tasked with creating an accurate record of proceedings, this suggests the records should be fit for the purpose of our analysis.
 
@@
 In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
-And in the US @GentzkowShapiroTaddy2018 examine congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
+And in the US @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
 
-[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
-For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
-@Edwards2016 examined Australia, New Zealand and the UK, and found that changes were usually made by those responsible for creating the Hansard record, instead of the parliamentarians.
-
-Australian Hansard records have been analysed for various purposes.
+Parts of Australian Hansard records have been analysed for various purposes.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
-There are roughly 54,331 **[UPDATE]** days worth of publicly available Hansard records across the state and federal parliaments (Table \ref{tab:yearsusedtable}).
+There are 14,551 days worth of publicly available Hansard records across the houses of federal parliament.
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
 
-```{r yearsusedtable, echo = FALSE, results = 'asis'}
-
-yearsUsed %>%
-  kable(
-    booktabs = T,
-    align = c('l', 'r', 'r', 'r'),
-    caption = "Hansard records used") %>%
-  kable_styling(font_size = 12)
-
-```
-
-The formatting of the Hansard records changes between the different parliaments and over time.
+The formatting of the Hansard records changes over time.
 We use scripts written in R (@R2018) to convert the PDFs into daily text records.
@@
 An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are corrected when they occur at scale and can be identified.
+These errors are corrected when they occur more than twice and can be identified.
 
@@
 This suggests that there is no significant difference in the quality of the parsing over time.
-Details of this process are provided in Appendix \@ref(stopwordsgraph).
-We mainly use Hansard records on a daily basis in this paper.
-Text is usually pre-processed before topic models are used.
+Details of this check are provided in Appendix \@ref(stopwordsgraph).
+We use Hansard records on a daily basis in this paper.
+We pre-process our text before applying a topic model.
 The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multiword names titles and phrases, such as new zealand to new_zealand.
@@
 The goal of our modeling strategy is twofold.
-Firstly, we want to topic modeling __(REF)__ to summarise all text contained in Hansard into meaningful topics, which reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
+Firstly, we want to use topic modeling [@Blei2003latent] to summarise the Hansard text into meaningful topics, which reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes and events, such as governement changes, elections, and other external events.
 
-We use a Correlated Topic Model (CTM) __(REF)__ to obtain estimated topic distributions over time.
+We use a Correlated Topic Model (CTM) @BleiLafferty2007 to obtain estimated topic distributions over time.
 We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
 We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
-__In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.__
+In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
 
@@
 However, in relaity, we would expect Hansard topics related the army may be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-The goal of the CTM __(REF)__ is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
+The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
 
@@
 The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
-__(REF)__ develop a fast variational inference procedure for estimating the CTM.
+@BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
 This estimation approach has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
@@
 For the next stage of the modeling process, we are interested in how the distribution of topics changes in relation to different types of events.
-But with around 40 topics **[UPDATE]** for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events.
+But with 40 topics for each of the roughly 14,551 **[UPDATE]** house-sitting-days the data are still too noisy to easily visualise changes around events.
 

### 2018-10-14 outputs/docs/events/paper.Rmd
Fix annoying minor typos

@@
     template: svm-latex-ms.tex
-title: "The Effect of Events on Australian Federal Parliamentary Discussion (1901--2017)"
+title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
@@
 abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
-We first create a dataset of what was said in the Australian Federal parliament from 1901 through to 2017 based on available public records.
+We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
 To reduce the dimensionality of this dataset we use a correlated topic model.
 We analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 1) elections that do not result in a change in government are rarely associated with topic changes; 2)  3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
+We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 2) elections that do not result in a change in government are rarely associated with topic changes; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
 Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycle becomes increasingly focused on short-term events."
@@
 
-In this paper we examine text records of what was said in Australian's federal parliament.
+In this paper we examine text records of what was said in the Australian Federal Parliament.
 We create a dataset based on all sitting days from 1901 through to 2017.
-Over this period we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons.
-Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove punctuation and numbers and join commonly collocated words.
+This means that we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons.
+Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove numbers and punctuation, join commonly co-located words, and remove stop words.
 
@@
 
-The advantage of using an analysis model in this way is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
-The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
-
 We find: 1) changes in government tend be associated with topic changes even when the party in power does not change.
-For instance, the change from Menzies to Holt in 1966; the change from Hawke to Keating in 1991; and the change from Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
+For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
 2) As expected, elections where the party in power also changes, such as Whitlam in 1972, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 2001 and 2004 Howard re-elections stand out as elections where the government was returned yet there was a significant change in topics.
@@
 Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
+The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
+The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
@@
 ## Parliamentary text data
-Following the example of the UK a daily text record called Hansard of what was said in Australian parliaments has been made available since their establishment.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
+Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
 This allowed for long time-frames and wide comparisons.
@@
 
-Australian parliaments generally make their daily Hansard records available online as PDFs and these are considered the official release.
+The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.
 Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
-There are 14,551 days worth of publicly available Hansard records across the houses of federal parliament.
+There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament.
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
 # Results
-We are interested in considering the effect of various events on what is talked about in Australia's parliaments. 
+We are interested in considering the effect of various events on what is talked about in the Australian Federal Parliament.
 <!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
@@
 While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
+
+Add discussions about weakenss of the model.
+
+Add other discussion that I thought of and now forget.
 

### 2018-10-14 scripts/from_monica/exploratory_4.Rmd
code copied from server

@@
 ---
-title: "Dirichlet with government groups"
+title: "Dirichlet with election groups"
 author: "Monica Alexander"
@@
 
-Now we have a model going, let's try and add in some groupings based on changes in government.
+Now we have a model going, let's try and add in some groupings based on changes in elections.
 Hopefully then we will be able to visualize the 'average' topic distributions across governments.
@@
 ```{r}
-dr <- d %>% 
-  filter(electionCounter %in%41:42)
+dr <- d %>% filter(electionCounter>43)
 ```
@@
                   y.stp = y.stp)
-parnames <- c("alpha", "mu.sp", "mu.alpha")
+parnames <- c("alpha", "mu.sp", "mu.alpha", "sigma.s")
 
@@
 mcmc.array <- mod$BUGSoutput$sims.array
-PlotTrace("mu.alpha[1,1]", mcmc.array)
+#save(mcmc.array, file = "mcmc.array.Rda")
+PlotTrace("sigma.s[16]", mcmc.array)
 ```
@@
 }
+write_csv(mu_res, "./elections/mu_res.csv")
 ```
@@
   facet_wrap(~topic)
+ggsave("./elections/mus_election.pdf", width = 15, height = 10)
 ```
@@
 }
+write_csv(alpha_res, "./elections/alpha_res.csv")
 ```
@@
 alpha_res %>% 
-  ggplot(aes(sitting, median, color = factor(election))) + geom_point() + facet_wrap(~topic)
+  ggplot(aes(sitting, median, color = factor(election))) + geom_line(lwd = 0.2) + geom_point(size = 0.1) + facet_wrap(~topic)
+ggsave("./elections/alphas_election.pdf", width = 30, height = 20)
 ```

### 2018-10-14 scripts/from_monica/governments.Rmd
code copied from server

--- 2018-10-14 scripts/from_monica/exploratory_4.Rmd
@@
 ---
-title: "Dirichlet with election groups"
+title: "Dirichlet with government groups"
 author: "Monica Alexander"
@@
 ---
-
-Now we have a model going, let's try and add in some groupings based on changes in elections.
-Hopefully then we will be able to visualize the 'average' topic distributions across governments.
-Let's try
-
-$$
-\gamma_{stp} \sim Dirichlet(\mu_{stp}) \\ 
-\log \mu_{stp} = \alpha_{sp} + \delta_{stp}\\
-\alpha_{s1} = 0 \\
-\alpha_{sp} \sim N(\eta_{g[s]}, \sigma^2_g) \text { for } p>1 \\
-\delta_{s,t,p} \sim N(\delta_{s,t-1,p}, \sigma^2_{\delta}) \\
-\sigma^2_{\delta} \sim U(0, 40)
-$$
 
@@
 ```{r}
-dr <- d %>% filter(electionCounter>43)
+dr <- d 
 ```
@@
 ```{r}
-dr %>% 
-  ggplot(aes(document, gamma, fill = factor(topic))) + geom_bar(stat = "identity")
-```
-
-```{r}
-unique(dr$electionCounter)
+unique(dr$governmentChangeDate)
 ```
@@
 
-election.s <- (dr_long %>% group_by(group) %>% summarise(election = electionCounter[row_number()==1]) %>% dplyr::select(election) %>% pull()) - min(dr_long$electionCounter) + 1
+# note: still calling elections but it is governments
+election.s <- (dr_long %>% group_by(group) %>% summarise(election = governmentChangeDate[row_number()==1]) %>% dplyr::select(election) %>% pull())
 
-nelections <- length(unique(dr_long$electionCounter))
+nelections <- length(unique(dr_long$governmentChangeDate))
+
+election.s <- sapply(1:length(election.s), function(i) which(unique(dr_long$governmentChangeDate) == election.s[i]))
 
@@
 mcmc.array <- mod$BUGSoutput$sims.array
-#save(mcmc.array, file = "mcmc.array.Rda")
-PlotTrace("sigma.s[16]", mcmc.array)
+save(mcmc.array, file = "./governments/mcmc.array.Rda")
+PlotTrace("sigma.s[24]", mcmc.array)
 ```
@@
   facet_wrap(~topic)
-ggsave("./elections/mus_election.pdf", width = 15, height = 10)
+ggsave("./governments/mus_election.pdf", width = 15, height = 10)
 ```
@@
 }
-write_csv(alpha_res, "./elections/alpha_res.csv")
+write_csv(alpha_res, "./governments/alpha_res.csv")
 ```
@@
   ggplot(aes(sitting, median, color = factor(election))) + geom_line(lwd = 0.2) + geom_point(size = 0.1) + facet_wrap(~topic)
-ggsave("./elections/alphas_election.pdf", width = 30, height = 20)
+ggsave("./governments/alphas_election.pdf", width = 30, height = 20)
 ```

### 2018-10-14 scripts/from_monica/getsplines.R

@@ -1,0 +1,29 @@
+GetSplines <- function(
+  x.i,
+  x0 = NULL,
+  I = 2.5,
+  degree = 3
+) {
+  if (is.null(x0)) {
+    x0 <- max(x.i)-0.5*I
+  }
+  # get knots, given that one knot needs to be in year0
+  knots <- seq(x0-1000*I, x0+1000*I, I)
+  while (min(x.i) < knots[1]) knots <- c(seq(knots[1]-1000*I, knots[1]-I,I), knots)
+  while (max(x.i) > knots[length(knots)]) knots <- c(knots, seq(knots[length(knots)]+I,
+                                                                knots[length(knots)]+1000*I, I))
+  Btemp.ik <- bs(x.i, knots = knots[-c(1, length(knots))],  degree = degree,
+                 Boundary.knots = knots[c(1, length(knots))])
+  indicesofcolswithoutzeroes <- which(apply(Btemp.ik, 2, sum) > 0)
+  # only remove columns with zeroes at start and end
+  startnonzerocol <- indicesofcolswithoutzeroes[1]
+  endnonzerocol <- indicesofcolswithoutzeroes[length(indicesofcolswithoutzeroes)]
+  B.ik <- Btemp.ik[,startnonzerocol:endnonzerocol]
+  colnames(B.ik) <- paste0("spline", seq(1, dim(B.ik)[2]))
+  knots.k <- knots[startnonzerocol:endnonzerocol]
+  names(knots.k) <- paste0("spline", seq(1, dim(B.ik)[2]))
+  ##value<< List of B-splines containing:
+  return(list(B.ik = B.ik, ##<< Matrix, each row is one observation, each column is one B-spline.
+              knots.k = knots.k ##<< Vector of knots.
+  ))
+}

### 2018-10-14 scripts/from_monica/results.R

@@ -1,63 +1,122 @@
-# trying to get results in useable form
+### goals
 
-library(tidyverse)
-load("mcmc.array.Rda")
-
-
-View(dimnames(mcmc.array))
-#
-ngovernments <- 32
-ntopics <- 60
-
-# pull out musi
+# 1. see which mu.govs are significantly different from the last
+# 2. see which mu.elections are dignificantly different
+# 3. find outliers within each period
+# 4. look at varinace over time
 
 
-mu_res <- c()
-for(i in 1:ngovernments){
-  for(j in 1:ntopics)
-    mu_res <- rbind(mu_res, tibble(government = i, topic = j, 
-                                   median = (median(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")])),
-                                   upper = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.95)),
-                                   lower = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.05))
-    ))
+# 1. different governments ------------------------------------------------
+
+
+mu_res_2 <- mu_res_2 %>% arrange(topic, government)
+
+#install.packages("DescTools")
+library(DescTools)
+
+mu_gov_sig <- c()
+
+for(i in 2:nrow(mu_res_2)){
+  sig <- !(c(mu_res_2$lower[i-1], mu_res_2$upper[i-1]) %overlaps% c(mu_res_2$lower[i], mu_res_2$upper[i]))
+  mu_gov_sig <- rbind(mu_gov_sig, tibble(government = mu_res_2$government[i], topic = mu_res_2$topic[i], sig))
 }
 
-mu_res <- mu_res %>% mutate(government = ifelse(government>18, government+1, government))
-write_csv(mu_res, "./governments/mu_res.csv")
+
+num_sig <- mu_gov_sig %>% spread(topic, sig) %>% 
+  select(-government) %>% rowSums()
+
+mu_gov_sig_all <- tibble(government = 1:32, sig = num_sig>0)
+
+# get original numbering 
 
 
-mu_res %>% 
-  filter(topic %in% 1:20) %>% 
-  ggplot(aes(government, median, color = factor(government))) + 
-  geom_point() + geom_errorbar(aes(ymin = lower, ymax = upper)) + 
-  facet_wrap(~topic)
+
+mu_gov_sig_all <- mu_gov_sig_all %>% cbind(original_number = 
[…]

### 2018-10-14 scripts/from_monica/run_elections.R

@@ -64,7 +64,7 @@ set.seed(123)
 for(i in 1:ngroups){
   ndays <- dr_long %>% ungroup() %>% filter(group==i) %>% summarise(max(day_number)) %>% pull()
   if(ndays>3){
-    no_days_to_sample <- floor(ndays/3)
+    no_days_to_sample <- floor(ndays/2)
     sampled_days <- sample(1:ndays, no_days_to_sample)
     dr_group_train <- dr_long %>% ungroup() %>% filter(group==i, day_number %in% sampled_days)
     dr_train <- bind_rows(dr_train, dr_group_train)
@@ -99,9 +99,12 @@ for (i in 1:ntopics){
 nsittings <- max(dr_train$group)
 ndays.s <- dr_train %>% group_by(group) %>% summarise(days = max(day_number_train)) %>% dplyr::select(days) %>% pull()
 
-election.s <- (dr_train %>% group_by(group) %>% summarise(election = electionCounter[row_number()==1]) %>% dplyr::select(election) %>% pull()) - min(dr_long$electionCounter) + 1
+election.s <- (dr_train %>% group_by(group) %>% 
+                 summarise(election = governmentChangeDate[row_number()==1]) %>% 
+                 dplyr::select(election) %>% pull()) 
 
-nelections <- length(unique(dr_train$electionCounter))
+nelections <- length(unique(dr_train$governmentChangeDate))
+election.s <- sapply(1:length(election.s), function(i) which(unique(dr_train$governmentChangeDate) == election.s[i]))
 
 # run the model
 
@@ -121,4 +124,40 @@ mod <- jags(data = jags.data,
 max(mod$BUGSoutput$summary[,"Rhat"])
 mcmc.array <- mod$BUGSoutput$sims.array
 save(mcmc.array, file = "mcmc.array.Rda")
-PlotTrace("sigma.s[16]", mcmc.array)
+PlotTrace("mu.alpha[23,27]", mcmc.array)
+
+mu_res <- c()
+for(i in 1:nelections){
+  for(j in 1:ntopics)
+    mu_res <- rbind(mu_res, tibble(election = i, topic = j, 
+                                   median = (median(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")])),
+                                   upper = (quantile(mcmc.array[,,paste0("mu.alpha[",i,",",j,"]")], 0.975)),
[…]

### 2018-10-14 outputs/docs/events/paper.Rmd

@@
 Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
-The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
+More specifically, we contribute in terms of both data and methods.
+To the best of our knowledge...
+**[dataset claim]**.
+Our dataset is available to other researchers via an accompanying R Package.
+**[Methods claim...]** The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
 The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
+
+**[Selling points:]**
+**[Almost complete record. Unique word count.]**
+**[Different events method.]**
+**[Highlight increase in volatility. ADD TO ABSTRACT. DISCUSS IMPLICATIONS IN DISCUSSION. Personality driven.]**
+**[Gary King paper?]**
 

### 2018-10-16 outputs/docs/events/paper.Rmd
Update paper through to analysis model writing

--- 2018-10-14 outputs/docs/events/paper.Rmd
@@
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
+Our dataset is available via an R package detailed at https://hansardr.com.
+Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
 author:
@@
 We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
-To reduce the dimensionality of this dataset we use a correlated topic model.
-We analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: 1) changes in government tend be associated with topic changes even when the party in power does not change; 2) elections that do not result in a change in government are rarely associated with topic changes; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
-Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycle becomes increasingly focused on short-term events."
+To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
+We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
+Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
 keywords: "text analysis, politics, Australia"
@@
 Conversely, that same discussion can indicate a government's priorities.
-But major events--both expected, such as an election, and unexpected, such as a recession or terrorist attack--can affect the course of parliamentary discussion.
+But major events -- be they expected, such as an election, and unexpected, such as a recession or terrorist attack -- can affect the course of parliamentary discussion.
 For instance, think of how a new government often goes to some trouble to seem different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
@@
 We create a dataset based on all sitting days from 1901 through to 2017.
-This means that we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate, although we drop a handful of days for various reasons.
+Although we drop a handful of days for various reasons, we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
 Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove numbers and punctuation, join commonly co-located words, and remove stop words.
 
-We use a topic model that allows correlation between topics to reduce the dimensionality of our dataset.
+To reduce the dimensionality of our dataset we use a topic model that allows correlation between topics.
 We then analyse the topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
-These events include: changes in government; elections; changes in economic conditions; and other significant events such as the 9/11 attacks.
+These events include: changes in government; elections; and other significant events such as an economic recession or terrorism.
 
@@
 For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
-2) As expected, elections where the party in power also changes, such as Whitlam in 1972, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 2001 and 2004 Howard re-elections stand out as elections where the government was returned yet there was a significant change in topics.
-3) Economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks.
-**[More here on that one.]** **[Do we have different slopes that we could talk about?]**
+2) As expected, elections where the party in power also changes, such as Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
+3) Economic events, such as financial crises, have less significant effects than other events such as terrorism.
+
+As our dataset covers 117 years we are able to see how the effect of events changes over time.
+We find that the events that we are interested in are rarely significant in the first half of our dataset.
+With a small number of exceptions, even changes of government where the party in power also changed were not associated with overly large changes in parliamentary discussion.
+If governments try to more thoroughly distinguish themselves from their predecessor then longer-term policy may be more difficult to enact.
+Similarly, there is the danger that larger-scale signature-accomplishments of a government may be neglected by their successor for solely political reasons.
 
 Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
-The advantage of using our analysis model is that it: allows the events to have more-complicated autocorrelated functional forms; allows us to implement pooling across groups of similar documents; and it identifies outlying topic distributions without the need to pre-specify the event of interest.
-The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
+This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics.
+We contribute to this literature in terms of both data and methods.
+To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via an accompanying R package.
+From a methods perspective, our analysis model has several advantages over existing methods.
+These include: allowing the events to have more-complicated autocorrelated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
+
+<!-- Selling points: -->
+<!-- Almost complete record. Unique word count. -->
+<!-- Different events method. -->
+<!-- Highlight increase in volatility. ADD TO ABSTRACT. DISCUSS IMPLICATIONS IN DISCUSSION. Personality driven. -->
+<!-- Gary King paper? -->
 
@@
 
-The formatting of the Hansard records changes over time.
+We use the official PDF release and the formatting of the Hansard records changes over time.
 We use scripts written in R (@R2018) to convert the PDFs into daily text records.
@@
 The goal of our modeling strategy is twofold.
-Firstly, we want to use topic modeling [@Blei2003latent] to summarise the Hansard text into meaningful topics, which reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
-Secondly, we want to relate the resulting topic distributions to temporal trends, changes and events, such as governement changes, elections, and other external events.
+Firstly, we want to use topic modeling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
+Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
 
-We use a Correlated Topic Model (CTM) @BleiLafferty2007 to obtain estimated topic distributions over time.
+We use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
 We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
@@
 In the following sections, we describe both the topic modeling approach and the Bayesian hierarchical analysis model.
-Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving on the CTM, which is a natural extension of LDA.
+Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving onto the CTM, which is a natural extension of LDA.
 We then discuss the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
@@
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent.[^topicmodelsfootnote]
+One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent.
 
-[^topicmodelsfootnote]: For instance as implemented by the R \texttt{topicmodels} package of @Grun2011.
-
-The key assumption behind the LDA method is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
+The key assumption behind LDA is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
 A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions.
@@
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
-This provides more flexibility than other approaches such as a strict word count method.
 The goal is to have the words found in each day's Hansard group themselves to define topics.
+This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.
 
-As applied to Hansard, the LDA method considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.
-After choosing the topics, the speaker then chooses appropriate words to use for each of those topics.
-More generally, the LDA topic model works by considering each document as having been generated by some probability distribution over topics.
-Similarly, each topic could be considered a probability distribution over terms.
-To choose the terms used in each document the speaker picks terms from each topic in the appropriate proportion.
-Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrates an example with five topics, two documents, and ten terms.
+As applied to Hansard, LDA considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.
+After choosing the topics, the politician then chooses appropriate words to use for each of those topics.
+Statistically, LDA considers each document as having been generated by some probability distribution over topics.
+Similarly, each topic is considered a probability distribution over terms.
+To choose the terms used in each document, terms are picked from each topic in the appropriate proportion.
+Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrate an example with five topics, two documents, and ten terms.
 
@@
 Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
-Again, strictly $\alpha$ is vector of length $K$ of hyperparameters, but in practice each is usually the same value.
+Again, strictly $\boldsymbol{\alpha}$ is vector of length $K$ of hyperparameters and tehy are usually equal.
 3. If there are $1, 2, \dots, n, \dots, N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
@@
 Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-This motivates the use of the Correlated Topic Model, described in the next section.
+This is the Correlated Topic Model, described in the next section.
 
@@
 As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
-Indeed, the corrleation between topics is not modeled or accounted for.
-However, in relaity, we would expect Hansard topics related the army may be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+Correlation between topics is neither modeled nor accounted for by LDA, but in reality often topics are related.
+For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
 The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
+The models are very similar, and the key difference is the underlying distributions that are drawn from.
 
 As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is slightly modified.
+The document generation process of @Blei2003latent discussed earlier, is just slightly modified.
 Rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
@@
 $$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
-This is the main addition of CTM over LDA, in that it replaces the assumption of the Dirichlet distribution with a more flexible logistic Normal distribution, which incorporates a covariance structure across the topics.
+This is, the main difference between the CTM and LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic Normal distribution.
+That distribution can incorporate a covariance structure across the topics.
 The remainder of the steps of the document generating process are identical to LDA.
@@
 @BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
-This estimation approach has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
+CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
+The main difference is to add a covariate to $\mu$ which allows consideration of additional information such as metadata.
 
@@
 
-Figure \@ref(fig:exampletopics) illustrates an output of the CTM This illustrative example only shows five per cent of data from the House of Representatives between 1901 and 2017.
-It shows how each day's parliamentary discussion can be allocated to a topic and highlights how the prominence of these topics changes over time.
+Figure \@ref(fig:exampletopics) illustrates a CTM output only a five per cent sample from the Australian House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
 
@@
 $$
-\alpha_{g[s],p} \sim N(0, 100)
+\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)
 $$
@@
 $$
-\alpha_{e[s],0,p} \sim N(0, 100)
+\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100)
 $$
 $$
-\rho_{e[s],p} \sim U(0,1)
+\rho_{e[s],p} \sim \mbox{Uniform}(0,1)
 $$
@@
 $$
-\beta_{p,k} \sim N(0, 100)
+\beta_{p,k} \sim \mbox{Normal}(0, 100)
 $$
@@
 $$
-\delta_{s,p} \sim N(0, \sigma_{e[s],p}^2)
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
 $$
@@
 $$
-\sigma_{e[s],p} \sim U(0,3)
+\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
 $$
 
-We run the model in Stan using the \texttt{RStan} package of @RStan. __An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation). __
+We run the model in JAGS using the \texttt{rjags} package of @Plummer2018.
+__An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
+__
 
@@
 
-Add discussions about weakenss of the model.
+Add discussions about weakenss of the model. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
+
+Add discussion of the weakness of the dataset.
 

### 2018-10-17 outputs/docs/events/paper.Rmd
Update results write up

@@
 hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
+
+elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
+  filter(Significant %in% c("Yes", "No"))
+
+governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
+  filter(Significant %in% c("Yes", "No")) %>% 
+  select(-Party, -`Died in Office`)
 
@@
 CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
-The main difference is to add a covariate to $\mu$ which allows consideration of additional information such as metadata.
+The main difference is to add a covariate to $\mu$ which allows consideration of additional information.
 
@@
 
-Figure \@ref(fig:exampletopics) illustrates a CTM output only a five per cent sample from the Australian House of Representatives between 1901 and 2017.
+Figure \@ref(fig:exampletopics) illustrates a CTM output based on a five per cent sample from the Australian House of Representatives between 1901 and 2017.
 It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
@@
 
-The main output of the CTM of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
-For the next stage of the modeling process, we are interested in how the distribution of topics changes in relation to different types of events.
-But with 40 topics for each of the roughly 14,551 **[UPDATE]** house-sitting-days the data are still too noisy to easily visualise changes around events.
+The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
+The aim of this stage of the modeling process is to analyse how the distribution of topics changes in relation to different types of events.
+But with 40 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
 
-One option for relating the topic distributions to events would be to use a Structural Topic Model (STM) [@RobertsStewartAiroldi2016].
+One option for relating the topic distributions to events would be to use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016.
 The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
 For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the government or election period, may affect the topics within that document.
-The STM allows this additional information, or meta-data, to affect the construction of topics, though influencing either topical prevalence or topical content.
-The assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
+The assumption that there is some document generation process is the same as in LDA, it is just that this process now includes metadata.
 
-Consider a matrix of covariates $X_d$, where each column relates to a different covariate or aspect of the meta-data, and the row refers to document $d$ value of each covariate.
+More specifically, consider a matrix of covariates.
+$X_d$, where each column relates to a different covariate or metadata aspect, and each row refers to a document.
+Then a cell has the value of each covariate for a particular document.
 Similar to the CTM, the STM assumes the topics within a document $\theta_d$ are a draw from a logistic Normal distribution with mean $\mu$.
@@
 
-The STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
-For example, one covariate within the model could be the government $g$ that was in power during the time corresponding to document $d$.
-However, there are several limitations to the STM covariate framework in relation to our goal of assess the relationship between topics and events:
+Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
+For instance, one covariate could be the government $g$ that was in power during the time corresponding to document $d$.
+However, the STM covariate framework has several limitations in terms of our goal to assess the relationship between topics and events:
 
@@
 For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
-In the STM framework, it is possible to specify constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
-- There is no way of implementing partial pooling across groups of similar documents.
-The STM framework assumes that  documents are independently and identically distributed conditional on the covariates in the model.
-However, it could be expected that topic distributions within a particular government period, for example, may be more or less likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
+In the STM framework, it is possible to specify a constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
+- There is no way to implement partial pooling across groups of similar documents.
+The STM framework assumes that  documents are independently and identically distributed, conditional on the model covariates.
+However, it could be expected that topic distributions within a particular government, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
 To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
 - There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
-For example, if we think that the 9/11 terrorist attacks had an effect on parliamentary discourse, a dummy for 9/11 would have to be included in the STM framework.
+For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
 Ideally, we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
 
-To overcome these challenges, we formalize a statistical framework which allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates proportions of each topic to underlying time trends, changes in goverments and elections.
-This set-up also allows us to identify 'outlying' topic distributions and relate these to other, non-scheduled political events.
+To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
+Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in goverments and elections.
+This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
 
@@
 We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are a total of 745 sitting periods across all years of interest (1901--2017).
+Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
 
-The topic proportions on day $d$ are modeled in reference to their membership in a particular sitting period $s$.
+The topic proportions on day $d$ are modeled in reference to their membership of a particular sitting period $s$.
 Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
@@
 $$
-where the notation $s[d]$ refers to the sitting period $s$ which day $d$ belongs to.
+where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
 This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
 
-The goal of the model is to relate these proportions to the government $g$ of time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
 The mean parameters $\mu_{sp}$ are modeled on the log scale as
@@
 
-- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$
-- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election
-- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modeled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$, and $\beta_{p,k}$ is a cofficient on the $k$th basis spline.
-- $\delta_{s,p}$ is a structured random effect for each sittiing period and topic.
+- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
+- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modeled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a cofficient on the $k$th basis spline; and
+- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
 
@@
 $$
-The value of the initial effect $\alpha_{e[s],0,p}$ and the AR(1) term $\rho$ both have non-informative priors:
+The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
 
@@
 The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
-The $x_{s,k}$ for $k = 1,2,\dots K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
-We chose to place knot points every 5 sitting periods as this is the average length of time for a government to sit (**CHECK**).
+The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
+We place knot points every five sitting periods as this is the average length of time for a government to sit (**CHECK**).
 Non-informative priors are placed on the splines coefficients:
@@
 
-Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on the government/election effects.
+Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
 This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
 In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{s,p}$'s are modeled as
+The $\delta_{s,p}$ values are modeled as:
 
@@
 # Results
-We are interested in considering the effect of various events on what is talked about in the Australian Federal Parliament.
-<!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
+We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
 Political events are those related to a change of government or an election.
-Other events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
-The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
+As Australia has a parliamentary system, it is possible for the government to change without an election.
+We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
+If a person was prime minster more than once then these are considered separately.
+If the mean parameter for a government or election period is outside the 95 per cent credible interval, then we consider that period to be different.
 
-First considering the mean topic distributions over governments, Figures \@ref(fig:mu1to20) - \@ref(fig:mu41to60).
+We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults).
+Those tables focus on elections and governments that were different to the ones that preceeded them.
 
-```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_topic1-20.pdf")
+```{r electionsresults, echo = FALSE, results = 'asis'}
+
+elections_results %>%
+  kable(booktabs = T, caption = "Significant elections, and neighours") %>%
+  kable_styling(font_size = 12)
+
 ```
 
-```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_topic21-40.pdf")
+```{r governmentsresults, echo = FALSE, results = 'asis'}
+
+governments_results %>%
+  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
+  kable_styling(font_size = 12)
+
 ```
 
-```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_topic41-60.pdf")
+In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
+
+<!-- 12;war, defence, country, ill, soldiers -->
+<!-- 13;industry, trade, countries, development, country -->
+<!-- 17;security, time, world, war, country -->
+<!-- 22;war, country, matter, production, time -->
+<!-- 23;defence, time, national, service, vietnam -->
+<!-- 24;time, budget, tax, billion, million -->
+<!-- 29;education, schools, students, school, university -->
+<!-- 30;oil, energy, industry, nuclear, research -->
+<!-- 32;industry, wheat, wool, growers, farmers -->
+<!-- 33;per_cent, budget, time, tax, business -->
+<!-- 35;community, time, health, support, local -->
+<!-- 39;health, services, funding, care, million -->
+
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_gov.pdf")
 ```
 
-Topics related to Federation such as the British Empire and the constitution decrease in importance over time. A substantial increase in the importance of issues dealing with
+```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election.pdf")
+```
 
-Increasing from 20th gov: 2, 4, 8, 12,
+**[Add some nice for specific changes for the discussion section?]**
 
-32 increases and then decreases
+Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
+The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
+Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.
 
-Increases only recently: 33, 35
+We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy.]**
 
-Breakpoint: 23, 25, 49, 48, 46, 47, 41
+We summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))
 
-Figure \@ref(fig:electionsevents) shows the grouping by election.
-If elections had significant effects on the discussion in parliament then there would be considerable change between groups.
-However changes generally appear to be longer-term rather than election to election.
+```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/sigma.pdf")
+```
 
+# Discussion
 Groupings by government.
@@
 Similarly, John Howard's three terms are all considered the one government for our purposes.
-
-Here we see much more difference between adjacent events. This suggests that new governments tend to talk about different topics than the government they replace.
-
-For instance, all of the incrementing variables have a significant effect on the prevalence of Topic 1.
-Table \@ref(tab:topwordssig) shows that this has to do with tariffs and trade.
-On the other hand, Topic 2 has to do with aspects of daily life such as community and children, and Topic 3 has to do with legal issues and neither is significant.
-This is not surprising given the centrality of these concerns at all times.
-
-```{r topwordssig, echo = FALSE, results = 'asis'}
-
-top_words %>% 
-  kable(booktabs = T, caption = "Top words for each topic") %>%
-  kable_styling(font_size = 8)
-
-```
 
@@
 
-Add discussions about weakenss of the model. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
+Add discussions about weakness of the model. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
 

### 2018-10-17 scripts/run_6_make_graphs/make_graphs_of_mu.R

@@ -1,0 +1,48 @@
+library(tidyverse)
+
+mu_election <- read_csv("scripts/from_monica/results/mu_election.csv")
+
+mu_election %>% 
+  ggplot(aes(x = election, y = median)) +
+  geom_point() +
+  facet_wrap(vars(topic)) 
+  
+mu_election %>% 
+  filter(topic %in% c(12, 13, 17, 22, 23, 24, 29, 30, 32, 33, 35, 39)) %>% 
+  ggplot(aes(x = election, y = median)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_wrap(vars(topic), nrow = 4, ncol = 3) +
+  theme_minimal()
+
+ggsave(
+  "outputs/figures/mu_election.pdf",
+  height = 10,
+  width = 8,
+  units = "in"
+)
+
+
+
+mu_gov <- read_csv("scripts/from_monica/results/mu_gov.csv")
+
+mu_gov %>% 
+  ggplot(aes(x = government, y = median)) +
+  geom_point() +
+  facet_wrap(vars(topic)) 
+
+mu_gov %>% 
+  filter(!government %in% c(19, 32)) %>% 
+  filter(topic %in% c(12, 13, 17, 22, 23, 24, 29, 30, 32, 33, 35, 39)) %>% 
+  ggplot(aes(x = government, y = median)) +
+  geom_point() +
+  geom_errorbar(aes(ymin = lower, ymax = upper)) +
+  facet_wrap(vars(topic), nrow = 4, ncol = 3) +
+  theme_minimal()
+
+ggsave(
+  "outputs/figures/mu_gov.pdf",
+  height = 10,
+  width = 8,
+  units = "in"
+)

### 2018-10-17 scripts/run_6_make_graphs/make_graphs_of_sigma.R

@@ -1,0 +1,17 @@
+library(tidyverse)
+
+sigma <- read_csv("scripts/from_monica/results/sigma.csv")
+
+sigma %>% 
+  filter(topic %in% c(4:15)) %>% 
+  ggplot(aes(x = election, y = sigma_median)) +
+  geom_point() +
+  facet_wrap(vars(topic), nrow = 4, ncol = 3) +
+  theme_minimal()
+
+ggsave(
+  "outputs/figures/sigma.pdf",
+  height = 10,
+  width = 8,
+  units = "in"
+)

### 2018-10-18 outputs/docs/events/paper.Rmd
Start discussion writeup

@@
 thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-Our dataset is available via an R package detailed at https://hansardr.com.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 We contribute to this literature in terms of both data and methods.
-To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via an accompanying R package.
+To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
 From a methods perspective, our analysis model has several advantages over existing methods.
@@
 The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.
-Additionally, XML records are available in some cases.[^XMLfootnote] We detail the sources of our Hansard PDFs in \@ref(hansardsources) and Appendix \@ref(examplehansardpage) provides an example of what a Hansard PDF looks like.
+Additionally, XML records are available in some cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
 There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament.
@@
 We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
-In Appendix \@ref(word2vec), we include an alternative approach that follows @Taddy2015 by using word2vec, which more closely uses words, rather than topics, as an input.
 
@@
 We run the model in JAGS using the \texttt{rjags} package of @Plummer2018.
-__An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).
-__
+__[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __
 
@@
 We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults).
-Those tables focus on elections and governments that were different to the ones that preceeded them.
+These tables focus on elections and governments that were different to the ones that preceeded them.
 
@@
 
-<!-- 12;war, defence, country, ill, soldiers -->
-<!-- 13;industry, trade, countries, development, country -->
-<!-- 17;security, time, world, war, country -->
-<!-- 22;war, country, matter, production, time -->
-<!-- 23;defence, time, national, service, vietnam -->
-<!-- 24;time, budget, tax, billion, million -->
-<!-- 29;education, schools, students, school, university -->
-<!-- 30;oil, energy, industry, nuclear, research -->
-<!-- 32;industry, wheat, wool, growers, farmers -->
-<!-- 33;per_cent, budget, time, tax, business -->
-<!-- 35;community, time, health, support, local -->
-<!-- 39;health, services, funding, care, million -->
-
 ```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
@@
 
-**[Add some nice for specific changes for the discussion section?]**
+The topics that we have focused on here are:
+12: war, defence, country, ill, soldiers; 
+13: industry, trade, countries, development, country; 
+17: security, time, world, war, country; 
+22: war, country, matter, production, time; 
+23: defence, time, national, service, vietnam; 
+24: time, budget, tax, billion, million; 
+29: education, schools, students, school, university; 
+30: oil, energy, industry, nuclear, research; 
+32: industry, wheat, wool, growers, farmers; 
+33: per_cent, budget, time, tax, business; 
+35: community, time, health, support, local; and
+39: health, services, funding, care, million.
 
@@
 
-We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy.]**
+We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy. Not sure what to do here.]**
 
-We summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))
+Finally, we summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))
 
@@
 # Discussion
+
+Of the 36 different governments, we find that 12 of them are significantly different to the government that preceeded them.
+However, two of these -- Page and the first Menezies government -- are likely due to the short length of the Page Government, and should be ignored, leaving only ten.
+The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years.
+
+The significant difference of the second Menzies Government is associated with a variety of changes.
+The Chifley Government that preceeded it had finsih  For instance there was a large increase in the number of lower house seats at the 1949 election.
+This brought many new politicians into the house and it may be that they brought different topics.
+
+Of the 45 general elections that have been held we find that 12 of them define periods that were significantly different to their immediate predecessor.
+1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
+
 Groupings by government.
@@
 Similarly, John Howard's three terms are all considered the one government for our purposes.
+
+**[Add some nice for specific changes for the discussion section?]**
 
@@
 # Hansard details
-
-## Hansard sources {#hansardsources}
-
-Hansard records are available from a variety of sources, as detailed in Table \ref{tab:hansardsourcestable}.
-
-```{r hansardsourcestable, cache = TRUE, echo = FALSE, results = 'asis'}
-
-hansard_sources %>%
-  kable(
-    booktabs = T,
-    align = c('l', 'r', 'r', 'r'),
-    caption = "Hansard sources and notes") %>%
-  kable_styling(font_size = 10)
-
-# Break cachee
-
-```
-
-Detail where from, and which years are being used and why.
-
-Which years are being used (not non-OCRd)
 
@@
 Insert graph of stop words over time.
-
-\newpage
-
-# word2vec alternative {#word2vec}
-An alternative approach that follows @Taddy2015.
 

### 2018-10-18 scripts/run_4_model_topics/run_0_topic_modelling_stm.R

@@ -27,68 +27,62 @@ library(tm)
 
 
 #### Load corpus
-tm_corpus <- tm::Corpus(DirSource(directory = "/Volumes/Backup/senate_topic_modelling_prep_2"))
+tm_corpus <-
+  tm::Corpus(DirSource(directory = "/Volumes/Backup/senate_topic_modelling_prep_2"))
 hansard <- corpus(tm_corpus)
 summary(hansard)
+rm(tm_corpus)
 
 
-# Load the metadata
-election_dates <-
-  read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
-hansard_dates <-
-  read_csv("inputs/misc/hansard_dates.csv", col_types = cols())
-governmentChanges <-
-  read_csv("inputs/misc/change_of_pm.csv", col_types = cols())
-keyEvents <-
-  read_csv("inputs/misc/key_events.csv", col_types = cols())
-
-
-
-# Add metadata
-all_dates <-
-  tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
-  mutate(
-    electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
-    electionDate = cumsum(electionDate),
-    governmentChangeDate = if_else(allDates %in% governmentChanges$end, 1, 0),
-    governmentChangeDate = cumsum(governmentChangeDate),
-    keyEvent = if_else(allDates %in% keyEvents$theDate, 1, 0),
-    keyEvent = cumsum(keyEvent),
-    electionOrGovernmentDate = if_else(allDates %in% c(election_dates$electionDate, governmentChanges$end), 1, 0),
-    electionOrGovernmentDate = cumsum(electionOrGovernmentDate)) %>%
-  rename(
-    electionCounter = electionDate,
-    governmentCounter = governmentChangeDate,
-    electionOrGovernmentCounter = electionOrGovernmentDate
-  )
-  
-head(all_dates)
-
-# all_dates <- all_dates %>%
-#   select(-keyEconomicChange, -keyOtherChange) %>%
-#   mutate(governmentChangeDate = governmentChangeDate + 1) %>%
-#   filter(allDates > "1901-03-29")
+# NEED TO COME BACK AND ADD METADATA
+# # Load the metadata
+# election_dates <-
+#   read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
[…]

### 2018-10-19 outputs/docs/events/paper.Rmd
Update paper

@@
 title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
-thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
-keywords: "text analysis, politics, Australia"
+keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 Although we drop a handful of days for various reasons, we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
-Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lowercase, remove numbers and punctuation, join commonly co-located words, and remove stop words.
+Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case, remove numbers and punctuation, join commonly co-located words, and remove stop words.
 
@@
 From a methods perspective, our analysis model has several advantages over existing methods.
-These include: allowing the events to have more-complicated autocorrelated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
+These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
@@
 We pre-process our text before applying a topic model.
-The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multiword names titles and phrases, such as new zealand to new_zealand.
-Then the sentences are deconstructed and each word considered individually.
+The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
+Then the sentences are de-constructed and each word considered individually.
 
@@
 
-The goal of our modeling strategy is twofold.
-Firstly, we want to use topic modeling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
+The goal of our modelling strategy is twofold.
+Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
@@
 
-In the following sections, we describe both the topic modeling approach and the Bayesian hierarchical analysis model.
+In the following sections, we describe both the topic modelling approach and the Bayesian hierarchical analysis model.
 Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving onto the CTM, which is a natural extension of LDA.
@@
 The distribution over the terms for the $k$th topic is $\beta_k$.
-Typically a topic would be a small number of terms and so the Dirichlet distribution with hyperparameter $\boldsymbol{\eta}$ is used: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.[^Dirichletfootnote] In practice, a symmetric Dirichlet distribution is usually used, where all elements of $\boldsymbol{\eta}$ are equal.
+Typically a topic would be a small number of terms and so the Dirichlet distribution with hyper-parameter $\boldsymbol{\eta}$ is used: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.[^Dirichletfootnote] In practice, a symmetric Dirichlet distribution is usually used, where all elements of $\boldsymbol{\eta}$ are equal.
 2.
@@
 The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
-Again, the Dirichlet distribution with the hyperparameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
-Again, strictly $\boldsymbol{\alpha}$ is vector of length $K$ of hyperparameters and tehy are usually equal.
+Again, the Dirichlet distribution with the hyper-parameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
+Again, strictly $\boldsymbol{\alpha}$ is vector of length $K$ of hyper-parameters and they are usually equal.
 3. If there are $1, 2, \dots, n, \dots, N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
@@
 If $\eta<1$, then the distribution is sparse and concentrated on a smaller number of the values, and this number decreases as $\eta$ decreases.
-A hyperparameter is a parameter of a prior distribution.
+A hyper-parameter is a parameter of a prior distribution.
 
@@
 As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
-Correlation between topics is neither modeled nor accounted for by LDA, but in reality often topics are related.
+Correlation between topics is neither modelled nor accounted for by LDA, but in reality often topics are related.
 For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
@@
 The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
-The aim of this stage of the modeling process is to analyse how the distribution of topics changes in relation to different types of events.
+The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
 But with 40 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
@@
 
-- There is no way of specifying more complicated autocorrelated functional forms of the effects of events over time.
+- There is no way of specifying more complicated auto-correlated functional forms of the effects of events over time.
 For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
@@
 To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in goverments and elections.
+Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in governments and elections.
 This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
@@
 
-The topic proportions on day $d$ are modeled in reference to their membership of a particular sitting period $s$.
+The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
 Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
@@
 The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
-The mean parameters $\mu_{sp}$ are modeled on the log scale as
+The mean parameters $\mu_{sp}$ are modelled on the log scale as
 
@@
 - $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
-- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modeled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a cofficient on the $k$th basis spline; and
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
 - $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
@@
 In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{s,p}$ values are modeled as:
+The $\delta_{s,p}$ values are modelled as:
 
@@
 We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
-If a person was prime minster more than once then these are considered separately.
+If a person was prime minister more than once then these are considered separately.
 If the mean parameter for a government or election period is outside the 95 per cent credible interval, then we consider that period to be different.
@@
 We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults).
-These tables focus on elections and governments that were different to the ones that preceeded them.
+These tables focus on elections and governments that were different to the ones that preceded them.
 
@@
 
-We summarise the periods where parliamentary discussion was significantly different in Table X. **[Oh boy. Not sure what to do here.]**
+We summarise the days where parliamentary discussion was significantly different from the rest prevailing in that week in Table X. **[Oh boy. Not sure what to do here.]**
 
-Finally, we summarise our results over time by looking at the standard deviation of sitting period estaimtes, around the mean election effect (Figure \@ref(fig:sigmaelection))
+Finally, we summarise our results over time by looking at the standard deviation of sitting period estimates, around the mean election effect (Figure \@ref(fig:sigmaelection))
 
@@
 # Discussion
+In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
+We download and parse PDFs of Hansard to create a new dataset of text.
+We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
+In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
+We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
 
-Of the 36 different governments, we find that 12 of them are significantly different to the government that preceeded them.
-However, two of these -- Page and the first Menezies government -- are likely due to the short length of the Page Government, and should be ignored, leaving only ten.
+We identify differences between governments and elections based on **[INSERT HOW]**.
+
+Of the 36 different governments over this period, we find that 12 **[UPDATE]** of them are significantly different to the government that preceded them.
+However, two of these -- Page and the first Menzies government -- are likely due to the short length of the Page Government, and should be ignored, leaving only ten **[UPDATE]**.
 The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years.
-
-The significant difference of the second Menzies Government is associated with a variety of changes.
-The Chifley Government that preceeded it had finsih  For instance there was a large increase in the number of lower house seats at the 1949 election.
-This brought many new politicians into the house and it may be that they brought different topics.
-
-Of the 45 general elections that have been held we find that 12 of them define periods that were significantly different to their immediate predecessor.
+Similarly, of the 45 general elections that have been held we find that 12 **[UPDATE]** of them define periods that were significantly different to their immediate predecessor.
 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
 
-Groupings by government.
-This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election.
-Similarly, John Howard's three terms are all considered the one government for our purposes.
+The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
+The Chifley Government had governed through the end of World War II and difficult economic times that followed.
+It is also the case that there was a large increase in the number of lower house seats at the 1949 election.
+Many new politicians entered parliament and this changed representation may also have been party to do with the changed discussion.
+The sixteen year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
 
-**[Add some nice for specific changes for the discussion section?]**
+There were six election within the second Menzies Government.
+However we do not find that any of those elections was associated with a significant change in the topics discussed.
+In this sense it was a period of consistency, especially when compared with later longer-term governments, such as the Howard Government.
 
-# Summary and conclusions
-In this paper we examined what was said in Australia's parliaments.
-We downloaded and parsed PDFs for Australian states and federal parliaments.
-We then used a text model to group the discussions into topics and analysed the effect of various events on the distribution of the discussion.
+The Menzies Government was succeeded by the Holt Government in January 1966.
+This is an example where there was a change in government without an election, as the next election only happened in November 1966.
+The Holt Government is significantly different to the Menzies Government.
 
-In general we found that changes in government changed the distribution of topics discussed in parliament, but that elections did not.
-We found that significant events such as 9/11 had substantial and lasting changes, but that with certain exceptions, economic events did not.
+**[Talk about the other significant results.]**
 
-Text analysis has well-known biases and weaknesses and is a complement to more detailed analysis such as qualitative methods and case studies.
-We consider the results presented in this paper, as well as many of those results of the larger text-as-data research program, as fitting within findings based on other methods.
+**[Add some nice graphs for specific changes.]**
 
-While using text as data has well-known shortcomings, it allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify patterns that may otherwise be overlooked.
+**[Talk about war compared with economic events and why they don't show up.]**
 
-Add discussions about weakness of the model. The main weakness of this approach is that it does not appropriately propagate uncertainty and future models should improve on this.
+We bring a new dataset of what was said in... **[Add discussion of the weakness of the dataset.]**
 
-Add discussion of the weakness of the dataset.
+Using text as data allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify associations and patterns that may otherwise be overlooked.
+That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies.
+For instance, the use of topic models is problematic because of the need to interpret the topics, which at can sometimes feel like interpreting hieroglyphics.
+This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
+Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
+For instance, selecting stop words for removal and which word to merge because of common co-location has an impact on the topics.
+Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
+One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches.
+As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could take that approach.
 
-Add other discussion that I thought of and now forget.
+**[Add discussions about weakness of the model.]** The main weakness of this approach is that it does not appropriately propagate uncertainty and future research should improve on this.
+
+Additionally, the way that we identify unusual periods could be improved.
+e.g.
+What happens if an event happens while parliament not sitting then it's not clear how whether that is going to be identiifed.
+And if an event happens in the middle of an sitting period, but it's really important and changes the discussion of the rest of the period then again that might not be different because of the average comparison.
+
+**[Add inspo final few paras.]**
 

### 2018-10-19 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -29,13 +29,13 @@ plan(multiprocess)
 #### Create lists of PDFs to read and file names to save text as ####
 # Change the path as required:
 # use_this_path_to_get_pdfs  <- "/Volumes/Backup/hansard_pdfs"
-use_this_path_to_get_pdfs  <- "/Volumes/Backup/senate"
+use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
 # use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
 
 
 # use_this_path_to_save_csv_files  <- "outputs/hansard/temp"
 # use_this_path_to_save_csv_files  <- "/Volumes/Backup/hansard_csv"
-use_this_path_to_save_csv_files  <- "/Volumes/Backup/senate_temp"
+use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
 
 # Get list of Hansard PDF filenames
 file_names <-

### 2018-10-19 scripts/run_2_parse_pdfs/run_2_split_columns.R

@@ -26,7 +26,7 @@ plan(multiprocess)
 # Change the path as required:
 # use_this_path_to_get_csvs  <- "/Volumes/Backup/temp"
 # use_this_path_to_get_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_get_csvs <- "/Volumes/Backup/senate_temp"
+use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
 file_names <-
@@ -50,11 +50,11 @@ file_names_tibble <- file_names_tibble %>%
 file_names <- file_names_tibble$file_name
 rm(file_names_tibble)
 
-#Sometimes it's useful to seperate the input and the output, but otherwise might prefer to overwrite
+#Sometimes it's useful to seperate the input and the output, but otherwise might prefer to overwrite - if you split it make sure to get the one column ones into the new folder
 # use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing"
 # use_this_path_to_save_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
 # use_this_path_to_save_csvs  <- "/Volumes/Backup/temp"
-use_this_path_to_save_csvs  <- "/Volumes/Backup/senate_split"
+use_this_path_to_save_csvs  <- "/Volumes/Hansard/parsed/federal/hor"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
 

### 2018-10-19 scripts/run_2_parse_pdfs/run_3_combine rows.R

@@ -27,7 +27,7 @@ plan(multiprocess)
 # use_this_path_to_get_csvs  <- "/Volumes/Backup/temp"
 # use_this_path_to_get_csvs  <- "outputs/hansard/temp/testing"
 # use_this_path_to_get_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_get_csvs <- "/Volumes/Backup/senate_split"
+use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
@@ -44,7 +44,7 @@ file_names <- file_names %>% sample() # Randomise the order
 # Seems unnecessary, but sometimes useful to separate input and output
 # use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing"
 # use_this_path_to_save_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_save_csvs <- "/Volumes/Backup/senate_combine"
+use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 # use_this_path_to_save_csvs  <- "/Volumes/Backup/temp/testing"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)

### 2018-10-21 outputs/docs/events/paper.Rmd
Update paper

@@
   select(-Party, -`Died in Office`)
+
+key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
 
@@
 
-We summarise the days where parliamentary discussion was significantly different from the rest prevailing in that week in Table X. **[Oh boy. Not sure what to do here.]**
+We summarise the days where parliamentary discussion was significantly different from the rest prevailing in that week in Table \@ref(tab:keyeventsresultstable).
+**[THIS IS A CUT-DOWN LIST FOR DRAFT PURPOSES - REPLACE WITH ONE FROM IMPROVED MODEL.]**
+
+```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
+
+key_events_results %>%
+  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
+  kable_styling(font_size = 12)
+
+```
 
@@
 
-We identify differences between governments and elections based on **[INSERT HOW]**.
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples.
+When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
+One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
+This allows us to identify differences between government and election effects even when there is a one-term government.
 
-Of the 36 different governments over this period, we find that 12 **[UPDATE]** of them are significantly different to the government that preceded them.
-However, two of these -- Page and the first Menzies government -- are likely due to the short length of the Page Government, and should be ignored, leaving only ten **[UPDATE]**.
-The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years.
-Similarly, of the 45 general elections that have been held we find that 12 **[UPDATE]** of them define periods that were significantly different to their immediate predecessor.
-1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
+Of the 36 different governments over this period, we find that 12 **[UPDATE BASED ON NEW MODEL]** of them are significantly different to the government that preceded them.
+However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only ten **[UPDATE BASED ON NEW MODEL]**.
+The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years **[UPDATE BASED ON NEW MODEL]**.
+Similarly, of the 45 general elections that have been held we find that 12 **[UPDATE BASED ON NEW MODEL]** of them define periods that were significantly different to their immediate predecessor.
+1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament **[UPDATE BASED ON NEW MODEL]**.
 
 The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
-The Chifley Government had governed through the end of World War II and difficult economic times that followed.
-It is also the case that there was a large increase in the number of lower house seats at the 1949 election.
-Many new politicians entered parliament and this changed representation may also have been party to do with the changed discussion.
-The sixteen year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
+There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
+Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
+The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
 
-There were six election within the second Menzies Government.
+There were six elections within the second Menzies Government.
 However we do not find that any of those elections was associated with a significant change in the topics discussed.
-In this sense it was a period of consistency, especially when compared with later longer-term governments, such as the Howard Government.
+In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
 
@@
 This is an example where there was a change in government without an election, as the next election only happened in November 1966.
-The Holt Government is significantly different to the Menzies Government.
+We find that the Holt Government is significantly different to the Menzies Government.
+In Figures \@ref(fig:mugovmeziesholt) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
+
+```{r mugovmeziesholt, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-finalmenzies-firstholt.pdf")
+```
+
+The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
+Figure \@ref(fig:muelectionwhitlam) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
+
+```{r muelectionwhitlam, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-whitlamelections.pdf")
+```
+
+The Howard Government is interesting because of the significant differences between elections.
+For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
+Figure \@ref(fig:muelectionhoward) compares the topics that are significant in the different Howard terms.
+
+```{r muelectionhoward, cache = TRUE, echo = FALSE, fig.cap = "Different ", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-howard.pdf")
+```
+
+To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
+However the change in 1998 and 2004 is more unexpected.
+Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
+**[I WONDER IF THERE'S SOME REFERENCE THAT MAKES SIMILAR POINTS TO THIS?]**
 
@@
 
-**[Add some nice graphs for specific changes.]**
+The model also provides estimates of topic prevalence by sitting period.
+This provides nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+
+```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
+knitr::include_graphics("../../figures/war_stack.pdf")
+```
+
+One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
+We estimate sitting-period level-effects (essentially a median for each topic by sitting period).
+This can be thought of as as equivalent to a 'actual' level, and then the points for we estimate are the 'estimated' points.
+The difference defines a measure that can be thought of as essentially a residual and we then identify days where the is at least a 99 per cent difference.
+This approach means that the model generates dates that are interesting without us having to specify interesting dates.
+
+The model identifies 11 September 2001, 12 October 2002.... **[Add more here.]**
 
@@
 e.g.
-What happens if an event happens while parliament not sitting then it's not clear how whether that is going to be identiifed.
+What happens if an event happens while parliament not sitting then it's not clear how whether that is going to be identified.
 And if an event happens in the middle of an sitting period, but it's really important and changes the discussion of the rest of the period then again that might not be different because of the average comparison.

### 2018-10-22 outputs/docs/events/paper.Rmd
Start slides and update paper

@@
 For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
-2) As expected, elections where the party in power also changes, such as Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
+2) As expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
 3) Economic events, such as financial crises, have less significant effects than other events such as terrorism.
@@
 # Data
-## Parliamentary text data
+
 Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
@@
 The topics that we have focused on here are:
-12: war, defence, country, ill, soldiers; 
-13: industry, trade, countries, development, country; 
-17: security, time, world, war, country; 
-22: war, country, matter, production, time; 
-23: defence, time, national, service, vietnam; 
-24: time, budget, tax, billion, million; 
-29: education, schools, students, school, university; 
-30: oil, energy, industry, nuclear, research; 
-32: industry, wheat, wool, growers, farmers; 
-33: per_cent, budget, time, tax, business; 
-35: community, time, health, support, local; and
-39: health, services, funding, care, million.
+12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
 
@@
 We summarise the days where parliamentary discussion was significantly different from the rest prevailing in that week in Table \@ref(tab:keyeventsresultstable).
-**[THIS IS A CUT-DOWN LIST FOR DRAFT PURPOSES - REPLACE WITH ONE FROM IMPROVED MODEL.]**
 
@@
 
-Of the 36 different governments over this period, we find that 12 **[UPDATE BASED ON NEW MODEL]** of them are significantly different to the government that preceded them.
-However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only ten **[UPDATE BASED ON NEW MODEL]**.
-The earliest of these is the second Menzies government starting in 1949, and these ten are concentrated in the second half of our sample, with three of them being in the past twenty years **[UPDATE BASED ON NEW MODEL]**.
-Similarly, of the 45 general elections that have been held we find that 12 **[UPDATE BASED ON NEW MODEL]** of them define periods that were significantly different to their immediate predecessor.
-1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament **[UPDATE BASED ON NEW MODEL]**.
+Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
+However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
+The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
+To a certain extent this is likely tied up with changes due to World War I.
+
+The Second Menzies Government, starting in 1949, is the next government that is significantly different to a precedessor.
+The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
+Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
+1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
 
@@
 We find that the Holt Government is significantly different to the Menzies Government.
-In Figures \@ref(fig:mugovmeziesholt) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
+In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
 
-```{r mugovmeziesholt, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election-finalmenzies-firstholt.pdf")
+```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-differences.pdf")
 ```
@@
 The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
-Figure \@ref(fig:muelectionwhitlam) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
-
-```{r muelectionwhitlam, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election-whitlamelections.pdf")
-```
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
 
@@
 For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
-Figure \@ref(fig:muelectionhoward) compares the topics that are significant in the different Howard terms.
-
-```{r muelectionhoward, cache = TRUE, echo = FALSE, fig.cap = "Different ", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election-howard.pdf")
-```
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
 
@@
 Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
-**[I WONDER IF THERE'S SOME REFERENCE THAT MAKES SIMILAR POINTS TO THIS?]**
-
-**[Talk about the other significant results.]**
 
@@
 
-The model identifies 11 September 2001, 12 October 2002.... **[Add more here.]**
+The model identifies 11 September 2001, 12 October 2002.... **[It doesn't anymore. Not really sure what to do. here.]**
 

### 2018-10-22 outputs/docs/events/slides/slides.Rmd
Start slides and update paper

---
title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
subtitle: 
author:
- Monica Alexander, University of Toronto\newline
- Rohan Alexander, Australian National University
date: 24 October 2018
institute: Presentation at SPIR, ANU.
output: binb::metropolis
fontsize: 12pt
---

```{r,setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

# Summary

## Approach

- Create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. 
- Use a correlated topic model to reduce dimemsionality.
- Analyse the effect of various events using a Bayesian hierarchical Dirichlet model.

## Findings

- Changes in government tend be associated with topic changes even when the party in power does not change;
- Elections that do not result in a change in government are rarely associated with topic changes; 
- Economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; 
- and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.

# Data

## Hansard
- A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
- Hansard records have been used in other counties but not really at scale in Australia.
- Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
- There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament.

## Example PDF page
Add photo.

## PDF parsing
- We use scripts written in R to convert the PDFs into daily text records.
- Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they occur more than twice and can be identified.

The percentage of stop-words in each record is reasonably consistent over time. This suggests that there is no significant difference in the quality of the parsing over time. Details of this check are provided in Appendix \@ref(stopwordsgraph). We use Hansard records on a daily basis in this paper. We pre-process our text before applying a topic model. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand. Then the sentences are de-constructed and each word considered individually.

# Model

# Results

# Future work

## Typography

```
The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.

In Markdown, you can also use _emphasize_ and **bold**.
```

\begin{center}becomes\end{center}

The theme provides sensible defaults to \emph{emphasize} text,
\alert{accent} parts or show \textbf{bold} results.

In Markdown, you can also use _emphasize_ and **bold**.

## Math

\begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
\end{equation*}

## R Figure Example

The following code generates the plot on the next slide (taken from
`help(bxp)` and modified slightly):

```{r pressureCode, eval=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```

## R Figure Example

```{r pressureFig, echo=FALSE}
library(stats)
set.seed(753)
bx.p <- boxplot(split(rt(100, 4),
                      gl(5, 20)), plot=FALSE)
bxp(bx.p, notch = FALSE, boxfill = "lightblue",
    frame = FALSE, outl = TRUE,
    main = "Example from help(bxp)")
```

## R Table Example

A simple `knitr::kable` example:

```{r kableEx}
knitr::kable(mtcars[1:5, 1:8],
             caption="(Parts of) the mtcars dataset")
```

## Resources

### For more information:
- See the [Metropolis repository](https://github.com/matze/mtheme) for more on Metropolis
- See the [RMarkdown repository](https://github.com/rstudio/rmarkdown) for more on RMarkdown
- See the [binb repository](https://github.com/eddelbuettel/binb) for more on binb 
- See the [binb vignettes](https://github.com/eddelbuettel/binb/vignettes) for more examples.

### 2018-10-22 scripts/run_6_make_graphs/make_graphs_of_sigma.R

@@ -3,10 +3,11 @@ library(tidyverse)
 sigma <- read_csv("scripts/from_monica/results/sigma.csv")
 
 sigma %>% 
-  filter(topic %in% c(4:15)) %>% 
+  # filter(topic %in% c(4:15)) %>% 
   ggplot(aes(x = election, y = sigma_median)) +
   geom_point() +
-  facet_wrap(vars(topic), nrow = 4, ncol = 3) +
+  # facet_wrap(vars(topic), nrow = 4, ncol = 3) +
+  facet_wrap(vars(topic)) +
   theme_minimal()
 
 ggsave(

### 2018-10-22 outputs/docs/events/paper.Rmd
MA edits

@@
 We create a dataset based on all sitting days from 1901 through to 2017.
-Although we drop a handful of days for various reasons, we have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
+We have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
 Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case, remove numbers and punctuation, join commonly co-located words, and remove stop words.
 
+We systematically analyse the text using two main statistical techniques.
 To reduce the dimensionality of our dataset we use a topic model that allows correlation between topics.
@@
 In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
-And in the US @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
+And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
 
@@
 $$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
-This is, the main difference between the CTM and LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic Normal distribution.
-That distribution can incorporate a covariance structure across the topics.
+That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
+This distribution can incorporate a covariance structure across the topics.
 The remainder of the steps of the document generating process are identical to LDA.
 
-However, the replacement of the Dirichlet distribution, which is conjugate to the multinomial, with the logistic Normal distribution adds a level of computational complexity to CTM.
+However, the replacement of the Dirichlet distribution with the logistic multivariate Normal distribution adds a level of computational complexity to CTM.
 The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
@@
 The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
-The mean parameters $\mu_{sp}$ are modelled on the log scale as
+The mean parameters $\mu_{s,p}$ are modelled on the log scale as
 
@@
 $$
+One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
+This allows us to identify differences between government and election effects even when there is a one-term government.
 The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
@@
 The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
-We place knot points every five sitting periods as this is the average length of time for a government to sit (**CHECK**).
+We place knot points every five sitting periods as this is the average length of time for a government to sit.
 Non-informative priors are placed on the splines coefficients:
@@
 We run the model in JAGS using the \texttt{rjags} package of @Plummer2018.
-__[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __
+
+<!-- __[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __ -->
 
@@
 If a person was prime minister more than once then these are considered separately.
-If the mean parameter for a government or election period is outside the 95 per cent credible interval, then we consider that period to be different.
 
-We summarise our results in terms of elections Table \@ref(tab:electionsresults) and in terms of governments in Table \@ref(tab:governmentsresults).
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples.
+When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
+
+We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults).
 These tables focus on elections and governments that were different to the ones that preceded them.
@@
 In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
+In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
+The error bars represent 95 per cent Bayesian credible intervals.
+The topics that we have focused on here are:
+12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
 
-```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics", out.width = '100%'}
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics.", out.width = '100%'}
 knitr::include_graphics("../../figures/mu_gov.pdf")
@@
 
-The topics that we have focused on here are:
-12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
-
 Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
@@
 
-We summarise the days where parliamentary discussion was significantly different from the rest prevailing in that week in Table \@ref(tab:keyeventsresultstable).
+We estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
+The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
+This approach means that the model generates dates that are interesting without us having to specify interesting dates.
+
+More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
 
@@
 
-Finally, we summarise our results over time by looking at the standard deviation of sitting period estimates, around the mean election effect (Figure \@ref(fig:sigmaelection))
+Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
+In general, the estimates of standard deviation are increasing over time, suggesting that discussed topics are more variable in more recent election periods compared to historical periods.
 
@@
 # Discussion
-In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
-We download and parse PDFs of Hansard to create a new dataset of text.
-We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
-In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
-We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
-
-We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples.
-When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
-One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
-This allows us to identify differences between government and election effects even when there is a one-term government.
-
 Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
@@
 One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
-We estimate sitting-period level-effects (essentially a median for each topic by sitting period).
-This can be thought of as as equivalent to a 'actual' level, and then the points for we estimate are the 'estimated' points.
-The difference defines a measure that can be thought of as essentially a residual and we then identify days where the is at least a 99 per cent difference.
-This approach means that the model generates dates that are interesting without us having to specify interesting dates.
 
@@
 **[Talk about war compared with economic events and why they don't show up.]**
+
+# Conclusion
+In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
+We download and parse PDFs of Hansard to create a new dataset of text.
+We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
+In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
+We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
 
@@
 
-**[Add discussions about weakness of the model.]** The main weakness of this approach is that it does not appropriately propagate uncertainty and future research should improve on this.
+In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model.
+Firstly, we are assuming that the effect of a particular government is constant across the whole period.
+In addition, we assume that the effect of elections is monotonically decreasing across days since election.
+In future work we will investigate different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.
 
-Additionally, the way that we identify unusual periods could be improved.
-e.g.
-What happens if an event happens while parliament not sitting then it's not clear how whether that is going to be identified.
-And if an event happens in the middle of an sitting period, but it's really important and changes the discussion of the rest of the period then again that might not be different because of the average comparison.
+The way that we identify unusual periods could also be improved.
+We defined sitting periods in a constant fashion across the whole dataset time frame, but the nature of how long parliaments sit for has most likely changed.
+In addition, more work needs to be done on how to identify outlying events.
+For example, it is not clear if an important event that occurs outside a sitting period would be identified.
+And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such specific days are not identified as significantly outlying.
+
+Finally, the current modeling and analysis set-up is a two stage process: we take the output of a topic model, and use this as the input to a second model.
+However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
+Future methodological work will focus on how to combine these two modeling steps by extending the STM approach into a more flexible framework.
 

### 2018-10-22 outputs/docs/events/paper.Rmd
more results changes

@@
 # Results
+
+Firstly, we describe the results of the CTM approach, which defined 40 unique topics over the period 1901-2017.
+We then describe the results of the Bayesian analysis model, which identified governments, elections and other events that were associated with a change in the topics discussed.
+
+## Topic modeling
+
+We applied the CTM approach discussed in Section 3.2 on the processed Hansard text database outlined in Section 2.
+The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
+
+The remainder of the results refer to a topic model which had a total of 40 distinct topics define. **ROHAN PLEASE ADD WHY 40**
+
+Table \@ref(tab:topwords) lists the top five words associated with each of the forty topics.
+The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
+Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.
+
+```{r topwords, echo = FALSE, results = 'asis'}
+
+top_words %>% 
+  kable(booktabs = T, caption = "Top words associated with each topic") %>%
+  kable_styling(font_size = 10)
+
+```
+
+## Analysis model
+
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
+As discussion in Section 3.3, the next stage of the modeling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+
+There are several outputs of interest from this modeling stage.
+For example, the model provides estimates of topic prevalence by each sitting period.
+This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
+For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+
+```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
+knitr::include_graphics("../../figures/war_stack.pdf")
+```
+
+One of the main goals of the analysis model is to see which political events are associated with changes in the prevalance of topics over time.
 Political events are those related to a change of government or an election.
@@
 
-We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples.
+As detailed in Section 3.3, the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.
 When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
@@
 Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
-
-The model also provides estimates of topic prevalence by sitting period.
-This provides nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
-
-```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
-knitr::include_graphics("../../figures/war_stack.pdf")
-```
 

### 2018-10-23 outputs/docs/events/paper.Rmd

@@
 elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
-  filter(Significant %in% c("Yes", "No"))
+  # filter(Significant %in% c("Yes", "No"))
+  filter(Significant %in% c("Yes"))
 
 governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
-  filter(Significant %in% c("Yes", "No")) %>% 
+  filter(Significant %in% c("Yes")) %>% 
+  # filter(Significant %in% c("Yes", "No")) %>% 
   select(-Party, -`Died in Office`)
@@
 Additionally, XML records are available in some cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament.
+There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
 
-## Topic modeling
+## Topic modelling
 
@@
 
-The remainder of the results refer to a topic model which had a total of 40 distinct topics define. **ROHAN PLEASE ADD WHY 40**
+The remainder of the results refer to a topic model that had 40 distinct topics defined.
+The choice of 40 topics was made as a trade-off between semantic coherence and exclusivity with 40 topics performing better on both measures than 20.
+Measures such as residuals and held-out likelihood suggest a larger number of topics would be more appropriate.
+See Appendix \@ref(selecttopicnumber) for these diagnostics.
 
@@
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussion in Section 3.3, the next stage of the modeling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+As discussion in Section 3.3, the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
 
-There are several outputs of interest from this modeling stage.
+There are several outputs of interest from this modelling stage.
 For example, the model provides estimates of topic prevalence by each sitting period.
@@
 
-One of the main goals of the analysis model is to see which political events are associated with changes in the prevalance of topics over time.
+One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
 Political events are those related to a change of government or an election.
@@
   kable(booktabs = T, caption = "Significant elections, and neighours") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
   kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
   kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 10)
 
@@
 
-Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
+<!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
 In general, the estimates of standard deviation are increasing over time, suggesting that discussed topics are more variable in more recent election periods compared to historical periods.
+-->
 
-```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
-knitr::include_graphics("../../figures/sigma.pdf")
-```
+<!-- ```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'} -->
+<!-- knitr::include_graphics("../../figures/sigma.pdf") -->
+<!-- ``` -->
 
@@
 
-The Second Menzies Government, starting in 1949, is the next government that is significantly different to a precedessor.
+The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
 The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
@@
 One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
-
-The model identifies 11 September 2001, 12 October 2002.... **[It doesn't anymore. Not really sure what to do. here.]**
-
-**[Talk about war compared with economic events and why they don't show up.]**
+The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
+For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
+It also appropriately identifies some of other key events that we were interested in.
+However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+Further work is needed to improve this approach.
+For instance, our approach may not be appropriately considering step-changes.
 
@@
 
-We bring a new dataset of what was said in... **[Add discussion of the weakness of the dataset.]**
+By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia.
+However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
 
@@
 
-Finally, the current modeling and analysis set-up is a two stage process: we take the output of a topic model, and use this as the input to a second model.
+Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model.
 However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
-Future methodological work will focus on how to combine these two modeling steps by extending the STM approach into a more flexible framework.
+Future methodological work will focus on how to combine these two modelling steps by extending the STM approach into a more flexible framework.
 
-**[Add inspo final few paras.]**
+Watching our politicians at work can sometimes be a little disheartening.
+It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there.
+Nonetheless, our work suggests that reasonable debate of important topics does occur in parliament.
+It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
+However, we do find that since the 1980s differences between government and election periods are greater than they used to be.
+It is, of course, reasonable that a government should act on the mandate they receive, but the longer-term nature of important policymaking means that progress may be held back if the media and political cycles become too focused on short-term events.
 
@@
 
-Figure \@ref(fig:asdf)
-
-```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '90%'}
 knitr::include_graphics("../../figures/example_hansard_page.png")
@@
 
+\newpage
+
 ## Known Hansard issues {#knownhansardissues}
-
-The NSW Legislative Council was established earlier than 1856, however the earlier Hansard records have not been through an independent OCR process and were not used in this paper.
-However, the Google Tesseract OCR engine as implemented by @Ooms2018tesseract provided useful data and these could be used in the future.
-
-Which PDFs are missing or have no content, etc.
+Comparing the sitting days to the dates that we have suggests some issues with the dataset (Table \@ref(tab:missingdays)).)
 
@@
   kable(booktabs = T, caption = "Missing days") %>%
-  kable_styling(font_size = 12)
+  kable_styling(font_size = 12) %>% 
+  kableExtra::kable_styling(latex_options = "hold_position")
 
@@
 
-Notes: Positive means I am missing some, Negative means I have too many.
+Positive means we are missing some, negative means we have too many.
 Source: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear
 
+\newpage
+
 ## Example Hansard PDf to text record workflow {#hansardworkflow}
-Example of the workflow from PDF to text
+Here we provide psuedo-code for the workflow from PDF to text.
+The scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
+The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues and the \texttt{tidytext} R package of @SilgeRobinson2016 and @Benoit2018 for compounding multiword expressions.
 
-These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
+**[TBD].**
 
-The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
-
-The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.
-
-In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.
-
-And @Benoit2018 for compounding multiword expressions.
+\newpage
 
 ## Stopwords over time {#stopwordsgraph}
-Insert graph of stop words over time.
+**[TBD].** Insert graph of stop words over time.
 
@@
 
+\newpage
+
 ## Selection of number of topics {#selecttopicnumber}
@@
 
-## Robustness of results
-**[IS THIS BEING USED?]**
-Here we change the number of sitting days considered either side of an event.
+<!-- \newpage -->
+
+<!-- ## Robustness of results -->
+<!-- **[IS THIS BEING USED?]** -->
+<!-- Here we change the number of sitting days considered either side of an event.
 The results in the main section of the paper are for the nearest ten days either side of an event.
 Here are show that the results are essentially the same if the nearest one, two, five, and twenty days either side of an event.
+-->
 
@@
 
-# Analysis model {#modeldetailsandsimulation}
+<!-- # Analysis model {#modeldetailsandsimulation} -->
 
-Here we illustrate the validity of our analysis model using simulated data.
+<!-- Here we illustrate the validity of our analysis model using simulated data. -->
 
-\newpage
+<!-- \newpage -->
 

### 2018-10-23 outputs/docs/events/slides/slides.Rmd

@@
 ## Example PDF page
-Add photo.
+
+```{r pressureFig, echo=FALSE, out.width = '50%', fig.align="center"}
+
+knitr::include_graphics("../../../figures/example_hansard_page.png")
+
+```
 
@@
 - We use scripts written in R to convert the PDFs into daily text records.
-- Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
-An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are corrected when they occur more than twice and can be identified.
-
-The percentage of stop-words in each record is reasonably consistent over time.
-This suggests that there is no significant difference in the quality of the parsing over time.
-Details of this check are provided in Appendix \@ref(stopwordsgraph).
-We use Hansard records on a daily basis in this paper.
-We pre-process our text before applying a topic model.
-The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
+- Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records e.g.
+'the' is often parsed as 'thc'.
+- We: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
 Then the sentences are de-constructed and each word considered individually.
@@
 
+## Latent Dirichlet Allocation - Overview
+
+- The key assumption behind LDA is that each text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics.
+- A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. 
+- The topics are not specified *ex ante*; they are an outcome of the method - this is an unsupervised machine learning method.
+
+## Latent Dirichlet Allocation - Example
+
+Add figure
+Statistically, LDA considers each document as having been generated by some probability distribution over topics.
+Similarly, each topic is considered a probability distribution over terms.
+To choose the terms used in each document, terms are picked from each topic in the appropriate proportion.
+
+## Latent Dirichlet Allocation - Data generation process
+
+1.
+There are $1, 2, \dots, k, \dots, K$ topics and the vocabulary consists of $1, 2, \dots, V$ terms.
+For each topic, decide the terms that the topic uses by randomly drawing distributions over the terms.
+The distribution over the terms for the $k$th topic is $\beta_k$.
+Typically a topic would be a small number of terms and so the Dirichlet distribution with hyper-parameter $\boldsymbol{\eta}$ is used: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.
+In practice, a symmetric Dirichlet distribution is usually used, where all elements of $\boldsymbol{\eta}$ are equal.
+2.
+Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $1, 2, \dots, d, \dots, D$ documents.
+The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
+Again, the Dirichlet distribution with the hyper-parameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
+Again, strictly $\boldsymbol{\alpha}$ is vector of length $K$ of hyper-parameters and they are usually equal.
+3. If there are $1, 2, \dots, n, \dots, N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
+    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$.
+    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.
+
+Given this set-up, the joint distribution for the variables is:
+$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}) = \prod^{K}_{i=1}p(\beta_i) \prod^{D}_{d=1}p(\theta_d) \left(\prod^N_{n=1}p(z_{d,n}|\theta_d)p\left(w_{d,n}|\beta_{1:K},z_{d,n}\right) \right).$$
+
+Based on this document generation process the analysis problem, discussed next, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
+This is intractable directly, but can be approximated.
+
+## Latent Dirichlet Allocation - Data generation process
+- After the documents are created, they are all that we have to analyse.
+The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'.
+We do not know the topics of each document, nor how terms defined the topics.
+In a sense we are trying to reverse the document generation process -- we have the terms and we would like to discover the topics.
+
+If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics.
+The outcomes of the LDA process are probability distributions and these define the topics.
+Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
+That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document:
+$$p(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N} | w_{1:D, 1:N}) = \frac{p\left(\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}, w_{1:D, 1:N}\right)}{p(w_{1:D, 1:N})}.$$
+
+The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
+If there is a strong reason for a particular number, then this can be used.
+Otherwise, one way to choose an appropriate number is to use cross validation.
+
+One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter.
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+This is the Correlated Topic Model, described in the next section.
+
+## Correlated Topic Model
+Slight modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
+Essentially it swaps the Dirichlet for the Logistic Multivariate Normal. This sounds easy, but it's hard to implement.
+
+The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information. 
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+Again, sounds easy, but hard to implement and they implement a very nice algorithm.
+
+## Correlated Topic Model - Example output
+
+```{r exampletopics, cache = TRUE, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/topics_example.pdf")
+```
+
+## Why not STM?
+- No way to specify more complicated auto-correlated functional forms of the effects of events over time. 
+- There is no way to implement partial pooling across groups of similar documents. 
+- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+
+## Analysis model
+Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in governments and elections.
+This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
+
+Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
+Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM.
+We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
+
+The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
+Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
+
+$$
+\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
+$$
+where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
+This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
+
+The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The mean parameters $\mu_{sp}$ are modelled on the log scale as
+
+$$
+\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
+$$
+where:
+
+- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
+- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
+- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
+
+The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
+$$
+\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)
+$$
+
+The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
+In particular, we model this as an AR(1) in $d$:
+
+$$
+\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
+$$
+The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
+
+$$
+\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100)
+$$
+$$
+\rho_{e[s],p} \sim \mbox{Uniform}(0,1)
+$$
+We model the underlying time trend in topics using splines regression.
+The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
+The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
+We place knot points every five sitting periods as this is the average length of time for a government to sit (**CHECK**).
+Non-informative priors are placed on the splines coefficients:
+$$
+\beta_{p,k} \sim \mbox{Normal}(0, 100)
+$$
+
+Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
+This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+In addition, this set up also partially pools effects across sitting periods.
+The $\delta_{s,p}$ values are modelled as:
+
+$$
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
+$$
+
+The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
+If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
+Non-informative priors are placed on the variance parameters:
+
+$$
+\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
+$$
+
+We run the model in JAGS using the \texttt{rjags} package.
+
 # Results
@@
 # Future work
+
+## Future work
+- Group identity: which is more important?
+-
+
+## Questions?
+- rohan.alexander@anu.edu.au
+- @RohanAlexander
+- rohanalexander.com
 
@@
 
-## R Figure Example
-
-```{r pressureFig, echo=FALSE}
-library(stats)
-set.seed(753)
-bx.p <- boxplot(split(rt(100, 4),
-                      gl(5, 20)), plot=FALSE)
-bxp(bx.p, notch = FALSE, boxfill = "lightblue",
-    frame = FALSE, outl = TRUE,
-    main = "Example from help(bxp)")
-```
-
 ## R Table Example

### 2018-10-23 outputs/docs/events/paper.Rmd
Update slides

@@
 However, we do find that since the 1980s differences between government and election periods are greater than they used to be.
-It is, of course, reasonable that a government should act on the mandate they receive, but the longer-term nature of important policymaking means that progress may be held back if the media and political cycles become too focused on short-term events.
+It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.
 

### 2018-10-23 outputs/docs/events/slides/slides.Rmd
Update slides

--- 2018-10-22 outputs/docs/events/slides/slides.Rmd
@@
 date: 24 October 2018
-institute: Presentation at SPIR, ANU.
+institute: Presentation at the School of Politics and International Relations, Australian National University, Canberra, Australia.
 output: binb::metropolis
+# output: ioslides_presentation
 fontsize: 12pt
@@
 
-```{r,setup, include=FALSE}
+```{r, setup, include=FALSE}
 knitr::opts_chunk$set(cache=TRUE)
+
+library(here)
+library(kableExtra)
+library(knitr)
+library(tidyverse)
+
+elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
+governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
+keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
+significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
+missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
+hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
+
+elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
+  # filter(Significant %in% c("Yes", "No"))
+  filter(Significant %in% c("Yes"))
+
+governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
+  filter(Significant %in% c("Yes")) %>% 
+  # filter(Significant %in% c("Yes", "No")) %>% 
+  select(-Party, -`Died in Office`)
+
+key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
+
 ```
@@
 
+<div class="notes">
+Test
+</div>
+
 ## Findings
 
-- Changes in government tend be associated with topic changes even when the party in power does not change;
-- Elections that do not result in a change in government are rarely associated with topic changes; 
-- Economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; 
-- and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
+- Changes in government tend be associated with topic changes even when the party in power does not change.
+- Elections that do not result in a change in government are rarely associated with topic changes.
+- Economic events, such as financial crises, have less significant effects than other events such as terrorist attacks.
+- The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
 
@@
 - A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
-- Hansard records have been used in other counties but not really at scale in Australia.
+- Hansard records have been used in other counties but not really at scale in Australia (although others are also starting to use them).
 - Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
-- There are 14,551 days worth of publicly available Hansard records across both chambers of the Australian Federal Parliament.
+- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
 
 ## Example PDF page
-Add photo.
+
+```{r pressureFig, echo=FALSE, out.width = '50%', fig.align="center"}
+
+knitr::include_graphics("../../../figures/example_hansard_page.png")
+
+```
 
@@
 - We use scripts written in R to convert the PDFs into daily text records.
-- Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
-An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are corrected when they occur more than twice and can be identified.
-
-The percentage of stop-words in each record is reasonably consistent over time.
-This suggests that there is no significant difference in the quality of the parsing over time.
-Details of this check are provided in Appendix \@ref(stopwordsgraph).
-We use Hansard records on a daily basis in this paper.
-We pre-process our text before applying a topic model.
-The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
+- Some error is introduced at this stage:
+    - because many of the records are in a two-column format that need to be separated; and 
+    - the PDF parsing is not always accurate especially for older records e.g. 'the' is often parsed as 'thc'.
+- We remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
 Then the sentences are de-constructed and each word considered individually.
 
-# Model
+# Topic Model
+
+## Latent Dirichlet Allocation - Overview
+
+- Each document is assumed to be from a speaker who decides the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. 
+- A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. 
+- The topics are not specified *ex ante*; they are an outcome of the method -- this is an unsupervised machine learning method.
+
+## Latent Dirichlet Allocation - Topic distribution for documents
+
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE}
+
+tibble(
+  Topics = rep(c("1", "2", "3", "4", "5"), 2),
+  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
+  Document = c(rep("Document 1", 5), rep("Document 2", 5))
+  ) %>%
+  ggplot(aes(Topics, Probability, colour = Document)) +
+  geom_point(size = 4) +
+  theme_classic() +
+  coord_flip()  +
+  scale_colour_viridis_d() +
+      theme(text = element_text(size = 20)) +
+    theme(
+    panel.background = element_rect(fill = "transparent") # bg of the panel
+    , plot.background = element_rect(fill = "transparent", color = NA) # bg of the plot
+    , panel.grid.major = element_blank() # get rid of major grid
+    , panel.grid.minor = element_blank() # get rid of minor grid
+    , legend.background = element_rect(fill = "transparent") # get rid of legend bg
+    , legend.box.background = element_rect(fill = "transparent") # get rid of legend panel bg
+  )
+
+```
+
+<!-- Statistically, LDA considers each document as having been generated by some probability distribution over topics.
+Similarly, each topic is considered a probability distribution over terms.
+To choose the terms used in each document, terms are picked from each topic in the appropriate proportion.
+-->
+
+## Latent Dirichlet Allocation - Term distribution over topics
+
+```{r topicsoverterms, cache = TRUE, echo=FALSE}
+
+tibble(
+  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
+  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
+  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
+  ) %>%
+  ggplot(aes(Terms, Probability, colour = Topics)) +
+  geom_point(size = 4) +
+  theme_classic() +
+  coord_flip() +
+  scale_colour_viridis_d() +
+    theme(text = element_text(size = 20)) +
+  theme(
+    panel.background = element_rect(fill = "transparent") # bg of the panel
+    , plot.background = element_rect(fill = "transparent", color = NA) # bg of the plot
+    , panel.grid.major = element_blank() # get rid of major grid
+    , panel.grid.minor = element_blank() # get rid of minor grid
+    , legend.background = element_rect(fill = "transparent") # get rid of legend bg
+    , legend.box.background = element_rect(fill = "transparent") # get rid of legend panel bg
+  )
+
+```
+
+## Latent Dirichlet Allocation - Data generation process
+
+1.
+There are $K$ topics and the vocabulary consists of $V$ terms.
+For each topic, decide the terms by randomly drawing distributions over the terms.
+The distribution over the terms for the $k$th topic is $\beta_k$.
+Use the Dirichlet distribution with hyper-parameter $\boldsymbol{\eta}$: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+
+2.
+Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $D$ documents.
+The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
+Again, the Dirichlet distribution with the hyper-parameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+3. If there are $N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
+    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$.
+    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+Given this set-up, we have a joint distribution for the variables and the analysis problem, discussed next, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
+This is intractable directly, but can be approximated.
+
+## Latent Dirichlet Allocation - Analysis problem
+- After the documents are created, they are all that we have to analyse. The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'. 
+- We do not know the topics of each document, nor how terms defined the topics. In a sense we are trying to reverse the document generation process.
+- If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics.
+
+## Latent Dirichlet Allocation - Analysis problem (cont.)
+- The outcomes of the LDA process are probability distributions and these define the topics.
+Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
+- That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document.
+- The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
+
+<!-- If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use cross validation. -->
+
+<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter.
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+This is the Correlated Topic Model, described in the next section.
+-->
+
+## Correlated Topic Model
+Modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
+Essentially it swaps the Dirichlet for the Logistic Multivariate Normal. This sounds easy, but it's hard to implement.
+
+## Correlated Topic Model - Example output
+
+```{r exampletopics, cache = TRUE, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/topics_example-slides.pdf")
+```
+
+## Structural Topic Model
+The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information. 
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+Again, sounds easy, but hard to implement, and they have a very nice solutions algorithm.
+
+## Why not use STM?
+STM is great, but it is specific to various contexts and ours is slightly outside them:
+
+- No way to specify more complicated auto-correlated functional forms of the effects of events over time. 
+- There is no way to implement partial pooling across groups of similar documents. 
+- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+In an ideal world we could modify the STM code, but instead we build a similar, but different, analysis model.
+
+<!-- Also you don't really understand something until you code it yourself. -->
+
+# Analysis model
+
+## Analysis model - Overview
+- We use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework.
+- This relates the proportions of each topic to underlying time trends, changes in governments and elections. 
+- This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
+
+## Analysis model - Set-up
+- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM. 
+- We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
+
+## Analysis model - Daily distribution
+The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
+Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
+
+$$
+\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
+$$
+
+<!-- where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
+This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
+-->
+
+The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+
+## Analysis model - Mean parameters
+
+The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
+$$
+\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
+$$
+
+- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
+- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
+- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
+
+## Analysis model - Government effects
+
+The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution.
+We place uninformative priors on each of these parameters: $\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)$
+
+## Analysis model - Election effects
+
+The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
+In particular, we model this as an AR(1) in $d$:
+$$
+\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
+$$
+
+We use non-informative priors.
+
+<!-- One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
+This allows us to identify differences between government and election effects even when there is a one-term government.
+We use non-informative priors.
+-->
+
+## Analysis model - Time effects
+
+We model the underlying time trend in topics using splines regression.
+The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
+The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
+We place knot points every five sitting periods as this is the average length of time for a government to sit.
+
+<!-- Non-informative priors are placed on the splines coefficients: -->
+<!-- $$ -->
+<!-- \beta_{p,k} \sim \mbox{Normal}(0, 100) -->
+<!-- $$ -->
+
+## Analysis model - Sitting period effects
+
+<!-- This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+In addition, this set up also partially pools effects across sitting periods.
+-->
+
+The sitting period-specific random effect $\delta_{s,p}$ allows the topic distributions in some sitting periods to be different than expected based on government and election effects:
+$$
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
+$$
+
+The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
+If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
+Non-informative priors are placed on the variance parameters:
+$$
+\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
+$$
+
+We run the model in JAGS using the \texttt{rjags} package.
 
@@
 
+## Topic modelling
+
+<!-- We applied the CTM approach discussed in Section 3.2 on the processed Hansard text database outlined in Section 2.
+The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
+-->
+
+<!-- The remainder of the results refer to a topic model that had 40 distinct topics defined.
+The choice of 40 topics was made as a trade-off between semantic coherence and exclusivity with 40 topics performing better on both measures than 20.
+Measures such as residuals and held-out likelihood suggest a larger number of topics would be more appropriate.
+-->
+
+<!-- Table \@ref(tab:topwords) lists the top five words associated with each of the forty topics.
+The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
+Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.
+-->
+
+We choose 40 topics because it is the minimum needed to have meaningful results.
+
+```{r topwords, echo = FALSE, results = 'asis'}
+# library(tidyverse)
+# # top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
+# library(kableExtra)
+
+top_words %>%
+  filter(topic %in% c(2, 4, 6, 8, 10, 12)) %>% 
+  kable()
+
+```
+
+## Analysis model - Estimates by sitting period
+
+<!-- There are several outputs of interest from this modelling stage.
+For example, the model provides estimates of topic prevalence by each sitting period.
+This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
+For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+-->
+
+```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/war_stack.pdf")
+```
+
+<!-- One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
+Political events are those related to a change of government or an election.
+As Australia has a parliamentary system, it is possible for the government to change without an election.
+We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
+If a person was prime minister more than once then these are considered separately.
+-->
+
+<!-- As detailed in Section 3.3, the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.
+When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
+-->
+
+<!-- We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults).
+These tables focus on elections and governments that were different to the ones that preceded them.
+-->
+
+## Analysis model - Significantly different elections
+
+```{r electionsresults, echo = FALSE, results = 'asis'}
+
+elections_results %>%
+  select(-Significant) %>% 
+  kable() %>%
+  kable_styling(font_size = 10)
+
+```
+
+## Analysis model - Significantly different governments
+
+```{r governmentsresults, echo = FALSE, results = 'asis'}
+
+governments_results %>%
+  select(-Significant) %>% 
+  kable() %>%
+  kable_styling(font_size = 10)
+
+```
+
+## Analysis model - All governments
+
+<!-- In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
+In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
+The error bars represent 95 per cent Bayesian credible intervals.
+The topics that we have focused on here are: -->
+<!-- 12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
+-->
+
+```{r mugov, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/mu_gov.pdf")
+```
+
+## Analysis model - All elections
+
+```{r muelection, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/mu_election.pdf")
+```
+
+## Analysis model - Events
+<!-- Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
+The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
+Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.
+-->
+
+<!-- We estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
+The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
+This approach means that the model generates dates that are interesting without us having to specify interesting dates.
+-->
+
+<!-- More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
+-->
+
+```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
+
+key_events_results %>%
+  kable(caption = "Days that were significantly different to other days in their sitting period") %>%
+  kable_styling(font_size = 10)
+
+```
+
+<!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
+In general, the estimates of standard deviation are increasing over time, suggesting that discussed topics are more variable in more recent election periods compared to historical periods.
+-->
+
+<!-- ```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'} -->
+<!-- knitr::include_graphics("../../figures/sigma.pdf") -->
+<!-- ``` -->
+
+## Menzies-Holt
+
+<!-- Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
+However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
+The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
+To a certain extent this is likely tied up with changes due to World War I.
+-->
+
+<!-- The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
+The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
+Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
+1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
+-->
+
+<!-- The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
+The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
+There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
+Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
+The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+-->
+
+<!-- There were six elections within the second Menzies Government.
+However we do not find that any of those elections was associated with a significant change in the topics discussed.
+In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
+-->
+
+<!-- The Menzies Government was succeeded by the Holt Government in January 1966.
+This is an example where there was a change in government without an election, as the next election only happened in November 1966.
+We find that the Holt Government is significantly different to the Menzies Government.
+In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
+-->
+
+```{r muelectionmenziesholt, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/mu_election-differences-menziesholt-slides.pdf")
+```
+
+## Whitlam stability
+
+```{r muelectionwhitlam, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/mu_election-differences-whitlam-slides.pdf")
+```
+
+<!-- The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
+-->
+
+## Howard instability
+
+```{r muelectionhoward, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/mu_election-differences-howard-slides.pdf")
+```
+
+<!-- The Howard Government is interesting because of the significant differences between elections.
+For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
+-->
+
+<!-- To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
+However the change in 1998 and 2004 is more unexpected.
+Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
+-->
+
+<!-- One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
+The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
+For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
+It also appropriately identifies some of other key events that we were interested in.
+However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+Further work is needed to improve this approach.
+For instance, our approach may not be appropriately considering step-changes.
+-->
+
+# Issues/tradeoffs
+
+## Issues/tradeoffs
+- Even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
+- Topic interpretation is difficult. 
+- Inputs have to be fine-tuned.
+- Assuming government effects are is constant across the whole period. 
+- Assuming the effect of elections is monotonically decreasing across days since election. 
+- Identification of unusual periods could also be improved. 
+- Propogation of uncertainty is inappropriate.
+
 # Future work
 
-## Typography
+## Future work
+- Group identity: which is more important?
+-
 
-```
-The theme provides sensible defaults to
-\emph{emphasize} text, \alert{accent} parts
-or show \textbf{bold} results.
-
-In Markdown, you can also use _emphasize_ and **bold**.
-```
-
-\begin{center}becomes\end{center}
-
-The theme provides sensible defaults to \emph{emphasize} text,
-\alert{accent} parts or show \textbf{bold} results.
-
-In Markdown, you can also use _emphasize_ and **bold**.
-
-## Math
-
-\begin{equation*}
-    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
-\end{equation*}
-
-## R Figure Example
-
-The following code generates the plot on the next slide (taken from
-`help(bxp)` and modified slightly):
-
-```{r pressureCode, eval=FALSE}
-library(stats)
-set.seed(753)
-bx.p <- boxplot(split(rt(100, 4),
-                      gl(5, 20)), plot=FALSE)
-bxp(bx.p, notch = FALSE, boxfill = "lightblue",
-    frame = FALSE, outl = TRUE,
-    main = "Example from help(bxp)")
-```
-
-## R Figure Example
-
-```{r pressureFig, echo=FALSE}
-library(stats)
-set.seed(753)
-bx.p <- boxplot(split(rt(100, 4),
-                      gl(5, 20)), plot=FALSE)
-bxp(bx.p, notch = FALSE, boxfill = "lightblue",
-    frame = FALSE, outl = TRUE,
-    main = "Example from help(bxp)")
-```
-
-## R Table Example
-
-A simple `knitr::kable` example:
-
-```{r kableEx}
-knitr::kable(mtcars[1:5, 1:8],
-             caption="(Parts of) the mtcars dataset")
-```
-
-## Resources
-
-### For more information:
-- See the [Metropolis repository](https://github.com/matze/mtheme) for more on Metropolis
-- See the [RMarkdown repository](https://github.com/rstudio/rmarkdown) for more on RMarkdown
-- See the [binb repository](https://github.com/eddelbuettel/binb) for more on binb 
-- See the [binb vignettes](https://github.com/eddelbuettel/binb/vignettes) for more examples.
+## Questions?
+- rohan.alexander@anu.edu.au
+- @RohanAlexander
+- rohanalexander.com

### 2018-10-23 outputs/docs/events/slides_xan/test.Rmd
Update slides

--- 2018-10-23 outputs/docs/events/slides/slides.Rmd
@@
 ---
-title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
-subtitle: 
-author:
-- Monica Alexander, University of Toronto\newline
-- Rohan Alexander, Australian National University
-date: 24 October 2018
-institute: Presentation at the School of Politics and International Relations, Australian National University, Canberra, Australia.
-output: binb::metropolis
-# output: ioslides_presentation
-fontsize: 12pt
+title: "Presentation Ninja"
+subtitle: "⚔<br/>with xaringan"
+author: "Yihui Xie"
+date: "2016/12/12 (updated: `r Sys.Date()`)"
+output:
+  xaringan::moon_reader:
+    lib_dir: libs
+    nature:
+      highlightStyle: github
+      highlightLines: true
+      countIncrementalSlides: false
 ---
 
-```{r, setup, include=FALSE}
-knitr::opts_chunk$set(cache=TRUE)
+```{r setup, include=FALSE}
+options(htmltools.dir.version = FALSE)
 
@@
 ```
+
+background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
+
+???
+
+Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)
+
+---
+class: center, middle
+
+# xaringan
+
+### /ʃæ.'riŋ.ɡæn/
+
+---
+class: inverse, center, middle
+
+# Get Started
+
+---
+
+# Hello World
+
+Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):
+
+```{r eval=FALSE, tidy=FALSE}
+devtools::install_github("yihui/xaringan")
+```
+
+--
+
+You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.
+
+- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>
+
+--
+
+- Click the `Knit` button to compile it;
+
+--
+
+- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.
+
+.footnote[
+[1] 中文用户请看[这份教程](http://slides.yihui.name/xaringan/zh-CN.html)
+
+[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
+]
+
+---
+background-image: url(`r xaringan:::karl`)
+background-position: 50% 50%
+class: center, bottom, inverse
+
+# You only live once!
+
+---
+
+# Hello Ninja
+
+As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:
+
+1. The [remark.js](https://remarkjs.com) library;
+
+1. The **xaringan** package;
+
+Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**.
+The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).
+
+---
+
+# remark.js
+
+You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to
+
+- create a new slide (Markdown syntax<sup>*</sup> and slide properties);
+
+- format a slide (e.g. text alignment);
+
+- configure the slideshow;
+
+- and use the presentation (keyboard shortcuts).
+
+It is important to be familiar with remark.js before you can understand the options in **xaringan**.
+
+.footnote[[*] It is different with Pandoc's Markdown!
+It is limited but should be enough for presentation purposes.
+Come on...
+You do not need a slide for the Table of Contents!
+Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]
+
+---
+background-image: url(`r xaringan:::karl`)
+background-size: cover
+class: center, bottom, inverse
+
+# I was so happy to have discovered remark.js!
+
+---
+class: inverse, middle, center
+
+# Using xaringan
+
+---
+
+# xaringan
+
+Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.
+
+```yaml
+---
+title: "A Cool Presentation"
+output:
+  xaringan::moon_reader
+    yolo: true
+    nature:
+      autoplay: 30000
+---
+```
+
+See the help page `?xaringan::moon_reader` for all possible options that you can use.
+
+---
+
+# remark.js vs xaringan
+
+Some differences between using remark.js (left) and using **xaringan** (right):
+
+.pull-left[
+1. Start with a boilerplate HTML file;
+
+1. Plain Markdown;
+
+1. Write JavaScript to autoplay slides;
+
+1. Manually configure MathJax;
+
+1. Highlight code with `*`;
+
+1. Edit Markdown source and refresh browser to see updated slides;
+]
+
+.pull-right[
+1. Start with an R Markdown document;
+
+1. R Markdown (can embed R/other code chunks);
+
+1. Provide an option `autoplay`;
+
+1. MathJax just works;<sup>*</sup>
+
+1. Highlight code with `{{}}`;
+
+1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
+]
+
+.footnote[[*] Not really. See next page.]
+
+---
+
+# Math Expressions
+
+You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:
+
+```
+$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
+```
+
+$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
+
+Limitations:
+
+1.
+The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;
+
+1. There should not be spaces after the opening `$` or before the closing `$`.
+
+1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).
+
+---
+
+# R Code
+
+```{r comment='#'}
+# a boring regression
+fit = lm(dist ~ 1 + speed, data = cars)
+coef(summary(fit))
+dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
+grep('天', dojutsu, value = TRUE)
+```
+
+---
+
+# R Plots
+
+```{r cars, fig.height=4, dev='svg'}
+par(mar = c(4, 4, 1, .1))
+plot(cars, pch = 19, col = 'darkgray', las = 1)
+abline(fit, lwd = 2)
+```
+
+---
+
+# Tables
+
+If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,
+
+```{r}
+knitr::kable(head(iris), format = 'html')
+```
+
+---
+
+# HTML Widgets
+
+I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.
+
+Similarly, the Shiny mode (`runtime: shiny`) does not work.
+I might get these issues fixed in the future, but these are not of high priority to me.
+I never turn my presentation into a Shiny app.
+When I need to demonstrate more complicated examples, I just launch them separately.
+It is convenient to share slides with other people when they are plain HTML/JS applications.
+
+See the next page for two HTML widgets.
+
+---
+
+```{r out.width='100%', fig.height=6, eval=require('leaflet')}
+library(leaflet)
+leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
+```
+
+---
+
+```{r eval=require('DT'), tidy=FALSE}
+DT::datatable(
+  head(iris, 10),
+  fillContainer = FALSE, options = list(pageLength = 8)
+)
+```
+
+---
+
+# Some Tips
+
+- When you use the "Infinite Moon Reader" addin in RStudio, your R session will be blocked by default.
+You can click the red button on the right of the console to stop serving the slides, or use the _daemonized_ mode so that it does not block your R session.
+To do the latter, you can set the option
+
+    ```r
+    options(servr.daemon = TRUE)
+    ```
+
+    in your current R session, or in `~/.Rprofile` so that it is applied to all future R sessions. I do the latter by myself.
+
+    To know more about the web server, see the [**servr**](https://github.com/yihui/servr) package.
+
+--
+
+- Do not forget to try the `yolo` option of `xaringan::moon_reader`.
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        yolo: true
+    ```
+
+---
+
+# Some Tips
+
+- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        nature:
+          autoplay: 30000
+    ```
+
+--
+
+- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        nature:
+          countdown: 60000
+    ```
+
+    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.
+
+---
+
+# Some Tips
+
+- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.
+
+    The title slide is set to `class: center, middle, inverse, title-slide` by default.
+You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        nature:
+          titleSlideClass: [top, left, inverse]
+    ```
+
+--
+
+- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        seal: false
+    ```
+
+---
+
+# Some Tips
+
+- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.name/xaringan/incremental.html) for examples.
+
+- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        nature:
+          highlightLines: true
+    ```
+
+    See examples on the next page.
+
+---
+
+# Some Tips
+
+.pull-left[
+An example using a leading `*`:
+
+    ```r
+    if (TRUE) {
+    ** message("Very important!")
+    }
+    ```
+Output:
+```r
+if (TRUE) {
+* message("Very important!")
+}
+```
+
+This is invalid R code, so it is a plain fenced code block that is not executed.
+]
+
+.pull-right[
+An example using `{{}}`:
+
+    `r ''````{r tidy=FALSE}
+    if (TRUE) {
+    *{{ message("Very important!") }}
+    }
+    ```
+Output:
+```{r tidy=FALSE}
+if (TRUE) {
+{{ message("Very important!") }}
+}
+```
+
+It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
+]
+
+---
+
+# Some Tips
+
+An example of using the trailing comment `#<<` to highlight lines:
+
+````markdown
+`r ''````{r tidy=FALSE}
+library(ggplot2)
+ggplot(mtcars) + 
+  aes(mpg, disp) + 
+  geom_point() +   #<<
+  geom_smooth()    #<<
+```
+````
+
+Output:
+
+```{r tidy=FALSE, eval=FALSE}
+library(ggplot2)
+ggplot(mtcars) + 
+  aes(mpg, disp) + 
+  geom_point() +   #<<
+  geom_smooth()    #<<
+```
+
+---
+
+# Some Tips
+
+- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).
+
+- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.
+
+- Then change the `chakra` option in YAML to point to this file, e.g.
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        chakra: libs/remark-latest.min.js
+    ```
+
+- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally.
+The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.
+
+---
+
+# Macros
+
+- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`.
+For example, before remark.js initializes the slides, you can define a macro named `scale`:
+
+    ```js
+    remark.macros.scale = function (percentage) {
+      var url = this;
+      return '<img src="' + url + '" style="width: ' + percentage + '" />';
+    };
+    ```
+
+    Then the Markdown text
+
+    ```markdown
+    ![:scale 50%](image.jpg)
+    ```
+
+    will be translated to
+
+    ```html
+    <img src="image.jpg" style="width: 50%" />
+    ```
+
+---
+
+# Macros (continued)
+
+- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,
+
+    ```yaml
+    output:
+      xaringan::moon_reader:
+        nature:
+          beforeInit: "macros.js"
+    ```
+
+    You save your remark.js macros in the file `macros.js`.
+
+- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.
+
+---
+
+# CSS
+
+Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.
+
+You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css).
+You can completely replace it with your own CSS files, or define new rules to override the default.
+See the help page `?xaringan::moon_reader` for more information.
+
+---
+
+# CSS
+
+For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:
+
+```css
+@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);
+
+.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
+```
+
+Then set the `css` option in the YAML metadata:
+
+```yaml
+output:
+  xaringan::moon_reader:
+    css: ["default", "ubuntu-mono.css"]
+```
+
+Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.
+
+See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.
+
+---
+
+# Themes
+
+Don't want to learn CSS?
+Okay, you can use some user-contributed themes.
+A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name.
+Below are some existing themes:
+
+```{r}
+names(xaringan:::list_css())
+```
+
+---
+
+# Themes
+
+To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,
+
+```yaml
+output:
+  xaringan::moon_reader:
+    css: [default, metropolis, metropolis-fonts]
+```
+
+If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.name/en/2017/10/xaringan-themes).
+
+---
+class: inverse, middle, center
+background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
+background-size: contain
+
+# Naruto
+
+---
+background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
+background-size: 100px
+background-position: 90% 8%
+
+# Sharingan
+
+The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:
+
+- the "Eye of Insight"
+
+- the "Eye of Hypnotism"
+
+I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>
+
+.footnote[
+[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.
+
+[2] By comparison, bad presentations only put the audience to sleep.
+
+[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
+]
+
+---
+
+# Naruto terminology
+
+The **xaringan** package borrowed a few terms from Naruto, such as
+
+- [Sharingan](http://naruto.wikia.com/wiki/Sharingan) (写輪眼; the package name)
+
+- The [moon reader](http://naruto.wikia.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)
+
+- [Chakra](http://naruto.wikia.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)
+
+- [Nature transformation](http://naruto.wikia.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)
+
+- The [infinite moon reader](http://naruto.wikia.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)
+
+- The [summoning technique](http://naruto.wikia.com/wiki/Summoning_Technique) (download remark.js from the web)
+
+You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.
+
+---
+
+class: center
+
+# Hand seals (印)
+
+Press `h` or `?` to see the possible ninjutsu you can use in remark.js.
+
+![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)
+
+---
+
+class: center, middle
+
+# Thanks!
+
+Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
+
+The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
 
@@
 
-```{r muelectionmenziesholt, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
-knitr::include_graphics("../../../figures/mu_election-differences-menziesholt-slides.pdf")
+```{r muelectionmenziesholt, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/mu_election-differences-menziesholt.pdf")
 ```
+
+---
 
@@
 
-```{r muelectionwhitlam, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
-knitr::include_graphics("../../../figures/mu_election-differences-whitlam-slides.pdf")
+```{r muelectionwhitlam, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/mu_election-differences-whitlam.pdf")
 ```
@@
 
+---
+
 ## Howard instability
 
-```{r muelectionhoward, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
-knitr::include_graphics("../../../figures/mu_election-differences-howard-slides.pdf")
+```{r muelectionhoward, cache = TRUE, echo = FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/mu_election-differences-howard.pdf")
 ```
@@
 
+---
+
 # Issues/tradeoffs
+
+---
 
@@
 
+---
+
 # Future work
@@
 
+---
+
 ## Questions?

### 2018-10-23 scripts/run_6_make_graphs/make_graphs_of_mu_election.R

@@ -1,5 +1,5 @@
 library(tidyverse)
-update.packages()
+# update.packages()
 
 mu_election <- read_csv("scripts/from_monica/results/mu_election.csv")
 
@@ -53,6 +53,8 @@ ggsave(
   units = "in"
 )
 
+
+
 all_differerences <- mu_election %>% 
   select(election, topic, median) %>% 
   mutate(previousElection = lag(median, 40)) %>% 
@@ -89,3 +91,184 @@ ggsave(
 # draft("myslides.Rmd", template="metropolis", package="binb", edit=FALSE)
 # setwd("myslides")  ## template creates a new subdir
 # render("myslides.Rmd")
+
+
+
+all_differerences <- mu_election %>% 
+  select(election, topic, median) %>% 
+  mutate(previousElection = lag(median, 40)) %>% 
+  mutate(diff = abs(median - previousElection))
+
+slides_data <- mu_election %>% 
+  select(election, topic, median) %>% 
+  mutate(previousElection = lag(median, 40)) %>% 
+  mutate(diff = abs(median - previousElection)) %>% 
+  mutate(grouper = case_when(election %in% c(26) ~ "Menzies-Holt",
+                             election %in% c(29) ~ "Whitlam",
+                             election %in% c(39, 40, 41) ~ "Howard",
+                             TRUE ~ "Other")) %>% 
+  filter(election %in% c(26, 29, 39, 40, 41))
+
+slides_data %>% 
+  filter(election %in% c(26)) %>% 
+  ggplot(aes(x = topic, y = diff, color = as.factor(election))) +
+  geom_point(data = all_differerences, aes(x = topic, y = diff), color = "grey90") +
+  geom_point() +
+  labs(y = "Absolute difference with previous", 
+       x = "Topic") +
+  scale_color_viridis_d(name = "Election") +
+  theme_minimal()
+
+ggsave(
+  "outputs/figures/mu_election-differences-menziesholt.pdf",
+  height = 8,
+  width = 10,
+  units = "in"
+)
+
+
+
+slides_data %>% 
+  filter(election %in% c(29)) %>% 
+  ggplot(aes(x = topic, y = diff, color = as.factor(election))) +
+  geom_point(data = all_differerences, aes(x = topic, y = diff), color = "grey90") +
+  geom_point() +
+  labs(y = "Absolute difference with previous", 
+       x = "Topic") +
+  scale_color_viridis_d(name = "Election") +
+  theme_minimal()
+
+ggsave(
[…]

### 2018-11-05 outputs/docs/events/paper.Rmd
Add graph of missing dates for Appendix A

@@
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 We systematically analyse the text using two main statistical techniques.
-To reduce the dimensionality of our dataset we use a topic model that allows correlation between topics.
-We then analyse the topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
+To reduce the dimensionality of our dataset we first use a topic model that allows correlation between topics.
+We then analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
 These events include: changes in government; elections; and other significant events such as an economic recession or terrorism.
@@
 ```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/topics_example.pdf")
+# knitr::include_graphics("../../figures/topics_example.pdf")
 ```
@@
 
-## Known Hansard issues {#knownhansardissues}
+## Summary statistics
+
+```{r countsbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '90%'}
+knitr::include_graphics("../../figures/counts_by_year.pdf")
+```
+
+\newpage
+
+## Compared with parliamentary website {#knownhansardissues}
 Comparing the sitting days to the dates that we have suggests some issues with the dataset (Table \@ref(tab:missingdays)).)
@@
 
-Add the graphs and procedures.
+Add the graphs and procedures. **[TBD]**
 

### 2018-11-05 outputs/docs/events/slides/slides.Rmd
Add graph of missing dates for Appendix A

@@
 - Rohan Alexander, Australian National University
-date: 24 October 2018
-institute: Presentation at the School of Politics and International Relations, Australian National University, Canberra, Australia.
+date: 25 October 2018
+institute: Presentation at the Research School of Economics, Australian National University, Canberra, Australia.
 output: binb::metropolis
@@
 key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
-
+#breka
 ```
@@
 - A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
-- Hansard records have been used in other counties but not really at scale in Australia (although others are also starting to use them).
+- Hansard records have been used in other counties but not really at scale in Australia (although others, such as Patrick Leslie, also use them).
 - Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
@@
 
-```{r pressureFig, echo=FALSE, out.width = '50%', fig.align="center"}
+```{r pressureFig, echo=FALSE, out.width = '75%', fig.align="center"}
 
@@
 
-```{r exampletopics, cache = TRUE, echo=FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/topics_example-slides.pdf")
+```{r exampletopics, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("../../../figures/topics_example-slides.png")
 ```
@@
 Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
-
 $$
@@
 
-```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/war_stack.pdf")
+```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/war_stack-slides.pdf")
 ```
@@
 
-```{r mugov, cache = TRUE, echo = FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/mu_gov.pdf")
+```{r mugov, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/mu_gov-slides.pdf")
 ```
@@
 
-```{r muelection, cache = TRUE, echo = FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/mu_election.pdf")
+```{r muelection, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
+knitr::include_graphics("../../../figures/mu_election-slides.pdf")
 ```
@@
 key_events_results %>%
-  kable(caption = "Days that were significantly different to other days in their sitting period") %>%
+  kable() %>%
   kable_styling(font_size = 10)
-
+#CAS
 ```
@@
 
-## Whitlam stability
+## Whitlam re-election
 
@@
 
-# Future work
+# Current/future work
 
-## Future work
-- Group identity: which is more important?
--
+## Current/future work
+<!-- ### Improve data -->
+<!-- - Trying to get website data instead of needing to parse PDFs. -->
+
+### Current work
+- In-group and out-group identity: which is more important?
+- Senate/HoR: just how different are they?
+- Methods assessment: how is your cleaning impacting your results?
+- States/Commonwealth: where does policy come from?
+
+### Future
+- Open to suggestions and keen for collaboration.
 
@@
 - rohanalexander.com
+
+```{r hansardphoto, echo=FALSE, out.width = '75%', fig.align="center"}
+
+knitr::include_graphics("../../../figures/hansard_photo.png")
+
+```

### 2018-11-05 scripts/run_3_make_topic_modelling_input/run_1_remove_num_punc_lower_multiword_unnest.R

@@ -31,7 +31,7 @@ multiword_expressions <- read_csv2("inputs/misc/multiwords_with_corrections.csv"
 # use_this_path_to_get_csvs  <- "/Volumes/Backup/temp"
 # use_this_path_to_get_csvs  <- "outputs/hansard/temp/testing"
 # use_this_path_to_get_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_get_csvs <- "/Volumes/Backup/senate_run_4_output"
+use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
 file_names <-
@@ -45,7 +45,8 @@ file_names <-
 file_names <- file_names %>% sample() # Randomise the order
 
 # use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing/test"
-use_this_path_to_save_csvs  <- "/Volumes/Backup/senate_topic_modelling_input"
+use_this_path_to_save_csvs <- "/Volumes/Hansard/for_topics/federal/hor"
+# use_this_path_to_save_csvs  <- "/Volumes/Backup/senate_topic_modelling_input"
 # use_this_path_to_save_csvs  <- "/Volumes/Backup/temp"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)

### 2018-11-05 scripts/run_3_make_topic_modelling_input/run_2_remove_stopwords_uncommon.R

@@ -75,7 +75,7 @@ custom_stop_words <- bind_rows(stop_words, # The default list
 # Change the path as required:
 # use_this_path_to_get_csvs  <- "outputs/hansard/temp/testing"
 use_this_path_to_get_csvs <-
-  "/Volumes/Backup/senate_topic_modelling_input"
+  "/Volumes/Hansard/for_topics/federal/hor"
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
 file_names <-
@@ -90,7 +90,7 @@ file_names <- file_names %>% sample() # Randomise the order
 
 # use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing/test"
 use_this_path_to_save_csvs  <-
-  "/Volumes/Backup/senate_topic_modelling_prep_2"
+  "/Volumes/Hansard/for_topics/federal/hor"
 # use_this_path_to_save_csvs  <- "/Volumes/Backup/temp"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)

### 2018-11-05 scripts/run_4_model_topics/run_0_topic_modelling_stm.R

@@ -1,1181 +1,0 @@
-# !diagnostics off
-#### Preamble ####
-# Purpose: Create topics, for the words used in each day of Hansard
-# Author: Rohan Alexander
-# Email: rohan.alexander@anu.edu.au
-# Last updated: 17 October 2018
-# Prerequisites:
-# Issues:
-
-
-#### Workspace set-up ####
-# Load libraries
-# devtools::install_github("dgrtwo/drlib")
-# library(drlib)
-# library(furrr)
-library(lubridate)
-library(quanteda)
-library(stm)
-library(tictoc)
-library(tidytext)
-library(tidyverse)
-library(tm)
-# library(viridis)
-# update.packages()
-
-# plan(multiprocess)
-
-
-#### Load corpus
-tm_corpus <-
-  tm::Corpus(DirSource(directory = "/Volumes/Backup/senate_topic_modelling_prep_2"))
-hansard <- corpus(tm_corpus)
-summary(hansard)
-rm(tm_corpus)
-
-
-# NEED TO COME BACK AND ADD METADATA
-# # Load the metadata
-# election_dates <-
-#   read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
-# hansard_dates <-
-#   read_csv("inputs/misc/hansard_dates.csv", col_types = cols())
-# governmentChanges <-
-#   read_csv("inputs/misc/change_of_pm.csv", col_types = cols())
-# keyEvents <-
-#   read_csv("inputs/misc/key_events.csv", col_types = cols())
-#
-# all_dates <-
-#   tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
-#   mutate(
-#     electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
-#     electionDate = cumsum(electionDate),
-#     governmentChangeDate = if_else(allDates %in% governmentChanges$end, 1, 0),
-#     governmentChangeDate = cumsum(governmentChangeDate),
-#     keyEvent = if_else(allDates %in% keyEvents$theDate, 1, 0),
-#     keyEvent = cumsum(keyEvent),
-#     electionOrGovernmentDate = if_else(allDates %in% c(election_dates$electionDate, governmentChanges$end), 1, 0),
-#     electionOrGovernmentDate = cumsum(electionOrGovernmentDate)) %>%
-#   rename(
-#     electionCounter = electionDate,
[…]

### 2018-11-05 scripts/run_4_model_topics/run_1_topic_modelling_stm.R

@@ -1,0 +1,1181 @@
+# !diagnostics off
+#### Preamble ####
+# Purpose: Create topics, for the words used in each day of Hansard
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 17 October 2018
+# Prerequisites:
+# Issues:
+
+
+#### Workspace set-up ####
+# Load libraries
+# devtools::install_github("dgrtwo/drlib")
+# library(drlib)
+# library(furrr)
+library(lubridate)
+library(quanteda)
+library(stm)
+library(tictoc)
+library(tidytext)
+library(tidyverse)
+library(tm)
+# library(viridis)
+# update.packages()
+
+# plan(multiprocess)
+
+
+#### Load corpus
+tm_corpus <-
+  tm::Corpus(DirSource(directory = "/Volumes/Hansard/for_topics/federal/hor"))
+hansard <- corpus(tm_corpus)
+summary(hansard)
+rm(tm_corpus)
+
+
+
+# NEED TO COME BACK AND ADD METADATA
+# # Load the metadata
+# election_dates <-
+#   read_csv("inputs/misc/misc_elections_data.csv", col_types = cols())
+# hansard_dates <-
+#   read_csv("inputs/misc/hansard_dates.csv", col_types = cols())
+# governmentChanges <-
+#   read_csv("inputs/misc/change_of_pm.csv", col_types = cols())
+# keyEvents <-
+#   read_csv("inputs/misc/key_events.csv", col_types = cols())
+#
+# all_dates <-
+#   tibble(allDates = seq(ymd('1901-01-01'), ymd('2017-12-31'), by = 'days')) %>%  # Make a column of all the dates from Federation
+#   mutate(
+#     electionDate = if_else(allDates %in% election_dates$electionDate, 1, 0),
+#     electionDate = cumsum(electionDate),
+#     governmentChangeDate = if_else(allDates %in% governmentChanges$end, 1, 0),
+#     governmentChangeDate = cumsum(governmentChangeDate),
+#     keyEvent = if_else(allDates %in% keyEvents$theDate, 1, 0),
+#     keyEvent = cumsum(keyEvent),
+#     electionOrGovernmentDate = if_else(allDates %in% c(election_dates$electionDate, governmentChanges$end), 1, 0),
+#     electionOrGovernmentDate = cumsum(electionOrGovernmentDate)) %>%
+#   rename(
+#     electionCounter = electionDate,
[…]

### 2018-11-05 scripts/run_6_make_graphs/make_table_pdf_by_year.R

@@ -1,0 +1,104 @@
+#### Preamble ####
+# Purpose: Create graphs and tables that summarise the Hansard data for the Appendix
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 5 November 2018
+# Prerequisites:
+# Issues:
+
+
+#### Workspace set-up ####
+library(ggrepel)
+library(lubridate)
+library(stringr)
+library(tidyverse)
+
+# Get the names of the PDFs
+# Senate
+senate_dates <- list.files(path = "/Volumes/Hansard/pdfs/federal/senate") %>% 
+  str_replace(".pdf", "") %>% 
+  ymd() 
+senate_dates <- tibble(pdf_date = senate_dates)
+# Reps
+reps_dates <- list.files(path = "/Volumes/Hansard/pdfs/federal/hor") %>% 
+  str_replace(".pdf", "") %>% 
+  ymd()
+reps_dates <- tibble(pdf_date = reps_dates)
+
+
+#### Create the dataset ####
+# Make the counts by each year for the PDFs that we have
+counts_by_year_senate <- senate_dates %>% 
+  group_by(year(pdf_date)) %>% 
+  count()
+  
+names(counts_by_year_senate) <- c("year", "senate_number")
+
+counts_by_year_reps <- reps_dates %>% 
+  group_by(year(pdf_date)) %>% 
+  count() 
+
+names(counts_by_year_reps) <- c("year", "house_number")
+
+counts_by_year <- counts_by_year_reps %>% 
+  left_join(counts_by_year_senate)
+
+rm(counts_by_year_senate, counts_by_year_reps)
+
+# Compare that to the counts that were on the parliament website at 
+# https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear
+counts_from_website <- read_csv("inputs/misc/number_of_sitting_days.csv")
+
+counts_by_year <- counts_by_year %>% 
+  left_join(counts_from_website)
+
+counts_by_year <- counts_by_year %>% 
+  mutate(rep_diff = reps - house_number, 
+         senate_diff = senate - senate_number)
+
+# write_csv(counts_by_year, "outputs/misc/missing_dates.csv")
+
+
+#### Graphs ####
+# Graph of counts by year
+counts_by_year %>% 
+  group_by(year) %>% 
+  select(year, house_number, senate_number) %>% 
[…]

### 2018-11-06 outputs/docs/events/paper.Rmd
Update gammas and fix one part of an appendix in the paper

@@
 significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
-top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
-missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
 hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
@@
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
-And @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
+@GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
+@FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups.
+The closest research to ours that we have found is @Boulous2013 who examines parliamentary debate in Australia for the period 1946 to 2012.
 
@@
 Additionally, XML records are available in some cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
+There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament that we have PDFs for and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
 top_words %>% 
-  kable(booktabs = T, caption = "Top words associated with each topic") %>%
-  kable_styling(font_size = 10)
+  kable(booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
+  kable_styling(font_size = 8, latex_options = c("repeat_header"))
 
@@
 
-```{r asdf, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '90%'}
+```{r asdf, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
 knitr::include_graphics("../../figures/example_hansard_page.png")
@@
 
-## Summary statistics
+## Summary statistics {#hansardsummarystatistics}
 
-```{r countsbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '90%'}
+The number of sitting days in a year varies considerably.
+The highest in the House of Representatives was 122 days in 1904, followed by 113 days in 1901 and 1920.
+The year with the most sitting days in the Senate was 1902 with 93 days, followed by 1989 with 92 days, and 1986 with 86 days (Figure \@ref(fig:countsbyyear)).
+
+```{r countsbyyear, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
 knitr::include_graphics("../../figures/counts_by_year.pdf")
 ```
+
+Until the 1950s the House of Representatives tended to have more sitting days than the Senate.
+It was then similar, before the Senate had more days in the 1980s and 1990s.
+Since the 2000s the House of Representatives again has tended to have more sitting days than the Senate.
+
+These counts of the number of sitting days are based on available PDFs.
+For this reason the counts may be slightly different to other counts.
+An example of one known issue of this type is detailed in the next section.
 
@@
 ## Compared with parliamentary website {#knownhansardissues}
-Comparing the sitting days to the dates that we have suggests some issues with the dataset (Table \@ref(tab:missingdays)).)
+The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.
 
-```{r missingdays, echo = FALSE, results = 'asis'}
+[^parliamentarywebsitelink]: As at 5 November, the website was available at: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear.
 
-missing_days %>% 
-  kable(booktabs = T, caption = "Missing days") %>%
-  kable_styling(font_size = 12) %>% 
-  kableExtra::kable_styling(latex_options = "hold_position")
+In general the number of sitting days on the parliamentary website summary table is similar to the number of PDFs that we have although it does identify a few particularly concerning years (Figure \@ref(fig:differencesbyyear)).
 
+```{r differencesbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics("../../figures/differences_by_year.pdf")
 ```
 
-Positive means we are missing some, negative means we have too many.
-Source: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear
+When the difference is positive, it means that in that year we have fewer PDFs than the parliamentary website claims.
+For instance, 5 could mean that the parliamentary website claimed there were 100 days, but we only had PDFs for 95 days.
+Similarly, when the difference is negative then we have more PDFs than the parliamentary website claims there were sitting days.
+
+The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer.
+
+The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
+1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09, .
+
+There are two unaccounted for differences in 2006, one unaccounted for difference in 2001.
+
+The Parliament website is missing the Hansard PDFs for the following dates in the House of Representatives: 
+1985-08-23,
+1992-09-10,
+1996-12-13,
+2002-05-14,
+2000-10-12, and
+2000-06-29.
+
+There is one unaccounted for differences in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012
 
@@
 
-## Example Hansard PDf to text record workflow {#hansardworkflow}
-Here we provide psuedo-code for the workflow from PDF to text.
-The scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.
-The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.
-The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues and the \texttt{tidytext} R package of @SilgeRobinson2016 and @Benoit2018 for compounding multiword expressions.
+## Example Hansard PDF to text record workflow {#hansardworkflow}
+The exact scripts that we use are too long to provide here but are available on request.
+Instead here we provide shorterned scripts for the workflow to convert the PDFs to usable text datasets that may be a useful starting point for other researchers.
+The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
+The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014.
+The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.
+
+The first step is scrape the websites for the PDFs.
+
+```{r scrapingexample, echo=TRUE, eval = FALSE}
+library(purrr)
+library(tidyverse)
+
+# Create lists of URLs to scrape and file names to save the PDF as
+data_to_scrape <- read_csv("csv_of_address_to_visit_and_save_names.csv")
+# Pull out the two pieces
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+# Add a containing folder to the save_names
+save_name <- paste0("pdfs/", save_name)
+# Create that containing folder if necessary
+dir.create("pdfs")
+
+# The function that will visit address_to_visit and save to save_name file
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    # Do the actual downloading of the PDF
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    # Helpful so that you know progress when running it on all the records
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
+    # Space out your requests so you don't overwhelm the website
+    Sys.sleep(sample(15:30, 1)) 
+  }
+
+# Make the function more resistent to issues
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+# Walk through the lists and get the PDFs
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
+```
+
+The next step is...
+
+UP TO HERE
 
@@
 
-**[TBD]**
+The choice of the number of topics to use in a topic model has a substantial affect on the results of the model.
+For instance, in our topic model, choosing a smaller number of topics, such as 10 or 20 results in a model that is not all that useful because the topics are so broad.
+
+There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice and we found it useful to try a few quite different measures before settling on 80 topics.
+Useful diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]
+
+[^Silgefootnote]: The code for creating the figures in this section is based on @Silge2018.
+
+```{r topicsdiagnostics, cache = TRUE, echo = FALSE, fig.cap = "Model diagnostics", out.width = '100%'}
+knitr::include_graphics("../../figures/diagnostics_for_k.pdf")
+```
+
+**[Discuss each of these...]**
+
+Additionally, the tradeoff between exclusitivity and semantic coherence...  (Figure \@ref(fig:topicsexclusivityvscoherence))
+
+```{r topicsexclusivityvscoherence, cache = TRUE, echo = FALSE, fig.cap = "Exclusitivity compared with semantic coherence", out.width = '100%'}
+knitr::include_graphics("../../figures/exclusivity_vs_coherence.pdf")
+```
+
+**[Discuss this one too...]**
 

### 2018-11-06 scripts/run_6_make_graphs/make_table_pdf_by_year.R

@@ -101,4 +101,3 @@ ggsave(
   units = "in"
 )
 
-# 10 September 1992 is missing a PDF

### 2018-11-06 scripts/run_4_model_topics/run_1_topic_modelling_stm.R
Update paper

@@ -3,7 +3,7 @@
 # Purpose: Create topics, for the words used in each day of Hansard
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 5 November 2018
+# Last updated: 6 November 2018
 # Prerequisites:
 # Issues:
 
@@ -38,6 +38,8 @@ rm(tm_corpus)
 # For now just get the filename
 file_names <- list.files(path = "/Volumes/Hansard/for_topics/federal/hor") %>% 
   str_replace(".csv", "")
+
+docvars(hansard, "date") <- file_names
 # # Load the metadata
 
 # election_dates <-
@@ -122,7 +124,7 @@ rm(docsTM,
 # Create models with different values for K
 # Takes an age to run
 many_models <-
-  data_frame(K = c(20, 40, 60, 80)) %>%
+  data_frame(K = c(20, 40, 60, 80, 100)) %>%
   mutate(topic_model = map(
     # mutate(topic_model = future_map(
     K,
@@ -166,7 +168,8 @@ k_result %>% transmute(
   `Lower bound` = lbound,
   Residuals = map_dbl(residual, "dispersion"),
   `Semantic coherence` = map_dbl(semantic_coherence, mean),
-  `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")
+  `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout"),
+  Exclusivity = map_dbl(exclusivity, mean)
 ) %>%
   gather(Metric, Value, -K) %>%
   ggplot(aes(K, Value)) +
@@ -203,7 +206,7 @@ ggsave(
   units = "in"
 )
 
-
+head(hansard_stm$meta)
 # Save the bits and pieces that are important for later
 topic_model_20 <- k_result %>%
   filter(K == 20) %>%
@@ -212,10 +215,7 @@ topic_model_20 <- k_result %>%
 save(topic_model_20, file = "outputs/results-topic_models_and_gammas/topic_model_20.RData")
 tidy(topic_model_20,
      matrix = "gamma",
-     # document_names = hansard_stm$meta$docid_field) %>%
-     document_names = file_names) %>%
-  mutate(str_split(document))
-# HERE
+     document_names = hansard_stm$meta$date) %>% 
   write_csv("outputs/results-topic_models_and_gammas/gammas_model_20.csv")
 tidy(topic_model_20,
      matrix = "beta",
[…]

### 2018-11-08 outputs/docs/events/paper.Rmd
Update paper
Add appendix about choosing topic number

@@
     template: svm-latex-ms.tex
-title: "The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)"
+title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
@@
   affiliation: Australian National University
-abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history.
+abstract: "We systematically analyse how parliamentary discussion changes in response to elections and changed governments in Australian history.
 We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
@@
 We contribute to this literature in terms of both data and methods.
-To the best of our knowledge we are the first to bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
+From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
 From a methods perspective, our analysis model has several advantages over existing methods.
@@
 @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
+And @Salisbury2011 examines unparliamentary behaviour.
 @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups.
@@
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
+There are two stages in our analytical process.
 
-We use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
+We first use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
 We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
@@
 
-In the following sections, we describe both the topic modelling approach and the Bayesian hierarchical analysis model.
-Firstly, we describe the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before moving onto the CTM, which is a natural extension of LDA.
-We then discuss the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
+In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
+More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(hansardworkflow)
 
@@
 
+In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....
+
+Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.
+
 \newpage
@@
 
-There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice and we found it useful to try a few quite different measures before settling on 80 topics.
-Useful diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]
+There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a more fine level such as choosing betweeen 60 and 65 topics.
+We found it useful to try a few quite different measures before settling on 80 topics.
+This provided a balance between being granular enough to be informative--anything less than 40 topics tended to be too broad-- yet still being tractable for our analysis model in a reasonable amount of time.
+In addition to looking at the topics and how they changed over time, diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, exclusivity.
+and semantic coherence (Figures \@ref(fig:topicsdiagnostics)).[^Silgefootnote]
 
@@
 
-**[Discuss each of these...]**
-
-Additionally, the tradeoff between exclusitivity and semantic coherence...  (Figure \@ref(fig:topicsexclusivityvscoherence))
+@RobertsStewartAiroldiRPackage provides more detail about the diagnostic tests that we use, but we briefly discuss each here.
+Exclusivity is a measure of how specific words are to particular topics.
+It looks at the proportion that a word makes up of a particular topic compared with the proportion that word makes up of the other topics.
+As the number of topics increases we usually expect exclusivity to increase because the topics become more particular.
+Higher values are better.
+The held out likelihood as described by @Wallach2009 takes a test/training approach to estimate the probability of held-out documents given the training documents.
+Higher values are better.
+The lower bound gives some indication of whether the model may have multiple modes and hence the end result be sensitive to the starting position (@Roberts2016navigating).
+Residuals analysis (@Taddy2012) compares the theoretical distribution of the variance with the eactual distribution.
+It is a test for overdispersion of the variance, and if it is found then this can suggest that more topics would be appropriate.
+Semantic coherence is the tradeoff for having topics that are more specific and the subsequent risk that the topics become meaningless.
+@Mimno2011 define a measure of coherence that is based on ratios of single words compared with pairs of words.
+The idea is that words that should occur in the one document should be more likely to be in a particular topic than ones that do not occur together.
+For instance, a topic that has 'wine' and 'cheese' as highly rated words would score better on their measure than another that contained 'cheese' and 'mining'.
+Lower values are better.
+@RobertsStewartAiroldiRPackage recommend examining the tradeoff between exclusitivity and semantic coherence.
+This suggests that the magnitude of improvement reduces from about 80 topics (Figure \@ref(fig:topicsexclusivityvscoherence)).
 
@@
 ```
-
-**[Discuss this one too...]**
 

### 2018-11-09 outputs/docs/events/paper.Rmd
Add political theory paras

@@
 top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
+
+top_words <- top_words %>% 
+  rename(Topic = topic, Terms = terms)
+
 hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
@@
 In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
-More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(hansardworkflow)
+More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(LDAexample).
 
@@
 But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.
-One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent.
+
+Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 does this by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate.
+This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
+In exchange for some reduction in the reasonableness of the categorisation, the LDA method of @Blei2003latent is able to provide consistent categorisation of the topics discussed in Hansard for large text collections.
 
@@
 This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.
-
+More detail on how LDA works is available in Appendix \@ref(LDAexample).
+
+One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+This is the Correlated Topic Model, described in the next section.
+
+## Correlated Topic Model
+As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
+Correlation between topics is neither modelled nor accounted for by LDA, but in reality often topics are related.
+For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
+The models are very similar, and the key difference is the underlying distributions that are drawn from.
+
+As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is just slightly modified.
+Rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
+
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
+That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
+This distribution can incorporate a covariance structure across the topics.
+The remainder of the steps of the document generating process are identical to LDA.
+
+However, the replacement of the Dirichlet distribution with the logistic multivariate Normal distribution adds a level of computational complexity to CTM.
+The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
+@BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
+CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
+The main difference is to add a covariate to $\mu$ which allows consideration of additional information.
+
+<!-- The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
+For instance, we generally have some information about the author and the date that a document was created.
+In the case of Hansard, we know who was speaking and the date they spoke.
+The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
+That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+-->
+
+<!-- The STM is set-up to include metadata to do with prevalence and content.
+Prevalence relates to the topic proportions in each document.
+For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
+Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
+The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate.
+For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
+Content relates to the words that make up each topic.
+For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
+STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
+-->
+
+<!-- As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM: -->
+
+<!-- 1.
+As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
+In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3): -->
+<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$ -->
+
+<!-- 2.
+To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
+Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$: -->
+<!-- $$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$ -->
+
+<!-- 3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$: -->
+<!--     a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics. -->
+<!--     b. Randomly choose a term from the topic-specific multinomial distribution over terms. -->
+
+<!-- We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+We consider both topic prevalence and content to be functions of time.
+The choice of the number of topics to use in the model is a situation-specific compromise.
+We use a standard diagnostic approach to decide on 80 **[UPDATE]** topics.
+More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
+-->
+
+Figure \@ref(fig:exampletopics) illustrates a CTM output based on a five per cent sample from the Australian House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
+
+```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
+# knitr::include_graphics("../../figures/topics_example.pdf")
+```
+
+## Analysis model
+
+<!-- **[Actually, maybe this whole paragraph not needed?]** There are many ways to consider the effect of events.
+One is to summarise the topic proportions by each event and then run multinomial tests for whether the groups are different, although this does not take full advantage of the frequency of our data.
+Another is to consider a variant of multinomial logistic regression, but then events would be constrained to have an effect in certain ways.
+An autoregressive moving average (ARMA) model could be used to test for structural breaks, but **[something]**.
+Or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model, but **[something]**.
+-->
+
+The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
+The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
+But with 80 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
+
+One option for relating the topic distributions to events would be to use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016.
+The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
+For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the government or election period, may affect the topics within that document.
+The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
+The assumption that there is some document generation process is the same as in LDA, it is just that this process now includes metadata.
+
+More specifically, consider a matrix of covariates.
+$X_d$, where each column relates to a different covariate or metadata aspect, and each row refers to a document.
+Then a cell has the value of each covariate for a particular document.
+Similar to the CTM, the STM assumes the topics within a document $\theta_d$ are a draw from a logistic Normal distribution with mean $\mu$.
+However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$:
+
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+
+Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
+For instance, one covariate could be the government $g$ that was in power during the time corresponding to document $d$.
+However, the STM covariate framework has several limitations in terms of our goal to assess the relationship between topics and events:
+
+- There is no way of specifying more complicated auto-correlated functional forms of the effects of events over time.
+For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
+In the STM framework, it is possible to specify a constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
+- There is no way to implement partial pooling across groups of similar documents.
+The STM framework assumes that  documents are independently and identically distributed, conditional on the model covariates.
+However, it could be expected that topic distributions within a particular government, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
+To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
+- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
+Ideally, we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
+
+To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
+Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in governments and elections.
+This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
+
+Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
+Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM.
+We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
+
+The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
+Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
+
+$$
+\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
+$$
+where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
+This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
+
+The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The mean parameters $\mu_{s,p}$ are modelled on the log scale as
+
+$$
+\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
+$$
+where:
+
+- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
+- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
+- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
+- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
+
+The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
+$$
+\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)
+$$
+
+The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
+In particular, we model this as an AR(1) in $d$:
+
+$$
+\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
+$$
+One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
+This allows us to identify differences between government and election effects even when there is a one-term government.
+The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
+
+$$
+\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100)
+$$
+$$
+\rho_{e[s],p} \sim \mbox{Uniform}(0,1)
+$$
+We model the underlying time trend in topics using splines regression.
+The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
+The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
+We place knot points every five sitting periods as this is the average length of time for a government to sit.
+Non-informative priors are placed on the splines coefficients:
+$$
+\beta_{p,k} \sim \mbox{Normal}(0, 100)
+$$
+
+Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
+This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+In addition, this set up also partially pools effects across sitting periods.
+The $\delta_{s,p}$ values are modelled as:
+
+$$
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
+$$
+
+The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
+If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
+Non-informative priors are placed on the variance parameters:
+
+$$
+\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
+$$
+
+We run the model in JAGS using the \texttt{rjags} package of @Plummer2018.
+
+<!-- __[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __ -->
+
+<!-- RA STUFF: -->
+
+<!-- The full model is: -->
+
+<!-- \begin{align} -->
+<!-- \gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ -->
+<!-- \log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\ -->
+<!-- \alpha_{s1} &= 0 (\#eq:zeroconstraint)\\ -->
+<!-- \alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\ -->
+<!-- \delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\ -->
+<!-- \sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance) -->
+<!-- \end{align} -->
+
+<!-- **[Does the variance parameter used in Equation 4 need to be specified too?]** -->
+
+<!-- Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
+This is considered as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
+In a sense, $\mu_{stp}$ will be mean topic distributions over whatever time period is of interest.
+-->
+
+<!-- Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
+These are themselves parameters.
+The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
+-->
+
+<!-- Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
+Equation \@ref(eq:alphasp) shows how we consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **[SOMETHING]** and a variance that depends on **[SOMETHING ELSE]**.
+Similarly, Equation \@ref(eq:deltasp) show how we model $\delta_{stp}$  as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution in Equation \@ref(eq:randomwalkvariance), that is, a random walk around each intercept.
+-->
+
+<!-- **[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]** -->
+
+<!-- We currently consider events in two ways.
+The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
+This illustrates the differences between the topics.
+The second is by including incrementing variables in the prevalence metadata This groups each day by events and we can then conduct significance tests.
+Unfortunately both of these do not consider short-term effects.
+-->
+
+<!-- **[Use tf-idf between them as illustrative instead? Use that other measure of difference?]** -->
+
+<!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics. -->
+
+<!-- Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
+It will be higher for words that are rarely used across all documents, but commonly used in a document.
+For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
+However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
+-->
+
+<!-- When we consider events using tf-idf, we gather terms from more than one day.
+We define groups of days that are roughly analogous to sitting periods.
+If there is more than a week between a day then we define a new group, otherwise the day is in the existing group.
+We use various measures **(Text2vec R package has some?
+or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
+-->
+
+# Results
+
+Firstly, we describe the results of the CTM approach, which defined 40 unique topics over the period 1901-2017.
+We then describe the results of the Bayesian analysis model, which identified governments, elections and other events that were associated with a change in the topics discussed.
+
+## Topic modelling
+
+We applied the CTM approach discussed in Section 3.2 on the processed Hansard text database outlined in Section 2.
+The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
+
+The remainder of the results refer to a topic model that had 80 distinct topics defined.
+The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model and understandable for us.
+The diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).
+
+Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics.
+The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
+Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.
+**[UPDATE THAT.]**
+
+```{r topwords, echo = FALSE, results = 'asis'}
+
+top_words %>% 
+  kable(booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
+  kable_styling(font_size = 8, latex_options = c("repeat_header"))
+
+```
+
+## Analysis model
+
+We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
+As discussion in Section 3.3, the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+
+There are several outputs of interest from this modelling stage.
+For example, the model provides estimates of topic prevalence by each sitting period.
+This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
+For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+
+```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
+knitr::include_graphics("../../figures/war_stack.pdf")
+```
+
+One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
+Political events are those related to a change of government or an election.
+As Australia has a parliamentary system, it is possible for the government to change without an election.
+We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
+If a person was prime minister more than once then these are considered separately.
+
+As detailed in Section 3.3, the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.
+When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
+
+We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults).
+These tables focus on elections and governments that were different to the ones that preceded them.
+
+```{r electionsresults, echo = FALSE, results = 'asis'}
+
+elections_results %>%
+  kable(booktabs = T, caption = "Significant elections, and neighours") %>%
+  kable_styling(font_size = 10)
+
+```
+
+```{r governmentsresults, echo = FALSE, results = 'asis'}
+
+governments_results %>%
+  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
+  kable_styling(font_size = 10)
+
+```
+
+In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
+In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
+The error bars represent 95 per cent Bayesian credible intervals.
+The topics that we have focused on here are:
+12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
+
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics.", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_gov.pdf")
+```
+
+```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election.pdf")
+```
+
+Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
+The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
+Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.
+
+We estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
+The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
+This approach means that the model generates dates that are interesting without us having to specify interesting dates.
+
+More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
+
+```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
+
+key_events_results %>%
+  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
+  kable_styling(font_size = 10)
+
+```
+
+<!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
+In general, the estimates of standard deviation are increasing over time, suggesting that discussed topics are more variable in more recent election periods compared to historical periods.
+-->
+
+<!-- ```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'} -->
+<!-- knitr::include_graphics("../../figures/sigma.pdf") -->
+<!-- ``` -->
+
+# Discussion
+Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
+However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
+The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
+To a certain extent this is likely tied up with changes due to World War I.
+
+The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
+The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
+Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
+1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
+
+The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
+The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
+There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
+Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
+The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+
+There were six elections within the second Menzies Government.
+However we do not find that any of those elections was associated with a significant change in the topics discussed.
+In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
+
+The Menzies Government was succeeded by the Holt Government in January 1966.
+This is an example where there was a change in government without an election, as the next election only happened in November 1966.
+We find that the Holt Government is significantly different to the Menzies Government.
+In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
+
+```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-differences.pdf")
+```
+
+The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
+
+The Howard Government is interesting because of the significant differences between elections.
+For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
+
+To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
+However the change in 1998 and 2004 is more unexpected.
+Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
+
+One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
+The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
+For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
+It also appropriately identifies some of other key events that we were interested in.
+However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+Further work is needed to improve this approach.
+For instance, our approach may not be appropriately considering step-changes.
+
+# Conclusion
+In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
+We download and parse PDFs of Hansard to create a new dataset of text.
+We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
+In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
+We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
+
+By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia.
+However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
+
+Using text as data allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify associations and patterns that may otherwise be overlooked.
+That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies.
+For instance, the use of topic models is problematic because of the need to interpret the topics, which at can sometimes feel like interpreting hieroglyphics.
+This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
+Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
+For instance, selecting stop words for removal and which word to merge because of common co-location has an impact on the topics.
+Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
+One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches.
+As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could take that approach.
+
+In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model.
+Firstly, we are assuming that the effect of a particular government is constant across the whole period.
+In addition, we assume that the effect of elections is monotonically decreasing across days since election.
+In future work we will investigate different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.
+
+The way that we identify unusual periods could also be improved.
+We defined sitting periods in a constant fashion across the whole dataset time frame, but the nature of how long parliaments sit for has most likely changed.
+In addition, more work needs to be done on how to identify outlying events.
+For example, it is not clear if an important event that occurs outside a sitting period would be identified.
+And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such specific days are not identified as significantly outlying.
+
+Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model.
+However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
+Future methodological work will focus on how to combine these two modelling steps by extending the STM approach into a more flexible framework.
+
+Watching our politicians at work can sometimes be a little disheartening.
+It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there.
+Nonetheless, our work suggests that reasonable debate of important topics does occur in parliament.
+It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
+However, we do find that since the 1980s differences between government and election periods are greater than they used to be.
+It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.
+
+<!-- What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation. -->
+
+\newpage
+
+# (APPENDIX) Appendix {-}
+
+# Hansard details
+
+## Example Hansard page {#examplehansardpage}
+
+```{r asdf, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
+knitr::include_graphics("../../figures/example_hansard_page.png")
+```
+
+\newpage
+
+## Summary statistics {#hansardsummarystatistics}
+
+The number of sitting days in a year varies considerably.
+The highest in the House of Representatives was 122 days in 1904, followed by 113 days in 1901 and 1920.
+The year with the most sitting days in the Senate was 1902 with 93 days, followed by 1989 with 92 days, and 1986 with 86 days (Figure \@ref(fig:countsbyyear)).
+
+```{r countsbyyear, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
+knitr::include_graphics("../../figures/counts_by_year.pdf")
+```
+
+Until the 1950s the House of Representatives tended to have more sitting days than the Senate.
+It was then similar, before the Senate had more days in the 1980s and 1990s.
+Since the 2000s the House of Representatives again has tended to have more sitting days than the Senate.
+
+These counts of the number of sitting days are based on available PDFs.
+For this reason the counts may be slightly different to other counts.
+An example of one known issue of this type is detailed in the next section.
+
+\newpage
+
+## Compared with parliamentary website {#knownhansardissues}
+The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.
+
+[^parliamentarywebsitelink]: As at 5 November, the website was available at: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear.
+
+In general the number of sitting days on the parliamentary website summary table is similar to the number of PDFs that we have although it does identify a few particularly concerning years (Figure \@ref(fig:differencesbyyear)).
+
+```{r differencesbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+knitr::include_graphics("../../figures/differences_by_year.pdf")
+```
+
+When the difference is positive, it means that in that year we have fewer PDFs than the parliamentary website claims.
+For instance, 5 could mean that the parliamentary website claimed there were 100 days, but we only had PDFs for 95 days.
+Similarly, when the difference is negative then we have more PDFs than the parliamentary website claims there were sitting days.
+
+The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer.
+
+The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
+1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09, .
+
+There are two unaccounted for differences in 2006, one unaccounted for difference in 2001.
+
+The Parliament website is missing the Hansard PDFs for the following dates in the House of Representatives: 
+1985-08-23,
+1992-09-10,
+1996-12-13,
+2002-05-14,
+2000-10-12, and
+2000-06-29.
+
+There is one unaccounted for differences in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012
+
+In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....
+
+Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.
+
+\newpage
+
+## Example Hansard PDF to text record workflow {#hansardworkflow}
+The exact scripts that we use are too long to provide here but are available on request.
+Instead here we provide shorterned scripts for the workflow to convert the PDFs to usable text datasets that may be a useful starting point for other researchers.
+The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
+The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014.
+The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.
+
+The first step is scrape the websites for the PDFs.
+
+```{r scrapingexample, echo=TRUE, eval = FALSE}
+library(purrr)
+library(tidyverse)
+
+# Create lists of URLs to scrape and file names to save the PDF as
+data_to_scrape <- read_csv("csv_of_address_to_visit_and_save_names.csv")
+# Pull out the two pieces
+address_to_visit <- data_to_scrape$URL
+save_name <- data_to_scrape$file_name
+# Add a containing folder to the save_names
+save_name <- paste0("pdfs/", save_name)
+# Create that containing folder if necessary
+dir.create("pdfs")
+
+# The function that will visit address_to_visit and save to save_name file
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    # Do the actual downloading of the PDF
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    # Helpful so that you know progress when running it on all the records
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
+    # Space out your requests so you don't overwhelm the website
+    Sys.sleep(sample(15:30, 1)) 
+  }
+
+# Make the function more resistent to issues
+safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
+
+# Walk through the lists and get the PDFs
+walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
+```
+
+The next step is remove the front matter from the PDFs.
+
+```{r frontmatterexample, echo=TRUE, eval = FALSE}
+library(furrr) # May need the devtools version devtools::install_github("DavisVaughan/furrr")
+library(lubridate)
+library(pdftools)
+library(stringi)
+library(tidyverse)
+library(tictoc)
+library(tm)
+# Set up furrr to use multiple processors
+plan(multiprocess)
+
+# Create the lists of PDFs to read and file names to save text as
+use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
+use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
+
+# Get list of Hansard PDF filenames
+file_names <-
+  list.files(
+    path = use_this_path_to_get_pdfs,
+    pattern = "*.pdf",
+    recursive = TRUE,
+    full.names = TRUE
+  )
+file_names <- file_names %>% sample() # Randomise the order
+# Modify the savenames
+save_names <- file_names %>%
+  str_replace(use_this_path_to_get_pdfs, "") %>%
+  str_replace(".pdf", ".csv")
+save_names <- paste0(use_this_path_to_save_csv_files, save_names)
+
+#### Create the function that will be applied to the files ####
+get_text_from_PDFs <-
+  function(name_of_input_PDF_file,
+           name_of_output_csv_file) {
+    pdf_document <- pdf_text(name_of_input_PDF_file)
+    # Convert to tibble so that tidyverse can be used
+    pdf_document_tibble <- tibble(text = pdf_document)
+    rm(pdf_document)
+    # Each row is now a page of the PDF
+    # Adding a column of the row numbers allows you to keep track of the page numbers
+    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
+    # Separate each line (of each page) into own row
+    pdf_document_tibble <-
+      separate_rows(pdf_document_tibble, text, sep = "\\n")
+
+    # Identify page headers and footers and remove them
+    pdf_document_tibble <- pdf_document_tibble %>%
+      group_by(pageNumbers) %>%
+      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
+      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
+      ungroup()
+
+    ## Identify front matter and remove it
+    # Primarily identify the start of talking based on the first occurence of 'Mr SPEAKER'. 
+    # It seems pretty common, but there are some misses (e.g. 1991-01-22). 
+    # Use various backups
+    pdf_document_tibble <- pdf_document_tibble %>%
+      mutate(
+        firstSpeakerRow = str_detect(text, "SPEAKER"),
+        firstPresidentRow = str_detect(text, "PRESIDENT"),
+        firstJointHouseRow = str_detect(text, "JOINT HOUSE"),
+        firstTookTheChairRow = str_detect(text, "took the chair"),
+        firstTheChairAtRow = str_detect(text, "the chair at")
+      )
+    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
+    pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == FALSE] <- NA
+    pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == FALSE] <- NA
+    pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == FALSE] <- NA
+    pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == FALSE] <- NA
+
+    # Get the row and corresponding page and then filter to only pages from that page
+    row_of_first_SPEAKER <-
+      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
+    row_of_first_PRESIDENT <-
+      pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == TRUE] %>% which() %>% first()
+    row_of_first_JOINTHOUSE <-
+      pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == TRUE] %>% which() %>% first()
+    row_of_first_TookTheChair <-
+      pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == TRUE] %>% which() %>% first()
+    row_of_first_TheChairAt <-
+      pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == TRUE] %>% which() %>% first()
+
+    first_page_of_interest_SPEAKER <-
+      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
+    first_page_of_interest_PRESIDENT <-
+      pdf_document_tibble[row_of_first_PRESIDENT, "pageNumbers"] %>% as.integer()
+    first_page_of_interest_JOINTHOUSE <-
+      pdf_document_tibble[row_of_first_JOINTHOUSE, "pageNumbers"] %>% as.integer()
+    first_page_of_interest_TookTheChair <-
+      pdf_document_tibble[row_of_first_TookTheChair, "pageNumbers"] %>% as.integer()
+    first_page_of_interest_TheChairAt <-
+      pdf_document_tibble[row_of_first_TheChairAt, "pageNumbers"] %>% as.integer()
+
+    first_page_of_interest_JOINTHOUSE <-
+      (first_page_of_interest_JOINTHOUSE + 1)  %>% as.integer()
+
+    filter_from_here <-
+      case_when(
+        !is.na(first_page_of_interest_TookTheChair) ~ first_page_of_interest_TookTheChair,
+        !is.na(first_page_of_interest_TheChairAt) ~ first_page_of_interest_TheChairAt,
+        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER,
+        !is.na(first_page_of_interest_PRESIDENT) ~ first_page_of_interest_PRESIDENT,
+        TRUE ~ first_page_of_interest_JOINTHOUSE
+      )
+
+    pdf_document_tibble <- pdf_document_tibble %>%
+      filter(pageNumbers >= filter_from_here) %>%
+      select(-firstSpeakerRow,
+             -firstPresidentRow,
+             -firstJointHouseRow,
+             -firstTookTheChairRow,
+             -firstTheChairAtRow)
+
+    # Save file
+    write_csv(pdf_document_tibble, name_of_output_csv_file)
+    # Helpful to know where you're up to
+    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
+  }
+
+#### Walk through the lists and parse the PDFs ####
+# Avoid errors
+safely_get_text_from_PDFs <- safely(get_text_from_PDFs)
+
+tic("Furrr walk2 stringr")
+future_walk2(file_names,
+             save_names,
+             ~ safely_get_text_from_PDFs(.x, .y),
+             .progress = TRUE)
+toc()
+
+```
+
+UP TO HERE
+
+**[TBD].**
+
+\newpage
+
+## Stopwords over time {#stopwordsgraph}
+Insert the graph of stop words over time.
+
+\newpage
+
+# Topic modelling example and details {#LDAexample}
+
+## Overview and example
 As applied to Hansard, LDA considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.
@@
 To choose the terms used in each document, terms are picked from each topic in the appropriate proportion.
-Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrate an example with five topics, two documents, and ten terms.
+
+As an example, Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) illustrate a smaller application with five topics, two documents, and ten terms.
+In this case, the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
+
+```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
+
+tibble(
+  Topics = rep(c("1", "2", "3", "4", "5"), 2),
+  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
+  Document = c(rep("Document 1", 5), rep("Document 2", 5))
+  ) %>%
+  ggplot(aes(Topics, Probability, colour = Document)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip()  +
+  scale_colour_viridis_d()
+
+```
+
+For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
+
+```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
+tibble(
+  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
+  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
+  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
+  ) %>%
+  ggplot(aes(Terms, Probability, colour = Topics)) +
+  geom_point() +
+  theme_classic() +
+  coord_flip() +
+  scale_colour_viridis_d()
+
+```
+
+\newpage
+
+## Document generation process
 
@@
 
-Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior.
-A summary of these approaches is provided in Appendix \@ref(LDAposteriorestimation).
-The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
-If there is a strong reason for a particular number, then this can be used.
-Otherwise, one way to choose an appropriate number is to use cross validation.
-
-One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
-It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
-Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-This is the Correlated Topic Model, described in the next section.
-
-## Correlated Topic Model
-As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
-Correlation between topics is neither modelled nor accounted for by LDA, but in reality often topics are related.
-For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
-The models are very similar, and the key difference is the underlying distributions that are drawn from.
-
-As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is just slightly modified.
-Rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
-
-$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
-That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
-This distribution can incorporate a covariance structure across the topics.
-The remainder of the steps of the document generating process are identical to LDA.
-
-However, the replacement of the Dirichlet distribution with the logistic multivariate Normal distribution adds a level of computational complexity to CTM.
-The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
-@BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
-CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
-The main difference is to add a covariate to $\mu$ which allows consideration of additional information.
-
-<!-- The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
-For instance, we generally have some information about the author and the date that a document was created.
-In the case of Hansard, we know who was speaking and the date they spoke.
-The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
-That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
--->
-
-<!-- The STM is set-up to include metadata to do with prevalence and content.
-Prevalence relates to the topic proportions in each document.
-For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
-Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
-The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate.
-For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
-Content relates to the words that make up each topic.
-For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
-STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
--->
-
-<!-- As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM: -->
-
-<!-- 1.
-As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
-In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3): -->
-<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$ -->
-
-<!-- 2.
-To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
-Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$: -->
-<!-- $$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$ -->
-
-<!-- 3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$: -->
-<!--     a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics. -->
-<!--     b. Randomly choose a term from the topic-specific multinomial distribution over terms. -->
-
-<!-- We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
-We consider both topic prevalence and content to be functions of time.
-The choice of the number of topics to use in the model is a situation-specific compromise.
-We use a standard diagnostic approach to decide on 80 **[UPDATE]** topics.
-More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
--->
-
-Figure \@ref(fig:exampletopics) illustrates a CTM output based on a five per cent sample from the Australian House of Representatives between 1901 and 2017.
-It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
-
-```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-# knitr::include_graphics("../../figures/topics_example.pdf")
-```
-
-## Analysis model
-
-<!-- **[Actually, maybe this whole paragraph not needed?]** There are many ways to consider the effect of events.
-One is to summarise the topic proportions by each event and then run multinomial tests for whether the groups are different, although this does not take full advantage of the frequency of our data.
-Another is to consider a variant of multinomial logistic regression, but then events would be constrained to have an effect in certain ways.
-An autoregressive moving average (ARMA) model could be used to test for structural breaks, but **[something]**.
-Or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model, but **[something]**.
--->
-
-The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
-The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
-But with 40 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
-
-One option for relating the topic distributions to events would be to use the Structural Topic Model (STM) of @RobertsStewartAiroldi2016.
-The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
-For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the government or election period, may affect the topics within that document.
-The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
-The assumption that there is some document generation process is the same as in LDA, it is just that this process now includes metadata.
-
-More specifically, consider a matrix of covariates.
-$X_d$, where each column relates to a different covariate or metadata aspect, and each row refers to a document.
-Then a cell has the value of each covariate for a particular document.
-Similar to the CTM, the STM assumes the topics within a document $\theta_d$ are a draw from a logistic Normal distribution with mean $\mu$.
-However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$:
-
-$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
-
-Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
-For instance, one covariate could be the government $g$ that was in power during the time corresponding to document $d$.
-However, the STM covariate framework has several limitations in terms of our goal to assess the relationship between topics and events:
-
-- There is no way of specifying more complicated auto-correlated functional forms of the effects of events over time.
-For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
-In the STM framework, it is possible to specify a constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
-- There is no way to implement partial pooling across groups of similar documents.
-The STM framework assumes that  documents are independently and identically distributed, conditional on the model covariates.
-However, it could be expected that topic distributions within a particular government, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
-To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
-- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
-For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
-Ideally, we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
-
-To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in governments and elections.
-This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
-
-Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
-Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM.
-We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
-
-The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
-Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
-
-$$
-\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
-$$
-where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
-This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
-
-The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
-The mean parameters $\mu_{s,p}$ are modelled on the log scale as
-
-$$
-\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
-$$
-where:
-
-- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
-- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
-- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
-- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
-
-The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
-$$
-\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)
-$$
-
-The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
-In particular, we model this as an AR(1) in $d$:
-
-$$
-\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
-$$
-One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
-This allows us to identify differences between government and election effects even when there is a one-term government.
-The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
-
-$$
-\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100)
-$$
-$$
-\rho_{e[s],p} \sim \mbox{Uniform}(0,1)
-$$
-We model the underlying time trend in topics using splines regression.
-The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
-The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
-We place knot points every five sitting periods as this is the average length of time for a government to sit.
-Non-informative priors are placed on the splines coefficients:
-$$
-\beta_{p,k} \sim \mbox{Normal}(0, 100)
-$$
-
-Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
-This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
-In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{s,p}$ values are modelled as:
-
-$$
-\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
-$$
-
-The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
-If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
-Non-informative priors are placed on the variance parameters:
-
-$$
-\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
-$$
-
-We run the model in JAGS using the \texttt{rjags} package of @Plummer2018.
-
-<!-- __[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __ -->
-
-<!-- RA STUFF: -->
-
-<!-- The full model is: -->
-
-<!-- \begin{align} -->
-<!-- \gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ -->
-<!-- \log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\ -->
-<!-- \alpha_{s1} &= 0 (\#eq:zeroconstraint)\\ -->
-<!-- \alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\ -->
-<!-- \delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\ -->
-<!-- \sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance) -->
-<!-- \end{align} -->
-
-<!-- **[Does the variance parameter used in Equation 4 need to be specified too?]** -->
-
-<!-- Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
-This is considered as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
-In a sense, $\mu_{stp}$ will be mean topic distributions over whatever time period is of interest.
--->
-
-<!-- Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
-These are themselves parameters.
-The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
--->
-
-<!-- Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
-Equation \@ref(eq:alphasp) shows how we consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **[SOMETHING]** and a variance that depends on **[SOMETHING ELSE]**.
-Similarly, Equation \@ref(eq:deltasp) show how we model $\delta_{stp}$  as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution in Equation \@ref(eq:randomwalkvariance), that is, a random walk around each intercept.
--->
-
-<!-- **[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]** -->
-
-<!-- We currently consider events in two ways.
-The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
-This illustrates the differences between the topics.
-The second is by including incrementing variables in the prevalence metadata This groups each day by events and we can then conduct significance tests.
-Unfortunately both of these do not consider short-term effects.
--->
-
-<!-- **[Use tf-idf between them as illustrative instead? Use that other measure of difference?]** -->
-
-<!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics. -->
-
-<!-- Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
-It will be higher for words that are rarely used across all documents, but commonly used in a document.
-For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
-However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
--->
-
-<!-- When we consider events using tf-idf, we gather terms from more than one day.
-We define groups of days that are roughly analogous to sitting periods.
-If there is more than a week between a day then we define a new group, otherwise the day is in the existing group.
-We use various measures **(Text2vec R package has some?
-or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
--->
-
-# Results
-
-Firstly, we describe the results of the CTM approach, which defined 40 unique topics over the period 1901-2017.
-We then describe the results of the Bayesian analysis model, which identified governments, elections and other events that were associated with a change in the topics discussed.
-
-## Topic modelling
-
-We applied the CTM approach discussed in Section 3.2 on the processed Hansard text database outlined in Section 2.
-The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
-
-The remainder of the results refer to a topic model that had 40 distinct topics defined.
-The choice of 40 topics was made as a trade-off between semantic coherence and exclusivity with 40 topics performing better on both measures than 20.
-Measures such as residuals and held-out likelihood suggest a larger number of topics would be more appropriate.
-See Appendix \@ref(selecttopicnumber) for these diagnostics.
-
-Table \@ref(tab:topwords) lists the top five words associated with each of the forty topics.
-The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
-Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.
-
-```{r topwords, echo = FALSE, results = 'asis'}
-
-top_words %>% 
-  kable(booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
-  kable_styling(font_size = 8, latex_options = c("repeat_header"))
-
-```
-
-## Analysis model
-
-We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussion in Section 3.3, the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
-
-There are several outputs of interest from this modelling stage.
-For example, the model provides estimates of topic prevalence by each sitting period.
-This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
-For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
-
-```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
-knitr::include_graphics("../../figures/war_stack.pdf")
-```
-
-One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
-Political events are those related to a change of government or an election.
-As Australia has a parliamentary system, it is possible for the government to change without an election.
-We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
-If a person was prime minister more than once then these are considered separately.
-
-As detailed in Section 3.3, the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
-We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.
-When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
-
-We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults).
-These tables focus on elections and governments that were different to the ones that preceded them.
-
-```{r electionsresults, echo = FALSE, results = 'asis'}
-
-elections_results %>%
-  kable(booktabs = T, caption = "Significant elections, and neighours") %>%
-  kable_styling(font_size = 10)
-
-```
-
-```{r governmentsresults, echo = FALSE, results = 'asis'}
-
-governments_results %>%
-  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
-  kable_styling(font_size = 10)
-
-```
-
-In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
-In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
-The error bars represent 95 per cent Bayesian credible intervals.
-The topics that we have focused on here are:
-12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
-
-```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics.", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_gov.pdf")
-```
-
-```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election.pdf")
-```
-
-Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
-The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
-Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.
-
-We estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
-The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
-This approach means that the model generates dates that are interesting without us having to specify interesting dates.
-
-More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
-Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
-
-```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
-
-key_events_results %>%
-  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
-  kable_styling(font_size = 10)
-
-```
-
-<!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
-In general, the estimates of standard deviation are increasing over time, suggesting that discussed topics are more variable in more recent election periods compared to historical periods.
--->
-
-<!-- ```{r sigmaelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'} -->
-<!-- knitr::include_graphics("../../figures/sigma.pdf") -->
-<!-- ``` -->
-
-# Discussion
-Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
-However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
-The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
-To a certain extent this is likely tied up with changes due to World War I.
-
-The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
-The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
-Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
-1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
-
-The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
-The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
-There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
-Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
-The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
-
-There were six elections within the second Menzies Government.
-However we do not find that any of those elections was associated with a significant change in the topics discussed.
-In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
-
-The Menzies Government was succeeded by the Holt Government in January 1966.
-This is an example where there was a change in government without an election, as the next election only happened in November 1966.
-We find that the Holt Government is significantly different to the Menzies Government.
-In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
-
-```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election-differences.pdf")
-```
-
-The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
-
-The Howard Government is interesting because of the significant differences between elections.
-For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
-
-To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
-However the change in 1998 and 2004 is more unexpected.
-Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
-
-One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
-The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
-For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
-It also appropriately identifies some of other key events that we were interested in.
-However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
-Further work is needed to improve this approach.
-For instance, our approach may not be appropriately considering step-changes.
-
-# Conclusion
-In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
-We download and parse PDFs of Hansard to create a new dataset of text.
-We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
-In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
-We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
-
-By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia.
-However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
-
-Using text as data allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify associations and patterns that may otherwise be overlooked.
-That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies.
-For instance, the use of topic models is problematic because of the need to interpret the topics, which at can sometimes feel like interpreting hieroglyphics.
-This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
-Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
-For instance, selecting stop words for removal and which word to merge because of common co-location has an impact on the topics.
-Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
-One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches.
-As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could take that approach.
-
-In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model.
-Firstly, we are assuming that the effect of a particular government is constant across the whole period.
-In addition, we assume that the effect of elections is monotonically decreasing across days since election.
-In future work we will investigate different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.
-
-The way that we identify unusual periods could also be improved.
-We defined sitting periods in a constant fashion across the whole dataset time frame, but the nature of how long parliaments sit for has most likely changed.
-In addition, more work needs to be done on how to identify outlying events.
-For example, it is not clear if an important event that occurs outside a sitting period would be identified.
-And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such specific days are not identified as significantly outlying.
-
-Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model.
-However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
-Future methodological work will focus on how to combine these two modelling steps by extending the STM approach into a more flexible framework.
-
-Watching our politicians at work can sometimes be a little disheartening.
-It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there.
-Nonetheless, our work suggests that reasonable debate of important topics does occur in parliament.
-It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
-However, we do find that since the 1980s differences between government and election periods are greater than they used to be.
-It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.
-
-<!-- What could happen if we had longer terms. Eg GST needed multiple generations of politicians but carbon tax couldn’t because it was one generation. -->
+Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior. A summary of these approaches is provided next.
 
 \newpage
-
-# (APPENDIX) Appendix {-}
-
-# Hansard details
-
-## Example Hansard page {#examplehansardpage}
-
-```{r asdf, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
-knitr::include_graphics("../../figures/example_hansard_page.png")
-```
-
-\newpage
-
-## Summary statistics {#hansardsummarystatistics}
-
-The number of sitting days in a year varies considerably.
-The highest in the House of Representatives was 122 days in 1904, followed by 113 days in 1901 and 1920.
-The year with the most sitting days in the Senate was 1902 with 93 days, followed by 1989 with 92 days, and 1986 with 86 days (Figure \@ref(fig:countsbyyear)).
-
-```{r countsbyyear, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
-knitr::include_graphics("../../figures/counts_by_year.pdf")
-```
-
-Until the 1950s the House of Representatives tended to have more sitting days than the Senate.
-It was then similar, before the Senate had more days in the 1980s and 1990s.
-Since the 2000s the House of Representatives again has tended to have more sitting days than the Senate.
-
-These counts of the number of sitting days are based on available PDFs.
-For this reason the counts may be slightly different to other counts.
-An example of one known issue of this type is detailed in the next section.
-
-\newpage
-
-## Compared with parliamentary website {#knownhansardissues}
-The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.
-
-[^parliamentarywebsitelink]: As at 5 November, the website was available at: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear.
-
-In general the number of sitting days on the parliamentary website summary table is similar to the number of PDFs that we have although it does identify a few particularly concerning years (Figure \@ref(fig:differencesbyyear)).
-
-```{r differencesbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
-knitr::include_graphics("../../figures/differences_by_year.pdf")
-```
-
-When the difference is positive, it means that in that year we have fewer PDFs than the parliamentary website claims.
-For instance, 5 could mean that the parliamentary website claimed there were 100 days, but we only had PDFs for 95 days.
-Similarly, when the difference is negative then we have more PDFs than the parliamentary website claims there were sitting days.
-
-The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer.
-
-The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
-1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09, .
-
-There are two unaccounted for differences in 2006, one unaccounted for difference in 2001.
-
-The Parliament website is missing the Hansard PDFs for the following dates in the House of Representatives: 
-1985-08-23,
-1992-09-10,
-1996-12-13,
-2002-05-14,
-2000-10-12, and
-2000-06-29.
-
-There is one unaccounted for differences in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012
-
-In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....
-
-Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.
-
-\newpage
-
-## Example Hansard PDF to text record workflow {#hansardworkflow}
-The exact scripts that we use are too long to provide here but are available on request.
-Instead here we provide shorterned scripts for the workflow to convert the PDFs to usable text datasets that may be a useful starting point for other researchers.
-The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
-The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014.
-The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.
-
-The first step is scrape the websites for the PDFs.
-
-```{r scrapingexample, echo=TRUE, eval = FALSE}
-library(purrr)
-library(tidyverse)
-
-# Create lists of URLs to scrape and file names to save the PDF as
-data_to_scrape <- read_csv("csv_of_address_to_visit_and_save_names.csv")
-# Pull out the two pieces
-address_to_visit <- data_to_scrape$URL
-save_name <- data_to_scrape$file_name
-# Add a containing folder to the save_names
-save_name <- paste0("pdfs/", save_name)
-# Create that containing folder if necessary
-dir.create("pdfs")
-
-# The function that will visit address_to_visit and save to save_name file
-visit_address_and_save_PDF <-
-  function(name_of_address_to_visit,
-           name_of_where_to_save) {
-    # Do the actual downloading of the PDF
-    download.file(name_of_address_to_visit, name_of_where_to_save)
-    # Helpful so that you know progress when running it on all the records
-    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
-    # Space out your requests so you don't overwhelm the website
-    Sys.sleep(sample(15:30, 1)) 
-  }
-
-# Make the function more resistent to issues
-safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
-
-# Walk through the lists and get the PDFs
-walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
-```
-
-The next step is...
-
-UP TO HERE
-
-**[TBD].**
-
-\newpage
-
-## Stopwords over time {#stopwordsgraph}
-**[TBD].** Insert graph of stop words over time.
-
-\newpage
-
-# Topic modelling example and details
-## Examples {#LDAexample}
-For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).
-
-```{r topicsoverdocuments, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over topics for two documents", fig.height = 4}
-
-tibble(
-  Topics = rep(c("1", "2", "3", "4", "5"), 2),
-  Probability = c(c(0.40, 0.40, 0.1, 0.05, 0.05), c(0.01, 0.04, 0.35, 0.20, 0.4)),
-  Document = c(rep("Document 1", 5), rep("Document 2", 5))
-  ) %>%
-  ggplot(aes(Topics, Probability, colour = Document)) +
-  geom_point() +
-  theme_classic() +
-  coord_flip()  +
-  scale_colour_viridis_d()
-
-```
-
-For instance, if there were ten terms, then one topic could be defined by giving more weight to terms related to immigration; and some other topic may give more weight to terms related to the economy (Figure \@ref(fig:topicsoverterms)).
-
-```{r topicsoverterms, cache = TRUE, echo=FALSE, fig.cap = "Probability distributions over terms", fig.height = 4}
-tibble(
-  Terms = rep(c("migration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"), 2),
-  Probability = c(c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2), c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)),
-  Topics = c(rep("Topic 1", 10), rep("Topic 2", 10))
-  ) %>%
-  ggplot(aes(Terms, Probability, colour = Topics)) +
-  geom_point() +
-  theme_classic() +
-  coord_flip() +
-  scale_colour_viridis_d()
-
-```
 
@@
 The initial random allocation of topics means that the results of early passes through the corpus of document are poor, but given enough time the algorithm converges to an appropriate estimate.
+
+The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
+If there is a strong reason for a particular number, then this can be used.
+Otherwise, one way to choose an appropriate number is to use cross validation.
+More detail on this process is provided in the next section.
 

### 2018-11-11 outputs/docs/events/paper.Rmd
Update first part of paper

@@
 title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
-thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
 We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library.
@@
   affiliation: Australian National University
-abstract: "We systematically analyse how parliamentary discussion changes in response to elections and changed governments in Australian history.
+abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments.
 We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
 To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: changes in government tend be associated with topic changes even when the party in power does not change; elections that do not result in a change in government are rarely associated with topic changes; economic events, such as financial crises, have less significant effects than other events such as terrorist attacks; and the effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
-Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
-keywords: "text, politics, Australia, unsupervised machine learning, Bayesian model."
+We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes.
+The residuals of our model suggest that economic events, such as financial crises, have less significant effects than other events such as terrorist attacks although this is partly due to the construction of our model.
+The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
+This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
+keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 We have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
-Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case, remove numbers and punctuation, join commonly co-located words, and remove stop words.
-
-We systematically analyse the text using two main statistical techniques.
-To reduce the dimensionality of our dataset we first use a topic model that allows correlation between topics.
-We then analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
-These events include: changes in government; elections; and other significant events such as an economic recession or terrorism.
-
-We find: 1) changes in government tend be associated with topic changes even when the party in power does not change.
+Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.
+
+We systematically analyse the text in two stages, each of which takes advantage of a different statistical technique.
+First, to reduce the dimensionality of our dataset we use a topic model that allows correlation between topics.
+Second, we analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
+We explicitly consider two types of events: changes in government and elections.
+The residuals of our model allow us to explore the effect of other significant events such as an economic recession or terrorism.
+
+We find that: firstly changes in government tend be associated with topic changes even when the party in power does not change.
 For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
-2) As expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
-3) Economic events, such as financial crises, have less significant effects than other events such as terrorism.
+Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
+Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.
 
@@
 
-Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to more traditional methods, rather than requiring separate analysis.
-This literature sits across and draws from various historically-separate disciplines including economic history, political science, and applied statistics.
+Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to statistical methods, rather than requiring separate analysis.
+This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
 We contribute to this literature in terms of both data and methods.
-From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
+From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
 From a methods perspective, our analysis model has several advantages over existing methods.
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this approach to only increase.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this quantitative social sciences approach to text to only increase and we expect the data and methods in our paper will be extended by other researchers in a variety of ways.
 
@@
 
-The recent digitisation of the Canadian Hansard, @BeelenEtc2017, allowed @RheaultCochran2018 to examine ideology and party polarisation in Britain and Canada.
-In the UK, @Duthie2016 analysed Hansard records to examine which politicians made supportive or aggressive statements toward other politicians between 1979 and 1990 and @PetersonSpirling2018 examined polarisation.
-And as digitisation methods improve older UK records can be analysed, for instance @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
-In New Zealand, @Curran2017 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
+The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed text analysis of Canadian parliament records.
+For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada.
+A digitised version of the UK Hansard has been available for some time and there has been much text analysis of it.
+For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians and @PetersonSpirling2018 examined polarisation.
+One exciting aspect of research using the UK Hansard has been linking text records with other datasets.
+For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties.
+Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
+In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
 And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
@@
 @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
-And @Salisbury2011 examines unparliamentary behaviour.
+And @Salisbury2011 examined unparliamentary behaviour.
 @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups.
-The closest research to ours that we have found is @Boulous2013 who examines parliamentary debate in Australia for the period 1946 to 2012.
+The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia for the period 1946 to 2012.
 
@@
 
-[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website (http://historichansard.net/) that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website -- http://historichansard.net/ -- that can be used to explore Commonwealth Hansard records from 1901 to 1980.
 Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
@@
 We use the official PDF release and the formatting of the Hansard records changes over time.
-We use scripts written in R (@R2018) to convert the PDFs into daily text records.
+We use scripts written in R, @R2018, to convert the PDFs into daily text records.
 An example of the workflow and some reduced-detail scripts are provided in Appendix \@ref(hansardworkflow).
@@
 An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are corrected when they occur more than twice and can be identified.
+These errors are corrected when they can be identified.
 
@@
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
-There are two stages in our analytical process.
-
-We first use the Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
+There are the two stages in our analytical process.
+
+We first use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain estimated topic distributions over time.
 We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
-We then formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
-
-In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
-More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(LDAexample).
+The approach that we use to analyse these is to formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
+
+In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model of @Blei2003latent, before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
+Background detail on topic modelling is available in Appendix \@ref(LDAexample).
 
@@
 
-Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 does this by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate.
+Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 addresses this problem by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate.
 This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
@@
 A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions.
-The topics are not specified *ex ante*; they are an outcome of the method.
-In this sense, this approach can be considered unsupervised machine learning.
+The topics are not specified *ex ante*; they are an outcome of the method, and it is in this sense that this approach can be considered unsupervised machine learning.
 Terms are not necessarily unique to a particular topic, and a document could be about more than one topic.
@@
 This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.
-More detail on how LDA works is available in Appendix \@ref(LDAexample).
+More detail on how topic modelling works is available in Appendix \@ref(LDAexample).
 
@@
 As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is just slightly modified.
-Rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
-
-$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
+The document generation process of @Blei2003latent, discussed in Appendix \@ref(LDAdocgenprocess), is just slightly modified.
+Specifically, rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in Step 2 of the LDA document generation process detailed in Appendix \@ref(LDAdocgenprocess), CTM assumes:
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma).$$
 That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
 This distribution can incorporate a covariance structure across the topics.
-The remainder of the steps of the document generating process are identical to LDA.
+The remainder of the steps of the document generating process are pretty much the same as LDA.
 
@@
 It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
+**[ADD GRAPH BACK.]**
 
@@
 The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
-But with 80 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
+But with many topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
 
@@
 However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$:
-
-$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma).$$
 
 Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
-For instance, one covariate could be the government $g$ that was in power during the time corresponding to document $d$.
+For instance, one covariate could be the government, $g$, that was in power during the time corresponding to document, $d$.
 However, the STM covariate framework has several limitations in terms of our goal to assess the relationship between topics and events:
 
-- There is no way of specifying more complicated auto-correlated functional forms of the effects of events over time.
+1.
+There is no way of specifying more complicated auto-correlated functional forms of the effects of events over time.
 For example, we believe that the effect of an election would peak at the time of the election, then gradually decay as a function of days since election.
 In the STM framework, it is possible to specify a constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
-- There is no way to implement partial pooling across groups of similar documents.
+2.
+There is no way to implement partial pooling across groups of similar documents.
 The STM framework assumes that  documents are independently and identically distributed, conditional on the model covariates.
@@
 To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
-- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+3.
+There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
 For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
-Ideally, we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
+Instead we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
 
@@
 
-Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$.
-Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM.
-We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$.
+Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM.
+We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
 Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
+**[UPDATE.]**
 
@@
 where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
-This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must equal 1.
+This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must be one.
 
 The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
-The mean parameters $\mu_{s,p}$ are modelled on the log scale as
-
+The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
 $$
@@
 $$
-where:
-
-- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
-- $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
-- $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and
-- $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
-
-The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
-$$
-\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)
-$$
-
-The election term $\alpha_{e[s],d,p}$ assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
+where: $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$; $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election; $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
+
+The government term, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
+$$
+\alpha_{g[s],p} \sim \mbox{Normal}(0, 100).
+$$
+
+The election term, $\alpha_{e[s],d,p}$, assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
 In particular, we model this as an AR(1) in $d$:
-
-$$
-\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}
-$$
+$$
+\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}.
+$$
+
 One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
@@
 The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
-
-$$
-\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100)
-$$
-$$
-\rho_{e[s],p} \sim \mbox{Uniform}(0,1)
-$$
+$$
+\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100);\mbox{ and}\\
+\rho_{e[s],p} \sim \mbox{Uniform}(0,1).
+$$
+
 We model the underlying time trend in topics using splines regression.
@@
 $$
-\beta_{p,k} \sim \mbox{Normal}(0, 100)
+\beta_{p,k} \sim \mbox{Normal}(0, 100).
 $$
@@
 The $\delta_{s,p}$ values are modelled as:
-
-$$
-\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2)
+$$
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2).
 $$
@@
 Non-informative priors are placed on the variance parameters:
-
-$$
-\sigma_{e[s],p} \sim \mbox{Uniform}(0,3)
+$$
+\sigma_{e[s],p} \sim \mbox{Uniform}(0,3).
 $$
@@
 
-Firstly, we describe the results of the CTM approach, which defined 40 unique topics over the period 1901-2017.
+Firstly, we describe the results of the CTM approach, which defined 80 unique topics over the period 1901-2017.
 We then describe the results of the Bayesian analysis model, which identified governments, elections and other events that were associated with a change in the topics discussed.
@@
 The remainder of the results refer to a topic model that had 80 distinct topics defined.
-The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model and understandable for us.
+The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model.
 The diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).
@@
 The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
-Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.
-**[UPDATE THAT.]**
+Note that some topics seem to somewhat overlap with their content: for instance, topics 4, 26, 28, 30 and 66 all relate to war and conflict.
 
@@
 
-## Document generation process
+## Document generation process  {#LDAdocgenprocess}
 

### 2018-11-12 outputs/docs/events/paper.Rmd
Update paper

@@
 
-# Data
+# Data  {#hansarddata}
 
@@
 
-## Correlated Topic Model
+## Correlated Topic Model  {#correlatedtopicmodelsection}
 As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
@@
 
-Figure \@ref(fig:exampletopics) illustrates a CTM output based on a five per cent sample from the Australian House of Representatives between 1901 and 2017.
+Figure \@ref(fig:exampletopics) illustrates a CTM output based on a sample from the Australian House of Representatives between 1901 and 2017.
 It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
-**[ADD GRAPH BACK.]**
-
-```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
-# knitr::include_graphics("../../figures/topics_example.pdf")
-```
-
-## Analysis model
+
+```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_example.png")
+```
+
+## Analysis model  {#analysismodelexplanation}
 
@@
 ## Topic modelling
-
-We applied the CTM approach discussed in Section 3.2 on the processed Hansard text database outlined in Section 2.
+We applied the CTM approach discussed in Section \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata).
 The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
@@
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussion in Section 3.3, the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+As discussion in Section \@ref(analysismodelexplanation), the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
 
@@
 For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+**[UPDATE ME]**
 
@@
 
-As detailed in Section 3.3, the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
+As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
 We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.

### 2018-11-13 outputs/docs/events/paper.Rmd
Update sig electionand governemnts
changes up to results section

@@
 We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes.
-The residuals of our model suggest that economic events, such as financial crises, have less significant effects than other events such as terrorist attacks although this is partly due to the construction of our model.
 The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
@@
 We explicitly consider two types of events: changes in government and elections.
-The residuals of our model allow us to explore the effect of other significant events such as an economic recession or terrorism.
+After taking into consideration these effects, we can then explore the effect of other significant events such as an economic recession or terrorism.
 
@@
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
-There are the two stages in our analytical process.
-
-We first use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain estimated topic distributions over time.
-We consider these topic distributions as reduced dimension inputs that can be analysed within another model.
-The approach that we use to analyse these is to formulate a Bayesian hierarchical Dirichlet model to assess changes in the topic distributions in relation to events of interest.
-
-In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model of @Blei2003latent, before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
+
+We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
+We consider these topic distributions as inputs that can be analysed within another model.
+Thus, the second modeling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.
+
+In the following section, we briefly describe the topic modelling approach, before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics.
 Background detail on topic modelling is available in Appendix \@ref(LDAexample).
 
-<!-- The models that we use in this paper are the Structural Topic Model (STM) as implemented by the \texttt{stm} R package of @RobertsStewartAiroldiRPackage, and Bayesian hierarchical Dirichlet analysis model.
-In a similar way to @MuellerRauh2018, we use topics as an input to another model, in our case to analyse the effect of various events.
--->
-
-<!-- The basis of the STM is the Latent Dirichlet Allocation (LDA) model of @Blei2003latent.
-In this section we provide a brief overview of both the LDA model and the STM.
-We consider the outputs of the topic model as reduced dimension inputs that can be analysed within another model.
-We then discuss the Bayesian hierarchical Dirichlet analysis model that we use for this purpose.
--->
-
-## Latent Dirichlet Allocation
+## Overview of topic modeling
 Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics.
@@
 This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
-In exchange for some reduction in the reasonableness of the categorisation, the LDA method of @Blei2003latent is able to provide consistent categorisation of the topics discussed in Hansard for large text collections.
+
+In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modeling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
+In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
 
@@
 
-One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
+<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
 It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
-Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-This is the Correlated Topic Model, described in the next section.
-
-## Correlated Topic Model  {#correlatedtopicmodelsection}
-As mentioned in the previous section, one of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
-Correlation between topics is neither modelled nor accounted for by LDA, but in reality often topics are related.
+-->
+
+One notable limitation of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
+However, in reality topics are often related.
 For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
-The models are very similar, and the key difference is the underlying distributions that are drawn from.
-
-As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent, discussed in Appendix \@ref(LDAdocgenprocess), is just slightly modified.
-Specifically, rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in Step 2 of the LDA document generation process detailed in Appendix \@ref(LDAdocgenprocess), CTM assumes:
-$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma).$$
-That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
-This distribution can incorporate a covariance structure across the topics.
-The remainder of the steps of the document generating process are pretty much the same as LDA.
-
-However, the replacement of the Dirichlet distribution with the logistic multivariate Normal distribution adds a level of computational complexity to CTM.
-The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
-@BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
-CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
-The main difference is to add a covariate to $\mu$ which allows consideration of additional information.
-
-<!-- The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
-For instance, we generally have some information about the author and the date that a document was created.
-In the case of Hansard, we know who was speaking and the date they spoke.
-The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
-That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
--->
-
-<!-- The STM is set-up to include metadata to do with prevalence and content.
-Prevalence relates to the topic proportions in each document.
-For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
-Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
-The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate.
-For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
-Content relates to the words that make up each topic.
-For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
-STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
--->
-
-<!-- As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
-The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM: -->
-
-<!-- 1.
-As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
-In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3): -->
-<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$ -->
-
-<!-- 2.
-To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
-Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$: -->
-<!-- $$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$ -->
-
-<!-- 3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$: -->
-<!--     a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics. -->
-<!--     b. Randomly choose a term from the topic-specific multinomial distribution over terms. -->
-
-<!-- We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
-We consider both topic prevalence and content to be functions of time.
-The choice of the number of topics to use in the model is a situation-specific compromise.
-We use a standard diagnostic approach to decide on 80 **[UPDATE]** topics.
-More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
--->
-
-Figure \@ref(fig:exampletopics) illustrates a CTM output based on a sample from the Australian House of Representatives between 1901 and 2017.
-It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
-
-```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/topics_example.png")
-```
+
+As such, we chose to use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain topic distributions.
+CTM is a slight extension to LDA which allows for correlations between topics.
+More details about CTM can be found in Appendix \@ref(LDAexample).
 
@@
 
-<!-- **[Actually, maybe this whole paragraph not needed?]** There are many ways to consider the effect of events.
-One is to summarise the topic proportions by each event and then run multinomial tests for whether the groups are different, although this does not take full advantage of the frequency of our data.
-Another is to consider a variant of multinomial logistic regression, but then events would be constrained to have an effect in certain ways.
-An autoregressive moving average (ARMA) model could be used to test for structural breaks, but **[something]**.
-Or splines could be fit with specific knot placements and then cross validation used to compare the RSS with a more general splines model, but **[something]**.
--->
-
-The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$.
+The CTM output of interest is the proportion of each topic appearing in each document.
 The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
@@
 
-More specifically, consider a matrix of covariates.
+<!-- More specifically, consider a matrix of covariates.
 $X_d$, where each column relates to a different covariate or metadata aspect, and each row refers to a document.
@@
 Similar to the CTM, the STM assumes the topics within a document $\theta_d$ are a draw from a logistic Normal distribution with mean $\mu$.
-However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$:
-$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma).$$
-
-Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
+However, the STM framework assumes that the mean parameter is a linear function of covariates $X_d$: -->
+<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma).$$ -->
+
+<!-- Using the STM framework with covariates could theoretically allow the relationships between topics and certain types of events to be assessed.
 For instance, one covariate could be the government, $g$, that was in power during the time corresponding to document, $d$.
+-->
+
 However, the STM covariate framework has several limitations in terms of our goal to assess the relationship between topics and events:
@@
 We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
-**[UPDATE.]**
+Using this definition, there are a total of 822 sitting periods over the period 1901 to 2017 inclusive.
 
@@
 
-<!-- __[An illustration of the validity of our analysis model using simulated data is in Appendix \@ref(modeldetailsandsimulation).] __ -->
-
-<!-- RA STUFF: -->
-
-<!-- The full model is: -->
-
-<!-- \begin{align} -->
-<!-- \gamma_{stp} &\sim \mbox{Dirichlet}(\mu_{stp}) (\#eq:distributionforgammas) \\ -->
-<!-- \log \mu_{stp} &= \alpha_{sp} + \delta_{stp} (\#eq:meanforgammas) \\ -->
-<!-- \alpha_{s1} &= 0 (\#eq:zeroconstraint)\\ -->
-<!-- \alpha_{sp} &\sim \mbox{Normal}\left(\eta_{g[s]}, \sigma^2_g\right) \mbox{ for } p>1 (\#eq:alphasp) \\ -->
-<!-- \delta_{s,t,p} &\sim \mbox{Normal}\left(\delta_{s,t-1,p}, \sigma^2_{\delta}\right) (\#eq:deltasp) \\ -->
-<!-- \sigma^2_{\delta} &\sim \mbox{Uniform}(0, 40). (\#eq:randomwalkvariance) -->
-<!-- \end{align} -->
-
-<!-- **[Does the variance parameter used in Equation 4 need to be specified too?]** -->
-
-<!-- Equation \@ref(eq:distributionforgammas) describes the proportion of each day within a sitting period given to a particular topic.
-This is considered as a draw from a Dirichlet distribution parameterised by $\mu_{stp}$.
-In a sense, $\mu_{stp}$ will be mean topic distributions over whatever time period is of interest.
--->
-
-<!-- Equation \@ref(eq:meanforgammas) describes that distribution parameter, $\mu_{stp}$, as the sum of $\alpha_{sp}$, which are sitting period specific topic distributions and mean the model is linear in time for each topic and sitting period, and $\delta_{stp}$, which is a simple time series that allows for a little variation within a sitting period.
-These are themselves parameters.
-The primary aim of the modelling task is to find an appropriate and meaningful functional form for $\mu$.
--->
-
-<!-- Equation \@ref(eq:zeroconstraint) constrains the first intercept to zero for identification purposes.
-Equation \@ref(eq:alphasp) shows how we consider $\alpha_{sp}$ as a draw from a Normal distribution with a mean that depends on **[SOMETHING]** and a variance that depends on **[SOMETHING ELSE]**.
-Similarly, Equation \@ref(eq:deltasp) show how we model $\delta_{stp}$  as a draw from a Normal distribution with a mean that depends on the preceding $\delta$ and some variance which is drawn from the Uniform distribution in Equation \@ref(eq:randomwalkvariance), that is, a random walk around each intercept.
--->
-
-<!-- **[Probably need to add: 1) where does each covariate come into it and how do they interact; 2) how does correlation work; 3) what are the random effects and fixed effects?]** -->
-
-<!-- We currently consider events in two ways.
-The first is graphically, grouping each of the daily topic proportions by the events and isolating the topics.
-This illustrates the differences between the topics.
-The second is by including incrementing variables in the prevalence metadata This groups each day by events and we can then conduct significance tests.
-Unfortunately both of these do not consider short-term effects.
--->
-
-<!-- **[Use tf-idf between them as illustrative instead? Use that other measure of difference?]** -->
-
-<!-- We consider events in two ways. The first is in the change in the word usage before and after events and the second is in changes in the topics. -->
-
-<!-- Differences in word usage can be evaluated using the term frequency-inverse document frequency (tf-idf) measure.
-It will be higher for words that are rarely used across all documents, but commonly used in a document.
-For instance, in Australian parliamentary text records 'the' is commonly used in many documents and so the fact that it is used in any particular document is not usual.
-However, 'aboriginal' is less common across, and so if it was especially prevalent in a particular document that may distinguish that document.
--->
-
-<!-- When we consider events using tf-idf, we gather terms from more than one day.
-We define groups of days that are roughly analogous to sitting periods.
-If there is more than a week between a day then we define a new group, otherwise the day is in the existing group.
-We use various measures **(Text2vec R package has some?
-or some other package)** to define a baseline measure of how different each group is, and then test for whether groups separated by our events are significantly different to this baseline.
--->
-
 # Results
@@
 
+```
+
+Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Australian House of Representatives between 1901 and 2017.
+It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
+The highlighted topics are those related to war and conflict.
+
+```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_example.png")
 ```
@@
 For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
-**[UPDATE ME]**
 
@@
 
+## Correlated Topic Model  {#correlatedtopicmodelsection}
+One of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
+In reality often topics are related.
+For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
+The goal of the CTM [@BleiLafferty2007] is to account for this correlation between topics, in order to produce more realistic and stable topic distributions over time.
+The models are very similar, and the key difference is the underlying distributions that are drawn from.
+
+As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent, discussed in Appendix \@ref(LDAdocgenprocess), is just slightly modified.
+Specifically, rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in Step 2 of the LDA document generation process detailed in Appendix \@ref(LDAdocgenprocess), CTM assumes:
+$$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma).$$
+That is, the main difference of CTM over LDA is that it replaces the assumption of the Dirichlet distribution with a more flexible logistic multivariate Normal distribution.
+This distribution can incorporate a covariance structure across the topics.
+The remainder of the steps of the document generating process are pretty much the same as LDA.
+
+However, the replacement of the Dirichlet distribution with the logistic multivariate Normal distribution adds a level of computational complexity to CTM.
+The posterior distributions of the parameters of interest ($\beta_{1:K}, \theta_{1:D}, z_{1:D, 1:N}$) can no longer be obtained using standard simulation techniques such as Gibbs Sampling.
+@BleiLafferty2007 develop a fast variational inference procedure for estimating the CTM.
+CTM itself has also been extended by @RobertsStewartAiroldi2016 as part of their work on Structural Topic Models.
+The main difference is to add a covariate to $\mu$ which allows consideration of additional information.
+
+<!-- The distinguishing aspect of the Structural Topic Model (STM) of @RobertsStewartAiroldi2016 is that it considers more than just a document's content when constructing topics.
+For instance, we generally have some information about the author and the date that a document was created.
+In the case of Hansard, we know who was speaking and the date they spoke.
+The STM allows this additional information to affect the construction of topics, though influencing either topical prevalence or topical content.
+That said, the assumption that there is some document generation process is the same as the LDA method, it is just that this process now includes metadata.
+-->
+
+<!-- The STM is set-up to include metadata to do with prevalence and content.
+Prevalence relates to the topic proportions in each document.
+For instance, we expect that topics related to the reasons for Federation, such as tariffs and trade, should be more prevalent in those earlier years than later.
+Similarly, we may expect topics to do with terrorism to be more prevalent in recent years.
+The prevalence meta-data for the $d$th document are in $X_d$, which has one column for each covariate.
+For instance, if there were 10 documents and each had a date and an author, then $X$ would be $10\times 2$.
+Content relates to the words that make up each topic.
+For instance, there are changes in the use of language over the period for which we have data, and it would be better for these to not be responsible for defining different topics rather than being part of the same topic.
+STM only allows for one covariate related to content changes, for example, documents could be grouped by year.
+-->
+
+<!-- As with LDA, the process assumed to generate the documents is the key aspect as this will be reversed to estimate the topics.
+The document generation process of @Blei2003latent discussed earlier, is slightly modified by @RobertsStewartAiroldi2016 for the STM: -->
+
+<!-- 1.
+As with LDA, the topic distributions, that is, the proportion of a document dedicated to a topic, for the $d$th document are $\theta_d$, and $\theta$ is a vector with length $D$.
+In contrast to LDA, this is a drawn from a logistic-normal distribution, parameterised such that the mean of that distribution, $\mu$, is affected by a vector of document covariates, $X_d$ (following @RobertsStewartTingley2018, p.3): -->
+<!-- $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$ -->
+
+<!-- 2.
+To decide the distribution over terms for each topic, $\beta_{d,k}$, start with some baseline distribution over the terms, $m$.
+Topic-$k$-specific deviations from this are controlled by $\kappa_k^{(t)}$, deviations due to the document meta-data are controlled by $\kappa_{y_d}^{(c)}$, and the interaction between these two deviations is controlled by  $\kappa_{y_d,k}^{(i)}$: -->
+<!-- $$\beta_{d,k}\propto \mbox{exp}\left(m+\kappa^{(t)}_{k} + \kappa_{y_d}^{(c)} + \kappa_{y_{d}k}^{(i)}\right) $$ -->
+
+<!-- 3. Then if there are $n$ terms in the $d$th document, then to choose the $n$th term, $w_{d,n}$: -->
+<!--     a. Randomly choose a topic for that term from the document-specific multinomial distribution over topics. -->
+<!--     b. Randomly choose a term from the topic-specific multinomial distribution over terms. -->
+
+<!-- We primarily implement the STM on the daily-level parliamentary text data described earlier using the \texttt{stm} R package of @RobertsStewartAiroldiRPackage.
+We consider both topic prevalence and content to be functions of time.
+The choice of the number of topics to use in the model is a situation-specific compromise.
+We use a standard diagnostic approach to decide on 80 **[UPDATE]** topics.
+More detail on this selection process is available in Appendix \@ref(selecttopicnumber).
+-->
+
 <!-- \newpage -->

### 2018-11-13 outputs/docs/events/paper.Rmd
Update Appendix B

@@
 The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
-1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09, .
+1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09.
 
@@
 
-There is one unaccounted for differences in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012
-
-In the Senate, the PDF for 10 August 1917 may be the wrong one? It says it is for 10 Jan 1918 on the cover sheet, but there's not even an entry for 10 Jan 1918...??? Very odd....
+There is one unaccounted for difference in 1920, 1921, 1935, 1942, 1948, 1951, 1991, 2003, 2004, and there are two unaccounted for in 1985 and four unaccounted for in 2012.
+
+In the Senate, the PDF for 10 August 1917 may be the wrong one. It says it is for 10 January 1918 on the cover sheet, but there's not an entry for 10 January 1918.
 
@@
 ```{r scrapingexample, echo=TRUE, eval = FALSE}
-library(purrr)
-library(tidyverse)
-
-# Create lists of URLs to scrape and file names to save the PDF as
-data_to_scrape <- read_csv("csv_of_address_to_visit_and_save_names.csv")
-# Pull out the two pieces
-address_to_visit <- data_to_scrape$URL
-save_name <- data_to_scrape$file_name
-# Add a containing folder to the save_names
-save_name <- paste0("pdfs/", save_name)
-# Create that containing folder if necessary
-dir.create("pdfs")
-
-# The function that will visit address_to_visit and save to save_name file
 visit_address_and_save_PDF <-
@@
   }
-
-# Make the function more resistent to issues
-safe_visit_address_and_save_PDF <- safely(visit_address_and_save_PDF)
-
-# Walk through the lists and get the PDFs
-walk2(address_to_visit, save_name, ~ safe_visit_address_and_save_PDF(.x, .y))
 ```
@@
 ```{r frontmatterexample, echo=TRUE, eval = FALSE}
-library(furrr) # May need the devtools version devtools::install_github("DavisVaughan/furrr")
-library(lubridate)
-library(pdftools)
-library(stringi)
-library(tidyverse)
-library(tictoc)
-library(tm)
-# Set up furrr to use multiple processors
-plan(multiprocess)
-
-# Create the lists of PDFs to read and file names to save text as
-use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
-use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
-
-# Get list of Hansard PDF filenames
-file_names <-
-  list.files(
-    path = use_this_path_to_get_pdfs,
-    pattern = "*.pdf",
-    recursive = TRUE,
-    full.names = TRUE
-  )
-file_names <- file_names %>% sample() # Randomise the order
-# Modify the savenames
-save_names <- file_names %>%
-  str_replace(use_this_path_to_get_pdfs, "") %>%
-  str_replace(".pdf", ".csv")
-save_names <- paste0(use_this_path_to_save_csv_files, save_names)
-
-#### Create the function that will be applied to the files ####
+
 get_text_from_PDFs <-
@@
       separate_rows(pdf_document_tibble, text, sep = "\\n")
-
     # Identify page headers and footers and remove them
@@
       ungroup()
-
     ## Identify front matter and remove it
-    # Primarily identify the start of talking based on the first occurence of 'Mr SPEAKER'. 
-    # It seems pretty common, but there are some misses (e.g. 1991-01-22). 
-    # Use various backups
     pdf_document_tibble <- pdf_document_tibble %>%
       mutate(
-        firstSpeakerRow = str_detect(text, "SPEAKER"),
-        firstPresidentRow = str_detect(text, "PRESIDENT"),
-        firstJointHouseRow = str_detect(text, "JOINT HOUSE"),
-        firstTookTheChairRow = str_detect(text, "took the chair"),
-        firstTheChairAtRow = str_detect(text, "the chair at")
+        firstSpeakerRow = str_detect(text, "SPEAKER")
       )
     pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
-    pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == FALSE] <- NA
-    pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == FALSE] <- NA
-    pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == FALSE] <- NA
-    pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == FALSE] <- NA
-
     # Get the row and corresponding page and then filter to only pages from that page
@@
       pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
-    row_of_first_PRESIDENT <-
-      pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == TRUE] %>% which() %>% first()
-    row_of_first_JOINTHOUSE <-
-      pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == TRUE] %>% which() %>% first()
-    row_of_first_TookTheChair <-
-      pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == TRUE] %>% which() %>% first()
-    row_of_first_TheChairAt <-
-      pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == TRUE] %>% which() %>% first()
-
     first_page_of_interest_SPEAKER <-
       pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
-    first_page_of_interest_PRESIDENT <-
-      pdf_document_tibble[row_of_first_PRESIDENT, "pageNumbers"] %>% as.integer()
-    first_page_of_interest_JOINTHOUSE <-
-      pdf_document_tibble[row_of_first_JOINTHOUSE, "pageNumbers"] %>% as.integer()
-    first_page_of_interest_TookTheChair <-
-      pdf_document_tibble[row_of_first_TookTheChair, "pageNumbers"] %>% as.integer()
-    first_page_of_interest_TheChairAt <-
-      pdf_document_tibble[row_of_first_TheChairAt, "pageNumbers"] %>% as.integer()
-
-    first_page_of_interest_JOINTHOUSE <-
-      (first_page_of_interest_JOINTHOUSE + 1)  %>% as.integer()
-
     filter_from_here <-
       case_when(
-        !is.na(first_page_of_interest_TookTheChair) ~ first_page_of_interest_TookTheChair,
-        !is.na(first_page_of_interest_TheChairAt) ~ first_page_of_interest_TheChairAt,
-        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER,
-        !is.na(first_page_of_interest_PRESIDENT) ~ first_page_of_interest_PRESIDENT,
-        TRUE ~ first_page_of_interest_JOINTHOUSE
+        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER
       )
-
     pdf_document_tibble <- pdf_document_tibble %>%
       filter(pageNumbers >= filter_from_here) %>%
-      select(-firstSpeakerRow,
-             -firstPresidentRow,
-             -firstJointHouseRow,
-             -firstTookTheChairRow,
-             -firstTheChairAtRow)
-
+      select(-firstSpeakerRow)
     # Save file
@@
 
-#### Walk through the lists and parse the PDFs ####
-# Avoid errors
-safely_get_text_from_PDFs <- safely(get_text_from_PDFs)
-
-tic("Furrr walk2 stringr")
-future_walk2(file_names,
-             save_names,
-             ~ safely_get_text_from_PDFs(.x, .y),
-             .progress = TRUE)
-toc()
-
-```
-
-UP TO HERE
-
-**[TBD].**
+```
+
+Then the rows need to be combined:
+```{r combinerows, echo=TRUE, eval = FALSE}
+split_columns <-
+  function(name_of_input_csv_file,
+           name_of_output_csv_file) {
+    # Read in the csv, based on the filename list
+    csv_with_rows_to_combine <-
+      read_csv(name_of_input_csv_file,
+               trim_ws = FALSE,
+               col_types = cols())
+    # Remove any extra whitespace i.e. two or more spaces and spaces at either end. 
+    # Yes, I know that I turned this off in the read_csv, but it's better to be 
+    #explicit because the whitespace is useful sometimes.
+    csv_with_rows_to_combine$text <-
+      str_squish(csv_with_rows_to_combine$text)
+    # Put everything onto one line, which allows us to rejoin words that have been 
+    #split across two lines e.g. Mon- ica
+    csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
+      mutate(text = str_replace_all(text, "-$", "MONICA"))
+    full_days_hansard <- csv_with_rows_to_combine %>%
+      select(-pageNumbers) %>%
+      summarise(text = paste(text, collapse = " ")) %>%
+      mutate(text = str_replace_all(text, "MONICA ", "")) %>%
+      mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - "))
+    rm(csv_with_rows_to_combine)
+    write_csv(full_days_hansard, name_of_output_csv_file)
+    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
+  }
+```
+
+Finally, we can fix the spelling:
+```{r fixspelling, echo=TRUE, eval = FALSE}
+fix_spelling <-
+  function(name_of_input_csv_file,
+           name_of_output_csv_file) {
+    csv_to_clean <-
+      read_csv(name_of_input_csv_file,
+               trim_ws = FALSE,
+               col_types = cols())
+    #Fix the spelling
+    csv_to_clean$text <-
+      stri_replace_all_regex(
+        csv_to_clean$text,
+        "\\b" %s+% fix_wrong_spellings$original %s+% "\\b",
+        fix_wrong_spellings$corrected,
+        vectorize_all = FALSE
+      )
+    # Save file
+    write_csv(csv_to_clean, name_of_output_csv_file)
+    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
+  }
+```
 

### 2018-11-15 outputs/docs/events/paper.Rmd
Update paper

@@
 
-elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
-governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
-keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
-significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
-top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
-
-top_words <- top_words %>% 
+elections <-
+  read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
+
+governments <-
+  read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
+
+keyEvents <-
+  read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
+
+significances <-
+  read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
+
+top_words <-
+  read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols()) %>% 
   rename(Topic = topic, Terms = terms)
 
-hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
-
-elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
-  # filter(Significant %in% c("Yes", "No"))
-  filter(Significant %in% c("Yes"))
-
-governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
+hansard_sources <-
+  read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
+
+elections_results <-
+  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
     filter(Significant %in% c("Yes")) %>%
-  # filter(Significant %in% c("Yes", "No")) %>% 
-  select(-Party, -`Died in Office`)
-
-key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())
+    select(-Significant)
+
+governments_results <-
+  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
+    filter(Significant %in% c("Yes")) %>%
+    select(-Party,-`Died in Office`,-Significant)
+
+key_events_results <-
+  read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols()) %>%
+    select(-Expected)
 
@@
 For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties.
-Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England.
+Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England.
 In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
@@
 We use scripts written in R, @R2018, to convert the PDFs into daily text records.
-An example of the workflow and some reduced-detail scripts are provided in Appendix \@ref(hansardworkflow).
+An example of the workflow and some pseudo-code are provided in Appendix \@ref(hansardworkflow).
 Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
@@
 ## Topic modelling
-We applied the CTM approach discussed in Section \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata).
-The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.
-
-The remainder of the results refer to a topic model that had 80 distinct topics defined.
-The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model.
-The diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).
+We applied the CTM approach discussed in Appendix \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata).
+The main output of interest are the types of topics identified by the model, and the prevalence of each topic for each day of parliamentary discussion.
+
+Our results are for a topic model that had 80 distinct topics.
+With almost 15,000 days and 80 topics, the analysis model is being fit to more than a million observations.
+The choice of 80 topics was made as a trade-off between standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the analysis model to be tractable.
+Those diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).
 
@@
 The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
-Note that some topics seem to somewhat overlap with their content: for instance, topics 4, 26, 28, 30 and 66 all relate to war and conflict.
+There are also some topics that appear to be about procedural or day-to-day, such as Topics 7 or 9.
+Note that, as expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.
 
@@
 The highlighted topics are those related to war and conflict.
+As expected, the two chambers of the Australian Federal Parliament are fairly similar.
 
@@
 knitr::include_graphics("../../figures/topics_example.png")
+
 ```
@@
 ## Analysis model
+
+### Main results
 
@@
 As discussion in Section \@ref(analysismodelexplanation), the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+That is, the topic model outputs are inputs for our analysis model.
 
@@
 This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
-For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+For instance, examining Topics 4, 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
 
@@
 Political events are those related to a change of government or an election.
-As Australia has a parliamentary system, it is possible for the government to change without an election.
-We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
-If a person was prime minister more than once then these are considered separately.
-
-As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$.
-We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects.
+Note that as Australia has a parliamentary system it is possible for the government to change without an election as we define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
+If a person was prime minister more than once then these periods are considered independently.
+
+As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level-effect for each government, $\alpha_g$ and each election, $\alpha_e$.
+We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects.
 When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
@@
 These tables focus on elections and governments that were different to the ones that preceded them.
+Complete lists of elections and governments are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
 
@@
 governments_results %>%
-  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
+  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
   kable_styling(font_size = 10)
@@
 
-In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively.
+In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between governments and elections, respectively.
 In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
 The error bars represent 95 per cent Bayesian credible intervals.
-The topics that we have focused on here are:
-12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.
+We have focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
 
@@
 
-Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
-The full list of events that we consider are detailed in Appendix \@ref(eventdetails).
-Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.
-
-We estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
+### Additional results
+
+Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period.
+We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occured on or before that sitting day.
+For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.
+
+To do this we estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
 The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
 This approach means that the model generates dates that are interesting without us having to specify interesting dates.
-
 More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
@@
 # Discussion
-Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
-However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
-The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
-To a certain extent this is likely tied up with changes due to World War I.
+Of the 36 governments over this period, we find that 20 of them are significantly different to the government that preceded them.
+However, four of these results -- the significance of the Page Government, the First Menzies Government, the Chifley Government and the Abbott Government -- are likely due to the short length of either the government or its predecessor and should be ignored, leaving only 16.
+The earliest of these is the First Fisher Government, the Cook Government and the Third Fisher Government, which were different to the Second Deakin Government, the Second Fisher Government, and the Cook Government, respectively.
+To a certain extent this is likely due to changes due to World War I.
 
 The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
-The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
+The rest of the governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
 Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
@@
 
-The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
+The Second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
 The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
@@
 Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
-The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
-
-There were six elections within the second Menzies Government.
-However we do not find that any of those elections was associated with a significant change in the topics discussed.
-In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
+The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+There were six elections within the Second Menzies Government.
+Three toward the middle of that government were associated with significant changes in the topics discussed.
 
@@
 This is an example where there was a change in government without an election, as the next election only happened in November 1966.
-We find that the Holt Government is significantly different to the Menzies Government.
+We find that the Holt Government is different to the Menzies Government.
 In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
@@
 
-The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
+The Whitlam government is especially interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
 Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
 
-The Howard Government is interesting because of the significant differences between elections.
-For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
+The Howard Government is also interesting because of the significant differences between elections.
+For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level.
 Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
@@
 One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
-The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
+The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement.
 For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
-It also appropriately identifies some of other key events that we were interested in.
-However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+It also appropriately identifies some of other key events in Australian history, such as X and Y.
+There are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+When we dig into this we find that some of them, such as X and Y, are associated with significant legislation.
 Further work is needed to improve this approach.
@@
 
-# Conclusion
+# Summary, weaknesses and future work
 In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
@@
 In addition, we assume that the effect of elections is monotonically decreasing across days since election.
-In future work we will investigate different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.
+Future work could consider different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.
 
 The way that we identify unusual periods could also be improved.
-We defined sitting periods in a constant fashion across the whole dataset time frame, but the nature of how long parliaments sit for has most likely changed.
+We defined sitting periods in a constant fashion across the whole dataset time frame, but how long the stretches are that parliament sits for has changed over time.
 In addition, more work needs to be done on how to identify outlying events.
-For example, it is not clear if an important event that occurs outside a sitting period would be identified.
-And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such specific days are not identified as significantly outlying.
+For instance, the extent to which an important event that occurs outside a sitting period can be identified has a great deal of uncertainty.
+And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.
 
@@
 However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
-Future methodological work will focus on how to combine these two modelling steps by extending the STM approach into a more flexible framework.
+Future methodological work could consider how to combine these two modelling steps by extending the STM approach into a more flexible framework.
 
@@
 
-```{r asdf, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
+```{r hansardexamplepage, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
 knitr::include_graphics("../../figures/example_hansard_page.png")
@@
 
-```{r differencesbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
+```{r differencesbyyear, echo=FALSE, fig.cap="Differences by year between the number of sitting days and our number of PDFs", out.width = '100%'}
 knitr::include_graphics("../../figures/differences_by_year.pdf")
@@
 The exact scripts that we use are too long to provide here but are available on request.
-Instead here we provide shorterned scripts for the workflow to convert the PDFs to usable text datasets that may be a useful starting point for other researchers.
+Instead here we provide shorterned pseudo-code that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers.
 The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
@@
 
-```{r governments, echo = FALSE, results = 'asis'}
-
-governments %>% 
-  kable(booktabs = T, caption = "Change in governments") %>%
-  kable_styling(font_size = 10)
-
-```
+## List of Elections {#fulllistofelections}
 
@@
   kable("latex", booktabs = T, caption = "Elections") %>%
-  kable_styling(font_size = 10)
-
-```
-
-```{r keyevents, echo = FALSE, results = 'asis'}
-
-keyEvents %>% 
-  kable(booktabs = T, caption = "Key events") %>%
-  kable_styling(font_size = 10)
-
-```
-
-For background on the Premiers' Plan see @Copland1934.
-
-For background on the Gruen tariff cut see @Gruen1975.
-
-Add the graphs and procedures. **[TBD]**
+  kable_styling(font_size = 8)
+
+```
+
+\newpage
+
+## List of Governments {#fulllistofgovernments}
+
+```{r governments, echo = FALSE, results = 'asis'}
+
+governments %>% 
+  kable(booktabs = T, caption = "Change in governments") %>%
+  kable_styling(font_size = 8)
+
+```
+
+<!-- \newpage -->
+
+<!-- ## List of Other Events {#othereventsdetails} -->
+
+<!-- ```{r keyevents, echo = FALSE, results = 'asis'} -->
+
+<!-- keyEvents %>%  -->
+<!--   kable(booktabs = T, caption = "Key events") %>% -->
+<!--   kable_styling(font_size = 8) -->
+
+<!-- ``` -->
+
+<!-- For background on the Premiers' Plan see @Copland1934. -->
+
+<!-- For background on the Gruen tariff cut see @Gruen1975. -->
 

### 2018-11-15 outputs/docs/events/paper.Rmd
Update paper

@@
 toc: FALSE
-# spacing: double
+spacing: double
 bibliography: ../bibliography.bib
@@
 
+key_events_results_cols <-
+  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())
+
+names(key_events_results_cols) <- c("Dates", "", "", "", "", "", "", "")
+
 ```
@@
 
-We find that: firstly changes in government tend be associated with topic changes even when the party in power does not change.
+We find that: firstly, changes in government tend be associated with topic changes even when the party in power does not change.
 For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
@@
 With a small number of exceptions, even changes of government where the party in power also changed were not associated with overly large changes in parliamentary discussion.
-If governments try to more thoroughly distinguish themselves from their predecessor then longer-term policy may be more difficult to enact.
+If governments try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact.
 Similarly, there is the danger that larger-scale signature-accomplishments of a government may be neglected by their successor for solely political reasons.
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in this quantitative social sciences approach to text to only increase and we expect the data and methods in our paper will be extended by other researchers in a variety of ways.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in a quantitative approach to text to only increase and the data and methods in our paper will be extended in a variety of ways.
 
@@
 We use scripts written in R, @R2018, to convert the PDFs into daily text records.
-An example of the workflow and some pseudo-code are provided in Appendix \@ref(hansardworkflow).
+An example of the workflow and some example scripts are provided in Appendix \@ref(hansardworkflow).
 Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
@@
 We consider these topic distributions as inputs that can be analysed within another model.
-Thus, the second modeling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.
+Thus, the second modelling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.
 
@@
 
-## Overview of topic modeling
+## Overview of topic modelling
 Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics.
@@
 
-In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modeling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
+In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modelling , a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
 In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
@@
 Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period.
-We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occured on or before that sitting day.
+We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occurred on or before that sitting day.
 For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.
@@
 
-key_events_results %>%
+key_events_results_cols %>%
   kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
@@
 There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
-Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
+Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics.
 The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
@@
 To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
-However the change in 1998 and 2004 is more unexpected.
+However, the change in 1998 and 2004 is more unexpected.
 Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
 
-One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
+One advantage of our analysis model compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
 The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement.
 For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
-It also appropriately identifies some of other key events in Australian history, such as X and Y.
-There are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
-When we dig into this we find that some of them, such as X and Y, are associated with significant legislation.
-Further work is needed to improve this approach.
-For instance, our approach may not be appropriately considering step-changes.
+But there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
+When we dig into this we find that some of them, such as 4 February 2009, are associated with significant legislation.
+However the over-weighting of dates in the first half of our sample in Table \@ref(tab:keyeventsresultstable) highlights further work is needed to improve this approach.
+For instance, our approach may not be appropriately considering step-changes or it may be that our identification of sitting periods is not appropriate for the entire period.
 
@@
 For instance, the extent to which an important event that occurs outside a sitting period can be identified has a great deal of uncertainty.
-And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.
+And if an event happens in the middle of a sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.
 
 Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model.
-However, this approach does not appropriately propagate uncertainty in topic distribution estimation.
-Future methodological work could consider how to combine these two modelling steps by extending the STM approach into a more flexible framework.
+However, this approach does not appropriately propagate the uncertainty of the topic distribution estimation stage.
+Future methodological work could consider how to combine these two modelling steps, for instance by extending the STM approach into a more flexible framework.
 
@@
 It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there.
-Nonetheless, our work suggests that reasonable debate of important topics does occur in parliament.
+Nonetheless, our work suggests that important topics are discussed in parliament.
 It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
-However, we do find that since the 1980s differences between government and election periods are greater than they used to be.
+However, we do find that since the 1980s differences between government and election periods seem to be more pronounced than they used to be.
 It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.
@@
 The exact scripts that we use are too long to provide here but are available on request.
-Instead here we provide shorterned pseudo-code that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers.
+Instead here we provide example scripts that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers.
 The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
@@
 
-The first step is scrape the websites for the PDFs.
-
-```{r scrapingexample, echo=TRUE, eval = FALSE}
-visit_address_and_save_PDF <-
-  function(name_of_address_to_visit,
-           name_of_where_to_save) {
-    # Do the actual downloading of the PDF
-    download.file(name_of_address_to_visit, name_of_where_to_save)
-    # Helpful so that you know progress when running it on all the records
-    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))  
-    # Space out your requests so you don't overwhelm the website
-    Sys.sleep(sample(15:30, 1)) 
-  }
-```
-
-The next step is remove the front matter from the PDFs.
-
-```{r frontmatterexample, echo=TRUE, eval = FALSE}
-
-get_text_from_PDFs <-
-  function(name_of_input_PDF_file,
-           name_of_output_csv_file) {
-    pdf_document <- pdf_text(name_of_input_PDF_file)
-    # Convert to tibble so that tidyverse can be used
-    pdf_document_tibble <- tibble(text = pdf_document)
-    rm(pdf_document)
-    # Each row is now a page of the PDF
-    # Adding a column of the row numbers allows you to keep track of the page numbers
-    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
-    # Separate each line (of each page) into own row
-    pdf_document_tibble <-
-      separate_rows(pdf_document_tibble, text, sep = "\\n")
-    # Identify page headers and footers and remove them
-    pdf_document_tibble <- pdf_document_tibble %>%
-      group_by(pageNumbers) %>%
-      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
-      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
-      ungroup()
-    ## Identify front matter and remove it
-    pdf_document_tibble <- pdf_document_tibble %>%
-      mutate(
-        firstSpeakerRow = str_detect(text, "SPEAKER")
-      )
-    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
-    # Get the row and corresponding page and then filter to only pages from that page
-    row_of_first_SPEAKER <-
-      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
-    first_page_of_interest_SPEAKER <-
-      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
-    filter_from_here <-
-      case_when(
-        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER
-      )
-    pdf_document_tibble <- pdf_document_tibble %>%
-      filter(pageNumbers >= filter_from_here) %>%
-      select(-firstSpeakerRow)
-    # Save file
-    write_csv(pdf_document_tibble, name_of_output_csv_file)
-    # Helpful to know where you're up to
-    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
-  }
-
-```
-
-Then the rows need to be combined:
-```{r combinerows, echo=TRUE, eval = FALSE}
-split_columns <-
-  function(name_of_input_csv_file,
-           name_of_output_csv_file) {
-    # Read in the csv, based on the filename list
-    csv_with_rows_to_combine <-
-      read_csv(name_of_input_csv_file,
-               trim_ws = FALSE,
-               col_types = cols())
-    # Remove any extra whitespace i.e. two or more spaces and spaces at either end. 
-    # Yes, I know that I turned this off in the read_csv, but it's better to be 
-    #explicit because the whitespace is useful sometimes.
-    csv_with_rows_to_combine$text <-
-      str_squish(csv_with_rows_to_combine$text)
-    # Put everything onto one line, which allows us to rejoin words that have been 
-    #split across two lines e.g. Mon- ica
-    csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
-      mutate(text = str_replace_all(text, "-$", "MONICA"))
-    full_days_hansard <- csv_with_rows_to_combine %>%
-      select(-pageNumbers) %>%
-      summarise(text = paste(text, collapse = " ")) %>%
-      mutate(text = str_replace_all(text, "MONICA ", "")) %>%
-      mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - "))
-    rm(csv_with_rows_to_combine)
-    write_csv(full_days_hansard, name_of_output_csv_file)
-    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
-  }
-```
-
-Finally, we can fix the spelling:
-```{r fixspelling, echo=TRUE, eval = FALSE}
-fix_spelling <-
-  function(name_of_input_csv_file,
-           name_of_output_csv_file) {
-    csv_to_clean <-
-      read_csv(name_of_input_csv_file,
-               trim_ws = FALSE,
-               col_types = cols())
-    #Fix the spelling
-    csv_to_clean$text <-
-      stri_replace_all_regex(
-        csv_to_clean$text,
-        "\\b" %s+% fix_wrong_spellings$original %s+% "\\b",
-        fix_wrong_spellings$corrected,
-        vectorize_all = FALSE
-      )
-    # Save file
-    write_csv(csv_to_clean, name_of_output_csv_file)
-    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
-  }
-```
+**[Insert the example scripts.]**
+
+<!-- The first step is to scrape the websites for the PDFs. -->
+
+<!-- ```{r scrapingexample, echo=TRUE, eval = FALSE} -->
+<!-- visit_address_and_save_PDF <- -->
+<!--   function(name_of_address_to_visit, -->
+<!--            name_of_where_to_save) { -->
+<!--     # Do the actual downloading of the PDF -->
+<!--     download.file(name_of_address_to_visit, name_of_where_to_save) -->
+<!--     # Helpful so that you know progress when running it on all the records -->
+<!--     print(paste("Done with", name_of_where_to_save, "at", Sys.time()))   -->
+<!--     # Space out your requests so you don't overwhelm the website -->
+<!--     Sys.sleep(sample(15:30, 1))  -->
+<!--   } -->
+<!-- ``` -->
+
+<!-- The next step is to remove the front matter from the PDFs.  -->
+
+<!-- ```{r frontmatterexample, echo=TRUE, eval = FALSE} -->
+
+<!-- get_text_from_PDFs <- -->
+<!--   function(name_of_input_PDF_file, -->
+<!--            name_of_output_csv_file) { -->
+<!--     pdf_document <- pdf_text(name_of_input_PDF_file) -->
+<!--     # Convert to tibble so that tidyverse can be used -->
+<!--     pdf_document_tibble <- tibble(text = pdf_document) -->
+<!--     rm(pdf_document) -->
+<!--     # Each row is now a page of the PDF -->
+<!--     # Adding a column of the row numbers allows you to keep track of the page numbers -->
+<!--     pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble) -->
+<!--     # Separate each line (of each page) into own row -->
+<!--     pdf_document_tibble <- -->
+<!--       separate_rows(pdf_document_tibble, text, sep = "\\n") -->
+<!--     # Identify page headers and footers and remove them -->
+<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
+<!--       group_by(pageNumbers) %>% -->
+<!--       mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page -->
+<!--       mutate(lastLine = n()) %>% # This tells you the number of the last line in each page -->
+<!--       ungroup() -->
+<!--     ## Identify front matter and remove it -->
+<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
+<!--       mutate( -->
+<!--         firstSpeakerRow = str_detect(text, "SPEAKER") -->
+<!--       ) -->
+<!--     pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA -->
+<!--     # Get the row and corresponding page and then filter to only pages from that page -->
+<!--     row_of_first_SPEAKER <- -->
+<!--       pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first() -->
+<!--     first_page_of_interest_SPEAKER <- -->
+<!--       pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer() -->
+<!--     filter_from_here <- -->
+<!--       case_when( -->
+<!--         !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER -->
+<!--       ) -->
+<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
+<!--       filter(pageNumbers >= filter_from_here) %>% -->
+<!--       select(-firstSpeakerRow) -->
+<!--     # Save file -->
+<!--     write_csv(pdf_document_tibble, name_of_output_csv_file) -->
+<!--     # Helpful to know where you're up to -->
+<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
+<!--   } -->
+
+<!-- ``` -->
+
+<!-- Then the rows need to be combined: -->
+<!-- ```{r combinerows, echo=TRUE, eval = FALSE} -->
+<!-- split_columns <- -->
+<!--   function(name_of_input_csv_file, -->
+<!--            name_of_output_csv_file) { -->
+<!--     # Read in the csv, based on the filename list -->
+<!--     csv_with_rows_to_combine <- -->
+<!--       read_csv(name_of_input_csv_file, -->
+<!--                trim_ws = FALSE, -->
+<!--                col_types = cols()) -->
+<!--     # Remove any extra whitespace i.e. two or more spaces and spaces at either end.  -->
+<!--     # Yes, I know that I turned this off in the read_csv, but it's better to be  -->
+<!--     #explicit because the whitespace is useful sometimes. -->
+<!--     csv_with_rows_to_combine$text <- -->
+<!--       str_squish(csv_with_rows_to_combine$text) -->
+<!--     # Put everything onto one line, which allows us to rejoin words that have been  -->
+<!--     #split across two lines e.g. Mon- ica -->
+<!--     csv_with_rows_to_combine <- csv_with_rows_to_combine %>% -->
+<!--       mutate(text = str_replace_all(text, "-$", "MONICA")) -->
+<!--     full_days_hansard <- csv_with_rows_to_combine %>% -->
+<!--       select(-pageNumbers) %>% -->
+<!--       summarise(text = paste(text, collapse = " ")) %>% -->
+<!--       mutate(text = str_replace_all(text, "MONICA ", "")) %>% -->
+<!--       mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - ")) -->
+<!--     rm(csv_with_rows_to_combine) -->
+<!--     write_csv(full_days_hansard, name_of_output_csv_file) -->
+<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
+<!--   } -->
+<!-- ``` -->
+
+<!-- Finally, we can fix the spelling: -->
+<!-- ```{r fixspelling, echo=TRUE, eval = FALSE} -->
+<!-- fix_spelling <- -->
+<!--   function(name_of_input_csv_file, -->
+<!--            name_of_output_csv_file) { -->
+<!--     csv_to_clean <- -->
+<!--       read_csv(name_of_input_csv_file, -->
+<!--                trim_ws = FALSE, -->
+<!--                col_types = cols()) -->
+<!--     #Fix the spelling -->
+<!--     csv_to_clean$text <- -->
+<!--       stri_replace_all_regex( -->
+<!--         csv_to_clean$text, -->
+<!--         "\\b" %s+% fix_wrong_spellings$original %s+% "\\b", -->
+<!--         fix_wrong_spellings$corrected, -->
+<!--         vectorize_all = FALSE -->
+<!--       ) -->
+<!--     # Save file -->
+<!--     write_csv(csv_to_clean, name_of_output_csv_file) -->
+<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
+<!--   } -->
+<!-- ``` -->
 
@@
 ## Stopwords over time {#stopwordsgraph}
-Insert the graph of stop words over time.
+**[Insert the graph of stop words over time.]**
 
@@
 
-The choice of the number of topics to use in a topic model has a substantial affect on the results of the model.
+The choice of the number of topics to use in a topic model has a substantial effect on the results of the model.
 For instance, in our topic model, choosing a smaller number of topics, such as 10 or 20 results in a model that is not all that useful because the topics are so broad.
 
-There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a more fine level such as choosing betweeen 60 and 65 topics.
+There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a finer level such as choosing between 60 and 65 topics.
 We found it useful to try a few quite different measures before settling on 80 topics.
@@
 Higher values are better.
-The held out likelihood as described by @Wallach2009 takes a test/training approach to estimate the probability of held-out documents given the training documents.
+The held-out likelihood as described by @Wallach2009 takes a test/training approach to estimate the probability of held-out documents given the training documents.
 Higher values are better.
 The lower bound gives some indication of whether the model may have multiple modes and hence the end result be sensitive to the starting position (@Roberts2016navigating).
-Residuals analysis (@Taddy2012) compares the theoretical distribution of the variance with the eactual distribution.
+Residuals analysis (@Taddy2012) compares the theoretical distribution of the variance with the actual distribution.
 It is a test for overdispersion of the variance, and if it is found then this can suggest that more topics would be appropriate.
-Semantic coherence is the tradeoff for having topics that are more specific and the subsequent risk that the topics become meaningless.
+Semantic coherence is the trade-off for having topics that are more specific and the subsequent risk that the topics become meaningless.
 @Mimno2011 define a measure of coherence that is based on ratios of single words compared with pairs of words.
@@
 Lower values are better.
-@RobertsStewartAiroldiRPackage recommend examining the tradeoff between exclusitivity and semantic coherence.
+@RobertsStewartAiroldiRPackage recommend examining the trade-off between exclusivity and semantic coherence.
 This suggests that the magnitude of improvement reduces from about 80 topics (Figure \@ref(fig:topicsexclusivityvscoherence)).

### 2018-11-18 outputs/docs/events/paper.Rmd
minor paper changes

@@
 Then the sentences are de-constructed and each word considered individually.
+The resulting dataset used for analysis contains counts of words by day for each of the 14,551 days between 1901 and 2017.
 
@@
 This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
-For instance, examining Topics 4, 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+For instance, examining Topics 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
 

### 2018-11-19 outputs/docs/events/paper.Rmd
Update paper

@@
 Conversely, that same discussion can indicate a government's priorities.
-But major events -- be they expected, such as an election, and unexpected, such as a recession or terrorist attack -- can affect the course of parliamentary discussion.
+But major events -- be they somewhat expected, such as an election, and unexpected, such as a recession or terrorist attack -- can affect the course of parliamentary discussion.
 For instance, think of how a new government often goes to some trouble to seem different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
@@
 In this paper we examine text records of what was said in the Australian Federal Parliament.
-We create a dataset based on all sitting days from 1901 through to 2017.
+We create a dataset based on the sitting days from 1901 through to 2017.
 We have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
@@
 
-Our work contributes to a growing modern quantitative social sciences literature that considers text as an input to statistical methods, rather than requiring separate analysis.
+Our work contributes to the growing literature in quantitative social science that considers text as an input to statistical methods, rather than requiring separate analysis.
 This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect interest in a quantitative approach to text to only increase and the data and methods in our paper will be extended in a variety of ways.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularlity of quantitative approaches to text to increase further and the data and methods in our paper to be extended in a variety of ways.
 
@@
 
-Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901.[^Verbatimfootnote] Earlier work on the influence of parliaments, such as @ZandenBuringhBosker2012, often examined broader activity measures such as counts of sitting days.
-This allowed for long time-frames and wide comparisons.
-But analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.
+Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since Federation in 1901.[^Verbatimfootnote] Analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.
 
@@
 
-The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed text analysis of Canadian parliament records.
+The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records.
 For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada.
-A digitised version of the UK Hansard has been available for some time and there has been much text analysis of it.
-For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians and @PetersonSpirling2018 examined polarisation.
+A digitised version of the UK Hansard has been available for some time.
+For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation.
 One exciting aspect of research using the UK Hansard has been linking text records with other datasets.
@@
 @GansLeigh2012 examined Australian Hansard records to associate mentions by politicians of certain public intellectuals with neutral or positive sentiment.
-And @Salisbury2011 examined unparliamentary behaviour.
-@FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups.
-The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia for the period 1946 to 2012.
+@Salisbury2011 examined unparliamentary behaviour.
+And @FraussenGrahamHalpin2019 examined Australian Hansard records to assess the prominence of interest groups.
+The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia between 1946 and 2012.
 
 The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.
-Additionally, XML records are available in some cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament that we have PDFs for and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
+Although we do not use them here, XML records are also available in most cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
+There are 14,551 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
 
-[^XMLfootnote]: Tim Sherratt makes these XML records available as a single download and also presents them in a website -- http://historichansard.net/ -- that can be used to explore Commonwealth Hansard records from 1901 to 1980.
+[^XMLfootnote]: Tim Sherratt makes Commonwealth XML records for 1901 to 1980 available as a single download at: http://historichansard.net/.
 Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
-The records can also be downloaded from the Australian Hansard website.
+The records can also be downloaded from the Australian Hansard website or the website can be scraped.
 
@@
 Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
+The output of the first stage is the input to the second stage.
 
 We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
-We consider these topic distributions as inputs that can be analysed within another model.
+We consider these topic distributions as inputs that can be analysed by another model.
 Thus, the second modelling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.
@@
 
-Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 addresses this problem by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate.
+Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 addressed this problem by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate.
 This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
 
-In order to effectively categorise topics over the whole period covering Hansard, we chose to use topic modelling , a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
+In order to effectively categorise the topics of the entire Hansard, we chose to use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
 In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
@@
 This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.
-More detail on how topic modelling works is available in Appendix \@ref(LDAexample).
+A
+
+An overview and simplified example of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample).
+The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics.
+Finally, the choice of the number of topics has a large effect on the composition of the topics, and some diagnostics for selecting the appropriate number are discussed in Appendix \@ref(selecttopicnumber).
 
@@
 CTM is a slight extension to LDA which allows for correlations between topics.
-More details about CTM can be found in Appendix \@ref(LDAexample).
+More details about CTM can be found in Appendix \@ref(correlatedtopicmodelsection).
 
@@
 $$
-\alpha_{e[s],0,p} \sim \mbox{Normal}(0, 100);\mbox{ and}\\
-\rho_{e[s],p} \sim \mbox{Uniform}(0,1).
+\begin{aligned}
+\alpha_{e[s],0,p} &\sim \mbox{Normal}(0, 100) \mbox{ and} \nonumber \\
+\rho_{e[s],p} &\sim \mbox{Uniform}(0,1). \nonumber
+\end{aligned}
 $$
@@
 We model the underlying time trend in topics using splines regression.
-The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes in the economy, and Australian society and culture.
+The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes to Australian society, culture, and the economy.
 The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
@@
 
-Finally, the sitting period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
+Finally, the sitting-period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
 This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
@@
 
-Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Australian House of Representatives between 1901 and 2017.
+Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Hansard.
 It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
@@
 These tables focus on elections and governments that were different to the ones that preceded them.
-Complete lists of elections and governments are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
-
-```{r electionsresults, echo = FALSE, results = 'asis'}
-
-elections_results %>%
-  kable(booktabs = T, caption = "Significant elections, and neighours") %>%
-  kable_styling(font_size = 10)
-
-```
+Complete lists of the Australian elections and governments are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
 
@@
   kable_styling(font_size = 10)
+
+```
+
+```{r electionsresults, echo = FALSE, results = 'asis'}
+
+elections_results %>%
+  kable(booktabs = T, caption = "Elections that were significantly different to the one before") %>%
+  kable_styling(font_size = 10) %>% 
+  footnote(general = "Here is a general comments of the table. ")
 
@@
 We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occurred on or before that sitting day.
-For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.
+For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would change the discussion, or that the sitting day when, for instance, the Apology to the Stolen Generation was delivered, or some particularly prominent legislation introduced, would be different to others in that sitting period.
 
@@
 However, four of these results -- the significance of the Page Government, the First Menzies Government, the Chifley Government and the Abbott Government -- are likely due to the short length of either the government or its predecessor and should be ignored, leaving only 16.
-The earliest of these is the First Fisher Government, the Cook Government and the Third Fisher Government, which were different to the Second Deakin Government, the Second Fisher Government, and the Cook Government, respectively.
+The earliest of these are the First Fisher Government, the Cook Government and the Third Fisher Government, which were different to the Second Deakin Government, the Second Fisher Government, and the Cook Government, respectively.
 To a certain extent this is likely due to changes due to World War I.
 
-The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
-The rest of the governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
+The Second Menzies Government, begining in 1949, is the next government that is significantly different to its predecessor.
+The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
 Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
@@
 As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could take that approach.
+
+In this paper we think of events as affecting discussion in parliament.
+Given the events that we consider and the broad topics of discussion we consider this the most appropriate direction for this paper.
+Other papers could consider an alternative specification, especially if they were to focus on particular aspects.
 
@@
 
-## Overview and example
+## Overview and example {#LDAoverviewandexample}
 As applied to Hansard, LDA considers each statement to be a result of a process where a politician first chooses the topics they want to speak about.

### 2018-11-21 outputs/docs/events/paper.Rmd
Update footnotes and appendix with errors list

@@
 endnote: no
+
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage[table]{xcolor}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+
 ---
@@
 This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.
-A
-
-An overview and simplified example of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample).
-The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics.
-Finally, the choice of the number of topics has a large effect on the composition of the topics, and some diagnostics for selecting the appropriate number are discussed in Appendix \@ref(selecttopicnumber).
+
+An overview, and an example, of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample).
+The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics.
+Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.
 
@@
 top_words %>% 
-  kable(booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
-  kable_styling(font_size = 8, latex_options = c("repeat_header"))
+  kable("latex", booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
+  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
+  footnote(general = "We display only the top ten words for each topic, but the topics are defined by probability distributions over all words.")
 
@@
   kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
-  kable_styling(font_size = 10)
+  kable_styling(font_size = 10) %>% 
+  footnote(
+    general = "The significance of a government is determined by whether at least one topic was significantly different during this government, compared with the previous one.", 
+    footnote_as_chunk = T, 
+    threeparttable = TRUE)
 
@@
 elections_results %>%
-  kable(booktabs = T, caption = "Elections that were significantly different to the one before") %>%
+  kable(booktabs = T, caption = "Election-periods that were significantly different to the one before") %>%
   kable_styling(font_size = 10) %>% 
-  footnote(general = "Here is a general comments of the table. ")
+   footnote(
+    general = "The significance of a government is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the previous one.",
+    footnote_as_chunk = T, 
+    threeparttable = TRUE)
 
@@
   kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
-  kable_styling(font_size = 10)
+  kable_styling(font_size = 10) %>% 
+  footnote(
+    general = "These days were significantly different to others in their sitting period after taking election and government effects into consideration.", 
+    footnote_as_chunk = T, 
+    threeparttable = TRUE)
 
@@
 
-## Compared with parliamentary website {#knownhansardissues}
+## Annual counts of sitting days, compared with parliamentary website {#knownhansardissues}
 The parliamentary website provides a summary table of the number of sitting days in each year by chamber.[^parliamentarywebsitelink] Comparing the numbers provided in that table with number of days that we have provides an indication of how complete our dataset is.
@@
 The two major years of concern are 1992 in the House of Representatives where we have 15 days more than the parliamentary website claims there were, and 1988 in the Senate where we have eight days fewer.
+We examined the physical copy of the Hansard kept in the NSW State Library and this suggests that the summary table on the parliamentary website may be wrong.
 
 The Parliament website is missing the Hansard PDFs for the following dates in the Senate: 
-1988-12-21, 1988-12-20, 1988-12-19, 1988-12-16, 1988-12-15, 1988-12-14, 1988-12-13, 1988-12-12, 2000-10-12, 2000-06-19, 2004-08-09.
+1988-12-21, 
+1988-12-20, 
+1988-12-19, 
+1988-12-16, 
+1988-12-15, 
+1988-12-14, 
+1988-12-13, 
+1988-12-12, 
+2000-10-12, 
+2000-06-19, and
+2004-08-09.
 
@@
 1996-12-13,
-2002-05-14,
-2000-10-12, and
-2000-06-29.
+2000-10-12,
+2000-06-29, and 
+2002-05-14.
 
@@
 
-In the Senate, the PDF for 10 August 1917 may be the wrong one. It says it is for 10 January 1918 on the cover sheet, but there's not an entry for 10 January 1918.
-
-Senate Hansard - 1918-12-18 has the wrong PDF so does 1917-08-01.
+In terms of other issues, in the Senate, the PDF for 10 August 1917 may be the wrong one.
+It says that it is for 10 January 1918 on the cover sheet, but there's no an entry for 10 January 1918.
+Similarly for 1918-12-18 and 1917-08-01.
 

### 2018-11-21 scripts/run_6_make_graphs/make_table_pdf_by_year.R

@@ -92,7 +92,8 @@ counts_by_year %>%
     geom_label_repel(aes(label = label_the_year)) + 
     facet_wrap(vars(Chamber), nrow = 2) +
     theme_classic() +
-    scale_fill_viridis_d()
+    scale_fill_viridis_d() + 
+    theme(text = element_text(size=12))
 
 ggsave(
   "outputs/figures/differences_by_year.pdf",

### 2018-11-23 outputs/docs/events/paper.Rmd
Update paper

@@
     template: svm-latex-ms.tex
-title: "The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)"
-thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, and the Parliamentary Library.
+title: "The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2017)"
+thanks: "Thank you to Ben Readshaw, Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, the Australian Parliamentary Library, and the U of T Political Behavior Group.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
   affiliation: Australian National University
-abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and changed governments.
+abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and prime ministers.
 We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
 To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: changes in government tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in government are rarely associated with topic changes.
-The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
-This has implications for how we think about the longer-term trajectory of government policymaking as the media and political cycles becomes increasingly focused on short-term events."
+We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes.
+The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades."
 keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
@@
 # Introduction
-Government policy is partly driven by parliamentary discussion.
+<!-- Government policy is partly driven by parliamentary discussion.
 Conversely, that same discussion can indicate a government's priorities.
@@
 For instance, think of how a new government often goes to some trouble to seem different to the one they replace, or how events such as the 9/11 attacks altered government priorities.
+-->
 
@@
 Second, we analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
-We explicitly consider two types of events: changes in government and elections.
-After taking into consideration these effects, we can then explore the effect of other significant events such as an economic recession or terrorism.
-
-We find that: firstly, changes in government tend be associated with topic changes even when the party in power does not change.
+We explicitly consider two types of events: changes in prime minister and elections.
+After taking into consideration these effects, we can then explore other significant events.
+
+We find that: firstly, changes in prime minister tend be associated with topic changes even when the party in power does not change.
 For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
-Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the government was returned yet there was a significant change in topics.
+Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the prime minister did not change but there was a significant change in topics.
 Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.
@@
 We find that the events that we are interested in are rarely significant in the first half of our dataset.
-With a small number of exceptions, even changes of government where the party in power also changed were not associated with overly large changes in parliamentary discussion.
-If governments try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact.
-Similarly, there is the danger that larger-scale signature-accomplishments of a government may be neglected by their successor for solely political reasons.
+With a small number of exceptions, even changes of prime minister where the party in power also changed were not associated with overly large changes in parliamentary discussion.
+If prime ministers try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact.
+Similarly, there is the danger that larger-scale signature-accomplishments of a prime minister may be neglected by their successor for solely political reasons.
 
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularlity of quantitative approaches to text to increase further and the data and methods in our paper to be extended in a variety of ways.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularlity of quantitative approaches to text to further increase and the data and methods in our paper can be improved on in a variety of ways.
 
@@
 The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records.
-For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada.
+For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings.
 A digitised version of the UK Hansard has been available for some time.
@@
 The records can also be downloaded from the Australian Hansard website or the website can be scraped.
+We do not use the XML records or scrape the website because those records are known to be incomplete but the extent of how incomplete they are is unknown.
+The trade-off for a more-complete record is the errors introduced by having to parse the PDFs.
 
@@
 The percentage of stop-words in each record is reasonably consistent over time.
-This suggests that there is no significant difference in the quality of the parsing over time.
+This suggests that there is no significant difference in the quality of the parsing over time, although manual inspection does suggest there is some improvement in quality over time.
 Details of this check are provided in Appendix \@ref(stopwordsgraph).
@@
 Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
-Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in government, elections, and other external events.
+Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in prime minister, elections, and other external events.
 The output of the first stage is the input to the second stage.
@@
 The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
-For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the government or election period, may affect the topics within that document.
+For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the prime minister or election period, may affect the topics within that document.
 The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
@@
 The STM framework assumes that  documents are independently and identically distributed, conditional on the model covariates.
-However, it could be expected that topic distributions within a particular government, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
+However, it could be expected that topic distributions within a particular prime minister's time, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
 To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
@@
 For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
-Instead we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, government and election effects.
+Instead we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, prime minister and election effects.
 
 To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in governments and elections.
+Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in prime minister and elections.
 This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
@@
 We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are a total of 822 sitting periods over the period 1901 to 2017 inclusive.
+Using this definition, there are 822 sitting periods over the period 1901 to 2017 inclusive.
 
@@
 
-The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The goal of the model is to relate these proportions to the prime minister $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
 The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
@@
 $$
-where: $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$; $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election; $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
-
-The government term, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each government on the topic distribution. We place uninformative priors on each of these parameters:
+where: $\alpha_{g[s],p}$ is the mean effect for prime ministers $g$ (which covers sitting period $s$) and topic $p$; $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election; $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
+
+The prime minister term, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution. We place uninformative priors on each of these parameters:
 $$
@@
 One advantage of our model over using the STM is that we can restrict the effect of an election to be monotonically decreasing.
-This allows us to identify differences between government and election effects even when there is a one-term government.
+This allows us to identify differences between prime minister and election effects even when there is a one-term prime minister.
 The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
@@
 The $x_{s,k}$ for $k = 1,2,\dots, K$ are the value of cubic basis splines for sitting period $s$ at knot point $k$.
-We place knot points every five sitting periods as this is the average length of time for a government to sit.
+We place knot points every five sitting periods as this is the average length of time for parliament to sit.
 Non-informative priors are placed on the splines coefficients:
@@
 
-Finally, the sitting-period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on government and election effects.
-This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-government and non-election events.
+Finally, the sitting-period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on prime minister and election effects.
+This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-prime-minister and non-election events.
 In addition, this set up also partially pools effects across sitting periods.
@@
 Firstly, we describe the results of the CTM approach, which defined 80 unique topics over the period 1901-2017.
-We then describe the results of the Bayesian analysis model, which identified governments, elections and other events that were associated with a change in the topics discussed.
+We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.
 
@@
 
-Our results are for a topic model that had 80 distinct topics.
+Our main results are based on a topic model with 80 distinct topics.
 With almost 15,000 days and 80 topics, the analysis model is being fit to more than a million observations.
@@
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussion in Section \@ref(analysismodelexplanation), the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.
+As discussion in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated in the CTM approach, and examines the association between these topic distributions and outside events.
 That is, the topic model outputs are inputs for our analysis model.
@@
 For example, the model provides estimates of topic prevalence by each sitting period.
-This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability.
+This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by prime ministers or elections tend not to provide enough variability.
 For instance, examining Topics 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
@@
 One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
-Political events are those related to a change of government or an election.
-Note that as Australia has a parliamentary system it is possible for the government to change without an election as we define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done.
+Political events are those related to a change of prime minister or an election.
+Note that as Australia has a parliamentary system it is possible for the prime minister to change without an election and we do not distinguish between terms or cabinet composition although this more detailed analysis is possible.
 If a person was prime minister more than once then these periods are considered independently.
 
-As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level-effect for each government, $\alpha_g$ and each election, $\alpha_e$.
-We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects.
-When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.
-
-We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults).
-These tables focus on elections and governments that were different to the ones that preceded them.
-Complete lists of the Australian elections and governments are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
-
-```{r governmentsresults, echo = FALSE, results = 'asis'}
+As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level-effect for each prime minister, $\alpha_g$ and each election, $\alpha_e$.
+We identify differences between neighbouring prime ministers and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects.
+When these do not overlap we consider that the model finds a significant difference between either the neighbouring prime ministers or elections.
+
+We summarise our results in terms of prime ministers in Table \@ref(tab:primeministersresults) and in terms of elections in Table \@ref(tab:electionsresults).
+These tables focus on elections and prime ministers that were different to the ones that preceded them.
+Complete lists of the Australian elections and prime ministers are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
+
+```{r primeministersresults, echo = FALSE, results = 'asis'}
 
 governments_results %>%
-  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
+  kable(booktabs = T, caption = "Prime ministers that were significantly different to their predecessor") %>%
   kable_styling(font_size = 10) %>% 
   footnote(
-    general = "The significance of a government is determined by whether at least one topic was significantly different during this government, compared with the previous one.", 
+    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during this prime minister, compared with the previous one.", 
     footnote_as_chunk = T, 
@@
    footnote(
-    general = "The significance of a government is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the previous one.",
+    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the previous one.",
     footnote_as_chunk = T, 
@@
 
-In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between governments and elections, respectively.
+In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively.
 In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
@@
 
-```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Government level effects on selected topics.", out.width = '100%'}
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "prime minister level effects on selected topics.", out.width = '100%'}
 knitr::include_graphics("../../figures/mu_gov.pdf")
@@
 
+In Appendix \@ref(resilientresults) we show that our main findings are resilient to both fewer - 60 - and more - 100 - topics.
+
 ### Additional results
 
-Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period.
+Once prime minister and election effects have been taken into consideration, some days stand out compared with others in their sitting period.
 We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occurred on or before that sitting day.
@@
   footnote(
-    general = "These days were significantly different to others in their sitting period after taking election and government effects into consideration.", 
+    general = "These days were significantly different to others in their sitting period after taking election and prime minister effects into consideration.", 
     footnote_as_chunk = T, 
@@
 # Discussion
-Of the 36 governments over this period, we find that 20 of them are significantly different to the government that preceded them.
-However, four of these results -- the significance of the Page Government, the First Menzies Government, the Chifley Government and the Abbott Government -- are likely due to the short length of either the government or its predecessor and should be ignored, leaving only 16.
-The earliest of these are the First Fisher Government, the Cook Government and the Third Fisher Government, which were different to the Second Deakin Government, the Second Fisher Government, and the Cook Government, respectively.
+Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them.
+However, four of these results -- the significance of the Page Premiership, the First Menzies Premiership, the Chifley Premiership and the Abbott Premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
+The earliest of these are the First Fisher Premiership, the Cook Premiership and the Third Fisher Premiership, which were different to the Second Deakin Premiership, the Second Fisher Premiership, and the Cook Premiership, respectively.
 To a certain extent this is likely due to changes due to World War I.
 
-The Second Menzies Government, begining in 1949, is the next government that is significantly different to its predecessor.
+The Second Menzies Premiership, begining in 1949, is the next government that is significantly different to its predecessor.
 The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
@@
 
-The Second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
-The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
+The Second Menzies Premiership was associated with a variety of changes compared with the preceding Chifley Government.
+The Chifley Premiership had governed through the end of World War II and the difficult economic times that followed.
 There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
 Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics.
-The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
-There were six elections within the Second Menzies Government.
-Three toward the middle of that government were associated with significant changes in the topics discussed.
-
-The Menzies Government was succeeded by the Holt Government in January 1966.
-This is an example where there was a change in government without an election, as the next election only happened in November 1966.
-We find that the Holt Government is different to the Menzies Government.
-In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
+The sixteen-year length of the Second Menzies Premiership, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+There were six elections within the Second Menzies Premiership Three toward the middle of that government were associated with significant changes in the topics discussed.
+
+The Menzies Premiership was succeeded by the Holt Premiership in January 1966.
+This is an example where there was a change in prime minister without an election, as the next election only happened in November 1966.
+We find that the Holt Premiership is different to the Menzies Premiership In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Premiership with the topics of the Holt Premiership
 
@@
 
-The Whitlam government is especially interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
-
-The Howard Government is also interesting because of the significant differences between elections.
+The Whitlam Premiership is especially interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam Premiership.
+
+The Howard Premiership is also interesting because of the significant differences between elections.
 For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level.
@@
 However, the change in 1998 and 2004 is more unexpected.
-Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
+Although the Howard Premiership is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Premiership as a combination of three or four different periods and that the Howard Premiership reinvented itself over this period.
 
@@
 We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
-In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not.
+In general we find that changes in prime minister change the distribution of topics discussed in parliament, but that most elections did not.
 We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
@@
 However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
+Future work could continue to improve the quality of this dataset which would allow complementary research using it.
 
@@
 That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies.
-For instance, the use of topic models is problematic because of the need to interpret the topics, which at can sometimes feel like interpreting hieroglyphics.
+For instance, the use of topic models is problematic because of the need to interpret the topics.
 This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
@@
 In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model.
-Firstly, we are assuming that the effect of a particular government is constant across the whole period.
+Firstly, we are assuming that the effect of a particular prime minister is constant across the whole period.
 In addition, we assume that the effect of elections is monotonically decreasing across days since election.
@@
 It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
-However, we do find that since the 1980s differences between government and election periods seem to be more pronounced than they used to be.
-It is, of course, reasonable that a government should act on the mandate they receive, but it takes a long time to get policy right, and we may find progress being held back if the media and political cycles become too focused on short-term events.
+However, we do find that since the 1980s differences between prime minister and election periods seem to be more pronounced than they used to be.
 
@@
 We found it useful to try a few quite different measures before settling on 80 topics.
-This provided a balance between being granular enough to be informative--anything less than 40 topics tended to be too broad-- yet still being tractable for our analysis model in a reasonable amount of time.
+This provided a balance between being granular enough to be informative---anything less than 40 topics tended to be too broad---yet still being tractable for our analysis model in a reasonable amount of time.
 In addition to looking at the topics and how they changed over time, diagnostic measures that we considered include the held-out likelihood, the lower bound, residuals, exclusivity.
@@
 The lower bound gives some indication of whether the model may have multiple modes and hence the end result be sensitive to the starting position (@Roberts2016navigating).
-Residuals analysis (@Taddy2012) compares the theoretical distribution of the variance with the actual distribution.
+Residuals analysis, @Taddy2012, compares the theoretical distribution of the variance with the actual distribution.
 It is a test for overdispersion of the variance, and if it is found then this can suggest that more topics would be appropriate.
@@
 
-## List of Governments {#fulllistofgovernments}
+## List of Prime Ministers {#fulllistofgovernments}
 
@@
 governments %>% 
-  kable(booktabs = T, caption = "Change in governments") %>%
+  kable(booktabs = T, caption = "Change in prime ministers") %>%
   kable_styling(font_size = 8)
@@
 
+# Effect of number of topics on analysis model results {#resilientresults}
+
+**[Add Lior's idea about running the model for 60 and for 100 and then showing that the main results don't change.]**
+
+\newpage
+
 <!-- # Analysis model {#modeldetailsandsimulation} -->

### 2018-11-23 outputs/docs/events/slides/slides.Rmd
Update paper

@@
 - Monica Alexander, University of Toronto\newline
-- Rohan Alexander, Australian National University
-date: 25 October 2018
-institute: Presentation at the Research School of Economics, Australian National University, Canberra, Australia.
+- \textbf{Rohan Alexander, Australian National University}
+date: 22 November 2018
+institute: Presentation at the University of Toronto Political Behaviour Group, Toronto, Canada.
 output: binb::metropolis
@@
 significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
-top_words <- read_csv2(here::here("outputs/misc/top_words_40.csv"), col_types = cols())
-missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
+top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
+missing_days <- read_csv(here::here("outputs/misc/missing_dates.csv"), col_types = cols())
 hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
 
-elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
-  # filter(Significant %in% c("Yes", "No"))
-  filter(Significant %in% c("Yes"))
+elections_results <-
+  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
+    filter(Significant %in% c("Yes")) %>%
+    select(-Significant)
 
-governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
+governments_results <-
+  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
     filter(Significant %in% c("Yes")) %>%
-  # filter(Significant %in% c("Yes", "No")) %>% 
-  select(-Party, -`Died in Office`)
+    select(-Party,-`Died in Office`,-Significant)
 
@@
 #breka
+
+key_events_results_cols <-
+  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())
+
+names(key_events_results_cols) <- c("Dates", "", "", "", "", "", "", "")
+
+key_events_results_cols <- key_events_results_cols[7:8]
+
+names(key_events_results_cols) <- c("Dates", "")
+
 ```
@@
 - Elections that do not result in a change in government are rarely associated with topic changes.
-- Economic events, such as financial crises, have less significant effects than other events such as terrorist attacks.
 - The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
@@
 - A daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since it was established in 1901. It's not vertatim, but it's pretty close.
-- Hansard records have been used in other counties but not really at scale in Australia (although others, such as Patrick Leslie, also use them).
-- Daily PDFs are available Hansard records available online as PDFs and these are considered the official release. 
+- Hansard records have been used in other counties but not really at scale in Australia.
+- Daily PDFs are available online and these are considered the official release. 
 - There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
@@
 
-## Latent Dirichlet Allocation - Data generation process
-
-1.
-There are $K$ topics and the vocabulary consists of $V$ terms.
-For each topic, decide the terms by randomly drawing distributions over the terms.
-The distribution over the terms for the $k$th topic is $\beta_k$.
-Use the Dirichlet distribution with hyper-parameter $\boldsymbol{\eta}$: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.
-
-## Latent Dirichlet Allocation - Data generation process (cont.)
-
-2.
-Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $D$ documents.
-The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
-Again, the Dirichlet distribution with the hyper-parameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
-
-## Latent Dirichlet Allocation - Data generation process (cont.)
-3. If there are $N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
-    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$.
-    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.
-
-## Latent Dirichlet Allocation - Data generation process (cont.)
-Given this set-up, we have a joint distribution for the variables and the analysis problem, discussed next, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
-This is intractable directly, but can be approximated.
-
-## Latent Dirichlet Allocation - Analysis problem
-- After the documents are created, they are all that we have to analyse. The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'. 
-- We do not know the topics of each document, nor how terms defined the topics. In a sense we are trying to reverse the document generation process.
-- If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics.
-
-## Latent Dirichlet Allocation - Analysis problem (cont.)
-- The outcomes of the LDA process are probability distributions and these define the topics.
-Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
-- That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document.
-- The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
-
-<!-- If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use cross validation. -->
-
-<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter.
-It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
-Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
-This is the Correlated Topic Model, described in the next section.
--->
-
 ## Correlated Topic Model
-Modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in step 2 in LDA above, CTM assumes
+Modification of LDA - rather than assuming that the distribution of topics in a document, $\theta_d$, are a draw from a Dirichlet distribution, as in LDA, CTM assumes
 $$\theta_d \sim \mbox{Logistic Normal}(\mu, \Sigma)$$
@@
 ```{r exampletopics, echo=FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/topics_example-slides.png")
+knitr::include_graphics("../../../figures/topics_example_slides_update.png")
 ```
@@
 $$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
-Again, sounds easy, but hard to implement, and they have a very nice solutions algorithm.
+Again, sounds easy, but hard to implement, and they have a very nice algorithm.
 
@@
 
-We choose 40 topics because it is the minimum needed to have meaningful results.
+We choose 80 topics because it is the minimum needed to have meaningful results.
 
@@
 elections_results %>%
-  select(-Significant) %>% 
+  filter(Number %in% c(9, 10, 19, 21, 22, 23, 28, 30, 32, 33)) %>% 
+  kable() %>%
+  kable_styling(font_size = 10)
+
+```
+
+## Analysis model - Significantly different elections (cont.)
+
+```{r electionsresultscont, echo = FALSE, results = 'asis'}
+
+elections_results %>%
+  filter(Number %in% c(34, 35, 36, 38, 39, 40, 41, 42, 43, 44)) %>% 
   kable() %>%
@@
 governments_results %>%
-  select(-Significant) %>% 
+  filter(Number %in% c(6, 9, 10, 12, 14, 15, 16, 20, 21, 22)) %>% 
+  kable() %>%
+  kable_styling(font_size = 10)
+
+```
+
+## Analysis model - Significantly different governments (cont.)
+
+```{r governmentsresultscont, echo = FALSE, results = 'asis'}
+
+governments_results %>%
+  filter(Number %in% c(24, 25, 26, 27, 28, 29, 30, 31, 32, 34)) %>% 
   kable() %>%
@@
 
-key_events_results %>%
+key_events_results_cols %>%
   kable() %>%
   kable_styling(font_size = 10)
-#CAS
+
 ```
@@
 ```
+
+# Supplementary
+
+## Latent Dirichlet Allocation - Data generation process
+
+1.
+There are $K$ topics and the vocabulary consists of $V$ terms.
+For each topic, decide the terms by randomly drawing distributions over the terms.
+The distribution over the terms for the $k$th topic is $\beta_k$.
+Use the Dirichlet distribution with hyper-parameter $\boldsymbol{\eta}$: $\beta_k \sim \mbox{Dirichlet}(\boldsymbol{\eta})$, where $\boldsymbol{\eta} = (\eta_1, \eta_2, \dots, \eta_{K})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+
+2.
+Decide the topics that each document will cover by randomly drawing distributions over the $K$ topics for each of the $D$ documents.
+The topic distributions for the $d$th document are $\theta_d$, and $\theta_{d,k}$ is the topic distribution for topic $k$ in document $d$.
+Again, the Dirichlet distribution with the hyper-parameter $0<\alpha<1$ is used here because usually a document would only cover a handful of topics: $\theta_d \sim \mbox{Dirichlet}(\boldsymbol{\alpha})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+3. If there are $N$ terms in the $d$th document, then to choose the $n$th term, $w_{d, n}$:
+    a. Randomly choose a topic for that term $n$, in that document $d$, $z_{d,n}$, from the multinomial distribution over topics in that document, $z_{d,n} \sim \mbox{Multinomial}(\theta_d)$.
+    b. Randomly choose a term from the relevant multinomial distribution over the terms for that topic, $w_{d,n} \sim \mbox{Multinomial}(\beta_{z_{d,n}})$.
+
+## Latent Dirichlet Allocation - Data generation process (cont.)
+Given this set-up, we have a joint distribution for the variables and the analysis problem, discussed next, is to compute a posterior over $\beta_{1:K}$ and $\theta_{1:D}$, given $w_{1:D, 1:N}$.
+This is intractable directly, but can be approximated.
+
+## Latent Dirichlet Allocation - Analysis problem
+- After the documents are created, they are all that we have to analyse. The term usage in each document, $w_{1:D, 1:N}$, is observed, but the topics are hidden, or 'latent'. 
+- We do not know the topics of each document, nor how terms defined the topics. In a sense we are trying to reverse the document generation process.
+- If the earlier process around how the documents were generated is assumed and we observe the terms in each document, then we can obtain estimates of the topics.
+
+## Latent Dirichlet Allocation - Analysis problem (cont.)
+- The outcomes of the LDA process are probability distributions and these define the topics.
+Each term will be given a probability of being a member of a particular topic, and each document will be given a probability of being about a particular topic.
+- That is, we are trying to calculate the posterior distribution of the topics given the terms observed in each document.
+- The choice of the number of topics, *k*, drives the results and must be specified *a priori*.
+
+<!-- If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use cross validation. -->
+
+<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter.
+It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
+Additionally, alternatives to the Dirichlet distribution can be used to extend the model to allow for correlation.
+This is the Correlated Topic Model, described in the next section.
+-->

### 2018-11-23 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -28,14 +28,11 @@ plan(multiprocess)
 
 #### Create lists of PDFs to read and file names to save text as ####
 # Change the path as required:
-# use_this_path_to_get_pdfs  <- "/Volumes/Backup/hansard_pdfs"
-use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
-# use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
+# use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
+use_this_path_to_get_pdfs  <- "inputs/for_testing_hansard_pdf"
 
-
-# use_this_path_to_save_csv_files  <- "outputs/hansard/temp"
-# use_this_path_to_save_csv_files  <- "/Volumes/Backup/hansard_csv"
-use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
+# use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
+use_this_path_to_save_csv_files  <- "outputs/hansard/temp"
 
 # Get list of Hansard PDF filenames
 file_names <-

### 2018-11-23 scripts/run_2_parse_pdfs/run_2_split_columns.R

@@ -24,9 +24,8 @@ plan(multiprocess)
 
 #### Create lists of CSVs to read ####
 # Change the path as required:
-# use_this_path_to_get_csvs  <- "/Volumes/Backup/temp"
-# use_this_path_to_get_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+use_this_path_to_get_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
 file_names <-
@@ -39,7 +38,7 @@ file_names <-
 
 file_names <- file_names %>% sample() # Randomise the order
 
-# The two columns is only issue up to 12 November 2013 so remove the file if it is after 2013-11-12
+# The two columns is only an issue up to 12 November 2013 so remove the file if it is after 2013-11-12
 file_names_tibble <- tibble(file_name = file_names)
 file_names_tibble <- file_names_tibble %>% 
   mutate(date = basename(file_names) %>% 
@@ -51,10 +50,8 @@ file_names <- file_names_tibble$file_name
 rm(file_names_tibble)
 
 #Sometimes it's useful to seperate the input and the output, but otherwise might prefer to overwrite - if you split it make sure to get the one column ones into the new folder
-# use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing"
-# use_this_path_to_save_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-# use_this_path_to_save_csvs  <- "/Volumes/Backup/temp"
-use_this_path_to_save_csvs  <- "/Volumes/Hansard/parsed/federal/hor"
+use_this_path_to_save_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_save_csvs  <- "/Volumes/Hansard/parsed/federal/hor"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
 
@@ -221,6 +218,9 @@ split_columns <-
       select(-emptyCell, -position, -counter) %>%
       rename(text = textInPosition) %>% 
       select(text, pageNumbers)
+    
+    # Check whether at the start of a row
+    all_one_column$text <- paste0("METHESTART- ", all_one_column$text)
     
     write_csv(all_one_column, name_of_output_csv_file)
     

### 2018-11-23 scripts/run_2_parse_pdfs/run_3_combine rows.R

@@ -24,11 +24,8 @@ plan(multiprocess)
 
 #### Create lists of CSVs to read ####
 # Change the path as required:
-# use_this_path_to_get_csvs  <- "/Volumes/Backup/temp"
-# use_this_path_to_get_csvs  <- "outputs/hansard/temp/testing"
-# use_this_path_to_get_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-
+use_this_path_to_get_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 
 # Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
 file_names <-
@@ -42,10 +39,8 @@ file_names <-
 file_names <- file_names %>% sample() # Randomise the order
 
 # Seems unnecessary, but sometimes useful to separate input and output
-# use_this_path_to_save_csvs  <- "outputs/hansard/temp/testing"
-# use_this_path_to_save_csvs  <- "outputs/big_files_do_not_push/hansard_csv"
-use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-# use_this_path_to_save_csvs  <- "/Volumes/Backup/temp/testing"
+use_this_path_to_save_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
 

### 2018-11-23 scripts/run_2_parse_pdfs/run_5_separate_rows_based_on_speaker.R

@@ -1,9 +1,9 @@
 # !diagnostics off
 #### Preamble ####
-# Purpose: This file takes Australian Hansard CSV files that are all in one column and one row and applies a brutal, replacement-based, custom-dictionary, spell-checker.
+# Purpose: This file takes Australian Hansard CSV files and attemps to split them into different lines for each speech.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 11 October 2018
+# Last updated: 23 November 2018
 # Prerequisites: You need to have done all the other parsing steps. For testing purposes there should be some in the /outputs/hansard folder.
 # To do:
 
@@ -20,12 +20,6 @@ library(tm)
 # update.packages()
 # Set up furrr
 plan(multiprocess)
-# Get the spell checker
-fix_wrong_spellings <-
-  read_csv2("inputs/misc/misspelt_words_with_corrections.csv") %>%
-  mutate(numberOfCharacters = nchar(original)) %>%
-  arrange(desc(numberOfCharacters)) %>%
-  select(-numberOfCharacters)
 
 
 #### Create lists of CSVs to read ####

### 2018-11-29 outputs/docs/events/paper.Rmd
Update paper

@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
+# install.packages("here")
+library(here)
+# install.packages("kableExtra")
+library(kableExtra)
+# install.packages("knitr")
+library(knitr)
+# install.packages("tidyverse")
+library(tidyverse)
+
 knitr::opts_chunk$set(echo = TRUE)
-library(here)
-library(kableExtra)
-library(knitr)
-library(tidyverse)
+
+library(readr)
 
 elections <-
-  read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
+  read_csv("../../../inputs/misc/misc_elections_data.csv", col_types = cols())
 
 governments <-
-  read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
+  read_csv("../../../inputs/misc/change_of_pm.csv", col_types = cols())
 
 keyEvents <-
-  read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
+  read_csv("../../../inputs/misc/key_events.csv", col_types = cols())
 
 significances <-
-  read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
+  read_csv("../../../outputs/misc/significance.csv", col_types = cols())
 
 top_words <-
-  read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols()) %>% 
+  read_csv2("../../../outputs/results-topic_models_and_gammas/top_words_80.csv", col_types = cols()) %>% 
   rename(Topic = topic, Terms = terms)
@@
 hansard_sources <-
-  read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())
+  read_csv("../../../outputs/misc/hansard_sources.csv", col_types = cols())
 
 elections_results <-
-  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
+  read_csv("../../../outputs/results-analysis_model/results-elections.csv", col_types = cols()) %>%
     filter(Significant %in% c("Yes")) %>%
@@
 governments_results <-
-  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
+  read_csv("../../../outputs/results-analysis_model/results-governments.csv", col_types = cols()) %>%
     filter(Significant %in% c("Yes")) %>%
@@
 key_events_results <-
-  read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols()) %>%
+  read_csv("../../../outputs/results-analysis_model/results-outliers.csv", col_types = cols()) %>%
     select(-Expected)
@@
 key_events_results_cols <-
-  read_csv(here::here("outputs/results-analysis_model/results-outliers_in_columns.csv"), col_types = cols())
+  read_csv("../../../outputs/results-analysis_model/results-outliers_in_columns.csv", col_types = cols())
 
@@
 Using this definition, there are 822 sitting periods over the period 1901 to 2017 inclusive.
+Appendix \@ref(wastonywrong) contains more information about the sitting patterns over time.
 
@@
 
+# Sitting periods over time {#wastonywrong}
+
+TBD
+
+\newpage
+
 ## List of Prime Ministers {#fulllistofgovernments}

### 2018-11-29 debris.R

@@ -1,49 +1,0 @@
-# Get the name fixer
-fix_wrong_names <-
-  read_csv2("inputs/misc/wrong_names_with_corrections.csv") %>%
-  mutate(numberOfCharacters = nchar(original)) %>%
-  arrange(desc(numberOfCharacters)) %>%
-  select(-numberOfCharacters)
-
-
-
-#### Create lists of CSVs to read ####
-# Change the path as required:
-use_this_path_to_get_csvs  <- "outputs/hansard/temp"
-# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-
-# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
-file_names <-
-  list.files(
-    path = use_this_path_to_get_csvs,
-    pattern = "*.csv",
-    recursive = FALSE,
-    full.names = TRUE
-  )
-
-file_names <- file_names %>% sample() # Randomise the order
-
-# Seems unnecessary, but sometimes useful to separate input and output
-use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
-# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-save_names <- file_names %>%
-  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
-
-
-
-
-file_names <-
-  list.files(
-    path = use_this_path_to_save_csvs,
-    pattern = "*.csv",
-    recursive = FALSE,
-    full.names = TRUE
-  )
-
-d <- purrr::map_df(file_names, readr::read_csv, .id = "id")
-
-names(d)
-
-speakers <- d$Speaker %>% unique()
-
-write_csv(d, "test.csv")

### 2018-11-29 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -75,14 +75,14 @@ get_text_from_PDFs <-
     # name_of_input_PDF_file <- "inputs/for_testing_senate_pdf/1901-06-06.pdf" # uncomment for testing
     pdf_document <- pdf_text(name_of_input_PDF_file)
     
-    # Convert to tibble so that tidyverse can be used
+    # Convert to tibble
     pdf_document_tibble <- tibble(text = pdf_document)
     rm(pdf_document)
     
     # Each row is now a page of the PDF so adding a column of the row numbers allows you to keep track of the page numbers later on
     pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
     
-    # Separate each line (of each page) into it's own row
+    # Separate each line (of each page) into a row
     pdf_document_tibble <-
       separate_rows(pdf_document_tibble, text, sep = "\\n")
     
@@ -93,10 +93,8 @@ get_text_from_PDFs <-
       str_replace_all(pdf_document_tibble$text, "’", "'")
     pdf_document_tibble$text <-
       str_replace_all(pdf_document_tibble$text, "•", "-") # Some hyphens are being read in as big dots
-    
     pdf_document_tibble$text <-
-      str_replace_all(pdf_document_tibble$text, "\\b- \\b", "") # Hyphens are being retained improperly e.g. Roh- an and that would affect the words analysis so needs to be fixed
-    
+      str_replace_all(pdf_document_tibble$text, "\\b- \\b", "") # Hyphens are being retained improperly e.g. Roh- an
     pdf_document_tibble$text <-
       str_replace_all(pdf_document_tibble$text, "—", "-") # I'm as pedantic as the next person about dash, hyphen, em dash usage, but this is not the place.
     pdf_document_tibble$text <-
@@ -105,18 +103,17 @@ get_text_from_PDFs <-
         "(?<=[:space:][:upper:])[:space:](?=[:upper:][:space:])",
         ""
[…]

### 2018-11-29 scripts/run_2_parse_pdfs/run_2.5_split_out_speakers.R

@@ -1,22 +1,20 @@
 # !diagnostics off
 #### Preamble ####
-# Purpose: This file takes Australian Hansard CSV files and isolates the name of the speaker into a separate column. 
+# Purpose: This file takes Australian Hansard CSV files and isolates the name of the person speaking into a separate column.
 # Author: Rohan Alexander
 # Email: rohan.alexander@anu.edu.au
-# Last updated: 26 November 2018
-# Prerequisites: You need to have downloaded the PDFs, read them into CSVs and the removed the two column format. For testing purposes there should be some in the /outputs/hansard/ folder.
+# Last updated: 28 November 2018
+# Prerequisites: 1) Download the PDFs; 2) read them into CSVs; 3) get rid of the front matter; 4) split the columns. For testing purposes there should be some Hansard PDFs in the /outputs/hansard/ folder.
 # To do:
 
 
 #### Set up workspace ####
 # devtools::install_github("DavisVaughan/furrr")
 library(furrr)
-# library(lubridate)
-# library(pdftools)
 library(stringi)
 library(tidyverse)
 library(tictoc)
-library(tm)
+# library(tm)
 # update.packages()
 # Set up furrr
 plan(multiprocess)
@@ -27,7 +25,6 @@ fix_wrong_names <-
   mutate(numberOfCharacters = nchar(original)) %>%
   arrange(desc(numberOfCharacters)) %>%
   select(-numberOfCharacters)
-
 
 
 #### Create lists of CSVs to read ####
@@ -58,8 +55,7 @@ split_columns <-
   function(name_of_input_csv_file,
            name_of_output_csv_file) {
     # Read in the csv, based on the filename list
-    # name_of_input_csv_file <-
-    #   "outputs/hansard/temp/1901-06-27.csv" # uncomment for testing
+    # name_of_input_csv_file <- "outputs/hansard/temp/1901-07-19.csv" # uncomment for testing
     csv_with_rows_to_combine <-
       read_csv(name_of_input_csv_file,
                trim_ws = FALSE,
@@ -112,40 +108,36 @@ split_columns <-
         full_days_hansard$text, 
         "(?<=\\S)Sir", 
         " Sir") # Again, if there is not a space to the left of Sir then put one there
-   
     full_days_hansard$text <-
       str_replace_all(
         full_days_hansard$text,
[…]

### 2018-11-29 scripts/run_2_parse_pdfs/run_2.7_split_out_titles_and_stage_directions.R

@@ -1,0 +1,9 @@
+
+
+
+
+# Misc other:
+# Motion (by Mr OHIFUBY). agreed .to-
+# Honorable members interjecting,
+# Sir Arthur Fadden interjecting,
+# Sitting suspended from 5.59 to 8 p.m.

### 2018-11-29 scripts/run_6_make_graphs/make_hansard_dates_graph.R

@@ -10,9 +10,8 @@ hansard_dates$sitting <- 1
 # hansard_dates_test <- hansard_dates[6000:7500,]
 # hansard_dates$class <- c(rep(0, nrow(hansard_dates)/2), rep(1, nrow(hansard_dates)/2))
 
-
-ggplot(data = hansard_dates,
-       mapping = aes(x = hansardDates)) +
+hansard_dates %>%
+  ggplot(mapping = aes(x = hansardDates)) +
   geom_bar() +
   # geom_vline(
   #   data = election_dates,
@@ -26,23 +25,17 @@ ggplot(data = hansard_dates,
   labs(x = "Date",
        title = "Sitting dates and election years",
        caption = "Data based on available Hansard records.") +
-  theme_classic() 
+  theme_classic()
 
 # Maybe split the data by 30 year panels?
 
 
-hansard_dates_by_year <- hansard_dates %>% 
-  mutate(year = year(hansardDates)) %>% 
-  group_by(year) %>% 
+hansard_dates_by_year <- hansard_dates %>%
+  mutate(year = year(hansardDates)) %>%
+  group_by(year) %>%
   summarise(countByYear = n())
 
 write_csv(hansard_dates_by_year, "counts_by_year.csv")
-  
-
- 
-  
-
-
 
 ggsave(
   "outputs/figures/age_at_election.pdf",
@@ -50,3 +43,35 @@ ggsave(
   width = 11.69,
   units = "in"
 )
+
+
+
+
+
+hansard_dates %>% 
+  filter(year(hansardDates) <= 1925) %>%
+  ggplot(mapping = aes(x = yday(hansardDates))) +
+  geom_bar() +
+  # facet_wrap(vars(year(hansardDates)), ncol = 10) +
+  facet_wrap(vars(year(hansardDates)), ncol = 5) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(),# GET RID OF THE Y AXIS LABELS
+        axis.text.y=element_blank(),
+        # axis.ticks.y = element_blank(), # GET RID OF THE Y AXIS TICKS
+        axis.ticks.y =  element_blank()) +
+  labs(x = "Day of year",
+       # title = "Sitting dates and election years",
+       caption = "Data based on Hansard PDF records available at https://parlinfo.aph.gov.au.")
+
+# install.packages("ggrepel")
+library(ggrepel)
+
+test <- hansard_dates %>% 
[…]

### 2018-11-30 outputs/docs/events/paper.Rmd
Update paper with Matt's commetns

@@
 To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
-We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes.
-The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades."
+We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; elections that do not result in a change in prime minister are rarely associated with topic changes; and that these effects have become more pronounced since the 1980s."
 keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
@@
 This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
-We contribute to this literature in terms of both data and methods.
+We contribute to this literature in terms of both data and methods, as well as our key findings.
 From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
+Those contributions allow us to to find that the effects in Australia of elections and prime ministers appears to have become more pronounced since the 1980s.
 As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularlity of quantitative approaches to text to further increase and the data and methods in our paper can be improved on in a variety of ways.
@@
 The resulting dataset used for analysis contains counts of words by day for each of the 14,551 days between 1901 and 2017.
+We do not stem the words because **[Add that reference that says that it affects the results.]**
 
@@
 For instance, examining Topics 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+Appendix \@ref(topicmodelresultsdiscussion) provides more detail about the topic model results in the context of economic events.
 
@@
 # Discussion
+
+**[Needs more.]**
+
 Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them.
@@
 Other papers could consider an alternative specification, especially if they were to focus on particular aspects.
+For instance, the effect of gender, the televising of question time, or the state of the economy and the budget position.
 
@@
 
+# Topic model outputs - economics {#topicmodelresultsdiscussion}
+
+**[TBD]**
+
+\newpage
+
 # Events {#eventdetails}

### 2018-12-05 scripts/debris.R
Get speaker splitter working

@@ -15,11 +15,15 @@ file_names <-
     full.names = TRUE
   )
 
-all_data <- purrr::map_df(file_names, readr::read_csv, .id = "id")
+names(file_names) <- list.files(use_this_path) %>% 
+  str_replace(".csv", "")
+  
+all_data <- purrr::map_df(file_names, readr::read_csv, .id = "date")
 
 names(all_data)
 
-speakers <- all_data$Speaker %>% count()
-count(all_data, Speaker, sort = TRUE)
+speakers <- count(all_data, Speaker, sort = TRUE)
+
+write_csv(speakers, "speakers.csv")
 
 write_csv(all_data, "test.csv")

### 2018-12-05 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -16,6 +16,7 @@
 library(furrr)
 # devtools::install_github("DavisVaughan/furrr")
 library(lubridate)
+# install.packages('pdftools')
 library(pdftools)
 library(stringi)
 library(tidyverse)

### 2018-12-05 scripts/run_2_parse_pdfs/run_2.5_split_out_speakers.R

@@ -1,219 +1,0 @@
-# !diagnostics off
-#### Preamble ####
-# Purpose: This file takes Australian Hansard CSV files and isolates the name of the person speaking into a separate column.
-# Author: Rohan Alexander
-# Email: rohan.alexander@anu.edu.au
-# Last updated: 28 November 2018
-# Prerequisites: 1) Download the PDFs; 2) read them into CSVs; 3) get rid of the front matter; 4) split the columns. For testing purposes there should be some Hansard PDFs in the /outputs/hansard/ folder.
-# To do:
-
-
-#### Set up workspace ####
-# devtools::install_github("DavisVaughan/furrr")
-library(furrr)
-library(stringi)
-library(tidyverse)
-library(tictoc)
-# library(tm)
-# update.packages()
-# Set up furrr
-plan(multiprocess)
-
-# Get the name fixer
-fix_wrong_names <-
-  read_csv2("inputs/misc/wrong_names_with_corrections.csv") %>%
-  mutate(numberOfCharacters = nchar(original)) %>%
-  arrange(desc(numberOfCharacters)) %>%
-  select(-numberOfCharacters)
-
-
-#### Create lists of CSVs to read ####
-# Change the path as required:
-use_this_path_to_get_csvs  <- "outputs/hansard/temp"
-# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-
-# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
-file_names <-
-  list.files(
-    path = use_this_path_to_get_csvs,
-    pattern = "*.csv",
-    recursive = FALSE,
-    full.names = TRUE
-  )
-
-file_names <- file_names %>% sample() # Randomise the order
-
-# Seems unnecessary, but sometimes useful to separate input and output
-use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
-# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-save_names <- file_names %>%
-  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
-
-
-#### Create the function that will be applied to the files ####
-split_columns <-
-  function(name_of_input_csv_file,
[…]

### 2018-12-05 scripts/run_2_parse_pdfs/run_3_split_out_speakers.R

@@ -1,0 +1,254 @@
+# !diagnostics off
+#### Preamble ####
+# Purpose: This file takes Australian Hansard CSV files and isolates the name of the person speaking into a separate column.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 5 December 2018
+# Prerequisites: 1) Download the PDFs; 2) read them into CSVs; 3) get rid of the front matter; 4) split the columns. For testing purposes there should be some Hansard PDFs in the /outputs/hansard/ folder.
+# To do:
+
+
+#### Set up workspace ####
+# devtools::install_github("DavisVaughan/furrr")
+library(furrr)
+# install.packages('lubridate')
+library(lubridate)
+library(stringi)
+library(tidyverse)
+# install.packages('tictoc')
+library(tictoc)
+# library(tm)
+# update.packages()
+# Set up furrr
+plan(multiprocess)
+
+# Get the name fixer
+fix_wrong_names <-
+  read_csv2("inputs/misc/wrong_names_with_corrections.csv") %>%
+  mutate(numberOfCharacters = nchar(original)) %>%
+  arrange(desc(numberOfCharacters)) %>%
+  select(-numberOfCharacters)
+
+
+#### Create lists of CSVs to read ####
+# Change the path as required:
+use_this_path_to_get_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+
+# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
+file_names <-
+  list.files(
+    path = use_this_path_to_get_csvs,
+    pattern = "*.csv",
+    recursive = FALSE,
+    full.names = TRUE
+  )
+
+file_names <- file_names %>% sample() # Randomise the order
+
+# Seems unnecessary, but sometimes useful to separate input and output
+use_this_path_to_save_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+save_names <- file_names %>%
+  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
+
+
+
[…]

### 2018-12-05 scripts/run_2_parse_pdfs/run_4_fix_spelling.R

@@ -1,95 +1,0 @@
-# !diagnostics off
-#### Preamble ####
-# Purpose: This file takes Australian Hansard CSV files that are all in one column and one row and applies a brutal, replacement-based, custom-dictionary, spell-checker.
-# Author: Rohan Alexander
-# Email: rohan.alexander@anu.edu.au
-# Last updated: 11 October 2018
-# Prerequisites: You need to have done all the other parsing steps. For testing purposes there should be some in the /outputs/hansard folder.
-# To do:
-
-
-#### Set up workspace ####
-# devtools::install_github("DavisVaughan/furrr")
-library(furrr)
-library(lubridate)
-# library(pdftools)
-library(stringi)
-library(tidyverse)
-library(tictoc)
-library(tm)
-# update.packages()
-# Set up furrr
-plan(multiprocess)
-# Get the spell checker
-fix_wrong_spellings <-
-  read_csv2("inputs/misc/misspelt_words_with_corrections.csv") %>%
-  mutate(numberOfCharacters = nchar(original)) %>%
-  arrange(desc(numberOfCharacters)) %>%
-  select(-numberOfCharacters)
-
-
-#### Create lists of CSVs to read ####
-# Change the path as required:
-use_this_path_to_get_csvs  <- "outputs/hansard/temp"
-# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-
-# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
-file_names <-
-  list.files(
-    path = use_this_path_to_get_csvs,
-    pattern = "*.csv",
-    recursive = FALSE,
-    full.names = TRUE
-  )
-
-file_names <- file_names %>% sample() # Randomise the order
-
-use_this_path_to_save_csvs  <- "outputs/hansard/temp"
-# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-save_names <- file_names %>%
-  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
-
-
-#### Create the function that will be applied to the files ####
-fix_spelling <-
-  function(name_of_input_csv_file,
-           name_of_output_csv_file) {
-    # Read in the csv, based on the filename list
-    # name_of_input_csv_file <- "/Volumes/Backup/temp/1971-10-05.csv" # uncomment for testing
-    
-    csv_to_clean <-
[…]

### 2018-12-05 scripts/run_2_parse_pdfs/run_5_combine rows.R

@@ -1,0 +1,117 @@
+# !diagnostics off
+#### Preamble ####
+# Purpose: This file takes Australian Hansard CSV files and combines everything onto one row, by speaker. The reason for this is that some words have been split across lines e.g. Moni- ca, and so they are treated as two words, but really ought to be combined.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 5 December 2018
+# Prerequisites: You need to have downloaded the PDFs, read them into CSVs and the removed the two column format. For testing purposes there should be some in the /outputs/hansard/ folder.
+# To do:
+
+
+#### Set up workspace ####
+# devtools::install_github("DavisVaughan/furrr")
+library(furrr)
+# library(lubridate)
+# library(pdftools)
+library(stringi)
+library(tidyverse)
+library(tictoc)
+# install.packages('tm')
+library(tm)
+# update.packages()
+# Set up furrr
+plan(multiprocess)
+
+
+#### Create lists of CSVs to read ####
+# Change the path as required:
+use_this_path_to_get_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+
+# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
+file_names <-
+  list.files(
+    path = use_this_path_to_get_csvs,
+    pattern = "*.csv",
+    recursive = FALSE,
+    full.names = TRUE
+  )
+
+file_names <- file_names %>% sample() # Randomise the order
+
+# Seems unnecessary, but sometimes useful to separate input and output
+use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
+# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+save_names <- file_names %>%
+  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
+
+
+#### Create the function that will be applied to the files ####
+split_columns <-
+  function(name_of_input_csv_file,
+           name_of_output_csv_file) {
+    # Read in the csv, based on the filename list
+    # name_of_input_csv_file <- "outputs/hansard/temp/1971-03-30.csv" # uncomment for testing
+    
+    csv_with_rows_to_combine <-
+      read_csv(name_of_input_csv_file,
+               trim_ws = FALSE,
+               col_types = cols())
+    
[…]

### 2018-12-05 scripts/run_2_parse_pdfs/run_5_separate_rows_based_on_speaker.R

@@ -1,87 +1,0 @@
-# !diagnostics off
-#### Preamble ####
-# Purpose: This file takes Australian Hansard CSV files and attemps to split them into different lines for each speech.
-# Author: Rohan Alexander
-# Email: rohan.alexander@anu.edu.au
-# Last updated: 23 November 2018
-# Prerequisites: You need to have done all the other parsing steps. For testing purposes there should be some in the /outputs/hansard folder.
-# To do:
-
-
-#### Set up workspace ####
-# devtools::install_github("DavisVaughan/furrr")
-library(furrr)
-library(lubridate)
-# library(pdftools)
-library(stringi)
-library(tidyverse)
-library(tictoc)
-library(tm)
-# update.packages()
-# Set up furrr
-plan(multiprocess)
-
-
-#### Create lists of CSVs to read ####
-# Change the path as required:
-use_this_path_to_get_csvs  <- "outputs/hansard/temp"
-# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-
-# Get list of Hansard csvs
-file_names <-
-  list.files(
-    path = use_this_path_to_get_csvs,
-    pattern = "*.csv",
-    recursive = FALSE,
-    full.names = TRUE
-  )
-
-file_names <- file_names %>% sample() # Randomise the order
-
-use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
-# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
-save_names <- file_names %>%
-  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
-
-
-#### Create the function that will be applied to the files ####
-split_lines <-
-  function(name_of_input_csv_file,
-           name_of_output_csv_file) {
-    # Read in the csv, based on the filename list
-    # name_of_input_csv_file <- "/Volumes/Backup/temp/1971-10-05.csv" # uncomment for testing
-    # name_of_input_csv_file <- "outputs/hansard/temp/1915-07-07.csv" # uncomment for testing
-    
-    csv_to_clean <-
-      read_csv(name_of_input_csv_file,
-               trim_ws = FALSE,
-               col_types = cols())
-    
-    csv_to_clean <- separate_rows(csv_to_clean, text, sep = "METHESTART- (?=Mr [:upper:]{2,})", convert = FALSE)
-    
[…]

### 2018-12-08 outputs/docs/events/paper.Rmd
Get speaker splitter working
Add counts of sitting days

@@
 elections <-
-  read_csv("../../../inputs/misc/misc_elections_data.csv", col_types = cols())
+  read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())
 
 governments <-
-  read_csv("../../../inputs/misc/change_of_pm.csv", col_types = cols())
+  read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())
 
@@
 In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
+One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time.
+A multinomial approach would not have this property.
 
@@
 
+**[Add graph of example.]**
+
 Once prime minister and election effects have been taken into consideration, some days stand out compared with others in their sitting period.
@@
 
-In terms of other issues, in the Senate, the PDF for 10 August 1917 may be the wrong one.
-It says that it is for 10 January 1918 on the cover sheet, but there's no an entry for 10 January 1918.
-Similarly for 1918-12-18 and 1917-08-01.
+In terms of other known issues, in the Senate, the PDF for the website date 10 August 1917 may be wrong.
+When downloaded the PDF says that it is for 10 January 1918 on the cover sheet, but there's no website entry for 10 January 1918.
+This is also the case for 18 December 1918 (which contains the PDF for 28 November 1918), and for 1 August 1917 (which contains the PDF for 10 August 1917).
 
@@
   filter(election == 1) %>% 
-  select(year, electionDate, electionWinner) %>% 
+  select(-election, -comment) %>% 
   kable("latex", booktabs = T, caption = "Elections") %>%
@@
 governments %>%
+  rename(
+    "Government" = "government",
+    "Prime Minister" = "primeMinister",
+    "Party" = "party",
+    "Start" = "start",
+    "End" = "end",
+    "Died in Office" = "diedInOffice",
+    "HoR" = "hor",
+    "Senate" = "senate"
+    ) %>% 
   kable(booktabs = T, caption = "Change in prime ministers") %>%
-  kable_styling(font_size = 8)
+  kable_styling(font_size = 8) %>% 
+  footnote(general = "Here is a general comments of the table. ",
+           number = c("Footnote 1; ", "Footnote 2; "),
+           alphabet = c("Footnote A; ", "Footnote B; "),
+           symbol = c("Footnote Symbol 1; ", "Footnote Symbol 2")
+           )
 

### 2018-12-08 scripts/run_6_make_graphs/make_tables_by_election_and_pm.R

@@ -1,0 +1,213 @@
+#### Preamble ####
+# Purpose: Create graphs and tables that summarise the Hansard data for the Appendix by election and PM
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 8 December 2018
+# Prerequisites:
+# Issues:
+
+
+#### Workspace set-up ####
+# library(ggrepel)
+library(lubridate)
+# library(stringr)
+library(tidyverse)
+
+# Get the names of the PDFs
+# Senate
+senate_dates <-
+  list.files(path = "/Volumes/Hansard/pdfs/federal/senate") %>%
+  str_replace(".pdf", "") %>%
+  ymd()
+senate_dates <- tibble(pdf_date = senate_dates, chamber = "senate")
+# Reps
+reps_dates <-
+  list.files(path = "/Volumes/Hansard/pdfs/federal/hor") %>%
+  str_replace(".pdf", "") %>%
+  ymd()
+reps_dates <- tibble(pdf_date = reps_dates, chamber = "hor")
+
+hansard_dates <- rbind(reps_dates, senate_dates)
+rm(reps_dates, senate_dates)
+
+# Get the PM periods
+pm_dates <- read_csv("inputs/misc/change_of_pm.csv")
+
+# hansard_dates <- read_csv("inputs/misc/hansard_dates.csv")
+
+
+sitting_days_counts_by_gov <- hansard_dates %>%
+  mutate(
+    government =  case_when(
+      pdf_date < "1903-09-24" ~ "Barton",
+      pdf_date < "1904-04-27" ~ "Deakin 1",
+      pdf_date < "1904-08-18" ~ "Watson",
+      pdf_date < "1905-07-05" ~ "Reid",
+      pdf_date < "1908-11-13" ~ "Deakin 2",
+      pdf_date < "1909-06-02" ~ "Fisher 1",
+      pdf_date < "1910-04-29" ~ "Deakin 3",
+      pdf_date < "1913-06-24" ~ "Fisher 2",
+      pdf_date < "1914-09-17" ~ "Cook",
+      pdf_date < "1915-10-27" ~ "Fisher 3",
+      pdf_date < "1923-02-09" ~ "Hughes",
+      pdf_date < "1929-10-22" ~ "Bruce",
[…]

### 2018-12-09 outputs/docs/events/paper.Rmd
Update paper

@@
     template: svm-latex-ms.tex
-title: "The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2017)"
-thanks: "Thank you to Ben Readshaw, Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU School of Politics and International Relations, the ANU Research School of Economics, the Australian Parliamentary Library, and the U of T Political Behavior Group.
+title: "The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)"
+thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, and the UofT Political Behavior Group.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
   affiliation: Australian National University
-abstract: "We systematically analyse how discussion in the Australian Federal Parliament changes in response to elections and prime ministers.
-We first create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records.
-To reduce the dimensionality of this dataset we use a correlated topic model, and then analyse the effect of various events using a Bayesian hierarchical Dirichlet model.
+abstract: "A large part of politics consists of reacting to events.
+But not all events provoke a reaction and so understanding political behaviour requires examining which ones do and how this changes over time.
+We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of events: elections and changed prime ministers.
+To do this we first create a new dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records.
+We reduce the dimensionality of this dataset by using a correlated topic model, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
 We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; elections that do not result in a change in prime minister are rarely associated with topic changes; and that these effects have become more pronounced since the 1980s."
-keywords: "text-as-data, Australian political history, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
+keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 
+**Update first para** Maybe include 
+"So maybe the implication here is something about the role of govt agenda setting in the chamber?"
+
 In this paper we examine text records of what was said in the Australian Federal Parliament.
-We create a dataset based on the sitting days from 1901 through to 2017.
-We have records for 7,869 days in the House of Representatives and 6,682 days in the Senate.
+We create a dataset based on the sitting days from 1901 through to 2018.
+We have records for 7,934 days in the House of Representatives and 6,746 days in the Senate.
 Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.
@@
 
-As our dataset covers 117 years we are able to see how the effect of events changes over time.
+As our dataset covers 118 years we are able to see how the effect of events changes over time.
 We find that the events that we are interested in are rarely significant in the first half of our dataset.
-With a small number of exceptions, even changes of prime minister where the party in power also changed were not associated with overly large changes in parliamentary discussion.
+With a small number of exceptions, even changes of prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion.
 If prime ministers try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact.
@@
 Although we do not use them here, XML records are also available in most cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are 14,551 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
+There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
 Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
@@
 Then the sentences are de-constructed and each word considered individually.
-The resulting dataset used for analysis contains counts of words by day for each of the 14,551 days between 1901 and 2017.
-We do not stem the words because **[Add that reference that says that it affects the results.]**
+The resulting dataset used for analysis contains counts of words by day for each of the 14,680 sitting days between 1901 and 2018.
+We do not stem the words because @SchofieldMimno2016 suggest that there is no significant benefit.
+
+**[Add discussion of how wonderful we are for making the data available.]**
 
@@
 The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
-But with many topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
+But with many topics for each of the roughly 14,680 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
 
@@
 We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are 822 sitting periods over the period 1901 to 2017 inclusive.
+Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive.
 Appendix \@ref(wastonywrong) contains more information about the sitting patterns over time.
@@
 
-Firstly, we describe the results of the CTM approach, which defined 80 unique topics over the period 1901-2017.
+Firstly, we describe the results of the CTM approach, which defined 80 unique topics over the period 1901 to 2018.
 We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.
@@
 The highlighted topics are those related to war and conflict.
-As expected, the two chambers of the Australian Federal Parliament are fairly similar.
+The two chambers of the Australian Federal Parliament appear to be similar at a broad scale.
 
@@
 For instance, examining Topics 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
-Appendix \@ref(topicmodelresultsdiscussion) provides more detail about the topic model results in the context of economic events.
+Appendix \@ref(topicmodeleconresultsdiscussion) provides more detail about the topic model results in the context of economic events.
 
@@
 
+**[For teh elections one, John says 'For the uninitiated, I think the govt party should be identified here, as well as the govt part of the predecessor--more like in Table 6.
+I'm left wondering whether these significantly different govts are mostly the result of a change in party.']**
 In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively.
@@
 The error bars represent 95 per cent Bayesian credible intervals.
-We have focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
+As there are 80 topics it would be overwhelming to show all of them, and so we have focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
 
@@
 There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
-Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics.
+Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics, although further investigation of this is left for future work.
 The sixteen-year length of the Second Menzies Premiership, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
@@
 # Summary, weaknesses and future work
-In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017.
+In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2018.
 We download and parse PDFs of Hansard to create a new dataset of text.
@@
 In general we find that changes in prime minister change the distribution of topics discussed in parliament, but that most elections did not.
-We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.
+We find that significant events such as 9/11 and the Bali Bombings had a substantial effect.
 
@@
 
-# Topic model outputs - economics {#topicmodelresultsdiscussion}
+# Topic model outputs - Economics {#topicmodeleconresultsdiscussion}
+
+Although the example topics in the main paper have a military and defence theme, there are other topics that also share a broader theme.
+An example of these are those to do with economics.
+For instance Topics 17, 22, 25, 44, 51, 55, 59, 71, 72, 74, 76, and 77.
 

### 2018-12-09 outputs/docs/events/paper.Rmd
Update intro and data

@@
   affiliation: Australian National University
-abstract: "A large part of politics consists of reacting to events.
-But not all events provoke a reaction and so understanding political behaviour requires examining which ones do and how this changes over time.
+abstract: "A large part of politics consists of reacting to events, but not all events provoke a reaction.
+As such, understanding political behaviour requires examining the reaction to events and how this changes over time.
 We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of events: elections and changed prime ministers.
@@
 
-**Update first para** Maybe include 
-"So maybe the implication here is something about the role of govt agenda setting in the chamber?"
-
-In this paper we examine text records of what was said in the Australian Federal Parliament.
-We create a dataset based on the sitting days from 1901 through to 2018.
+Events are a well-known cause of political behaviour.
+But the extent of their effect is varied and changes over time.
+Here we focus on just two types of events: elections, and a change in prime minister.
+We examine the effect of these types of events on the topics that are discussed in the Australian Federal Parliament.
+
+The main data source for our paper is the text record of what was said in the Australian Federal Parliament known as 'Hansard'.
+From this we create a dataset based on the sitting days from 1901 through to 2018.
 We have records for 7,934 days in the House of Representatives and 6,746 days in the Senate.
@@
 We explicitly consider two types of events: changes in prime minister and elections.
-After taking into consideration these effects, we can then explore other significant events.
+After taking these into consideration these effects, we can then explore other significant events.
 
@@
 Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the prime minister did not change but there was a significant change in topics.
+The effects in Australia of elections and prime ministers appear to have become more pronounced since the 1980s.
 Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.
@@
 With a small number of exceptions, even changes of prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion.
-If prime ministers try to more thoroughly distinguish themselves from their predecessor, then longer-term policy may be more difficult to enact.
-Similarly, there is the danger that larger-scale signature-accomplishments of a prime minister may be neglected by their successor for solely political reasons.
+It may be that these days prime ministers are trying to more thoroughly distinguish themselves from their predecessor, or that the role of the government in agenda setting in the Australian Federal Parliament is changing.
 
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-Those contributions allow us to to find that the effects in Australia of elections and prime ministers appears to have become more pronounced since the 1980s.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularlity of quantitative approaches to text to further increase and the data and methods in our paper can be improved on in a variety of ways.
+As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularity of quantitative approaches to text to further increase and the data and methods in our paper can be improved on in a variety of ways.
 
@@
 
-Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since Federation in 1901.[^Verbatimfootnote] Analysing Hansard records and their equivalents directly is increasingly viable as new methods and reduced computational costs make it easier.
+Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since Federation in 1901.[^Verbatimfootnote] Analysing Hansard records and their equivalents is increasingly viable as new methods and reduced computational costs make it easier.
 
@@
 The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
+We do not stem the words because @SchofieldMimno2016 suggest that there is no significant benefit.
 Then the sentences are de-constructed and each word considered individually.
-The resulting dataset used for analysis contains counts of words by day for each of the 14,680 sitting days between 1901 and 2018.
-We do not stem the words because @SchofieldMimno2016 suggest that there is no significant benefit.
-
-**[Add discussion of how wonderful we are for making the data available.]**
+The resulting dataset used for analysis contains counts of words by day for each of the 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]
+
+[^datasourcefootnote]: We have made our dataset available via the R package \texttt{hansardr}.
+R users can draw on the devtools package [@Wickham2018] to install it from: https://github.com/RohanAlexander/hansardr.
+Users of other languages can download the daily CSV files from the data-raw folder of that repository.
 

### 2018-12-10 outputs/docs/events/paper.Rmd
Update paper

@@
 Events are a well-known cause of political behaviour.
-But the extent of their effect is varied and changes over time.
-Here we focus on just two types of events: elections, and a change in prime minister.
+But their effect is varied, and changes over time.
+Here we focus on just two types of events: elections, and changes in prime minister.
 We examine the effect of these types of events on the topics that are discussed in the Australian Federal Parliament.
@@
 We explicitly consider two types of events: changes in prime minister and elections.
-After taking these into consideration these effects, we can then explore other significant events.
+After taking these effects into consideration, we then explore other significant events.
 
@@
 Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the prime minister did not change but there was a significant change in topics.
-The effects in Australia of elections and prime ministers appear to have become more pronounced since the 1980s.
 Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.
 
-As our dataset covers 118 years we are able to see how the effect of events changes over time.
+As our dataset covers 118 years we are able to see how the effect of these two types of events changes over time.
+In Australia the effect of elections and a change in prime minister appear to have become more pronounced since the 1980s.
 We find that the events that we are interested in are rarely significant in the first half of our dataset.
-With a small number of exceptions, even changes of prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion.
-It may be that these days prime ministers are trying to more thoroughly distinguish themselves from their predecessor, or that the role of the government in agenda setting in the Australian Federal Parliament is changing.
-
-Our work contributes to the growing literature in quantitative social science that considers text as an input to statistical methods, rather than requiring separate analysis.
+With a small number of exceptions, even changes in prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion until the 1980s.
+It may be that more recent prime ministers are trying to more thoroughly distinguish themselves from their predecessor, or that the role of the government in agenda setting in the Australian Federal Parliament has changed.
+
+Our work contributes to the growing literature that considers text as an input to statistical methods.
 This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
-We contribute to this literature in terms of both data and methods, as well as our key findings.
-From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and we make our dataset available to other researchers via the R package \texttt{hansardr}.
+In addition to our key findings about Australian politics, we contribute to this literature in terms of both data and methods.
+From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and our dataset is available to other researchers.
 From a methods perspective, our analysis model has several advantages over existing methods.
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularity of quantitative approaches to text to further increase and the data and methods in our paper can be improved on in a variety of ways.
+
+<!-- As the digitisation of historical sources continues and computational power becomes cheaper, we expect the popularity of quantitative approaches to text to further increase.
+For instance, our dataset could be linked to others or our statistical approach could be improved.
+with others, and the data and methods in our paper can be improved on in a variety of ways.
+-->
 
@@
 We use the official PDF release and the formatting of the Hansard records changes over time.
-We use scripts written in R, @R2018, to convert the PDFs into daily text records.
+We use scripts written in R [@R2018] to convert the PDFs into daily text records.
 An example of the workflow and some example scripts are provided in Appendix \@ref(hansardworkflow).
-Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records.
+Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records.
 An example of the latter issue is that 'the' is often parsed as 'thc'.
@@
 
-The percentage of stop-words in each record is reasonably consistent over time.
-This suggests that there is no significant difference in the quality of the parsing over time, although manual inspection does suggest there is some improvement in quality over time.
-Details of this check are provided in Appendix \@ref(stopwordsgraph).
+The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)).
+This is evidence to suggest that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time.
 We use Hansard records on a daily basis in this paper.
 We pre-process our text before applying a topic model.
-The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new zealand to new_zealand.
-We do not stem the words because @SchofieldMimno2016 suggest that there is no significant benefit.
+The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales.
+We do not stem the words because @SchofieldMimno2016 suggest that there may not be any significant benefit.
 Then the sentences are de-constructed and each word considered individually.
@@
 [^datasourcefootnote]: We have made our dataset available via the R package \texttt{hansardr}.
-R users can draw on the devtools package [@Wickham2018] to install it from: https://github.com/RohanAlexander/hansardr.
+R users can use the devtools package [@Wickham2018] to install it from: https://github.com/RohanAlexander/hansardr.
 Users of other languages can download the daily CSV files from the data-raw folder of that repository.
@@
 
-As such, we chose to use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain topic distributions.
-CTM is a slight extension to LDA which allows for correlations between topics.
-More details about CTM can be found in Appendix \@ref(correlatedtopicmodelsection).
+As such, we use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain topic distributions.
+The CTM is a modification of LDA that allows for correlations between topics.
+More detail about the CTM is in Appendix \@ref(correlatedtopicmodelsection).
 
@@
 
-Firstly, we describe the results of the CTM approach, which defined 80 unique topics over the period 1901 to 2018.
+Firstly, we describe the results of the CTM approach, which defined 80 topics over the period 1901 to 2018.
 We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.
@@
 The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
-There are also some topics that appear to be about procedural or day-to-day, such as Topics 7 or 9.
-Note that, as expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.
+Similar to when topic models are run using the parliamentary text records of other countries, there are also some topics that appear to be about procedural or day-to-day matters, such as Topics 7 or 9.
+As expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.
 
@@
 
+Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history.
+
+```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_examples_three.pdf")
+
+```
+
+The first panel of Figure \@ref(fig:threeexamples) is the second Menzies premiership.
+The dashed lines show the elections.
+While the results here abstract from differences based on topic mix, the shape of the distribution seems to be reasonably similar.
+Given 80 topics, it may be difficult to see differences in the topic mix manually, and so we would like for the analysis model to be able to suggest whether the mix is changing.
+The second panel shows the 1983 election, and the subsequent change from Fraser to Hawke on 11 March 1983, identified by a dotted line on that date.
+The distribution of topics seems less bunched after the change, but it is difficult to tell how different it is.
+We would like the analysis model to be able to distinguish between the two if they seem different.
+The third panel shows the first Rudd premiership.
+The important aspect to note is that the period after the 2007 election and the Rudd premiership contain essentially the same Hansard dates.
+The analysis model needs to be able to deal with this situation.
+
+Appendix \@ref(topicmodeleconresultsdiscussion) provides another example from the topic model results in the context of economic events.
+
 ## Analysis model
@@
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussion in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated in the CTM approach, and examines the association between these topic distributions and outside events.
+As discussed in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated by the CTM, and examines the association between these topic distributions and outside events.
 That is, the topic model outputs are inputs for our analysis model.
@@
 This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by prime ministers or elections tend not to provide enough variability.
-For instance, examining Topics 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
-Appendix \@ref(topicmodeleconresultsdiscussion) provides more detail about the topic model results in the context of economic events.
+For instance, examining Topics 4, 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
 
@@
 
-One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time.
-Political events are those related to a change of prime minister or an election.
-Note that as Australia has a parliamentary system it is possible for the prime minister to change without an election and we do not distinguish between terms or cabinet composition although this more detailed analysis is possible.
+One of the main goals of the analysis model is to see which elections and changes of prime minister are associated with changes in the prevalence of topics over time.
+By way of background, as Australia has a parliamentary system it is possible for the prime minister to change without an election and we do not distinguish between terms or cabinet composition although this more-detailed analysis is possible.
 If a person was prime minister more than once then these periods are considered independently.
@@
 We identify differences between neighbouring prime ministers and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects.
-When these do not overlap we consider that the model finds a significant difference between either the neighbouring prime ministers or elections.
+When these do not overlap we consider that the model finds a difference between either the neighbouring prime ministers or elections, as appropriate.
 
@@
   footnote(
-    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during this prime minister, compared with the previous one.",
+    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during this premiership, compared with the previous one.",
     footnote_as_chunk = T,
@@
    footnote(
-    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the previous one.",
+    general = "The significance of an election is determined by whether at least one topic was significantly different during the period between this election and the next, compared with the period between the previous election and this one.",
     footnote_as_chunk = T, 
@@
 
-**[For teh elections one, John says 'For the uninitiated, I think the govt party should be identified here, as well as the govt part of the predecessor--more like in Table 6.
-I'm left wondering whether these significantly different govts are mostly the result of a change in party.']**
 In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively.
@@
 The error bars represent 95 per cent Bayesian credible intervals.
-As there are 80 topics it would be overwhelming to show all of them, and so we have focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
+As there are 80 topics it would be unwieldy to show all of them, and so we have again focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
 
@@
 ### Additional results
-
-**[Add graph of example.]**
 
@@
 
+<!-- **[Add graph of example.]** -->
+
 <!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
@@
 
-**[Needs more.]**
+<!-- **[Needs more.]** -->
 
@@
 
-**[TBD]**
+**[Insert the econ examples.]**
 
@@
 
-TBD
+**[Add the graph.]**
 
@@
   kable_styling(font_size = 8) %>% 
-  footnote(general = "Here is a general comments of the table. ",
-           number = c("Footnote 1; ", "Footnote 2; "),
-           alphabet = c("Footnote A; ", "Footnote B; "),
-           symbol = c("Footnote Symbol 1; ", "Footnote Symbol 2")
+  footnote(general = "This table contains summary information for each prime minister of Australia.
+HoR and Senate refer to the number of days that each chamber sat for while that person was prime minister.",
+  footnote_as_chunk = T, 
+    threeparttable = TRUE
            )
@@
 
-**[Add Lior's idea about running the model for 60 and for 100 and then showing that the main results don't change.]**
+**[Add results for 60 and 100 topics.]**
+
+<!-- **[Add Lior's idea about running the model for 60 and for 100 and then showing that the main results don't change.]** -->
 

### 2018-12-10 scripts/run_6_make_graphs/make_graph_of_topics-four_examples.R

@@ -1,0 +1,89 @@
+# Just a quick chart as an example for the paper
+
+library(lubridate)
+library(tidyverse)
+
+td_gamma <- read_csv("outputs/results-topic_models_and_gammas/gammas_model_80.csv")
+dates <- read_csv("outputs/results-topic_models_and_gammas/dates.csv")
+elections <- read_csv("inputs/misc/misc_elections_data.csv") %>% 
+  filter(election == 1)
+pms <- read_csv("inputs/misc/change_of_pm.csv") 
+
+
+td_gamma <- td_gamma %>% 
+  separate(document, into = c("chamber", "date"), sep = "-", extra = "merge")
+
+td_gamma$chamber[td_gamma$chamber == "hor"] <- "House of Representatives"
+td_gamma$chamber[td_gamma$chamber == "senate"] <- "Senate"
+
+td_gamma$date <- ymd(td_gamma$date)
+
+td_gamma <- td_gamma %>% 
+  filter(chamber == "House of Representatives")
+
+
+# For paper
+td_gamma_reduced <- td_gamma %>% 
+  mutate(
+    example = case_when(
+             between(date, ymd("1958-01-01"), ymd("1959-12-31")) ~ "1. Menzies",
+             between(date, ymd("1982-01-01"), ymd("1983-12-31")) ~ "2. Fraser, Hawke",
+             between(date, ymd("2007-09-01"), ymd("2010-10-01")) ~ "3. Rudd",
+             TRUE ~ "0"
+           )
+         ) %>% 
+  filter(example != "0") %>% 
+  filter(chamber == "House of Representatives")
+
+ggplot() +
+  geom_point(data = td_gamma_reduced, 
+             size = 0.5, 
+             aes(x = date, 
+                 y = gamma)) +
+  geom_vline(xintercept = elections$electionDate, linetype = "dashed") +
+  geom_vline(xintercept = pms$start, linetype = "dotted") +
+  theme_minimal() +
+  labs(x = "Date",
+       y = "Topic share") +
+  facet_wrap(vars(example), nrow = 3, scales = "free_x") +
+  theme_classic()
+
+  
+ggsave(
+    "outputs/figures/topics_examples_three.pdf",
+     height = 8,
+     width = 6,
+     units = "in"
+  )
+
+
+
+# For slides
+td_gamma_reduced <- td_gamma %>% 
+  filter(topic %in% c(4, 26, 28, 30, 66))
+
+ggplot(data = td_gamma, aes(x = date, y = gamma, color = as.factor(topic))) +
[…]

### 2018-12-11 outputs/docs/events/slides/slides.Rmd
Add Rostock slides

@@
 ---
-title: The Effect of Events on Discussion in the Australian Federal Parliament (1901--2017)
+title: The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)
 subtitle: 
@@
 - \textbf{Rohan Alexander, Australian National University}
-date: 22 November 2018
-institute: Presentation at the University of Toronto Political Behaviour Group, Toronto, Canada.
+date: 11 December 2018
+institute: Presentation at the Max Planck Institute for Demographic Research, Rostock, Germany.
 output: binb::metropolis
@@
 
-- Create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2017 based on available public records. 
+- Create a dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records. 
 - Use a correlated topic model to reduce dimemsionality.
@@
 
-<div class="notes">
-Test
-</div>
-
 ## Findings
 
-- Changes in government tend be associated with topic changes even when the party in power does not change.
-- Elections that do not result in a change in government are rarely associated with topic changes.
-- The effect of events is much more pronounced in the second half of our sample, and especially in the past two decades.
+- Changing the prime minister tends be associated with topic changes even when the party in power does not change.
+- Elections that do not result in a change in prime minister are rarely associated with topic changes.
+- The effect of these types of events is much more pronounced in the second half of our sample, and especially in the past two decades.
 
@@
 - Daily PDFs are available online and these are considered the official release. 
-- There are 14,551 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
+- There are 14,680 days of publicly available Hansard records across both chambers of the Australian Federal Parliament.
 
@@
 
-## Why not use STM?
-STM is great, but it is specific to various contexts and ours is slightly outside them:
-
-- No way to specify more complicated auto-correlated functional forms of the effects of events over time. 
-- There is no way to implement partial pooling across groups of similar documents. 
-- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
-In an ideal world we could modify the STM code, but instead we build a similar, but different, analysis model.
-
-<!-- Also you don't really understand something until you code it yourself. -->
-
 # Analysis model
@@
 ## Analysis model - Set-up
-- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=40$ are equal to the estimated values of $\theta_d$ from the CTM. 
+- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=80$ are equal to the estimated values of $\theta_d$ from the CTM. 
 - We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are a total of 745 sitting periods over the period 1901 to 2017 inclusive.
+Using this definition, there are 745 sitting periods over the period 1901 to 2018 inclusive.
 
@@
 -->
+
+## Why not use STM?
+STM is great, but it is specific to various contexts and ours is slightly outside them:
+
+- No way to specify more complicated auto-correlated functional forms of the effects of events over time. 
+- There is no way to implement partial pooling across groups of similar documents. 
+- There is no way of identifying 'outlying' topic distributions -- and therefore events that had an important effect -- without pre-specifying the event of interest in the model.
+In an ideal world we could modify the STM code, but instead we build a similar, but different, analysis model.
+
+<!-- Also you don't really understand something until you code it yourself. -->

### 2018-12-13 outputs/docs/events/paper.Rmd
Minor improve paper

@@
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, and the UofT Political Behavior Group.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, and the UofT Political Behavior Group.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 We reduce the dimensionality of this dataset by using a correlated topic model, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
-We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; elections that do not result in a change in prime minister are rarely associated with topic changes; and that these effects have become more pronounced since the 1980s."
+We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1990s."
 keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
@@
 toc: FALSE
-spacing: double
+# spacing: double
 bibliography: ../bibliography.bib
@@
 
-The main data source for our paper is the text record of what was said in the Australian Federal Parliament known as 'Hansard'.
+The main data source for our paper is the text record, known as 'Hansard', of what was said in the Australian Federal Parliament.
 From this we create a dataset based on the sitting days from 1901 through to 2018.
-We have records for 7,934 days in the House of Representatives and 6,746 days in the Senate.
+We have records for 7,934 days in the 'House of Representatives' (lower house) and 6,746 days in the 'Senate' (upper house).
+In contrast to the US, but similar to Canada and the UK, the executive is drawn from the legislature, and the Australian prime minister typically sits in the lower house.
+Unlike Canada or the UK, both houses are elected, although each has different mechanisms and constituencies.
 Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.
@@
 As our dataset covers 118 years we are able to see how the effect of these two types of events changes over time.
-In Australia the effect of elections and a change in prime minister appear to have become more pronounced since the 1980s.
-We find that the events that we are interested in are rarely significant in the first half of our dataset.
-With a small number of exceptions, even changes in prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion until the 1980s.
+We find that in Australia the effect of elections and a change in prime minister appear to have become more pronounced since the 1980s.
+With a small number of exceptions, in the first half of our dataset, even changes in prime minister where the party in power also changed were not associated with overly large changes in the topics of parliamentary discussion.
 It may be that more recent prime ministers are trying to more thoroughly distinguish themselves from their predecessor, or that the role of the government in agenda setting in the Australian Federal Parliament has changed.
@@
 This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
-In addition to our key findings about Australian politics, we contribute to this literature in terms of both data and methods.
+In addition to our findings about the effect of events in Australian politics, we contribute to this literature in terms of both data and methods.
 From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and our dataset is available to other researchers.
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
+There are many avenues for closely related future work such as: investigating the effect of other types of events; including a richer set of covariates to tease out the reason for different effects; and reversing the causality to examine the effect of what is said in parliament on various outcomes.
 
@@
 
-Parts of Australian Hansard records have been analysed for various purposes.
+Parts of Australian Hansard records have been analysed for various purposes and our paper contributes to a small but growing literature.
 For instance, @Rasiah2010 examined Hansard records for the Australian House of Representatives to examine whether politicians attempted to evade questions about Iraq during February and March 2003.
@@
 Users of other languages can download the daily CSV files from the data-raw folder of that repository.
+While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper.
+If you have different requirements or have suggestions for how we can improve the dataset for other uses please contact us.
 
@@
 
-The goal of the model is to relate these proportions to the prime minister $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The goal of the model is to relate these proportions to the prime minister $g$, at time $d$, and also the days since the most recent election $e$, while accounting for underlying time trends.
 The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
@@
 
-The prime minister term, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution. We place uninformative priors on each of these parameters:
+The term for the prime minister, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution.
+We place uninformative priors on each of these parameters:
 $$
@@
 However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
-Future work could continue to improve the quality of this dataset which would allow complementary research using it.
+Future work could continue to improve the quality of this dataset.
+For instance, exploiting the availability of XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and would be used in a variety of research.
 
@@
 Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
-For instance, selecting stop words for removal and which word to merge because of common co-location has an impact on the topics.
+For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics.
 Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
 One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches.
-As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could take that approach.
-
-In this paper we think of events as affecting discussion in parliament.
-Given the events that we consider and the broad topics of discussion we consider this the most appropriate direction for this paper.
-Other papers could consider an alternative specification, especially if they were to focus on particular aspects.
-For instance, the effect of gender, the televising of question time, or the state of the economy and the budget position.
-
-In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model.
+As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.
+
+In this paper we think of events as affecting daily discussion in parliament.
+Given the events that we consider and the broad topics of discussion we consider this the most appropriate direction for our paper.
+However, conducting a similar analysis at a person, instead of daily, level would lead to interesting results.
+This would allow the analysis model to include a rich set of person-level covariates such as gender or party, and account for broader factors such as the televising of question time, or the state of the economy and the budget position.
+It would also be especially interesting to consider reversing the direction of causality and examine the effect of what is said in parliament on various economic, political and social events.
+
+In terms of the analysis model that relates the topic distributions with events, there are several limitations to the model.
 Firstly, we are assuming that the effect of a particular prime minister is constant across the whole period.
@@
 It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
-However, we do find that since the 1980s differences between prime minister and election periods seem to be more pronounced than they used to be.
+However, we do find that since the 1990s the effect of prime ministers and elections on the topics discussed in the Australian parliament does seem to be more pronounced than it used to be.
 
@@
 
+# Sitting periods over time {#wastonywrong}
+
+**[Add the graph.]**
+
+\newpage
+
 # Topic model outputs - Economics {#topicmodeleconresultsdiscussion}
@@
 
-**[Insert the econ examples.]**
+**[Insert the econ examples. Zoom in on the Great Depression, the Premiers' Plan, the 80s/90s, privatisation debate.]**
 
@@
 ```
-
-\newpage
-
-# Sitting periods over time {#wastonywrong}
-
-**[Add the graph.]**
 

### 2018-12-14 outputs/docs/events/paper.Rmd
Update graphs in appendix fo counts

@@
 From this we create a dataset based on the sitting days from 1901 through to 2018.
-We have records for 7,934 days in the 'House of Representatives' (lower house) and 6,746 days in the 'Senate' (upper house).
+We have records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).
 In contrast to the US, but similar to Canada and the UK, the executive is drawn from the legislature, and the Australian prime minister typically sits in the lower house.
@@
 Then the sentences are de-constructed and each word considered individually.
-The resulting dataset used for analysis contains counts of words by day for each of the 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]
+The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]
 
@@
 Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive.
-Appendix \@ref(wastonywrong) contains more information about the sitting patterns over time.
+Appendix \@ref(hansardsummarystatistics) contains more information about the sitting patterns over the course of the year, which have changed considerably since Federation.
 
@@
 
-Using text as data allows larger-scale analysis that would not be viable using less-automated approaches and so it can identify associations and patterns that may otherwise be overlooked.
-That said, text analysis has well-known shortcomings and weaknesses and should be considered a complement to more detailed analysis such as qualitative methods and case studies.
-For instance, the use of topic models is problematic because of the need to interpret the topics.
-This can be difficult especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
+Using text as data allows us to conduct larger-scale analysis that would not be viable using less-automated approaches and so researchers may be able to identify associations and patterns that would otherwise have been overlooked.
+That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013.
+Our paper should thus be considered a complement to more detailed analysis such as qualitative methods and case studies.
+An example of one of the more glaring issues when using topic models is the need to interpret the topics.
+This can be difficult, especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
 Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
+Most obviously the number of topics needs to be specified, but there are also more nuanced aspects to be aware of.
 For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics.
 Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
-One way to get around using topic models is to use the words more directly, for instance word2vec and other approaches.
+One way to get around using topic models is to use a supervised learning approach, such as that used by @AshMorelliOsnabru2018 in the context of New Zealand Hansard.
+Another is to use the words more directly, for instance word2vec and other approaches.
 As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.
@@
 
+### Counts per year
+
 The number of sitting days in a year varies considerably.
@@
 Since the 2000s the House of Representatives again has tended to have more sitting days than the Senate.
+
+### Distribution over the year
+
+The distribution of sitting days over the course of the year changes over time.
+It was initially more piecemeal.
+This can be seen by comparing the pattern of sitting days in the years to 1920 (Figure \@ref(fig:dayssattonineteentwenty)) with those in the 19 years from, and including, 2000 (Figure \@ref(fig:dayssatfromtwothousand)).
+
+```{r dayssattonineteentwenty, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
+knitr::include_graphics("../../figures/sitting_dates_before_1920.pdf")
+```
+
+```{r dayssatfromtwothousand, echo=FALSE, fig.cap="Number of sitting days, by year", out.width = '100%'}
+knitr::include_graphics("../../figures/sitting_dates_from_2000.pdf")
+```
+
+The largest gap between sitting dates for both the House of Representatives and the Senate is 284 days, which happened when neither house sat between 25 November 1910 and 5 September 1911.
+The next longest gap is 244 the House of Representatives and 243 for the Senate when the lower house last sat on 9 October 1924, the upper house last sat on 10 October 1924 and neither sat again until 10 June 1925.
 
@@
 
-<!-- The first step is to scrape the websites for the PDFs. -->
-
-<!-- ```{r scrapingexample, echo=TRUE, eval = FALSE} -->
-<!-- visit_address_and_save_PDF <- -->
-<!--   function(name_of_address_to_visit, -->
-<!--            name_of_where_to_save) { -->
-<!--     # Do the actual downloading of the PDF -->
-<!--     download.file(name_of_address_to_visit, name_of_where_to_save) -->
-<!--     # Helpful so that you know progress when running it on all the records -->
-<!--     print(paste("Done with", name_of_where_to_save, "at", Sys.time()))   -->
-<!--     # Space out your requests so you don't overwhelm the website -->
-<!--     Sys.sleep(sample(15:30, 1))  -->
-<!--   } -->
-<!-- ``` -->
+The first step is to scrape the websites for the PDFs.
+
+```{r scrapingexample, echo=TRUE, eval = FALSE}
+name_of_address_to_visit <- c("wwww1", "wwww2")
+name_of_where_to_save <- c("2017-02-01.pdf", "2017-02-02.pdf")
+
+visit_address_and_save_PDF <-
+  function(name_of_address_to_visit,
+           name_of_where_to_save) {
+    # Do the actual downloading of the PDF
+    download.file(name_of_address_to_visit, name_of_where_to_save)
+    # Helpful so that you know progress when running it on all the records
+    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))
+    # Space out your requests so you don't overwhelm the website
+    Sys.sleep(sample(15:30, 1))
+  }
+```
 
@@
 
-# Sitting periods over time {#wastonywrong}
-
-**[Add the graph.]**
-
-\newpage
-
 # Topic model outputs - Economics {#topicmodeleconresultsdiscussion}

### 2018-12-14 scripts/run_6_make_graphs/make_hansard_dates_graph.R

@@ -1,77 +1,134 @@
+# Load the libraries
 library(lubridate)
 library(tidyverse)
 library(ggrepel)
 
+# Read in the data
 hansard_dates <- read_csv("inputs/misc/hansard_dates.csv")
 election_dates <- read_csv("inputs/misc/misc_elections_data.csv") %>% filter(!is.na(electionDate))
 
-hansard_dates$sitting <- 1
+hansard_dates$chamber[hansard_dates$chamber == "HoR"] <- "House of Representatives"
 
-# hansard_dates_test <- hansard_dates[6000:7500,]
-# hansard_dates$class <- c(rep(0, nrow(hansard_dates)/2), rep(1, nrow(hansard_dates)/2))
-
+# Barcode plots
+## All dates
 hansard_dates %>%
   ggplot(mapping = aes(x = hansardDates)) +
   geom_bar() +
-  # geom_vline(
-  #   data = election_dates,
-  #   aes(xintercept = electionDate),
-  #   linetype = "dashed",
-  #   color = "grey50"
-  # ) +
+  facet_wrap(vars(chamber), nrow = 2) +
   theme_classic() +
-  theme(axis.title.y = element_blank(), # GET RID OF THE Y AXIS LABELS AND TICKS
-        axis.ticks.y =  element_blank()) +
+  theme(axis.title.y = element_blank(), # Remove y axis title
+        axis.ticks.y =  element_blank(), # Remove y axis ticks
+        axis.text.y =  element_blank()) +
   labs(x = "Date",
-       title = "Sitting dates and election years",
-       caption = "Data based on available Hansard records.") +
-  theme_classic()
+       caption = "Data based on available Hansard records.") 
 
-# Maybe split the data by 30 year panels?
-
-
-hansard_dates_by_year <- hansard_dates %>%
-  mutate(year = year(hansardDates)) %>%
-  group_by(year) %>%
-  summarise(countByYear = n())
-
-write_csv(hansard_dates_by_year, "counts_by_year.csv")
+## 1920 and before
+hansard_dates %>%
+  filter(year(hansardDates) < 1920) %>% 
+  ggplot(mapping = aes(x = hansardDates)) +
+  geom_bar() +
+  facet_wrap(vars(chamber), nrow = 2) +
+  theme_classic() +
+  theme(axis.title.y = element_blank(), # Remove y axis title
[…]

### 2018-12-14 scripts/run_6_make_graphs/make_table_pdf_by_year.R

@@ -68,9 +68,12 @@ counts_by_year %>%
   gather(key = "Chamber", value = "Number", House:Senate) %>% 
   ungroup() %>% 
   ggplot(aes(x = Year, y = Number, fill = Chamber, group = Chamber)) +
-  geom_bar(stat = "identity", position = "dodge") +
+  # geom_bar(stat = "identity", position = "dodge") +
+  geom_point(aes(color = Chamber), size = 2) +
   theme_classic() +
-  scale_fill_viridis_d()
+  # scale_fill_viridis_d() +
+  scale_colour_viridis_d() +
+  ylim(0, 125)
 
 ggsave(
   "outputs/figures/counts_by_year.pdf",

### 2018-12-15 outputs/docs/events/paper.Rmd
Add stop words graph and update appendix tables

@@
 - \usepackage{makecell}
+- \usepackage{subfig}
 
@@
 
-elections <-
-  read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())
-
-governments <-
-  read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())
+# elections <-
+#   read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())
+
+# governments <-
+#   read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols())
 
@@
 In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
-And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.
 
@@
 We use the official PDF release and the formatting of the Hansard records changes over time.
-We use scripts written in R [@R2018] to convert the PDFs into daily text records.
-An example of the workflow and some example scripts are provided in Appendix \@ref(hansardworkflow).
-Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records.
+We use scripts written in R [@R2018] to convert the PDFs into daily text records.[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records.
 An example of the latter issue is that 'the' is often parsed as 'thc'.
 These errors are corrected when they can be identified.
+
+[^scriptsfootnote]: The exact scripts that we use are available on request or via the GitHub repository for this paper.
+The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
+The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014.
+The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.
 
@@
 Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.
-
-<!-- One weakness of the LDA method is that it considers a 'bag of words' where the order of those words does not matter [@blei2012].
-It is possible to extend the model to reduce the impact of the bag-of-words assumption and add conditionality to word order.
--->
 
@@
 We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
-Using this definition, there are 822 **[UPDATE]** sitting periods over the period 1901 to 2018 inclusive.
+Using this definition, there are 822 sitting periods over the period 1901 to 2018 inclusive.
 Appendix \@ref(hansardsummarystatistics) contains more information about the sitting patterns over the course of the year, which have changed considerably since Federation.
@@
 
-Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics.
-The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
-Similar to when topic models are run using the parliamentary text records of other countries, there are also some topics that appear to be about procedural or day-to-day matters, such as Topics 7 or 9.
+LDA output defines a topic as a distribution of probabilities over words.
+In Table \@ref(tab:topwords) we display the ten words with the highest association for each of the 80 topics, but the topics are defined by probability distributions over all words.
+LDA does not apply labels to each topic, or collection of words, instead this has to be done by inspection.
+The topics cover areas such as budgets, demography, transport and infrastructure, war and conflict, health, education, agriculture, and trade.
+Similar to when topic models are run using the parliamentary text records of other countries, there are also some topics that seem to be about procedural or day-to-day matters, such as Topics 7 or 9.
 As expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.
@@
 top_words %>% 
-  kable("latex", booktabs = T, longtable = TRUE, caption = "Top words associated with each topic") %>%
-  kable_styling(font_size = 8, latex_options = c("repeat_header")) %>% 
-  footnote(general = "We display only the top ten words for each topic, but the topics are defined by probability distributions over all words.")
-
+  kable("latex", 
+        booktabs = T, 
+        longtable = TRUE, 
+        caption = "The ten words most strongly associated with each topic"
+        ) %>%
+  kable_styling(font_size = 8, 
+                latex_options = c("repeat_header")
+                )
 ```
@@
 ```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
-knitr::include_graphics("../../figures/topics_example.png")
+knitr::include_graphics("../../figures/topics_example.png", auto_pdf = FALSE)
 
@@
 ```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
-knitr::include_graphics("../../figures/topics_examples_three.pdf")
-
+knitr::include_graphics("../../figures/topics_examples_three.png", auto_pdf = FALSE)
 ```
@@
 
-```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "prime minister level effects on selected topics.", out.width = '100%'}
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Level effects for prime ministers by selected topics.", out.width = '100%'}
 knitr::include_graphics("../../figures/mu_gov.pdf")
@@
 
-```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Elections level effects on selected topics", out.width = '100%'}
+```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Level effects for election periods by selected topics", out.width = '100%'}
 knitr::include_graphics("../../figures/mu_election.pdf")
@@
 
-In Appendix \@ref(resilientresults) we show that our main findings are resilient to both fewer - 60 - and more - 100 - topics.
+<!-- In Appendix \@ref(resilientresults) we show that our main findings are resilient to both fewer - 60 - and more - 100 - topics. -->
 
@@
 Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them.
-However, four of these results -- the significance of the Page Premiership, the First Menzies Premiership, the Chifley Premiership and the Abbott Premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
-The earliest of these are the First Fisher Premiership, the Cook Premiership and the Third Fisher Premiership, which were different to the Second Deakin Premiership, the Second Fisher Premiership, and the Cook Premiership, respectively.
+However, four of these results -- the significance of the Page premiership, the first Menzies premiership, the Chifley premiership and the Abbott premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
+The earliest of these are the first Fisher premiership, the Cook premiership and the third Fisher premiership, which were different to the second Deakin premiership, the second Fisher Premiership, and the Cook Premiership, respectively.
 To a certain extent this is likely due to changes due to World War I.
@@
 Future work could continue to improve the quality of this dataset.
-For instance, exploiting the availability of XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and would be used in a variety of research.
+For instance, exploiting the available XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and was more useful for variety of research.
 
@@
 That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013.
-Our paper should thus be considered a complement to more detailed analysis such as qualitative methods and case studies.
+
+Our paper should be considered a complement to more detailed analysis such as qualitative methods and case studies.
 An example of one of the more glaring issues when using topic models is the need to interpret the topics.
@@
 Another is to use the words more directly, for instance word2vec and other approaches.
-As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018, are developed this becomes a more feasible options and future research could explore that direction.
+As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018 in the context of examining congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades, are developed this becomes a more feasible options and future research could explore that direction.
 
@@
 
-Watching our politicians at work can sometimes be a little disheartening.
-It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that we voted to put them there.
+Watching Australian politicians at work can sometimes be a little disheartening.
+It can be hard to believe that not only are those in charge shouting insults that would not be tolerated in a schoolyard, but that the electorate voted to put them there.
 Nonetheless, our work suggests that important topics are discussed in parliament.
 It is easy to look back and think that we live in uniquely tumultuous times, but our analysis suggests events have always driven debate and that periods of stability may be the exception.
-However, we do find that since the 1990s the effect of prime ministers and elections on the topics discussed in the Australian parliament does seem to be more pronounced than it used to be.
+However, we do find that since the 1990s the effect of prime ministers and elections on the topics discussed in the Australian parliament does seem more pronounced than it used to be.
 
@@
 
-The distribution of sitting days over the course of the year changes over time.
+The distribution of sitting days over the course of the year changes over time (Figure \@ref(fig:allsittingdaysplotted)).
+
+```{r allsittingdaysplotted, echo=FALSE, fig.cap="All sitting days", out.width = '100%'}
+knitr::include_graphics("../../figures/sitting_dates_all.pdf")
+```
+
 It was initially more piecemeal.
@@
 
-## Example Hansard PDF to text record workflow {#hansardworkflow}
-The exact scripts that we use are too long to provide here but are available on request.
-Instead here we provide example scripts that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers.
-The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
-The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014.
-The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.
-
-**[Insert the example scripts.]**
-
-The first step is to scrape the websites for the PDFs.
-
-```{r scrapingexample, echo=TRUE, eval = FALSE}
-name_of_address_to_visit <- c("wwww1", "wwww2")
-name_of_where_to_save <- c("2017-02-01.pdf", "2017-02-02.pdf")
-
-visit_address_and_save_PDF <-
-  function(name_of_address_to_visit,
-           name_of_where_to_save) {
-    # Do the actual downloading of the PDF
-    download.file(name_of_address_to_visit, name_of_where_to_save)
-    # Helpful so that you know progress when running it on all the records
-    print(paste("Done with", name_of_where_to_save, "at", Sys.time()))
-    # Space out your requests so you don't overwhelm the website
-    Sys.sleep(sample(15:30, 1))
-  }
-```
-
-<!-- The next step is to remove the front matter from the PDFs.  -->
-
-<!-- ```{r frontmatterexample, echo=TRUE, eval = FALSE} -->
-
-<!-- get_text_from_PDFs <- -->
-<!--   function(name_of_input_PDF_file, -->
-<!--            name_of_output_csv_file) { -->
-<!--     pdf_document <- pdf_text(name_of_input_PDF_file) -->
-<!--     # Convert to tibble so that tidyverse can be used -->
-<!--     pdf_document_tibble <- tibble(text = pdf_document) -->
-<!--     rm(pdf_document) -->
-<!--     # Each row is now a page of the PDF -->
-<!--     # Adding a column of the row numbers allows you to keep track of the page numbers -->
-<!--     pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble) -->
-<!--     # Separate each line (of each page) into own row -->
-<!--     pdf_document_tibble <- -->
-<!--       separate_rows(pdf_document_tibble, text, sep = "\\n") -->
-<!--     # Identify page headers and footers and remove them -->
-<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
-<!--       group_by(pageNumbers) %>% -->
-<!--       mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page -->
-<!--       mutate(lastLine = n()) %>% # This tells you the number of the last line in each page -->
-<!--       ungroup() -->
-<!--     ## Identify front matter and remove it -->
-<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
-<!--       mutate( -->
-<!--         firstSpeakerRow = str_detect(text, "SPEAKER") -->
-<!--       ) -->
-<!--     pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA -->
-<!--     # Get the row and corresponding page and then filter to only pages from that page -->
-<!--     row_of_first_SPEAKER <- -->
-<!--       pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first() -->
-<!--     first_page_of_interest_SPEAKER <- -->
-<!--       pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer() -->
-<!--     filter_from_here <- -->
-<!--       case_when( -->
-<!--         !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER -->
-<!--       ) -->
-<!--     pdf_document_tibble <- pdf_document_tibble %>% -->
-<!--       filter(pageNumbers >= filter_from_here) %>% -->
-<!--       select(-firstSpeakerRow) -->
-<!--     # Save file -->
-<!--     write_csv(pdf_document_tibble, name_of_output_csv_file) -->
-<!--     # Helpful to know where you're up to -->
-<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
-<!--   } -->
-
-<!-- ``` -->
-
-<!-- Then the rows need to be combined: -->
-<!-- ```{r combinerows, echo=TRUE, eval = FALSE} -->
-<!-- split_columns <- -->
-<!--   function(name_of_input_csv_file, -->
-<!--            name_of_output_csv_file) { -->
-<!--     # Read in the csv, based on the filename list -->
-<!--     csv_with_rows_to_combine <- -->
-<!--       read_csv(name_of_input_csv_file, -->
-<!--                trim_ws = FALSE, -->
-<!--                col_types = cols()) -->
-<!--     # Remove any extra whitespace i.e. two or more spaces and spaces at either end.  -->
-<!--     # Yes, I know that I turned this off in the read_csv, but it's better to be  -->
-<!--     #explicit because the whitespace is useful sometimes. -->
-<!--     csv_with_rows_to_combine$text <- -->
-<!--       str_squish(csv_with_rows_to_combine$text) -->
-<!--     # Put everything onto one line, which allows us to rejoin words that have been  -->
-<!--     #split across two lines e.g. Mon- ica -->
-<!--     csv_with_rows_to_combine <- csv_with_rows_to_combine %>% -->
-<!--       mutate(text = str_replace_all(text, "-$", "MONICA")) -->
-<!--     full_days_hansard <- csv_with_rows_to_combine %>% -->
-<!--       select(-pageNumbers) %>% -->
-<!--       summarise(text = paste(text, collapse = " ")) %>% -->
-<!--       mutate(text = str_replace_all(text, "MONICA ", "")) %>% -->
-<!--       mutate(text = str_replace_all(text, "[:space:]-(?=[:alpha:])", " - ")) -->
-<!--     rm(csv_with_rows_to_combine) -->
-<!--     write_csv(full_days_hansard, name_of_output_csv_file) -->
-<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
-<!--   } -->
-<!-- ``` -->
-
-<!-- Finally, we can fix the spelling: -->
-<!-- ```{r fixspelling, echo=TRUE, eval = FALSE} -->
-<!-- fix_spelling <- -->
-<!--   function(name_of_input_csv_file, -->
-<!--            name_of_output_csv_file) { -->
-<!--     csv_to_clean <- -->
-<!--       read_csv(name_of_input_csv_file, -->
-<!--                trim_ws = FALSE, -->
-<!--                col_types = cols()) -->
-<!--     #Fix the spelling -->
-<!--     csv_to_clean$text <- -->
-<!--       stri_replace_all_regex( -->
-<!--         csv_to_clean$text, -->
-<!--         "\\b" %s+% fix_wrong_spellings$original %s+% "\\b", -->
-<!--         fix_wrong_spellings$corrected, -->
-<!--         vectorize_all = FALSE -->
-<!--       ) -->
-<!--     # Save file -->
-<!--     write_csv(csv_to_clean, name_of_output_csv_file) -->
-<!--     print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time())) -->
-<!--   } -->
-<!-- ``` -->
-
-\newpage
-
 ## Stopwords over time {#stopwordsgraph}
-**[Insert the graph of stop words over time.]**
+
+Figure \@ref(fig:stopwordsproportion) shows the proportion of five common words -- 'and', 'be', 'of', 'the', 'to' -- compared with the total number of words over time.
+
+```{r stopwordsproportion, echo=FALSE, fig.cap="Proportion that some common words comprise of all words, over time", out.width = '100%'}
+knitr::include_graphics("../../figures/stop_words.pdf")
+```
 
@@
 
+The first of the two types of events that we consider in this paper is an election (Table \@ref(tab:elections)).
+
 ```{r elections, echo = FALSE, results = 'asis'}
 
-elections %>% 
+read_csv("../../../outputs/misc/misc_elections.csv", col_types = cols())  %>% 
   filter(election == 1) %>% 
   select(-election, -comment) %>%
-  kable("latex", booktabs = T, caption = "Elections") %>%
-  kable_styling(font_size = 8)
-
-```
+  select(election_count, everything()) %>% 
+  rename(
+    "Number" = "election_count",
+    "Year" = "year", 
+    "Date" = "electionDate", 
+    "Total seats" = "seatsTotalNumber", 
+    "Winner" = "electionWinner"
+    ) %>%  
+  kable("latex", 
+        booktabs = T, 
+        longtable = TRUE, 
+        caption = "List of Australian elections"
+        ) %>%
+  kable_styling(font_size = 8) %>% 
+  footnote(
+    general = "This table contains summary information for each prime minister of Australia. HoR and Senate refer to the number of days that each chamber sat for between elections.",
+    footnote_as_chunk = T, 
+    threeparttable = TRUE
+    )
+
+```
+
+Between 1901 and 2018 there are 45 elections, roughly one every two to three years.
+All of the election periods have a reasonable number of sitting days within them.
+The fewest was the election on 17 November 1928, with only 40 sitting days in the House of Representatives and 29 in the Senate, as there was another election almost a year later on 12 October 1929.
+
+The number of seats increases from 74 to 121 at the 10 December 1949 election, having been reasonably consistent to that point.
+Another large increase in the number of seats, this time from 125 to 148, happens at the 1 December 1984 election.
+
+In the first half of our sample especially, the name of the major opposition party changes.
+For this reason we distinguish between the Labor Party, and the non-Labor Party in terms of who won the election, that is which party was able to form government.
 
@@
 
+The second of the two types of events that we consider in this paper is a change in prime minister (Table \@ref(tab:governments)).
+
 ```{r governments, echo = FALSE, results = 'asis'}
 
-governments %>%
+read_csv("../../../outputs/misc/pm_dates.csv", col_types = cols()) %>%
   rename(
@@
     ) %>% 
-  kable(booktabs = T, caption = "Change in prime ministers") %>%
-  kable_styling(font_size = 8) %>% 
+  kable(booktabs = T, 
+        longtable = TRUE, 
+        caption = "List of Australian prime ministers"
+        ) %>%
+  kable_styling(font_size = 8
+                ) %>% 
   footnote(general = "This table contains summary information for each prime minister of Australia.
@@
 
+Between 1901 and 2018 30 different people have been prime minister.
+Four of those---Deakin, Fisher, Menzies and Rudd---returned to the primiership at least once after being replaced, meaning Scott Morrison defines the 36th prime ministerial period.
+
+Three people have died while prime minister: Lyons in 1939, Curtin in 1945, and Holt in 1967.
+Their respective immediate successors were only prime minister for a short period.
+As such, we do not consider them when determining the neighbouring prime minister.
+Specifically, we compare: the first Menzies premiership with Lyons instead of Page; Chifley with Curtin instead of with Forde; and Gorton with Holt instead of with McEwan.
+
+The other prime ministerial period that we do not consider in this paper is the second Rudd premiership This is because it only contained a few sitting days.
+That is, we compare Tony Abbot with Julia Gillard.
+
 <!-- \newpage -->
@@
 
+<!-- \newpage -->
+
+<!-- # Effect of number of topics on analysis model results {#resilientresults} -->
+
+<!-- **[Add results for 60 and 100 topics.]** -->
+
+<!-- **[Add Lior's idea about running the model for 60 and for 100 and then showing that the main results don't change.]** -->
+
 \newpage
 
-# Effect of number of topics on analysis model results {#resilientresults}
-
-**[Add results for 60 and 100 topics.]**
-
-<!-- **[Add Lior's idea about running the model for 60 and for 100 and then showing that the main results don't change.]** -->
-
-\newpage
-
 <!-- # Analysis model {#modeldetailsandsimulation} -->

### 2018-12-15 scripts/run_6_make_graphs/make_hansard_dates_graph.R

@@ -132,3 +132,26 @@ test <- hansard_dates %>%
   geom_bar() +
   scale_y_continuous(trans = "log")
 
+
+  
+  
+  
+hansard_dates %>%
+  ggplot(mapping = aes(x = yday(hansardDates), 
+                       y = year(hansardDates))) +
+  geom_point(size = 0.25) +
+  facet_wrap(vars(chamber), ncol = 2) +
+  theme_classic() +
+  labs(x = "Day of year",
+       # caption = "Data based on Hansard PDF records available at https://parlinfo.aph.gov.au.",
+       y = "Year"
+       )
+
+  
+  
+ggsave(
+  "outputs/figures/sitting_dates_all.pdf",
+  height = 12,
+  width = 10,
+  units = "in"
+  )

### 2018-12-15 scripts/run_6_make_graphs/make_stop_words.R

@@ -1,0 +1,55 @@
+library(lubridate)
+library(purrr)
+library(stringr)
+library(tidyverse)
+
+str_count("Hey the Malcolm the ex PM", "the")
+str_count("Hey the Malcolm the ex PM", " ")
+
+
+# Get the data
+# House
+# From: https://github.com/STAT545-UBC/Discussion/issues/398
+reps_files <- list.files(path = "outputs/hansard/tempp", full.names = TRUE)
+
+names(reps_files) <- list.files(path = "outputs/hansard/tempp") %>% 
+  gsub(pattern = ".csv$", replacement = "")
+
+all_data <- purrr::map_df(reps_files, readr::read_csv, .id = "Date")
+
+# Check the
+all_data$the_count <- str_count(all_data$text, " the ")
+all_data$and_count <- str_count(all_data$text, " and ")
+all_data$be_count <- str_count(all_data$text, " be ")
+all_data$to_count <- str_count(all_data$text, " to ")
+all_data$of_count <- str_count(all_data$text, " of ")
+
+all_data$word_count <- str_count(all_data$text, " ")
+
+all_data$Date <- ymd(all_data$Date)
+
+stop_words_data <- all_data %>%
+  group_by(Date) %>% 
+  summarise(the = sum(the_count),
+            be = sum(be_count),
+            to = sum(to_count),
+            of = sum(of_count),
+            and = sum(and_count),
+            all_words = sum(word_count))
+
+stop_words_data %>% 
+  gather(key = "Word", value = "Count", the, be, to, of, and) %>% 
+  mutate(Proportion = Count / all_words) %>% 
+    ggplot(aes(x = Date, y = Proportion, color = Word)) +
+    geom_point() +
+    ylim(0, 0.10) +
+    theme_classic() +
+  scale_color_viridis_d()
+
+
+ggsave(
+  "outputs/figures/stop_words.pdf",
+  height = 6,
+  width = 8,
+  units = "in"
+)

### 2018-12-15 outputs/docs/events/paper.Rmd
Add economics examples

@@
 
-**[Insert the econ examples. Zoom in on the Great Depression, the Premiers' Plan, the 80s/90s, privatisation debate.]**
+In Figure \@ref(fig:greatd) we focus on the period around the Great Depression and the Premiers' Plan.
+
+```{r greatd, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes around the the Great Depression", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_example-GreatD.pdf")
+```
+
+In Figure \@ref(fig:theeightsnighties) we focus on the period of the 1980s and 1990s when there was a great deal of economic change.
+
+```{r theeightsnighties, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes during the 1980s and 1990s", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_example-the80s.pdf")
+```
+
+In Figure \@ref(fig:economicsgfc) we focus on the financial crisis of 2007-08.
+
+```{r economicsgfc, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes around the 2007-08 financial crisis", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_example-GFC.pdf")
+```
 

### 2018-12-15 scripts/run_6_make_graphs/make_graph_of_topics-economics.R

@@ -4,20 +4,20 @@ library(lubridate)
 library(tidyverse)
 
 td_gamma <- read_csv("outputs/results-topic_models_and_gammas/gammas_model_80.csv")
-dates <- read_csv("outputs/results-topic_models_and_gammas/dates.csv")
+# dates <- read_csv("outputs/results-topic_models_and_gammas/dates.csv")
 
 head(td_gamma)
 
-td_gamma <- td_gamma %>% 
+td_gamma <- td_gamma %>%
   separate(document, into = c("chamber", "date"), sep = "-", extra = "merge")
 
 td_gamma$chamber[td_gamma$chamber == "hor"] <- "House of Representatives"
 td_gamma$chamber[td_gamma$chamber == "senate"] <- "Senate"
 
-
 td_gamma$date <- ymd(td_gamma$date)
 
-# td_gamma$document %>% unique() %>% length()
+
+# td_gamma$date %>% unique() %>% length()
 
 # td_gamma$date <- rep(dates$dates, 60)
 
@@ -26,27 +26,145 @@ td_gamma$date <- ymd(td_gamma$date)
 #   sample_frac(0.05) # reduce to 5 per cent of the dataset so that it doesn't take an age to load
 
 
-# For paper
+# Great Depression
 td_gamma_reduced <- td_gamma %>% 
-  filter(topic %in% c(17, 22, 25, 44, 51, 55, 59, 71, 72, 74, 76, 77))
+  filter(topic %in% c(17, 22, 25, 44, 51, 55, 59, 71, 72, 74, 76, 77)) 
+# %>% 
+#   filter(topic %in% c(51, 55, 59))
 
-ggplot(data = td_gamma, aes(x = date, y = gamma, color = as.factor(topic))) +
-  # geom_point(color = "grey", alpha = 0.5, size = 0.5) +
-  # geom_point(data = td_gamma_reduced, size = 0.5) +
-  geom_smooth(data = td_gamma_reduced, method = loess) +
-  theme_minimal() +
+td_gamma_reduced <- td_gamma_reduced %>% 
+  filter(date >= "1928-01-01") %>% 
+  filter(date <= "1932-12-31") 
+
+labels <- tibble(
+  date = c(ymd("1929-10-29"), ymd("1931-06-11")),
+  label_with_this = c("Black Tuesday", "Premiers' Plan"),
+  height = c(0.65, 0.60)
+)
+
+
+ggplot(data = td_gamma_reduced, 
+       aes(x = date, 
+           y = gamma, 
[…]

### 2018-12-15 outputs/docs/events/paper.Rmd
SECOND DRAFT DONE

@@
 
-The first panel of Figure \@ref(fig:threeexamples) is the second Menzies premiership.
+The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term.
 The dashed lines show the elections.
@@
 We would like the analysis model to be able to distinguish between the two if they seem different.
-The third panel shows the first Rudd premiership.
-The important aspect to note is that the period after the 2007 election and the Rudd premiership contain essentially the same Hansard dates.
+The third panel shows the first Rudd term.
+The important aspect to note is that the period after the 2007 election and the Rudd term contain essentially the same Hansard dates.
 The analysis model needs to be able to deal with this situation.
@@
   footnote(
-    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during this premiership, compared with the previous one.",
+    general = "The significance of a prime minister is determined by whether at least one topic was significantly different during this term, compared with the previous one.",
     footnote_as_chunk = T,
@@
 Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them.
-However, four of these results -- the significance of the Page premiership, the first Menzies premiership, the Chifley premiership and the Abbott premiership -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
-The earliest of these are the first Fisher premiership, the Cook premiership and the third Fisher premiership, which were different to the second Deakin premiership, the second Fisher Premiership, and the Cook Premiership, respectively.
+However, four of these results -- the significance of the Page term, the first Menzies term, the Chifley term and the Abbott term -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
+The earliest of these are the first Fisher term, the Cook term and the third Fisher term, which were different to the second Deakin term, the second Fisher term, and the Cook term, respectively.
 To a certain extent this is likely due to changes due to World War I.
 
-The Second Menzies Premiership, begining in 1949, is the next government that is significantly different to its predecessor.
+The second Menzies term, beginning in 1949, is the next government that is significantly different to its predecessor.
 The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
@@
 
-The Second Menzies Premiership was associated with a variety of changes compared with the preceding Chifley Government.
-The Chifley Premiership had governed through the end of World War II and the difficult economic times that followed.
+The second Menzies term was associated with a variety of changes compared with the preceding Chifley Government.
+Chifley had governed through the end of World War II and the difficult economic times that followed.
 There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
 Many new politicians entered parliament, and this changed representation may also have been partly to do with the changed distribution of discussion topics, although further investigation of this is left for future work.
-The sixteen-year length of the Second Menzies Premiership, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
-There were six elections within the Second Menzies Premiership Three toward the middle of that government were associated with significant changes in the topics discussed.
-
-The Menzies Premiership was succeeded by the Holt Premiership in January 1966.
+The sixteen-year length of the second Menzies term, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
+There were six elections within the second Menzies term.
+Three toward the middle of that government were associated with significant changes in the topics discussed.
+
+Menzies was succeeded  Holt in January 1966.
 This is an example where there was a change in prime minister without an election, as the next election only happened in November 1966.
-We find that the Holt Premiership is different to the Menzies Premiership In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Premiership with the topics of the Holt Premiership
+We find that Holt is different to Menzies.
+In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt.
 
@@
 
-The Whitlam Premiership is especially interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam Premiership.
-
-The Howard Premiership is also interesting because of the significant differences between elections.
+Whitlam's term is especially interesting as we find a difference in the topics after he was first elected in December 1972, compared with his second election win in May 1974.
+Figure \@ref(fig:muelectionall) compares the topics that are significant before and after the election.
+
+Howard is also interesting because of the significant differences between elections.
 For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
+Figure \@ref(fig:muelectionall) compares the topics that are significant in the different elections that Howard won.
 
@@
 However, the change in 1998 and 2004 is more unexpected.
-Although the Howard Premiership is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Premiership as a combination of three or four different periods and that the Howard Premiership reinvented itself over this period.
+Although Howard is the second-longest serving prime minister and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of Howard as a combination of three or four different periods and that Howard reinvented itself over this period.
 
@@
 But there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
-When we dig into this we find that some of them, such as 4 February 2009, are associated with significant legislation.
+When we examine this we find that some of them, such as 4 February 2009, are associated with significant legislation.
 However the over-weighting of dates in the first half of our sample in Table \@ref(tab:keyeventsresultstable) highlights further work is needed to improve this approach.
@@
 Residuals analysis, @Taddy2012, compares the theoretical distribution of the variance with the actual distribution.
-It is a test for overdispersion of the variance, and if it is found then this can suggest that more topics would be appropriate.
+It is a test for over-dispersion of the variance, and if it is found then this can suggest that more topics would be appropriate.
 Semantic coherence is the trade-off for having topics that are more specific and the subsequent risk that the topics become meaningless.
@@
 One of the limitations of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic.
-In reality often topics are related.
+In reality, topics are often related.
 For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
@@
 
-In Figure \@ref(fig:theeightsnighties) we focus on the period of the 1980s and 1990s when there was a great deal of economic change.
+The notable aspect of the response to the 1929 'Black Tuesday' stock market declines was the Premiers' Plan, which appeared newspapers on 11 June 1931.
+@Copland1934 describes the differences of opinion that occurred in the lead-up to the plan, but Figure \@ref(fig:greatd) highlights how new the Scullin Government was when the economic troubles began.
+
+In Figure \@ref(fig:theeightsnighties) we focus on the 1980s and 1990s when there was a great deal of economic change.
 
@@
 
-In Figure \@ref(fig:economicsgfc) we focus on the financial crisis of 2007-08.
+One notable aspect is the difference between the House of Representatives and the Senate that the proportion of economic topics accounts for.
+The emphasis that the Hawke/Keating government placed on economic issues comes through clearly given the clear change following Hawke's election.
+
+Finally, in Figure \@ref(fig:economicsgfc) we focus on the financial crisis of 2007-08.
 
@@
 ```
+
+It is notable that despite the enormous importance of the financial crisis of 2007-08, topics that are clearly related to economic issues do not dominate the discussion in either house.
 
@@
 Between 1901 and 2018 30 different people have been prime minister.
-Four of those---Deakin, Fisher, Menzies and Rudd---returned to the primiership at least once after being replaced, meaning Scott Morrison defines the 36th prime ministerial period.
+Four of those---Deakin, Fisher, Menzies and Rudd---returned as prime minister at least once after being replaced, meaning Scott Morrison defines the 36th prime ministerial period.
 
@@
 As such, we do not consider them when determining the neighbouring prime minister.
-Specifically, we compare: the first Menzies premiership with Lyons instead of Page; Chifley with Curtin instead of with Forde; and Gorton with Holt instead of with McEwan.
-
-The other prime ministerial period that we do not consider in this paper is the second Rudd premiership This is because it only contained a few sitting days.
+Specifically, we compare: the first Menzies term with Lyons instead of Page; Chifley with Curtin instead of with Forde; and Gorton with Holt instead of with McEwan.
+
+The other prime ministerial period that we do not consider in this paper is the second Rudd term This is because it only contained a few sitting days.
 That is, we compare Tony Abbot with Julia Gillard.

### 2018-12-15 scripts/run_6_make_graphs/make_graph_of_topics-economics.R

@@ -39,8 +39,17 @@ td_gamma_reduced <- td_gamma_reduced %>%
 labels <- tibble(
   date = c(ymd("1929-10-29"), ymd("1931-06-11")),
   label_with_this = c("Black Tuesday", "Premiers' Plan"),
-  height = c(0.65, 0.60)
+  height = c(0.60, 0.55)
 )
+
+
+pms <- tibble(
+  date = c(ymd("1929-10-22", "1932-01-06")),
+  label_with_this = c("Scullin", "Lyons"),
+  height = c(0.65, 0.65)
+)
+
+
 
 
 ggplot(data = td_gamma_reduced, 
@@ -51,6 +60,8 @@ ggplot(data = td_gamma_reduced,
   geom_jitter(size = 0.5) +
   geom_smooth() +
   geom_vline(data = labels, aes(xintercept = date), linetype = "dashed") +
+  geom_vline(data = pms, aes(xintercept = date), linetype = "dotted") +
+  geom_label(data = pms, aes(x = date, y = height, label = label_with_this, color = "black"), color = "black") +
   geom_label(data = labels, aes(x = date, y = height, label = label_with_this, color = "black"), color = "black") +
   theme_classic() +
   labs(x = "Date",
@@ -70,51 +81,6 @@ ggsave(
 
 
 
-# Financial criss
-
-# For paper
-td_gamma_reduced <- td_gamma %>% 
-  filter(topic %in% c(17, 22, 25, 44, 51, 55, 59, 71, 72, 74, 76, 77)) 
-# %>% 
-#   filter(topic %in% c(51, 55, 59))
-
-td_gamma_reduced <- td_gamma_reduced %>% 
-  filter(date >= "2007-01-01") %>% 
-  filter(date <= "2010-12-31") 
-
-labels <- tibble(
-  date = c(ymd("2008-09-15")),
-  label_with_this = c("Lehman Brothers"),
-  height = c(0.60)
-)
-
-
-
-ggplot(data = td_gamma_reduced, 
-       aes(x = date, 
-           y = gamma, 
-           color = as.factor(topic))
-) +
-  geom_jitter(size = 0.5) +
-  geom_smooth() +
-  geom_vline(data = labels, aes(xintercept = date), linetype = "dashed") +
-  geom_label(data = labels, aes(x = date, y = height, label = label_with_this, color = "black"), color = "black") +
-  theme_classic() +
-  labs(x = "Date",
-       y = "Proportion") +
-  facet_wrap(vars(chamber), ncol = 2) +
[…]

### 2018-12-19 outputs/docs/paper/paper.Rmd
Update parsing

--- 2018-12-15 outputs/docs/events/paper.Rmd
@@
 We have records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).
-In contrast to the US, but similar to Canada and the UK, the executive is drawn from the legislature, and the Australian prime minister typically sits in the lower house.
+In contrast to the US, but similar to Canada and the UK, in Australia the executive is drawn from the legislature, and the prime minister typically sits in the lower house.
 Unlike Canada or the UK, both houses are elected, although each has different mechanisms and constituencies.
@@
 
-Our work contributes to the growing literature that considers text as an input to statistical methods.
-This literature sits across and draws from various historically-separate disciplines including applied statistics, economics, and political science.
+Our work contributes to the growing literature that analyses text using quantitative methods.
+It sits across, and draws from, various historically-separate disciplines including applied statistics, economics, and political science.
 In addition to our findings about the effect of events in Australian politics, we contribute to this literature in terms of both data and methods.
@@
 These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
-There are many avenues for closely related future work such as: investigating the effect of other types of events; including a richer set of covariates to tease out the reason for different effects; and reversing the causality to examine the effect of what is said in parliament on various outcomes.
+There are many avenues for closely related future work such as: investigating the effect of other types of events; including a richer set of covariates to disentangle the reason for different effects; and reversing the causality to examine the effect of what is said in parliament on various outcomes.
 
@@
 The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales.
-We do not stem the words because @SchofieldMimno2016 suggest that there may not be any significant benefit.
+We do not stem the words because we found, following @SchofieldMimno2016, that there did not appear to be much appreciable benefit.
 Then the sentences are de-constructed and each word considered individually.
@@
 That said, the approach has well-known shortcomings and weaknesses, such as those documented by @GrimmerStewart2013.
-
-Our paper should be considered a complement to more detailed analysis such as qualitative methods and case studies.
-An example of one of the more glaring issues when using topic models is the need to interpret the topics.
-This can be difficult, especially when the number of topics is large, but in a dataset of the size that we have, a large number of topics is needed.
-Also, although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
-Most obviously the number of topics needs to be specified, but there are also more nuanced aspects to be aware of.
+Because of these, our paper should be considered a complement to more detailed analysis such as qualitative methods and case studies.
+
+An obvious weakness of topic models is that the number of topics needs to be specified but there is rarely a clear reason to choose some particular number.
+There are also more nuanced weaknesses to be aware of.
+For instance, the topics need to be interpreted.
+Some of our topics were not overly meaningful, especially on their own.
+Interpretation is especially difficult when the number of topics is large, but we found that a large number of topics worked best for our dataset.
+
+Although topic modelling is an unsupervised machine learning technique, the inputs require fine-tuning.
 For instance, selecting stop words for removal and which words to merge because of common co-location has an impact on the topics.
-Even after doing this there tend to be topics that are not overly meaningful, especially on their own.
+Topic model outcomes are known to be sensitive to preprocessing [@DennySpirling2018] and ours was no exception.
+
 One way to get around using topic models is to use a supervised learning approach, such as that used by @AshMorelliOsnabru2018 in the context of New Zealand Hansard.
 Another is to use the words more directly, for instance word2vec and other approaches.
-As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018 in the context of examining congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades, are developed this becomes a more feasible options and future research could explore that direction.
+As computational power become cheaper and more appropriate analytical methods, such as @Taddy2015 as applied in @GentzkowShapiroTaddy2018 in the context of examining congressional speech records, are developed this becomes a more feasible options and future research could explore that direction.
 

### 2018-12-19 outputs/docs/slides/slides.Rmd
Update parsing

--- 2018-12-11 outputs/docs/events/slides/slides.Rmd
@@
 ```{r exampletopics, echo=FALSE, out.width = '100%'}
-knitr::include_graphics("../../../figures/topics_example_slides_update.png")
+knitr::include_graphics("../../../figures/topics_examples_three_one.png")
 ```
-
-## Structural Topic Model
-The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information. 
-$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
-Again, sounds easy, but hard to implement, and they have a very nice algorithm.
 
@@
 - We use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework.
-- This relates the proportions of each topic to underlying time trends, changes in governments and elections. 
+- This relates the proportions of each topic to underlying time trends, changes in prime minister and elections. 
 - This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
@@
 ## Analysis model - Set-up
-- Define $\theta_{dp}$ to be the proportion of topic of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=80$ are equal to the estimated values of $\theta_d$ from the CTM. 
+- Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$. Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P=80$ are equal to the estimated values of $\theta_d$ from the CTM. 
 - We assume that the majority of variation in topics is across sitting periods $s$, where a sitting period is defined as any group of days that are less than one week apart.
@@
 
-The goal of the model is to relate these proportions to government $g$ at time $d$, and also the days since the most recent election, $e$, while account for underlying time trends.
+The goal of the model is to relate these proportions to prime minister $g$ at time $d$, and also the days since the most recent election, $e$, while accounting for underlying time trends.
 
@@
 
-- $\alpha_{g[s],p}$ is the mean effect for government $g$ (which covers sitting period $s$) and topic $p$;
+- $\alpha_{g[s],p}$ is the mean effect for prime minister $g$ (which covers sitting period $s$) and topic $p$;
 - $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election;
@@
 
-## Analysis model - Government effects
+## Analysis model - Prime minister effects
 
-The government term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each government on the topic distribution.
+The prime minister term $\alpha_{g[s],p}$ assumes there is some underlying mean effect of each prime minister on the topic distribution.
 We place uninformative priors on each of these parameters: $\alpha_{g[s],p} \sim \mbox{Normal}(0, 100)$
@@
 
-The sitting period-specific random effect $\delta_{s,p}$ allows the topic distributions in some sitting periods to be different than expected based on government and election effects:
+The sitting period-specific random effect $\delta_{s,p}$ allows the topic distributions in some sitting periods to be different than expected based on prime minister and election effects:
 $$
@@
 
-## Analysis model - Estimates by sitting period
+<!-- ## Analysis model - Estimates by sitting period -->
 
@@
 -->
-
-```{r wartopicsgraph, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
-knitr::include_graphics("../../../figures/war_stack-slides.pdf")
-```
 
@@
 
-## Analysis model - Significantly different governments
+## Analysis model - Significantly different prime ministers
 
@@
 
-## Analysis model - Significantly different governments (cont.)
+## Analysis model - Significantly different prime ministers (cont.)
 
@@
 
-## Analysis model - All governments
+## Analysis model - All prime ministers
 
@@
 
-## Analysis model - Events
+<!-- ## Analysis model - Events -->
 <!-- Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision.
@@
 
-```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
-
-key_events_results_cols %>%
-  kable() %>%
-  kable_styling(font_size = 10)
-
-```
-
 <!-- Finally, Figure \@ref(fig:sigmaelection) illustrates the estimated standard deviation of topic distributions, around the mean election effect, over time.
@@
 
-<!-- Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them.
-However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12.
-The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively.
-To a certain extent this is likely tied up with changes due to World War I.
--->
-
-<!-- The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor.
-The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
-Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor.
-1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
--->
-
-<!-- The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government.
-The Chifley Government had governed through the end of World War II and the difficult economic times that followed.
-There was also a large increase in the number of seats in the House of Representatives at the 1949 election.
-Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics.
-The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.
--->
-
-<!-- There were six elections within the second Menzies Government.
-However we do not find that any of those elections was associated with a significant change in the topics discussed.
-In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.
--->
-
-<!-- The Menzies Government was succeeded by the Holt Government in January 1966.
-This is an example where there was a change in government without an election, as the next election only happened in November 1966.
-We find that the Holt Government is significantly different to the Menzies Government.
-In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.
--->
-
 ```{r muelectionmenziesholt, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
@@
 
-## Whitlam re-election
+<!-- ## Whitlam re-election -->
 
-```{r muelectionwhitlam, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"}
-knitr::include_graphics("../../../figures/mu_election-differences-whitlam-slides.pdf")
-```
-
-<!-- The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.
--->
+<!-- ```{r muelectionwhitlam, cache = TRUE, echo = FALSE, out.width = '100%', fig.align="center"} -->
+<!-- knitr::include_graphics("../../../figures/mu_election-differences-whitlam-slides.pdf") -->
+<!-- ``` -->
 
@@
 ```
-
-<!-- The Howard Government is interesting because of the significant differences between elections.
-For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level.
-Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.
--->
-
-<!-- To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
-However the change in 1998 and 2004 is more unexpected.
-Although the Howard Government is the second-longest serving government and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of the Howard Government as a combination of three or four different periods and that the Howard Government reinvented itself over this period.
--->
-
-<!-- One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent.
-The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement.
-For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
-It also appropriately identifies some of other key events that we were interested in.
-However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
-Further work is needed to improve this approach.
-For instance, our approach may not be appropriately considering step-changes.
--->
 
@@
 
+## Structural Topic Model
+The Structural Topic Model approach then adds a covariate to $\mu$ which allows consideration of additional information.
+$$\theta_d|X_d\gamma\Sigma \sim \mbox{Logistic Normal}(\mu = X_d\gamma, \Sigma)$$
+Again, sounds easy, but hard to implement, and they have a very nice algorithm.
+
 ## Why not use STM?

### 2018-12-19 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -245,20 +245,19 @@ get_text_from_PDFs <-
 
 
 #### Walk through the lists and parse the PDFs ####
-# tic("Normal walk2")
-# walk2(file_names, save_names, ~ get_text_from_PDFs(.x, .y))
-# toc()
-
 safely_get_text_from_PDFs <- safely(get_text_from_PDFs)
-
 # file_names <- file_names[1:10]
 # save_names <- save_names[1:10]
 # file_names <- file_names[1:(length(file_names)/2)]
 # save_names <- save_names[1:(length(save_names)/2)]
-
 tic("Furrr walk2 stringr")
 future_walk2(file_names,
              save_names,
              ~ safely_get_text_from_PDFs(.x, .y),
              .progress = TRUE)
 toc()
+
+
+walk2(file_names,
+      save_names,
+      ~ safely_get_text_from_PDFs(.x, .y))

### 2018-12-19 scripts/run_2_parse_pdfs/run_2_split_columns.R

@@ -61,7 +61,7 @@ split_columns <-
   function(name_of_input_csv_file,
            name_of_output_csv_file) {
     # Read in the csv, based on the filename list
-    # name_of_input_csv_file <- "outputs/hansard/temp/1971-10-05.csv" # uncomment for testing
+    # name_of_input_csv_file <- "outputs/hansard/temp/1971-03-30.csv" # uncomment for testing
     # name_of_input_csv_file <- "senate.csv" # uncomment for testing
     
     csv_to_split <-
@@ -234,6 +234,10 @@ split_columns <-
 # toc()
 
 safely_split_columns <- safely(split_columns)
+
+walk2(file_names,
+      save_names,
+      ~ safely_split_columns(.x, .y))
 
 tic("Furrr walk2 stringr")
 future_walk2(file_names,

### 2018-12-19 scripts/run_2_parse_pdfs/run_3_split_out_speakers.R

@@ -73,6 +73,7 @@ split_columns <-
     
     full_days_hansard <- csv_with_rows_to_combine
     
+    
     # Clean the text a little more - toward making it possible to identify the politicians
     full_days_hansard$text <-
       str_replace_all(
@@ -154,53 +155,54 @@ split_columns <-
       )
     
     on_the_regular <- paste(
-      "(?<=(Mr [:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Mr [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Mr [:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Mr [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Mr [:upper:]{1,30}[:blank:]?(\\(.{1,20})\\)))-",
-      "(?<=(Mrs [:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Mrs [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Mrs [:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Mrs [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Ms [:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Ms [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Ms [:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Ms [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Dr [:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Dr [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))-",
-      "(?<=(Dr [:upper:]{1,30}[:blank:]?))\\(",
-      "(?<=(Dr [:upper:]{1,30}[:blank:]?(\\(.{1,20})\\)))-",
-      "(?<=(Dr [:upper:]{1,30}[:blank:][:upper:]{1,30}[:blank:]?))\\(",
[…]

### 2018-12-19 scripts/run_2_parse_pdfs/run_4_split_out_titles_and_stage_directions.R

@@ -1,7 +1,3 @@
-
-
-
-
 # Misc other:
 # Motion (by Mr OHIFUBY). agreed .to-
 # Honorable members interjecting,
@@ -10,10 +6,124 @@
 # Mrs Sudmalis interjecting-
 
 
-
-
-
 # There's a contents pages at the end of 2001-08-09. WTF.
 # 2003-02-13.pdf - Not there
 # 2001-08-09.pdf - There
 # 1998-04-09.pdf - Not there
+
+
+# !diagnostics off
+#### Preamble ####
+# Purpose: This file takes Australian Hansard CSV files and isolates the name of the person speaking into a separate column.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 18 December 2018
+# Prerequisites: 1) Download the PDFs; 2) read them into CSVs; 3) get rid of the front matter; 4) split the columns. For testing purposes there should be some Hansard PDFs in the /outputs/hansard/ folder.
+# To do:
+
+
+#### Set up workspace ####
+# devtools::install_github("DavisVaughan/furrr")
+library(furrr)
+# install.packages('lubridate')
+library(lubridate)
+library(stringi)
+library(tidyverse)
+# install.packages('tictoc')
+library(tictoc)
+# library(tm)
+# update.packages()
+# Set up furrr
+plan(multiprocess)
+
+
+#### Create lists of CSVs to read ####
+# Change the path as required:
+use_this_path_to_get_csvs  <- "outputs/hansard/temp"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+
+# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
+file_names <-
+  list.files(
+    path = use_this_path_to_get_csvs,
+    pattern = "*.csv",
+    recursive = FALSE,
+    full.names = TRUE
+  )
+
+file_names <- file_names %>% sample() # Randomise the order
+
+# Seems unnecessary, but sometimes useful to separate input and output
+use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
+# use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+save_names <- file_names %>%
+  str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
+
+
+
+#### Create the function that will be applied to the files
+split_titles <-
+  function(name_of_input_csv_file,
+           name_of_output_csv_file) {
[…]

### 2018-12-19 scripts/run_2_parse_pdfs/run_5_combine rows.R

@@ -40,7 +40,7 @@ file_names <-
 file_names <- file_names %>% sample() # Randomise the order
 
 # Seems unnecessary, but sometimes useful to separate input and output
-use_this_path_to_save_csvs  <- "outputs/hansard/tempp"
+use_this_path_to_save_csvs  <- "outputs/hansard/temp"
 # use_this_path_to_save_csvs <- "/Volumes/Hansard/parsed/federal/hor"
 save_names <- file_names %>%
   str_replace(use_this_path_to_get_csvs, use_this_path_to_save_csvs)
@@ -115,3 +115,9 @@ future_walk2(file_names,
              ~ safely_split_columns(.x, .y),
              .progress = TRUE)
 toc()
+
+walk2(file_names,
+      save_names,
+      ~ safely_split_columns(.x, .y)
+      )
+

### 2019-01-10 outputs/docs/paper/paper.Rmd
model changes

@@
 In the STM framework, it is possible to specify a constant or linear effect of elections over time, or a spline relationship over elections, but it is not possible to restrict the effect of a specific election over time to be monotonically decreasing.
+We are interested in time effects within election periods, which requires a more flexible framework.
 2.
@@
 However, it could be expected that topic distributions within a particular prime minister's time, for example, may be more- or less-likely to contain certain topics for reasons that are not reflected in the topic prevalence covariates.
-To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period.
+To account for this, we would like a covariate model that allows for the partial pooling of variance in topic distributions by group, such as sitting period, or election period.
 3.
@@
 For example, if we think that the 9/11 attacks had an effect on parliamentary discourse, then a dummy for 9/11 would have to be included in the STM framework, but the specifics of the dummy construction affect the results.
-Instead we would like to identify important events based on different-to-expected topic distributions, after accounting for time trends, prime minister and election effects.
+Instead we would like to identify important events based on different-to-expected topic distributions, after accounting for prime minister and election effects.
 
@@
 
-Define $\theta_{dp}$ to be the proportion of topic $p$ on day $d$.
-Note that the $\theta_{d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_d$ from the CTM.
-We assume that the majority of variation in topics is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
+Define $\theta_{cdp}$ to be the proportion of topic $p$ on day $d$ in chamber $c$ (where chamber refers to either the House of Representatives or the Senate).
+Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_{cd}$ from the CTM.
+We assume that the majority of variation in topics by day is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
 Using this definition, there are 822 sitting periods over the period 1901 to 2018 inclusive.
@@
 
-The topic proportions on day $d$ are modelled in reference to their membership of a particular sitting period $s$.
-Firstly, we assume that each distribution of topics, $\theta_{d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[d],1:P}$:
+The topic proportions on day $d$ in chamber $c$ are modelled in reference to their membership of a particular sitting period $s$.
+Firstly, we assume that each distribution of topics, $\theta_{c,d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[c,d],1:P}$:
 $$
-\theta_{d,1:P} \sim \mbox{Dirichlet}(\mu_{s[d],1:P})
+\theta_{c,d,1:P} \sim \mbox{Dirichlet}(\mu_{s[c,d],1:P})
 $$
-where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ belongs.
-This distributional assumption accounts for the fact that on any given day, the sum of all proportions in each topic must be one.
-
-The goal of the model is to relate these proportions to the prime minister $g$, at time $d$, and also the days since the most recent election $e$, while accounting for underlying time trends.
+where the notation $s[c,d]$ refers to the sitting period $s$ to which day $d$ of chamber $c$ belongs.
+This distributional assumption accounts for the fact that on any given day in either chamber, the sum of all proportions in each topic must be one.
+
+The goal of the model is to relate these proportions to the current prime minister $g$ and election period $e$, assuming that an 'election effect' would be at its peak in the days close to the election, then decay over the period.
 The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
+
 $$
-\log \mu_{s,p} = \alpha_{g[s],p} + \cdot\alpha_{e[s],d,p}  + \sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k} + \delta_{s,p}
+\log \mu_{s,p} = \alpha_{g[c,s],p} + \beta_{e[c,s],p} \cdot (N_{s[e]} - s) + \delta_{s[c],p}
 $$
-where: $\alpha_{g[s],p}$ is the mean effect for prime ministers $g$ (which covers sitting period $s$) and topic $p$; $\alpha_{e[s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$) for topic $p$ on day $d$ since the election; $\sum_{k=1}^{K} \beta_{p,k} \cdot x_{s,k}$ is the underlying time trend, modelled using splines: $x_{s,k}$ is the $k$th basis spline in sitting period $s$ and $\beta_{p,k}$ is a coefficient on the $k$th basis spline; and $\delta_{s,p}$ is a structured random, or levels, effect for each sitting period and topic.
-
-The term for the prime minister, $\alpha_{g[s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution.
+where: $\alpha_{g[c,s],p}$ is the mean effect for prime ministers $g$ (which covers sitting period $s$ in chamber $c$) and topic $p$; $\beta_{e[c,s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$, in chamber $c$) for topic $p$; $N_s$ is the total number of sitting periods in election period $e$; and $\delta_{s,p}$ is a random, or levels, effect for each sitting period and topic.
+
+The term for the prime minister, $\alpha_{g[c,s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution.
 We place uninformative priors on each of these parameters:
 $$
-\alpha_{g[s],p} \sim \mbox{Normal}(0, 100).
+\alpha_{g[c,s],p} \sim \mbox{Normal}(0, 100).
 $$
 
-The election term, $\alpha_{e[s],d,p}$, assumes there is an initial effect of an election on the topic distribution, which then decays as a function of days since election, $d$.
-In particular, we model this as an AR(1) in $d$:
-$$
-\alpha_{e[s],d,p} = \rho_{e[s],p} \cdot \alpha_{e[s],d-1,p}.
-$$
+The election term, $\beta_{e[c,s],p}$, assumes there is an initial effect of an election on the topic distribution, which then decays as a function of sitting periods since election, $s$.
+In the model above, $\beta_{e[c,s],p}$ is multiplied by the numbers of sitting periods since the election, $(N_{s[e]} - s)$.
+When the sitting period counter is small, $(N_{s[e]} - s)$ is large, so the election effect is larger.
 
@@
 This allows us to identify differences between prime minister and election effects even when there is a one-term prime minister.
-The value of the initial effect, $\alpha_{e[s],0,p}$, and the AR(1) term, $\rho$, both have non-informative priors:
+The value of the initial effect, $\beta_{e[c,s],p}$, has a non-informative prior:
 $$
-\begin{aligned}
-\alpha_{e[s],0,p} &\sim \mbox{Normal}(0, 100) \mbox{ and} \nonumber \\
-\rho_{e[s],p} &\sim \mbox{Uniform}(0,1). \nonumber
-\end{aligned}
+\beta_{e[c,s],p} \sim \mbox{Normal}(0, 100).
 $$
 
-We model the underlying time trend in topics using splines regression.
+<!-- We model the underlying time trend in topics using splines regression.
 The intuition behind this term is to capture the underlying non-linear trend in topic distributions over time, which is caused by large-scale structural changes to Australian society, culture, and the economy.
@@
 We place knot points every five sitting periods as this is the average length of time for parliament to sit.
-Non-informative priors are placed on the splines coefficients:
-$$
-\beta_{p,k} \sim \mbox{Normal}(0, 100).
-$$
-
-Finally, the sitting-period-specific random effect $\delta_{s,p}$ allows for the topic distributions in some sitting periods to be different than expected based on prime minister and election effects.
+Non-informative priors are placed on the splines coefficients: -->
+<!-- $$ -->
+<!-- \beta_{p,k} \sim \mbox{Normal}(0, 100). -->
+<!-- $$ -->
+
+Finally, the sitting-period-specific random effect $\delta_{s[c],p}$ allows for the topic distributions in some sitting periods to be different than expected based on prime minister and election effects.
 This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-prime-minister and non-election events.
 In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{s,p}$ values are modelled as:
+The $\delta_{s[c],p}$ values are modelled as:
 $$
-\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{e[s],p}^2).
+\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{g[c,s],p}^2).
 $$
 
-The variance parameters $\sigma_{e[s],p}^2$ give an indication of the how the variation in topics is changing over election periods.
-If the estimates of the variance are larger, then there is more variation in the topics discussed within an election period.
+The variance parameters $\sigma_{g[c,s],p}^2$ give an indication of the how the variation in topics is changing over government periods.
+If the estimates of the variance are larger, then there is more variation in the topics discussed within a government period.
 Non-informative priors are placed on the variance parameters:
 $$
-\sigma_{e[s],p} \sim \mbox{Uniform}(0,3).
+\sigma_{g[c,s],p} \sim \mbox{Uniform}(0,3).
 $$

### 2019-01-10 outputs/docs/paper/paper.Rmd
Update paper and slides for Warwick

@@
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, and the UofT Political Behavior Group.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, and the U of T Political Behavior Group.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 We reduce the dimensionality of this dataset by using a correlated topic model, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
-We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1990s."
+We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1980s."
 keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
@@
 Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the prime minister did not change but there was a significant change in topics.
-Finally, economic events, such as financial crises, have less significant effects than other events such as terrorism.
 
@@
 The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)).
-This is evidence to suggest that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time.
-We use Hansard records on a daily basis in this paper.
-We pre-process our text before applying a topic model.
+This suggests that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time.
+We use Hansard records on a daily basis in this paper, and we pre-process our text before applying a topic model.
 The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales.
-We do not stem the words because we found, following @SchofieldMimno2016, that there did not appear to be much appreciable benefit.
 Then the sentences are de-constructed and each word considered individually.
+Not that we do not stem the words because, following @SchofieldMimno2016, we were not able to see much appreciable benefit.
 The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]
 
-[^datasourcefootnote]: We have made our dataset available via the R package \texttt{hansardr}.
-R users can use the devtools package [@Wickham2018] to install it from: https://github.com/RohanAlexander/hansardr.
-Users of other languages can download the daily CSV files from the data-raw folder of that repository.
+[^datasourcefootnote]: Our dataset is available at: https://github.com/RohanAlexander/hansardr.
 While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper.
@@
 Define $\theta_{cdp}$ to be the proportion of topic $p$ on day $d$ in chamber $c$ (where chamber refers to either the House of Representatives or the Senate).
-Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots P = 80$ are equal to the estimated values of $\theta_{cd}$ from the CTM.
+Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots, P = 80$ are equal to the estimated values of $\theta_{cd}$ from the CTM.
 We assume that the majority of variation in topics by day is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
@@
 More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period.
-Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
-
-```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
-
-key_events_results_cols %>%
-  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
-  kable_styling(font_size = 10) %>% 
-  footnote(
-    general = "These days were significantly different to others in their sitting period after taking election and prime minister effects into consideration.", 
-    footnote_as_chunk = T, 
-    threeparttable = TRUE)
-
-```
+
+<!-- Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. -->
+
+<!-- ```{r keyeventsresultstable, echo = FALSE, results = 'asis'} -->
+
+<!-- key_events_results_cols %>% -->
+<!--   kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>% -->
+<!--   kable_styling(font_size = 10) %>%  -->
+<!--   footnote( -->
+<!--     general = "These days were significantly different to others in their sitting period after taking election and prime minister effects into consideration.",  -->
+<!--     footnote_as_chunk = T,  -->
+<!--     threeparttable = TRUE) -->
+
+<!-- ``` -->
 
@@
 
-The other prime ministerial period that we do not consider in this paper is the second Rudd term This is because it only contained a few sitting days.
+The other prime ministerial period that we do not consider in this paper is the second Rudd term.
+This is because it only contained a few sitting days.
 That is, we compare Tony Abbot with Julia Gillard.

### 2019-01-21 outputs/docs/paper/paper.Rmd
Update the fifth parser

@@
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, and the U of T Political Behavior Group.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."

### 2019-01-21 scripts/run_2_parse_pdfs/run_5_combine rows.R

@@ -52,19 +52,19 @@ split_columns <-
   function(name_of_input_csv_file,
            name_of_output_csv_file) {
     # Read in the csv, based on the filename list
-    # name_of_input_csv_file <- "outputs/hansard/run_4_output/hor-1961-10-26.csv" # uncomment for testing
+    # name_of_input_csv_file <- "outputs/hansard/run_4_output/hor-2004-11-29.csv" # uncomment for testing
     
     csv_with_rows_to_combine <-
       read_csv(name_of_input_csv_file,
                trim_ws = FALSE,
-               col_types = "cccd")
+               col_types = cols())
     
     # Remove any extra whitespace i.e. two or more spaces and spaces at either end. Yes, I know that I turned this off in the read_csv, but it's important to be explicit because the whitespcae is useful sometimes.
     csv_with_rows_to_combine$Text <-
       str_squish(csv_with_rows_to_combine$Text)
     
-    csv_with_rows_to_combine$Misc <-
-      str_squish(csv_with_rows_to_combine$Misc)
+    csv_with_rows_to_combine$Title <-
+      str_squish(csv_with_rows_to_combine$Title)
     
     # # Put everything onto one line, which allows us to rejoin words that have been split across two lines e.g. Mon- ica
     csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
@@ -83,9 +83,9 @@ split_columns <-
     # Thanks to Mark Needham for this: https://markhneedham.com/blog/2015/06/27/r-dplyr-squashing-multiple-rows-per-group-into-one/
     csv_with_rows_to_combine <- csv_with_rows_to_combine %>%
       group_by(speakerGroups) %>%
-      mutate(Misc = replace_na(Misc, "ZZZZZ")) %>% 
+      mutate(Title = replace_na(Title, "ZZZZZ")) %>% 
       summarise(Speaker = first(Speaker),
-                Misc = min(Misc),
+                Title = first(Title),
                 text = paste(Text, collapse = " "),
                 pageNumbers = min(pageNumbers)
                 )

### 2019-03-23 outputs/docs/paper/paper.Rmd
Add CAP converted topics

--- 2019-01-10 outputs/docs/paper/paper.Rmd
@@
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, and the U of T Political Behavior Group.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the UofT Political Behavior Group, and the 2019 PSA Political Methodology Conference.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
 author:
+- name: Rohan Alexander
+  affiliation: Australian National University
 - name: Monica Alexander
   affiliation: University of Toronto
-- name: Rohan Alexander
-  affiliation: Australian National University
 abstract: "A large part of politics consists of reacting to events, but not all events provoke a reaction.
@@
 To do this we first create a new dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records.
-We reduce the dimensionality of this dataset by using a correlated topic model, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
+We reduce the dimensionality of this dataset using a correlated topic model, relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
 We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1980s."
-keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model"
+keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
@@
 
+top_words_comp <-
+  read_csv2("../../../outputs/results-topic_models_and_gammas/top_words_80_comparative_agendas.csv", col_types = cols()) %>% 
+  select(-`CAP number`)
+
 top_words <-
@@
 Then the sentences are de-constructed and each word considered individually.
-Not that we do not stem the words because, following @SchofieldMimno2016, we were not able to see much appreciable benefit.
+We do not stem the words because, following @SchofieldMimno2016, we were not able to see much appreciable benefit.
 The resulting dataset used for analysis contains counts of words by day for 14,680 sitting days between 1901 and 2018.[^datasourcefootnote]
@@
 This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
-
-In order to effectively categorise the topics of the entire Hansard, we chose to use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
+@AshMorelliOsnabru2018 combined the best of both in the context of the New Zealand Hansard, using a supervised machine learning approach that would likly be beneficial in the Australian Hansard case as well.
+
+In order to effectively categorise the topics of the entire Hansard, we use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts.
 In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
@@
 An overview, and an example, of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample).
-The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics.
+The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics given documents.
 Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.
@@
 The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
-For example, we may believe a document's author, or the time at which it was written, or, in the case of Hansard, the prime minister or election period, may affect the topics within that document.
+For example, we may believe a document's author, or the time at which it was written, or, in the case of our paper, the prime minister or election period, may affect the topics within that document.
 The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
@@
 ```{r topwords, echo = FALSE, results = 'asis'}
-
-top_words %>% 
+# 
+# top_words %>% 
+#   kable("latex", 
+#         booktabs = T, 
+#         longtable = TRUE, 
+#         caption = "The ten words most strongly associated with each topic"
+#         ) %>%
+#   kable_styling(font_size = 8, 
+#                 latex_options = c("repeat_header")
+#                 )
+```
+
+```{r topwordscomp, echo = FALSE, results = 'asis'}
+
+top_words_comp %>% 
   kable("latex", 
@@
         ) %>%
-  kable_styling(font_size = 8, 
+  kable_styling(font_size = 7, 
                 latex_options = c("repeat_header")
@@
 
+In the final column of Table \@ref(tab:topwords) we summarise the results of our 80-topic model using the categories of the Comparative Agendas Project (CAP), as summarised by @Bevan2017.\footnote{We use Version 1.0 of the Master Codebook, as at 31 July 2014 available at \url{http://sbevan.com/cap-master-codebook.html}.} We do this firstly, to assist other researchers in understanding our results, by trying to relate them to a a more well-known approach.
+We also do this because it allows us to further reduce our 80-topic model to only 21 topics.\footnote{Although the CAP Codebook topic numbering goes to 23, there are only 21 topics because there is no topic 11 or topic 22.
+Our 80 topics did not relate to CAP topics 21 or 23, meaning that we have 19 CAP-based categories.} It is these 19 CAP groupings to which we apply our analysis model.
+
 ## Analysis model
@@
 
-An obvious weakness of topic models is that the number of topics needs to be specified but there is rarely a clear reason to choose some particular number.
+One weakness of topic models is that the number of topics needs to be specified but there is rarely a clear reason to choose some particular number.
 There are also more nuanced weaknesses to be aware of.
@@
 
-[^parliamentarywebsitelink]: As at 5 November, the website was available at: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear.
+[^parliamentarywebsitelink]: As at 5 November 2018, the website was available at: https://www.aph.gov.au/Parliamentary_Business/Statistics/Senate_StatsNet/General/sittingdaysyear.
 
@@
 
-There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely an obvious best choice, especially at a finer level such as choosing between 60 and 65 topics.
+There are a variety of diagnostic measures that can guide the selection of the topics, but there is rarely a clear best choice, especially at a finer level such as choosing between 60 and 65 topics.
 We found it useful to try a few quite different measures before settling on 80 topics.

### 2019-03-23 scripts/convert_topics_to_cap.R

@@ -1,0 +1,30 @@
+#### Preamble ####
+# Purpose: Convert our topics to the CAP
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 23 March 2019
+# Prerequisites:
+# Issues:
+
+
+#### Workspace set-up ####
+library(tidyverse)
+# update.packages()
+
+
+#### Load data  ####  
+the_gammas <- read_csv("outputs/results-topic_models_and_gammas/gammas_model_80.csv")
+the_conversion <- read_csv2("outputs/results-topic_models_and_gammas/top_words_80_comparative_agendas.csv")
+
+the_conversion <- rename(the_conversion, topic = Topic, CAP_number = `CAP number`)
+
+the_conversion <- the_conversion %>% 
+  select(topic, CAP_number)
+
+
+
+the_gammas <- the_gammas %>% 
+  left_join(the_conversion)
+
+
+write_csv(the_gammas, "outputs/results-topic_models_and_gammas/gammas_model_80-with-cap.csv")

### 2019-03-23 scripts/count words.R

@@ -1,0 +1,56 @@
+library(quanteda)
+library(tidyverse)
+
+
+function()
+
+
+
+ntoken(hansard$text, remove_punct = TRUE) %>% class()
+
+
+
+
+#### Create the function that will be applied to the files ####
+count_tokens <-
+  function(name_of_input_csv_file) {
+    # Read in the csv, based on the filename list
+    # name_of_input_csv_file <- "outputs/hansard/run_7_output/hor-1901-07-19.csv" # uncomment for testing
+    
+           hansard <-
+             read_csv(name_of_input_csv_file,
+                      col_types = cols())
+           
+           numbers <- tibble(number = ntoken(hansard$text, remove_punct = TRUE))
+
+    # Save file
+    return(numbers)
+    
+    print(paste0("Done with ", name_of_input_csv_file, " at ", Sys.time()))
+  }
+
+
+files <- c("outputs/hansard/run_7_output/hor-1901-07-19.csv"), "outputs/hansard/run_7_output/hor-1903-06-25.csv")
+
+use_this_path_to_get_csvs  <- "/Volumes/Hansard/parsed/federal/for_zoe/run_7_output"
+# use_this_path_to_get_csvs <- "/Volumes/Hansard/parsed/federal/hor"
+
+# Get list of Hansard csvs that have been parsed from PDFs and had front matter removed
+file_names <-
+  list.files(
+    path = use_this_path_to_get_csvs,
+    pattern = "*.csv",
+    recursive = FALSE,
+    full.names = TRUE
+  )
+
+
+test <- map_dfr(files, count_tokens)
+
+sum(test$number)
+
+8 times wiht both
+
+2 times with just the first
+
+6 times wiht just the second

### 2019-03-31 outputs/docs/paper/paper.Rmd
model updates in paper

@@
 The topic proportions on day $d$ in chamber $c$ are modelled in reference to their membership of a particular sitting period $s$.
-Firstly, we assume that each distribution of topics, $\theta_{c,d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{s[c,d],1:P}$:
+Firstly, we assume that each distribution of topics, $\theta_{c,d,1:P}$ for each day is a draw from a Dirichlet distribution with mean parameter $\mu_{c,s[d],1:P}$:
 $$
-\theta_{c,d,1:P} \sim \mbox{Dirichlet}(\mu_{s[c,d],1:P})
+\theta_{c,d,1:P} \sim \mbox{Dirichlet}(\mu_{c,s[d],1:P})
 $$
-where the notation $s[c,d]$ refers to the sitting period $s$ to which day $d$ of chamber $c$ belongs.
+where the notation $s[d]$ refers to the sitting period $s$ to which day $d$ of chamber $c$ belongs.
 This distributional assumption accounts for the fact that on any given day in either chamber, the sum of all proportions in each topic must be one.
@@
 The goal of the model is to relate these proportions to the current prime minister $g$ and election period $e$, assuming that an 'election effect' would be at its peak in the days close to the election, then decay over the period.
-The mean parameters $\mu_{s,p}$ are modelled on the log scale as:
+The mean parameters $\mu_{c,s,p}$ are modelled on the log scale as:
 
 $$
-\log \mu_{s,p} = \alpha_{g[c,s],p} + \beta_{e[c,s],p} \cdot (N_{s[e]} - s) + \delta_{s[c],p}
+\log \mu_{c,s,p} = \alpha_{g[c,s],p} + \beta_{e[c,s],p} \cdot (N_{s[e]} - s) + \delta_{c,s,p}
 $$
-where: $\alpha_{g[c,s],p}$ is the mean effect for prime ministers $g$ (which covers sitting period $s$ in chamber $c$) and topic $p$; $\beta_{e[c,s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$, in chamber $c$) for topic $p$; $N_s$ is the total number of sitting periods in election period $e$; and $\delta_{s,p}$ is a random, or levels, effect for each sitting period and topic.
-
-The term for the prime minister, $\alpha_{g[c,s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution.
+where: $\alpha_{g[c,s],p}$ is the mean effect for prime ministers $g$ (which covers sitting period $s$ in chamber $c$) and topic $p$; $\beta_{e[c,s],d,p}$ is the effect of election $e$ (which occurs in sitting period $s$, in chamber $c$) for topic $p$; $N_s$ is the total number of sitting periods in election period $e$; and $\delta_{c,s,p}$ is a random, or levels, effect for each chamber, sitting period and topic.
+
+The term for the prime minister, $\alpha_{g[c,s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution that is common across chambers.
 We place uninformative priors on each of these parameters:
@@
 
-Finally, the sitting-period-specific random effect $\delta_{s[c],p}$ allows for the topic distributions in some sitting periods to be different than expected based on prime minister and election effects.
-This allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-prime-minister and non-election events.
+Finally, the sitting-period-specific random effect $\delta_{c,s,p}$ allows for chamber- and sitting-period specific deviations in the topic distributions.
+This allows us to identify periods where there may be differences in the topics discussed across the two chambers.
+It also allows us to identify large deviations away from the expected distribution, thus helping to identify the effect of other, non-prime-minister and non-election events.
 In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{s[c],p}$ values are modelled as:
+The $\delta_{c,s,p}$ values are modelled as:
 $$
-\delta_{s,p} \sim \mbox{Normal}(0, \sigma_{g[c,s],p}^2).
+\delta_{c,s,p} \sim \mbox{Normal}(0, \sigma_{g[c,s],p}^2).
 $$

### 2019-04-01 outputs/docs/paper/paper.Rmd
Update paper

@@
     template: svm-latex-ms.tex
-title: "The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)"
+title: "The Increased Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament between 1901 and 2018"
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the UofT Political Behavior Group, and the 2019 PSA Political Methodology Conference.
+We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference.
+The code and data for this paper is available at: https://github.com/RohanAlexander/hansard.
 Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
@@
 
-names(key_events_results_cols) <- c("Dates", "", "", "", "", "", "", "")
+names(key_events_results_cols) <- c("Dates", "", "", "", "", "")
 
@@
 We systematically analyse the text in two stages, each of which takes advantage of a different statistical technique.
-First, to reduce the dimensionality of our dataset we use a topic model that allows correlation between topics.
+First, to reduce the dimensionality of our dataset we use a topic model that allows correlation between topics, and then further reduce those topics to match the Comparative Agendas Project.
 Second, we analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
 We explicitly consider two types of events: changes in prime minister and elections.
-After taking these effects into consideration, we then explore other significant events.
 
 We find that: firstly, changes in prime minister tend be associated with topic changes even when the party in power does not change.
-For instance, the change from Hughes to Bruce in 1922, Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
-Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Whitlam in 1972, Fraser in 1975, Hawke in 1983, Howard in 1996, Rudd in 2007, and Abbott in 2013 are associated with topic changes, but the 1974 Whitlam, 1980 Fraser, and the 1998 and 2004 Howard re-elections, stand out as elections where the prime minister did not change but there was a significant change in topics.
+For instance, the change from Hughes to Bruce in 1923, Forde to Chifley in 1945; Menzies to Holt in 1966; Hawke to Keating in 1991; and Rudd to Gillard in 2010 are all associated with significant changes in topics despite no change in the party in power.
+Secondly, as expected, elections where the party in power also changes, such as Fisher in 1910 and 1914, Menzies in 1949, Hawke in 1983, and Howard in 1996 are associated with topic changes, but the 1974 Whitlam, and 1984 Hawke re-elections stand out as elections where the prime minister did not change but there was a significant change in topics.
 
@@
 The records can also be downloaded from the Australian Hansard website or the website can be scraped.
-We do not use the XML records or scrape the website because those records are known to be incomplete but the extent of how incomplete they are is unknown.
+We do not use the XML records or scrape the website for this paper because those records are known to be incomplete but the extent of how incomplete they are is unknown.
 The trade-off for a more-complete record is the errors introduced by having to parse the PDFs.
@@
 An example of the latter issue is that 'the' is often parsed as 'thc'.
-These errors are corrected when they can be identified.
-
-[^scriptsfootnote]: The exact scripts that we use are available on request or via the GitHub repository for this paper.
+These errors are corrected when they can be identified, but as there are almost a billion words in the dataset, we are restricted to changes that can be made at scale.
+
+[^scriptsfootnote]: Our code and data are available on request or via the GitHub repository for this paper: https://github.com/RohanAlexander/hansard.
 The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018.
@@
 
-[^datasourcefootnote]: Our dataset is available at: https://github.com/RohanAlexander/hansardr.
+[^datasourcefootnote]: Our dataset is available at: https://github.com/RohanAlexander/hansard.
 While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper.
@@
 
-We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time.
+We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time, and then further group these topics to match those of the Comparative Agendas Project.
 We consider these topic distributions as inputs that can be analysed by another model.
@@
 This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited.
-@AshMorelliOsnabru2018 combined the best of both in the context of the New Zealand Hansard, using a supervised machine learning approach that would likly be beneficial in the Australian Hansard case as well.
+@AshMorelliOsnabru2018 combined the best of both in the context of the New Zealand Hansard, using a supervised machine learning approach that would likely be beneficial in the Australian Hansard case as well.
 
@@
 One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time.
-A multinomial approach would not have this property.
+A multinomial approach would not necessarily have this property.
 
@@
 More detail about the CTM is in Appendix \@ref(correlatedtopicmodelsection).
+There are various methods to help determine the appropriate number of topics to specify, and we further discuss the implications given our setting later in the paper.
+However the main implication is that the optimal number of topics was too large to be tractable by our analysis model, and too large to be easily visualised or examined.
+For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project.
+It is these proportions that we use as an input to our analysis model.
 
@@
 
-The CTM output of interest is the proportion of each topic appearing in each document.
-The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
+The output of interest from the topic modelling stage, is the proportion of each topic appearing in each document.
+The aim of the analysis stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
 But with many topics for each of the roughly 14,680 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
@@
 Define $\theta_{cdp}$ to be the proportion of topic $p$ on day $d$ in chamber $c$ (where chamber refers to either the House of Representatives or the Senate).
-Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots, P = 80$ are equal to the estimated values of $\theta_{cd}$ from the CTM.
+Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots, P = 19$ are equal to the estimated values of $\theta_{cd}$ from the CTM after we group them into the Comparative Agendas Project topics.
 We assume that the majority of variation in topics by day is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
@@
 The mean parameters $\mu_{c,s,p}$ are modelled on the log scale as:
-
 $$
@@
 
-Firstly, we describe the results of the CTM approach, which defined 80 topics over the period 1901 to 2018.
+Firstly, we describe the results of the CTM approach, which defined 80 topics over the period 1901 to 2018, and which we then further reduced to match the Comparative Agendas Project.
 We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.
@@
 LDA output defines a topic as a distribution of probabilities over words.
-In Table \@ref(tab:topwords) we display the ten words with the highest association for each of the 80 topics, but the topics are defined by probability distributions over all words.
+In Table \@ref(tab:topwordscomp) we display the ten words with the highest association for each of the 80 topics, but the topics are defined by probability distributions over all words.
 LDA does not apply labels to each topic, or collection of words, instead this has to be done by inspection.
@@
 
-In the final column of Table \@ref(tab:topwords) we summarise the results of our 80-topic model using the categories of the Comparative Agendas Project (CAP), as summarised by @Bevan2017.\footnote{We use Version 1.0 of the Master Codebook, as at 31 July 2014 available at \url{http://sbevan.com/cap-master-codebook.html}.} We do this firstly, to assist other researchers in understanding our results, by trying to relate them to a a more well-known approach.
+In the final column of Table \@ref(tab:topwordscomp) we summarise the results of our 80-topic model using the categories of the Comparative Agendas Project (CAP), as summarised by @Bevan2017.\footnote{We use Version 1.0 of the Master Codebook, as at 31 July 2014 available at \url{http://sbevan.com/cap-master-codebook.html}.} We do this firstly, to assist other researchers in understanding our results, by trying to relate them to a more well-known approach.
 We also do this because it allows us to further reduce our 80-topic model to only 21 topics.\footnote{Although the CAP Codebook topic numbering goes to 23, there are only 21 topics because there is no topic 11 or topic 22.
@@
 We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussed in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated by the CTM, and examines the association between these topic distributions and outside events.
-That is, the topic model outputs are inputs for our analysis model.
+As discussed in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated by the CTM and reduced to the Comparative Agendas Project, and examines the association between these topic distributions and outside events.
+That is, the topic groupings are inputs for our analysis model.
 
@@
 This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by prime ministers or elections tend not to provide enough variability.
-For instance, examining Topics 4, 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).
+For instance, examining topics that have to do with war and conflict illustrates discussions of Australia's military involvement (Figure \@ref(fig:wartopicsgraph)).
 
 ```{r wartopicsgraph, cache = TRUE, echo = FALSE, fig.cap = "Model estimates of topic prevalance by sitting period for those related to war and conflict", out.width = '100%'}
-knitr::include_graphics("../../figures/war_stack.pdf")
+knitr::include_graphics("../../results-analysis_model/two_house_results/defense_topic_fitted_data.pdf")
 ```
@@
 
-```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Level effects for prime ministers by selected topics.", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_gov.pdf")
-```
-
-```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Level effects for election periods by selected topics", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election.pdf")
+```{r mugov, cache = TRUE, echo = FALSE, fig.cap = "Level effects for prime ministers by selected topics.", out.width = '90%'}
+knitr::include_graphics("../../results-analysis_model/two_house_results/mu_gov_big_topics")
+```
+
+```{r muelection, cache = TRUE, echo = FALSE, fig.cap = "Level effects for election periods by selected topics", out.width = '90%'}
+knitr::include_graphics("../../results-analysis_model/two_house_results/mu_election_big_topics.pdf")
 ```
@@
 
-<!-- Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. -->
-
-<!-- ```{r keyeventsresultstable, echo = FALSE, results = 'asis'} -->
-
-<!-- key_events_results_cols %>% -->
-<!--   kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>% -->
-<!--   kable_styling(font_size = 10) %>%  -->
-<!--   footnote( -->
-<!--     general = "These days were significantly different to others in their sitting period after taking election and prime minister effects into consideration.",  -->
-<!--     footnote_as_chunk = T,  -->
-<!--     threeparttable = TRUE) -->
-
-<!-- ``` -->
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
+
+```{r keyeventsresultstable, echo = FALSE, results = 'asis'}
+
+key_events_results_cols %>%
+  kable(booktabs = T, caption = "Days that were significantly different to other days in their sitting period") %>%
+  kable_styling(font_size = 10) %>%
+  footnote(
+    general = "These days were significantly different to others in their sitting period after taking election and prime minister effects into consideration.",
+    footnote_as_chunk = T,
+    threeparttable = TRUE)
+
+```
 
@@
 
-Of the 36 prime ministers over this period, we find that 20 of them are significantly different to the prime minister that preceded them.
-However, four of these results -- the significance of the Page term, the first Menzies term, the Chifley term and the Abbott term -- are likely due to the short length of either the prime minister or the predecessor and should be ignored, leaving only 16.
-The earliest of these are the first Fisher term, the Cook term and the third Fisher term, which were different to the second Deakin term, the second Fisher term, and the Cook term, respectively.
-To a certain extent this is likely due to changes due to World War I.
+Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceded them, after we account for and remove some that had especially short terms.
+The three earliest of them occur in the first decade after Federation, and to a certain extent this may be due to the variety of the issues that had to be addressed in those initial years.
+Joseph Cook's time as prime minister is found to be significantly different to that of his predecessor, Andrew Fisher, although it may be that this is due to World War I.
 
@@
 We find that Holt is different to Menzies.
-In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt.
-
-```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
-knitr::include_graphics("../../figures/mu_election-differences.pdf")
-```
+
+<!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->
+
+<!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} -->
+<!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") -->
+<!-- ``` -->
 
@@
 The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement.
-For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively.
+For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001.
 But there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising.
-When we examine this we find that some of them, such as 4 February 2009, are associated with significant legislation.
-However the over-weighting of dates in the first half of our sample in Table \@ref(tab:keyeventsresultstable) highlights further work is needed to improve this approach.
-For instance, our approach may not be appropriately considering step-changes or it may be that our identification of sitting periods is not appropriate for the entire period.
+When we examine this we find that some of them are associated with significant legislation.
+Although our results are not overly over-weighted in the first half of our sample, there is a substantial gap between 1965 and 1991.
+Table \@ref(tab:keyeventsresultstable) highlights further work is needed to improve this approach.
+For instance, it may be that our approach is not appropriately considering step-changes or it may be that our identification of sitting periods is not appropriate for the entire period, given the changed sitting pattern that we identify.
 

### 2019-10-30 outputs/docs/paper/paper_MA_structure_edit.Rmd
intro edits

--- 2019-04-01 outputs/docs/paper/paper.Rmd
@@
     template: svm-latex-ms.tex
-title: "The Increased Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament between 1901 and 2018"
+title: "The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018"
 thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
@@
   affiliation: University of Toronto
-abstract: "A large part of politics consists of reacting to events, but not all events provoke a reaction.
-As such, understanding political behaviour requires examining the reaction to events and how this changes over time.
-We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of events: elections and changed prime ministers.
-To do this we first create a new dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on available public records.
-We reduce the dimensionality of this dataset using a correlated topic model, relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model that has several advantages over existing models.
-We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and elections that do not result in a change in prime minister are rarely associated with topic changes in the first half of our sample, but have been increasingly significant since the 1980s."
+abstract: "Politics and discussion in parliament is likely to be influenced by the party in power and associated election cycles.
+However, little is known about the extent to which these events affect discussion and how this has changed over time.
+We systematically analyse how discussion in the Australian Federal Parliament changes in response to two types of political events: elections and changed prime ministers.
+We use a newly constructed dataset of what was said in the Australian Federal Parliament from 1901 through to 2018 based on extracting and cleaning available public records.
+We reduce the dimensionality of discussion in this dataset by using a correlated topic model to obtain a set of comparable topics over time.
+We then relate those topics to the Comparative Agendas Project, and then analyse the effect of these two types of events using a Bayesian hierarchical Dirichlet model.
+We find that: changes in prime minister tend to be associated with topic changes even when the party in power does not change; and the effect of elections has been increasing since the 1980s, regardless of whether the election results in a change of prime minister."
 keywords: "text-as-data, Australian politics, unsupervised machine learning, Bayesian hierarchical Dirichlet model, Comparative Agendas Project"
@@
 
-Events are a well-known cause of political behaviour.
-But their effect is varied, and changes over time.
-Here we focus on just two types of events: elections, and changes in prime minister.
-We examine the effect of these types of events on the topics that are discussed in the Australian Federal Parliament.
-
-The main data source for our paper is the text record, known as 'Hansard', of what was said in the Australian Federal Parliament.
-From this we create a dataset based on the sitting days from 1901 through to 2018.
-We have records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).
-In contrast to the US, but similar to Canada and the UK, in Australia the executive is drawn from the legislature, and the prime minister typically sits in the lower house.
-Unlike Canada or the UK, both houses are elected, although each has different mechanisms and constituencies.
-Our dataset consists of counts of every word that occurs at least thrice, after we convert all words to lower-case; remove names, numbers, and punctuation; join commonly co-located words; and remove stop words.
-
-We systematically analyse the text in two stages, each of which takes advantage of a different statistical technique.
-First, to reduce the dimensionality of our dataset we use a topic model that allows correlation between topics, and then further reduce those topics to match the Comparative Agendas Project.
-Second, we analyse those topics using a Bayesian hierarchical Dirichlet model to examine changes at various types of events.
-We explicitly consider two types of events: changes in prime minister and elections.
+What is discussed in parliament is a key indicator of a government's priorities and likely policy outcomes.
+While in an ideal world, we may hope that topics of discussion represent the most important social, economic and environmental issues for the country at that particular time, in reality, discussion is heavily influenced by party politics, the priorities of the head of government at the time, and where they are in the current election cycle.
+
+For example, XX NEED A BIT OF A LITERATURE REVIEW HERE on papers that look at discussion and political changes?? XX
+
+While there is evidence to suggest a relationship between parliamentary discussion and political events, little research exists that systematically analyses the sensitivity of topics discussed in parliament to political changes in a statistical way.
+This is mostly likely because historical data are difficult to obtain, and parliamentary discourse and events are inherently complex and multi-dimensional, and difficult to operationalise into an analysable form.
+However, the increased accessibility of optical character recognition to parse historical documents, and recent developement in statistical text analysis, allow for a more broad analysis of parliamentary events and discussion over time.
+
+In this paper, we exame the effect of elections and changes in prime ministers on the topics that are discussed in the Australian Federal Parliament.
+We construct a new dataset from the text record, known as 'Hansard', of what was said in the Australian Federal Parliament since its inception in 1908, to 2018.
+The dataset covers records for 7,934 days in the House of Representatives (lower house) and 6,746 days in the Senate (upper house).
+
+We then systematically analyse the text contained in the Hansard dataset in two stages, each of which takes advantage of a different statistical technique.
+First, we used a correlated topic model to obtain a set of comparable topics discussed in parliament over time, and then further reduce those topics to match the Comparative Agendas Project.
+Second, we introduce a new modeling approach to examine the association between changes in topics discussed changes in prime minister and elections.
+The second modeling approach centers on a Bayesian hierarchical Dirichlet model, which allows for the effect of these two event types to be modeled concurrently, while taking time since election into account.
+The model also allows for information about event effects to be pooled across documents.
 
@@
 From a data perspective we bring to bear an essentially-complete record of what was said in the Australian Federal Parliament on a daily basis, and our dataset is available to other researchers.
-From a methods perspective, our analysis model has several advantages over existing methods.
-These include: allowing the events to have more-complicated auto-correlated functional forms; implementing pooling across groups of similar documents; and identifying outlying topic distributions without the need to pre-specify the event of interest.
+From a methods perspective, we present a modeling framework that can be generalizable to other problems looking at the association between text data and events.
+The model allows for time since event to be taken into account; implements pooling across groups of similar documents; and additionally identifies potential outlying topic distributions without the need to pre-specify the event of interest.
 There are many avenues for closely related future work such as: investigating the effect of other types of events; including a richer set of covariates to disentangle the reason for different effects; and reversing the causality to examine the effect of what is said in parliament on various outcomes.
+
+The remainder of the paper is structured as follows XX
 

### 2019-10-30 outputs/docs/paper/paper_MA_structure_edit.Rmd
edits to data section

@@
 
-The remainder of the paper is structured as follows XX
+The remainder of the paper is structured as follows XX.
 
@@
 
-Following the example of the UK a daily text record called Hansard of what was said in the Australian Federal Parliament has been made available since Federation in 1901.[^Verbatimfootnote] Analysing Hansard records and their equivalents is increasingly viable as new methods and reduced computational costs make it easier.
-
-[^Verbatimfootnote]: While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
+The first step is to construct a dataset drived from the Australian Hansard, which contains the text of what was said throughout history in the Australian Federal Parliament.
+This section gives on the availability and characteristics of such data and outlines the method and steps undertaken to create a ready-to-analyse dataset.
+
+## Background
+
+The term 'Hansard' refers to a daily text record of what was said in parliament.
+The UK, Australia and Canada all have a Hansard, which span historical periods right up to present day.
+Following the example of other countries, the Hansard for the Australian Federal Parliament has been made available since Federation in 1901.
+Analysing Hansard records and their equivalents is increasingly viable as new methods and reduced computational costs make it easier.
+While Hansard is not necessarily verbatim, it is considered close enough for text-as-data purposes.
 For instance, @Mollin2008 found that in the case of the UK Hansard the differences would only affect specialised linguistic analysis.
@@
 
-The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed increased analysis of Canadian parliament text records.
+The recent digitisation of Hansard records has allowed increased analysis of parliament text records.
 For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada using word embeddings.
-A digitised version of the UK Hansard has been available for some time.
-For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation.
+In the UK, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians, and @PetersonSpirling2018 examined polarisation.
 One exciting aspect of research using the UK Hansard has been linking text records with other datasets.
 For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties.
-Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England.
+As digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England.
 In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950.
@@
 The closest research to ours that we have found is @Boulous2013 who examined parliamentary debate in Australia between 1946 and 2012.
-
-The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.
-Although we do not use them here, XML records are also available in most cases.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs and further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
-Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
-
-[^XMLfootnote]: Tim Sherratt makes Commonwealth XML records for 1901 to 1980 available as a single download at: http://historichansard.net/.
+To our knowledge, this is the first paper that analyses the complete Hansard record since 1901.
+
+## Creation of Hansard dataset
+
+The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
+There are XX PDF files that cover the Hansard over the entire period 1901-2018.
+Our goal is to take these PDFs and convert them into a digitized dataset of text that is able to be analysed.
+
+[^XMLfootnote]: Although we do not use them here, XML records are also available in most cases.
+Tim Sherratt makes Commonwealth XML records for 1901 to 1980 available as a single download at: http://historichansard.net/.
 Commonwealth XML records from 1998 to 2014 are available from Andrew Turpin’s website, and from 2006 through to today from Open Australia’s website.
@@
 
-We use the official PDF release and the formatting of the Hansard records changes over time.
-We use scripts written in R [@R2018] to convert the PDFs into daily text records.[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records.
+The creation of the Hansard dataset involves the following steps.
+Firstly, optical character recognition (OCR) is used to convert static PDFs into digitised text.
+This creates a text file for each PDF with a single character string.
+Secondly, as many of the original PDFs contained two columns per page, the text file is reshuffled to ensure the text is in the right order.
+Thirdly, the text is split out such that it is separated by speaker.
+This involves XX.
+Lastly, the dataset is created in tidy format (XX REF here), such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker.
+XX could add more detail to this paragraph XX
+
+These steps were performed using R [@R2018].[^scriptsfootnote] Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate, especially for older records.
 An example of the latter issue is that 'the' is often parsed as 'thc'.
@@
 
+There are 14,680 days of publicly available Hansard records across the two chambers of the Australian Federal Parliament for which we have PDFs.
+Further summary statistics for this are provided in Appendix \@ref(hansardsummarystatistics).
+In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset.
+XX MAYBE pull out a few more summary stats here XX
+
+Our data cleaning process indicates concerns with a small number of PDFs and these are detailed in Appendix \@ref(knownhansardissues).
 The percentage of stop-words each day is reasonably consistent over time (see Appendix \@ref(stopwordsgraph)).
 This suggests that the data are fit-for-purpose, although manual inspection does suggest there is some improvement in quality over time.
-We use Hansard records on a daily basis in this paper, and we pre-process our text before applying a topic model.
+
+## Creation of analysis dataset
+
+Using the Hansard dataset, we pre-process the text to create an analysis dataset to model topics and to subsequently investigate the relationship between topics and events.
 The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multi-word names titles and phrases, such as new south wales to new_south_wales.
@@
 While we are making our data public in an attempt to help other researchers, we cleaned the dataset toward the requirements of this paper.
-If you have different requirements or have suggestions for how we can improve the dataset for other uses please contact us.
 

### 2019-10-31 outputs/docs/paper/paper_MA_structure_edit.Rmd
topics model

@@
 Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time.
-Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in prime minister, elections, and other external events.
-The output of the first stage is the input to the second stage.
-
-We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time, and then further group these topics to match those of the Comparative Agendas Project.
+Secondly, we want to relate the resulting topic distributions to elections and changing prime ministers over time, accounting for temporal trends.
+
+We first use a Correlated Topic Model [@BleiLafferty2007] to obtain estimated topic distributions over time, and then further group these topics to match those of the Comparative Agendas Project.
 We consider these topic distributions as inputs that can be analysed by another model.
@@
 
-## Overview of topic modelling
+## Overview of topic modelling and topic selection
 Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics.
@@
 In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.
-One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time.
+
+<!-- One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time.
 A multinomial approach would not necessarily have this property.
+-->
 
@@
 The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics given documents.
-Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.
 
@@
 For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.
-
 As such, we use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain topic distributions.
@@
 More detail about the CTM is in Appendix \@ref(correlatedtopicmodelsection).
-There are various methods to help determine the appropriate number of topics to specify, and we further discuss the implications given our setting later in the paper.
-However the main implication is that the optimal number of topics was too large to be tractable by our analysis model, and too large to be easily visualised or examined.
-For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project.
-It is these proportions that we use as an input to our analysis model.
+
+### Categorisation of topics using the Comparative Agendas Project
+
+There are various methods to help determine the appropriate number of topics to specify.
+Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen based on the output of the CTM.
+However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised or examined.
+In addition, many of the topics in the optimal set referred to similar themes, such as budgeting or administrative topics.
+
+For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. XX NEED TO EXPLAIN WHAT THIS IS - I HAVE NO IDEA XX
 

### 2019-10-31 outputs/docs/paper/paper_MA_structure_edit.Rmd
rest of methods

@@
 In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset.
-XX MAYBE pull out a few more summary stats here XX
+XX MAYBE PULL OUT MORE SUMMARY STATS IN PARTICULAR HIGHLIGHT THE TWO CHAMBERS XX
 
@@
 
-The output of interest from the topic modelling stage, is the proportion of each topic appearing in each document.
+The output of interest from the topic modelling stage is the proportion of each topic appearing in each document.
 The aim of the analysis stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events.
-But with many topics for each of the roughly 14,680 chamber-sitting-days the data are still too noisy to easily visualise changes around events.
+But with many topics for each of the roughly 14,680 chamber-sitting-days spanning 118 years, the data are still too noisy to easily visualise changes around events.
 
@@
 The distinguishing aspect of the STM is that it considers more than just a document's content when constructing topics.
-For example, we may believe a document's author, or the time at which it was written, or, in the case of our paper, the prime minister or election period, may affect the topics within that document.
+For example, we may believe a document's author, or, in the case of our paper, the prime minister or election period, may affect the topics within that document.
 The STM allows this additional information, or metadata, to affect the construction of topics, though influencing either topical prevalence or topical content.
@@
 To overcome these challenges, we formalise a statistical framework that allows us to systematically identify significant changes in topic distributions over time.
-Specifically, we use the estimated topic distributions from the CTM described in the previous section as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in prime minister and elections.
-This set-up also allows us to identify 'outlying' topic distributions and relate these to other events.
-
-Define $\theta_{cdp}$ to be the proportion of topic $p$ on day $d$ in chamber $c$ (where chamber refers to either the House of Representatives or the Senate).
+Specifically, we use the estimated topic distributions from the previous step as an input into a Bayesian hierarchical Dirichlet regression framework, which relates the proportions of each topic to underlying time trends, changes in prime minister and elections.
+
+### Model set-up
+
+Define $\theta_{c,d,p}$ to be the proportion of speech that refers to topic $p$ on day $d$ in chamber $c$ (where chamber refers to either the House of Representatives or the Senate).
 Note that the $\theta_{c,d,1:P}$ for $p = 1,2,\dots, P = 19$ are equal to the estimated values of $\theta_{cd}$ from the CTM after we group them into the Comparative Agendas Project topics.
-We assume that the majority of variation in topics by day is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
+We assume that the majority of variation in topics by day $d$ is across sitting periods, $s$, where a sitting period is defined as any group of days that are less than one week apart.
 Using this definition, there are 822 sitting periods over the period 1901 to 2018 inclusive.
@@
 The mean parameters $\mu_{c,s,p}$ are modelled on the log scale as:
+
 $$
@@
 The term for the prime minister, $\alpha_{g[c,s],p}$, assumes there is some underlying mean effect of each prime minister on the topic distribution that is common across chambers.
-We place uninformative priors on each of these parameters:
+Non-informative priors are placed on $\alpha_{g[c,s],p}$:
+
 $$
@@
 In addition, this set up also partially pools effects across sitting periods.
-The $\delta_{c,s,p}$ values are modelled as:
+The $\delta_{c,s,p}$ values are modelled heirarchically as:
+
 $$
-\delta_{c,s,p} \sim \mbox{Normal}(0, \sigma_{g[c,s],p}^2).
+\delta_{c,s,p} \sim \mbox{Normal}(\mu_{c,p}, \sigma_{g[c,s],p}^2).
 $$
+This structure assumes that the sitting period effect is a draw from a distribution with a mean that is common to that particular chamber and topic, with some associated variance.
+This allows for the sitting-period-specific random effect $\delta_{c,s,p}$ to be partially informed by other sitting periods for that chamber and topic combination.
 
@@
 Non-informative priors are placed on the variance parameters:
+
 $$

### 2019-11-01 outputs/docs/paper/paper_MA_structure_edit.Rmd
topic results

@@
 
-Firstly, we describe the results of the CTM approach, which defined 80 topics over the period 1901 to 2018, and which we then further reduced to match the Comparative Agendas Project.
+Firstly, we describe the results of the topic modeling and aggregation using the CTM approach, which defined 80 topics over the period 1901 to 2018,which we then further reduced to match the Comparative Agendas Project.
 We then describe the results of the Bayesian analysis model, which identified prime ministers, elections and other events that were associated with a change in the topics discussed.
@@
 ## Topic modelling
-We applied the CTM approach discussed in Appendix \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata).
+We applied the CTM approach on the processed Hansard text database outlined in Section \@ref(hansarddata).
 The main output of interest are the types of topics identified by the model, and the prevalence of each topic for each day of parliamentary discussion.
@@
 As expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.
+
+In the final column of Table \@ref(tab:topwordscomp) we summarise the results of our 80-topic model using the categories of the Comparative Agendas Project (CAP), as summarised by @Bevan2017.\footnote{We use Version 1.0 of the Master Codebook, as at 31 July 2014 available at \url{http://sbevan.com/cap-master-codebook.html}.} We do this firstly, to assist other researchers in understanding our results, by trying to relate them to a more well-known approach.
+We also do this because it allows us to further reduce our 80-topic model to only 21 topics.\footnote{Although the CAP Codebook topic numbering goes to 23, there are only 21 topics because there is no topic 11 or topic 22.
+Our 80 topics did not relate to CAP topics 21 or 23, meaning that we have 19 CAP-based categories.} It is these 19 CAP groupings to which we apply our analysis model.
 
@@
 Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Hansard.
-It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time.
-The highlighted topics are those related to war and conflict.
-The two chambers of the Australian Federal Parliament appear to be similar at a broad scale.
+The two panels refer to the two different chambers of the Australian Federal Parliament.
+The highlighted topics are categorised as 'Defense' in CAP terms, i.e.
+those related to war and conflict.
+The figure shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time; for example, the highlighted defense topics have notable peaks around the two World Wars, and post-9/11 attacks.
+The two chambers appear to be similar at a broad scale in terms of the increases and decreases in the different topics.
+Appendix \@ref(topicmodeleconresultsdiscussion) provides another example from the topic model results in the context of economic events.
 
@@
 Figure \@ref(fig:threeexamples) shows the topic model output in the context of three notable periods of Australian political history. 
-
-```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
-knitr::include_graphics("../../figures/topics_examples_three.png", auto_pdf = FALSE)
-```
-
 The first panel of Figure \@ref(fig:threeexamples) is the second Menzies term.
@@
 The analysis model needs to be able to deal with this situation.
-
-Appendix \@ref(topicmodeleconresultsdiscussion) provides another example from the topic model results in the context of economic events.
-
-In the final column of Table \@ref(tab:topwordscomp) we summarise the results of our 80-topic model using the categories of the Comparative Agendas Project (CAP), as summarised by @Bevan2017.\footnote{We use Version 1.0 of the Master Codebook, as at 31 July 2014 available at \url{http://sbevan.com/cap-master-codebook.html}.} We do this firstly, to assist other researchers in understanding our results, by trying to relate them to a more well-known approach.
-We also do this because it allows us to further reduce our 80-topic model to only 21 topics.\footnote{Although the CAP Codebook topic numbering goes to 23, there are only 21 topics because there is no topic 11 or topic 22.
-Our 80 topics did not relate to CAP topics 21 or 23, meaning that we have 19 CAP-based categories.} It is these 19 CAP groupings to which we apply our analysis model.
+XX I FIND THESE FIGURES HARD TO READ...
+CONSIDER REDOING OR REMOVING XX
+
+```{r threeexamples, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, for three periods", out.width = '100%'}
+knitr::include_graphics("../../figures/topics_examples_three.png", auto_pdf = FALSE)
+```
 

### 2019-11-01 outputs/docs/paper/paper_MA_structure_edit.Rmd
rest of results

@@
 
-## Analysis model
-
-### Main results
-
-We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament.
-As discussed in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated by the CTM and reduced to the Comparative Agendas Project, and examines the association between these topic distributions and outside events.
-That is, the topic groupings are inputs for our analysis model.
+## Results from analysis model
+
+As discussed in Section \@ref(analysismodelexplanation), the modelling process takes the topic proportions estimated by the CTM and reduced to the Comparative Agendas Project, and examines the association between these topic distributions and events.
 
@@
 For example, the model provides estimates of topic prevalence by each sitting period.
-This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by prime ministers or elections tend not to provide enough variability.
-For instance, examining topics that have to do with war and conflict illustrates discussions of Australia's military involvement (Figure \@ref(fig:wartopicsgraph)).
+Figure \@ref(fig:wartopicsgraph) illustrates the estimated topic prevlance by sitting period for topic XX, one of the defense-related topics, overlayed with the daily topic prevalnce (as also illustrated in Figure XX above).
+This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable.
 
@@
 One of the main goals of the analysis model is to see which elections and changes of prime minister are associated with changes in the prevalence of topics over time.
-By way of background, as Australia has a parliamentary system it is possible for the prime minister to change without an election and we do not distinguish between terms or cabinet composition although this more-detailed analysis is possible.
+By way of background, as Australia has a parliamentary system it is possible for the prime minister to change without an election.
 If a person was prime minister more than once then these periods are considered independently.
 
-As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level-effect for each prime minister, $\alpha_g$ and each election, $\alpha_e$.
-We identify differences between neighbouring prime ministers and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects.
+As detailed in Section \@ref(analysismodelexplanation), the model estimates an effect for each prime minister, $\alpha_g$ and each election, $\beta_e$.
+We identify differences between neighbouring prime ministers and between neighbouring elections based on calculating 95 per cent Bayesian credible intervals from posterior samples of these respective mean effects.
 When these do not overlap we consider that the model finds a difference between either the neighbouring prime ministers or elections, as appropriate.
@@
 We summarise our results in terms of prime ministers in Table \@ref(tab:primeministersresults) and in terms of elections in Table \@ref(tab:electionsresults).
-These tables focus on elections and prime ministers that were different to the ones that preceded them.
-Complete lists of the Australian elections and prime ministers are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
+These tables focus on prime ministers and elections that were different to the ones that preceded them.[^listfootnote] A total of XX out of the XX prime ministers had significantly different topic discussions than their predecessor.
+In terms of elections, XX out of a total of XX elections were significant different to the previous cycle.
+
+[^listfootnote]: Complete lists of the Australian elections and prime ministers are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).
 
@@
 In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between prime ministers and elections, respectively.
-In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified.
+In the graphs, the points show the estimated value of $\alpha_g$ and $\beta_e$, respectively, for each of the topics specified.
 The error bars represent 95 per cent Bayesian credible intervals.
-As there are 80 topics it would be unwieldy to show all of them, and so we have again focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.
+We have focused on Topics XX here which have to do with war and conflict.
+Large differences can be seen for XX ADD A BIT OF COMMENTARY HERE XX
 
@@
 
-### Additional results
+### Additional results: identifying outlying days
 
@@
 
-To do this we estimate sitting-period level-effects (essentially a mean for each topic by sitting period).
-The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days.
+The model set-up allows for these outlying days to be identified.
+In particular, we are estimating $\mu_{c,s,p}$, which can be thought of as the mean topic prevalence for topic $p$ in chamber $c$ and sitting period $s$.
+We can identify 'outlying days' by comparing this mean prevalence and a particular day's topic distribution.
 This approach means that the model generates dates that are interesting without us having to specify interesting dates.
@@
 
-Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. XX ADD A BIT OF COMMENTARY HERE XX
 

### 2019-11-01 outputs/docs/paper/paper_MA_structure_edit.Rmd
discussion

@@
 
+In this paper we explored changes in parliamentary discussion in association with changing prime minister and elections events in Australia.
+We used OCR and other text processing techniques to create a comprehensive dataset which covers parliamentary discussion in Australia throughout history since Federation in 1901 to the present day.
+We then used topic modeling to ascertain comparable topics of discussion over time, and a Bayesian hierarchical Dirichlet model to relate these topics to changes in elections and prime ministers.
+In general we find that changes in prime minister change the distribution of topics discussed in parliament, but that most elections did not.
+We find that significant events such as 9/11 and the Bali Bombings had a substantial effect.
+
 Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceded them, after we account for and remove some that had especially short terms.
@@
 
-# Summary, weaknesses and future work
-In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2018.
-We download and parse PDFs of Hansard to create a new dataset of text.
-We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model.
-In general we find that changes in prime minister change the distribution of topics discussed in parliament, but that most elections did not.
-We find that significant events such as 9/11 and the Bali Bombings had a substantial effect.
-
-By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia.
+## Limitations and future work
+
+<!-- By bringing a new dataset of what was said in the Australian Federal Parliament to bear for our analysis we are able to consider events over the full history of the Commonwealth of Australia.
 However even after cleaning the dataset remains imperfect and is more fit-for-purpose than of broad applicability.
@@
 For instance, exploiting the available XML records to enhance the record parsed from the PDFs would enable the creation of a Hansard for research purposes that combined the best of both and was more useful for variety of research.
+-->
 

### 2019-11-25 outputs/docs/paper/paper-hansarddataonly_test.Rmd
Update paper

--- 2019-04-01 outputs/docs/paper/paper.Rmd
@@
     template: svm-latex-ms.tex
-title: "The Increased Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament between 1901 and 2018"
-thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference.
+title: "A Text Corpus based on the Hansard of the Australian Federal Parliament between 1901 and 2018"
+thanks: "Thank you to Monica Alexander for her helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
 The code and data for this paper is available at: https://github.com/RohanAlexander/hansard.
@@
 - name: Rohan Alexander
-  affiliation: Australian National University
-- name: Monica Alexander
   affiliation: University of Toronto
@@
 
-Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceded them, after we account for and remove some that had especially short terms.
-The three earliest of them occur in the first decade after Federation, and to a certain extent this may be due to the variety of the issues that had to be addressed in those initial years.
-Joseph Cook's time as prime minister is found to be significantly different to that of his predecessor, Andrew Fisher, although it may be that this is due to World War I.
-
-The second Menzies term, beginning in 1949, is the next government that is significantly different to its predecessor.
+Of the 36 prime ministers over this period, we find that 17 of them were significantly different to the prime minister that preceeded them, after we account for and remove some that had especially short terms.
+The first three that are significant occur in the first decade after Federation.
+To a certain extent, this may be due to the variety of the issues that had to be addressed in those initial years.
+The fourth prime minister that was significantly different to his predecessor was Joseph Cook.
+This coincided with the initial period of World War I and it may be that this is the reason for difference, compared with his predecessor, and successor Andrew Fisher.
+
+Stanley Bruce is significantly different from his predecessor Billy Hughes, even though they were ostensibly from the same party.
+Hughes had been prime minister for over six years, and Bruce was a compromise choice in order to form a coalition.
+
+<!-- The Lyons 14 -->
+
+<!-- The second Menzies term, beginning in 1949, is the next government that is significantly different to its predecessor.
 The other governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years.
@@
 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.
-
-The second Menzies term was associated with a variety of changes compared with the preceding Chifley Government.
+-->
+
+<!-- The second Menzies term was associated with a variety of changes compared with the preceding Chifley Government.
 Chifley had governed through the end of World War II and the difficult economic times that followed.
@@
 Three toward the middle of that government were associated with significant changes in the topics discussed.
-
-Menzies was succeeded  Holt in January 1966.
+-->
+
+<!-- Menzies was succeeded  Holt in January 1966.
 This is an example where there was a change in prime minister without an election, as the next election only happened in November 1966.
 We find that Holt is different to Menzies.
-
-<!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->
-
-<!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} -->
-<!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") -->
-<!-- ``` -->
-
-Whitlam's term is especially interesting as we find a difference in the topics after he was first elected in December 1972, compared with his second election win in May 1974.
+-->
+
+<!-- <!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->
+
+<!-- <!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} --> 
+<!-- <!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") --> 
+<!-- <!-- ``` -->
+
+<!-- Whitlam's term is especially interesting as we find a difference in the topics after he was first elected in December 1972, compared with his second election win in May 1974.
 Figure \@ref(fig:muelectionall) compares the topics that are significant before and after the election.
-
-Howard is also interesting because of the significant differences between elections.
+-->
+
+<!-- Howard is also interesting because of the significant differences between elections.
 For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level.
 Figure \@ref(fig:muelectionall) compares the topics that are significant in the different elections that Howard won.
-
-To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
+-->
+
+<!-- To a certain extent the change after the November 2001 election is expected because of the 9/11 terrorist attacks that had only occurred two months earlier, the Bali Bombings that occurred in October 2002, and the dramatic increase in the discussion related to terrorism and conflict over these years.
 However, the change in 1998 and 2004 is more unexpected.
 Although Howard is the second-longest serving prime minister and commonly thought of as a period of stability because the senior ministers were consistent as well, it might be that it is better to think of Howard as a combination of three or four different periods and that Howard reinvented itself over this period.
+-->
 

### 2019-11-25 outputs/docs/paper/paper.Rmd
Update paper

@@
 - \usepackage{multirow}
-- \usepackage[table]{xcolor}
+# - \usepackage[table]{xcolor}
 - \usepackage{wrapfig}

### 2019-11-25 outputs/docs/paper/paper_MA_structure_edit.Rmd
Update paper

@@
 title: "The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018"
-thanks: "Thank you to Chris Cochrane, Dan Simpson, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
-We are grateful for the many excellent comments that we received from seminar participants at the ANU SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the U of T Political Behavior Group, and the 2019 PSA Political Methodology Conference.
+thanks: "Thank you to Chris Cochrane, Dan Simpson, Edward Morgan, Jill Sheppard, John McAndrews, John Tang, Leslie Root, Martine Mariotti, Matt Jacob, Matthew Kerby, Myles Clark, Ruth Howlett, Tianyi Wang, Tim Hatton, and Zach Ward for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources.
+We are grateful for the many excellent comments that we received from seminar participants at the Australian National University (ANU) SPIR, the ANU RSE, the Australian Parliamentary Library, the Max Planck Institute for Demographic Research, the University of Toronto Political Behavior Group, and the 2019 PSA Political Methodology Conference.
 The code and data for this paper is available at: https://github.com/RohanAlexander/hansard.
-Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
+Comments and suggestions on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@utoronto.ca."
 author:
 - name: Rohan Alexander
-  affiliation: Australian National University
+  affiliation: University of Toronto
 - name: Monica Alexander
@@
 - \usepackage{multirow}
-- \usepackage[table]{xcolor}
 - \usepackage{wrapfig}
@@
 What is discussed in parliament is a key indicator of a government's priorities and likely policy outcomes.
-While in an ideal world, we may hope that topics of discussion represent the most important social, economic and environmental issues for the country at that particular time, in reality, discussion is heavily influenced by party politics, the priorities of the head of government at the time, and where they are in the current election cycle.
-
-For example, XX NEED A BIT OF A LITERATURE REVIEW HERE on papers that look at discussion and political changes?? XX
+While in an ideal world, we may hope that topics of discussion represent the most important social, economic, and environmental issues for the country at that particular time, in reality, discussion is heavily influenced by party politics, the priorities of the government of the day, and the current election cycle.
+
+<!-- TODO: For example, XX NEED A BIT OF A LITERATURE REVIEW HERE on papers that look at discussion and political changes?? XX -->
 
@@
 
-In this paper, we exame the effect of elections and changes in prime ministers on the topics that are discussed in the Australian Federal Parliament.
+In this paper, we examine the effect of elections and changes in prime ministers on the topics that are discussed in the Australian Federal Parliament.
 We construct a new dataset from the text record, known as 'Hansard', of what was said in the Australian Federal Parliament since its inception in 1908, to 2018.
@@
 
-The remainder of the paper is structured as follows XX.
+The remainder of the paper is structured as follows.
+Section \@ref(hansarddata) examines the data that we use; Section \@ref(model) introduces our models; Section \@ref(results) goes into our results; and finally, Section \@ref(discussion) discusses our results and some of the shortcomings.
 
@@
 The Australian Federal Parliament makes daily Hansard records available online as PDFs and these are considered the official release.[^XMLfootnote] We provide an example of a Hansard PDF page in Appendix \@ref(examplehansardpage).
-There are XX PDF files that cover the Hansard over the entire period 1901-2018.
+There are 14,680 PDF files that cover the Hansard over the entire period 1901-2018.
 Our goal is to take these PDFs and convert them into a digitized dataset of text that is able to be analysed.
@@
 Thirdly, the text is split out such that it is separated by speaker.
-This involves XX.
-Lastly, the dataset is created in tidy format (XX REF here), such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker.
-XX could add more detail to this paragraph XX
+This involves identifying names and the structure of how speakers are introduced and then splitting based on this.
+Lastly, the dataset is created in tidy format [@wickham2014tidy], such that there are columns for speaker, the date, and the text of what was said, and every row refers to a different speaker.
+<!-- XX could add more detail to this paragraph XX -->
 
@@
 In general, the frequency of sitting days based on information from the Hansard dataset compared to the actual number of sitting days is comparable, almost complete coverage of our dataset.
-XX MAYBE PULL OUT MORE SUMMARY STATS IN PARTICULAR HIGHLIGHT THE TWO CHAMBERS XX
+<!-- XX MAYBE PULL OUT MORE SUMMARY STATS IN PARTICULAR HIGHLIGHT THE TWO CHAMBERS XX -->
 
@@
 Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen based on the output of the CTM.
-However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised or examined.
+However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised, or examined.
 In addition, many of the topics in the optimal set referred to similar themes, such as budgeting or administrative topics.
 
-For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. XX NEED TO EXPLAIN WHAT THIS IS - I HAVE NO IDEA XX
+For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project.
+The Comparative Agendas Project provides a classification of a large number of specific issues into a small number of major topics.
 
@@
 
-```{r topwords, echo = FALSE, results = 'asis'}
-# 
-# top_words %>% 
-#   kable("latex", 
-#         booktabs = T, 
-#         longtable = TRUE, 
-#         caption = "The ten words most strongly associated with each topic"
-#         ) %>%
-#   kable_styling(font_size = 8, 
-#                 latex_options = c("repeat_header")
-#                 )
-```
+<!-- # ```{r topwords, echo = FALSE, results = 'asis'} -->
+<!-- # #  -->
+<!-- # # top_words %>%  -->
+<!-- # #   kable("latex",  -->
+<!-- # #         booktabs = T,  -->
+<!-- # #         longtable = TRUE,  -->
+<!-- # #         caption = "The ten words most strongly associated with each topic" -->
+<!-- # #         ) %>% -->
+<!-- # #   kable_styling(font_size = 8,  -->
+<!-- # #                 latex_options = c("repeat_header") -->
+<!-- # #                 ) -->
+<!-- # ``` -->
 
@@
 The analysis model needs to be able to deal with this situation.
-XX I FIND THESE FIGURES HARD TO READ...
-CONSIDER REDOING OR REMOVING XX
+<!-- XX I FIND THESE FIGURES HARD TO READ... CONSIDER REDOING OR REMOVING XX -->
 
@@
 For example, the model provides estimates of topic prevalence by each sitting period.
-Figure \@ref(fig:wartopicsgraph) illustrates the estimated topic prevlance by sitting period for topic XX, one of the defense-related topics, overlayed with the daily topic prevalnce (as also illustrated in Figure XX above).
+Figure \@ref(fig:wartopicsgraph) illustrates the estimated topic prevlance by sitting period for topic 15, one of the defense-related topics, overlayed with the daily topic prevalence (as also illustrated in Figure \@ref(fig:threeexamples) above).
 This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable.
@@
 We summarise our results in terms of prime ministers in Table \@ref(tab:primeministersresults) and in terms of elections in Table \@ref(tab:electionsresults).
-These tables focus on prime ministers and elections that were different to the ones that preceded them.[^listfootnote] A total of XX out of the XX prime ministers had significantly different topic discussions than their predecessor.
-In terms of elections, XX out of a total of XX elections were significant different to the previous cycle.
+These tables focus on prime ministers and elections that were different to the ones that preceded them.[^listfootnote] A total of 17 out of the 36 prime ministerial periods had significantly different topic discussions than their predecessor.
+In terms of elections, 12 out of a total of 45 elections were significantly different to the previous cycle.
 
@@
 The error bars represent 95 per cent Bayesian credible intervals.
-We have focused on Topics XX here which have to do with war and conflict.
-Large differences can be seen for XX ADD A BIT OF COMMENTARY HERE XX
+We have focused on Topics 1, 2, 7, 13, 15, 16, 17, and 19 here which have to do with war and conflict.
+Large differences can be seen at various times.
+<!-- XX ADD A BIT OF COMMENTARY HERE XX -->
 
@@
 
-Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week. XX ADD A BIT OF COMMENTARY HERE XX
+Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.
+Notably, considerably more than a majority of these dates occur in the first half of our sample.
+And a full seven occur in 1909.
 
@@
 
-<!-- In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt. -->
-
-<!-- ```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'} -->
-<!-- knitr::include_graphics("../../figures/mu_election-differences.pdf") -->
-<!-- ``` -->
+In Figures \@ref(fig:muelectionall) we compare the topics during Menzies' final term with the topics of Holt.
+
+```{r muelectionall, cache = TRUE, echo = FALSE, fig.cap = "Differences between various elections", out.width = '100%'}
+knitr::include_graphics("../../figures/mu_election-differences.pdf")
+```
 

### 2019-11-25 scripts/alt_run_2_parse_pdfs_ABBYY_outputs/parse_each_pdf_and_save_csv_tm.R

@@ -1,0 +1,185 @@
+# !diagnostics off
+#### Preamble ####
+# Purpose: This file takes Australian Hansard PDF files and it converts them to tidied text data that can be analysed.
+# Author: Rohan Alexander
+# Email: rohan.alexander@anu.edu.au
+# Last updated: 2 September 2018
+# Prerequisites: You need to have downloaded the PDFs from the parliament's website, e.g. get_80s_and_90s_PDFs.R. There are many GBs of PDFs and they are saved on an external drive - have fun finding that future-Rohan. For testing purposes there should be some in the /data folder.
+# To do:
+# - Identify and remove front matter
+# - Identify and remove headers/footers
+# - Deal with two columns better
+# - Identify speakers
+
+
+#### Set up workspace ####
+# library(stringi)
+# library(stringr)
+library(tidyverse)
+library(tm)
+# update.packages()
+
+# Get the spell checker
+load("outputs/corrections.RData")
+
+
+#### Read in PDFs ####
+read <-
+  readPDF(engine = c("xpdf")) # Despite the name this affects the options for how to read PDFs, it doesn't actually read the PDFs. -layout asks it to maintain the layout as best as possible.
+# Handy for background: https://data.library.virginia.edu/reading-pdf-files-into-r-for-text-mining/
+read <-
+  readPDF(engine = c("xpdf"), control = list(info = "-f")) # I don't know why, but some of the more recent ones don't work with the above, but do work with this one
+# An alternative is here that tries to maintain the layout:
+# read <- readPDF(engine = c("xpdf"), control = list(text = "-layout"))
+# Engine options: c("pdftools", "xpdf", "Rpoppler", "ghostscript", "Rcampdf", "custom")
+# If you use pdftools then you need to split the lines - there's some code below in a playground to get started
+# Handy example of UN speeches: https://medium.com/@CharlesBordet/how-to-extract-and-clean-data-from-pdf-files-in-r-da11964e252e
+# The issue with this is that the PDFs are two column - the version without trying to maintain layout just seems to put the second column under the first one, which is what we'd want.
+
+
[…]

### 2019-11-25 scripts/run_2_parse_pdfs/run_1_parse_each_pdf_and_remove_front_matter.R

@@ -31,11 +31,14 @@ plan(multiprocess)
 # Change the path as required:
 # use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
 # use_this_path_to_get_pdfs  <- "inputs/for_testing_pdfs"
-use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
+# use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
+use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/senate"
+
 
 # use_this_path_to_save_csv_files  <- "outputs/hansard/run_1_output"
 # use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"
-use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/for_zoe/run_1_output"
+# use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/for_zoe/run_1_output"
+use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/senate/run_1_output"
 
 # Get list of Hansard PDF filenames
 file_names <-
@@ -51,7 +54,7 @@ file_names <- file_names %>% sample() # Randomise the order
 file_tibble <- tibble(filename = file_names)
 file_tibble <- file_tibble %>% 
   mutate(the_year = filename,
-         the_year = str_replace(the_year, "/Volumes/Hansard/pdfs/federal/hor/", ""),
+         the_year = str_replace(the_year, "/Volumes/Hansard/pdfs/federal/senate/", ""),
          the_year = str_replace(the_year, ".pdf", ""),
          the_year = ymd(the_year)) %>% 
   # filter(year(the_year) < 1981) %>% 
